### 2017-08-22 paper_notes.tex
Initial commit

\documentclass{book}
\usepackage[utf8]{inputenc}
\usepackage{indentfirst}	% make indent in first paragraph
\usepackage{bm}
\usepackage{geometry}		% to make typesettings like margins
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{natbib}			% to insert citations
\usepackage{xcolor}			% extend the colors can be used

\usepackage{bibentry}		% package used to insert full citation in body text
\nobibliography*

\usepackage[framemethod=default]{mdframed}
\usepackage{showexpl}
\mdfdefinestyle{comment}{
linecolor=gray,leftmargin=60,
rightmargin=40,
backgroundcolor=gray!10,
innertopmargin=4pt,
topline=false,leftline=false,bottomline=false,rightline=false}

\usepackage[english]{babel}
\renewcommand{\baselinestretch}{1.5}

\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{thm}{Theorem}[section] % reset theorem numbering for each chapter
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition} % definition numbers are dependent on theorem numbers
\newtheorem{exmp}[thm]{Example} % same for example numbers
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{obs}{Observation}

\citestyle{chicago}
\geometry{letterpaper, margin=1in}
% \setlength\parindent{0pt} % to cancel indent

% A list of new commands
\newcommand{\R}{\mathbb{R}}			% depends on the package amssymb

\title{Paper Notes}
\author{Kaida Zhang}
\date{}

\begin{document}

% \maketitle

\tableofcontents{}
\setcounter{tocdepth}{1}			% show only parts, chapters, and sections in content

\chapter{Econometrics}
\label{cha:econometrics}

\section{Low and Meghir, 2017, JEP} % (fold)
\label{sec:low_and_meghir_jep_2017}

\textbf{\bibentry{Low:2017jb}}\\

\textbf{Defining a structural model:}

A \textbf{fully specified model} make explicit assumptions about the economic actors' objectives and their economic enviroment and information set, as well as specifying which choices are being made within the model. They allow a complete solution to the individual's optimization problem as a function of current information set.
Fully specified models are particularly useful in understanding mechanism of a policy, especially when we want to estimate some long-term effects of the policy.

A \textbf{partially specified model} relies on a sufficient statistic that summarizes choices not being modeled specifically. For example, assuming that the choices is only intratemporal instead of intertemporal.

\textbf{Treatment effect models} focus on identifying a specific causal effect of a policy while saying least about the theoretical environment. The pro is the cleaness of causality. The con is the limitation in exploiting the results outside. The identification of treatment model depends on assumptions that the experienment has not been compromised and there is no spillovers from the treatment units.

A combination of fully speficied model and randomized experiments can enhance anaysis for both. Experimental evidence can be used either to validate a structural model, or to aid in the estimation process (in identification).

\textbf{Solving structural models}

This has been described in Adda and Cooper(2003) well. 
The general process is: 
1) write down the bellmand function;
2) discrete the state space and decision space;
3) use value function iteration to solve the bellman function.

% section low_and_meghir_jep_2017 (end)

\section{Lewbel, 2016, JEL} % (fold)
\label{sec:lewbel_2016_jel}

\textbf{\bibentry{Lewbel:2016wn}}\\

\url{https://www2.bc.edu/arthur-lewbel/ident-zoo-SL-Part1.pdf}

\url{https://www2.bc.edu/arthur-lewbel/ident-zoo-SL-Part2.pdf}

are links for a ppt on this paper by Lewbel.\\

There are two kinds of identification problems. 
1. One is to identify the treatment effect, a typical example is the selection bias. The problem in these cases are that selection (determing who is treated or observed) and outcomes may be correlated. 
2. Another is to identify the true coefficient in a linear regression when regressors are measureed with error.

\subsection{Point Identification} % (fold)
\label{sub:point_identification}

We start by assuming some information $\phi$ is knowable. A simple definition of point identification is that a parameter $\theta$ is point identified if, given the model, is uniquely determined from $\phi$. Notice that this definition of point identification is recursive in some sense. To identify $\theta$, we first need to assume some $\phi$ is knowable, which means $\phi$ itself is identified. This identification of $\phi$ can only be justified by further assumptions of DGP (Data Generating Process).

For example, for a model $Y = X\theta +e$, we assume that $E(E^2)\ne0$ and $E(eX)=0$, and suppose $\phi$ includes the second order of $(Y,X)$. Then we can conclude that $\phi$ is point identified, given by $E(XY)/E(X^2)$. Notice that the identification comes from the \textit{assumptions} of model.

One common DGP is IID. Under this DGP, we can consistently indentify the distribution of observation W. Another DGP is where each data point consists of a value of X chosen from its support, then we randomly draw Y conditional on X, which is independent from other draws conditional on this X. Under this DGP, we can consistently identify $F(Y|X)$. We can also use more complicated DGPs, for example, we generally assume only the second order moments are knowable in time series. One reason is this being sufficient for identification, another reason is higher order moments become unstable over time. Assumptions over GDP are always needed, even in experienment data, and which specific assumptions to take depend on the model.

% subsection point_identification (end)

% section lewbel_2016_jel (end)

% chapter econometrics (end)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% IO %%%%%%%%%%%%%%%%%%%%%%

\chapter{IO} % (fold)
\label{cha:io}

\section{Rey and Stiglitz, 1995, RAND} % (fold)
\label{sec:rey_and_stiglitz_1995_rand}

\textbf{\bibentry{Rey:1995ft}}

For detailed proof of this paper, see Evernote.\\

\textbf{Main result:}
vertical restrains can be used to reduce interband competition. Because exclusive territories alter the perceived demand curve, making each producer believe he faces a less elastic demand curve, inducing an increase in eqm price and producer's profits even in the abscence of franchise fee. This result is different from traditional Chicago school results, which insist that exclusive terittories will increase efficiency. This difference comes from market structure. Chicago schools investigate in full competition and full monopoly producer cases, while this paper looks at duopoly producer. In full competition and full monopoly case, the competition level has already been \textit{preassumed}, while exclusive territories can reduce the competition level among producers in other cases.\\

The key for the result is the the following compound demand elastic:
\[\tilde\varepsilon(p^e):=m_1(p,p)\varepsilon_1(q,q)+m_2(p,p)\varepsilon_2(q,q) \]
where $q=q_1^r(p,p)$ (the response retail price),
$m_1(p,p)=\partial \log q_1^r(p_1,p_2)/\partial \log p_1$ (the own elasticity of retail price to producer price),
and  $m_2(p,p)=\partial \log q_1^r(p_1,p_2)/\partial \log p_2$ (the cross elasticity of retail price to producer price),
and $\varepsilon_1(q_1,q_2)=-\partial \log D^1(q_1,q_2)/q_1$ (the own elasticity of demand to retail price, positive),
and $\varepsilon_2(q_1,q_2)=-\partial \log D^1(q_1,q_2)/q_2$ (the cross elasticity of demand to retail price, negative).

In the above equation, it is very reasonable to think $0<m_1<1$ and $0<m_2$. $m_1>0$ because the own elasticity of retail price to producer price is positive. $m_1<1$ means that retailer will absorb some increase in producers' price, which will be the case if demand elasticity becomes higher in high retail price. And $0<m_2$ derives from the two products to be substitutes. Under these two conditions, combined with $\varepsilon_1>0$ and $\varepsilon_2<0$, then $\tilde\varepsilon(p^e)<\varepsilon_1$. Thus, under exclusive territories, the producers' perceived demand curve is less elastic. So the equilibrium price (both retail and producer) is higher even when no franchise fee applies.

\noindent
\textbf{Setting:}

\begin{itemize}
	\item two manufacturers produce imperfect substitutes at same marginal cost \textit{c}
	\item retailers are perfect competition / or exclusive territory
	\item the final good demand depends on retail prices and is given by $D^i(q_1,q_2)$
	\item costs and demand functions are common knowledge, retailers observe all contracts signed by each producer
	\item producers only observer the quantity bought by retailers; they do not observe the quantities sold by retailers (i.e. fullline forcing is infeasible)
	\item producers serve many markets at no addtional cost
	\item consumers have no search cost
\end{itemize}

Under these settings and information conditions, we can see it as a two stave game. In the first stage, producers simultaneously set wholesale price $p_1$ and $p_2$. In the second stage, the retailer observe all wholesale price and decide the retail price simutaneously.

\subsection{Benchmark Case} % (fold)
\label{sub:benchmark}

We use the following assumptions throughout the paper unless specified otherwise:

\begin{enumerate}
	\item Let $\pi(p_i,q_1,q_2) := (q_i-p_i)D^i(q_1,q_2)$ denote the retail profit for product i; assume it to be twice differentiable wrt each argument, and is sigle peaked wrt $q_i$. The reaction function $q_i^a(p_i,q_j)$ is thus continously differentiable and characterized by FOC.
	\item Products are substitutes: $\partial D^i/\partial q_i \leq 0$ and $\partial D^i/\partial q_j \geq 0$
	\item Demand functions are symmetric: $\forall p_1,p_2 \in \R_+, D^1(p_1,p_2) = D^2(p_2,p_1)$
\end{enumerate}

Think of the benckmark case that no vertical restriction so the retailers are perfect competitive, and the producer monopolizes. In this case, the game is just a one step optimal pricing problem. The producer chooses an optimal retail price.\\

\begin{mdframed}[style=comment]

\noindent
\textbf{Useful trick:}

Throughout this paper, we can write the symmetric eqm conditions in the following form:
\[(p^c - c)/p^c=1/\varepsilon(p^c,p^c)\]
where $p^c$ is the symmetric eqm price, and $\varepsilon$ is some kind of elasticity.

In a symmetric eqm, the FOC of each producer gives 
\((p^c - c)/p^c=1/\varepsilon_1(p^c,p^c)\)
where $\varepsilon_1 = -\partial \log D^1(q_1,q_2)/\partial \log q_1$, i.e. the self elasticity of demand.

In the simplest benchmark case, the two factories are integrated, leading us to:
\((p^c - c)/p^c=1/E(q^m)\),
$E(q):=\varepsilon_1(q,q)+\varepsilon_2(q,q)$, where $\varepsilon_2 = -\partial \log D^1(q_1,q_2)/\partial \log q_2$ (the cross demand elasticity).

In the exclusive territory case, the symmetric eqm satisfies \((p^e - c)/p^e=1/\tilde\varepsilon(p^e)\), where 
\[\tilde\varepsilon(p^e):=m_1(p,p)\varepsilon_1(q,q)+m_2(p,p)\varepsilon_2(q,q) \]
where $q=q_1^r(p,p)$ (the response retail price),
$m_1(p,p)=\partial \log q_1^r(p_1,p_2)/\partial \log p_1$ (the own elasticity of retail price to producer price),
and  $m_2(p,p)=\partial \log q_1^r(p_1,p_2)/\partial \log p_2$ (the cross elasticity of retail price to producer price).

\end{mdframed}

% subsection benchmark (end)

% section patrick_and_stiglitz_1995_rand (end)

% chapter io (end)

\chapter{Decision Theory} % (fold)
\label{cha:decision_theory}

\section{Dekel and Lipman, 2010, Annu Rev Econ} % (fold)
\label{sec:dekel_and_lipman_2010_annu_rev_econ}

\textbf{\bibentry{Dekel:2010bm}}\\

\noindent
\textbf{What we can learn from decision theory}

1) to know whether our intuition is correct;
2) to flesh out initial intuition to get additional or better prediction (e.g. some additional observable prediction);
3) to help us understand of why and how mechanism works

\noindent
\textbf{Story of the model}

Why the story of the model is important even if it is not realistic? Why we can't just choose the model by the 'prediction-rejection' procedure?

1) The story makes us believe the predictions more;
2) Having a nice intuition helps us to utilize the model and to expand the model;
3) And a model can never be realistic, the important thing is whether it captures something important.

% section dekel_and_lipman_2010_annu_rev_econ (end)

% chapter decision_theory (end)

\renewcommand\refname{Reference}
\bibliographystyle{plainnat}
\bibliography{paper_notes}

\end{document}

### 2017-08-24 paper_notes.tex
Add kiyotaki 2011.
Add Gale and Shapley, 1962. Initialize matching theorem.

@@
 
+\chapter{Matching Theory} % (fold)
+\label{cha:matching_theory}
+
+\section{Gale and Shapley, 1962} % (fold)
+\label{sec:gale_and_shapley_1962}
+
+\textbf{\bibentry{Gale:1962kl}}
+
+This paper introduces Deffered Acceptance (DA) algorithms in matching, and shows that it is stable and optimal.
+
+\begin{defn}
+An assignment is called \textbf{unstable} if there are two applicants $\alpha$ and $\beta$ who are assigned to universities A and B, although $\beta$ prefers A to B and A prefers $\beta$ to $\alpha$.
+\end{defn}
+
+\begin{defn}
+A stable assignment is called \textbf{optimal} if \textit{every} applicant is at least as well off under it as under any other stable assignments.
+\end{defn}
+
+Comment: it loos at first that optimal assignments may not always exist. But as we will show constructively, it does.
+
+\begin{defn}
+\textbf{Deferred Acceptance algorithm} works as following.
+First let each boy propose to his favorite girl.
+Each girl who receives more than one proposal rejects all but her favorite boy.
+Yet, she doesn't accept him, but keeps him in a string to allow for the better may come later.
+Then in the second round, each rejected boy propose their second favorite girl, and each girl picks her favorite among the new proposers and the one in the string, and put him in her string.
+This process continues, until each girl has one boy in the string (this will happen after finite rounds), then each girl picks the boy in her string.
+\end{defn}
+
+We will show the assignment by above algorithm is stable and optimal.
+
+% section gale_and_shapley_1962 (end)
+
+% chapter matching_theory (end)
+
+\chapter{Macro} % (fold)
+\label{cha:chapter_name}
+
+\section{Kiyotaki, 2011} % (fold)
+\label{sec:kiyotaki_2011}
+
+\textbf{\bibentry{Kiyotaki:2011fc}}
+
+This paper mainly discusses the micro structures which may induce financial friction (inefficiency).
+These structures include private information of income, private technology for storage, limited commitment and their combinations.
+
+% section kiyotaki_2011 (end)
+
+% chapter chapter_name (end)
+
 \renewcommand\refname{Reference}

### 2017-09-05 paper_notes.tex
Initiate Section 'Production Function Estimation' under IO.

@@
 
+\section{Production Function Estimation} % (fold)
+\label{sec:production_function_estimation}
+
+There are several difficulties in estimating production functions which will cause endogeneity problem. To name some:
+\begin{itemize}
+	\item Simultaneouty.
+For a production function like $y_{it}=\beta_0+\beta_1 k_{it}+\beta_2 l_{it} + \omega_{it}+\varepsilon_{it}$, we suppose that $\omega_{it}$ is obseved by firm but not by econometricians, and $\varepsilon_{it}$ is observed neither by firm nor econometrician.
+This could induce endogeneity when directly using OLS.
+Suppose $\omega_{it}$ has positive serial correlation, when $\omega_{it}$ is high, firm will choose higher input bacause it is very possible that $\omega$ in next period will be high as well.
+This induces a positive bias for $\beta_k$.
+	\item Exit selection bias. When constructing a balanced panel, then we only observe those firms with high $\omega_{it}$.
+\end{itemize}
+
+There are several approaches in solving this problem.
+
+\begin{itemize}
+	\item Classical Approach.
+	\begin{itemize}
+		\item Use input price as IV.
+The problem is input price is generally the same across firms.
+When we do observe different input prices, which generally indicates market power in input markets.
+Thus those facing higher $\omega_i$ will tend to produce more, inducing their input price to increase, which has a negative bias on $\beta_k$.
+		\item Use fixed effect. If we assume that a firm faces same $\omega_{it}$ across time, which is not very practical.
+	\end{itemize}
+	\item Proxy for $\omega_{it}$.
+This approach first raised by \cite{Olley:1996ef} and developed by \cite{Levinsohn:2003ej} and \cite{Ackerberg:2015ha}.
+We name them OP, LP, ACF here after.
+The key idea is to use a function of what we know (for example, $k_t$ and $i_{t-1}$ in OP) to proxy $\omega$, the existence of such function is guaranteed by the solutioin property of the firm optimization problem.
+And the specific form of this function is estimated nonparametrically.
+\end{itemize}
+
+% section production_function_estimation (end)
+
 % chapter io (end)

### 2017-09-10 paper_notes.tex
Add section log-linearization. Add section production function estimation.

@@
 \usepackage{hyperref}
+\usepackage{amsmath}
 \usepackage{natbib}			% to insert citations
@@
 Thus those facing higher $\omega_i$ will tend to produce more, inducing their input price to increase, which has a negative bias on $\beta_k$.
-		\item Use fixed effect. If we assume that a firm faces same $\omega_{it}$ across time, which is not very practical.
+		\item Use fixed effect. We need to assume that a firm faces same $\omega_{it}$ across time, which is not very practical.
 	\end{itemize}
-	\item Proxy for $\omega_{it}$.
+	\item Control Function for  $\omega_{it}$.
 This approach first raised by \cite{Olley:1996ef} and developed by \cite{Levinsohn:2003ej} and \cite{Ackerberg:2015ha}.
@@
 And the specific form of this function is estimated nonparametrically.
+	\begin{itemize}
+		\item OP uses a two step estimation process.
+First step, use $k_t$ and $i_{t-1}$ nonparametrically estimate $\omega_t$, plug this into original production function then use OLS.
+Notice the unobserved $\omega_t$ has been controled by $k_t$ and $i_{t-1}$, then OLS will give consistent estimator for $l_t$ but not $k_t$.
+In second step, we first write $\omega_{it} = E[\omega_{it}|\omega_{it-1}]+\xi_{it}$, notice that $\xi_{it}$ is independent of any information set at t-1.
+Thus we get the moment condition $E[\xi_{it}k_{it}]=0$, then we can use method of simulating moments to estimate $\beta_k$.
+		\item LP is very similar to OP, just that use intermediate input $m_{it}$ instead of investment $i_{it}$ in proxy $\omega_{it}$.
+Because OP approach requires the policy function of $i_{it}$ be monotonicity in $\omega_{it}$, which is unsatisfied when $i_{it}=0$.
+But data shows that in many observations $i=0$.
+Using intermediate input can solve this.
+		\item ACF critizition is
+	\end{itemize}
+	\item \cite{Gandhi:2017un} Approach (GNR).
+GNR criticizes control function approach is nonparametrically not identified in the presence of flexible inputs.
+They raise a new approach using FOC conditions.
 \end{itemize}
@@
 
+\chapter{General (mathematical) Skills} % (fold)
+\label{cha:general_mathematical_skills}
+
+\section{Log-Linearization}
+
+\noindent
+\textbf{Motivation}
+
+Why we need log linearizations?
+Because for most nonlinear discrete dynamic programming problems,
+we fail to find a closed solution.
+Thus we have to use numerical method or to find a approximation.
+By using log-linearization,
+we transform the nonlinear problem to a linear problem (around the steady state),
+and we know how to solve the linear diffrence equations.
+
+Another advantege of log-linearization is,
+the new variables are in forms of $\frac{x-x^*}{x^*}$,
+which is interpretable.\\
+
+% subsection: how to do log-linearization
+\subsection{How to do Log-Linearization}
+
+Log linearization is a common method to approximate non-linear function using Taylor expansion.
+
+When we do linearization in macroeconomics, one key is to find \emph{\textbf{steady state}} of the model.
+Then we do linearization aroud the steady state.
+
+The basic idea is, for functions like:
+\[f(x)=\frac{g(x)}{h(x)}\]
+
+take log in both sides:
+\[ln(f(x))=ln(g(x))-ln(h(x))\]
+
+By Taylor expansion, for a smooth function f(x) we have:
+\[f(x)=f(x^*)+\frac{f'(x^*)}{1!}(x-x^*)+o(1)\]
+
+Thus 
+\[lnf(x) \approx lnf(x^*)+\frac{f'(x^*)}{f(x^*)}(x-x^*)\]
+
+The above follows from the fact that $\frac{dln(f(x))}{dx}=\frac{f'(x)}{f(x)}$. Thus,
+\[lnf(x)-lnf(x^*)=\frac{f'(x^*)}{f(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}\]
+
+And the equation becomes:
+\[lnf(x^*)+\frac{f'(x^*)}{f(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}=lng(x^*)-lnh(x^*)
+\frac{g'(x^*)}{g(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}-
+\frac{h'(x^*)}{h(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}\]
+
+\[\frac{f'(x^*)}{f(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}=
+\frac{g'(x^*)}{g(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}-
+\frac{h'(x^*)}{h(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}\]
+
+Dedine $\hat x=\frac{x-x^*}{x^*}$, and we are done.
+\[\frac{f'(x^*)}{f(x^*)} x^* \cdot \hat x=
+\frac{g'(x^*)}{g(x^*)} x^* \cdot \hat x-
+\frac{h'(x^*)}{h(x^*)} x^* \cdot \hat x\]
+
+Notice, when we use $\hat x$ in place of $x-x^*$in the approximation,
+don't forget to times $x^*$ !!\\
+
+% How to do log-linearization when there is Expectation
+
+\subsection{log-linearization when there is expectation (An Example)}
+
+It may be annoying to do log-linearization when there is expectation,
+because in general,
+log and expectation cannot switch.
+But if we don't switch, we cannot do the log-linearization as previous.
+For example, see Adda\&Cooper(2003) CH5, page 115.
+
+Suppose we have the following Euler equation:
+
+\[u'(c)=\beta E_{A'|A}u'(c)[Af'(k')+(1-\delta)]\]
+
+where $c=Af(k)+(1-\delta)k-k'$.
+
+These two expressions, along with the evolution of A,
+defines a system of equations.
+
+In this system, actually we do not have to take log,
+but directly do Taylor expansion at $c^*$, $x^*$ and $k^*$.
+We get:
+
+\begin{multline}
+u'(c^*)+u''(c^*)c^*\hat c_t=
+\beta E_{A'|A}[u'(c^*)(\bar Af'(k^*)+(1-\delta))
++(\bar Af'(k^*)+(1-\delta))u''(c^*)c^*\hat c_{t+1}\\
++u'(c^*)f'(k^*)\bar A\hat A_{t+1}+
+u'(c^*)\bar Af''(k^*)k^* \hat k_{t+1}]
+\end{multline}
+
+The first term in LHS and the first term in RHS cancel each other.
+And we divide both sides by $u'(c^*)$, and we will get:
+
+\begin{equation}\label{eq1}
+\frac{u''(c^*)c^*}{u'(c^*)}\hat c_t
+=\beta E_{A|A'}[\frac{u''(c^*)c^*}{u'(c^*)}\hat c_{t+1} \frac{1}{\beta}
++f'(k^*)\bar A \hat A{t+1}
++f''(k^*)k^*\hat k_{t+1}]
+\end{equation}
+
+Notice, we derive this based on the fact $\frac{1}{\beta}=\bar A f'(k^*)+(1-\delta)$.
+Because by FOC
+\[u'(c)=\beta E_{A'|A}V'(k')\]
+
+To derive $V'(k')$, we first derive $V'(k)$,
+by Envelop THM we get:
+\[V'(k)=u'(c)[Af'(k)+(1-\delta)]\]
+
+Substitute this into FOC we get:
+\[u'(c)=\beta E_{A|A'}[u'(c')(A'f'(k')+(1-\delta))]\]
+
+In this approach we fix A at the mean $\bar A$,
+and thus the steady state satisfy:
+\[1=\beta [\bar Af'(k^*)+(1-\delta)]\]
+
+Here, the introduce of $\bar A$ is to describe the steady state in existence of shock.
+We can see $\bar A$ as the "long term" growth of the economy,
+and the we investigate what's the optimal steady $k^*$ under this long-term growth rate.
+
+\textcolor{red}
+{But I still don't know why we can cancel the expectation in the RHS.}
+
+The equation \ref{eq1} is the linear function we want.\\
+
+\noindent
+\emph{Some Comments on the above method:}
+
+Although it seems that the above method uses no log-linearization,
+actually it does!
+
+(to be added later)
+
+% section log-linearization (end)
+
+% chapter general_mathematical_skills (end)
+
 \renewcommand\refname{Reference}

### 2017-09-18 paper_notes.tex
Add .gitignore file. Add Costly State Verification and Collataral Borrowing section in Macro chapter.

@@
 \nobibliography*
+
+\usepackage{graphicx}		% to insert image
+\graphicspath{ {images/} }
 
@@
 
-\section{Gale and Shapley, 1962} % (fold)
+\section{Gale and Shapley, 1962, Ame.Math.Mon.} % (fold)
 \label{sec:gale_and_shapley_1962}
@@
 
-% chapter chapter_name (end)
+\section{Costly State Verification} % (fold)
+\label{sec:costly_state_verification}
+
+Financial frictions is an important yet not well explained phenomena.
+Generally financial frictions means some possible financial frictions not happening, resulting in fluctuations in real economy.
+There are several micro foundations for financial frictions, we learned some in Ruilin's course:
+\begin{itemize}
+	\item costly state verification
+	\item collateral constraints
+	\item moral hazard
+	\item asymmetric information
+\end{itemize}
+
+The main framework for costly state verification is following.
+The borrower has some private information on productivity, and lender has to pay some cost to get this information.
+This will give the borrower some advantage, and make some possible transactions unable to happen.
+\cite{Townsend:1979ef} gives a micro model describing contract under costly state verification.
+\cite{BenBernanke:1989eg} and \cite{Carlstrom:1997fb} are two important works using this to explain business cycles (also called Financial Accelarator).
+
+\textcolor{red}{Add breif introduction for costly state verification literature.}
+
+% section costly_state_verification (end)
+
+\section{Collateral Constraints} % (fold)
+\label{sec:collateral_constraints}
+
+Another explaination for financial friction is collateral constraint. Important literatures include \cite{Kiyotaki:1997hl},
+
+\cite{Kiyotaki:1997hl} has a simple idea.
+Suppose the borrower needs some collateral (say land) for borrowing.
+What is the effect of a temporary increase in land productivity?
+The direct effect is it will increase this period land price.
+More important is the indirect effect, the borrower now can buy more land since their collateral becomes more valuable.
+And thus in next period they can buy even more land.
+This long chain has a large effect on the initial price of the land.
+Thus financial sector can amplify the fluctuation of real economy.
+
+\includegraphics[width=\textwidth]{kiyotaki-moore-97.png}
+
+% section collateral_constraints (end)
+
+% chapter macro (end)
 

### 2017-12-10 paper_notes.tex
normal update

@@
 \usepackage{hyperref}
-\usepackage{amsmath}
+
 \usepackage{natbib}			% to insert citations
 \usepackage{xcolor}			% extend the colors can be used
+\usepackage{calrsfs}		% caligraphy font family
 
 \usepackage{bibentry}		% package used to insert full citation in body text
+\makeatletter 
+\renewcommand\BR@b@bibitem[2][]{\BR@bibitem[#1]{#2}\BR@c@bibitem{#2}}
+\makeatother
 \nobibliography*
+
+\usepackage{setspace}		% set space for comment bullet
 
@@
 
+\usepackage{tocbibind}		% to add toc and bib into table of content
+\usepackage{bookmark}	% to separate the last chapter from previous ones
+
 \usepackage{amsthm}
+\makeatletter
+\def\th@plain{%
+  \thm@notefont{}% same as heading font
+  \itshape % body font
+}
+\def\th@definition{%
+  \thm@notefont{}% same as heading font
+  \normalfont % body font
+}
+
 \theoremstyle{plain}
@@
 \theoremstyle{definition}
-\newtheorem{defn}[thm]{Definition} % definition numbers are dependent on theorem numbers
-\newtheorem{exmp}[thm]{Example} % same for example numbers
+\newtheorem{defn}{Definition}[section] % definition numbers are dependent on theorem numbers
+\newtheorem{exmp}{Example}[section] % same for example numbers
 \newtheorem{lemma}[thm]{Lemma}
-\newtheorem{prop}{Proposition}
+\newtheorem{prop}[thm]{Proposition}
 \newtheorem{obs}{Observation}
+
+\newenvironment{myproof}
+{\noindent\textit{Proof:}}{\hfill$\square$}
 
@@
 \newcommand{\R}{\mathbb{R}}			% depends on the package amssymb
+\newcommand{\F}{\mathcal{F}}
+\newcommand{\myline}{\vspace{3mm} \hrule \vspace{4mm}}
+
+\usepackage{amsmath}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
@@
 \tableofcontents{}
+\label{toc}
 \setcounter{tocdepth}{1}			% show only parts, chapters, and sections in content
+
+\part{Economics}
+\label{part:economics}
 
@@
 
+\section{Gentzkow-Kelley-Taddy, 17 WP} % (fold)
+\label{sec:gentzkow_kelley_taddy_17_wp}
+
+\noindent
+\textbf{\bibentry{Gentzkow_el.al:17WP}}
+
+An survey paper on how text analysis can be used in economic research. 
+The main difficulty is the high-dimensionality of text.
+
+\noindent
+Steps to reduce dimension:
+\begin{enumerate}
+	\item Represent raw text $\mathcal{D}$ as a numerical array $C$
+	\begin{enumerate}
+		\item Divide $\mathcal D$ into individual documents $\mathcal D_i$, the level is determined by the level of $V$. For example, daily attributes or monthly attributes.
+		\item Feature Selection.
+Drop out punctuations, numbers, HTML tags, proper names and so on.
+Both very common and very rare words will be excluded.
+And words with the same stems will be reduced to one.
+		\item Limit dependence between words using N-gram. The idea is to only consider consider phrase of length n.
+	\end{enumerate}
+	\item Map $C$ to predicted values $\hat V$ of unknown outcomes $V$
+	\item Use $\hat V$ in subsequent descriptive or causla analysis
+\end{enumerate}
+
+\textcolor{blue}{Reading not finished.
+\cite{grimmer_stewart_2013} also talks this problem. worth reading}
+% section gentzkow_kelley_taddy_17_wp (end)
+
+\section{Seminar Notes} % (fold)
+\label{sec:seminar_notes}
+
+\noindent
+\textbf{AI and Economics}
+(\url{http://taddylab.com/slides/EconAI.pdf})
+
+This slides procides some clear intro on why and how AI (also deep learning) can be applied in economics.
+Many references provided in slides as well.
+
+\textcolor{blue}{Not understand much. Needs further reading.}
+
+% section seminar_notes (end)
+
 % chapter econometrics (end)
@@
 \label{cha:io}
+
+\section{Data and Techniques} % (fold)
+\label{sec:data_and_techniques}
+
+\subsection{Data Source} % (fold)
+\label{sub:data_source}
+
+\noindent
+\textbf{Uber and Taxi}
+\begin{itemize}
+	\item New York Taxi and Limousine Commission Trip Data
+	\begin{itemize}
+		\item \url{http://www.nyc.gov/html/tlc/html/about/trip_record_data.shtml}
+		\item Literature: Bian Bo (JMP)
+	\end{itemize}
+\end{itemize}
+
+% subsection data_source (end)
+
+\subsection{Techniques} % (fold)
+\label{sub:techniques}
+
+% subsection techniques (end)
+
+\noindent
+\textbf{High Resolution Satelite Data:}
+\begin{itemize}
+	\item Pixel is as accurate as 0.5m, much finer than the Night Light data;
+	\item Use machine learning to identify the roads, cars, buildings etc;
+	\item Jonathan Hersh has a paper over this.
+\textbf{\href{https://www.dropbox.com/s/zeph7rrch2rwfwp/PovSpace_JMP_Oct31.pdf?dl=0}{Poverty from Space: Using High Resolution Satellite Imagery for Estimating Economic Well-being and Geographic Targeting}}
+\end{itemize}
+
+\myline
+
+\noindent
+\textbf{Paralelle Computation:}
+\begin{itemize}
+	\item A detailed cook manual on Paralelle computation of RBC model:
+
+	\url{https://www.kellogg.northwestern.edu/researchcomputing/docs/ParallelComputing/ParallelizationForRBCModel.pdf}
+
+	\item Another source: \url{https://bfi.uchicago.edu/sites/default/files/file_uploads/Lecture_Parallel_Programming_Chicago%20%282%29.pdf}
+\end{itemize}
+
+\myline
+
+\noindent
+\textbf{Text as Data:}
+\begin{itemize}
+	\item \href{run:resources/text_as_data}{Course Materials by Justin Grimmer}
+	\item \bibentry{grimmer_stewart_2013}
+	\item \bibentry{Gentzkow_el.al:17WP}
+\end{itemize}
+
+% section data_and_techniques (end)
 
@@
 \begin{itemize}
-	\item Simultaneouty.
-For a production function like $y_{it}=\beta_0+\beta_1 k_{it}+\beta_2 l_{it} + \omega_{it}+\varepsilon_{it}$, we suppose that $\omega_{it}$ is obseved by firm but not by econometricians, and $\varepsilon_{it}$ is observed neither by firm nor econometrician.
+	\item Simultaneity.
+For a production function like $y_{it}=\beta_0+\beta_1 k_{it}+\beta_2 l_{it} + \omega_{it}+\varepsilon_{it}$, we suppose that $\omega_{it}$ is obseved by firm but not by econometricians, and $\varepsilon_{it}$ is observed neither by firm nor econometricians.
 This could induce endogeneity when directly using OLS.
-Suppose $\omega_{it}$ has positive serial correlation, when $\omega_{it}$ is high, firm will choose higher input bacause it is very possible that $\omega$ in next period will be high as well.
+	Suppose $\omega_{it}$ has \textit{positive serial correlation}, when $\omega_{it}$ is high, firm will choose higher input because it is very possible that $\omega$ in next period will be high as well.
 This induces a positive bias for $\beta_k$.
 	\item Exit selection bias. When constructing a balanced panel, then we only observe those firms with high $\omega_{it}$.
+	\textcolor{blue}{Why we have to construct a balanced panel?}
 \end{itemize}
@@
 Thus those facing higher $\omega_i$ will tend to produce more, inducing their input price to increase, which has a negative bias on $\beta_k$.
+		\begin{itemize}
+			\item (My comment) When using input price as IV, we actually assume they are independent of productivities.
+			This may not be the case.
+			If productivity has some correlation across the firms,
+			then it is possible that when productivity is high,
+			the input price in the market will also be high.
+		\end{itemize}
 		\item Use fixed effect. We need to assume that a firm faces same $\omega_{it}$ across time, which is not very practical.
@@
 The key idea is to use a function of what we know (for example, $k_t$ and $i_{t-1}$ in OP) to proxy $\omega$, the existence of such function is guaranteed by the solutioin property of the firm optimization problem.
-And the specific form of this function is estimated nonparametrically.
+And the specific form of this function is estimated non-parametrically.
 	\begin{itemize}
 		\item OP uses a two step estimation process.
-First step, use $k_t$ and $i_{t-1}$ nonparametrically estimate $\omega_t$, plug this into original production function then use OLS.
-Notice the unobserved $\omega_t$ has been controled by $k_t$ and $i_{t-1}$, then OLS will give consistent estimator for $l_t$ but not $k_t$.
+First step, use $k_t$ and $i_{t}$ non-parametrically estimate $\omega_t$, plug this into original production function then use OLS.
+Notice the unobserved $\omega_t$ has been controlled by $k_t$ and $i_{t}$, then OLS will give consistent estimator for $l_t$ but not $k_t$.
 In second step, we first write $\omega_{it} = E[\omega_{it}|\omega_{it-1}]+\xi_{it}$, notice that $\xi_{it}$ is independent of any information set at t-1.
 Thus we get the moment condition $E[\xi_{it}k_{it}]=0$, then we can use method of simulating moments to estimate $\beta_k$.
+		\begin{itemize}
+			\item The key assumption in first step is, current period investment $i_t$ can be represented by a function of $f(k_t,\omega_t)$. 
+			If $f$ is invertible in $\omega_t$ (for example, $f$ being monotone in $\omega$), then we can write $\omega$ as a function of $(i_t, k_t)$.
+		\end{itemize}
+
 		\item LP is very similar to OP, just that use intermediate input $m_{it}$ instead of investment $i_{it}$ in proxy $\omega_{it}$.
@@
 Using intermediate input can solve this.
-		\item ACF critizition is
+
+		\item ACF criticizing is that $\beta_l$ cannot be identified in the first step.
+In LP we assume that $m_{it}=f_t(k_{it},\omega_{it})$.
+But we can reasonably argue by the same reason that $l_{it}=h_t(k_{it},\omega_{it})$.
+Then since $f(\cdot)$ is invertible, then we can write $l_t$ as some deterministic function of $k_{it}$ and $m_{it}$.
+This implies we cannot identify $\beta_l$ in the first step.
+The solution of ACF is to identify both $\beta_k$ and $\beta_l$ simultaneously at step 2, which is feasible since we now have two moment conditions.
 	\end{itemize}
@@
 
+\section{Demand Function Estimation} % (fold)
+\label{sec:demand_function_estimation}
+
+\noindent
+\textbf{Reference:} \cite{shum:2016bk} CH 1 is very good for motivation and techniques.\\
+
+\noindent
+\textbf{Motivation for demand estimation}
+\begin{itemize}
+	\item Firstly, it is important per se, we want to understand consumer behaviour. And we want to \textit{predict the results of price change}, and \textit{introduction of new products}. 
+	Such counter factual predictions can only be built upon a structural model.
+	\item Secondly, estimation of demand function helps us better understand market structure.
+Markup itself is rarely observed (with some exceptions, like the electronic industry), but we can generally observe demand elasticity.
+	Recall that $\frac{p-MC}{p}=1/\varepsilon$ (see \ref{sec:rey_and_stiglitz_1995_rand}). Estimation of $\varepsilon$ will help us know the markup of firm, thus infer market structure.
+\end{itemize}
+
+\noindent
+\textbf{Challenges in demand function estimation:}
+\begin{itemize}
+	\item Too many parameters.
+Think of a market with 100 commodities and we want to estimate the cross elasticities.
+The number of parameters will be 10,000.
+Obviously it is impossible to have enough data to estimate so many parameters.
+	\begin{itemize}
+		\item Solved by nested logit model.
+	\end{itemize}
+	\item Unobserved quality. This will causes the endogeneity of price. And because the unobservable quality affects the selling in a highly nonlinear way, so IV is not very applicable in this case.
+	\begin{itemize}
+		\item Solved by BLP style estimation.
+	\end{itemize}
+\end{itemize}
+
+\subsection{Brief Literature Review} % (fold)
+\label{sub:brief_literature_review}
+
+There are two branches of demand function estimation.
+The early literature features differentiated goods (continuous choices). Classical examples include \cite{Hausman:1994km} introducing a nested approach to reduce the dimension of parameters.
+
+Recent literature focus much more on discrete choice model. The seminal papers are \cite{Berry:1994jh} and \cite{berry.et.al.1995.emca}.
+The address of these two papers is to overcome the \textbf{endogenous price problem due to unobserved quality}. 
+Suppose we use a characteristic approach, where consumer utility and thus their purchase decision is decided by characteristics of products. 
+Some of the characteristics are obervable to consumer (and firms) but not to econometricians, for example the advertisement. 
+For higher unobserved quality, the equilibrium price will be higher, leading to a downward bias of price elasticity.
+
+\cite{Berry:1994jh} comes with a method to overcome this endogeneity problem with only \textit{market level data}.
+\begin{itemize}
+	\setlength{\itemsep}{0pt}
+	\item The basic idea is a IV based two step estimation.
+	\item First step: denote $\delta_j$ to be the `mean utility' for brand $j$.
+Notice this includes unobserved quality.
+Under some conditions, $\delta_j$ can be \textit{inversed} by market shares $(s_1,...,s_J)$, and thus we can get $\hat \delta_j$ by observed market shares.
+	\textcolor{blue}{This inversion step is the key for this paper, and many following papers treating endogenous quality problem.}
+	\item Second step: By definition, $\delta_j=X_j\beta -\alpha p +\xi_j$.
+Thus we can get $\hat \xi_j$ if we get $\hat \delta_j$.
+Suppose $E[\xi Z]=0$, then we can use $Z$ as IV to estimate consistently.
+\end{itemize}
+
+\cite{berry.et.al.1995.emca} (BLP henceforce) is more comprehensive with the same idea.
+They introduce random-coefficients logit model, which allows each individual to have different taste coefficients.
+Thus we can't directly use the inverse technique.
+The way is to use a Simulation Method of Moments (inner loop and outer loop).
+First guees a $\delta$, match mkt share, then run a IV regression, then guess different $\delta$ and get an outer loop.
+They prove a contraction mapping.
+
+\myline
+
+\textbf{\bibentry{Quan_Williams:2017wp}}
+
+This paper addresses the local heterogeneity of consumer demand,
+and concludes that usual BLP method will overestimate the welfare increase of e-commerce because local stores have satisfied most local demands.\\
+
+\noindent
+\textbf{Challenges:}
+\begin{itemize}
+	\item Huge varieties of goods in fine-grid locations make scarce data in each category. Two possible solutions for this: 1) aggregating over locations; 2) just ignore the zero sales. 
+	Aggregating is unsatisfactory since the heterogeneity of local preference is our study focus.
+	Ignoring will cause selection bias and cause overestimation of local heterogeneity.
+	\item Mean utility level cannot be recovered solely by observable variables.
+	They raise specific Converging in Distribution theorem to tackle this.
+\end{itemize}
+
+% subsection brief_literature_review (end)
+
+% section demand_function_estimation (end)
+
+\section{Price Dispersion} % (fold)
+\label{sec:price_dispersion}
+
+\textbf{\bibentry{Baye:2013un}}
+
+\begin{itemize}
+	\item Price comparing sites becoming less popular,
+	more consumers choose to direcly go to like Amazon and eBay.
+	These websites also have `marketplace'.
+	\item Many searching behaviour are not observed. Non-texture data (e.g. in the menu, directories).
+	\item Search time across platforms can hardly be compared.
+	Because maybe it's enough to search only once in Amazon, 
+	but many times in eBay.
+\end{itemize}
+
+\myline
+
+\noindent
+\textbf{Random Ideas}
+\begin{itemize}
+	\item Collusion when there is consumer searching cost.
+	Intuitively, collusion should be easier to sustein with 
+	\textcolor{blue}{[no idea]}
+
+	\item Awaya-Krishna (2016) 
+\end{itemize}
+
+% section price_dispersion (end)
+
+\section{Multisided Platforms} % (fold)
+\label{sec:multisided_platforms}
+
+\textbf{\bibentry{Evans_Schmalensee:2012wp} }
+\begin{itemize}
+	\item Price structure matters. Reduce charge by one side and increase charge by another side will affect the transaction.
+	\item Transaction cost is necessarily high for multisided platform.
+	\item Two kind of externalities. Usage externality and membership externality.
+	\item Pricing is compelicated. Per-transaction fee, or membership-fee. \textcolor{blue}{This looks similar to conventional IO model.}
+	\begin{itemize}
+		\item In per-transaction fee case. Price is directly proportional to the elasticity, while in conventional models price is inversely related to elasticity.
+		\[\frac{p_1+p_2-c_1-c_2}{c_1+c_2}=\frac{1}{e_1+e_2}\]
+		\[\frac{p_1}{e_1}=\frac{p_2}{e_2}\]
+		Notice the second equation is unconventional.
+		\item In membership-fee case.
+		\item Both models can lead to a highly skewed price structure.
+	\end{itemize}
+	\item Competition Structure.
+	\begin{itemize}
+		\item Product differentiation
+		\item Multi-home.
+		\item Asymetric Competition.
+A n-sided platform may face competition from 1) one-sided firms; 2) a multisided platform competing in some but not all sides; 3) a multisided platform that has additional sides
+	\end{itemize}
+\end{itemize}
+
+\myline
+
+\textbf{Random Ideas}
+\begin{itemize}
+	\item Multisided platform as a commitment device changes the game structure.
+Like in the Truck-GasStation case raised in the book, the fleet-card company provides commitment power to the card companny, no renegotiation problem.
+\end{itemize}
+
+% section multisided_platforms (end)
+
+\section{Erdem-Keane, 96 MktSci} % (fold)
+\label{sec:erdem_keane_96_mktsci}
+
+\textbf{\bibentry{erdem_kean:96_MngSci}}
+
+\cite{erdem_kean:96_MngSci} provides an example on how to estimate demand when quality is uncertain and consumer learns by Bayesian rule.
+
+\vspace{2mm}
+\noindent
+\textbf{Motivation:}
+\begin{itemize}
+	\item Avoide ad hoc assumptions on how consumers utilizing experience information
+	\item Estimate structural models to do policy analysis
+\end{itemize}
+
+\noindent
+\textbf{Features:}
+\begin{itemize}
+	\item Estimate Dynamic Programming.
+	Consumers make decision based on their perceptions,
+	but econometricians only observe the consumption. 
+	So have to integrate over the distribution of perception errors $v_{ij}(t)$, which is is a Markov process.
+	The integration part will be very complicated.
+	\begin{itemize}
+		\item Provides a way to estimate Dynamic Programming model with simulation. Also see \cite{keane_wolpin:94REStat}.
+	\end{itemize}
+	\item Experience Shocks.
+	This indicates that even after purchasing once, 
+	consumer is not certain about the quality of the good (or the preference of himself).
+	This is mainly motivated by empirical fact: 
+	consumption behavior generally do not converge.
+\end{itemize}
+
+\noindent
+\textbf{Empirical Findings:}
+\begin{itemize}
+	\item Bayesian learning very well fit the date.
+
+\end{itemize}
+
+% section erdem_keane_96_mngsci (end)
+
+\section{Gentzkov-Shapiro-Taddy, 17 WP} % (fold)
+\label{sec:gentzkov_shapiro_taddy_17_wp}
+
+\textbf{\bibentry{Gentzkow:2017hb}}
+
+\begin{itemize}
+	\item Methods for analyzing high-dimensional choices decisions
+	\begin{itemize}
+		\item also see \bibentry{Gentzkow_el.al:17WP}
+	\end{itemize}
+	\item Index for measuring polarization
+\end{itemize}
+
+This is a methodology paper introducing how to analyze high-dimensional choices decisions. They show that traditional logit model has severe finite sample bias.
+They also raise a index for measuring polarization.
+
+\textcolor{red}{[TO BE ADDED]}
+
+% section gentzkov_shapiro_taddy_17_wp (end)
+
 % chapter io (end)
+
+\chapter{Game Theory} % (fold)
+\label{cha:game_theory}
+
+\section{Important Tools} % (fold)
+\label{sec:important_tools}
+
+\begin{thm}[Revelation Principle, Myerson, 1981]
+Suppose that $\psi$ was a Bayes Nash equilibrium of the indirect mechanism $\Gamma$. 
+Then there exists a direct mechanism that is payoff-equivalent and where truthful revelation is an equilibrium.
+\end{thm}
+
+\begin{myproof}
+[to be added]
+\end{myproof}
+
+\begin{singlespacing}
+\noindent
+\textit{Comment:}
+\end{singlespacing}
+\begin{itemize}
+	\setlength{\itemsep}{0pt}
+	\item Revelation Principle is defined over some specific solution concept. Here it is Bayes Nash Eqm.
+	\item Revelation principle is not always satisfied. The stronger solution concept we use, the more likely it is not satisfied.
+\end{itemize}
+
+\subsection{Solution Concept} % (fold)
+\label{sec:solution_concept}
+
+There are many solution concepts:
+\begin{itemize}
+	\item Nash eqm
+	\item Subgame Perfect eqm
+	\item Perfect eqm
+	\item $\varepsilon$-Perfect eqm
+	\item Proper eqm
+	\item Trembling-Hand eqm
+	\item Bayesian Nash eqm
+	\item (Weak) Perfect Bayesian eqm
+	\item Sequential eqm
+	\item Forward looking eqm
+	\item Self-Confirming eqm
+
+\end{itemize}
+
+\begin{defn}[Self-confirming Equilibrium, \cite{Fudenberg_Levine:93EMCAa}]
+Profile $\sigma$ is a \textit{self-confirming equilibrium} if for each player i, $s_i \in$ support($\sigma_i$) there exists belief $\mu_i$ such that:
+\begin{enumerate}
+	\item $s_i$ maximizes $u_i(\dot,\mu_i)$, and
+	\item $\mu_i[\{\pi_{-i}|\pi_j(h_j)=
+	\hat \pi_j(h_j|\sigma_j)\}]=1$, for all $j \neq i$ and $h_j \in \bar H(s_i,\sigma_-i)$, where $\bar H$ is the set of info sets that are reached with positive probability
+\end{enumerate}
+\end{defn}
+
+\begin{singlespacing}
+\noindent
+\textit{Comment:}
+\end{singlespacing}
+\begin{itemize}
+	\setlength{\itemsep}{0pt}
+	\item This definition mainly requires that the belief $\mu_i$ is consistent only at information sets that are reached with positive probability when player $i$ plays $s_i$.
+	\item This is most obvious when contrast with Nash Eqm, which is almost the same as this definition,
+	except for the consistency requirement is for all $h_j \in H_{-i}$. The consistency is required  for all information sets.
+	\item Self-confirming is a weaker solution concept than Nash Equilibrium. 
+	It uses the idea that players can only learn through what they observe.
+	For those outcomes that they cannot observe,
+	there is no particular reason for their beliefs to coincide.
+	Players can never learn something they lack information on.
+\end{itemize}
+
+\begin{exmp}
+
+\end{exmp}
+
+% subsection solution_concept (end)
+
+% section important_tools (end)
+
+\section{Learning Theory} % (fold)
+\label{sec:learning_theory}
+
+\subsection{Important tools in learning} % (fold)
+\label{sub:important_tools_in_learning}
+
+\begin{defn}[Monotone Likelihood Ratio Property]
+For all $l<S$,
+
+\[\frac{p_{q,l}}{p_{q+1,l}} \geq \frac{p_{q,l+1}}{p_{q+1,l+1}} \ for \ all \ q<R\]
+with strictly inequality for at least one q.
+
+\end{defn}
+
+This is first raised by \cite{Milgrom:1981dv}, which ensures that the conditional expectation of each individual increases in his signal realization.
+
+\begin{defn}[Martingale]
+A \textit{martingale} is a pair $(X_n,\F_N)$, where $\{\F_n\}$ is a filtration and $X_n$ an integrable (i.e. $E|X|<\infty$) stochastic process adapted to this filtration, such that 
+\[E[X_{n+1}|\mathcal{F}_n]=X_n,\ a.s. \ \forall n\]
+\end{defn}
+
+\noindent
+\textit{Comment:}
+\begin{itemize}
+	\setlength{\itemsep}{0pt}
+	\item Notice that Martingale process is much more restricted than Markov process, not only in the realization of expectation value. Markov process requires that 
+	\[Pr(X_{t+1}\in A)|X_t=x_0,X_{t-1}=x_{t-1},...,X_{t-k}=x_{t-k}
+	=Pr(X_{t+1}\in A)|X_t=x_0\]
+	for all $A \in \mathcal{X}$, all $x_0,x_1,...,x_k \in \mathbb{X}$, and all $0\leq k\leq t$. 
+	\begin{itemize}
+		\item This actually restricts all stochastic properties, including expectations, variations and others.
+		\item Also, Martingale process require conditional on $\F_t$, but Markov process only requires $x_t$.
+	\end{itemize}
+\end{itemize}
+
+\begin{thm}[Martingale Convergence Theorem]
+
+\end{thm}
+
+% subsection important_tools_in_learning (end)
+
+\subsection{Overview of literature} % (fold)
+\label{sub:overview_of_literature}
+
+% subsection overview_of_literature (end)
+
+\textcolor{red}{The equilibrium concept used in literature is Bayesian Nash Eqm.
+Thus we put no restriction on off-eqm path beliefs.
+Nageeb said something about this, but I don't understand why this is important.}
+
+\cite{Bikhchandani:1992fs} (BHW here after) is one of the original papers for learning in games.
+The main point is to explain the easily formulated but fragile information cascade when only actions are observed.
+The idea is, if only actions are observed, then after some threshold, private information will not affect action.
+And this private will NOT join the information pool, thus all following individual's private information will not contribute to the action.
+But since very little information is needed to form a cascade, this cascade can also be easily reversed when some shocks happen.
+
+\cite{Smith:2000tz} is a generalization of BHW paper. The generalization lies in these aspects:
+\begin{itemize}
+	\setlength{\itemsep}{0pt}
+	\item Heterogeneity in quality of information (possibly unbounded private information)
+	\item Heterogeneity of preference (noise by crazy types)
+	\item Information cascade is NOT a generic feature; but 'herding' is.
+	\item Necessary and sufficient condition for \textit{complete learning}.
+\end{itemize}
+This paper also provides a general approach on how to handle learning behaviour.
+% section learning_theory (end)
+
+\subsection{Bikhchandani-Hirshleifer-Welch, 92 JPE} % (fold)
+\label{subsec:bikhchandani_hirshleifer_welch_92_jpe}
+
+\textbf{\bibentry{Bikhchandani:1992fs}}
+
+BHW is the seminal paper of social learning, which explains imitating in social phenomena without any ad hoc assumptions. By ad hoc assumptions, I means following:
+\begin{itemize}
+	\setlength{\itemsep}{0pt}
+	\item sanctions on deviants
+	\item positive payoff externalities
+	\item conformity preference
+\end{itemize}
+This assumptions all have the unsatisfying property that puts the cart before the horse.
+
+\textcolor{red}{TO BE ADDED}
+
+% section bikhchandani_hirshleifer_welch_92_jpe (end)
+
+\subsection{Kremer-Mansour-Perry, 14 JPE} % (fold)
+\label{subsec:kremer_mansour_perry_14_jpe}
+
+\textbf{\bibentry{KMP:2014jpe}}
+
+Different from previous learning papers, KMP focuses on the optimal information disclosure of planner.
+They find that it is not always optimal for planner to disclose full information, because it will discourage agents' incentive to explore and exploration has positive externalities.
+
+Example: Online review website like TripAdvisor, Yelp; Google Map\\
+
+\noindent
+\textit{Illustrative example:}
+
+Say $R_1$ is uniformly distributed in $[-1,5]$, and $R_2$ is uniformly distributed in $[-5,-5]$.
+Then agent-1 for sure will choose $a_1$ since its ex-ante expeted payoff is higher.
+Planner cannot force agent-1 to choose $a_2$ because of IC condition.
+
+If realized $R_1$ is lower than 0, then for sure agent-2 will choose $a_2$.
+But planner can do better by recommending agnet-2 to play $a_2$ whenever $R_1 \leq 1$.
+Agent-2 will follow this suggestion because the $E[R_1]$ is 0 conditional on planner not disclosing.
+
+If unfortunately the realized $R_1$ is higher than 1, then there is no way to make agent-2 to choose $a_2$,
+but it is still possible to ask agent-3 to explore if $R_1$ is not too high.
+Because when player-3 is recommended to play $a_2$, she cannot distinguish between:
+1) planner knows both realization and $R_2>R_1$;
+or 2) planner wants her to explore.
+The second situation is in the same shoes as agent-2,
+but because of the possibility of the first situation,
+agent-3 will admit a higher upper threshold for exploring.\\
+$\hfill\square$
+
+\vspace{2mm}
+\noindent
+\textit{\textbf{Main Results:}}
+(The proof of this paper is not difficult, and worth learning)
+\begin{itemize}
+	\item The optimal policy is threshold policy. For each individual, there is an interval of realization $r_1$ such that he is the first agent to explore.
+	\item There is an upper bound of exploration time, which is independent of agents number $T$ and realization of $R_1,R_2$.
+	This indicates result will converge to first best when $T$ is large enough.
+\end{itemize}
+
+\vspace{2mm}
+\noindent
+\textit{\textbf{Comments:}}
+\begin{itemize}
+	\item Generalize action to $n$ will not affect the structure of optimal policy. While continuum of action will ask for new setting. See referee report for more.
+
+	\item We can also think the realization of $R_1$ and $R_2$ is \textbf{correlated}. 
+	The result of this paper will not hold in this case.
+	Think of the extreme case that correlation between $R_1$ and $R_2$ is $-1$.
+	Then for any $R_1>0$, the planner will never explore $a_2$. For any $R_1<0$, the planner will recommend $a_2$ for all agents except for first one, and they will accept this recommendation.
+	The correlation problem also exists when the relization of $R_i$ is not a value but a distribution, in the sense of correlation in mean value.
+In another direction, if the realization is positively correlated, then the exploration cost will be lower.
+And optimal policy should have lower upper threshold for each agent.
+	\vspace{1mm}
+
+	I think this extension important, because we have correlations in many real world applications.
+	Take TripAdvisor as an example. If we already have reviews on one Marriott hotel in Paris, then it's not very useful to explore another Marriott at Toulouse! 
+	Intuitively, planner should utilize such correlation, and put more weight on exploration of independent realizations.
+	The optimal policy could be interesting.
+
+	\item I also think of how this can be combined with optimal persuasion.
+	If planner and agents have discrepancy in interest, 
+	then persuasion is needed.
+\end{itemize}
+
+% section kremer_mansour_perry_14_jpe (end)
+
+\section{Hard Information} % (fold)
+\label{sec:hard_information}
+
+\noindent
+\textbf{Unraveling:}
+
+\textit{Unraveling} is first discussed by \cite{Grossman:1981ih} and \cite{Milgrom:1981dv}. 
+They show that if investor knows the type of firm's information, 
+such information is perfectly verifiable at no cost, and the disclosure of such information is at no cost.
+Then exist a sequential equilibrium, where the firm will disclose all information, good or bad.
+The intuition is, since investors know the type (distribution) of information firm has, the nondisclosure indicates a worst information.
+If the investor is so suspicious, firm will disclose those not so good information.
+
+\cite{Dye:1985a} finds that such unraveling may not always happen.
+There are many possible reasons, basically they are violations of above three assumptions.
+
+\cite{Quigley:2017us} discusses unraveling in existence of outside information. They show that such information beyond control of insiders will \textit{reverse} unraveling result.
+The highest quality insiders remain quiet, and only the mediocre insiders disclose information.
+Notice that sending message is costly in this model.
+The intuition for this result is,
+when type is high enough,
+outside information is enough to persuade the outsider.
+My guess is,
+this holds because the outsider decision is not fully divisible.
+
+\myline
+\noindent
+\textbf{Mechanism Design with Hard Information:}
+
+\cite{galzer_ruinstein:emca04} discusses the optimal decision rule when listener can check only one value.
+\textcolor{blue}{[Not yet read]}
+
+\cite{Green:1986gs} discusses the direct mechanism under partially verifiable information. 
+They show that the \textit{Nested Range Condition} is necessary and sufficient for all socially-implementable mechanisms to be truthfully-implementable mechanisms.
+The condition requires that if A can pretend to be B,
+B can pretend to be C, then A can pretend to be C.
+This condition is used in many other papers like \cite{Hart_et:17aer_evidence_games}, and monotonicity condition in \cite{Grossman:1981ih} is also included.
+But notice that their paper does not consider a explicit checking process, so the result cannot apply to \cite{BenPorath:2014bc}, where a perfect but costly checking technique exists.
+
+\subsection{Evidence Game} % (fold)
+\label{sub:evidence_game}
+
+\textcolor{blue}{[Below is based on the talk by Xiao]}
+The paper by \cite{Hart_et:17aer_evidence_games} provides a general framework for evidence games. It shows that under conditions:
+\begin{itemize}
+	\item A1. $\theta \in m(\theta) \subseteq \Theta$.
+	It basically restricts the message space to be the type space, and every can truthfully report his own type.
+	\item A2. If $\theta' \in m(\theta'')$ and $\theta \in m(\theta')$, then $\theta \in m(\theta'')$. It means the masquerade is transitive, which is quite restrictive condition.
+\end{itemize}
+With above two assumptions, and \textit{truth-leaning} refinement of equilibriums, they show that giving receiver commitment power will make him no strict better off.
+
+Many more basic models like \cite{Dye:1985a} and \cite{Milgrom:1981dv} can be encompassed by this framework. \textcolor{blue}{[Worth trying to put them in.]}
+
+% subsection evidence_game (end)
+
+\subsection{Beyer-Cohen-Lys-Walther, 10 JAcctE} % (fold)
+\label{sub:beyer_cohen_lys_Walther_10_jaccte}
+
+\textbf{\bibentry{Beyer:2010cj}}
+
+This paper surveys literature of \textbf{voluntary information disclosure}, which is highly correlated with \textit{hard information} literature we discuss in reading group.
+I mainly read the section 3 (voluntary disclosure) of this paper.
+
+We have unraveling result in \cite{Milgrom:1981dv} and \cite{Grossman:1981ih}. Unraveling means the agent will disclose all their private information. This result relies on the following conditions:
+\begin{enumerate}
+	\setlength{\itemsep}{0pt}
+	\item disclosures are costless;
+	\item investors know that firms DO have private info;
+	\item all investors interpret the firm's disclosure in the same way, and firms know how investors will interpret that disclosure;
+	\item agents want to maximize their firm's share prices (no moral hazard problem);
+	\item agents can credibly disclose their private info;
+	\item firms cannot commit ex-ante to a specific disclosure policy.
+\end{enumerate}
+
+Violation of any conditions will result in partial nondisclosure of private information.
+\begin{enumerate}
+	\setlength{\itemsep}{0pt}
+	\item \textit{Costly disclosure.} If disclosure is costly to a firm, then it will choose not to disclose even when signal is not that bad.
+	\item \textit{Probabilistic information endowment.} If firms get private information in probability, then they have incentive to not report some bad results.
+Because investors cannot distinguish them from those without private information.
+	\item \textit{Uncertain investor response.}
+	\item \textit{Uncertain disclosure incentives.} In this case, there will be moral hazard problem.
+	\item \textit{Non-verifiable disclosure.} There are many important models in this category.
+For example, Cheap Talk model and Costly State Verification models.
+In cheap talk, exists "babbling eqm" since signal can't be verified.
+In Costly State Verification, firms have some rent since it's not wise to investors to check at every case.
+	\item \textit{Ex-ante commitment}.
+\end{enumerate}
+
+% section beyer_cohen_lys_ (end)
+
+\subsection{Milgrom, 81 Bell} % (fold)
+\label{sub:milgrom_81_bell}
+
+\textbf{\bibentry{Milgrom:1981dv}}
+
+\cite{Milgrom:1981dv} introduces a way to measure how good a message is.
+The difficulty here is that we are comparing two conditional distributions, not two values, thus something similar to FOSD is needed.
+
+\begin{defn}
+A signal is \textit{more favorable than} another signal if the posterior belief $G(\cdot|x)$ FOSD $G(\cdot|y)$.
+\end{defn}
+
+\begin{prop}
+x is more faborable than y iff for every $\theta_1>\theta_2$,
+\begin{equation}
+\label{eq:milgrom81_2a}
+\frac{f(x|\theta_1)}{f(x|\theta_2)}>\frac{f(y|\theta_1)}{f(y|\theta_2)}
+\end{equation}
+\end{prop}
+
+Intuitively, x is more favorable iff x is more likely to appear when the state is high.
+
+\begin{defn}[Strict Monotone Likelihood Ratio Property]
+The family of densities $\{f(\cdot|\theta)\}$ have the monotone likelihood ratio property if for every $x>y$ ad $\theta_1>\theta_2$, \eqref{eq:milgrom81_2a} is satisfied.
+\end{defn}
+
+Densities with MLRP has the good property that any two signals are comparable.
+
+% subsection milgrom_81_bell (end)
+
+% section hard_information (end)
+
+\section{Green-Porter, 84 EMCA} % (fold)
+\label{sec:green_porter_84_emca}
+
+\textbf{\bibentry{Green_Porter:1984EMCA}}\\
+
+\noindent
+\textbf{Motivation:}
+\begin{itemize}
+	\setlength{\itemsep}{0pt}
+	\item In perfect monitoring models, the price is constant over time. But empirically, we observe price war frequently.
+	\item Using imperfect monitoring, the price war is an intrinsic property of the model.
+	\item The idea is: based on imperfect monitoring. The firms cannot perfectly distinguish others' deviation with a price shock.
+	\item So there will be an  price threshold. Above this threshold, they take the collusion action. Below this, they will exert retaliation for some period, then back to collusion.
+\end{itemize}
+
+\noindent
+\textbf{Model:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+% section green_porter_84_emca (end)
+
+\section{Repeated Game} % (fold)
+\label{sec:repeated_game}
+
+This section highly depends on Nageeb's notes and Mailath-Samuelson book.
+
+\subsection{Imperfect Monitoring} % (fold)
+\label{sub:imperfect_monitoring}
+
+\begin{itemize}
+	\item \href{run:resources/repeated_game/imperfect_monitoring_najeeb.pdf}{Nageeb's notes}
+\end{itemize}
+
+Motivation for imperfect monitoring:
+\begin{itemize}
+	\item In practice, monitoring is often imperfect (\cite{Green_Porter:1984EMCA})
+	\item \textcolor{blue}{NOT UNDERSTAND.} Helps to understand punishments at off-path histories
+\end{itemize}
+
+With imperfect monitoring, `forgiveness' will often make the equilibrium better while keeping IC satisfied.
+
+The difficulty in describing imperfect monitoring game with automata is, we can only observe ex-post history, 
+how can we use automata graph to describe this ex-post history?
+The answer is we can think the equilibrium (and strategy) ex-ante. 
+Because everything is linear, so it actually does not really matter what ex post realization is.
+
+% subsection imperfect_monitoring (end)
+
+% section repeated_game (end)
+
+\section{Seminar Notes} % (fold)
+\label{sec:seminar_notes}
+
+\noindent
+\textbf{George Mailath (WP 17): “The Wisdom of The Confused Crowd: Model-Based Inference”}\\
+
+\noindent
+\textbf{Main idea:}
+\begin{itemize}
+	\item If players are non-Bayesian, how do they update?
+	How they exchange information in the information mkt?
+	\item Agents do `model-based' inference.
+	Basically this is a two step structure.
+	\item Agents have a model which addresses on some dimension of the information,
+	and when they receive an information, 
+	they will only first focuses on the dimensions that their model addresses.
+	\item Then they exchange the posterior belief with other agents.
+	Since other agents have different model addressing different aspects,
+	their posterior belief reveals some information of other dimension signal.
+	\item Since the signals in different dimensions are correlated,
+	one agent may use other's posterior belief to infer partial information of signals in the dimensions that he is interested in.
+	\item Thus, although they have different models addressing different dimensions,
+	they can still exchange in the info market.
+\end{itemize}
+
+\myline
+
+\noindent
+\textbf{Simon Board, Moritz Meyer-ter-Vehn (WP 17): An Inspection Model of Learning in Networks}\\
+
+\noindent
+Main idea: 
+\begin{itemize}
+	\item \href{run:resources/learning/Talk_note_Learning in network.pdf}{Note of Takl by Board}
+	\item Two concerns in network learning
+	\begin{itemize}
+		\item I get awaked at a constant rate, and may want to try
+		\item I see my neighbor trying, and want to try
+	\end{itemize}
+	\item Learning in small network is very difficult to numerically computing.
+	\begin{itemize}
+		\item Self-reinforcement structure
+		\item Triangle correlation
+		\item $\Rightarrow$ can characterize, but cannot compute
+	\end{itemize}
+	\item In large random network, such concern disappears
+	\begin{itemize}
+		\item Because in large random network, the prob of each two points are connected is the same.
+		And with large enough network, the prob of a small local structure is second order small. 
+		\item Can write the graph as a tree in this case
+	\end{itemize}
+	\item (?) Learning rate increases exponentially with the number of neighbors.
+\end{itemize}
+
+\vspace{3mm}
+\hrule
+\vspace{3mm}
+
+\noindent
+\textbf{\bibentry{deb_kitamura_quah_stoye:2017wp}}
+
+\textcolor{blue}{Important paper, worth reading.}
+
+This paper raises a new representation theorem over preference and utility. 
+Traditionally we use preferences over consumption bundles $x$, 
+and Afriat theorem guarantees a well-behaving utility representation if GARP is satisfied for preference.
+This paper raises a representation theorem for preference over price bundles.
+
+More specifically, GARP says if we have $p^{t'}\cdot x^t<p^{t'}\cdot x^{t'}$,
+then we conclude $x^{t'}$ is revealed preferred to $x^t$, because $x^t$ is affordable when the consumer choose $x^{t'}$.
+To test this approach, econometricians have to observe the consumption bundles of \textit{all} goods, which is infeasible in many cases.
+
+This paper raises another way to view data.
+\begin{itemize}
+	\item If $p^{t'}\cdot x^t < p^t \cdot x^t$, then we say $p^{t'}$ is revealed preferred to $p^t$.
+	Because the consumer has money left for other goods when price is $p^{t'}$. 
+	In this way, we can construct the preference over prices.
+	\item This paper raises GAAP corresponding to GARP,
+	and augmented utility function (seems integrating expenditure directly in the utility) w.r.t. GAAP.
+	\item This representation can be empirically tested without observing all goods being purchased.
+	And solves the endogenous expenditure level problem,
+	which McFadden-Richter estimation approach assumes.
+	\item Ron points out that this representation model cannot account for budget change.
+\end{itemize}
+
+\myline
+
+\noindent
+\textbf{Cooperation Game:}
+
+Nageeb mentions in class that one reason for cooperation game to be unpopular is the difficulty in treating informations.
+How to treat to coalition when someone has information while others don't?
+
+% section seminar_notes (end)
+
+% chapter game_theory (end)
 
@@
 
-This paper introduces Deffered Acceptance (DA) algorithms in matching, and shows that it is stable and optimal.
+This paper introduces Deferred Acceptance (DA) algorithms in matching, and shows that it is stable and optimal.
 
@@
 
-Comment: it loos at first that optimal assignments may not always exist. But as we will show constructively, it does.
+Comment: it looks at first that optimal assignments may not always exist. But as we will show constructively, it does.
 
@@
 
+\chapter{Search Theory} % (fold)
+\label{cha:search_theory}
+
+\section{Shi, 09 EMCA} % (fold)
+\label{sec:shi_09_emca}
+
+% subsection shi_09_emca (end)
+
+% section search_theory (end)
+
 \chapter{Macro} % (fold)
@@
 \cite{Townsend:1979ef} gives a micro model describing contract under costly state verification.
-\cite{BenBernanke:1989eg} and \cite{Carlstrom:1997fb} are two important works using this to explain business cycles (also called Financial Accelarator).
-
-\textcolor{red}{Add breif introduction for costly state verification literature.}
+\cite{BenBernanke:1989eg} and \cite{Carlstrom:1997fb} are two important works using this to explain business cycles (also called Financial Accelerator).
+
+\textcolor{red}{Add brief introduction for costly state verification literature.}
+
+\section{Townsend, 79 JET} % (fold)
+\label{sec:townsend_79_jet}
+
+\textcolor{red}{seminal paper in costly state verification, important, to be added.}
+
+% section townsend_79_jet (end)
 
@@
 
-\section{Collateral Constraints} % (fold)
-\label{sec:collateral_constraints}
-
-Another explaination for financial friction is collateral constraint. Important literatures include \cite{Kiyotaki:1997hl},
+\section{Kiyotaki-Moore, 97 JPE} % (fold)
+\label{Kiyotaki_Moore_97_jpe}
+
+\textbf{\bibentry{Kiyotaki:1997hl}}
+
+Another explanation for financial friction is collateral constraint. Important literatures include \cite{Kiyotaki:1997hl},
 
@@
 
+\noindent
+\textbf{Skills:}
+\begin{itemize}
+	\item How they deal with specific-targeted loan (i.e. the loan can only be used to purchase land)
+\end{itemize}
+
 % section collateral_constraints (end)
 
+\section{Gorton and Ordonez, 14 AER} % (fold)
+\label{sec:gorton_and_ordonez_14}
+
+\textbf{\bibentry{10.1257/aer.104.2.343}}\\
+
+\textbf{Motivation}: How a small shock can sometimes have a very huge, sudden effect, while at other times the effect of the same size shock is small or nonexistent.
+Leverage per se is not enough to explain this.
+This paper explains how credit booms arise, leading to financial fragility where a small shock can lead to huge consequences.
+Thus, "tail risk" is endogenous.
+The same reason causes boom and huge recession, and the degree of recession is positively correlated with the boom lasting time.
+
+\textbf{Mechanism}:
+
+\begin{enumerate}
+	\item Firm needs land as collateral to borrow money from households.
+Land is either good or bad.
+Neither firm nor household know the quality of land, and checking fee is $\gamma>0$.
+It can be shown that, when the probability of a land to be good is too high or too low, it will be optimal (for both firm and household) to not check the quality.
+	\item Then suppose there are idiosyncratic shocks to land.
+For each land in each period, there is $\lambda$ prob to be unchanged, and $1-\lambda$ to be changed.
+In case of changing, $\hat p$ prob becoming good and $1-\hat p$ becoming bad, independent of initial type.
+So we can take it as a $\hat p$ type, it will become either 0 or 1 after checking.
+If $\hat p$ lies in some range that no checking is appropriate, then uncertainty in the economy will accumulate.
+Notice such accumulation will lead to a boom.
+	\item Now think of an aggregate shock.
+All good type and $\hat p$ type have weaker beliefs after such shock, changing to $\eta$ and $\eta \hat p$ respectively.
+Notice that $\eta$ and $\eta \hat p$ may have very different effect.
+It may be optimal to not check with $\eta$ but optimal to check with $\eta \hat p$.
+Thus if an economy has accumulated a large portion of $\hat p$, i.e.
+a long boom, then many of them will choose to check, inducing a huge crisis.
+	\item Notice that it is not because of any \textit{intrisinc} change in economy.
+The $\hat p$ will change the real portion of good land in the economy only once.
+What really matters is that once the bad one becomes $\hat p$, then even it switches back to bad in following periods, it will still be taken as $\hat p$.
+That means, the $\hat p$ type will accumulate in the economy.
+\end{enumerate}
+
+\textcolor{red}{Why this paper is important}:
+\begin{itemize}
+	\item Provide a way to endogenize information in general equilibrium model.
+\end{itemize}
+
+% section gorton_and_ordonez (end)
+
+\section{Williamson, 87 QJE} % (fold)
+\label{sec:williamson_87_qje}
+
+\textbf{\bibentry{10.2307/1884684}}\\
+
+\cite{10.2307/1884684} mainly wants to explain two things:
+\begin{itemize}
+	\item Why is debt contract so popular?
+	\begin{itemize}
+		\item By MM Theorem, we know that in a frictionless world, debt contract is equivalent to equity contract. But we notice that most fund is raised through debt.
+		\item Explain by moral hazard. Borrower has private information on outcome. And lender has to pay for checking.
+	\end{itemize}
+	\item Why there is credit rationing?
+	\begin{itemize}
+		\item If the borrowing demand exceeds lending supply, why doesn't the interest rate increase to clear the market?
+		\item Because checking is costly, so incentive compatibleness requires interest rate not being too high.
+		They prove that the optimal interest rate is hump shape.
+	\end{itemize}
+\end{itemize}
+
+An IC contract $\{S,K(w),R(w)\}$ contains three parts.
+$S$ is the checking area.
+$K(w)$ is the transfer to lender when not checking.
+$R(w)$ is the transfer to lender when checking.
+Since the contract is IC, so the reported $\hat w$ is just actual realized $w$.
+
+There are three steps to prove the optimal contract is debt contract in this asymmetric information case.
+\begin{enumerate}
+	\item Prove $K(w)$ equals a constant x. [easy]
+	\item Prove the IR constraint of lender will be tight. [easy]
+	\item Prove $R(w)=w$, i.e. lender will take away everything in checking case. [difficult] 
+\end{enumerate}
+
+In the third step, the idea is easy.
+Because if lender takes away everything in checking case, then the checking area can be smaller, thus can save checking cost.
+The difficulty is: when we lower x (to make checking area A smaller), the non-checking area B becomes larger.
+The changes are in two different directions and problem becomes subtle.
+\textcolor{red}{In discussion we use the total differentiation approach to solve this.
+Important}.\\
+
+\noindent
+\textbf{Techniques:}
+
+\textbf{how to prove optimal contract format:}
+
+See above.\\
+
+\textbf{recursive structure in defining EQM:}
+
+One difficulty in determining the optimal contract is how to characterize outside options of lender.
+In equilibrium, When a lender decides whether to accept a contract from a specific borrower (entrepreneur), his outside option should be market interest rate $r$.
+Because entrepreneur can't identify lender, and all entrepreneur are homogeneous ex ante, so if the expected return from a specific contract should be larger than mkt interest rate $r$.
+Thus the IR of lender is:
+
+\[\int_A R(w)d(F(w))+\int_B xd(F(w))-\gamma Pr(A) \geq r\]
+
+$r$ has to be pinned down in the eqm. Because all agents have rational expectation, thus the market clearing $r$ will be the same as their expectation.
+
+The equilibrium is defined as:
+\begin{itemize}
+	\item 
+\end{itemize}
+
+% section williamson_87_qje (end)
+
+\section{Chari et.al, 14 AER} % (fold)
+\label{sec:chari_et_al_14_aer}
+
+\textbf{\bibentry{Chari_etal2014:aer}}
+
+\vspace{3mm}
+\noindent
+\textbf{Empirical Facts:}
+\begin{itemize}
+ 	\item simultaneous fluctuation between secondary loan market and underlying land market
+ 	\item persistence of collapse in secondary loan market trade volume
+ \end{itemize}
+
+ \noindent
+ \textbf{Main Mechanism:}
+ \begin{itemize}
+ 	\item adverse selection AND reputation
+ 	\item key assumptions:
+ 	\begin{itemize}
+ 		\item agent (bank) types persist over time
+ 		\item players are non-annonymous (possible to build reputation)
+ 	\end{itemize}
+ 	\item adverse selection: can account for trade volume fluctuations correlated with underlying collateral value
+ 	\item reputation:
+ 	\begin{itemize}
+ 		\item wihout reputation concern, adverse selection will be solved quickly. Because the first stage features a separating equilibrium
+ 		\item with high enough reputation concern (patient enough), first stage cannot be fully separate, so adverse selection problem persists
+ 	\end{itemize}
+ \end{itemize}
+
+% section chari_et_al_14_aer (end)
+
+\section{Euro Crisis} % (fold)
+\label{sec:euro_crisis}
+
+This section is based on a course material of Wang Jue.
+Basically it discusses the theoretical concerns of Optimal Currency Area (OCA), why Europe adopts it, its success and its failure, and the recent Euro crisis.\\
+
+\textbf{\bibentry{Krugman:2012eu}}
+
+\cite{Krugman:2012eu} discusses the crisis of Euro area.
+Based on OCA theory by Mundell, there are two big things to look at: \textbf{labour mobility} and \textbf{fiscal integration}.
+Because areas are likely to suffer local idiosyncratic shocks.
+\begin{itemize}
+	\item Without labour mobility, a state has to make wage fall to restore the full employment, this will be much easier with its own to devalue.
+But if labour mobility is high, then workers can just move to other states.
+	\item Fiscal integration will also help. First because federal transfer is like a insurance, also because the borrowing cost for federal gevernment is much lower.
+\end{itemize}
+The Euro crisis faces challenges in both parts.
+\begin{itemize}
+	\item The labor mobility is not high enough.
+	\item No fiscal integration. And the asymmetric shock is so severe, making fiscal burden so large that calls government solvency into question. (e.g. in Spain and Greek)
+	\item The bank issue. There is no `last resort', so the fear of sovereign default undermineds confidence in private banks which hold these bonds. This is called \textit{doom loops}.
+	\begin{itemize}
+		\item Compare between euro area countries and pegged-to-euro countries.
+Austria and Finland uses euro, but Finland just pegged to euro.
+This flexibility makes interest rate much lower during the crisis.
+	\end{itemize}
+\end{itemize}
+
+\vspace{2mm}
+\textbf{\bibentry{baldwin2015eurozone}}
+
+\section{Seminar Notes} % (fold)
+\label{sec:seminar_notes}
+
+\noindent
+\textbf{Cryptocurrency}
+
+\begin{itemize}
+	\item By Jesús Fernández-Villaverde and Daniel	Sanches 2017
+		.Use Lagos and Wright (2005) framework.
+	\begin{itemize}
+		\item \url{http://economics.sas.upenn.edu/~jesusfv/Cryptocurrencies.pdf}
+		\item Not positive on private currencies. First, competitive private money will not provide price stability, either with a profit-maximizing entrpreneurs or through automaton.
+		\item Even with price stability, value of private moneis may go zero in infinite equilibriums.
+		\item Purely private money system does not provide social optimal quantity of money.
+	\end{itemize}
+\end{itemize}
+
+% section seminar_notes (end)
+
+% section euro_crisis (end)
+
+\chapter{Methodology} % (fold)
+\label{cha:methodology}
+
+\noindent
+\textbf{Reductionism, and Micro Fundations of Economics:}
+
+Economists are fascinated in forming `micro fundations' for almost all models. But do we really need this, does this effort pay?
+
+As pointed in famous paper \cite{anderson1972:science}: `\textit{The ability to reduce everything to simple fundamental laws doesn't imply the ability to start from those laws and reconstruct the universe...
+At each level of complexity entirely new properties appear...
+There is no useful parallel to be drawn between the way in which complexity appears in simplest cases of many modies and chemistry and culture ones.}'
+The aggregated economy is so complecated that may not be reduced to individual decision problems.
+\footnote{Zhao Dingxing has an article discussing this problem.
+
+See \url{https://www.evernote.com/l/ATUOIdQb8hBM5r3QQv8cTK52Amq4-qlwb0E}}
+
+Another problem worth thinking is the relationship between Sonnethein-Debreu theorem and macro economics models.
+
+\vspace{3mm}
+\hrule
+\vspace{3mm}
+
+\vspace{3mm}
+\noindent
+\textbf{Meaning of Decision Theory:}
+
+(This part is heavily influenced by Henrique's class.)
+
+Why we need to do decision theory?
+Take an \textit{inverse engineering} perspective.
+Suppose we have a model, which uses utility function to describe people's decison choices. 
+That is, $u:X \rightarrow \R$.
+And we define $C(B)=\argmin_{x\in B} u(x)=
+\{x\in B | u(x)\geq u(y),\forall y\in B\}$.
+We can map such functions to a \textit{equivalent class}, and can further map it to a \textit{preference relation} (a subset of relations).
+
+The problem is such mapping is not surjective.
+Every utility function has a corresponding equivalence and a prefence relation,
+but there is some preference relation that cannot be represented by a utility function.
+Thus we need to put some restrictions over preference relation.
+
+The first relation is that the cardinality of indifference curves cannot be larger than $\R$.
+This is easy to understand.
+
+But this restriction is not enough.
+Think of lexicographic preference,
+every point in the two-dimension space is a indifference class.
+The cardinality of which is $R^2$, equivalent to cardinality of $\R$.
+But we know that such preference do not have a corresponding utility function.
+We can further restrict preference to \textit{order separable} relations,
+then by Debreu Thm, we can show the \textit{iff} between utility and preference relations.
+
+\begin{defn}[Order Separable]
+A preference relation defined over $X$ is order separable if $\exists Y \subseteq X$ countable s.t. $\forall x_1,x_3 \subseteq X$,
+we have $x_1 \succ x_2 \Rightarrow \exists y \in Y$
+ s.t. $x_1 \succ y \succ x_2$.
+\end{defn}
+
+Important here is thaat by assuming the range of utility function is $\R$ (such a weak condition),
+we actually put some restrictions over preference.
+
+\vspace{3mm}
+\hrule
+\vspace{3mm}
+
+\vspace{2mm}
+\noindent
+\textbf{Calibration:}
+
+\noindent
+Why use calibration instead of estimation?
+\begin{itemize}
+	\item Because we live in a `tenth-best' world, and our model only catches a small part of the world.
+	Use calibration we can fit the moments that our model fail to catch,
+	in this sense to be more accurate.
+\end{itemize}
+
+May use calibration parameters as an intuitive check of whether the code we wrote is correct.
+
+\myline
+
+\noindent
+\textbf{Research Reproducibility}
+
+\cite{Maniadis:2017gq} claims two aspects of reproducibility problem.
+First, it can be seen as an `evidence game', 
+where researchers have some private information
+and evaluators have to design a incentive compatible mechanism for publishing and granting.
+Second, empirical methods from meta-research may help. 
+(I don't understand the second part.)
+
+\cite{Maniadis:2017hi} in the same issue provides more detailed guide on what will affect the credibility of scientific research.
+It raises a concept post-study probability,
+\[PSP=\frac{(1-\beta)\pi}{(1-\beta)\pi+ \alpha(1-\pi)}\]
+where $\alpha$ is significance level, $1-\beta$ is power,
+and $\pi$ is the probability that a research question is actually true. $\pi$ can be think of as \textit{prior} given by theory.
+This is the fraction of `truly true and reported true' divided by `all reported true'.
+Easy to see, when $\pi$ is low, 
+the PSP can be very low even with low $\alpha$.
+This indicates that with those fields where theory can provide little guide,
+we have to be very skeptical to the `rejection' outcomes.
+They are very likely to be `false positive'.
+
+% chapter methodology (end)
+
 % chapter macro (end)
+\part{Mathematics}
 
@@
 
+\section{Supermodularity} % (fold)
+\label{sec:supermodularity}
+
+\noindent
+Reference: 
+\begin{itemize}
+	\item \href{run:resources/sobel_supermodularity.pdf}{Sobel's Notes:} \url{http://econweb.ucsd.edu/~jsobel/205f10/notes12.pdf}
+	\item \href{run:resources/monotone_comparative_statics.pdf}{A more detailed note:} \url{https://pages.wustl.edu/files/pages/imce/nachbar/monotonecomparativestatics.pdf}
+	\item \bibentry{topkis1998:supermodularity}
+\end{itemize}
+
+% section supermodularity (end)
+
 % chapter general_mathematical_skills (end)
 
+\chapter{Probability} % (fold)
+\label{cha:probability}
+
+\section{Bayesian Statistics} % (fold)
+\label{sec:bayesian_statistics}
+
+\subsection{Bayesian Updating} % (fold)
+\label{sub:bayesian_updating}
+
+\begin{thm}[Bayesian Update in Odds]
+For hypothesis $H$, data $d$ and prior odds $O(H)$. We have posterior odds 
+$O(H|d) = O(H)\cdot\frac{Pr(d|H)}{Pr(d|H^c)}$,
+where the second term is called \textit{Bayes Factor}.
+\end{thm}
+
+\begin{myproof}
+\begin{align*}
+	O(H|d)&=\frac{Pr(H|d)}{Pr(H^c|d)} \\
+	&=\frac{Pr(d|H)Pr(H)}{Pr(d|H^c)Pr(H^c)}\\
+	&=\frac{Pr(d|H)}{Pr(d|H^c)}\cdot O(H)
+\end{align*}
+\end{myproof}
+
+% subsection bayesian_updating (end)
+
+% section bayesian_statistics (end)
+
+% chapter probability (end)
+
+\chapter{Numerical Methods} % (fold)
+\label{cha:numerical_methods}
+
+\noindent
+\textbf{Computation laguage:}
+\begin{itemize}
+	\item \url{http://economics.sas.upenn.edu/~jesusfv/comparison_languages.pdf}
+	\begin{itemize}
+		\item discusses efficiency of different languages
+		\item hybrid language can significantly increase efficiency
+	\end{itemize}
+\end{itemize}
+
+\noindent
+\textbf{Matlab Speed Up:}
+\begin{itemize}
+	\item Microeconometrics and Matlab: an Introduction, Ch-10
+	\item vectorize and preallocate values
+		\begin{itemize}
+		 	\item Cooper's growth model uses clever vectorizing, avoid one loop
+		 \end{itemize} 
+	\item profiling code: profile on, main, profile off
+	\item parallel computing
+\end{itemize}
+
+\section{Numerical Maximization} % (fold)
+\label{sec:numerical_maximization}
+
+\noindent
+\textbf{Newton-Raphson Method:}
+
+Idea: use quadratic function to approaximating real function at current guess,
+then find the maximization point of this quadratic function as next guess.
+\[\beta_{t+1}=\beta_t + \lambda(-H^{-1}_t)g_t\]
+where $H_t$ is the Hessian of the function to be evaluated at $\beta_t$, 
+and $g_t$ is the Jacobian at $\beta_t$,
+$\lambda$ is the step size, generally may take 1.
+
+\vspace{3mm}
+\noindent
+\textbf{BHHH Method:}
+
+Idea: almost the same as Newton-Raphson, but use the outer product to approximate Hessian.
+\[\beta_{t+1}=\beta_t + \lambda(-B^{-1}_t)g_t\]
+where $B_t = \frac{1}{N}\sum_{n=1}^N{s_n(\beta_t)s_n(\beta_t)'}$
+and $s_n(\beta_t)= \partial P_n(\beta)/\partial \beta$ evaluated at $\beta_t$,
+and $g_t=\frac{1}{N}\sum_{n=1}^N{s_n(\beta_t)}$.
+
+Key is, when evaluated at maximum value, $s_n$ should be zero. Thus $B_t$ evaluated at maximum is the variance of $s_n$ in the sample, which is just the Hessian of the sample likelihood function.
+This is just \textit{information equality}.
+
+\begin{itemize}
+	\item [\textbf{pros:}] BHHH is generally faster than Newton-Raphson near the maximum.
+	Because $s_n$ have to be calculated anyway, 
+	but in NR procedure we have to calculate the second derivatives as well.
+	\textcolor{blue}{But seems this is not the case, in experiments BHHH always slower than Newton-Raphson.}
+	\item [\textbf{cons:}] BHHH is generally slower when $\beta_t$ is far from true value. 
+	Because at these points $B_t$ is not a good approximate of $H_t$.
+\end{itemize}
+
+% section numerical_maximization (end)
+
+\begin{itemize}
+	\item Root Solving
+	\item Integration
+	\begin{itemize}
+		\item Gaussian quadrature
+		\item Sparse grid
+		\item Monte Carlo integration
+		\begin{itemize}
+			\item antithetic accelerating
+			\item importantce sampling
+		\end{itemize}
+		\item Quasi Monte Carlo
+	\end{itemize}
+\end{itemize}
+
+% chapter numerical_methods (end)
+
+\bookmarksetup{startatroot}% this is it
+\addtocontents{toc}{\bigskip}% perhaps as well
+
+\chapter{Miscellany} % (fold)
+\label{cha:miscellany}
+
+\noindent
+\textbf{Presentation:}
+\begin{itemize}
+	\item Always motivate very clearly, both from economics facts and from literature.
+	\begin{itemize}
+		\item In macro, a graph generally helps
+	\end{itemize}
+	\item If possible, always use a simple model at the beginning
+	\begin{itemize}
+		\item To pin down the concepts/definitions
+		\item To show the mechanism intuitively
+	\end{itemize}
+	\item Understand the result both mathematically and intuitively
+	\item When writing, write horizontally!
+\end{itemize}
+
+% part miscellany_ (end)
+
 \renewcommand\refname{Reference}
-\bibliographystyle{plainnat}
+\bibliographystyle{chicago}
 \bibliography{paper_notes}

### 2017-12-10 resources/text_as_data/HW1.tex
normal update

\documentclass[12pt,letterpaper]{article}
\usepackage{graphicx,textcomp}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fullpage}
\usepackage{color}
\usepackage[reqno]{amsmath}
\usepackage{amsthm}
\usepackage{amssymb,enumerate}
\usepackage[all]{xy}
\usepackage{endnotes}
\usepackage{lscape}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
\usepackage[compact]{titlesec}
\usepackage{dcolumn}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{multirow}
\usepackage{xcolor}
\newcolumntype{.}{D{.}{.}{-1}}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\definecolor{light-gray}{gray}{0.65}
\usepackage{url}
\newcommand{\Sref}[1]{Section~\ref{#1}}
\newtheorem{hyp}{Hypothesis}

\title{Text as Data: Homework 1}
\date{}

\begin{document}
\maketitle

\subsubsection*{Question 1: Using Python}
\begin{itemize}
\item[a)] Install {\tt Python}, {\tt Rstudio}, and {\tt R markdown}
\item[b)] Using {\tt Python} write to a {\tt .txt} file:
\begin{itemize}
\item[-] {\tt Hello World}
\end{itemize}
With a for loop, write the numbers 1-100 to the same text file
\item[c)] Close the .txt file, turn it in with your homework
\end{itemize}

\subsubsection*{Question 2: Properties of Random Variables}  
\begin{itemize}
\item[a)] Suppose $X$ is a random variable, with $E[X] = \mu$ and var$(X) = \sigma^2$.  Show that $c = E[X]$ minimizes
\begin{eqnarray}
E[ (X - c)^2] \nonumber 
\end{eqnarray}
Why does this suggest $E[X]$ is a ``good" guess for the value of $X$?
\item[b)]  Suppose $Y$ and $Z$ are random variables, with joint density $f(y, z)$.  
\begin{itemize}
\item[i)] How do we obtain the marginal distribution of $Y$, $f_{Y}(y)$ (should be an expression involving an integral)
\item[ii)] How do we obtain the marginal distribution of $Z$, $f_{Z}(z)$ (should be an expression involving an integral)
\item[iii)] Show that if $Y$ and $Z$ are independent, $E[YZ] = E[Y]E[Z]$
\end{itemize} 
%\item[c)] \textbf{Iterated Expectations}: Suppose $Y$ and $Z$ are random variables, with joint density $f(y, z)$. Show that 
%\begin{eqnarray}
%E[Y] & = & E[ E[ Y|Z ] ] \nonumber \\
%& = & \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} f_{Y|Z}(y|z)f_{Z}(z) dy dz \nonumber 
%\end{eqnarray}
\end{itemize}

\subsubsection*{Question 3: Finding Critical Values for a Function}

Suppose we have a function $f:\Re\rightarrow\Re$, $f(x) = \sin(x)$.  
\begin{itemize}
\item[a)] Using {\tt R} plot $\sin(x)$ for $x \in [-2 \pi, 2 \pi] $ (here $\pi$ is the mathematical constant). 
\item[b)] What is $f^{'}(x)$ (first derivative at $x$)?  Using {\tt R} plot it over $[-2 \pi, 2 \pi]$
\item[c)] What is $f^{''}(x)$ (second derivative at $x$)? Using {\tt R} plot it over $[-2 \pi, 2 \pi]$
\end{itemize}
We say that $x^{*}$ is a critical value for a function if $f^{'}(x^{*}) = 0$.  We can find $x^{*}$ algebraically. Or, we can use a computational approach.\\
\noindent We discussed the Newton-Raphson approach in class on Thursday.  We're going to write our own implementation of the algorithm in {\tt R} and apply it to find the critical values of $f(x) = \sin(x)$ 
\begin{itemize}
\item[d)] Suppose that we have current guess for the root $x_{t}$.  Then the updated guess, $x_{t+1}$ is given by
\begin{eqnarray}
x_{t+1} & = & x_{t} - \frac{f^{'}(x_{t})}{f^{''}(x_{t})} \nonumber 
\end{eqnarray}
\noindent where $f^{'}(x_{t})$ is the first derivative evaluated at $x_{t}$ and $f^{''}(x_{t})$ is the second derivative evaluated at $x_{t}$.  \\
\noindent Write a function in {\tt R} that provides the update step for some value $x_{t}$ if $f(x) = \sin(x)$.  
\item[e)] The Newton-Raphson algorithm continues to update until the size of the update step drops below a threshold.  Using the {\tt while} command in R, write a loop that continues updating until the change,( $|x_{t+1} - x_{t}|$) drops below $10^{-5}$.  
\item[f)] Place the while loop in a function that returns the converged value $x_{\text{final}}$
\item[g)] Use your function with initial guesses $-2, -1, 1, 2$.  What values do you obtain?  Now examine the behavior close to $0$.  Why is it so unstable?
\end{itemize}

\begin{table}[hbt!]
\caption{Pseudo Code for Newton Raphson (To assist in developing your function)}
\begin{itemize}
\item $x_{0}$ = initial guess
\item Do while change $>$ tolerance:
\begin{itemize}
\item[] $x_{t+1}  = x_{t} - \frac{f^{'}(x_{t})}{f^{''}(x_{t} ) } $
\item[] change = $| x_{t+1} - x_{t}|$ 
\end{itemize}
\item return $x_{t+1}$
\end{itemize}
\end{table}

\subsubsection*{Problem 3: Probit Regression with a Prior}

Suppose that we assume the following data generation process
\begin{eqnarray}
Y_{i} & \sim & \text{Bernoulli}(\pi_{i} ) \nonumber \\
\pi_{i} & = & \Phi(\boldsymbol{X}_{i} \boldsymbol{\beta}) \nonumber \\
\beta_{j} & \sim & \text{Normal}(\mu, \sigma^{2}_{j} )\nonumber 
\end{eqnarray}

with $\boldsymbol{X}_{i} = (1, x_{i})$ for all $i$ $(i = 1, \hdots, N)$,  $\boldsymbol{\beta} = (\beta_{1}, \beta_{2})$, and $\Phi(\cdot)$ is the cumulative normal distribution function.  \\

We might equivalently write a directed acyclic graph as,

\vspace{0.25in}

\begin{large}
\begin{tikzpicture}
\node(dummy) at (-8, 8) [] {} ; 
\node(covariates) at (-3, 9) [] {$\boldsymbol{X}$} ; 
\node(betas) at (-3, 7) [] {$\boldsymbol{\beta}$ } ; 
\node(prior1) at (-5.5, 7.5) [] {$\mu$ } ; 
\node(prior2) at (-5.5, 6.5) [] {$\sigma^2$ } ; 
\node(dependent) at (2, 8) [] {$\boldsymbol{Y}$};
\draw[->, line width = 1.5pt] (prior1) to [out = 0, in = 145] (betas) ; 
\draw[->, line width = 1.5pt] (prior2) to [out = 0, in = 225] (betas) ; 
\draw[->, line width = 1.5pt] (covariates) to [out = 0, in= 180] (dependent) ; 
\draw[->, line width = 1.5pt] (betas) to [out = 0, in= 180] (dependent) ; 
\end{tikzpicture}
\end{large}

This is very similar to the model described in class, but now we have added a \emph{prior} on $\boldsymbol{\beta}$.  This slightly alters the objective function:

\begin{eqnarray}
p(\boldsymbol{\beta} | \boldsymbol{Y}, \boldsymbol{X}) & \propto & p(\boldsymbol{\beta}|\mu, \sigma^2) \times p(\boldsymbol{Y}| \boldsymbol{X}, \boldsymbol{\beta}) \label{e:post} \\
& \propto &  \prod_{j=1}^{2} \frac{1}{\sqrt{2\pi} \sigma} \exp\left( - \frac{(\beta_{j} - \mu)^2}{2 \sigma^2} \right) \times \prod_{i=1}^{N} \Phi(\boldsymbol{X}_{i}\boldsymbol{\beta})^{Y_{i} } ( 1- \Phi(\boldsymbol{X}_{i}\boldsymbol{\beta})^{1 - Y_{i} } \nonumber 
\end{eqnarray}

In this problem, we will examine how the prior on $\boldsymbol{\beta}$, and in particular the values we set for $\mu$ and $\sigma^2$, alters our inferences about $\boldsymbol{\beta}$.

\begin{itemize}
\item[a)] Analytically, write out the $\log(p(\boldsymbol{\beta} | \boldsymbol{Y}, \boldsymbol{X}))$.  
\item[b)] In {\tt R} create a function for the $\log$ of Equation \ref{e:post}.
\item[c)] Using the synthetic data and the optim guide from class, use {\tt optim} to find $\widehat{\boldsymbol{\beta}}$ with $\mu = 0$ and $\sigma^2 = 1000$
\item[d)] Set $\mu = 1$ and then vary $\sigma^2$.  Using a {\tt for} loop, store estimates of how $\beta_{2}$ changes as you vary $\sigma^2$ from $10$ to $0.01$.  Plot $\beta_{2}$ against $\sigma^2$ and describe what happens as $\sigma^2$ varies.  
\end{itemize}

\end{document}

### 2017-12-10 resources/text_as_data/HW2.tex
normal update

\documentclass[12pt,letterpaper]{article}
\usepackage{graphicx,textcomp}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fullpage}
\usepackage{color}
\usepackage[reqno]{amsmath}
\usepackage{amsthm}
\usepackage{amssymb,enumerate}
\usepackage[all]{xy}
\usepackage{endnotes}
\usepackage{lscape}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
\usepackage[compact]{titlesec}
\usepackage{dcolumn}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{multirow}
\usepackage{xcolor}
\newcolumntype{.}{D{.}{.}{-1}}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\definecolor{light-gray}{gray}{0.65}
\usepackage{url}
\newcommand{\Sref}[1]{Section~\ref{#1}}
\newtheorem{hyp}{Hypothesis}

\title{Text as Data: Homework 2}
\date{}

\begin{document}
\maketitle

In this homework assignment we're going to analyze the first presidential debate from the 2012 election.  \\

\subsubsection*{Problem 1} 
To analyze the debate, we first need to load the debate and parse the content.  On the coursewebsite, you'll find the file {\tt debate1.html}.  Download the file and open it in a browser. We will use {\tt BeautifulSoup} to parse HTML file containing the debate transcript.

\begin{itemize}
\item Load the webpage into {\tt Python} and use {\tt BeautifulSoup} to create a searchable version of the debate. What tags can you use to identify statements?

\item Note that not all of the statements contain information about the speaker. Devise a rule to assign the unlabeled statements to speakers.

\item For substantive reasons, we would like to define a single statement as any \textit{uninterrupted} speech from a candidate. We'll say a candidate is interrupted when the transcript says that a new speaker has begun.  In other words, cross talk doesn't count as an interruption. Create a list with just the text (not the tags) of each statement as an element. Some statements are split among several tags; these will need to be concatenated according to the rule you devised above. Remember to filter out notes about audience behavior

\end{itemize}

\subsection*{Problem 2}
Now we're going to do some more preprocessing to create a dataset that includes useful information about our texts. We will use a curated dictionary list from Neal Caren. The positive words are at {\tt http://www.unc.edu/~ncaren/haphazard/positive.txt} and the negative words are at {\tt http://www.unc.edu/~ncaren/haphazard/negative.txt}.
\begin{itemize}
\item Load the positive and negative words into {\tt python}

\item Use the {\tt porter}, {\tt snowball} and {\tt lancaster} stemmers from the {\tt nltk} package to create stemmed versions of the dictionaries.

\item Using the original and stemmed dictionaries, we're going to create a statement by statement data set of the speech. 
The data set should have the following columns: 
\begin{itemize}
\item[1)] Statement number (place in debate)
\item[2)] Speaker 
\item[3)] Number of non-stop words spoken
\item[4)] Number of positive words
\item[5)] Number of negative words
\item[6)] Number of lancaster stemmed positive words
\item[7)] Number of lancaster stemmed negative words
\item[8)] Number of porter stemmed positive words
\item[9)] Number of porter stemmed negative words
\item[10)] Number of snowball stemmed positive words
\item[11)] Number of snowball stemmed negative words
\end{itemize}
\end{itemize}

To create the data set, create a set of nested dictionaries that map each statement in the list created in Problem 1 to the each of the attributes described above. To  calculate the values for items 3 - 11 above, you'll need to do the following to each statement:
\begin{itemize}
\item[-] Discard punctuation
\item[-] Remove capitalization
\item[-] Remove stop words with the list of words provided here: \\
{\tt `http://jmlr.org/papers/volume5/lewis04a/a11-smart-stop-list/english.stop'}
\item[-] Tokenize the words
\item[-] Apply each of the stemmers, determining which of the words appear in the corresponding stemmed dictionaries
\end{itemize}

Write your dataset as a csv file and save it to a working directory. Turn it in with your homework.

\subsection*{Problem 3}

Using our new data set, let's make some observations about the debate
\begin{itemize}
\item[-] Load the data into {\tt R} 
\item[-] Create a visualization that compares the overall positive and negative word rate for Obama, Romney, and Lehrer.  What patterns do you notice?  There is no one right answer, be creative!
\item[-] Using your data set, examine trends in each candidate's statements and Lehrer's speeches.  Do you notice any
\begin{itemize}
\item[i)] Trends in the measured tone?
\item[ii)] Response to the other candidate's tone (examining who spoke previously)?
\item[iii)] Overall interesting patterns? (this is an intentionally vague question)
\end{itemize}
\end{itemize}

\end{document}

### 2017-12-10 resources/text_as_data/HW4.tex
normal update

\documentclass[12pt,letterpaper]{article}
\usepackage{graphicx,textcomp}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fullpage}
\usepackage{color}
\usepackage[reqno]{amsmath}
\usepackage{amsthm}
\usepackage{amssymb,enumerate}
\usepackage[all]{xy}
\usepackage{endnotes}
\usepackage{lscape}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
\usepackage[compact]{titlesec}
\usepackage{dcolumn}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{multirow}
\usepackage{xcolor}
\newcolumntype{.}{D{.}{.}{-1}}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\definecolor{light-gray}{gray}{0.65}
\usepackage{url}
\newcommand{\Sref}[1]{Section~\ref{#1}}
\newtheorem{hyp}{Hypothesis}

\title{Text as Data: Homework 4}
\date{Due: 11/7 at 5pm}

\begin{document}
\maketitle

In this homework assignment we will analyze Machiavelli's \emph{The Prince}.  Download {\tt Mach.tar} from the course website and expand the compressed folder.  (This is relevant {\tt http://xkcd.com/1168/}).  \\

Each file represents a subset of the manuscript.  We will analyze its contents using principal components, multidimensional scaling, and clustering methods.

\subsection*{Create a Document-Term Matrix}

Using the sections from the Machiavelli text, create a document term matrix.
\begin{itemize}
\item[-] Discard punctuation, capitalization
\item[-] Apply the porter stemmer to the documents
\item[-] Remove stop words from the following list (remembering to stem the stop words):
{\tt `http://jmlr.org/papers/volume5/lewis04a/a11-smart-stop-list/english.stop'}
\item[-] Identify the 500 most common unigrams
\item[-] Create a $N \times 500$ document term matrix $\boldsymbol{X}$, where the columns count the unigrams and the rows are the documents
\end{itemize}

We will work with a normalized version of the term document matrix.  That is we will divide each row by the total number of words in the top 500 unigrams used:
\begin{eqnarray}
\boldsymbol{x}_{i}^{*} & = & \frac{\boldsymbol{x}_{i}}{\sum_{j=1}^{500} x_{ij}} \nonumber\\
\boldsymbol{X}^{*} & = & \begin{pmatrix} \boldsymbol{x}_{1}^{*} \\
\boldsymbol{x}_{2}^{*} \\
\vdots \\
\boldsymbol{x}_{N}^{*} \\
  \end{pmatrix}  \nonumber 
\end{eqnarray}

\subsection*{Low Dimensional Embeddings with Principal Components}

\begin{itemize}
\item[1)]  Wise Will (WW), your friend with a weird name, notices you looking at the slides about principal component analysis (PCA).   WW casually remarks that the variance of the eigenvalues of the variance-covariance matrix is a useful heuristic for knowing if PCA can be fruitfully applied to some document-term matrix.  WW, completely unsolicited, explains that as the variance of the eigenvalues goes up, the more useful PCA will be.  He then laughs and leaves your office.  WW is kind of a jerk.   \\

Let's formalize WW's suggestion. Suppose document-term matrix $\boldsymbol{X}$ has variance-covariance matrix $\boldsymbol{\Sigma} = \frac{\boldsymbol{X}^{'}\boldsymbol{X}}{N}$.  And suppose that $\boldsymbol{\Sigma}$ has eigenvalues $\lambda_{1}>\lambda_{2}>\hdots > \lambda_{d}>0$. Then we calculate the variance of the eigenvalues as 
\begin{eqnarray}
\sigma^{2} & = & \frac{1}{d} \sum_{j=1}^{d}(\lambda_{j} - \bar{\lambda})^{2} \nonumber 
\end{eqnarray}

where $\bar{\lambda}$ is $\frac{1}{d} \sum_{i=1}^{d} \lambda_{i}$. WW is saying that as $\sigma^{2}$ gets bigger, a low-dimensional embedding via PCA will provide a better summary of our data.   \\

Does WW have a good point?  Why or why not? (Hint: what do the eigenvalues represent?)
\item[2)] Apply the function {\tt prcomp} to $\boldsymbol{X}^{*}$. Be sure to set use a scaled version of the data, by setting {\tt scale = T}, which will ensure that each column has unit variance.  
\begin{itemize}
\item[a)] Create a plot of variance explained by each additional principal component. What does this plot suggest about the number of components to include?
\item[b)] Plot the two-dimensional embedding of the text documents.  Label the texts with their number.  (Each file is {\tt Mach\_XX.txt}, where {\tt XX} is the chunk number)
\item[c)] Label the two largest principal components.  What does this embedding suggest about the primary variation this representation of the Prince?  (Hint: if your {\tt embed} is your object with principal components, examine {\tt embed\$rotation})
\end{itemize}

\item[3)]An alternative method---discussed at the end of the seventh lecture---is multidimensional scaling (MDS).  Classic MDS attempts to preserve distances between objects in a low dimensional scaling.

\begin{itemize}
\item[a)] Calculate the Euclidean distance between each document using $\boldsymbol{X}^{*}$.  Call this matrix $\boldsymbol{D}(\boldsymbol{X}^{*})$  (Hint: use {\tt R}'s built in function {\tt dist})
\item[b)] Apply the classic MDS to $\boldsymbol{D}(\boldsymbol{X}^{*})$ using the {\tt R} function {\tt cmdscale}.  That is, execute the code\\
{\tt mds\_scale<- cmdscale(DISTANCE\_MATRIX, k = 2)} 
\item[c)] Apply PCA to $\boldsymbol{X}^{*}$, but this time do not use {\tt prcomp}'s scaling option.  That is, use {\tt prcomp} with {\tt scale = F}.  
\item[d)] Compare the first dimension of the output from classic MDS to the first dimension of the embedding from principal components. What is the correlation between the embeddings? 
\item[d)] Now use {\tt dist} to create a distance matrix using the {\tt manhattan} metric, apply Classic multidimensional scaling to the distance matrix based on manhattan distance, and compare the first dimension of this embedding to the first dimension from PCA.  What is the correlation?
\item[e)] What do you conclude about the relationship between PCA and MDS?
\end{itemize}

\end{itemize}

\subsection*{Clustering Methods}

\begin{itemize}
\item[1)] Using the {\tt kmeans} function, create a plot of the {\tt kmeans} objective function as the number of clusters varies from 2 to $N - 1$.    
\item[2)] Apply K-Means with 6 clusters, being sure to use {\tt set.seed} to ensure you can replicate your analysis
\item[3)] Label each cluster using computer and hand methods:
\begin{itemize}
\item[i)] Suppose $\boldsymbol{\theta}_{k}$ is the cluster center for cluster $k$ and define $\bar{\boldsymbol{\theta}}_{-k} = \frac{\sum_{j \neq k} \boldsymbol{\theta_{j}}   }{K-1 }$ or the average of the centers not $k$.  Define 
\begin{eqnarray}
\text{Diff}_{k} & = & \boldsymbol{\theta}_{k} - \bar{\boldsymbol{\theta}}_{-k}\nonumber 
\end{eqnarray}

Use the top ten words from $\text{Diff}_{k}$ to label the clusters
\item[ii)] Sample and read texts assigned to each cluster and produce a hand label
\end{itemize}
\item[4)] Measure the cohesiveness and exclusivity of each cluster.  What is the most exclusive and most cohesive topics? What are the least?  Does this align with your reading of the texts?

\end{itemize}

\end{document}

### 2017-12-10 resources/text_as_data/HW5.tex
normal update

\documentclass[12pt,letterpaper]{article}
\usepackage{graphicx,textcomp}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{fullpage}
\usepackage{color}
\usepackage[reqno]{amsmath}
\usepackage{amsthm}
\usepackage{amssymb,enumerate}
\usepackage[all]{xy}
\usepackage{endnotes}
\usepackage{lscape}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
\usepackage[compact]{titlesec}
\usepackage{dcolumn}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{multirow}
\usepackage{xcolor}
\newcolumntype{.}{D{.}{.}{-1}}
\newcolumntype{d}[1]{D{.}{.}{#1}}
\definecolor{light-gray}{gray}{0.65}
\usepackage{url}
\newcommand{\Sref}[1]{Section~\ref{#1}}
\newtheorem{hyp}{Hypothesis}

\title{Text as Data: Homework 5}
\date{Due: 12/5 at 5pm}

\begin{document}
\maketitle

In this homework we will analyze a collection of news stories from the New York Times from the November 1-3, 2004 (the day before, of, and after the 2004 general election). This data come from the New York Times Annotated Corpus and is for academic use only. We have done some preprocessing in order to simplify the homework tasks.

\section{Preprocessing and Creating a Document-Term Matrix}

\begin{itemize}
\item[a)] From the course website, download {\tt nyt\_ac.json} 
\item[b)] Using the {\tt JSON} library in python, import the data. Use {\tt type} to explore the structure of this data. How are this data organized?
\item[c)] Extract the title and text from each story.  Create an individual document for each story and write each of the files to a new directory (we will use this later to run {\tt Mallet})
\item[d)] Using the loaded {\tt json} file, create a document term matrix of the 1000 most used terms.  Be sure to: 
\begin{itemize}
\item[-] Discard word order
\item[-] Remove stop words
\item[-] Apply the porter stemmer
\end{itemize}
\item[e)] Include in your document-term matrix the \emph{desk} from which the story originated, which we will include later
\end{itemize}

\section{Using {\tt MALLET} to Fit Topic Models}

\begin{itemize}
\item[a)] Go to {\tt http://mallet.cs.umass.edu/download.php} and install {\tt MALLET} on your computer
\item[b)] Following the syntax from the code posted on the course website (flake.mallet) and from the {\tt MALLET} website, apply LDA with 4 and 8 topics
\item[c)] Using the code from the course website {\tt Examp\_tc11.R} move the output of {\tt MALLET} into {\tt R} and create a table describe both versions of LDA
\item[d)] Compare the 4 and 8 topic models.  How do the 4 and 8 topic models differ?  What information is included in the 8 topic model that isn't in the 4 topic model
\item[e)] For each originating desk, calculate the average proportion of documents from a desk dedicate to each topic.  How does the topic attention differ across desks?
\end{itemize}

\section{Using the {\tt Structural Topic Model} in {\tt R}}

\begin{itemize}
\item[a)] Download the {\tt stm} package for {\tt R} from {\tt CRAN}
\item[b)] Convert the document-term matrix to the appropriate format.  To do this, create a list in {\tt R} where each component of the list corresponds to an individual document.  Store in each component of the list a two rom matrix.  The number of columns corresponds to the number of non-zero entries for the document in the document-term matrix.  The first row will describe the words used in the document (the columns with the non-zero entry).  The second row will correspond to a count of each of the words in the document (they should all be non-zero)
\item[c)] Following the help file in {\tt STM} fit a model with 8 topics that conditions on the {\tt desk} of origin for topic prevalence
\item[d)] Use {\tt labelTopics} to label each of the topics
\item[e)] Compare the 8 topic proportions for each document to the 8 topic proportions without conditioning on {\tt desk} (in vanilla LDA).  How do the results differ?
\end{itemize}

\section{Supervised Learning with Naive Bayes}

\begin{itemize}
\item[a)] Using the version of Naive Bayes outlined on slide 24 of lecture 14, write a function to estimate $p(C_{k})$ and $\boldsymbol{\theta}_{k}$ for an arbitrary collection of categories.  Hint: to compute the probability of a document from a category, note you can work with the log of the probability equivalently.  
\item[b)] Let's focus on documents that came from Business/Financial desk and National Desk.  Using leave-one out cross validation, calculate the accuracy of Naive Bayes to calculate the label.
\item[c)] Compare the performance of Naive Bayes to the performance of 2 of the following 3 algorithms using 10-fold cross validation:
\begin{itemize}
\item[-] LASSO 
\item[-] Ridge 
\item[-] KRLS 
\end{itemize}
How does Naive Bayes compare? 
\end{itemize}

\end{document}

### 2017-12-10 resources/text_as_data/tc1.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{September 23rd, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

%%Introduction: who is in the class
%%what are they working on

\begin{frame}
\frametitle{Text and Political Science}

A pre-2000's view of text in social science
\begin{itemize}
\item[-] Social interaction often occurs in texts \pause 
\invisible<1>{\item[-] Social Scientists avoided studying texts/speech} \pause 
\invisible<1-2>{\item[-] Why?} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Hard to find} \pause 
\invisible<1-4>{\item[-] Time Consuming} \pause 
\invisible<1-5>{\item[-]  Not generalizable (each new data set...new coding scheme)} \pause 
\invisible<1-6>{\item[-]  Difficult to store/search} \pause 
\invisible<1-7>{\item[-] Idiosyncratic to coders/researcher} \pause 
\invisible<1-8>{\item[-] Statistical methods/algorithms, computationally intensive} 
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}

A post-2000's view of text in social science: 
\vspace{0.25in}

\invisible<1>{ Massive collections of texts are increasingly used as a data source in social science: }

\begin{itemize}
\invisible<1-2>{\item[-] Congressional speeches, press releases, newsletters, ...}
\invisible<1-3>{\item[-]  Facebook posts, tweets, emails, cell phone records, ...} 
\invisible<1-4>{\item[-]  Newspapers, magazines, news broadcasts, ...  } 
\invisible<1-5>{\item[-] Foreign news sources, treaties, sermons, fatwas, ...}
\end{itemize}

\pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
%
\footnotesize
Why? \pause
\begin{itemize}
\invisible<1>{\item[-] Massive increase in availability of unstructured text (10 minutes of worldwide email = 1 LOC )} \pause 
\invisible<1-2>{\item[-] Cheap storage: 1956: \$10,000 megabyte.  2014: $<<<<<$ \$0.0001 per megabyte  (Unless you're sending an SMS)  } \pause 
\invisible<1-3>{\item[-] Explosion in methods and programs to analyze texts} \pause 
\begin{itemize}
\invisible<1-4>{\item[-] Generalizable:  one method can be used across many methods and to unify collections of texts} \pause 
\invisible<1-5>{\item[-] Systematic: parameters/statistics demonstrate how models make coding decisions} \pause 
\invisible<1-6>{\item[-] Cheap: easily applied to many new collections of texts, computing power is inexpensive} \pause 
\end{itemize}
\invisible<1-7>{\item[-] \alert{Unchanged Demand}: Social life (politics, economic exchanges, social interactions) occurs in \alert{texts} } \pause 
\begin{itemize}
\invisible<1-8>{\item[-] Laws} \pause 
\invisible<1-9>{\item[-] Treaties } \pause
\invisible<1-10>{\item[-] News media} \pause
\invisible<1-11>{\item[-] Campaigns} \pause
\invisible<1-12>{\item[-] Political pundits} \pause
\invisible<1-13>{\item[-] Petitions } \pause
\invisible<1-14>{\item[-] Press Releases} \pause
\invisible<1-15>{\item[-] ...} 
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{What Can Text Methods Do?}

Haystack metaphor:\pause  \invisible<1>{\alert{ Improve Reading}} \pause 
\begin{itemize}
\invisible<1-2>{\item[-]  Interpreting the meaning of a sentence or phrase $\leadsto$ Analyzing a straw of hay} \pause 
\begin{itemize}
\invisible<1-3>{\item[-]Humans: amazing (Straussian political theory, analysis of English poetry) 
\item[-] Computers: struggle } \pause 
\end{itemize}
\invisible<1-4>{\item[-] Comparing, Organizing, and Classifying Texts$\leadsto$ Organizing hay stack} \pause 
\begin{itemize}
\invisible<1-5>{\item[-] Humans: terrible.  Tiny active memories
\item[-] Computers: amazing$\leadsto$ largely what we'll discuss today} \pause 
\end{itemize}
\end{itemize}
\invisible<1-6>{What automated text methods don't do:} \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Develop a comprehensive statistical model of language
\item[-] Replace the need to read 
\item[-] Develop a single tool + evaluation for all tasks } 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Texts are Deceptively Complex}

{\tt We've got some difficult days ahead.  But it doesn't matter with me now. Because I've been to the mountaintop. And I don't mind. Like anybody, I would like to live a long life. Longevity has its place. But I'm not concerned about that now. }

\pause

\begin{itemize}
\invisible<1>{\item[-] Who is the {\tt I} ?} \pause 
\invisible<1-2>{\item[-] Who is the {\tt We}? } \pause 
\invisible<1-3>{\item[-] What is the {\tt mountaintop} (literal?)} \pause 
\end{itemize}

\invisible<1-4>{Texts$\leadsto$ high dimensional, not self contained}

\end{frame}

\begin{frame}
\frametitle{Texts are Surprisingly Simple}

(Lamar Alexander (R-TN) Feb 10, 2005)
\begin{table}
\begin{tabular}{ll}
\hline
 Word & No. Times Used in Press Release \\
 \hline
 department &     12\\
  grant  &      9 \\
  program &   7 \\
  firefight &  7 \\
  secure  &    5 \\
  homeland  &  4 \\
  fund   &    3 \\
 award  &    2 \\
 safety  &     2 \\
 service &    2 \\
 AFGP   &    2 \\
 support &   2 \\
equip  &    2 \\
applaud  &  2\\ 
 assist  &   2\\ 
prepared &  2 \\
\hline  
\end{tabular}
\end{table}

\end{frame}

\begin{frame}
\frametitle{Texts are Surprisingly Simple (?)}

{\tt US  Senators Bill Frist  (R-TN)  and Lamar Alexander (R-TN) today applauded the U S  Department of Homeland Security for awarding a \$8,190 grant to the Tracy City Volunteer Fire Department under the 2004 Assistance to Firefighters Grant Program's  (\alert{AFGP})  FirePrevention and Safety Program...}

\end{frame}

\begin{frame}
\frametitle{Not just for ``big data" }

\pause

\invisible<1>{Manually develop categorization scheme for partitioning small (100) set of documents} \pause

  \begin{itemize}
\invisible<1-2>{ \item[-] Bell$(n) = $ number of ways of partitioning $n$ objects}
    \pause
   \invisible<1-3>{ \item[-] Bell$(2)=2$ (AB, A B)}\pause
  \invisible<1-4>{ \item[-] Bell$(3)=5$ (ABC, AB C, A BC, AC B, A B
   C)} \pause
   \invisible<1-5>{ \item[-] Bell$(5)=52$}\pause
   \invisible<1-6>{ \item[-] Bell(100)}\pause \invisible<1-7>{$\approx 4.75 \times
   10^{115}$ partitions} \pause
   \invisible<1-8>{\item[-] \alert{Big Number}:}\pause  \\
   \invisible<1-9>{7 Billion RAs} \pause  \\
   \invisible<1-10>{ Impossibly Fast (enumerate one clustering every millisecond)} \pause  \\
   \invisible<1-11>{ Working around the clock (24/7/365)}\pause  \\
        \invisible<1-12>{$\approx 1.54\times 10^{84} \times $} \invisible<1-13>{($14,000,000,000$)} \invisible<1-14>{years}
        \pause \pause\pause 
    \end{itemize}

\invisible<1-15>{\alert{Automated methods can help with even small problems}}

\end{frame}

\begin{frame}
\frametitle{What We'll Do:}

\alert{Statistical} and \alert{Computational} tools for working with texts

\end{frame}

\begin{frame}
\frametitle{Prerequisites}

Statistics:\pause 
\begin{itemize}
\invisible<1>{\item[-] Probability Theory/Univariate Inference (Old 350a)} \pause 
\invisible<1-2>{\item[-] Linear Regression (Old 350b)} \pause 
\invisible<1-3>{\item[-] (Ideally) Model Based Inference (Old 350c) 
\item[-] Willingness to learn new statistical models(!!)} \pause 
\end{itemize}

\invisible<1-4>{Computational:}\pause

\begin{itemize}
\invisible<1-5>{\item[-] Familiarity with {\tt R} programming language} \pause 
\invisible<1-6>{\item[-] Experience with:} \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Programming functions} \pause 
\invisible<1-8>{\item[-] Writing for loops} \pause 
\invisible<1-9>{\item[-] Using standard {\tt R} packages} \pause 
\invisible<1-10>{\item[-] Creating plots } \pause 
\end{itemize}
\invisible<1-11>{\item[-] Willingness to learn {\tt Python}} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Course Staff}

\begin{itemize}
\item[] \textbf{Me:} Justin Grimmer
\item[] \textbf{Office:} Encina West 414 (last door on left)
\item[] \textbf{Office Hours:} I'm usually in during business hours. Set up an appointment if you must meet with me
\item[] \textbf{Contact:} Gchat: justin.grimmer@gmail.com; Cell phone (617) 710-6803
\end{itemize}

\pause

\invisible<1>{\alert{Programming TA}

\begin{itemize}
\item[] \textbf{Python/R/Programming}: Frances Zlotnick
\item[] \textbf{Office/Programming Section}: Encina Hall West, Room 417
\item[] \textbf{Office Hours}: 230-430 and by appointment
\item[] \textbf{Contact}: Zlotnick@stanford.edu
\end{itemize}
}

\end{frame}

\begin{frame}
\frametitle{Evaluation}

\alert{Homework}:

\begin{itemize}
\item[-] Weekly homework assignments
\item[-] Computational Component
\begin{itemize}
\item[-] Preprocessing texts
\item[-] Moving from texts$\leadsto$ data
\end{itemize}
\item[-] Statistical component
\begin{itemize}
\item[-] Applying algorithms, statistics to analyze texts
\end{itemize}
\end{itemize}

Our workspace
\begin{itemize}
\item[1)] {\tt RStudio} $\leadsto$ lowers startup costs of ${\tt R}$ 
\item[2)] {\tt R Markdown} $\leadsto$ integrates write up and code
\item[3)] {\tt Enthought Python Distribution} (academic license) $\leadsto$ python distribution that ships with most packages
\end{itemize}

Writeup can also occur in \LaTeX\

\end{frame}

\begin{frame}
\frametitle{Evaluation}

\alert{Homework}:

\begin{itemize}
\item[1)] Will be distributed on Tuesday
\item[2)] Due on Tuesday, 5pm 
\item[3)] {\tt Email:} Frannie and me
\end{itemize}

\alert{Collaborate}!
\begin{itemize}
\item[1)] Work together in groups
\item[2)] Individual write ups
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Evaluation}

\alert{Final Project}: \pause

\begin{itemize}
\invisible<1>{\item[1)] An original research paper} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Part of a dissertation
\item[-] Field paper
\item[-] Paper for publication} \pause 
\end{itemize}
\invisible<1-3>{\item[2)] Contributing to ongoing research project} \pause 
\begin{itemize}
\invisible<1-4>{\item[1)] Michael Crespin (U of Oklahoma, Congressional Scholar): Categorizing floor speeches$\leadsto$ citations} \pause 
\invisible<1-5>{\item[2)] Alison McQueen (Stanford): Characterizing Hobbes' context$\leadsto$ political theory} \pause 
\invisible<1-6>{\item[3)] Robert Gulotty (Stanford$\leadsto$ U of Chicago) and Judith Goldstein (Stanford) Examine trade speeches in the 19th century Congress} \pause 
\end{itemize}
\end{itemize}
\invisible<1-7>{\alert{Talk to me about your ideas!}}

\end{frame}

\begin{frame}
\frametitle{Evaluation}

\alert{Final Project:} \pause

\begin{itemize}
\invisible<1>{\item[1)] Poster Session} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Opportunity to receive feedback on your projects} \pause 
\end{itemize}
\invisible<1-3>{\item[2)] Final paper} \pause 
\begin{itemize}
\invisible<1-4>{\item[-] Research length (25-30 pages)} \pause 
\invisible<1-5>{\item[-] Format appropriate for your field} \pause 
\end{itemize}
\invisible<1-6>{\item[-] Collaborative$\leadsto$ work in two-person teams} \pause 
\invisible<1-7>{\item[-] We will not adjudicate disputes (frankly, unimportant)} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Evaluation}

\alert{Participation:} \\ \pause

\begin{itemize}
\invisible<1>{\item[-] Attend class} \pause 
\invisible<1-2>{\item[-] Ask questions (!!!)} \pause 
\invisible<1-3>{\item[-] Enroll in Piazza course site} \pause 
\begin{itemize}
\invisible<1-4>{\item[-] piazza.com/stanford/fall2014/polsci452} \pause 
\invisible<1-5>{\item[-] I'll post lecture slides there and readings (ensures auditors/guests have access)} \pause 
\invisible<1-6>{\item[-] Post Questions/Answer Questions/Course Announcements} 
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Plan for the Course}

\alert{Computational} and \alert{Statistical} tools \pause

\begin{itemize}
\invisible<1>{\item[-] Acquiring and Preprocessing Text data} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Basics of webscraping
\item[-] Regular expressions
\item[-] Text $\leadsto$ Document Term Matrices} \pause 
\end{itemize}
\invisible<1-3>{\item[-] Dictionary Methods} \pause 
\begin{itemize}
\invisible<1-4>{\item[-] \alert{Assume}$\leadsto$ known categories
\item[-] \alert{Assume}$\leadsto$ known how words relate to groups
\item[-] Measure prevalence of categories} \pause 
\end{itemize}
\invisible<1-5>{\item[-] Discriminating Words} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] \alert{Assume}$\leadsto$ known categories
\item[-] Statistical methods/algorithms to measure word discrimination} 
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Plan for the Course}
\begin{itemize}
\item[-] Geometry of Texts \pause 
\begin{itemize}
\invisible<1>{\item[-] \alert{Assume}$\leadsto$ relationship between texts
\item[-] Statistical methods/algorithms to \alert{project} (scale) texts in lower dimension} \pause 
\end{itemize}
\invisible<1-2>{\item[-] Clustering Methods (Unknown Groups, Unknown relationship of document characteristics to those groups)} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Fully Automated Clustering Methods} \pause 
\begin{itemize}
\invisible<1-4>{\item[-] \alert{Assume}$\leadsto$ Known distance
\item[-] \alert{Assume}$\leadsto$ Known objective
\item[-] \alert{Assume}$\leadsto$ Known method for optimization
\item[-] Statistical model to partition documents} \pause 
\end{itemize}
\invisible<1-5>{\item[-] Computer Assisted Clustering} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] \alert{Assume}$\leadsto$ Method for organizing clusters
\item[-] Method for generating, organizing partitions for discovery} 
\end{itemize}
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Plan for the Course}

\begin{itemize}
\item[-] ``Vanilla" Latent Dirichlet Allocation (Topic Models) \pause 
\begin{itemize}
\invisible<1>{\item[-] Unknown categories
\item[-] \alert{Assume}$\leadsto$ documents are \alert{mixture} of topics
\item[-] Statistical method for measuring topics and document attention to topics} \pause 
\end{itemize}
\invisible<1-2>{\item[-] Structural Topic Models} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] \alert{Assume}$\leadsto$ condition on characteristics 
\item[-] Measure topics, prevalence of topics across characteristics, distinctiveness of language} \pause 
\end{itemize}
\invisible<1-4>{\item[-] Supervised Methods} \pause 
\begin{itemize}
\invisible<1-5>{\item[-] \alert{Assume}$\leadsto$ Known categories (training documents)
\item[-] Statistical model: learn relationship between labels, words categorize remaining documents
\item[-] \alert{Ensembles of methods}} \pause 
\end{itemize}
\invisible<1-6>{\item[-] Ideological Scaling}\pause 
\begin{itemize}
\invisible<1-7>{\item[-] Application of methods, measuring political positions
\item[-] Supervised$\leadsto$ Wordscores
\item[-] Unsupervised $\leadsto$ Item Response Theory (IRT) Models} 
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Four Principles of Automated Text Analysis}

Principle 1: All Quantitative Models of Language are Wrong---But Some are Useful \pause

\begin{itemize}
\invisible<1>{\item[-] Data generation process for text$\leadsto$ unknown} \pause 
\invisible<1-2>{\item[-] Complexity of language:} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Time flies like an arrow}\pause\invisible<1-4>{, fruit flies like a banana} \pause 
\invisible<1-5>{\item[-] Make peace, not war}\pause\invisible<1-6>{ , Make war not peace} \pause
\invisible<1-7>{\item[-] ``Years from now, you'll look back and you'll say that this was the moment, this was the place where America remembered what it means to hope. " } \pause 
\end{itemize}
\invisible<1-8>{\item[-] Models \alert{necessarily} fail to capture language$\leadsto$ useful for specific tasks}\pause
\invisible<1-9>{\item[-] \alert{Validation}$\leadsto$ demonstrate methods perform task } 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Four Principles of Automated Text Analysis}

Principle 2: Quantitative Methods Augment Humans, Not Replace Them \pause

\begin{itemize}
\invisible<1>{\item[-] \alert{Computer-Assisted} Reading} \pause 
\invisible<1-2>{\item[-] Quantitative methods organize, direct, and suggest} \pause 
\invisible<1-3>{\item[-] Humans: read and interpret } 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Four Principles of Automated Text Analysis}

Principle 3: There is no Globally Best Method for Automated Text Analysis \pause

\begin{itemize}
\invisible<1>{\item[-] Supervised methods$\leadsto$ known categories} \pause 
\invisible<1-2>{\item[-] Unsupervised methods$\leadsto$ discover categories} \pause 
\invisible<1-3>{\item[-] Debate$\leadsto$ acknowledge differences, resolved} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Four Principles of Automated Text Analysis}

Principle 4: Validate, Validate, Validate \pause

\begin{itemize}
\invisible<1>{\item[-] Quantitative methods$\leadsto$ variable performance across tasks} \pause 
\invisible<1-2>{\item[-] \alert{Few theorems to guarantee performance}} \pause 
\invisible<1-3>{\item[-] Apply methods $\leadsto$ validate} \pause 
\invisible<1-4>{\item[-] \alert{Avoid}: blind application of methods} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Going Forward}

\begin{itemize}
\item[1)] Assignment distributed tonight
\item[2)] Install {\tt R} and {\tt Python}
\item[3)] Thursday: The Statistical/Computational Background for Text as Data!
\end{itemize}

\end{frame}

\end{document}

\begin{frame}
\frametitle{Conclusion}

Today: Introduction and where to get text\\
Next week: how to represent text quantitatively

\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/tc10.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\newcommand{\argmin}{\arg\!\min}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
 \numberwithin{equation}{section}

%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{October 23rd, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Interpreting Clusterings + Computer Assisted Clusterings}

\begin{itemize}
\begin{footnotesize}
\item[1)] Task: \pause 
\begin{itemize}
\invisible<1>{\item[-] Select a clustering model, Characterize Model Fit}  \pause 
\invisible<1-2>{\item[-] Choose the number of components for our mixture} \pause 
\end{itemize}
\invisible<1-3>{\item[2)] Objective function:} \pause 
\begin{itemize}
\invisible<1-4>{\item[-] Mathematical objective function} \pause 
\begin{eqnarray}
\invisible<1-5>{\text{Math Obj} & = & f(\boldsymbol{X}, \boldsymbol{T}, \boldsymbol{\Theta}) \nonumber } \pause 
\end{eqnarray}
\invisible<1-6>{\item[-] Substantively $\Theta$:} \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Cohesive: words that are prominent in $\boldsymbol{\theta}_{k}$ actually occur together} \pause 
\invisible<1-8>{\item[-] Exclusive: words that are featured in $\boldsymbol{\theta}_{k}$ only occur in $k$} \pause 
\invisible<1-9>{\item[-] The mathematical ``groupings" align with meaningful groupings} \pause 
\end{itemize}
\end{itemize}
\invisible<1-10>{\item[3)] Optimization} \pause 
\begin{itemize}
\invisible<1-11>{\item[-] Select the \alert{best} model.} \pause 
\begin{itemize}
\invisible<1-12>{\item[-] Run several candidate models$\leadsto$ optimize $\boldsymbol{\Theta}$ and $\boldsymbol{T}$ } \pause 
\invisible<1-13>{\item[-] Stats + Substance to select model + $K$ } \pause 
\end{itemize}
\end{itemize}
\invisible<1-14>{\item[4)] Validation} \pause 
\begin{itemize}
\invisible<1-15>{\item[-] Is our statistic capturing what we want from the clustering?} \pause 
\invisible<1-16>{\item[-] Are there features we're missing} \pause 
\invisible<1-17>{\item[-] \alert{Very Open Research Question}} 
\end{itemize}
\end{footnotesize}

\end{itemize}

\end{frame}

\begin{frame}
\frametitle{A Motivating Clustering Model$\leadsto$ Mixture of von Mises Fisher Distributions}

$J$ element long unit-length vector\pause 
\begin{eqnarray}
\invisible<1>{\boldsymbol{x}_{i}^{*}  & = &  \frac{\boldsymbol{x}_{i}}{\sqrt{\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i}} } } \nonumber 
\end{eqnarray}
 \pause

\invisible<1-2>{Mixture of von Mises-Fisher (vMF) distributions:}\pause

\begin{eqnarray}
\invisible<1-3>{\boldsymbol{\tau}_{i} & \sim & \overbrace{\text{Multinomial}(1, \boldsymbol{\pi})}^{\text{Mixture component}} \nonumber \\} \pause 
\invisible<1-4>{\boldsymbol{x}_{i}^{*} | \tau_{ik} = 1, \boldsymbol{\mu}_{k} & \sim & \underbrace{\text{vMF}(\kappa, \boldsymbol{\mu}_{k})}_{\text{Language model}} \nonumber } \pause 
\end{eqnarray}

\invisible<1-5>{Provides:} \pause 
\begin{itemize}
\invisible<1-6>{\item $\boldsymbol{\tau}_{i}\leadsto$ Each document's cluster assignment} \pause 
\invisible<1-7>{\item $\boldsymbol{\pi} = (\pi_{1}, \pi_{2}, \hdots, \pi_{K})\leadsto$ Proportion of documents in each component } \pause 
\invisible<1-8>{\item $\boldsymbol{\mu}_{k}\leadsto$ Exemplar document for cluster $k$} \pause 
\end{itemize}

\invisible<1-9>{EM algorithm in slides appendix}

\end{frame}

\begin{frame}
\frametitle{Measuring Cluster Performance: Out of Sample Prediction}

How well does our model perform?\pause\invisible<1>{$\leadsto$ predict new documents?} \pause   \\
\invisible<1-2>{Problem}\pause\invisible<1-3>{$\leadsto$ in sample evaluation leads to overfit. } \pause \\
\invisible<1-4>{Solution$\leadsto$ evaluate performance on \alert{held out} data} \pause \\

\invisible<1-5>{For held out document $\boldsymbol{x}^{*}_{\text{out}}$ } \pause

\begin{eqnarray}
\invisible<1-6>{\log p(\boldsymbol{x}^{*}_{\text{out}}| \boldsymbol{\mu},\boldsymbol{\pi}, \boldsymbol{X} ) & = & \log \sum_{k=1}^{K} p(\boldsymbol{x}^{*}_{\text{out}}, \tau_{ik} | \boldsymbol{\mu}_{k} , \boldsymbol{\pi}, \boldsymbol{X}) \nonumber \\ } \pause 
\invisible<1-7>{& = & \log \sum_{k=1}^{K} \left[ \pi_{k} \exp(\kappa \boldsymbol{\mu}_{k}^{'} \boldsymbol{x}^{*}_{\text{out}})\right] \nonumber \\ } \pause 
\invisible<1-8>{\text{Perplexity}_{\text{word}} & = & \exp\left( - \log p(\boldsymbol{x}^{*}_{\text{out}}| \boldsymbol{\mu},\boldsymbol{\pi} )   \right) \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}

\scalebox{0.5}{\includegraphics{Perplex1.pdf}}

\end{frame}

\begin{frame}
\frametitle{What's Prediction Got to Do With It?}

\begin{itemize}
\item[-] Prediction$\leadsto$ One Task \pause \\
\invisible<1>{\item[-] Do we care about it?}\pause\invisible<1-2>{$\leadsto$ Social science application where we're predicting new texts?} \pause\\
\invisible<1-3>{\item[-] Does it correspond to how we might use the model?} \pause 
\end{itemize}

\invisible<1-4>{Chang et al 2009 (``Reading the Tea Leaves") :} \pause 
\begin{itemize}
\invisible<1-5>{\item[-] Compare perplexity with \alert{human} based evaluations} \pause 
\invisible<1-6>{\item[-] \alert{NEGATIVE} relationship between perplexity and human based evaluations} \pause 
\end{itemize}

\invisible<1-7>{Different strategy$\leadsto$ measure quality in \alert{topics} and \alert{clusters} } \pause \\
\begin{itemize}
\invisible<1-8>{\item[-] Statistics: measure \alert{cohesiveness} and \alert{exclusivity}} (Roberts, et al AJPS Forthcoming) \pause 
\invisible<1-9>{\item[-] Experiments: measure \alert{topic} and \alert{cluster} quality} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Measuring \alert{Cohesiveness} and Exclusivity}
\pause 
\begin{itemize}
\invisible<1>{\item[-] Consider the output of a 3-component mixture of model (say, Multinomials or von Mises-Fisher models)\\} \pause 
\invisible<1-2>{\item[-] We might select 5 \alert{top} words for each topic} \pause 
\end{itemize}
\begin{tabular}{l|lllll}
\hline \hline
\invisible<1-3>{Topic 1 & bill & congressman & earmarks & following & house} \pause \\
\invisible<1-4>{Topic 2 & immigration & reform & security & border & worker}\pause \\
\invisible<1-5>{Topic 3 & earmark & egregious & pork & fiscal & today} \pause  \\
\hline\hline
\end{tabular}
\begin{itemize}
\invisible<1-6>{\item[-] An ideal topic?$\leadsto$ will see these words co-occur in documents} \pause
\invisible<1-7>{\item[-] Define $\boldsymbol{v}_{k} = (v_{1k}, v_{2k}, \hdots, v_{Lk})$ be the top words for a topic} \pause
\invisible<1-8>{\item[-] For example $\boldsymbol{v}_{3}$ = (earmark , egregious , pork , fiscal , today )} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Measuring \alert{Cohesiveness} and Exclusivity}

Define the function $D$ as a function that counts the number of times its argument occurs: \pause 
\begin{eqnarray}
\invisible<1>{D(\text{earmark}, \text{egregious} ) & = & \text{ No. times earmark and egregious co-occur} \nonumber \\} \pause 
\invisible<1-2>{D(\text{egregious}) & = & \text{ Number of times Egregious occurs} \nonumber } \pause 
\end{eqnarray}

\invisible<1-3>{Define cohesiveness for topic $k$ as } \pause 
\begin{eqnarray}
\invisible<1-4>{\text{Cohesive}_{k}  & = & \sum_{l=2}^{L} \sum_{m=1}^{l-1} \log \left( \frac{D(v_{lk}, v_{mk}) + 1}{ D(v_{mk})  }  \right)\nonumber } \pause 
\end{eqnarray}

\invisible<1-5>{Define overall cohesiveness as:} \pause 
\begin{eqnarray}
\invisible<1-6>{\text{Cohesive}  & = & (\sum_{k=1}^{K} \text{Cohesive}_{k})/K    \nonumber \\} \pause 
\invisible<1-7>{&= & \left( \sum_{k=1}^{K} \sum_{l=2}^{L} \sum_{m=1}^{l-1} \log \left( \frac{D(v_{lk}, v_{mk}) + 1}{ D(v_{mk})  }  \right)\right)/K\nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Measuring Cohesiveness and \alert{Exclusivity}}

We also want topics that are exclusive\pause \invisible<1>{$\leadsto$ few replicates of each topic} \pause

\begin{eqnarray}
\invisible<1-2>{\text{Exclusivity}(k, v) & = &  \frac{\mu_{k, v}}{\sum_{l=1}^{K} \mu_{l,v}} \nonumber } \pause 
\end{eqnarray}

\invisible<1-3>{Suppose again we pick $L$ top words.  Measure Exclusivity for a topic as for a topic as:} \pause
\begin{eqnarray}
\invisible<1-4>{\text{Exclusivity}_{k} & = & \sum_{j: v_{j} \in \boldsymbol{v}_{k}} \frac{\mu_{k, j}}{\sum_{l=1}^{K} \mu_{l,j}} \nonumber \\} \pause 
\invisible<1-5>{\text{Exclusivity} & = & \left(\sum_{k=1}^{K} \text{Exclusivity}_{k}\right)/K \nonumber \\} \pause 
\invisible<1-6>{& = & \left(\sum_{k=1}^{K} \sum_{j: v_{j} \in \boldsymbol{v}_{k}} \frac{\mu_{k, j}}{\sum_{l=1}^{K} \mu_{l,j}}\right)/K \nonumber} 
\end{eqnarray}

\end{frame}

\begin{frame}

\only<1>{\scalebox{0.5}{\includegraphics{Cohesive1.pdf}}}
\only<2>{\scalebox{0.5}{\includegraphics{Exclusive1.pdf}}}
\only<3>{\scalebox{0.5}{\includegraphics{Frontier1.pdf}}}

\end{frame}

\begin{frame}
\frametitle{Experimental Approaches}

Mathematical approaches\pause \invisible<1>{$\leadsto$ suppose we can capture quality with numbers assumes we're \alert{in the model}$\leadsto$ including text representation } \pause \\
\invisible<1-2>{\alert{Humans}$\leadsto$ read texts} \pause \\
\invisible<1-3>{\alert{Humans}$\leadsto$ use cluster output} \pause \\

\invisible<1-4>{Do \alert{humans} think the model is performing well?\\} \pause

\begin{itemize}
\invisible<1-5>{\item[1)] Topic Quality} \pause
\invisible<1-6>{\item[2)] Cluster Quality} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Experimental Approaches}

\begin{itemize}
\item[1)] Take $M$ top words for a topic
\item[2)] Randomly select a top word from another topic
\begin{itemize}
\item[2a)] Sample the topic number from $l$ from $K-1$ (uniform probability)
\item[2b)] Sample word $j$ from the $M$ top words in topic $l$
\item[2c)] Permute the words and randomly insert the \alert{intruder}:
\item[-] List: 
\begin{eqnarray}
\text{test} &  =  & (v_{k, 3}, v_{k, 1}, \alert{v_{l, j}}, v_{k, 2}, v_{k, 4}, v_{k,5}) \nonumber 
\end{eqnarray}
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Example Experiment: Word Intrusion (Weiss and Grimmer, In Progress)}

\only<1-2>{{\tt bowl, \alert<2>{flooding}, olympic, olympics, nfl, coach}}

\only<3-4>{{\tt stocks, investors, fed, \alert<4>{guns},  trading, earning}}

\invisible<1-4>{Higher rate of intruder identification $\leadsto$ more exclusive/cohesive topics}  \\

\vspace{0.25in}

\invisible<1-5>{Deploy on Mechanical Turk}

\pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Cluster Quality (Grimmer and King 2011) }

Assessing Cluster Quality with experiments
\pause
\begin{itemize}
\invisible<1>{\item[-] Goal: group together similar documents} \pause 
\invisible<1-2>{\item[-] Who knows if similarity measure corresponds with semantic similarity} 
\end{itemize} \pause 
\invisible<1-3>{
$\leadsto$ Inject human judgement on pairs of documents} \\
\vspace{0.125in}

\pause \invisible<1-4>{Design to assess cluster quality} \pause
\begin{itemize}
\invisible<1-5>{\item[-] Estimate clusterings }\pause
 \invisible<1-6>{\item[-] Sample pairs of documents (hint: you only need to compare discrepant pairs)} \pause
\invisible<1-7>{\item[-] Scale: (1) unrelated, (2) loosely related,
(3) closely related (richer instructions, based on thing you want to cluster on) } \pause \invisible<1-8>{\item[-] Cluster Quality
= mean(within cluster) - mean(between clusters)}\pause 
\invisible<1-9>{\item[-] Select clustering with highest cluster quality } \pause 
\invisible<1-10>{\item[-] Can be used to compare any clusterings, regardless of source} 
%\invisible<1-9>{\item[-] Clust. Qual(Our Method) - Clust. Qual
%(Comparison Method)} \pause
%\invisible<1-9>{\item[-] \alert{Bias results against ourselves by
%not letting evaluators choose clustering}}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{How do we Choose $K$?}

Generate many candidate models
\begin{itemize}
\item[1)] Assess Cohesiveness/Exclusivity, select models on frontier
\item[2)] Use experiments 
\item[3)] \alert{Read}
\item[4)] Final decision$\leadsto$ combination
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Computer Assisted Clustering Methods}
There are a lot of different clustering models (and many variations within each): \\

k-means \pause \invisible<1>{, Mixture of multinomials} \pause \invisible<1-2>{, k-medoids} \pause \invisible<1-3>{, affinity propagation} \pause \invisible<1-4>{, agglomerative Hierarchical} \pause 
\invisible<1-5>{ fuzzy k-means, trimmed k-means, k-Harmonic means, fuzzy k-medoids, fuzzy k modes, maximum entropy clustering, model based hierarchical (agglomerative), proximus, ROCK, divisive hierarchical, DISMEA, Fuzzy, QTClust, self-organizing map, self-organizing tree, unnormalized spectral, MS spectral, NJW Spectral, SM Spectral, Dirichlet Process Multinomial, Dirichlet Process Normal, Dirichlet Process von-mises Fisher, Mixture of von mises-Fisher (EM), Mixture of von Mises Fisher (VA), Mixture of normals, co-clustering mutual information, co-clustering SVD, LLAhclust, CLUES, bclust, c-shell, qtClustering, LDA, Express Agenda Model, Hierarchical Dirichlet process prior, multinomial, uniform process mulitinomial, Chinese Restaurant Distance Dirichlet process multinomial, Pitmann-Yor Process multinomial, LSA, ...}

\end{frame}

\begin{frame}
  \frametitle{The Problem with Fully Automated Clustering (Grimmer and King 2011) }
  \begin{itemize}
  \item[-] Large quantitative literature on \alert{cluster analysis}
  \pause
  \invisible<1>{\item[-] The Goal --- an optimal application-independent cluster
    analysis method ---}\pause \invisible<1-2>{ is mathematically impossible:} \pause
 \begin{itemize}
     \invisible<1-3>{ \item[-] \alert{No free lunch theorem}: every possible clustering
      method performs equally well on average over all possible
      substantive applications} \pause
 \end{itemize}
\invisible<1-4>{\item[-] Existing methods:} \pause
  \begin{itemize}
\invisible<1-5>{\item[-] \alert{Many choices}: model-based,
subspace, spectral,
      grid-based, graph- based, fuzzy $k$-modes, affinity propagation,
      self-organizing maps,\alert{$\dots$}} \pause
\invisible<1-6>{\item[-] \alert{Well-defined} statistical, data
analytic, or machine
      learning foundations} \pause
\invisible<1-7>{\item[-] How to add substantive knowledge: With few
        exceptions, \alert{unclear}} \pause
\invisible<1-8>{\item[-] The literature: \alert{little guidance on
when methods apply}} \pause
  \invisible<1-9>{\item[-] \alert{Deriving such guidance: difficult or
  impossible}} \pause
   \end{itemize}
  \end{itemize}
  \large
\invisible<1-10>{ \alert{Deep problem in cluster analysis
literature: full automation requires more information}}
%\invisible<1-8>{\item[-] (Perhaps true by definition in unsupervised
%learning: If we knew the DGP, we wouldn't be at the discovery
%stage.)
\normalsize

\end{frame}

\begin{frame}
\frametitle{Fully Automated $\rightarrow$ Computer Assisted (Grimmer and King 2011) }

\pause 
\begin{itemize}
\invisible<1>{\item[-] \alert{Fully Automated Clustering} may succeed, fails in general.  Too hard to know when to apply models} \pause 
\invisible<1-2>{\item[-] An alternative: \alert{Computer Assisted Clustering} } \pause
\begin{itemize}
\invisible<1-3>{\item[-] Easy (if you don't think about it): list all clustering, choose \alert{best}} \pause
\invisible<1-4>{\item[-] \alert{Impossible in Practice} } \pause
\invisible<1-5>{\item[-] Solution: \alert{Organized list} } \pause
\invisible<1-6>{\item[-] \alert{Insight}: Many clusterings are perceptually identical} \pause
\invisible<1-7>{\item[-] Consider two clusterings of 10,000 documents, we move one document from 5 to 6.  } \pause
\end{itemize}
\invisible<1-8>{\item[-] \alert{How to organize clusterings so humans can undestand?}} \pause
\invisible<1-9>{\item[-] Our answer: a geography of clusterings} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{A New Strategy (Grimmer and King 2011) } 
  \begin{enumerate}
  \item[1)] \alert{Code text as numbers} (in one \emph{or more} of several
   ways)  \pause
 \invisible<1>{ \item[2)] \alert{Apply many different clustering methods} to the data ---
    each representing different (unstated) substantive assumptions} \pause
   \begin{itemize}
    \invisible<1-2>{\item[-] Introduce sampling methods to extend search beyond existing methods} \pause
    %\invisible<1-3>{\item[-] Take a uniform draw from the Bell space (related to Pitman-Yor Process)}
 %  \invisible<1-2>{ \item[-] Adaptive search over tuning parameters for
 %  methods} \pause
 %  \invisible<1-3>{ \item[-] Efficient fully Bayesian inference via Variational Approximations (\alert{parametric} and
 %   \alert{nonparametric} Bayesian models)} \pause
    \end{itemize}
  \invisible<1-3>{\item[3)] Develop a metric
    between clusterings} \pause
  \invisible<1-4>{\item[4)] Create a \alert{metric space of clusterings}, and a 2-D
    projection} \pause
  \invisible<1-5>{\item[5)] Introduce the \alert{local cluster ensemble} to summarize any
    point, including points with no existing clustering} \pause
    \begin{itemize}
   \invisible<1-6>{ \item[-] New Clustering: weighted average of clusterings from methods }
   \end{itemize}\pause
  \invisible<1-7>{\item[6)] Use \alert{animated visualization}: use the local
    cluster ensemble to explore the space of clusterings (smoothly
    morphing from one into others)} \pause
\invisible<1-8>{\item[7)] $\alert{\leadsto}$ Millions of clusterings easily comprehended}     \pause 
\invisible<1-9>{\item[8)] (Or, our new strategy: represent entire Bell space directly; no need to examine document contents ) }     
 \end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Crosas, Grimmer, King, and Stewart$\leadsto$ Consilience}

A brief live demonstration

\end{frame}

\begin{frame}
\frametitle{Example Discovery:  What Do Members of Congress Do?}
\begin{itemize}
\item[-] Paper (Grimmer and King 2011): introduce new evaluation methods (like Cluster Quality) \pause
\end{itemize}

\begin{itemize}
\invisible<1>{\item[-] David Mayhew's (1974) famous typology} \pause
\begin{enumerate}
\invisible<1-2>{\item[-] Advertising}\pause \invisible<1-3>{\item[-]
Credit Claiming} \pause
 \invisible<1-4>{\item[-] Position Taking}
\end{enumerate}
\pause \invisible<1-5>{\item[-] Data: 200 press releases from Frank
Lautenberg's office (D-NJ) } \pause \invisible<1-6>{\item[-] Apply
our method (relying on many clustering algorithms)}% \pause \invisible<1-7>{\item[-] Result}
% \invisible<1-8>{we find one
%more: \alert{Partisan Taunting}}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Example Discovery\invisible<1-16>{: Partisan Taunting}}
\begin{columns}[]
\column{0.55\textwidth} \vspace{0.2in}
\begin{flushleft}
\only<1>{\scalebox{0.3}{\includegraphics{TauntingSpace.pdf}}}
\only<2>{\scalebox{0.3}{\includegraphics{TauntingSpaceAffProp.pdf}}}
\only<3>{\scalebox{0.3}{\includegraphics{TauntingSpaceAffPropMixVMF.pdf}}}
\only<4>{\scalebox{0.3}{\includegraphics{TauntingSpace.pdf}}}
\only<5>{\scalebox{0.3}{\includegraphics{TauntingSpaceLCE1.pdf}}}
\only<6>{\scalebox{0.3}{\includegraphics{TauntingSpaceLCE.pdf}}}
\only<7>{\scalebox{0.3}{\includegraphics{TauntingSpace.pdf}}}
\only<8>{\scalebox{0.3}{\includegraphics{TauntingSpaceHull.pdf}}}
\only<9-12>{\scalebox{0.3}{\includegraphics{TauntingSpacePoint.pdf}}}
\only<13>{\scalebox{0.3}{\includegraphics{ClusterSpace1.pdf}}}
\only<14>{\scalebox{0.3}{\includegraphics{ClusterCredit.pdf}}}
\only<15>{\scalebox{0.3}{\includegraphics{ClusterCredit2.pdf}}}
\only<16>{\scalebox{0.3}{\includegraphics{Clusterad.pdf}}}
\only<17>{\scalebox{0.3}{\includegraphics{Clustertaunt.pdf}}}
\end{flushleft}

%\only<1-3>{\scalebox{0.4}{\includegraphics{BlackSpace.pdf}}}
\column{0.45\textwidth}\only<9-12>{ \invisible<1-3>{Mixture:}
\footnotesize
\begin{enumerate}
\invisible<1-9>{\item[0.39] Hclust-Canberra-McQuitty}
\invisible<1-10>{\item[0.30]  Spectral clustering \\ Random Walk
\\(Metrics 1-6)} \invisible<1-9>{\item[0.13]
Hclust-Correlation-Ward} \invisible<1-9>{\item[0.09]
Hclust-Pearson-Ward} \invisible<1-11>{\item[0.05] Kmediods-Cosine}
\invisible<1-10>{\item[0.04] Spectral clustering\\ Symmetric \\
(Metrics 1-6)}
\end{enumerate}
}
\begin{flushleft}
\only<2-3>{Each point is a \alert{clustering}\\
Affinity Propagation-Cosine  (Dueck and Frey 2007)\\
\invisible<1-2>{\alert{Close to:}\\
 Mixture of von Mises-Fisher distributions (Banerjee et. al. 2005)} \\
\invisible<1-2>{ $\Rightarrow$ Similar clustering of documents}}

\only<4-6>{Space between methods:\\ \invisible<4-5>{\alert{local
cluster ensemble}} }

\only<8>{Found a \alert{region} with clusterings that all reveal the
same important insight}

\only<14>{\alert{Credit Claiming, Pork}:\\}
 \only<14>{``Sens. Frank R. Lautenberg
(D-NJ) and Robert Menendez (D-NJ) announced that the U.S. Department
of Commerce has awarded a \$100,000 grant to the South Jersey
Economic Development District"} \only<15>{\alert{Credit Claiming,
Legislation}:\\}
 \only<15>{``As the Senate begins its recess, Senator Frank Lautenberg today pointed to a string of victories
in Congress on his legislative agenda during this work period"}
\only<16>{\alert{Advertising}:\\}
 \only<16>{``Senate Adopts Lautenberg/Menendez Resolution Honoring Spelling Bee Champion from
New Jersey"} \only<17>{\alert{Partisan Taunting}:\\}
\only<17>{``Republicans Selling Out Nation on Chemical Plant
Security" } %\only<21>{``Senator Lautenberg's amendment would change
%the name of ...the Republican bill...to `More Tax Breaks for the
%Rich and More Debt for Our Grandchildren Deficit Expansion
%Reconciliation Act of 2006' "} %\only<22-23>{ \\
%\invisible<1-22>{\Large \alert{Taunting ruins deliberation}}}
\end{flushleft}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{In Sample Illustration of Partisan Taunting}
\framesubtitle{Important Concept Overlooked in Mayhew's (1974)
typology} \invisible<1-3>{\alert{Definition}: Explicit, public, and
negative attacks on another political party or its members}\\
\invisible<1-4>{\alert{Consequences for representation}: Deliberative, Polarization, Policy} \normalsize
\begin{columns}
\column{0.25\textwidth}
\begin{flushleft}
\scalebox{0.35}{\includegraphics{LautChicken.jpg}}

Sen. Lautenberg on Senate Floor 4/29/04 \\
\end{flushleft}
\column{0.1\textwidth}

 \column{0.55\textwidth}
\begin{itemize}
\item[-] ``Senator Lautenberg Blasts Republicans as
      `Chicken Hawks' '' [Government~Oversight] \pause
\invisible<1>{\item[-] ``The scopes trial took place in 1925. Sadly,
President Bush's veto today shows that we haven't progressed much
since then''
      [Healthcare]}\pause
%\invisible<1-2>{\item[-] `` Senator Lautenberg Expressed Shock Over
%President Bush's Mock Search for Weapons of Mass Destruction" [War
%on Terrorism]} \pause
\invisible<1-2>{\item[-] ``Every day the House Republicans dragged
this out was a day that made our communities less safe."[Homeland
Security]} \pause \pause
\end{itemize}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{Out of Sample Confirmation of Partisan Taunting }
\begin{itemize}
\item[-] Discovered using 200 press releases; 1 senator. \pause
\invisible<1>{\item[-] Demonstrate prevalence using senators' press releases.} \pause \invisible<1-2>{\item[-] Apply supervised
learning method: measure \alert{proportion of press releases} a
senator taunts other party}
\end{itemize}
\invisible<1-3>{\begin{figure}[hbt!]
\begin{center}
\scalebox{0.4}{\includegraphics{PartisanTauntHistBlack.pdf}}
\end{center}
\end{figure}}
\end{frame}

\begin{frame}
\frametitle{Out of Sample Confirmation of Partisan Taunting}
\begin{itemize}
\item[-] Discovered using 200 press releases; 1 senator.
\item[-] Demonstrate prevalence using senators' press releases. 
\item[-] Apply supervised learning method: measure \alert{proportion of press releases} a senator
taunts other party
\end{itemize}
\only<1>{
\begin{figure}[hbt!]
\begin{center}
\scalebox{0.4}{\includegraphics{PartisanTauntHistBlack.pdf}}
\end{center}
\end{figure}} \pause
\only<2>{
\begin{figure}[hbt!]
\begin{center}
\scalebox{0.4}{\includegraphics{PartisanTauntHistBlack2.pdf}}
\end{center}\end{figure}
}
\end{frame}

\begin{frame}
\frametitle{Over Time Tauting Rates in Speeches}

\begin{figure}[hbt!]
      \begin{center}
        \scalebox{0.45}{\includegraphics{OverTimeParty.pdf}}
      \end{center}
     \end{figure}

 \end{frame}

\begin{frame}
%\frametitle{Advancing Inference Through Computer Assisted Conceptualization}
%\begin{tikzpicture}
 %\node (concept) at (-1,8)[] {1) \alert{Conceptualization}};
 %\node (measure) at (-1.37,5.85) [] {2) Measurement};
 %\node (valid) at (-1.64, 3.2) [] {3) Validation};

%\node (quant) at (5 ,4.525) [] {\alert{Quantitative Methods}};
%\draw[->] (quant) to [out=180, in=355] (measure);
 %  \draw[->] (quant) to [out=185, in=5] (valid);

%\node (qual) at (5 ,7.16) [] {Qualitative Methods}; \draw[->] (qual)
%to [out=175, in=355] (concept);
 %  \draw[->] (qual) to [out=185, in=5] (measure);

 %\draw[->, red,thick] (quant) to [out=175, in=345] (concept);

%\end{tikzpicture}

 How do we formulate conceptualizations?\pause  \\

\invisible<1>{ Tension in potential methods} \pause 
\begin{enumerate}
\invisible<1-2>{\item[1)]  FAC methods tuned to problem } \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Provides single answer, uncertainty estimates} \pause 
\invisible<1-4>{\item[-] Imposes many unstated assumptions, narrow set of conceptualizations considered} \pause 
\invisible<1-5>{\item[-] Difficult for political scientist to tune to their problem} \pause 
\end{itemize}
\invisible<1-6>{\item[2)] CAC methods to explore a space of partitions} \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Varies assumptions, ensures many different conceptualizations considered} \pause 
\invisible<1-8>{\item[-] Burden on user to discover conceptualization} \pause 
\end{itemize}
\end{enumerate}

\begin{itemize}
\invisible<1-9>{\item[-] Best evaluation: An improbable experiment } \pause 
\begin{itemize}
\invisible<1-10>{\item[-] Randomly assign incoming grad students to three conditions} \pause 
\begin{itemize}
\invisible<1-11>{\item[-] Topic Models (FAC)} \pause 
\invisible<1-12>{\item[-] Semi-supervised methods (CAC)} \pause 
\invisible<1-13>{\item[-] Manual methods} \pause 
\end{itemize}
\invisible<1-14>{\item[-] Observe group with most productivity 20-30 years later} \pause 
\end{itemize}
\invisible<1-15>{\item[-] To identify limits of methods, when to use which approach, need evaluations for the \alert{usefulness} of conceptualizations}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Clustering, FAC and CAC}

This week
\begin{itemize}
\item[-] Introduction to clustering
\item[-] Fully automated clustering algorithms
\item[-] Introduction to computer assisted clustering
\end{itemize}
Next week:
\begin{itemize}
\item[-] \alert{Vanilla Topic models}
\item[-] Structural Topic Models
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{EM Algorithm for Mixture of vMF Distributions}

\begin{itemize}
\item[1)] Initialize $\boldsymbol{\mu}$
\item[2)] Set $r_{ik}$ to 
\begin{eqnarray}
r_{ik} & = & \frac{ \pi_{k} \exp(\kappa \boldsymbol{\mu}_{k}^{'}\boldsymbol{x}_{i}^{*})  }{ \sum_{l=1}^{K} \pi_{k} \exp(\kappa \boldsymbol{\mu}_{l}^{'}\boldsymbol{x}_{i}^{*})  } \nonumber 
\end{eqnarray}
\item[3)] Set $\boldsymbol{\mu}_{k}$ to 
\begin{eqnarray}
\boldsymbol{\mu}_{k} & = & \frac{\sum_{i=1}^{N} r_{ik} \boldsymbol{x}_{i}  }{||\sum_{i=1}^{N} r_{ik} \boldsymbol{x}_{i}|| } \nonumber 
\end{eqnarray}
Set $\pi_{k} = \sum_{i=1}^{N} \frac{ r_{ik} }{ N }$
\item[4)] Assess change in objective function
\end{itemize}

\end{frame}

\end{document}

\end{document}

### 2017-12-10 resources/text_as_data/tc12.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\newcommand{\argmin}{\arg\!\min}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
 \numberwithin{equation}{section}

%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{October 30th, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Structured Topic Models}

\begin{itemize}
\item[1)] Task: 
\begin{itemize}
\item[-] Examine how document attention, topic content varies$\leadsto$ over time, across authors, or with \alert{general set of covariates}
\end{itemize}
\item[2)] Objective Function
\begin{eqnarray}
&& f(\boldsymbol{X}, \boldsymbol{\pi}, \boldsymbol{\Theta}, \boldsymbol{\alpha}, \alert{\boldsymbol{W}})  \nonumber 
\end{eqnarray}
Where:
\begin{itemize}
\item[-] $\boldsymbol{W}$ condition on information in document$\leadsto$ other potential modifications to objective function.  \alert{Meta-data}.  
\item[-] $f(\boldsymbol{X}, \boldsymbol{\pi}, \boldsymbol{\Theta}, \boldsymbol{\alpha}, \alert{\boldsymbol{W}})$ may encode additional information$\leadsto$ layers of clustering, layers of topics, etc
\end{itemize}
\item[3)] Optimization
\begin{itemize}
\item[-] EM, Variational Approximation, Gibbs Sampling, $\hdots $
\end{itemize}
\item[4)] Validation$\leadsto$ many of the same methods from clustering
\begin{itemize}
\item[-] Semantic, Convergent, Discriminant, Predictive, Hypothesis validity
\item[-] \alert{How do we avoid the electric machine critique}?
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{LDA Revisited}

\only<1>{\begin{eqnarray}
\boldsymbol{\theta}_{k} & \sim & \text{Dirichlet}(\boldsymbol{1}) \nonumber \\
\boldsymbol{\pi}_{i}|\boldsymbol{\alpha} & \sim &  \text{Dirichlet}(\boldsymbol{\alpha}) \nonumber \\
\boldsymbol{\tau}_{im}| \boldsymbol{\pi}_{i} & \sim & \text{Multinomial}(1, \boldsymbol{\pi}_{i}) \nonumber \\
x_{im} | \boldsymbol{\theta}_{k}, \tau_{imk} = 1 & \sim & \text{Multinomial}(1, \boldsymbol{\theta}_{k}) \nonumber 
\end{eqnarray}}

\only<2>{\begin{eqnarray}
\textbf{Unigram Model}_{k} & \sim & \text{Dirichlet}(\boldsymbol{1}) \nonumber \\
\textbf{Doc. Prop}_{i} & \sim & \text{Dirichlet}(\textbf{Pop. Proportion}) \nonumber \\
\textbf{Word Topic}_{im} & \sim & \text{Multinomial}(1, \textbf{Doc. Prop}_{i}) \nonumber \\
\text{Word}_{im} & \sim & \text{Multinomial}(1, \textbf{Unigram Model}_{k}) \nonumber 
\end{eqnarray}}

\end{frame}

\begin{frame}
\frametitle{A General Hierarchical Structure}

LDA: 
\begin{tikzpicture}

\node (col) at (0, 10) [] {\textbf{Pop. Proportion}} ;

\invisible<1>{

\node (doc1) at (-5, 8) [] {\textbf{Doc. Prop}$_{1}$} ; 
\node (doc2) at (-1, 8) [] {\textbf{Doc. Prop}$_{2}$} ; 
\node (dots) at ( 2, 8) [] {$\hdots$} ; 
\node (docN) at (4, 8) [] {\textbf{Doc. Prop}$_{N}$} ;

\draw[->, line width=1.5pt] (col) to [out=240, in = 90] (doc1); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (doc2); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (docN);

}

\invisible<1-2>{

\node (word11) at (-5, 7) [] {\textbf{Word Topics}$_{1}$} ; 
\node (word22) at (-1, 7) [] {\textbf{Word Topics}$_{2}$} ; 
\node (wordnn) at (4, 7) [] {\textbf{Word Topics}$_{N}$ } ;

\draw[->, line width=1.5pt] (doc1) to [out=270, in=90] (word11) ; 
\draw[->, line width=1.5pt] (doc2) to [out=270, in=90] (word22) ; 
\draw[->, line width=1.5pt] (docN) to [out=270, in=90] (wordnn) ;

}

\invisible<1-3>{

\node (wordaa) at (-5, 6) [] {\textbf{Words}$_{1}$} ; 
\node (wordbb) at (-1, 6) [] {\textbf{Words}$_{2}$} ; 
\node (wordcc) at (4, 6) [] {\textbf{Words}$_{N}$ } ;

\draw[->, line width = 1.5pt] (word11) to [out = 270, in = 90] (wordaa); 
\draw[->, line width = 1.5pt] (word22) to [out = 270, in = 90] (wordbb); 
\draw[->, line width = 1.5pt] (wordnn) to [out = 270, in = 90] (wordcc);

\node (topics) at (-1, 4) [] {$\textbf{Unigram Models}$} ;

\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordaa); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordbb); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordcc);

}

\end{tikzpicture}

\pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{A General Hierarchical Structure}

Dynamic Topic Model (Quinn et al 2010) 
\begin{tikzpicture}

\node (col) at (0, 10) [] {\textbf{Dynamic Prior Across Days}} ;

\invisible<1>{

\node (doc1) at (-5, 8) [] {\textbf{Day Prop}$_{1}$} ; 
\node (doc2) at (-1, 8) [] {\textbf{Day Prop}$_{2}$} ; 
\node (dots) at ( 2, 8) [] {$\hdots$} ; 
\node (docN) at (4, 8) [] {\textbf{Day Prop}$_{N}$} ;

\draw[->, line width=1.5pt] (col) to [out=240, in = 90] (doc1); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (doc2); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (docN);

}

\invisible<1-2>{

\node (word11) at (-5, 7) [] {\textbf{Speech Topics}$_{1}$} ; 
\node (word22) at (-1, 7) [] {\textbf{Speech Topics}$_{2}$} ; 
\node (wordnn) at (4, 7) [] {\textbf{Speech Topics}$_{N}$ } ;

\draw[->, line width=1.5pt] (doc1) to [out=270, in=90] (word11) ; 
\draw[->, line width=1.5pt] (doc2) to [out=270, in=90] (word22) ; 
\draw[->, line width=1.5pt] (docN) to [out=270, in=90] (wordnn) ;

}

\invisible<1-3>{

\node (wordaa) at (-5, 6) [] {\textbf{Speeches}$_{1}$} ; 
\node (wordbb) at (-1, 6) [] {\textbf{Speeches}$_{2}$} ; 
\node (wordcc) at (4, 6) [] {\textbf{Speeches}$_{N}$ } ;

\draw[->, line width = 1.5pt] (word11) to [out = 270, in = 90] (wordaa); 
\draw[->, line width = 1.5pt] (word22) to [out = 270, in = 90] (wordbb); 
\draw[->, line width = 1.5pt] (wordnn) to [out = 270, in = 90] (wordcc);

\node (topics) at (-1, 4) [] {$\textbf{Unigram Models}$} ;

\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordaa); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordbb); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordcc);

}

\end{tikzpicture}

\pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{A General Hierarchical Structure}

Expressed Agenda Model (Grimmer 2010) 
\begin{tikzpicture}

\node (col) at (0, 10) [] {\textbf{Average Attention Across Authors}} ;

\invisible<1>{

\node (doc1) at (-5, 8) [] {\textbf{Author Prop}$_{1}$} ; 
\node (doc2) at (-1, 8) [] {\textbf{Author Prop}$_{2}$} ; 
\node (dots) at ( 2, 8) [] {$\hdots$} ; 
\node (docN) at (4, 8) [] {\textbf{Author Prop}$_{N}$} ;

\draw[->, line width=1.5pt] (col) to [out=240, in = 90] (doc1); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (doc2); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (docN);

}

\invisible<1-2>{

\node (word11) at (-5, 7) [] {\textbf{Text Topics}$_{1}$} ; 
\node (word22) at (-1, 7) [] {\textbf{Text Topics}$_{2}$} ; 
\node (wordnn) at (4, 7) [] {\textbf{Text Topics}$_{N}$ } ;

\draw[->, line width=1.5pt] (doc1) to [out=270, in=90] (word11) ; 
\draw[->, line width=1.5pt] (doc2) to [out=270, in=90] (word22) ; 
\draw[->, line width=1.5pt] (docN) to [out=270, in=90] (wordnn) ;

}

\invisible<1-3>{

\node (wordaa) at (-5, 6) [] {\textbf{Texts}$_{1}$} ; 
\node (wordbb) at (-1, 6) [] {\textbf{Texts}$_{2}$} ; 
\node (wordcc) at (4, 6) [] {\textbf{Texts}$_{N}$ } ;

\draw[->, line width = 1.5pt] (word11) to [out = 270, in = 90] (wordaa); 
\draw[->, line width = 1.5pt] (word22) to [out = 270, in = 90] (wordbb); 
\draw[->, line width = 1.5pt] (wordnn) to [out = 270, in = 90] (wordcc);

\node (topics) at (-1, 4) [] {$\textbf{Unigram Models}$} ;

\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordaa); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordbb); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordcc);

}

\end{tikzpicture}

\pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{A General Hierarchical Structure}

Structural Topic Model (Roberts, Stewart, Airoldi 2014) 
\begin{tikzpicture}

\node (col) at (0, 10) [] {$g(\boldsymbol{W}, \boldsymbol{\gamma}) $} ;

\invisible<1>{

\node (doc1) at (-5, 8) [] {\textbf{Strata Prop}$_{1}$} ; 
\node (doc2) at (-1, 8) [] {\textbf{Strata Prop}$_{2}$} ; 
\node (dots) at ( 2, 8) [] {$\hdots$} ; 
\node (docN) at (4, 8) [] {\textbf{Strata Prop}$_{N}$} ;

\draw[->, line width=1.5pt] (col) to [out=240, in = 90] (doc1); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (doc2); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (docN);

}

\invisible<1-2>{

\node (word11) at (-5, 7) [] {\textbf{Text Topics}$_{1}$} ; 
\node (word22) at (-1, 7) [] {\textbf{Text Topics}$_{2}$} ; 
\node (wordnn) at (4, 7) [] {\textbf{Text Topics}$_{N}$ } ;

\draw[->, line width=1.5pt] (doc1) to [out=270, in=90] (word11) ; 
\draw[->, line width=1.5pt] (doc2) to [out=270, in=90] (word22) ; 
\draw[->, line width=1.5pt] (docN) to [out=270, in=90] (wordnn) ;

}

\invisible<1-3>{

\node (wordaa) at (-5, 6) [] {\textbf{Texts}$_{1}$} ; 
\node (wordbb) at (-1, 6) [] {\textbf{Texts}$_{2}$} ; 
\node (wordcc) at (4, 6) [] {\textbf{Texts}$_{N}$ } ;

\draw[->, line width = 1.5pt] (word11) to [out = 270, in = 90] (wordaa); 
\draw[->, line width = 1.5pt] (word22) to [out = 270, in = 90] (wordbb); 
\draw[->, line width = 1.5pt] (wordnn) to [out = 270, in = 90] (wordcc);

\node (topics) at (-1, 4) [] {$\textbf{Unigram Models}$} ;

\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordaa); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordbb); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordcc);

}

\invisible<1-4>{
\node (reg) at (3, 4) [] {$h(\tilde{\boldsymbol{W}}, \boldsymbol{\kappa})$ )};

\draw[->, line width = 1.5pt] (reg) to [out = 180, in = 0] (topics);

}
\end{tikzpicture}

\pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{A General Hierarchical Structure}

Conditioning on Unknown Covariates$\leadsto$ levels of mixtures at proportions (Grimmer 2013; Wallach 2008) 
\begin{tikzpicture}

\only<1>{\node (col_on) at (0, 10)[] {\textbf{Mixture of Top. Attn. Models}} ; }

\invisible<1>{\node (col1) at (-2, 10) [] {\textbf{Strata Indic.} } ; 
\node (col) at (2, 10) [] {\textbf{Topic Attention Models} }  ; }

\invisible<1-2>{

\node (doc1) at (-5, 8) [] {\textbf{Strata Prop}$_{1}$} ; 
\node (doc2) at (-1, 8) [] {\textbf{Strata Prop}$_{2}$} ; 
\node (dots) at ( 2, 8) [] {$\hdots$} ; 
\node (docN) at (4, 8) [] {\textbf{Strata Prop}$_{N}$} ;

\draw[->, line width=1.5pt, red] (col1) to [out=270, in = 135] (doc1); 
\draw[->, line width=1.5pt, red] (col1) to [out=270, in = 135] (doc2); 
\draw[->, line width=1.5pt, red] (col1) to [out=270, in = 135] (docN); 
}

\invisible<1-3>{

\draw[->, line width=1.5pt] (col) to [out=270, in = 45] (doc1); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (doc2); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (docN);

}

\invisible<1-4>{

\node (word11) at (-5, 7) [] {\textbf{Text Topics}$_{1}$} ; 
\node (word22) at (-1, 7) [] {\textbf{Text Topics}$_{2}$} ; 
\node (wordnn) at (4, 7) [] {\textbf{Text Topics}$_{N}$ } ;

\draw[->, line width=1.5pt] (doc1) to [out=270, in=90] (word11) ; 
\draw[->, line width=1.5pt] (doc2) to [out=270, in=90] (word22) ; 
\draw[->, line width=1.5pt] (docN) to [out=270, in=90] (wordnn) ;

}

\invisible<1-5>{

\node (wordaa) at (-5, 6) [] {\textbf{Texts}$_{1}$} ; 
\node (wordbb) at (-1, 6) [] {\textbf{Texts}$_{2}$} ; 
\node (wordcc) at (4, 6) [] {\textbf{Texts}$_{N}$ } ;

\draw[->, line width = 1.5pt] (word11) to [out = 270, in = 90] (wordaa); 
\draw[->, line width = 1.5pt] (word22) to [out = 270, in = 90] (wordbb); 
\draw[->, line width = 1.5pt] (wordnn) to [out = 270, in = 90] (wordcc);

\node (topics) at (-1, 4) [] {$\textbf{Unigram Models}$} ;

\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordaa); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordbb); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordcc);

}

\end{tikzpicture}

\pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{A General Hierarchical Structure}

Conditioning on Unknown Covariates for Topics$\leadsto$ hierarchy of topics (Li and McCallum 2006; Blaydes, Grimmer, and McQueen 2014) 
\begin{tikzpicture}

\node (col) at (-1, 10)[] {\textbf{Population attention}} ;

\invisible<1>{

\node (doc1) at (-5, 8) [] {\textbf{Strata Prop}$_{1}$} ; 
\node (doc2) at (-1, 8) [] {\textbf{Strata Prop}$_{2}$} ; 
\node (dots) at ( 2, 8) [] {$\hdots$} ; 
\node (docN) at (4, 8) [] {\textbf{Strata Prop}$_{N}$} ;

\draw[->, line width=1.5pt] (col) to [out=270, in = 45] (doc1); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (doc2); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (docN);

}

\invisible<1-2>{

\node (word11) at (-5, 7) [] {\textbf{Text Topics}$_{1}$} ; 
\node (word22) at (-1, 7) [] {\textbf{Text Topics}$_{2}$} ; 
\node (wordnn) at (4, 7) [] {\textbf{Text Topics}$_{N}$ } ;

\draw[->, line width=1.5pt] (doc1) to [out=270, in=90] (word11) ; 
\draw[->, line width=1.5pt] (doc2) to [out=270, in=90] (word22) ; 
\draw[->, line width=1.5pt] (docN) to [out=270, in=90] (wordnn) ;

}

\invisible<1-3>{

\node (wordaa) at (-5, 6) [] {\textbf{Texts}$_{1}$} ; 
\node (wordbb) at (-1, 6) [] {\textbf{Texts}$_{2}$} ; 
\node (wordcc) at (4, 6) [] {\textbf{Texts}$_{N}$ } ;

\draw[->, line width = 1.5pt] (word11) to [out = 270, in = 90] (wordaa); 
\draw[->, line width = 1.5pt] (word22) to [out = 270, in = 90] (wordbb); 
\draw[->, line width = 1.5pt] (wordnn) to [out = 270, in = 90] (wordcc);

\node (topics) at (-1, 4) [] {$\textbf{Unigram Models}$} ;

\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordaa); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordbb); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordcc);

}

\invisible<1-4>{
\node (mix) at (3, 4) [] {\textbf{Hierarchy of Topics}} ; 
\draw[->, line width = 1.5pt] (mix) to [out = 180, in = 0] (topics); 
}

\end{tikzpicture}

\pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Why Encode Structure in Extensions of LDA?}

\pause

\begin{itemize}
\invisible<1>{\item[-] Substantive reasons} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Additional structure corresponds to substantively interesting content} \pause 
\invisible<1-3>{\item[-] Avoids potential ad-hoc secondary analysis} \pause 
\invisible<1-4>{\item[-] Clear data generating process} \pause 
\end{itemize}
\invisible<1-5>{\item[-] Statistical reasons} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] \alert{Smoothing}$\leadsto$ borrow information across groups intelligently} \pause 
\invisible<1-7>{\item[-] \alert{Uncertainty}$\leadsto$ potential for better uncertainty estimates} \pause 
\invisible<1-8>{\item[-] \alert{Improved topics}$\leadsto$ small word conditions, structure could help} 
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Plan for the Class}

\begin{itemize}
\item[1)] Discuss model with unknown covariates for strata proportions$\leadsto$ presentational style
\item[2)] Discuss model with hierarchy of topics$\leadsto$ mirrors genre
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Unknown Covariates for Issue Attention: Measuring Attention in Senate Press Releases}

Substantive problem: \pause  \\
\invisible<1>{Senators (representatives) regularly engage the public $\rightarrow$ presentational style\\
But we know little about this engagement} \pause \\
\invisible<1-2>{Why?  \alert{Hard to Measure} } \pause \\

\invisible<1-3>{Describe model that facilitates estimation of \alert{presentational styles} in Senate press releases} \pause 
\begin{itemize}
\invisible<1-4>{\item[-] Characterize representation provided to constituents} \pause 
\invisible<1-5>{\item[-] Divide attention over a set of topics} \pause 
\invisible<1-6>{\item[-] Given attention to topics, write press releases} 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Presentational Styles$\leadsto$ Objective Function}
\begin{itemize}
\item[-] $\pi_{itk} \equiv$ Attention senator $i$ allocates to
issue $k$ in year $t$
\item[-] $\pi_{itk} \equiv$ Probability press release is
about issue $k$
\item[-] $\boldsymbol{\pi}_{it} = (\pi_{it1},
\hdots, \pi_{it 44}) $
\end{itemize}
\pause 
\invisible<1>{Press release-level parameters (press release $j$ from senator $i$
in year $t$)} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] \alert{Assume}: Each press release $j$
assigned to one topic.
\item[-] Let
$\boldsymbol{\tau}_{ijt}$ indicate press release $j$'s topic.} \pause 
\end{itemize}
\invisible<1-3>{\begin{center} $\boldsymbol{\tau}_{ijt} \sim
\text{Multinomial}(1, \boldsymbol{\pi}_{it}) $ \end{center}} \pause 
\begin{itemize}
\invisible<1-4>{\item[-] Conditional on topic, draw document's
content.} \pause 
\invisible<1-5>{\item[-] If $\tau_{ijtk} =1$ then
\end{itemize}
\begin{center}$\boldsymbol{x}_{ijt} \sim \text{Multinomial}(n_{ijt}, \boldsymbol{\theta}_k
).$} 
\end{center}
\end{frame}

\begin{frame}
\frametitle{Priors}

 Each $\boldsymbol{\pi}_{it}$ is a draw from one-of-$S$ styles$\leadsto$ mixture of Dirichlet distributions \pause .
\begin{eqnarray}
 \invisible<1>{\boldsymbol{\sigma}_{it} & \sim  & \text{Multinomial}(1, \boldsymbol{\beta}). } \pause \nonumber \\
 \invisible<1-2>{\boldsymbol{\pi}_{it}|\sigma_{its}=1, \boldsymbol{\alpha}_s & \sim &  \text{Dirichlet}(\boldsymbol{\alpha}_s) \nonumber } \pause \\
\invisible<1-3>{\alpha_{ks} & \sim & \text{Gamma}(0.25, 1)} \pause  \nonumber
\end{eqnarray}

\invisible<1-4>{Other priors:} \pause 
\begin{eqnarray}
\invisible<1-5>{\boldsymbol{\theta}_k & \sim & \text{Multinomial}(\boldsymbol{\lambda}) \nonumber \\} \pause 
\invisible<1-6>{\boldsymbol{\beta} & \sim & \text{Multinomial}(\boldsymbol{1})} 
\nonumber
\end{eqnarray}

\end{frame}

%\begin{frame}
%\begin{eqnarray}
%\alpha_{sk} & \sim & \text{Gamma}(0.25, 1) \text{ for all } k, s \nonumber \\
%\boldsymbol{\beta} & \sim & \text{Dirichlet}(\boldsymbol{1}) \nonumber \\
%\boldsymbol{\theta}_k & \sim & \text{Dirichlet}(\boldsymbol{\lambda} ) \nonumber \\
%\boldsymbol{\sigma}_{it} | \boldsymbol{\beta} & \sim & \text{Multinomial}(1, \boldsymbol{\beta} ) \text{ for all } i ; t \nonumber \\
%\boldsymbol{\pi}_{it} | \boldsymbol{\sigma}_{its}=1, \boldsymbol{\alpha}_s & \sim & \text{Dirichlet}(\boldsymbol{\alpha}_s) \text{ for all } i ; t  \nonumber \\
%\boldsymbol{\tau}_{ijt}|\boldsymbol{\pi}_{it} & \sim & \text{Multinomial}(1, \boldsymbol{\pi}_{it} ) \text{ for all } j ; t ; i  \nonumber \\
%\boldsymbol{y}_{ijt} | \boldsymbol{\tau}_{ijtk} = 1,
%\boldsymbol{\theta}_k & \sim & \text{Multinomial}(n_{ijt},
%\boldsymbol{\theta}_k) \text{ for all } j ; t ; i  \nonumber
%\end{eqnarray}
%\end{frame}

\begin{frame}
\frametitle{Presentational Styles$\leadsto$ Objective Function}

\pause 
\begin{eqnarray}
\invisible<1>{\boldsymbol{\beta}& \sim & \text{Dirichlet}(\boldsymbol{1}) \nonumber } \\
\invisible<1>{\boldsymbol{\theta}_{k} & \sim & \text{Dirichlet}(\boldsymbol{\lambda}) \nonumber}  \\
\invisible<1>{\alpha_{ks} & \sim & \text{Gamma}(0.25, 1) \nonumber}  \\
\invisible<1-2>{\boldsymbol{\sigma}_{it} & \sim & \text{Multinomial}(1, \boldsymbol{\beta}) \nonumber } \\
\invisible<1-3>{\boldsymbol{\pi}_{it}| \sigma_{its} = 1, \boldsymbol{\alpha}_{s} & \sim & \text{Dirichlet}(\boldsymbol{\alpha}_{s})\nonumber} \\
\invisible<1-4>{\boldsymbol{\tau}_{ijt} | \boldsymbol{\pi}_{it} & \sim & \text{Multinomial}(1, \boldsymbol{\pi}_{it}) \nonumber \\}
\invisible<1-5>{\boldsymbol{x}_{ijt}| \tau_{ijtk} = 1, \boldsymbol{\theta}_{k} & \sim & \text{Multinomial}(n_{ijt}, \boldsymbol{\theta}_{k})\nonumber }
\end{eqnarray}

\pause \pause \pause \pause \pause 
\end{frame}

\begin{frame}
\frametitle{Mixture of Styles, Mixture of Topics}

\begin{tikzpicture}

\node (col1) at (-2, 10) [] {\textbf{Style Indicators} } ; 
\node (col) at (2, 10) [] {\textbf{Dirichlet Distributions} }  ;

\node (doc1) at (-5, 8) [] {\textbf{Senator Prop}$_{1}$} ; 
\node (doc2) at (-1, 8) [] {\textbf{Senator Prop}$_{2}$} ; 
\node (dots) at ( 2, 8) [] {$\hdots$} ; 
\node (docN) at (4, 8) [] {\textbf{Senator Prop}$_{N}$} ;

\draw[->, line width=1.5pt, red] (col1) to [out=270, in = 135] (doc1); 
\draw[->, line width=1.5pt, red] (col1) to [out=270, in = 135] (doc2); 
\draw[->, line width=1.5pt, red] (col1) to [out=270, in = 135] (docN);

\draw[->, line width=1.5pt] (col) to [out=270, in = 45] (doc1); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (doc2); 
\draw[->, line width=1.5pt] (col) to [out=270, in = 90] (docN);

\node (word11) at (-5, 7) [] {\textbf{Press Topics}$_{1}$} ; 
\node (word22) at (-1, 7) [] {\textbf{Press Topics}$_{2}$} ; 
\node (wordnn) at (4, 7) [] {\textbf{Press Topics}$_{N}$ } ;

\draw[->, line width=1.5pt] (doc1) to [out=270, in=90] (word11) ; 
\draw[->, line width=1.5pt] (doc2) to [out=270, in=90] (word22) ; 
\draw[->, line width=1.5pt] (docN) to [out=270, in=90] (wordnn) ;

\node (wordaa) at (-5, 6) [] {\textbf{Press}$_{1}$} ; 
\node (wordbb) at (-1, 6) [] {\textbf{Press}$_{2}$} ; 
\node (wordcc) at (4, 6) [] {\textbf{Press}$_{N}$ } ;

\draw[->, line width = 1.5pt] (word11) to [out = 270, in = 90] (wordaa); 
\draw[->, line width = 1.5pt] (word22) to [out = 270, in = 90] (wordbb); 
\draw[->, line width = 1.5pt] (wordnn) to [out = 270, in = 90] (wordcc);

\node (topics) at (-1, 4) [] {$\textbf{Unigram Models}$} ;

\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordaa); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordbb); 
\draw[->, line width = 1.5pt] (topics) to [out = 90, in = 270] (wordcc);

\end{tikzpicture}

\end{frame}

\begin{frame}

Posterior: \tiny
\begin{eqnarray}
p(\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\theta},
\boldsymbol{\sigma}, \boldsymbol{\pi},
\boldsymbol{\tau}|\boldsymbol{X}) & \propto &
\prod_{k=1}^{K}\prod_{s=1}^{S} \frac{\exp( -
\frac{\alpha_{ks}}{1/4})}{1/4} \times \frac{\Gamma(\sum_{w=1}^{W}
\lambda_w) }{\prod_{w=1}^{W} \Gamma(\lambda_w) } \prod_{w=1}^{W}
\theta_{k,w}^{\lambda_w - 1}
\times \nonumber \\
& & \prod_{i=1}^{N} \prod_{t=2005}^{2007} \prod_{s=1}^{S} \left[
\beta_s \frac{\Gamma(\sum_{k=1}^{K} \alpha_{ks})}{\prod_{k=1}^{K}
\Gamma(\alpha_{ks} )} \prod_{k=1}^{K} \pi_{itk}^{\alpha_{ks}-1}
\prod_{j=1}^{D_{it} }\prod_{k=1}^{K} \left[ \pi_{itk}
\prod_{w=1}^{W} \theta_{kw} ^{x_{ijtw} }
 \right]^{\tau_{ijtk}} \right]^{\sigma_{its}} \nonumber
\end{eqnarray}

\pause

\normalsize
\begin{itemize}
\invisible<1>{\item[1)] Estimate with Variational Approximation} \pause 
\invisible<1-2>{\item[2)] Determining number of clusters at top? (Grimmer, Shorey, Wallach, and Zlotnick, In Progress)} \pause
\begin{itemize}
\invisible<1-3>{\item[-] Non-parametric model$\leadsto$ statistical selection} \pause
\invisible<1-4>{\item[-] Experiments/Coding Exercises to assess} 
\end{itemize}

\end{itemize}

\end{frame}

\begin{frame}

\only<1>{\scalebox{0.35}{\includegraphics{ShelbyPress.pdf}}}
\only<2>{\scalebox{0.35}{\includegraphics{SessionsPress.pdf}}}

\end{frame}

\begin{frame}
\frametitle{Notions of validity: From Quinn, Monroe, et al (2010) }

\begin{enumerate}
\item[-] \alert{Semantic Validity:} All categories are coherent and meaningful
\item[-] \alert{Convergent Construct Validity:} Measures concur with existing measures in critical details.
\item[-]  \alert{Discriminant Construct Validity}: Measures differ from existing measures in productive ways.  
\item[-] \alert{Predictive Measure:} Measures from the model corresponds to external events in expected ways.
\item[-] \alert{Hypothesis Validity:} Measures generated from the model can be used to test substantive hypotheses. 
\end{enumerate}

To establish utility of new measures, demonstrate variety of \alert{validations}\\
\alert{None of these validations are performed using a canned statistic}\\
\alert{All}: require substantive knowledge on areas (and what we expect!) [

\end{frame}

\begin{frame}
\frametitle{Home Style Measures, Semantic Validity}

\alert{Must}: Demonstrate to reader that topics are coherent and semantically meaningful

\begin{tabular}{lll}
\hline\hline
Description & Stems & \% \\
\hline
Honorary& honor,prayer,rememb,fund,tribut& 5.0\\
Transp. Grants& airport,transport,announc,urban,hud&4.8\\
Iraq& iraq,iraqi,troop,war,sectarian& 4.7\\
DHS Policy& homeland,port,terrorist,dh,fema&4.1\\
Judicial Nom.& judg,court,suprem,nomin,nomine&3.8\\
Fire Dept. Grant& firefight,homeland,afgp,award,equip&3.7\\
\hline
\end{tabular}

How: \alert{examples} in text are also useful.

\end{frame}

\begin{frame}
\frametitle{Home Style Measures, Convergent Validity}

\only<1-3>{\alert{Over time variation} }
\only<4>{\alert{Supervised/Unsupervised Convergence} } 
\only<1>{\scalebox{0.4}{\includegraphics{ImmigrationPlot.pdf}}}
\only<2>{\scalebox{0.4}{\includegraphics{IraqWarPlot.pdf}}}
%\only<3>{\scalebox{0.4}{\includegraphics{Worker5.pdf}}}
\only<3>{\scalebox{0.4}{\includegraphics{HonorPlot.pdf}}}

\only<4>{\scalebox{0.3}{\includegraphics{SupervisedUnsupervised.pdf}}}
\only<5>{\scalebox{0.3}{\includegraphics{ConvValid.pdf}}}

\end{frame}

\begin{frame}
\frametitle{Discriminant Construct Validity}

\scalebox{0.45}{\includegraphics{IdealAttn.pdf} }

\end{frame}

\begin{frame}
\frametitle{Predictive Validity}

\scalebox{0.4}{\includegraphics{CompareLeaders.pdf} }

\end{frame}

\begin{frame}
\frametitle{Hypothesis Validity}

\scalebox{0.28}{\includegraphics{PrioritiesPlotLabel.pdf}}

\begin{columns}[]
\invisible<1>{\column{0.25\textwidth}
\textcolor{blue}{Senate}\\
\textcolor{blue}{Statesperson}
\begin{itemize}
\item[-] \textcolor{blue}{Iraq War}
\item[-] \textcolor{blue}{Intelligence}
\item[-] \textcolor{blue}{Intl. Relations}
\item[-] \textcolor{blue}{Budget}
\end{itemize}}

\invisible<1-2>{\column{0.25\textwidth}
\textcolor{darkgreen}{Domestic}\\
\textcolor{darkgreen}{Policy}
\begin{itemize}
\item[-] \textcolor{darkgreen}{Environment}
\item[-] \textcolor{darkgreen}{Gas prices}
\item[-] \textcolor{darkgreen}{DHS}
\item[-] \textcolor{darkgreen}{Consumer Safety}
\end{itemize}}

\invisible<1-3>{\column{0.25\textwidth} \textcolor{brown}{Pork \&
Policy}
\begin{itemize}
\item[-] \textcolor{brown}{WRDA grants}
\item[-] \textcolor{brown}{Farming}
\item[-] \textcolor{brown}{Health Care}
\item[-] \textcolor{brown}{Education Policy}
\end{itemize}}

\invisible<1-4>{\column{0.25\textwidth}
\textcolor{red}{Appropriators}
\begin{itemize}
\item[-] \textcolor{red}{Fire Grants}
\item[-] \textcolor{red}{Airport Grants}
\item[-] \textcolor{red}{University Money}
\item[-] \textcolor{red}{Police Grants}
\end{itemize}}

\end{columns}

\pause\pause\pause\pause
\end{frame}

\begin{frame}
\frametitle{Hypothesis Validity}

Why do senators adopt different styles?\\
\alert{District Fit}

\scalebox{0.4}{\includegraphics{FinalAvoidance.pdf}}

\end{frame}

\begin{frame}
\frametitle{What are the right number of topics?}

\pause

\begin{itemize}
\invisible<1>{\item[-] Number of topics$\leadsto$ depends on task at hand}
\invisible<1-2>{\item[-] Coarse$\leadsto$ broad comparisons, lose distinctions}
\invisible<1-3>{\item[-] Granular$\leadsto$ specific insights, lose broader picture}
\invisible<1-4>{\item[-] \alert{Hierarchy of topics}$\leadsto$ Pachinko Allocation, Hierarchies of von-Mises Fisher Distributions}
\end{itemize}

\invisible<1-5>{Blaydes, Grimmer, and McQueen [In Progress]$\leadsto$ estimate nested topics to explore the \alert{Mirros for Princes}}

\pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{The Mirrors Genre}

26 Christian mirrors \pause 
\begin{itemize}
\invisible<1>{\item[-] The Prince (1513 CE)} \pause 
\invisible<1-2>{\item[-] Advice to Justinian (527 CE)} \pause 
\invisible<1-3>{\item[-] The Adventures of Telemachus (1699 CE)} \pause 
\end{itemize}

\invisible<1-4>{21 Islamic texts} \pause 
\begin{itemize}
\invisible<1-5>{\item[-] Advice on the Art of Governance (1612 CE)} \pause
\invisible<1-6>{\item[-] Kalila wa Dimna (748 CE)} \pause
\invisible<1-7>{\item[-] The Sultan's Register of Laws (1632-1633 CE)} \pause 
\end{itemize}

\invisible<1-8>{Work with translations}\pause\invisible<1-9>{$\leadsto$ little evidence of selection} \pause 
\begin{itemize}
\invisible<1-10>{\item[-] Collect data on collection of 98 (51 Christian, 47 Islamic, some not translated)} \pause 
\invisible<1-11>{\item[-] No difference on Year/Region} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Preprocessing Texts}

47 books \invisible<1>{$\leadsto$ Each divided into paragraphs} \\
\invisible<1-2>{Create feature space} 
\begin{itemize}
\invisible<1-3>{\item[-] Bag of words, stem, discard punctuation, stop words}
\invisible<1-4>{\item[-] Translate words left in Arabic (\alert{allah}) and discard proper nouns}
\invisible<1-5>{\item[-] Identified synonyms} 
\begin{itemize}
\invisible<1-6>{\item[-] \alert{almighty}, \alert{god}}
\invisible<1-7>{\item[-] \alert{monarch}, \alert{prince}, \alert{king}, \alert{ruler}}
\invisible<1-8>{\item[-] \alert{Lord} $\neq$ \alert{lord} }
\end{itemize}
\end{itemize}

\invisible<1-9>{Result: short segment $j$ in book $i$ is a count vector} 
\begin{eqnarray}
\invisible<1-10>{\textbf{x}_{ij} & = & (x_{ij1}, x_{ij2}, \hdots, x_{ij2124}) \nonumber}
\end{eqnarray}

\invisible<1-11>{We work with a normalized version of the documents, }
\begin{eqnarray}
\invisible<1-12>{\textbf{x}^{*}_{ij} & = & \frac{\textbf{x}_{ij}}{\sqrt{\textbf{x}^{'}_{ij}\textbf{x}_{ij}} } \nonumber}
\end{eqnarray}

\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Measuring Themes in the Mirrors}

\only<1-3>{Model built around two hierarchies: 
\begin{itemize}
\invisible<1>{\item[1)] Books $\leadsto$ paragraphs (Blei, Ng, Jordan 2003; Wallach, 2008; Quinn et al 2010; Grimmer 2010; Roberts et al 2014)}
\invisible<1-2>{\item[2)] Coarse topics $\leadsto$ granular topics (Li and McCallum 2006; Gopal and Yang 2014)}
\end{itemize}
}

\only<4->{
Estimate \alert{four} quantities of interest
\begin{itemize}
\invisible<1-4>{\item[1)] Granular topics (60)} 
\invisible<1-5>{\item[2)] Coarse (broad) topics (3)} 
\begin{itemize}
\invisible<1-6>{\item[-] Each granular topic classified into one coarse topic } 
\end{itemize}
\invisible<1-7>{\item[3)] Each book $i'$s  $\textbf{themes}_{i}}$ 
\invisible<1-8>{\item[4)] Each short segment's granular (and coarse) topic } 
\end{itemize}

\begin{eqnarray}
\invisible<1-7, 9->{\textbf{themes}_{i} & = & (\text{theme}_{i1}, \text{theme}_{i2}, \hdots, \text{theme}_{i60} ) \nonumber }
\end{eqnarray}

}

\pause \pause \pause \pause \pause \pause \pause \pause 
\end{frame}

\begin{frame}
\frametitle{A Hierarchy of Topics}

\begin{tikzpicture}

\node (Dummy) at (-9,8) [] {} ; 
\node (theme1) at (-8, 9) [] {$\textbf{themes}_{i} $} ; 
\invisible<1>{\node (draws) at (-4, 9) [] {$\textbf{Topic}_{ij}$};}
\invisible<1>{\draw[->, line width = 2pt] (theme1) to [out = 0, in = 180] (draws);}

\invisible<1-2>{\node (document) at (-1, 8) [] {$\textbf{x}^{*}_{ij}$ }; }
\invisible<1-2>{\draw[->, line width = 2pt] (draws) to [out = 350, in  = 145] (document); }

\invisible<1-2>{\node (topics)   at (-4, 7) [] {$\textbf{granular}$}; }

\invisible<1-2>{\draw[->, line width = 2pt] (topics) to [out = 0, in = 225] (document) ; }

\invisible<1-3>{\node (topic_sig) at (-6, 8.25) [] {$\textbf{broad}$} ; }

\invisible<1-3>{\draw[->, line width = 2pt] (topic_sig) to [out = 350, in = 110] (topics) ; }

\invisible<1-3>{\node (coarse)    at (-8, 7) [] {$\textbf{coarse}$}; }

\invisible<1-3>{\draw[->, line width = 2pt] (coarse) to [out = 0, in= 180] (topics) ; }

\end{tikzpicture}

\begin{eqnarray}
\invisible<1>{\textbf{Topic}_{ij} & \sim & \text{Multinomial}(1, \textbf{themes}_{i}) \nonumber }\\
\invisible<1-2>{\textbf{x}^{*}_{ij} | \text{Topic}_{ijk} =  1 & \sim & \text{vMF} (\kappa, \textbf{granular}_{k} ) \nonumber }\\
\invisible<1-3>{\textbf{broad}_{k} & \sim & \text{Multinomial}(1, \textbf{Broad Theme Prior}) \nonumber }\\
\invisible<1-3>{\textbf{granular}_{k} | \text{broad}_{km} = 1 & \sim & \text{vMF}(\kappa, \textbf{coarse}_{m}) \nonumber }
\end{eqnarray}

\invisible<1-4>{Estimate model with Variational Approximation}\\
\invisible<1-5>{Model selection: automatic model fit, qualitative evaluation}

\pause \pause \pause \pause \pause

%%draws theme
%%then draws content from a topic specific distribution
%%our model classifies each of those granular themes into coarse themes

\end{frame}

\begin{frame}
\frametitle{Interpreting Unsupervised Models}

Two approaches to labeling output \pause  
\begin{itemize}
\invisible<1>{\item[1)] \alert{Computational}: identify discriminating words }\pause 
\invisible<1-2>{\item[2)] \alert{Manual}: Segments classified to coarse, granular topics.  Read, discuss, and label} \pause 
\end{itemize}

\invisible<1-3>{Unsupervised models \alert{structure} and \alert{guide} our reading}

\end{frame}

\begin{frame}
\frametitle{Art of Rulership}

Practices and ideals of political rule

\vspace{0.5in}
\begin{tabular}{l}
\invisible<1>{king}\invisible<1-2>{,princ}\invisible<1-3>{,citi}\invisible<1-4>{,great,place,work,emperor,enemi,armi,letter} \\
\end{tabular}

\vspace{0.5in}
 \invisible<1-5>{36.5\% of paragraphs }

\pause \pause \pause \pause \pause

\end{frame}

\begin{frame}

\begin{center}
\scalebox{0.45}{\includegraphics{Hist_Super1_p.pdf}}
\end{center}

\end{frame}

\begin{frame}

\begin{center}
\scalebox{0.45}{\includegraphics{Super1.pdf}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Religion and Virtue}

Connection between religion, virtue, justice and political rule \pause

\vspace{0.5in}
\begin{tabular}{l}
\invisible<1>{almighti,good,virtu,power,ruler,justic,prayer,rule,prophet,mena \\}
\end{tabular}

\pause 
\vspace{0.5in}

\invisible<1-2>{32.2\% of pargraphs}

\end{frame}

\begin{frame}

\begin{center}
\scalebox{0.45}{\includegraphics{Hist_Super2_p.pdf}}
\end{center}

\end{frame}

\begin{frame}

\begin{center}
\scalebox{0.45}{\includegraphics{Super2.pdf}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Inner Life of the Ruler}

Personal relationships, care for and practices of the self, and ultimate fate of the soul \pause

\vspace{0.5in}

\begin{tabular}{ll}
\invisible<1>{man,land,woman,know,bodi,eye,ladi,love,faculti,old} \pause 
\end{tabular}

\vspace{0.5in}

\invisible<1-2>{31.2\% of paragraphs}

\end{frame}

\begin{frame}

\begin{center}
\scalebox{0.45}{\includegraphics{Hist_Super3_p.pdf}}
\end{center}

\end{frame}

\begin{frame}

\begin{center}
\scalebox{0.45}{\includegraphics{Super3.pdf}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Granular: Best Practices for Ruling}

\begin{tabular}{l}
\hline
king,princ,citi,great,place,work,emperor,enemi,armi,letter \\
\hline
\alert{king,kingdom,royal,minist,reign,father,court,majesti,presenc,war}
\end{tabular}

\vspace{0.5in}

6.2\% of paragraphs

\end{frame}

\begin{frame}

\begin{center}
\scalebox{0.45}{\includegraphics{1point1.pdf}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Granular: Characteristics that distinguish Just Ruler from Tyrant}

\begin{tabular}{l}
\hline
king,princ,citi,great,place,work,emperor,enemi,armi,letter \\
\hline
king,kingdom,royal,minist,reign,father,court,majesti,presenc,war\\
\alert{princ,good,peopl,christian,tyranni,war,mind,ought,state,public}\\
\end{tabular}

\vspace{0.5in}

3.1\% of paragraphs

\end{frame}

\begin{frame}

\begin{center}
\scalebox{0.45}{\includegraphics{1point2.pdf}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Granular: Religious Virtues and Political Ideals}

\begin{tabular}{l}
\hline
almighti,good,virtu,power,ruler,justic,prayer,rule,prophet,mena\\
\hline 
\alert{almighti,bless,grant,peac,messeng,prophet,merci,holi,command,grace}
\end{tabular}

\vspace{0.5in}

6.9\% of paragraphs

\end{frame}

\begin{frame}

\begin{center}
\scalebox{0.45}{\includegraphics{2point1.pdf}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Structural Topic Models}

\begin{itemize}
\item[-] Encode observed and unobserved meta data
\item[-] ?Improve substantive inferences
\end{itemize}

Next week:
\begin{itemize}
\item[1)] Hanna Wallach on canonical topic models
\item[2)] Introduction to supervised learning
\end{itemize}

Work on your problem sets!

\end{frame}

\begin{frame}

Appendix: Inference for both Models

\end{frame}

\begin{frame}
\frametitle{Inference}

Invariance in posterior makes it difficult (impossible) to
approximate with sampling based methods (relabeling, aliasing problem).  \\

Deterministic alternative: variational approximations.  \\

Intuition: approximate posterior with simpler (still very general)
approximating distribution. \\

Make approximation as ``close" as possible\\

\end{frame}

\begin{frame}
Approximate posterior with:

\scriptsize
\begin{eqnarray}
q(\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\theta},
\boldsymbol{\sigma}, \boldsymbol{\pi}, \boldsymbol{\tau}) & = &
q(\boldsymbol{\alpha})q(\boldsymbol{\beta})q( \boldsymbol{\theta})q(\boldsymbol{\sigma})q(\boldsymbol{\pi})q(\boldsymbol{\tau}) \nonumber \\
& = & q(\boldsymbol{\beta} ) \prod_{k=1}^{K}
q(\boldsymbol{\theta})_{k} \prod_{i=1}^{n}
\prod_{t=2005}^{2007}\left[ q(\boldsymbol{\sigma})_{it}
q(\boldsymbol{\pi})_{it}
 \prod_{j=1}^{J} q(\boldsymbol{\tau})_{ijt} \right] \prod_{s=1}^{S} q(\boldsymbol{\alpha})_{s}
 \nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Variational Approximation} Optimization goal:
\begin{itemize}
\item[-] Minimize the Kullback-Leibler divergence
between approximating distribution $q$ and true posterior $p$
\begin{itemize}
\item[-] KL-divergence is a functional: takes
\alert{functions} as an input, returns a positive scalar
\item[-] Measures ``divergence" between two
measures
\end{itemize}
\item[-] Use calculus of variations and theory from
exponential models to derive iterative algorithm
\item[-] See ``An Introduce to Bayesian Inference via Variational
Approximations" for extended introduction (Grimmer, 2011)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Minimize KL-divergence by Maximizing a Lower Bound}

\scriptsize
\begin{eqnarray}
\log p(\boldsymbol{Y}) & = & \log
\sum_{\boldsymbol{\sigma}}\sum_{\boldsymbol{\tau}} \iiiint
p(\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\theta},
\boldsymbol{\sigma}, \boldsymbol{\pi},
\boldsymbol{\tau}|\boldsymbol{Y}) d\boldsymbol{\theta}
d\boldsymbol{\alpha}d\boldsymbol{\beta}d\boldsymbol{\pi} \nonumber
\end{eqnarray}

\begin{eqnarray}
\log p(\boldsymbol{Y}) & = & \log
\sum_{\boldsymbol{\sigma}}\sum_{\boldsymbol{\tau}} \iiiint
p(\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\theta},
\boldsymbol{\sigma}, \boldsymbol{\pi},
\boldsymbol{\tau}|\boldsymbol{Y}) \frac{q(\boldsymbol{\alpha},
\boldsymbol{\beta}, \boldsymbol{\theta}, \boldsymbol{\sigma},
\boldsymbol{\pi}, \boldsymbol{\tau})}{q(\boldsymbol{\alpha},
\boldsymbol{\beta}, \boldsymbol{\theta}, \boldsymbol{\sigma},
\boldsymbol{\pi}, \boldsymbol{\tau})}d\boldsymbol{\theta}
d\boldsymbol{\alpha}d\boldsymbol{\beta}d\boldsymbol{\pi} \nonumber
\end{eqnarray}

\begin{eqnarray}
\log p(\boldsymbol{Y}) & \geq &
\underbrace{\sum_{\boldsymbol{\sigma}}\sum_{\boldsymbol{\tau}}
\iiiint q(\boldsymbol{\alpha}, \boldsymbol{\beta},
\boldsymbol{\theta}, \boldsymbol{\sigma}, \boldsymbol{\pi},
\boldsymbol{\tau}) \log\frac{p(\boldsymbol{\alpha},
\boldsymbol{\beta}, \boldsymbol{\theta}, \boldsymbol{\sigma},
\boldsymbol{\pi},
\boldsymbol{\tau}|\boldsymbol{Y})}{q(\boldsymbol{\alpha},
\boldsymbol{\beta}, \boldsymbol{\theta}, \boldsymbol{\sigma},
\boldsymbol{\pi}, \boldsymbol{\tau})}d\boldsymbol{\theta}
d\boldsymbol{\alpha}d\boldsymbol{\beta}d\boldsymbol{\pi}}_{\mathcal{L}(q)
}. \nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Minimize KL-divergence by Maximizing a Lower Bound}

\begin{eqnarray}
\log p(\boldsymbol{Y}) & =& \mathcal{L}(q) + \text{KL}(q||p)
\nonumber
 \\ \pause
\invisible<1>{\underbrace{\log p(\boldsymbol{Y})}_{\text{fixed
number}} & =& \mathcal{L}(q) +
\underbrace{\text{KL}(q||p)}_{\text{Positive}} \nonumber}
\end{eqnarray}
\pause  \invisible<1-2>{If $\mathcal{L}(q)$ get bigger,
$\text{KL}(q||p)$
get smaller. $\Rightarrow$} \pause \\
\invisible<1-3>{If $\mathcal{L}(q)$ is at a maximum
$\text{KL}(q||p)$ is at a minimum (duals).}
\end{frame}

\begin{frame}
\frametitle{Maximizing $\mathcal{L}(q)$}

Goal: choose $q$ to maximize $\mathcal{L}(q)$.  \\

\begin{eqnarray}
q(\boldsymbol{\alpha})^{\text{old}},
q(\boldsymbol{\beta})^{\text{old}}, q(
\boldsymbol{\theta})^{\text{old}},
q(\boldsymbol{\sigma})^{\text{old}},
q(\boldsymbol{\pi})^{\text{old}}, q(\boldsymbol{\tau})^{\text{old}}.
\nonumber
\end{eqnarray}

Iterative Algorithm:  \\
\footnotesize Choose, $q(\boldsymbol{\pi})^{\text{new}}$ to max
$\mathcal{L}(q)$--holding
$q(\boldsymbol{\theta})^{\text{old}},q(\boldsymbol{\tau})^{\text{old}},q(\boldsymbol{\alpha})^{\text{old}},
q(\boldsymbol{\beta})^{\text{old}},q(\boldsymbol{\sigma})^{\text{old}}$
constant. \\
Choose, $q(\boldsymbol{\theta})^{\text{new}}$ to max
$\mathcal{L}(q)$--holding
$q(\boldsymbol{\pi})^{\text{new}},q(\boldsymbol{\tau})^{\text{old}},q(\boldsymbol{\alpha})^{\text{old}},
q(\boldsymbol{\beta})^{\text{old}},q(\boldsymbol{\sigma})^{\text{old}}$
constant. \\
Choose, $q(\boldsymbol{\tau})^{\text{new}}$ to max
$\mathcal{L}(q)$--holding
$q(\boldsymbol{\theta})^{\text{new}},q(\boldsymbol{\pi})^{\text{new}},q(\boldsymbol{\alpha})^{\text{old}},
q(\boldsymbol{\beta})^{\text{old}},q(\boldsymbol{\sigma})^{\text{old}}$
constant. \\
Choose, $q(\boldsymbol{\alpha})^{\text{new}}$ to max
$\mathcal{L}(q)$--holding
$q(\boldsymbol{\theta})^{\text{new}},q(\boldsymbol{\tau})^{\text{new}},q(\boldsymbol{\pi})^{\text{new}},
q(\boldsymbol{\beta})^{\text{old}},q(\boldsymbol{\sigma})^{\text{old}}$
constant. \\
Choose, $q(\boldsymbol{\beta})^{\text{new}}$ to max
$\mathcal{L}(q)$--holding
$q(\boldsymbol{\theta})^{\text{new}},q(\boldsymbol{\tau})^{\text{new}},q(\boldsymbol{\pi})^{\text{new}},
q(\boldsymbol{\alpha})^{\text{new}},q(\boldsymbol{\sigma})^{\text{old}}$
constant. \\
Choose, $q(\boldsymbol{\sigma})^{\text{new}}$ to max
$\mathcal{L}(q)$--holding
$q(\boldsymbol{\theta})^{\text{new}},q(\boldsymbol{\tau})^{\text{new}},q(\boldsymbol{\pi})^{\text{new}},
q(\boldsymbol{\alpha})^{\text{new}},q(\boldsymbol{\beta})^{\text{new}}$
constant.
\end{frame}

\begin{frame}
\frametitle{Example for $q(\boldsymbol{\pi})^{\text{new}}$} \tiny
\begin{eqnarray}
\mathcal{L}(q) & =& \int q(\boldsymbol{\pi})^{\text{new}}
\underbrace{\left\{ \sum_{\boldsymbol{\sigma}}
\sum_{\boldsymbol{\tau}} \iiint \log p(\boldsymbol{Y},
\boldsymbol{\pi}, \boldsymbol{\alpha}, \boldsymbol{\theta},
\boldsymbol{\tau})
q(\boldsymbol{\sigma})^{\text{old}}q(\boldsymbol{\tau})^{\text{old}}q(\boldsymbol{\theta})^{\text{old}}q(\boldsymbol{\alpha})^{\text{old}}q(\boldsymbol{\beta})^{\text{old}}
d\boldsymbol{\theta} d\boldsymbol{\alpha}
d\boldsymbol{\beta}\right\}}_{\text{E}_{\boldsymbol{\alpha},
\boldsymbol{\tau}, \boldsymbol{\theta}, \boldsymbol{\sigma},
\boldsymbol{\beta} }[\log p(\boldsymbol{Y}, \boldsymbol{\pi},
\boldsymbol{\alpha},
\boldsymbol{\theta}, \boldsymbol{\tau}, \boldsymbol{\beta}, \boldsymbol{\sigma})]}d\boldsymbol{\pi} \nonumber \\
&&- q(\boldsymbol{\pi})^{\text{new}}\log
q(\boldsymbol{\pi})^{\text{new}} + \text{constants} \nonumber
\end{eqnarray}
\normalsize Define
\begin{eqnarray}
\log \tilde{p}(\boldsymbol{\pi}) & = &
\text{E}_{\boldsymbol{\alpha}, \boldsymbol{\tau},
\boldsymbol{\theta}, \boldsymbol{\sigma}, \boldsymbol{\beta} }[\log
p(\boldsymbol{Y}, \boldsymbol{\pi}, \boldsymbol{\alpha},
\boldsymbol{\theta}, \boldsymbol{\tau}, \boldsymbol{\beta},
\boldsymbol{\sigma})] + \text{constants} \nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Example for $q(\boldsymbol{\pi})^{\text{new}}$}
Substituting $\log \tilde{p}(\boldsymbol{\pi})$,
\begin{eqnarray}
& = & \int q(\boldsymbol{\pi})^{\text{new}} \log
\left(\frac{\tilde{p}(\boldsymbol{\pi})}{q(\boldsymbol{\pi})^{\text{new}}}
\right)d\boldsymbol{\pi} \nonumber \\
& = & -
\text{KL}(q(\boldsymbol{\pi})^{\text{new}}||\tilde{p}(\boldsymbol{\pi})
) \nonumber
\end{eqnarray}
$\Rightarrow$ At a maximum when $q(\boldsymbol{\pi})^{\text{new}}
=\tilde{p}(\boldsymbol{\pi}) $.  \\
Equivalently,
\begin{eqnarray}
\log q(\boldsymbol{\pi})^{\text{new}} & = & \log
\tilde{p}(\boldsymbol{\pi}) \nonumber \\
& = & \text{E}_{\boldsymbol{\alpha}, \boldsymbol{\tau},
\boldsymbol{\theta}, \boldsymbol{\sigma}, \boldsymbol{\beta} }[\log
p(\boldsymbol{Y}, \boldsymbol{\pi}, \boldsymbol{\alpha},
\boldsymbol{\theta}, \boldsymbol{\tau}, \boldsymbol{\beta},
\boldsymbol{\sigma})] + \text{constants}\nonumber
\end{eqnarray}
Or,
\begin{eqnarray}
q(\boldsymbol{\pi})^{\text{new}} & = &
\frac{\exp(\text{E}_{\boldsymbol{\alpha}, \boldsymbol{\tau},
\boldsymbol{\theta}, \boldsymbol{\sigma}, \boldsymbol{\beta} }[\log
p(\boldsymbol{Y}, \boldsymbol{\pi}, \boldsymbol{\alpha},
\boldsymbol{\theta}, \boldsymbol{\tau}, \boldsymbol{\beta},
\boldsymbol{\sigma})])}{\int \exp(\text{E}_{\boldsymbol{\alpha},
\boldsymbol{\tau}, \boldsymbol{\theta}, \boldsymbol{\sigma},
\boldsymbol{\beta} }[\log p(\boldsymbol{Y}, \boldsymbol{\pi},
\boldsymbol{\alpha}, \boldsymbol{\theta}, \boldsymbol{\tau},
\boldsymbol{\beta}, \boldsymbol{\sigma})])d\boldsymbol{\pi}}
\nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
To maximize $\mathcal{L}(q)$ we use the following iterative
algorithm \scriptsize
\begin{eqnarray}
q(\boldsymbol{\sigma})^{\text{new}} & \propto &
\exp\left(\text{E}_{\boldsymbol{\tau}, \boldsymbol{\theta},
\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\pi} }[\log
p(\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\theta},
\boldsymbol{\sigma}, \boldsymbol{\pi}, \boldsymbol{\tau},
\boldsymbol{Y}) ] \right) \nonumber \\
q(\boldsymbol{\tau})^{\text{new}} & \propto &
\exp\left(\text{E}_{\boldsymbol{\sigma}, \boldsymbol{\theta},
\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\pi} }[\log
p(\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\theta},
\boldsymbol{\sigma}, \boldsymbol{\pi}, \boldsymbol{\tau},
\boldsymbol{Y}) ] \right) \nonumber \\
q(\boldsymbol{\theta})^{\text{new}} & \propto &
\exp\left(\text{E}_{\boldsymbol{\sigma}, \boldsymbol{\tau},
\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\pi} }[\log
p(\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\theta},
\boldsymbol{\sigma}, \boldsymbol{\pi}, \boldsymbol{\tau},
\boldsymbol{Y}) ] \right) \nonumber \\
q(\boldsymbol{\alpha})^{\text{new}} & \propto &
\exp\left(\text{E}_{\boldsymbol{\sigma}, \boldsymbol{\tau},
\boldsymbol{\theta}, \boldsymbol{\beta}, \boldsymbol{\pi} }[\log
p(\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\theta},
\boldsymbol{\sigma}, \boldsymbol{\pi}, \boldsymbol{\tau},
\boldsymbol{Y}) ] \right) \nonumber \\
q(\boldsymbol{\beta})^{\text{new}} & \propto &
\exp\left(\text{E}_{\boldsymbol{\sigma}, \boldsymbol{\tau},
\boldsymbol{\theta}, \boldsymbol{\alpha}, \boldsymbol{\pi} }[\log
p(\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\theta},
\boldsymbol{\sigma}, \boldsymbol{\pi}, \boldsymbol{\tau},
\boldsymbol{Y}) ] \right) \nonumber \\
q(\boldsymbol{\pi})^{\text{new}} & \propto &
\exp\left(\text{E}_{\boldsymbol{\sigma}, \boldsymbol{\tau},
\boldsymbol{\theta}, \boldsymbol{\alpha}, \boldsymbol{\beta} }[\log
p(\boldsymbol{\alpha}, \boldsymbol{\beta}, \boldsymbol{\theta},
\boldsymbol{\sigma}, \boldsymbol{\pi}, \boldsymbol{\tau},
\boldsymbol{Y}) ] \right) \nonumber
\end{eqnarray}
\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\sigma})_{it}$}
$q(\boldsymbol{\sigma})_{it}$ is a Multinomial$(1,
\boldsymbol{c}_{it})$ distribution, with typical parameter $c_{its}$

\scriptsize

\begin{eqnarray}
\boldsymbol{c}_{its} & \propto & \exp\left\{ \text{E}[\log \beta_s]
+ \log \Gamma (\sum_{k=1}^{K} \alpha_{ks} ) - \sum_{k=1}^{K} \log
\Gamma (\alpha_{ks})  +
            \sum_{k=1}^{K} (\alpha_{ks} - 1 )\text{E}[\log \pi_{itk}]    \right\}. \nonumber
\end{eqnarray}
\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\tau})_{ijt} $ }
$q(\boldsymbol{\tau})_{ijt} $ is a Multinomial$(1,
\boldsymbol{r}_{ijt})$ distribution with typical parameter,
\scriptsize

\begin{eqnarray}
r_{ijtk} & \propto & \exp \left\{\text{E}[\log \pi_{itk}] +
\sum_{w=1}^{W} y_{ijtw}\text{E}[\log \theta_{kw}] \right\}.\nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\pi})_{it}$}
$q(\boldsymbol{\pi})_{it}$ is a
Dirichlet($\boldsymbol{\gamma}_{it}$) distribution, with typical
parameter $\gamma_{itk}$ equal to

\scriptsize
\begin{eqnarray}
\gamma_{itk}  & = & \sum_{s=1}^{S} c_{its} \alpha_{sk}^{*} +
\sum_{j=1}^{D_{it}} r_{ijtk} \nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\theta})_{k}$}
$q(\boldsymbol{\theta})_{k}$ is a Dirichlet($\boldsymbol{\eta}_k$)
distribution, with typical parameter equal to, \scriptsize
\begin{eqnarray}
\eta_{kw} & = & \lambda_w + \sum_{i=1}^{n} \sum_{t=2005}^{2007}
\sum_{j=1}^{D_{it}}r_{itjk}y_{itw} \nonumber
\end{eqnarray}
\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\beta} )$}
$q(\boldsymbol{\beta} )$ is a Dirichlet$(\boldsymbol{\phi})$
distribution, with typical parameter $\phi_s$ equal to,\scriptsize
\begin{eqnarray}
\phi_s & = & 1 + \sum_{i=1}^{n} \sum_{t=2005}^{2007} c_{its}
\nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Completing $q(\boldsymbol{\sigma})_{it}$ and
$q(\boldsymbol{\tau})_{ijt}$}

Finishing $q(\boldsymbol{\sigma})_{it}$:
\begin{itemize}
\item[-] $\text{E}[\log \beta_s] = \Psi(\phi_s) -
\Psi(\sum_{z=1}^{S}\phi_{z})$ where $\Psi(\cdot)$ is the digamma
function (the derivative of the gamma function)
\item[-]  $\text{E}[\log
\pi_{itk}] =\Psi(\gamma_{itk}) - \Psi(\sum_{z=1}^{K} \gamma_{itz})$
\end{itemize}

Finishing $q(\boldsymbol{\tau})_{ijt}$
\begin{itemize}
\item[-]  $\text{E}[\log \theta_{kw}] =
\Psi(\eta_{kw} ) - \Psi(\sum_{z=1}^{w} \eta_{kz}   ) $.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Update Steps for $\boldsymbol{\alpha}_{s}$
}(Newton-Raphson, Minka 2000)
\begin{itemize}
\item[-]  Define
$N_{s} = \sum_{i=1}^{n} \sum_{t=2005}^{2007} c_{its}$.
\end{itemize}
Differentiating with respect to $\alpha_{ks}$ shows that \scriptsize
\begin{eqnarray}
\frac{\partial \log
q(\boldsymbol{\alpha})_{k}^{\text{new}}}{\partial \alpha_{ks} } & =
& - \frac{1}{\lambda} + N_{s} \Psi(\sum_{k=1}^{K} \alpha_{ks} ) -
N_{s} \Psi(\alpha_{ks}) + \sum_{i=1}^{n} \sum_{t=2005}^{2007}
c_{its} \frac{\left(\Psi(\gamma_{itk}) - \Psi(\sum_{z=1}^{K}
\gamma_{itz} )   \right)}{N{s}} \nonumber
\end{eqnarray}
\normalsize

\begin{itemize}
\item[-] Call Gradient $\frac{\partial \log
q(\boldsymbol{\alpha})_{k}^{\text{new}}}{\partial
\boldsymbol{\alpha}_k}$.
\item[-] Define $\boldsymbol{\text{H}}$ as the Hessian (matrix of second
derivatives).

\item[-] Diagonal element $h_{jj} = N_{s}
\Psi^{'} (\sum_{k=1}^{K} \alpha_{ks}  ) - N_{s} \Psi^{'}
(\alpha_{js} ) $ where $\Psi^{'} (\cdot)$ is the trigamma function
\item[-] Off-diagonal element ($a \neq b$)
$h_{ab} = N_{z} \Psi^{'} (\sum_{k=1}^{K} \alpha_{ks})$.
\end{itemize}

 For each $s$
we iterate,

\scriptsize
\begin{eqnarray}
\boldsymbol{\alpha}_{s}^{\text{new}} & = &
\boldsymbol{\alpha}^{\text{old}}_{s} -
\boldsymbol{\text{H}}^{-1}\frac{\partial \log
q(\boldsymbol{\alpha})_{k}^{\text{new}}}{\partial
\boldsymbol{\alpha}_k} \nonumber
\end{eqnarray}
\normalsize until convergence
\end{frame}

\begin{frame}

%\tiny
%\begin{table}[hbt!]
%\caption{Pseudo Code for Variational Approximation}\label{code}
\footnotesize
% \framebox[6.35in]{
\begin{tabular}{l}
Initialize $\boldsymbol{\gamma}_{it}^{\text{old}}$ (for all $i$ and
$t$), $\boldsymbol{\eta}_k^{\text{old}}$ (for all $k$),
$\boldsymbol{\phi}^{\text{old}}$,
$\boldsymbol{\alpha}_s^{\text{old}}$ (for all $s$). \\
Do until convergence in lower-bound. \\
- \indent  for all $i$, $t$, $j$ and $k$, set \\
$ r_{ijtk}^{\text{new}} \propto \exp\left(
\Psi(\gamma_{itk}^{\text{old}}) - \Psi(\sum_{z=1}^{K}
\gamma_{itz}^{\text{old}}) + \sum_{w=1}^{W}y_{ijtw} \left[
\Psi(\eta_{kw}^{\text{old}} ) - \Psi(\sum_{z=1}^{W}\eta_{kz}^{\text{old}} )\right] \right)$ \\
-\indent for all $i$,$t$, and $s$ set \\
$ c_{its}^{\text{new}} \propto \exp(\Psi(\phi_s^{\text{old}}) -
\Psi(\sum_{z=1}^{S}\phi_s^{\text{old}}) + \log \Gamma(\sum_{k=1}^{K}
\alpha_{ks}^{\text{old}}  ) -
\sum_{k=1}^{K} \log \Gamma (\alpha_{ks}^{\text{old}} )$ \\
\hspace{2in}$+ \sum_{k=1}^{K} (\alpha_{ks}^{\text{old}}-1)[\Psi(\gamma_{itk}^{\text{old}}) - \Psi(\sum_{z=1}^{K} \gamma_{itz}^{\text{old}})] )$ \\
- \indent for all  $i$, $t$ , and $k$ set  \\
$\gamma_{itk}^{\text{new}}  =  \sum_{s=1}^{S}c_{its}^{\text{new}}\alpha_{ks}^{\text{old}} + \sum_{j=1}^{D_{it}} r_{ijtk}^{\text{new}} $\\
- \indent for all $k$ and $w$ set \\
$\eta_{kw}^{\text{new}} = \lambda_w +
\sum_{i=1}^{n}\sum_{t=2005}^{2007}
\sum_{j=1}^{D_{it}} r_{ijtk}^{\text{new}} y_{ijtw}$ \\
-\indent for all $s$ set \\
$\phi_s^{\text{new}}  = 1 + \sum_{i=1}^{n} \sum_{t=2005}^{2007} c_{its}^{\text{new}}$\\
- For all $s$ obtain $\boldsymbol{\alpha}_s^{\text{new}}$ using Newton-Raphson algorithm. \\
- Evaluate lower-bound.  \\
If converged:\\
 Return posterior approximation.
\end{tabular}%}
%\end{table}

\end{frame}

\begin{frame}
$</$ Variational Approximation $>$
\end{frame}

\begin{frame}

$<$ Model Selection $>$
\end{frame}

\begin{frame}
\frametitle{Number of Topics}
\begin{enumerate}
\item[1)] Substantive search (about 40-50)
\item[2)] 10-fold cross-validation.  Loss function, approximate predictive
posterior
\begin{eqnarray}
p(\hat{\boldsymbol{y}}| \boldsymbol{Y}) & \approx &
\sum_{\widehat{\boldsymbol{\tau}}} \iint p(\hat{\boldsymbol{y}}|
\hat{\boldsymbol{\tau}}, \boldsymbol{\theta})
p(\hat{\boldsymbol{\tau}}|\boldsymbol{\pi})
q(\boldsymbol{\theta}|\boldsymbol{\eta}) q(\boldsymbol{\pi})
d\boldsymbol{\theta} d\boldsymbol{\pi} \nonumber
\end{eqnarray}

\item[3)] Convergence with Nonparametric Bayesian model (Dirichlet
process prior)
\end{enumerate}

\Large All converge on about 44 topics

\end{frame}

\begin{frame}
\frametitle{Number of Styles}

BIC $= 2 \log p(\boldsymbol{Y})$

\begin{itemize}
\item[1)] BIC $\approx 2 (\mathcal{L}(q) + \log K! + \log S!) - (K \times
S)(n)$
\item[2)] BIC $ \approx 2 \log p(\boldsymbol{Y}|\bar{\boldsymbol{\pi}},\bar{\theta},\bar{\boldsymbol{\tau}} ) - (K \times
S)(n)$
\end{itemize}

\end{frame}

\begin{frame}

$</$ Model Selection $>$
\end{frame}

\begin{frame}

Hierarchy of Topics

\end{frame}

\begin{frame}
\frametitle{Posterior Distribution}

\begin{tiny}
\begin{eqnarray}
p(\boldsymbol{\alpha}, \boldsymbol{\pi}, \boldsymbol{\eta} , \boldsymbol{\beta}, \boldsymbol{\sigma}, \boldsymbol{\mu}, \boldsymbol{\tau}| \boldsymbol{X} ) & \propto & \prod_{m=1}^{M} c(\kappa) \exp\left(\kappa \boldsymbol{\eta}_{m}^{'} \boldsymbol{\frac{1}{\sqrt{J}}} \right) \times \prod_{m=1}^{M} \prod_{k=1}^{K} \left[\beta_{m} c(\kappa)  \exp\left(\kappa \boldsymbol{\mu}_{k}^{'} \boldsymbol{\eta}_{m} \right) \right ]^{\sigma_{mk}} \prod_{k=1}^{K} \exp(-\alpha_{k} ) \times \nonumber \\
&& \prod_{i=1}^{48} \left[\frac{\Gamma (\sum_{k=1}^{K} \alpha_{k} )}{\prod_{k=1}^{K} (\alpha_{k} ) } \prod_{k=1}^{K} \pi_{ik}^{\alpha_{k}-1} \times \prod_{j=1}^{D_{i}} \prod_{k=1}^{K} \left[\pi_{ik} c(\kappa) \exp(\kappa \boldsymbol{x}^{*}_{ij} \boldsymbol{\mu}_{k} \right]^{\tau_{ijk} } \right] \label{e:post}
\end{eqnarray}
\end{tiny}

Which we approximate with:
\begin{tiny}
\begin{eqnarray}
q(\boldsymbol{\alpha}, \boldsymbol{\pi}, \boldsymbol{\eta} , \boldsymbol{\beta}, \boldsymbol{\sigma}, \boldsymbol{\mu}, \boldsymbol{\tau}) & = & q(\boldsymbol{\alpha}) q(\boldsymbol{\pi}) q(\boldsymbol{\eta} ) q(\boldsymbol{\beta}) q(\boldsymbol{\sigma}) q(\boldsymbol{\mu}) q(\boldsymbol{\tau}) \label{e:approx} \\
& = & q(\boldsymbol{\alpha}) \prod_{i=1}^{48} q(\boldsymbol{\pi})_{i} \prod_{m=1}^{M}q(\boldsymbol{\eta} )_{m} q(\boldsymbol{\beta}) \prod_{k=1}^{K} q(\boldsymbol{\sigma})_{k}  \prod_{k=1}^{K} q(\boldsymbol{\mu})_{k} \prod_{i=1}^{48}\prod_{j=1}^{D_{i}} q(\boldsymbol{\tau})_{ij} \nonumber 
\end{eqnarray}
\end{tiny}
\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\sigma})_{k}$}
$q(\boldsymbol{\sigma})_{k}$ is a Multinomial(1, $\boldsymbol{c}_{k}$ ) where typical element $c_{mk}$ is equal to

\begin{eqnarray}
c_{mk} & \propto & \exp\left(\text{E}[\log \beta_{m} ]  +\text{E}[ \kappa \boldsymbol{\mu}_{k} \boldsymbol{\eta}_{m} ]  \right). \nonumber
\end{eqnarray}
We will complete the update step when we have determined the remaining forms of the distribution

\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\tau})_{ij}$}
$q(\boldsymbol{\tau})_{ij}$ is a Multinomial(1, $\boldsymbol{r}_{ij}$, with typical element of $r_{ijk}$ equal to
\begin{eqnarray}
r_{ijk} & \propto & \exp\left(\text{E}[\log \pi_{ik} ]  + \text{E}[\kappa \boldsymbol{y}^{*}_{ij} \boldsymbol{\mu}_{k}] \right) \nonumber
\end{eqnarray}
Again, as we complete the parametric forms of the other update steps we can complete this update equation.
\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\pi})_{i}$ }
$q(\boldsymbol{\pi})_{i}$ is a Dirichlet$(\boldsymbol{\gamma}_{i})$ distribution, where typical element $\gamma_{ik}$ is equal to
\begin{eqnarray}
\gamma_{ik} & = & \alpha_{k} + \sum_{j=1}^{D_{i}}r_{ijk}  \nonumber
\end{eqnarray}
\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\beta})$}

$q(\boldsymbol{\beta})$ is a Dirichlet($\boldsymbol{\phi}$) distribution with typical parameter $\phi_{m}$ equal to
\begin{eqnarray}
\phi_{m} & = & 1 + \sum_{k=1}^{K} c_{mk} \nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\eta})_{m}$ }
Given the complications of taking expectations with the vMF distribution, we instead provide maximization steps for the vMF parameters.  To obtain the form of the updates we follow the derivation outlined in Banerjee et al (2005).  To do this, we take the log of the posterior distribution and identify the parameters that depend upon $\boldsymbol{\eta}_{m}$.
\begin{eqnarray}
\log(p(\boldsymbol{\eta}_{m} ) & = & \sum_{k=1}^{K} c_{km} \kappa \boldsymbol{\mu}_{k} \boldsymbol{\eta}_{m} + \kappa \boldsymbol{\eta}_{m}\boldsymbol{\frac{1}{\sqrt{J}}}  + \text{constants} \nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\eta})_{m}$ }

To set up the constrained optimization we also introduce the Langragian $\lambda$, with the constraint that $\boldsymbol{\eta}_{m}^{'} \boldsymbol{\eta}_{m}$  = 1,

\begin{eqnarray}
\log(p(\boldsymbol{\eta}_{m} ) &  \propto & \sum_{k=1}^{K} c_{km} \kappa \boldsymbol{\mu}_{k} \boldsymbol{\eta}_{m} + \kappa \boldsymbol{\eta}_{m}\boldsymbol{\frac{1}{\sqrt{J}}}  - \lambda(\boldsymbol{\eta}_{m}^{'} \boldsymbol{\eta}_{m} - 1). \nonumber
\end{eqnarray}
Differentiating with respect to $\boldsymbol{\eta}_{m}$, setting equal to zero and solving yields
\begin{eqnarray}
\frac{\kappa \left(\sum_{k=1}^{K} c_{mk} \boldsymbol{\mu}_{k}  + \boldsymbol{\frac{1}{\sqrt{J}}} \right) }{2 \lambda } & = & \boldsymbol{\eta}_{m} \label{e:Start}
\end{eqnarray}
\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\eta})_{m}$ }
If we differentiate with respect to $\lambda$ and solve we see that $\boldsymbol{\eta}_{m}^{'} \boldsymbol{\eta}_{m} = 1$ or that $||\boldsymbol{\eta}_{m}^{'} \boldsymbol{\eta}_{m}|| =1$.  Substituting this into Equation \ref{e:Start} we have,
\begin{eqnarray}
\frac{\kappa}{2 \lambda} \left( \left(\sum_{k=1}^{K} c_{mk} \boldsymbol{\mu}_{k}  + \boldsymbol{\frac{1}{\sqrt{J}}} \right)^{'} \left(\sum_{k=1}^{K} c_{mk} \boldsymbol{\mu}_{k}  + \boldsymbol{\frac{1}{\sqrt{J}}} \right) \right)^{1/2}  & = & 1 \nonumber \\
\frac{\kappa ||\sum_{k=1}^{K} c_{mk} \boldsymbol{\mu}_{k}  + \boldsymbol{\frac{1}{\sqrt{J}}} || }{2} & = & \lambda \nonumber
\end{eqnarray}

Doing a final substitution we have
\begin{eqnarray}
\boldsymbol{\eta}^{*}_{m} & = & \frac{\sum_{k=1}^{K} c_{mk} \boldsymbol{\mu}_{k}  + \boldsymbol{\frac{1}{\sqrt{J}}}}{||\sum_{k=1}^{K} c_{mk} \boldsymbol{\mu}_{k}  + \boldsymbol{\frac{1}{\sqrt{J}}}||} \nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Update for $q(\boldsymbol{\mu})_{k}$ }
Following a very similar set of derivations, the update step for $\boldsymbol{\mu}_{k}$ is
\begin{eqnarray}
\boldsymbol{\mu}_{k}^{*} & = & \frac{ \sum_{i=1}^{48}\sum_{j=1}^{D_{i}} r_{ijk} \boldsymbol{x}_{ij}^{*}  + \sum_{m=1}^{M} c_{mk} \boldsymbol{\eta}^{*}_{m} }{||\sum_{i=1}^{48}\sum_{j=1}^{D_{i}} r_{ijk} \boldsymbol{x}_{ij}^{*}  + \sum_{m=1}^{M} c_{mk} \boldsymbol{\eta}^{*}_{m}|| } \nonumber
\end{eqnarray}
\end{frame}

\begin{frame}
\frametitle{Completing updates for $q(\boldsymbol{\sigma})_{k}$ and $q(\boldsymbol{\tau})_{ij}$}
Given the forms E$[\log \beta_{m} ] = \Psi(\phi_{m} ) - \Psi(\sum_{m=1}^{M} \phi_{m} ) $ and E$[\log \pi_{ik} ] = \Psi(\gamma_{ik} ) - \Psi(\sum_{k=1}^{K} \gamma_{ik} ) $ where $\Psi(\cdot)$ is the Digamma function.

\end{frame}
\begin{frame}
\frametitle{Update for q$(\boldsymbol{\alpha})$}

A closed form update for the $\boldsymbol{\alpha}$ parameters is unavailable.  So we use the Newton-Raphson algorithm outlined in Minka (2000) and Blei, Ng, and Jordan (2003).
\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/tc14.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{November 6th, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Supervised Learning}

\begin{itemize}
\item[1)] Task
\begin{itemize}
\item[-] Classify documents to pre existing categories
\item[-] Measure the proportion of documents in each category
\end{itemize}
\item[2)] Objective function
\begin{itemize}
\item[-] Suppose we have $K$ categories.  
\item[-] Select $N_{\text{train}}$ document to hand-label, $Y_{i} = k$, $\boldsymbol{Y} = (Y_{1}, Y_{2}, \hdots, Y_{N_{\text{train}}})$
\begin{eqnarray}
\boldsymbol{Y} & = & f(\boldsymbol{X}, \boldsymbol{\theta}) \nonumber 
\end{eqnarray}

\end{itemize}
\item[3)] Optimization
\begin{itemize}
\item[-] Method specific: MLE, Bayesian, EM, ...
\item[-] We learn $\widehat{\boldsymbol{\theta}}$
\end{itemize}
\item[4)] Validation
\begin{itemize}
\item[-] Obtain predicted fit for new data $f(\boldsymbol{X}_{i}, \widehat{\boldsymbol{\theta}})$
\item[-] Examine prediction performance$\leadsto$ compare classification to \alert{gold standard}
\end{itemize}

\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Supervised Learning}

Clustering and Topic Models:
\begin{itemize}
\item[-] Models for \alert{discovery} 
\begin{itemize}
\item[-] Infer categories
\item[-] Infer document assignment to categories
\item[-] \alert{Pre-estimation}: relatively little work
\item[-] \alert{Post-estimation}: extensive validation testing
\end{itemize}
\end{itemize}
\pause 
\invisible<1>{Supervised Methods: } \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Models for \alert{categorizing texts}} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Know (develop) categories before hand} \pause 
\invisible<1-4>{\item[-] Hand coding: assign documents to categories
\item[-] Infer: new document assignment to categories (distribution of documents to categories)} \pause 
\invisible<1-5>{\item[-] \alert{Pre-estimation}: extensive work constructing categories, building classifiers
\item[-] \alert{Post-estimation}: relatively little work} 
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Supervised Learning}

Today:\pause 
\begin{itemize}
\invisible<1>{\item[-] How to generate \alert{valid} hand coding categories} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Assessing coder performance
\item[-] Assessing disagreement among coders
\item[-] Evidence coders perform well} \pause 
\end{itemize}
\invisible<1-3>{\item[-] Supervised Learning Methods: \alert{Naive Bayes} } \pause 
\invisible<1-4>{\item[-] Assessing Model Performance}  \pause
\end{itemize}

\invisible<1-5>{Next week:} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Supervised Learning Methods: Lasso, Ridge, Support Vector Machines, and ReadMe} \pause 
\invisible<1-7>{\item[-] Ensemble methods: combining the results of many supervised algorithms} \pause 
\invisible<1-8>{\item[-] \alert{Cross validation}: } \pause 
\begin{itemize}
\invisible<1-9>{\item[-] \alert{Replicate classification exercise, with data} 
\item[-] Avoid over training data: Balance \alert{bias} and \alert{variance} in model selection
\item[-] \alert{Super learning}: optimal ensemble methods } \pause 
\end{itemize}
\end{itemize}

\invisible<1-10>{\alert{Methods generalize beyond text} }

\end{frame}

\begin{frame}
\frametitle{Components to Supervised Learning Method}

 \pause 
\begin{itemize}
\invisible<1>{\item[1)] Set of \alert{categories}  } \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Credit Claiming, Position Taking, Advertising
\item[-] Positive Tone, Negative Tone
\item[-] Pro-war, Ambiguous, Anti-war} \pause 
\end{itemize}
\invisible<1-3>{\item[2)] Set of \alert{hand-coded} documents } \pause 
\begin{itemize}
\invisible<1-4>{\item[-] Coding done by human coders
\item[-] \alert{Training} Set: documents we'll use to learn how to code
\item[-] \alert{Validation} Set: documents we'll use to learn how well we code } \pause 
\end{itemize}
\invisible<1-5>{\item[3)] Set of \alert{unlabeled} documents} \pause 
\invisible<1-6>{\item[4)] Method to extrapolate from hand coding to unlabeled documents} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{How Do We Generate Coding Rules and Categories?}

\pause 
\invisible<1>{\alert{Challenge}: coding rules/training coders to maximize coder performance} \pause \\
\invisible<1-2>{\alert{Challenge}: developing a clear set of categories} \pause 
\begin{itemize}
\invisible<1-3>{\item[1)] Limits of Humans:} \pause  
\begin{itemize}
\invisible<1-4>{\item[-] Small working memories
\item[-] Easily distracted
\item[-] Insufficient motivation} \pause 
\end{itemize}
\invisible<1-5>{\item[2)] Limits of Language:} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Fundamental ambiguity in language [careful analysis of texts]
\item[-] Contextual nature of language} 
\end{itemize}
\end{itemize}

\pause

\invisible<1-7>{For supervised methods to work:  maximize coder agreement } \pause 
\begin{itemize}
\invisible<1-8>{\item[1)] Write careful (and brief) coding rules } \pause 
\begin{itemize}
\invisible<1-9>{\item[-] Flow charts help simplify problems } \pause 
\end{itemize}
\invisible<1-10>{\item[2)] Train coders to remove ambiguity, misinterpretation}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{How Do We Generate Coding Rules?}

Iterative process for generating coding rules:\pause 
\begin{itemize}
\invisible<1>{\item[1)] Write a set of coding rules} \pause 
\invisible<1-2>{\item[2)] Have coders code documents (about 200) } \pause 
\invisible<1-3>{\item[3)] Assess coder agreement } \pause 
\invisible<1-4>{\item[4)] Identify sources of disagreement, repeat }
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{How Do We Identify Coding Disagreement?}

\alert{Many} measures of inter-coder agreement\\
Essentially attempt to summarize a \alert{confusion} matrix\\

\begin{tabular}{l|l|l|l|l||l}
\hline
 & Cat 1& Cat 2 & Cat 3 & Cat 4  & Sum, Coder 1\\
 \hline
 Cat 1 &  \textbf{30}  & 0      &  \alert{1}          & 0         &       31             \\
 \hline
 Cat 2 & 1   &     \textbf{1}  &      0	      &   0        & 	2			\\
 \hline
 Cat 3&  0  &   0    &  \textbf{1}           &   0        & 1				\\
 \hline
 Cat 4  &  \alert{3} 	&  1   &  0      &  \textbf{7}    &   11        				\\
 \hline\hline
 Sum, Coder 2& 34   &  2     &  2          &   7        & 		Total: \textbf{45}		\\ 
 \hline
\end{tabular}

\begin{itemize}
\item[-] \textbf{Diagonal}: coders agree on document
\item[-] \alert{Off-diagonal} : coders disagree (confused) on document 
\end{itemize}

\alert{Generalize} across ($k$) coders:
\begin{itemize}
\item[-]  $\frac{k (k-1) }{2} $ pairwise comparisons
\item[-] $k$ comparisons: Coder A against All other coders
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{How Do We Identify Coding Disagreements?}

During coding development phase/coder assessment phase, \alert{full} confusion matrices help to identify
\begin{itemize}
\item[-] Ambiguity
\item[-] Coder slacking
\end{itemize}
Example: 3 Coders, 8 categories.

\only<2>{\scalebox{0.5}{\includegraphics{Coder1.png}}}
\only<3>{\scalebox{0.5}{\includegraphics{Coder2.png}}}
\only<4>{\scalebox{0.5}{\includegraphics{Coder3.png}}}

\end{frame}

\begin{frame}
\frametitle{Example Coding Document}

8 part coding scheme
\begin{itemize}
\item[-] \alert{Across Party Taunting}: explicit public and negative attacks on the other party or its members
\item[-] \alert{Within Party Taunting}: explicit public and negative attacks on the same party or its members [for 1960's politics]
\item[-] \alert{Other taunting}: explicit public and negative attacks not directed at a party
\item[-] \alert{Bipartisan support}: praise for the other party
\item[-] \alert{Honorary Statements}: qualitatively different kind of speech
\item[-] \alert{Policy speech}: a speech without taunting or credit claiming
\item[-] \alert{Procedural}
\item[-] \alert{No Content}: (occasionally occurs in CR) 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Example Coding Document}

\scalebox{0.5}{\includegraphics{TauntingFig.png}}

\end{frame}

\begin{frame}
\frametitle{How Do We Summarize Confusion Matrix?}

Lots of statistics to summarize confusion matrix:
\begin{itemize}
\item[-] \alert{Most common}: intercoder agreement 
\end{itemize}

\begin{eqnarray}
\text{Inter Coder}(A, B) & = & \frac{\text{No. (Coder A \& Coder B agree) }  } { \text{No. Documents}  } \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}

\alert{Liberal} measure of agreement: \pause 
\begin{itemize}
\invisible<1>{\item[-] Some agreement by \alert{chance}} \pause 
\invisible<1-2>{\item[-] Consider coding scheme with two categories \\
 $\{$ Class 1, Class 2$\}$. } \pause
\invisible<1-3>{\item[-] Coder $A$ and Coder $B$ flip a (biased coin).   \\
$($ Pr(Class 1) = 0.75, Pr(Class 2) = 0.25 $)$ } \pause
\invisible<1-4>{\item[-] Inter Coder reliability: \alert{0.625 } } \pause 
\end{itemize}

\invisible<1-5>{What to do?} \pause \\
\invisible<1-6>{Suggestion: \alert{Subtract off amount expected by chance:} } \pause 
\begin{itemize}
\invisible<1-7>{\item[]$\text{Inter Coder} (A,B)_{\text{norm}}  =  $
\item[]$   \frac{\text{No. (Coder A \& Coder B agree)} - \text{No. Expected by Chance}  }   { \text{No. Documents}  }$  } \pause 
\end{itemize}

\invisible<1-8>{\alert{Question}: what is amount expected by chance? } \pause 
\begin{itemize}
\invisible<1-9>{\item[-] $\frac{1}{\# \text{Categories}}$ ? 
\item[-] Avg Proportion in categories across coders?  (Krippendorf's Alpha)  } \pause 
\end{itemize}

\invisible<1-10>{\alert{Best Practice}: present confusion matrices. } \\

\end{frame}

\begin{frame}
\frametitle{Krippendorf's Alpha}

Define coder reliability as: \pause 
\begin{eqnarray}
\invisible<1>{\alpha & = & 1- \frac{\text{No. Pairwise Disagreements Observed }} {\text{No Pairwise Disagreements Expected By Chance}} \nonumber } \pause 
\end{eqnarray}
\begin{itemize}
\invisible<1-2>{\item[] No. Pairwise Disagreements Observed = observe from data} \pause 
\invisible<1-3>{\item[] No Expected pairwise disagreements: coding by chance, with rate labels used available from data } \pause 
\end{itemize}

\invisible<1-4>{Thinking through expected differences: }\pause 
\begin{itemize}
\invisible<1-5>{\item[-] Pretend I know something I'm trying to estimate
\item[-] How is that we know coders estimate levels well?
\item[-] Have to present correlation statistic: vary assumptions about ``expectations" (from uniform, to data driven)} \pause 
\end{itemize}

\invisible<1-6>{Calculate in {\tt R} with {\tt concord} package and function {\tt kripp.alpha} }

\end{frame}

\begin{frame}
\frametitle{How Many To Code By Hand/How Many to Code By Machine}

Next week: we'll discuss how to answer this question systematically for \alert{your data set}.  \\
Rules of thumb: 
\begin{itemize}
\item[-] Hopkins and King (2010): \alert{500 documents} likely sufficient
\item[-] Hopkins and King (2010): \alert{100 documents} may be enough
\item[-] \alert{BUT}: depends on quantity of interest
\item[-] May \alert{REQUIRE} many more documents
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Percent data coded, Error (From Dan Jurafsky) }

\scalebox{0.35}{\includegraphics{TestError.png}}

\end{frame}

\begin{frame}
\frametitle{Three categories of documents}

\alert{Hand labeled}
\begin{itemize}
\item[-] Training set (what we'll use to estimate model)
\item[-] Validation set (what we'll use to assess model)
\end{itemize}
\alert{Unlabeled}
\begin{itemize}
\item[-] Test set (what we'll use the model to categorize)
\end{itemize}

\alert{Label more documents than necessary to train model}

\end{frame}

\begin{frame}
\frametitle{Methods to Perform Supervised Classification}

\begin{itemize}
\item[-] Use the hand labels to \alert{train} a statistical model.
\item[-] Naive Bayes
\begin{itemize}
\item[-] Shockingly simple application of Bayes' rule
\item[-] Shockingly useful$\leadsto$ often default classifier
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Naive Bayes and General Problem Setup}

Suppose we have document $i$, $(i=1, \hdots, N)$ with $J$ features \pause \\
\invisible<1>{$\boldsymbol{x}_i = (x_{1i}, x_{2i}, \hdots, x_{Ji} ) $} \pause \\
\invisible<1-2>{Set of $K$ categories.  Category $k$ $(k=1, \hdots, K)$ \\
$\{C_{1}, C_{2}, \hdots, C_{K} \}$} \pause\\
\invisible<1-3>{Subset of labeled documents $\boldsymbol{Y} = (Y_{1}, Y_{2}, \hdots, Y_{N_{\text{train}}})$ where $Y_{i} \in \{C_{1}, C_{2}, \hdots, C_{K} \}$.}\pause \\
\invisible<1-4>{\alert{Goal}: classify every document into \alert{one} category. } \pause  \\
\invisible<1-5>{Learn a function that maps from space of (possible) documents to categories} \pause \\
\invisible<1-6>{To do this: use hand coded observations to estimate (train) regression model } \pause \\
\invisible<1-7>{Apply model to test data, classify those observations}

\end{frame}

\begin{frame}
\frametitle{Naive Bayes and General Problem Setup (Jurafsky Inspired Slide) }

Goal: For each document $\boldsymbol{x}_i$, we want to infer most likely \alert{category} \pause \\

\begin{eqnarray}
\invisible<1>{C_{\text{Max} }  & = & \text{arg max}_{k} p(C_k | \boldsymbol{x}_{i} ) \nonumber } \pause 
\end{eqnarray}

\invisible<1-2>{We're going to use Bayes' rule to estimate $p(C_k| \boldsymbol{x}_i)$.} \pause 
\begin{eqnarray}
\invisible<1-3>{p(C_k| \boldsymbol{x}_i ) & = &\text{     } \frac{p(C_k, \boldsymbol{x}_i)}{p(\boldsymbol{x}_i )}}\pause \nonumber \\
	\only<1-5>{\invisible<1-4>{& = & \text{     } \frac{ p(C_k) p(\boldsymbol{x}_i|C_k) }  { p(\boldsymbol{x}_i)  } \nonumber } \pause \\}
	\only<6>{\invisible<1-5>{ & = &\text{     } \frac{ \overbrace{p(C_k)}^{\text{Proportion in $C_{k}$}} \underbrace{p(\boldsymbol{x}_i|C_k)}_{\text{Language model}}  }  { p(\boldsymbol{x}_i)  } \nonumber } }
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Naive Bayes and Optimization (Jurafsky Inspired Slide) } 
\pause 
\begin{eqnarray}
\invisible<1>{C_{\text{Max} } & = & \text{arg max}_{k} \text{      } p(C_k| \boldsymbol{x}_i )} \pause  \nonumber \\
\invisible<1-2>{C_{\text{Max} } & = & \text{arg max}_{k} \text{      } \frac{ p(C_k)p(\boldsymbol{x}_i|C_k)  }  { p(\boldsymbol{x}_i)  } } \pause \nonumber \\
\invisible<1-3>{C_{\text{Max} } & = & \text{arg max}_{k} \text{      } p(C_k) p(\boldsymbol{x}_i|C_k) } \pause \nonumber 
\end{eqnarray}

\invisible<1-4>{Two probabilities to estimate:} \pause  
\begin{itemize}
\invisible<1-5>{\item[] $p(C_k) = \frac{\text{No. Documents in } k } {\text{No. Documents } } $ (training set)} \pause 
\invisible<1-6>{\item[] $p(\boldsymbol{x}_i|C_k) $ \alert{complicated} without assumptions} \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Imagine each $x_{ij}$ just binary indicator.  Then $2^{J}$ possible $\boldsymbol{x}_i$ documents} \pause 
\invisible<1-8>{\item[-] Simplify: assume each feature is independent } \pause 
\end{itemize}
\end{itemize}
\begin{eqnarray}
\invisible<1-9>{p(\boldsymbol{x}_i|C_k) & = & \prod_{j=1}^{J} p(x_{ij} | C_k)  \nonumber}  
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Naive Bayes and Optimization (Jurafsky Inspired Slide) }

Two components to estimation:
\begin{itemize}
\item[-] $p(C_k) = \frac{\text{No. Documents in } k } {\text{No. Documents } } $  (training set)
\item[-] $p(\boldsymbol{x}_i|C_k) = \prod_{j=1}^{J} p(x_{ij} | C_k)$ \pause 
\end{itemize}

\invisible<1>{Maximum likelihood estimation (training set): } \pause 
\begin{eqnarray}
\invisible<1-2>{p(x_{im} = z | C_k ) & = & \frac{ \text{No( Docs$_{ij}$ = z and C = C$_k$ ) }  } { \text{No(C= C$_k$)}  } } \pause   \nonumber 
\end{eqnarray}

\invisible<1-3>{\alert{Problem}: What if \text{No( Docs$_{ij}$ = z and C = C$_k$ ) } = 0 ?} \pause 
\invisible<1-4>{$\prod_{j=1}^{J} p(x_{ij} | C_k) = 0 $}

\end{frame}

\begin{frame}
\frametitle{Naive Bayes and General Problem Setup (Jurafsky Inspired Slide) }

\pause

\invisible<1>{Solution: smoothing (Bayesian estimation) } \pause 
\begin{eqnarray}
\invisible<1-2>{p(x_{ij} = z | C_k ) & = & \frac{ \text{No( Docs$_{ij}$ = z and C = C$_k$ ) }   + 1} { \text{No(C= C$_k$)}  + k  } \nonumber } \pause 
\end{eqnarray}

\invisible<1-3>{Algorithm steps:} \pause 
\begin{itemize}
\invisible<1-4>{\item[1)] Learn $\hat{p}(C)$ and $\hat{p}(\boldsymbol{x}_i|C_k)$ on \alert{training data}} \pause 
\invisible<1-5>{\item[2)] Use this to identify most likely $C_k$ for each document $i$ in \alert{test set} } \pause 
\end{itemize}

\begin{eqnarray}
\invisible<1-6>{C_{i} & = & \text{arg max  }_{k} \hat{p}(C_k) \hat{p}(\boldsymbol{x}_i | C_k) \nonumber } \pause 
\end{eqnarray}

\invisible<1-7>{Simple intuition about Naive Bayes:} \pause 
\begin{itemize}
\invisible<1-8>{\item[-] Learn what documents in class $j$ look like} \pause 
\invisible<1-9>{\item[-] Find class $k$ that document $i$ is most similar to} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Naive Bayes and Unigram Language Models}

Assume the following data generating process (should look familiar)
\begin{eqnarray}
\boldsymbol{\pi} & \sim & \text{Dirichlet}(\boldsymbol{\alpha}) \nonumber \\
\boldsymbol{\theta} & \sim & \text{Dirichlet}(\boldsymbol{\lambda}) \nonumber \\
\boldsymbol{\tau}_{i} & \sim & \text{Multinomial}(1, \boldsymbol{\pi}) \nonumber \\
\boldsymbol{x}_{i} | \tau_{ik} = 1 , \boldsymbol{\theta} & \sim & \text{Multinomial}(n_{i}, \boldsymbol{\theta}_{k}) \nonumber 
\end{eqnarray}

\pause

\invisible<1>{If we randomly sample documents $N_{\text{train}}$ and label them $(\boldsymbol{Y})$, then we can estimate } \pause 
\begin{eqnarray}
\invisible<1-2>{\widehat{\pi}_{k} & = & \frac{ \sum_{i=1}^{N} I(Y_{i} = k) + \alpha_{k} }{N_{\text{train}} } \nonumber \\} \pause 
\invisible<1-3>{\widehat{\theta}_{jk} & = & \frac{ \sum_{i=1}^{N} I(Y_{i} = k) x_{ij} + \lambda_{j}  } { \sum_{j=1}^{J} \sum_{i=1}^{N} I(Y_{i} = k) x_{ij}  } \nonumber} 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Naive Bayes and Unigram Language Models}

The probability a new document has $\tau_{ik} = 1$ is then \pause

\begin{eqnarray}
\invisible<1>{p(\tau_{ik} = 1 | \boldsymbol{x}_{i}, \widehat{\boldsymbol{\pi}}, \widehat{\boldsymbol{\theta}}) & \propto & p(\tau_{ik} =1 ) p(\boldsymbol{x}_{i}| \boldsymbol{\theta}, \tau_{ik}=1 )\nonumber \\} \pause 
\invisible<1-2>{& \propto & \widehat{\pi_{k}} \prod_{j=1}^{J} \left(\widehat{\theta}_{jk}\right)^{x_{ij}} \nonumber \\} \pause 
\invisible<1-3>{& \propto & \overbrace{\widehat{\pi_{k}}}^{p(C_{k})} \underbrace{\prod_{j=1}^{J} \left(\widehat{\theta}_{jk}\right)^{x_{ij}}}_{\text{Unigram model}} \nonumber }
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Some {\tt R} Code}

{\tt library(e1071) } \\
{\tt dep<- c(labels, rep(NA, no.testSet)) } \\
{\tt dep<- as.factor(dep) } \\
{\tt out<- naiveBayes(dep$\sim$., as.data.frame(tdm)) } \\
{\tt predicts<- predict(out, as.data.frame(tdm[-training.set,])) }

\end{frame}

\begin{frame}
\frametitle{Assessing Models (Elements of Statistical Learning) }

\begin{itemize}
\item[-] \alert{Model Selection}: tuning parameters to select final model (next week's discussion)
\item[-] \alert{Model assessment} : after selecting model, estimating error in classification
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Comparing Training and Validation Set}

Text classification and model assessment 
\begin{itemize}
\item[-] \alert{Replicate} classification exercise with \alert{validation} set
\item[-] General \alert{principle} of classification/prediction
\item[-] Compare supervised learning labels to hand labels
\end{itemize}

\alert{Confusion matrix}

\end{frame}

\begin{frame}
\frametitle{Comparing Training and Validation Set}

Representation of Test Statistics from Dictionary week (along with some new ones) \\

\begin{tabular}{l|l|l}
 \hline
  & \multicolumn{2}{c}{Actual Label}  \\
  \hline
  Classification (algorithm) &   Liberal & Conservative \\
  \hline 
  Liberal &  \alert{True Liberal} & False Liberal \\
  \hline
  Conservative & False Conservative & \alert{True Conservative} \\
  \hline
  \hline
\end{tabular}

\pause 
\begin{eqnarray}
\invisible<1>{\text{Accuracy} & = & \frac{ \alert{\text{TrueLib} }+ \alert{\text{TrueCons}}  } { \alert{\text{TrueLib} } + \alert{\text{TrueCons}} + \text{FalseLib} + \text{FalseCons} } \nonumber } \pause  \\
\invisible<1-2>{\text{Precision}_{\text{Liberal}} &= &   \frac{ \alert{\text{True Liberal}}    }  { \alert{\text{True Liberal }} + \text{False Liberal}      } } \pause  \nonumber \\
\invisible<1-3>{\text{Recall}_{\text{Liberal} } & = & \frac{ \alert{\text{True Liberal}}   } { \alert{\text{True Liberal}} + \text{False Conservative}   } } \pause  \nonumber \\
\invisible<1-4>{F_{\text{Liberal}} & = & \frac{ 2\text{Precision}_{\text{Liberal}} \text{Recall}_{\text{Liberal} } } { \text{Precision}_{\text{Liberal}} +  \text{Recall}_{\text{Liberal} }} }   \nonumber \pause 
\end{eqnarray}

\end{frame}

% \begin{frame}
% \frametitle{Precision Recall Tradeoff}

% \scalebox{0.4}{\includegraphics{PrecRecall.pdf}}

% \end{frame}

\begin{frame}
\frametitle{ROC Curve}

ROC as a measure of model performance
\begin{eqnarray}
\text{Recall}_{\text{Liberal}} & = & \frac{\text{True Liberal}  } {\text{True Liberal} + \text{False Conservative}  }\nonumber \\
\text{Recall}_{\text{Conservative}} & =  & \frac{\text{True Conservative}  } {\text{True Conservative} + \text{False Liberal}  }\nonumber 
\end{eqnarray}

\alert{Tension}:
\begin{itemize}
\item[-] Everything liberal: Recall$_{\text{Liberal}}$ =1 ; $\text{Recall}_{\text{Conservative}}=0$
\item[-] Everything conservative: Recall$_{\text{Liberal}}$ =0 ; $\text{Recall}_{\text{Conservative}}=1$
\end{itemize}

Characterize Tradeoff: \\
Plot True Positive Rate $\text{Recall}_{\text{Liberal}}$ \\
 False Positive Rate (1 - $\text{Recall}_{\text{Conservative}}$)

\end{frame}

\begin{frame}
\frametitle{Precision/Recall Tradeoff}

\scalebox{0.4}{\includegraphics{ROC.pdf}}

\end{frame}

\begin{frame}
\frametitle{Simple Classification Example}

Analyzing house press releases\\
\alert{Hand Code}: 1,000 press releases
\begin{itemize}
\item[-] Advertising
\item[-] Credit Claiming
\item[-] Position Taking
\end{itemize}
Divide 1,000 press releases into two sets
\begin{itemize}
\item[-] 500: Training set
\item[-] 500: Test set
\end{itemize}

\alert{Initial exploration}: provides baseline measurement at classifier performances \\
\alert{Improve}: through improving model fit
\end{frame}

\begin{frame}
\frametitle{Example from Ongoing Work}

\begin{tabular}{l|lll}
 & \multicolumn{3}{c}{Actual Label} \\
 \hline
Classification (Naive Bayes) & Position Taking & Advertising & Credit Claim. \\ 
Position Taking   &    10  &   0  &   0 \\
Advertising   & 2  & 40  &  2 \\
Credit Claiming   &   80 & 60 & 306\\
\hline\hline
\end{tabular}

\footnotesize
\begin{eqnarray}
\text{Accuracy} & = & \frac{10 + 40 + 306} {500}  = 0.71 \nonumber  \\
\text{Precision}_{PT} & = & \frac{10}{10}  = 1 \nonumber \\
\text{Recall}_{PT} & = & \frac{10}{10 + 2 + 80 }  = 0.11 \nonumber \\
\text{Precision}_{AD} & = & \frac{40}{40 + 2 + 2}  = 0.91 \nonumber \\
\text{Recall}_{AD} & = & \frac{40}{40 + 60 }  = 0.4 \nonumber \\
\text{Precision}_{Credit} & = & \frac{306}{306  + 80 + 60 } = 0.67 \nonumber  \\
\text{Recall}_{Credit} & = & \frac{306}{306 + 2}  = 0.99 \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Fit Statistics in R}

{\tt RWeka} library provides \textbf{Amazing} functionality.\\
\alert{We'll have more to say on how to install, use this next week!}

\end{frame}
\end{document}

### 2017-12-10 resources/text_as_data/tc16.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{November 13th, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{ReadMe: Optimization for a Different Goal (Hopkins and King 2010) }

Naive Bayes, SVM, LASSO, Ridge, $\hdots$: focused on individual document classification. \pause \\
\invisible<1>{But what if we're focused on \alert{proportions only}? } \pause  \\
\invisible<1-2>{Hopkins and King (2010): method for characterizing distribution of classes} \pause  \\
\invisible<1-3>{\alert{Can be much more accurate than individual classifiers}, requires fewer assumptions (\alert{do not need random sample of documents } ) .} \pause   
\begin{itemize}
\invisible<1-4>{\item[-] King and Lu (2008): derive method for characterizing causes of deaths for verbal autopsies }\pause 
\invisible<1-5>{\item[-] Hopkins and King (2010): extend the method to text documents } \pause 
\end{itemize}

\invisible<1-6>{Basic intuition: } \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Examine joint distribution of characteristics (without making Naive Bayes like assumption)
\item[-] Focus on distributions (only) makes this analysis possible} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{ReadMe: Optimization for a Different Goal (Hopkins and King 2010) }

Measure \alert{only} presence/absence of each term [$(J x 1) $ vector ] \pause 
\begin{eqnarray}
\invisible<1>{\boldsymbol{x}_i & = & (1, 0, 0, 1, \hdots, 0) \nonumber } \pause 
\end{eqnarray}

\invisible<1-2>{What are the possible realizations of $\boldsymbol{x}_i$?} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] $2^{J}$ possible vectors} \pause 
\end{itemize}

\invisible<1-4>{Define:} \pause 
\begin{eqnarray}
\invisible<1-5>{P(\boldsymbol{x}) & = & \text{probability of observing } \boldsymbol{x}} \pause  \nonumber \\
\invisible<1-6>{P(\boldsymbol{x}|C_j) & = & \text{Probability of observing } \boldsymbol{x} \text{ conditional on category } C_j} \pause  \nonumber \\
\invisible<1-7>{P(\boldsymbol{X}| C) & = & \text{Matrix collecting vectors} } \pause \nonumber \\
\invisible<1-8>{P(C ) & = & P(C_1, C_2, \hdots, C_K) \text{ target quantity of interest } } \pause \nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{ReadMe: Optimization for a Different Goal (Hopkins and King 2010) }

\begin{eqnarray}
\underbrace{P(\boldsymbol{x} )}_{2^{J} x 1}  & = & \underbrace{P(\boldsymbol{x}| C )}_{2^{J} x K}  \underbrace{P(C)}_{K x 1 }  \nonumber
\end{eqnarray}
Matrix algebra problem to solve, for $P(C)$ \\
Like Naive Bayes, requires two pieces to estimate\\
Complication $2^{J} >> \text{no. documents} $\\
\alert{Kernel Smoothing Methods} (without a formal model)
\begin{itemize}
\item[-] $P(\boldsymbol{x})$ = estimate directly from test set
\item[-] $P(\boldsymbol{x}| C)$ = estimate from training set 
\begin{itemize}
\item[-] Key assumption: $P(\boldsymbol{x}| C)$ in training set is equivalent to $P(\boldsymbol{x}| C)$ in test set
\end{itemize}
\item[-] If true, can perform biased sampling of documents, worry less about drift...
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Algorithm Summarized}

\begin{itemize}
\item[-] Estimate $\hat{p}(\boldsymbol{x})$ from test set
\item[-] Estimate $\hat{p}(\boldsymbol{x}|C)$ from training set 
\item[-] Use $\hat{p}(\boldsymbol{x})$ and $\hat{p}(\boldsymbol{x}|C)$ to solve for $p(C)$
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Assessing Model Performance}

Not classifying individual documents $\rightarrow$ different standards\\
\alert{Mean Square Error} : 
\begin{eqnarray}
\text{E}[(\hat{\theta} - \theta) ^2] & = & \text{var} (\hat{\theta} ) + \text{Bias}(\hat{\theta},  \theta)^2 \nonumber 
\end{eqnarray}
Suppose we have true proportions $P(C)^{\text{true}}$.  Then, we'll estimate \alert{Root Mean Square Error } 
\begin{eqnarray}
\text{RMSE} & = & \sqrt{ \frac{\sum_{j=1}^{J} (P(C_j)^{\text{true}} - P(C_j) ) } {J} } \nonumber \\
\text{Mean Abs. Prediction Error} & = & | \frac{\sum_{j=1}^{J} (P(C_j)^{\text{true}} - P(C_j) ) } {J} | \nonumber
\end{eqnarray}

\alert{Visualize}: plot true and estimated proportions

\end{frame}

\begin{frame}
\begin{center}
\only<1>{\scalebox{0.8}{\includegraphics{Shot1.png}}} 
\end{center}
\only<2>{\scalebox{0.5}{\includegraphics{Shot2.png}}}

\end{frame}

\begin{frame}
\frametitle{Using the House Press Release Data}

\begin{tabular}{lll} 
\hline\hline
Method & RMSE & APSE  \\
\hline
ReadMe &  0.036  & 0.056 \\
NaiveBayes & 0.096 & 0.14 \\
SVM & 0.052 & 0.084 \\
\hline
\end{tabular}

\end{frame}

\begin{frame}
\frametitle{Code to Run in R}

Control file: \\
\begin{tabular}{lll} 
filename & truth & trainingset \\
\hline
20July2009LEWIS53.txt & 4 & \alert{1} \\
26July2006LEWIS249.txt & 2 & \alert{0} \\
\hline
\end{tabular}

{\tt tdm<- undergrad(control=control, fullfreq=F)  } \\
{\tt process<- preprocess(tdm) } \\
{\tt output<- undergrad(process) } \\
{\tt output\$est.CSMF \#\# proportion in each category} \\
{\tt output\$true.CSMF \#\# if labeled for validation set (but not used in training set) }

\end{frame}

\begin{frame}
\frametitle{Classification (Prediction)}
\begin{itemize}
\item[1)] Task
\begin{itemize}
\item[-] Classify Documents
\item[-] Measure proportions
\end{itemize}
\item[2)] Objective Function
\begin{eqnarray}
Y & = & f(\underbrace{\boldsymbol{\beta}}_{\text{coefficients}}, \boldsymbol{X}, \boldsymbol{Y}, \underbrace{\boldsymbol{\lambda}}_{\text{Tuning}}) + \epsilon \nonumber 
\end{eqnarray}
Models often assume $\boldsymbol{\lambda}$ are known$\leadsto$ search over lambda values
\item[3)] Optimization
\begin{itemize}
\item[-] Grid search, examine \alert{loss} function
\item[-] Best procedure: test performance on data held in ``vault"
\item[-] Approximate in two ways:
\begin{itemize}
\item[a)] Analytically: AIC, BIC
\item[b)] Computationally: \alert{Cross validation}
\end{itemize}
\end{itemize}
\item[4)] Validation
\begin{itemize}
\item[-] Out of sample predictive performance
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Loss Functions and Model Complexity}

Suppose each document $i$ has labels (scores) $Y_{i}$ and count vector $\boldsymbol{x}_{i} = (x_{i1}, x_{i2}, \hdots, x_{iJ})$. \pause   \\
\invisible<1>{Fit model to obtain $\hat{\boldsymbol{\beta}}$.  \\} \pause 
\invisible<1-2>{Potential \alert{loss} functions:} \pause 
\begin{eqnarray}
\invisible<1-3>{L\left(Y_{i}, f(\hat{\boldsymbol{\beta}}, \boldsymbol{x}_{i} , \boldsymbol{\lambda})\right)}\pause \invisible<1-4>{ & = & \left(Y_{i} - f(\hat{\boldsymbol{\beta}}, \boldsymbol{x}_{i} , \boldsymbol{\lambda})\right)^{2} \nonumber \\} \pause
\invisible<1-5>{& = & \left| Y_{i} - f(\hat{\boldsymbol{\beta}}, \boldsymbol{x}_{i} , \boldsymbol{\lambda})\right| \nonumber \\} \pause 
\invisible<1-6>{& = & I\left(Y_{i}  = f(\hat{\boldsymbol{\beta}}, \boldsymbol{x}_{i} , \boldsymbol{\lambda})\right) \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Loss Functions and Model Complexity}

Suppose that we have: \pause 
\begin{itemize}
\invisible<1>{\item[-] Training sets, $\mathcal{T}$, with $|\mathcal{T}| = N_{\text{train}}$ } \pause 
\invisible<1-2>{\item[-] Test sets, $\mathcal{O}$ with $| \mathcal{O}| = N_{\text{test}}$} \pause 
\end{itemize}

\invisible<1-3>{Training (in-sample) error is:} \pause

\begin{eqnarray}
\invisible<1-4>{\text{Error}_{\text{in}}\pause & = & \sum_{i \in \mathcal{T}} \frac{1}{N_{\text{train}}} L(Y_{i} , f(\hat{\boldsymbol{\beta}}, \boldsymbol{x}_{i} , \boldsymbol{\lambda})) \nonumber } \pause 
\end{eqnarray}

\invisible<1-5>{We'd like to estimate out of sample performance with } 
\begin{eqnarray}
\invisible<1-6>{\text{Error}_{\text{out}} & = & \text{E}[L(\boldsymbol{Y}_{i \in \mathcal{O}} , f(\hat{\boldsymbol{\beta}} , \boldsymbol{X}_{i \in \mathcal{O}} , \boldsymbol{\lambda}))| \mathcal{T} ] \nonumber } \pause 
\end{eqnarray}

\invisible<1-7>{where the expectation is taken over \alert{samples} for test sets and supposes we have a training set.   } \pause

\begin{eqnarray}
\invisible<1-8>{\text{Error} & = & \text{E}\left[\text{E}[L(\boldsymbol{Y} , f(\hat{\boldsymbol{\beta}} , \boldsymbol{X}, \boldsymbol{\lambda}))| \mathcal{T} ] \right] \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Loss Functions and Model Complexity}

Suppose $Y_{i} = f(\boldsymbol{x}_{i} ) + \epsilon_{i}$ \pause  \\
\invisible<1>{Where $E[\epsilon_{i} ] = 0 $ } \pause \\
\invisible<1-2>{$\text{var}(\epsilon_{i}) = \sigma^{2}_{\epsilon} $} \pause \\
\invisible<1-3>{Define $f(\hat{\boldsymbol{\beta}}, \boldsymbol{x}, \boldsymbol{\lambda} ) = \hat{f}(\boldsymbol{x})$ } \pause \\
\invisible<1-4>{With squared error loss: } \pause 
\begin{eqnarray}
\invisible<1-5>{\text{Error}(\boldsymbol{x}_{0}) & = & \text{E}[(Y_{i} - \hat{f}(\boldsymbol{x}_{i}))^{2} | \boldsymbol{x}_{i} = \boldsymbol{x}_{0} ]  \nonumber \\} \pause 
\invisible<1-6>{& = & \text{E}[(f(\boldsymbol{x}_{i}) + \epsilon_{i}  - \hat{f}(\boldsymbol{x}_{i}))^{2} | \boldsymbol{x}_{i} = \boldsymbol{x}_{0} ]  \nonumber \\} \pause 
\invisible<1-7>{& = & \sigma^{2}_{\epsilon} + [ f(\boldsymbol{x}_{i}) - \text{E}\hat{f}(\boldsymbol{x}_{i})]^{2}  + E[\left(\hat{f}(\boldsymbol{x}_{i} ) - E[\hat{f}(\boldsymbol{x}_{i} )]\right)^{2} ] \nonumber \\} \pause 
\invisible<1-8>{& = & \text{Irreducible error} + \text{Bias}^{2} + \text{Variance} \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{How Do We Build A Model?}

There are many ways to fit models \\
And many choices made when performing model fit\\
How do we choose? \pause \\

\invisible<1>{Bad way to choose:}\pause \invisible<1-2>{ within sample model fit (HTF Figure 7.1) }

\begin{center}
\scalebox{0.5}{\includegraphics{TestTrain.png}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{How Do We Build A Model?}

\begin{center}
\scalebox{0.325}{\includegraphics{TestTrain.png}}
\end{center}

Model \alert{overfit}$\leadsto$ in sample error is \alert{optimistic}: \pause 
\begin{itemize}
\invisible<1>{\item[-] Some model complexity captures \alert{systematic} features of the data} \pause 
\invisible<1-2>{\item[-] Characteristics found in both training and test set} \pause 
\invisible<1-3>{\item[-] Reduces error in both training and test set } \pause 
\invisible<1-4>{\item[-] Additional model complexity: \alert{idiosyncratic} features of the training set} \pause 
\invisible<1-5>{\item[-] Reduces error in training set, increases error in test set} 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Probit Regression (for motivational purposes)}

Suppose: 
\begin{eqnarray}
Y_{i} & \sim & \text{Bernoulli}(\pi_{i}) \nonumber \\
\pi_{i} & = & \Phi(\boldsymbol{\beta}^{'}\boldsymbol{x}_{i}) \nonumber 
\end{eqnarray}

where $\Phi(\cdot)$ is the cumulative normal distribution.\\
Implies log-likelihood
\begin{eqnarray}
\log \text{L}(\boldsymbol{\beta}| \boldsymbol{X} , \boldsymbol{Y}) &  = & \sum_{i=1}^{N} \left[ Y_{i} \log \Phi(\boldsymbol{\beta}^{'}\boldsymbol{x}_{i} )   + (1-Y_{i}) \log (1-  \Phi(\boldsymbol{\beta}^{'}\boldsymbol{x}_{i} )) \right] \nonumber  
\end{eqnarray}

Log-likelihood is a loss function, but optimistic$\leadsto$ improves with more parameters

\end{frame}

\begin{frame}
\frametitle{Analytic Solutions}

Approximate optimism and compensate in loss function.  \pause \\

\invisible<1>{Akaike Information Criterion (AIC).\\} \pause 
\invisible<1-2>{As $N \rightarrow \infty $ } \pause

\begin{eqnarray}
\invisible<1-3>{- 2 \text{E} [ \log P_{\hat{\boldsymbol{\beta}}} (Y)] & = & -\frac{2}{N} \text{E} [\log \text{L}(\hat{\boldsymbol{\beta}}| \boldsymbol{X} , \boldsymbol{Y})]  + 2 \frac{d}{N} \nonumber \\} \pause 
\invisible<1-4>{\text{AIC} & = & - \frac{2}{N} \log \text{L}(\hat{\boldsymbol{\beta}}| \boldsymbol{X} , \boldsymbol{Y}) + 2 \frac{d}{N} \nonumber } \pause
\end{eqnarray}

\invisible<1-5>{where $d$ are the number of parameters in the model} \pause

\begin{itemize}
\invisible<1-6>{\item[-] Intuition: balances model fit with penalty for complexity} \pause 
\invisible<1-7>{\item[-] Derived from method to estimate \alert{optimism} in likelihood based models} \pause 
\invisible<1-8>{\item[-] Derived from a method to compute similarity between estimated model and true model (under assumptions of course)} \pause 
\invisible<1-9>{\item[-] Can be extended to general models, though requires estimate of irresolvable error} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Analytic Solutions}

Bayesian Information Criterion (BIC) [Schwarz Criterion] \pause

\begin{eqnarray}
\invisible<1>{\text{BIC} &  = &  - 2 \log \text{L}(\boldsymbol{\beta}| \boldsymbol{X} , \boldsymbol{Y}) + (\log N) d \nonumber } \pause 
\end{eqnarray}

\invisible<1-2>{where $d$ is again the effective number of parameters} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Intuition: balances model fit with penalty for complexity} \pause 
\invisible<1-4>{\item[-] Derived from \alert{Bayesian} approach to model selection} \pause 
\invisible<1-5>{\item[-] Approximation to Bayes' factor} \pause 
\invisible<1-6>{\item[-] \alert{Penalizes more heavily than AIC}} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{BIC or AIC?}

\begin{center}
\only<1>{\scalebox{0.55}{\includegraphics{Bayes1.pdf}}}\only<2>{\scalebox{0.55}{\includegraphics{Bayes2.pdf}}}\only<3>{\scalebox{0.55}{\includegraphics{Bayes3.pdf}}}\only<4>{\scalebox{0.55}{\includegraphics{Bayes4.pdf}}}\only<5>{\scalebox{0.55}{\includegraphics{Bayes5.pdf}}}\only<6>{\scalebox{0.55}{\includegraphics{Bayes6.pdf}}}\only<7>{\scalebox{0.55}{\includegraphics{Bayes7.pdf}}}\only<8>{\scalebox{0.55}{\includegraphics{Bayes8.pdf}}}\only<9>{\scalebox{0.55}{\includegraphics{Bayes9.pdf}}}\only<10>{\scalebox{0.55}{\includegraphics{Bayes10.pdf}}}\only<11>{\scalebox{0.55}{\includegraphics{AIC1.pdf}}}\only<12>{\scalebox{0.55}{\includegraphics{AIC2.pdf}}}\only<13>{\scalebox{0.55}{\includegraphics{AIC3.pdf}}}\only<14>{\scalebox{0.55}{\includegraphics{AIC4.pdf}}}\only<15>{\scalebox{0.55}{\includegraphics{AIC5.pdf}}}\only<16>{\scalebox{0.55}{\includegraphics{AIC6.pdf}}}\only<17>{\scalebox{0.55}{\includegraphics{AIC7.pdf}}}\only<18>{\scalebox{0.55}{\includegraphics{AIC8.pdf}}}\only<19>{\scalebox{0.55}{\includegraphics{AIC9.pdf}}}\only<20>{\scalebox{0.55}{\includegraphics{AIC10.pdf}}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{BIC or AIC?}

\begin{itemize}
\item[-] BIC
\begin{itemize}
\item[-] Asymptotically consistent
\item[-] As $N\rightarrow \infty$ will choose correct model with probability 1
\item[-] Small samples$\leadsto$ overpenalize
\end{itemize}
\item[-] AIC
\begin{itemize}
\item[-] No asymptotic guarantees
\item[-] In large samples$\leadsto$ favors complexity
\item[-] Small samples$\leadsto$ avoids over penalization
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{How Do We Select A Model?}

Analytic statistics for selection, include penalty for complexity \pause 
\begin{itemize}
\invisible<1>{\item[-] AIC : Akaka Information Criterion} \pause 
\invisible<1-2>{\item[-] BIC: Bayesian Information Criterion} \pause 
\invisible<1-3>{\item[-] DIC: Deviance Information Criterion} \pause 
\end{itemize}

\invisible<1-4>{Can work well, but...} \pause 
\begin{itemize}
\invisible<1-5>{\item[-] Rely on specific loss function} \pause 
\invisible<1-6>{\item[-] Rely on asymptotic argument} \pause 
\invisible<1-7>{\item[-] Rely on estimate of number of parameters} \pause 
\invisible<1-8>{\item[-] \alert{Extremely model dependent} } \pause 
\end{itemize}

\invisible<1-9>{Need: general tool for evaluating models, \alert{replicates} decision problem}

\end{frame}

\begin{frame}
\frametitle{Cross-Validation: Some Intuition}

Recall Optimal division of data: \pause 
\begin{itemize}
\invisible<1>{\item[-] Train: build model} \pause 
\invisible<1-2>{\item[-] Validation: assess model} \pause 
\invisible<1-3>{\item[-] Test: classify remaining documents} \pause 
\end{itemize}

\invisible<1-4>{K-fold Cross-validation idea: create many training and test sets.  } \pause 
\begin{itemize}
\invisible<1-5>{\item[-] Idea: use observations both in training and test sets} \pause 
\invisible<1-6>{\item[-] Each step: use held out data to evaluate performance} \pause 
\invisible<1-7>{\item[-] \alert{Avoid overfitting} and have context specific penalty } \pause 
\end{itemize}

\invisible<1-8>{Estimates:}
\begin{eqnarray}
\invisible<1-8>{\text{Error} & = & \text{E}\left[\text{E}[L(\boldsymbol{Y} , f(\hat{\boldsymbol{\beta}} , \boldsymbol{X}, \boldsymbol{\lambda}))| \mathcal{T} ] \right] \nonumber }
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Cross-Validation: A How To Guide}

Process: \pause 
\begin{itemize}
\invisible<1>{\item[-]  Randomly partition data into K groups. } \pause 
\invisible<1-2>{\item[] (Group 1, Group 2, Group3, $\hdots$, Group K ) } \pause 
\invisible<1-3>{\item[-]  Rotate through groups as follows} \pause 
\end{itemize}
\begin{tabular}{lll} 
\invisible<1-4>{Step & Training & Validation (``Test") \\} \pause 
\invisible<1-5>{1 & Group2, Group3, Group 4, $\hdots$, Group K & Group 1\\} \pause 
\invisible<1-6>{2 & Group 1, Group3, Group 4, $\hdots$, Group K & Group 2 \\} \pause 
\invisible<1-7>{3 & Group 1, Group 2, Group 4, $\hdots$, Group K & Group 3 \\} \pause 
\invisible<1-8>{$\vdots$ & $\vdots$ & $\vdots$ \\} \pause 
\invisible<1-9>{K & Group 1, Group 2, Group 3, $\hdots$, Group K - 1 & Group K } 
\end{tabular}

\end{frame}

\begin{frame}
\frametitle{Cross-Validation: A How To Guide} 
\footnotesize
\begin{tabular}{lll} 
Step & Training & Validation (``Test") \\
1 & Group2, Group3, Group 4, $\hdots$, Group K & Group 1\\
2 & Group 1, Group3, Group 4, $\hdots$, Group K & Group 2 \\
3 & Group 1, Group 2, Group 4, $\hdots$, Group K & Group 3 \\
$\vdots$ & $\vdots$ & $\vdots$ \\
K & Group 1, Group 2, Group 3, $\hdots$, Group K - 1 & Group K 
\end{tabular} 
\normalsize
 \pause \invisible<1>{Strategy: } \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Divide data into $K$ groups} \pause 
\invisible<1-3>{\item[-] Train data on $K-1$ groups.  Estimate $\hat{f}^{-K}(\boldsymbol{X}, \boldsymbol{\lambda})$  } \pause 
\invisible<1-4>{\item[-] Predict values for $K^{\text{th}}$} \pause 
\invisible<1-5>{\item[-] Summarize performance with loss function: $L(\boldsymbol{Y}_i , \hat{f}^{-k} (\boldsymbol{X}, \boldsymbol{\lambda})  ) $} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Mean square error, Absolute error, Prediction error, ...} \pause 
\end{itemize}
\invisible<1-7>{\item[] CV(ind. classification)  = $ \frac{1}{N}\sum_{i=1}^{N} L(\boldsymbol{Y}_i , f^{-k} (\boldsymbol{X}_i)  ) $} \pause 
\invisible<1-8>{\item[] CV(proportions)   =  $\frac{1}{K} \sum_{j=1}^{K} \text{Mean Square Error Proportions from Group j}$} \pause 
\invisible<1-9>{\item[-] Final choice: model with highest $CV$ score} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{How Do We Select $K$? (HTF, Section 7.10)  }

Common values of $K$ 
\begin{itemize}
\item[-] $K = 5$: Five fold cross validation
\item[-] $K = 10$: Ten fold cross validation
\item[-] $K = N $: Leave one out cross validation
\end{itemize}

Considerations:
\begin{itemize}
\item[-] How sensitive are inferences to number of coded documents? (HTF, pg 243-244) 
\item[-] 200 labeled documents 
\begin{itemize}
\item[-] $K= N \rightarrow$ 199 documents to train, 
\item[-] $K = 10 \rightarrow$ 180 documents to train
\item[-] $K = 5 \rightarrow$ 160 documents to train
\end{itemize}
\item[-] 50 labeled documents
\begin{itemize}
\item[-] $K= N \rightarrow$ 49 documents to train, 
\item[-] $K = 10 \rightarrow$ 45 documents to train
\item[-] $K = 5 \rightarrow$ 40 documents to train
\end{itemize}
\item[-] How long will it take to run models?  
\begin{itemize}
\item[-] $K-$fold cross validation requires $K \times $ One model run 
\end{itemize}
\item[-] What is the correct loss function?
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{If you cross validate, you really need to cross validate (Section 7.10.2, ESL)}

\begin{itemize}
\item[-] Use CV to estimate prediction error
\item[-] \alert{All} supervised steps performed in cross-validation
\item[-] \alert{Underestimate} prediction error
\item[-] \alert{Could lead to selecting lower performing model} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Generalized Cross Validation and Ridge Regression}

In some special cases there are analytic solutions: \\ \pause

\begin{eqnarray}
\invisible<1>{\boldsymbol{\beta}^{\text{Ridge}} & = & \left(\boldsymbol{X}^{'}\boldsymbol{X} + \lambda \boldsymbol{I}_{J} \right)^{-1} \boldsymbol{X}^{'} \boldsymbol{Y} \nonumber } \pause \\
\invisible<1-2>{\widehat{\boldsymbol{Y}} & = & \boldsymbol{X}(\boldsymbol{\beta})^{\text{Ridge}} \nonumber\\} \pause 
\invisible<1-3>{& = & \underbrace{\boldsymbol{X}\left(\boldsymbol{X}^{'}\boldsymbol{X} + \lambda \boldsymbol{I}_{J} \right)^{-1} \boldsymbol{X}^{'}}_{\text{Hat Matrix}} \boldsymbol{Y} \nonumber\\} \pause
\invisible<1-4>{\widehat{\boldsymbol{Y}} & = & \underbrace{\boldsymbol{H}}_{\text{Smoother Matrix}} \boldsymbol{Y}  \nonumber } \pause
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Generalized Cross Validation and Ridge Regression}

Why do we care?  \pause \\
\invisible<1>{Leave one out cross validation\\} \pause 
\begin{eqnarray}
\invisible<1-2>{\text{Cross Validation}(1) & = & \frac{1}{N} \sum_{i=1}^{N} (Y_{i} - f (\boldsymbol{X}_{-i}, \boldsymbol{Y}_{-i}, \lambda, \hat{\boldsymbol{\beta}} ))^{2} \nonumber \\} \pause 
\invisible<1-3>{& = & \frac{1}{N} \sum_{i=1}^{N}  \left(\frac{Y_{i} - f (\boldsymbol{X}, \boldsymbol{Y}, \lambda, \hat{\boldsymbol{\beta} }) }{1 - H_{ii}} \right)^2 \nonumber} 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Generalized Cross Validation and Ridge Regression}

Calculating $\boldsymbol{H}$ can be computationally expensive \pause \\
\begin{itemize}
\invisible<1>{\item[-] $\text{Trace}(\boldsymbol{H}) \equiv \text{Tr}(\boldsymbol{H})  = \sum_{i=1}^{N} H_{ii} $ } \pause 
\invisible<1-2>{\item[-] $\text{Tr}(\boldsymbol{H})$ = Effective number of parameters (class regression = number of independent variables + 1)} \pause 
\invisible<1-3>{\item[-] For Ridge regression:} \pause 
\begin{eqnarray}
\invisible<1-4>{\text{Tr}(\boldsymbol{H}) & = & \sum_{i=1}^{N} \frac{\lambda_{i}}{\lambda_{i} + \lambda} \nonumber } \pause 
\end{eqnarray}
\invisible<1-5>{where $\lambda_{i}$ is the $i^{\text{th}}$ Eigenvalue from $\boldsymbol{\Sigma} = \boldsymbol{X}^{'}\boldsymbol{X}$} \pause \invisible<1-6>{ (!!!!!)} \pause 
\end{itemize}

\invisible<1-7>{Define generalized cross validation:} \pause 
\begin{eqnarray}
\invisible<1-8>{\text{GCV} &  = & \frac{1}{N} \sum_{i=1}^{N} \left( \frac{Y_{i} - \hat{Y}_{i}}{1 - \frac{\text{Tr}(\boldsymbol{H})}{N} }    \right)^2 \nonumber } \pause 
\end{eqnarray}

\invisible<1-9>{Applicable in any setting where we can write \alert{Smoother} matrix} \pause

\end{frame}

\begin{frame}
\frametitle{Cross Validation}

Use cross validation extensively:
\begin{itemize}
\item[1)] Selecting tuning parameters
\item[2)] Learning weights in an ensemble
\item[3)] But it is no panacea:
\begin{itemize}
\item[-] Depends on $K$
\item[-] Sampling$\leadsto$ maintain dependencies
\end{itemize}
\end{itemize}

Next week: Ensembles + Ideological scaling

\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/tc17.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{November 18th, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Final Project}

Poster Session: 12/4 \pause \\
\begin{itemize}
\invisible<1>{\item[-] Make posters in \LaTeX\ or related software for asthetics} \pause 
\invisible<1-2>{\item[-] Landscape orientation is preferable} \pause 
\invisible<1-3>{\item[-] \alert{Less is More}} \pause 
\end{itemize}
\invisible<1-4>{Papers Due: 12/12, 5pm {\huge \alert{This is a hard deadline}!}} \pause 
\begin{itemize}
\invisible<1-5>{\item[-] An academic paper$\leadsto$ appropriate for your field} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Succinct (not cute) title} \pause 
\invisible<1-7>{\item[-] Abstract that explains your contribution} \pause 
\invisible<1-8>{\item[-] Introduction that explains why your paper exists} \pause 
\invisible<1-9>{\item[-] Presentation of Results} \pause 
\invisible<1-10>{\item[-] Avoid: Long/breezy lit reviews that merely list previous scholarship} 
\end{itemize}

\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Supervised Learning: Ensemble Learning}
\begin{itemize}
\item[1)] Task \pause 
\begin{itemize}
\invisible<1>{\item[-] Subsidize hand coding$\leadsto$ learn a rule between labels and features} \pause 
\end{itemize}
\invisible<1-2>{\item[2)] Objective function } \pause 
\begin{eqnarray}
\invisible<1-3>{\text{Pr}(Y_{i} = C_{k} | \boldsymbol{x}_{i} ) & = & f(\boldsymbol{x}_{i}, \boldsymbol{\beta}, \boldsymbol{\lambda}) \nonumber } \pause 
\end{eqnarray}
\begin{itemize}
\invisible<1-4>{\item[-] ``Coefficients" $\boldsymbol{\beta}$} \pause 
\invisible<1-5>{\item[-] Tuning parameters $\boldsymbol{\lambda}$} \pause 
\invisible<1-6>{\item[-] Functional form $f$} \pause 
\invisible<1-7>{\item[-] \alert{Necessarily requires consequential assumptions}} \pause 
\invisible<1-8>{\item[-] Ensembles: aggregate classifiers to increase performance} \pause 
\end{itemize}
\invisible<1-9>{\item[3)] Optimization} \pause 
\begin{itemize}
\invisible<1-10>{\item[-] Optimization of individual classifiers$\leadsto$ methods already discussed} \pause 
\invisible<1-11>{\item[-] Determination of weights on models$\leadsto$ equal (bagging), out of sample performance via cross validation (super learning)} \pause 
\end{itemize}
\invisible<1-12>{\item[4)] Validation} \pause 
\begin{itemize}
\invisible<1-13>{\item[-] Out of sample predictive performance} 
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Ensemble Learning: Intuition}

\alert{Heuristic} (upon which we'll improve):\pause\invisible<1>{ if classifiers are \alert{accurate} and \alert{diverse}$\rightarrow$ ensemble methods improve} \pause \\
\invisible<1-2>{\alert{Intuition}: } \pause 
\begin{itemize} 
\invisible<1-3>{\item[-] Classify documents into two categories (Category 1, Category 2). }  \pause 
\invisible<1-4>{\item[-] True labels: evenly distributed across two categories}  \pause 
\invisible<1-5>{\item[-] Three classifiers with $75\%$ accuracy, but independent  }\pause 
\invisible<1-6>{\item[-] Implement majority voting rule  }\pause 
\end{itemize}
\begin{eqnarray}
\invisible<1-7>{\text{Pr(Correct Guess}| \text{Votes} )} \pause \invisible<1-8>{ & = & \text{Pr(3 correct)} + \text{Pr(2 correct)} } \pause \nonumber \\
 \invisible<1-9>{& = & 0.75^3 + 3 \times (0.75^2 \times 0.25)} \pause  \nonumber \\
  \invisible<1-10>{& = &  0.844 \nonumber }
  \end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Ensemble Learning: Intuition}

\only<1>{\scalebox{0.45}{\includegraphics{Ensemble1.pdf}}}

\end{frame}

\begin{frame}
\frametitle{Ensemble Learning: Intuition}

\alert{Diverse} and \alert{Accurate} matter.

\only<1>{\scalebox{0.45}{\includegraphics{Ensemble2.pdf}}} 
\only<2>{\scalebox{0.45}{\includegraphics{Ensemble3.pdf}}}

\end{frame}

\begin{frame}
\frametitle{Wisdom of the Crowds:}

Goal: estimate a document's category$\leadsto$ $Y \in \{0, 1\}$ \pause \\
\invisible<1>{Classifiers: (suppose) a sequence of identically distributed (\alert{not independent}) random variables. } \pause  \\
\invisible<1-2>{Suppose $Y = 1$} \pause \\
\invisible<1-3>{Guess from classifer $m$ is $B_{m}$ with Pr$(B_{i} = 1) = p>0.5$.  \\} \pause 
\begin{eqnarray}
\invisible<1-4>{\bar{B} & = & \sum_{m=1}^{M} \frac{B_{m}}{M} \nonumber } \pause 
\end{eqnarray}

\invisible<1-5>{\alert{Wisdom of crows} (Condorcet Jury Theorem)} \pause 
\begin{eqnarray}
\invisible<1-6>{\lim_{M\rightarrow \infty} P(\bar{B}> 0.5) & = & 1 \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Wisdom of the Crowds}

Suppose $B_{m}$ have variance $\sigma^2$ and pairwise correlation $\rho$. \pause   \\
\invisible<1>{Then, } \pause

\begin{eqnarray}
\invisible<1-2>{\text{var}(\bar{B}) }\pause\invisible<1-3>{& = & \text{var}\left(\sum_{i=1}^{M} \frac{B_{i}}{M}  \right)} \pause  \nonumber \\
 \invisible<1-4>{& = & \frac{1}{M^{2}} \sum_{i=1}^{M} \text{var}\left(B_{i}\right) + \frac{2}{M^2} \sum_{i<j} \text{cov}(B_{i}, B_{j}) \nonumber } \pause\\
 \invisible<1-5>{& = & \frac{M \sigma^2}{M^2}  + \frac{2}{M^2} \rho \sigma^2 {{M}\choose{2}} \nonumber } \pause\\
\invisible<1-6>{& = & \underbrace{\rho \sigma^2}_{\text{Resolve with independence}} + \underbrace{\frac{1 - \rho}{M} \sigma^2}_{\text{Resolve with $\uparrow$classifiers}} \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{\alert{Bagging}: bootstrap aggregation}

\begin{small}
Creating Weak Classifiers with resampling: \pause 
\begin{itemize}
\invisible<1>{\item[-] Suppose we have labels $\boldsymbol{Y}$ and document term matrix $\boldsymbol{X}$} \pause
\invisible<1-2>{\item[-] For each bootstrap step $m$, $(m = 1,2, \hdots, M)$ draw $N$ observations with replacement, $\tilde{\boldsymbol{Y}}_{m}$, $\tilde{\boldsymbol{X}}_{m}$.  } \pause 
\invisible<1-3>{\item[-] Train classifier on bootstrapped data, } \pause 
\begin{eqnarray}
\invisible<1-4>{\tilde{\boldsymbol{Y}}_{m} & = & f^{m}(\tilde{\boldsymbol{X}}_{m}, \widehat{\boldsymbol{\beta}}, \boldsymbol{\lambda} ) \nonumber } \pause 
\end{eqnarray}
\invisible<1-5>{\item[-] Aggregating across classifiers, } \pause 
\begin{eqnarray}
\invisible<1-6>{f_{\text{bag}}(\boldsymbol{x}_{i}) & = & \frac{1}{M} \sum_{m=1}^{M} f^{m}(\tilde{\boldsymbol{X}}_{m}, \widehat{\boldsymbol{\beta}}, \boldsymbol{\lambda}) \nonumber } \pause 
\end{eqnarray}
\invisible<1-7>{\item[-] Only leads to a difference in estimate if classifiers are non-linear. } \pause 
\invisible<1-8>{\item[-] Strong Correlation between classifiers}
\end{itemize}
\end{small}
\end{frame}

\begin{frame}
\frametitle{Classification and Regression Trees (CART): Intuition}

Consider regression $E[Y|\boldsymbol{x}_{i}]$. \pause  \\
\invisible<1>{With no assumptions, \alert{stratify}$\leadsto$ different mean for unique values of $\boldsymbol{x}_{i}$\\} \pause
\begin{itemize}
\invisible<1-2>{\item[-] Within each strata $p$, compute average $Y$} \pause 
\begin{eqnarray}
\invisible<1-3>{\bar{Y}|\boldsymbol{x}_{p} & = & \sum_{i=1}^{N} \frac{I(\boldsymbol{x}_{i} = \boldsymbol{x}_{p})Y_{i}}{\sum_{t=1}^{N} I(\boldsymbol{x}_{t} = \boldsymbol{x}_{p}) } \nonumber } \pause 
\end{eqnarray}
\end{itemize}

\invisible<1-4>{Implies that for test data we would fit:} \pause

\begin{eqnarray}
\invisible<1-5>{\hat{f}(\boldsymbol{x}_{i}) & = & \sum_{p=1}^{P} \bar{Y}|\boldsymbol{x}_{p}  I(\boldsymbol{x}_{i} = \boldsymbol{x}_{p}) \nonumber }\pause\\
\invisible<1-6>{& = & \sum_{p=1}^{P} c_{p}  I(\boldsymbol{x}_{i} = \boldsymbol{x}_{p}) \nonumber }\pause 
\end{eqnarray}

\invisible<1-7>{Curse of dimensionality(!!!)\\} \pause 
\invisible<1-8>{Approximate with \alert{regions}$\leadsto$ search for splits of data to approximate stratification}

\end{frame}

\begin{frame}
\frametitle{Classification and Regression Trees (CART): Objective function}

Labels $\boldsymbol{Y}_{i}$ and documents $\boldsymbol{x}_{i}$

\begin{eqnarray}
E[Y| \boldsymbol{x}_{i}] & = & \widehat{f}(\boldsymbol{x}_{i}) \nonumber \\
& = & \sum_{p=1}^{P} c_{p} I (\boldsymbol{x}_{i} \in R_{p}) \nonumber 
\end{eqnarray}

where:
\begin{itemize}
\item[-] $R_{p}$ describes a \alert{region} $\leadsto$ node
\item[-] $c_{p}$ describes values of $Y_{i}$ for document in $R_{p}$
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Classification and Regression Trees (CART): Optimization function}

Suppose we want to minimize sum of squared residuals with each \alert{node}\\ \pause

\invisible<1>{Then $c_{p} = $ Average $Y$ for documents assigned to $R_{p}$ \\} \pause 
\begin{eqnarray}
\invisible<1-2>{\widehat{c}_{p} & =&  \sum_{i=1}^{N} \frac{Y_{i} I(\boldsymbol{x}_{i} \in R_{p} )  }{\sum_{j=1}^{N} I(\boldsymbol{x}_{j} \in R_{p} )  } \nonumber } \pause
\end{eqnarray}

\invisible<1-3>{Determining an optimal partition$\leadsto$ NP-Hard.  \\} \pause 
\invisible<1-4>{Suppose we are in some node (perhaps at the start).  \\} \pause 
\invisible<1-5>{Greedy algorithm:} \pause 
\begin{footnotesize}
\begin{eqnarray}
\invisible<1-6>{(j^{*}, s^{*})  & = & \text{arg min}_{j, s} \left[ \underbrace{\text{min}_{c_{1}} \sum_{i=1}^{N}I(x_{ij}< s)(Y_{i} - c_{1})^2}_{\text{``cost" group 1}}  + \underbrace{\text{min}_{c_{2}} \sum_{i=1}^{N}I(x_{ij}> s)(Y_{i} - c_{2})^2}_{\text{``cost" group 2}}   \right] \nonumber } 
\end{eqnarray}
\end{footnotesize}

\end{frame}

\begin{frame}
\frametitle{Classification and Regression Trees (CART): Algorithm}

\begin{itemize}
\item[-] Start in Node
\item[-] Partition according to Greedy algorithm
\item[-] Continue until some stopping rule: number of observations per node
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{CART Picture (Spirling 2008)}

\scalebox{0.7}{\includegraphics{CART_Example.png}}

\end{frame}

\begin{frame}
\frametitle{Forests and Trees}

Recall: accurate (unbiased) and uncorrelated classifiers \pause 
\begin{itemize}
\invisible<1>{\item[-] Grow trees deeply$\leadsto$ unbiased classifers, though high variance} \pause
\invisible<1-2>{\item[-] \alert{Average}$\leadsto$ reduces variance, but will be correlated} \pause 
\invisible<1-3>{\item[-] Random forest$\leadsto$ introduce additional sampling to induce independence$\leadsto$ Only split on subset of variables} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Random Forest Algorithm (ESL, 588)}

\pause 
\begin{itemize}
\invisible<1>{\item[1)] For $m$ bootstrap samples $(m = 1,\hdots, M)$, draw $N$ observations with replacement, $\tilde{\boldsymbol{Y}_{m}}, \tilde{\boldsymbol{X}_{m}}$} \pause 
\invisible<1-2>{\item[2)] Until a minimum node size is reached:} \pause 
\begin{itemize}
\invisible<1-3>{\item[i)] \alert{Select $z$ of the $J$ variables}$\leadsto$ introduces independences across the trees} \pause 
\invisible<1-4>{\item[ii)] Among those $z$, select the best split node} \pause 
\invisible<1-5>{\item[iii)] Split into daughter nodes} \pause 
\end{itemize}
\invisible<1-6>{\item[3)] The result is an ensemble (forest) of trees $\boldsymbol{T} = (T_{1}, T_{2}, \hdots, T_{M})$, } \pause 
\begin{eqnarray}
\invisible<1-7>{\hat{f}(\boldsymbol{x}_{i}) & = & \frac{1}{M} \sum_{m=1}^{M} T_{m} (\boldsymbol{x}_{i}) \nonumber } \pause 
\end{eqnarray}
\end{itemize}

\invisible<1-8>{{\tt RandomForest}$\leadsto$ Not a silver bullet!} \pause 
\begin{itemize}
\invisible<1-9>{\item[-] With many poor predictors$\leadsto$ the $p$ selected may be meaningless} 
\end{itemize}

\end{frame}

% \begin{frame}
% \frametitle{Common Ensemble Methods}

% \alert{Boosting}: sequential training of weak classifiers
% \begin{itemize}
% \item[-] Method for combining several \alert{weak} classifiers
% \item[-] Basic idea: 
% \begin{itemize}
% \item[-] Model 1: classify initially based on all data (equal weight)
% \item[-] Model 2: classify all data, more weight to incorrectly classified data
% \item[-] Model 3: classify all data, more weight to incorrectly classified data
% \item[] $\hdots $
% \item[-] Model M: classify all data, more weight to incorrectly classified data
% \end{itemize}
% \item[-] Aggregate using weighted committee 
% \end{itemize}

% \end{frame}

\begin{frame}
\frametitle{Super Learning}

\begin{itemize}
\item[1) ] Set of hand labeled documents.  For each $i$, $(i=1, \hdots, N_{\text{train}})$
\begin{itemize}
\invisible<1>{\item[] $Y_{i, \text{train} } \in \{C_{1} C_{2}, \hdots C_{K} \}$}
\end{itemize}
\invisible<1-2>{\item[2)] Estimate relationship between labels and words } 
\begin{itemize}
\invisible<1-3>{\item[-] Each document $i$  is a \alert{count vector} of $K$ words} 
\invisible<1-4>{\item[] $ \textbf{x}_{i, \text{train}}  =  (X_{i1}, X_{i2}, \hdots, X_{iK}  )$ } \nonumber 
\end{itemize}
\end{itemize}

\only<1->{
\begin{eqnarray}
\invisible<1-5>{\text{Pr}(Y_{i} = C_{k} | \textbf{x}_{i} )\invisible<1-6>{_{\text{train}}}\invisible<1-7>{& = & \widehat{g} (\textbf{x}_{i} )_{\text{train}} } \nonumber }
\end{eqnarray}
} 
%\only<7->{
%\begin{eqnarray}
%\text{Pr}(Y_{i}  = \text{Credit} | \textbf{w}_{i} )_{\text{train}} \invisible<1-7>{& = & \widehat{g} (\textbf{w}_{i} )_{\text{train}} } %\nonumber 
%\end{eqnarray}
%}

\begin{itemize}
\invisible<1-7>{\item[-] Identify systematic relationship between words, labels}  \invisible<1-8>{$\leadsto$ Data and \alert{assumptions}}
\begin{itemize}
\invisible<1-9>{\item[-] LASSO (Tibshirani 1996): \alert{sparsity} }
\invisible<1-10>{\item[-] KRLS (Hainmueller and Hazlett 2013): \alert{dense}, flexible surface}
\invisible<1-11>{\item[-] Ridge, Elastic-Net, SVM, Random Forests, BART, ...}
\end{itemize}
\invisible<1-12>{\item[-] Which model?  Difficult to know before hand}
\invisible<1-13>{\item[-] Assess out of sample performance with \alert{cross validation}}
\end{itemize}
\invisible<1-14>{\alert{Weighted ensemble}: weights determined by (unique) out of sample predictive performance}

\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause 
\end{frame}

\begin{frame}

Committee Methods:\\

Fit many methods, average with equal weights

\begin{itemize}
\item[-] Voting (classification)
\item[-] Averaging (predictions) 
\end{itemize}

Problem: many poor methods may overwhelm high quality fit (remember earlier figures)\\
Solution: learn weights via cross validation

\end{frame}

\begin{frame}
\frametitle{Weighted Ensemble to Classify Documents}

\begin{itemize}
\item[-] Suppose we have $M$ $(m = 1, \hdots, M)$ models.  
\end{itemize}
\begin{eqnarray}
\invisible<1>{\alert<14->{\text{Pr}(Y_{i}   =  \text{C}_{1} | \textbf{x}\only<1-13>{_{i}}\only<14->{_{i,\text{test}}} )_{\text{train}} } & = & \alert<14->{  \sum_{m=1}^{M} \alert<3>{\widehat{\pi}_{m} } \alert<4>{\widehat{g}_{m}(\textbf{x}\only<1-13>{_{i}}\only<14->{_{i, \text{test}}} )}} \nonumber } 
\end{eqnarray}

\begin{itemize}
\invisible<1-4>{\item[-] Estimate weights $(\widehat{\pi}_{m})$} 
\only<1-11>{
\begin{itemize}
\invisible<1-5>{\item[-] K-fold cross validation: generate $M$ out of sample predictions for each document in training set}
\invisible<1-6>{\item[] $\widehat{\textbf{Y}}_{i}  = (\widehat{Y}_{i1}, \widehat{Y}_{i2}, \hdots, \widehat{Y}_{iM} )$} 
\invisible<1-7>{\item[-] Estimate weights with constrained regression:}
\begin{eqnarray}
\invisible<1-8>{Y_{i} & = & \sum_{m=1}^{M} \pi_{m} \hat{Y}_{im} + \epsilon_{i} \nonumber }
\end{eqnarray}
\invisible<1-9>{\item[] where we impose constraints: $\pi_{m} \geq 0 $ and $\sum_{m=1}^{M} \pi_{m} = 1$. } 
\invisible<1-10>{\item[-] Result $\widehat{\pi}_{m}$ for each method } 
\end{itemize}
}
\invisible<1-11>{\item[-] Estimate  $\widehat{g}_{m}(\textbf{x}_{i} ) \leadsto $ Apply all $M$ models to entire training set} 
\end{itemize}
\invisible<1-12>{3) For each document $i$ in test set, $\textbf{x}_{i, \text{test}}$ } \\
%\begin{eqnarray}
%\invisible<1-11>{\text{Pr}(Y_{i} = \text{Credit} | \textbf{w}_{i} ) & = & \sum_{m=1}^{M} \widehat{\pi}_{m} \widehat{g}_{m}(\textbf{w}_{i} ) \nonumber } 
%\end{eqnarray}
\invisible<1-14>{(Classify if above threshold)} \\

\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause 
\end{frame}

\begin{frame}

\scalebox{0.6}{\includegraphics{SuperLearner.png}}

\end{frame}

\begin{frame}
\frametitle{Why Super Learn?}

van der Laan et al (2007) prove:
\begin{itemize}
\item[-] \alert{Asymptotically}: super learners will perform as well the \alert{best} candidates for data 
\item[-] \alert{Oracle}: performs like the best possible method among candidate methods
\begin{itemize}
\item[-] Asymptotically outperforms constituent methods
\item[-] Performs as well as optimal combinations of those methods
\end{itemize}
\end{itemize}

Practical questions:
\begin{itemize}
\item[-] Final regression: 
\begin{itemize}
\item[-] Logistic
\item[-] Linear 
\item[-] \alert{Could super learn again!}
\end{itemize}
\item[-] How Many Folds?
\begin{itemize}
\item[-] van der Laan et al's proofs rely on growing folds with $N$ (but slowly)
\item[-] Use 10-fold cross validation for simulations
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Impression of Influence}

Estimate: $Y_{i} \in \{\text{Credit}, \text{Not Credit} \}$ \pause \\
\begin{itemize}
\invisible<1>{\item[-] Triple hand code 800 press releases} \pause 
\invisible<1-2>{\item[-] Resolve disagreement with voting$\leadsto$ few disagreements} \pause
\end{itemize}

\invisible<1-3>{Use five classifiers to form Ensemble (cross validating within each to tune parameters)}\pause 
\begin{itemize}
\invisible<1-4>{\item[-] LASSO} \pause \invisible<1-9>{0} 
\invisible<1-5>{\item[-] Elastic-Net}\pause \invisible<1-9>{ 23\%} 
\invisible<1-6>{\item[-] Random Forest} \pause \invisible<1-9>{61\%} 
\invisible<1-7>{\item[-] A Support Vector Machine}\pause \invisible<1-9>{16\%} 
\invisible<1-8>{\item[-] Kernel Regularized Least Squares (KRLS, Hainmueller and Hazlett 2014)}\pause \invisible<1-9>{ 0} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Strategic Credit Claiming to Build a Personal Vote}

\begin{tikzpicture}
\node (dummy1) at (-8, 8) [] {} ; 
\node at (-6, 8) [] {\scalebox{0.4}{\includegraphics{DensTikz.pdf}}};

\invisible<1>{\node (trial) at (-8.75,5.7) [] {} ; 
\only<1-9>{\node(Burton) at (-10, 10) [] {\scalebox{0.5}{\includegraphics{Burton.jpg}}}; 
\draw[->, line width = 1.5pt] (Burton) to [out = 270, in = 90] (trial) ; }

\only<3>{\node (McGroff) at (-3, 11) [] {\alert{John McGroff}: ``voted for every spending bill "} ; }
\only<3>{\node (McGroff2) at (-3, 10.6) [] {that went through the office"} ;}
\only<4>{\node (McGroff3) at (-3, 11) [] {\alert{John McGroff}:  ``Not the actions of a fiscally "};}
\only<4>{\node (McGroff4) at (-3, 10.6) [] {conservative congressman who } ; } 
\only<4>{\node (McGroff5) at (-3, 10.2) [] {cares about personal responsibility"}; }
}
%\invisible<1-4>{\node (Price) at (-10, 8) [] {\scalebox{0.2}{\includegraphics{Price.jpg}}} ; 
%\node (trial1) at (-8.7,5.7) [] {} ; 
%\draw[->, line width = 1.5pt] (Price) to [out = 0, in = 90] (trial1) ; }

\only<1-9>{
\invisible<1-4>{\node (Flake) at (-8.2, 11) [] {\scalebox{0.1}{\includegraphics{Flake.jpg}}} ; 
\node (trial2) at (-8.6,5.7) [] {} ; 
\draw[->, line width = 1.5pt] (Flake) to [out = 270, in = 90] (trial2) ; }

\invisible<1-5>{\node (Degette) at (-10, 6) [] {\scalebox{0.1}{\includegraphics{Jan.jpg}}} ; 
\node (trial3) at (-8.65, 5.7) [] {} ; 
\draw[->, line width = 1.5pt] (Degette) to [out = 30, in = 90] (trial2) ; }

\invisible<1-6>{\node (Lobiondo) at (-6, 10) [] {\scalebox{0.08}{\includegraphics{Lobiondo.jpg}}} ; 
\node (trial4) at (-5.1, 5.7) [] {} ; 
\draw[->, line width = 1.5pt] (Lobiondo) to [out = 270, in = 90] (trial4) ; }

\invisible<1-7>{\node (Lobiondo) at (-4, 9.5) [] {\scalebox{0.125}{\includegraphics{Edwards.jpg}}} ; 
\node (trial5) at (-4.95, 5.7) [] {} ; 
\draw[->, line width = 1.5pt] (Lobiondo) to [out = 270, in = 90] (trial5) ; }}

\invisible<1-8>{\node (Rogers) at (-1.8, 11) [] {\scalebox{0.15}{\includegraphics{Rogers.jpg}}}; 
\node (trial6) at (-2.4, 5.7) [] {} ; 
\draw[->, line width = 1.5pt] (Rogers) to [out = 270, in = 90] (trial6) ; }

\only<10>{\node (Pork1) at (-7, 11)  [] {``We just can't afford luxuries like ideology" } ; } 
\only<11>{\node (Pork2) at (-7, 11)  [] {Lexington Herald-Leader: \alert{Prince of Pork}} ; }

\end{tikzpicture}

\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause

%\only<1>{\scalebox{0.4}{\includegraphics{DensTikz.pdf}}}
%\only<1>{\scalebox{0.4}{\includegraphics{NewDensity1.pdf}}}\only<2>{\scalebox{0.4}{\includegraphics{NewDensity2.pdf}}}\only<3>{\scalebox{0.4}{\includegraphics{NewDensity3.pdf}}}\only<4>{\scalebox{0.4}{\includegraphics{NewDensity4.pdf}}}\only<5>{\scalebox{0.4}{\includegraphics{NewDensity5.pdf}}}\only<6>{\scalebox{0.4}{\includegraphics{NewDensity9.pdf}}}\only<7>{\scalebox{0.4}{\includegraphics{NewDensity10.pdf}}}\only<8>{\scalebox{0.4}{\includegraphics{NewDensity11.pdf}}}\only<9>{\scalebox{0.4}{\includegraphics{NewDensity12.pdf}}}\only<10>{\scalebox{0.4}{\includegraphics{NewDensity13.pdf}}}

\end{frame}

\begin{frame}
\frametitle{Other Reasons to Ensemble (Dietterich 2000) }

Statistical \pause 
\begin{itemize}
\invisible<1>{\item[-] With little data, many algorithms offer similar performance } \pause 
\invisible<1-2>{\item[-] Ensemble ensures we avoid \alert{wrong} model in test set } \pause 
\end{itemize}
\invisible<1-3>{Computational } \pause 
\begin{itemize}
\invisible<1-4>{\item[-] Methods stuck in local modes} \pause 
\invisible<1-5>{\item[-] Result: no one run provides best model} \pause 
\invisible<1-6>{\item[-] Averages of runs may perform better } \pause 
\end{itemize}
\invisible<1-7>{Complex ``true" functional forms } \pause 
\begin{itemize} 
\invisible<1-8>{\item[-] One method may be unable to approximate true DGP } \pause 
\invisible<1-9>{\item[-] Mixtures of methods may approximate better } \pause 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Ensembles Beyond Text Data}

Machine Learning $\leftrightarrow$ Causal Inference

\end{frame}

\begin{frame}
\frametitle{\alert{An Example} Experiment }

\only<1-2>{\invisible<1>{Rep. Harold ``Hal" Rogers (KY-05) announced today that Kentucky is slated to
receive \$962,500 to protect critical infrastructure- power plants, chemical
facilities, stadiums, and other high-risk assets, through the U.S. Department of
Homeland Security's buffer zone protection program} }

\only<3>{A federal grant will help keep the Brainerd Lakes Airport operating in winter
weather. Today, Congressman Jim Oberstar announced that the Federal Aviation
Administration (FAA) will award \$528,873 to the Brainerd airport. The funding
will be used to purchase new snow removal and deicing equipment.}

\only<4>{Congresswoman Darlene Hooley (OR-5) and Congressmen Earl Blumenauer (OR-3),
David Wu (OR-1) and Greg Walden (OR-2) joined together today in announcing
\$375,000 in federal funding for the Oregon Partnership to combat methamphetamine
abuse in Oregon.\\}

\only<5>{What information in credit claiming messages affect evaluations?}

\pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Rewarding Actions and Type of Expenditure, Not Money}

Experiment: vary the \alert{recipient} of money and the \alert{action} reported in credit claiming statement (and many other features)

\invisible<1>{Treatments: \alert<2>{type}}\invisible<1-2>{, \alert<3>{stage}}\invisible<1-3>{, \alert<4>{money}}\invisible<1-4>{, \alert<5>{collaboration}}\invisible<1-5>{, \alert<6>{partisanship}}

%\invisible<1>{Treatments: \alert<2>{type}}\invisible<1-2>{, \alert<3>{stage}} \invisible<1-3>{money, collaboration, and partisanship}

\only<1>{\vspace{1.65in}}
\only<7>{\alert{Control Condition}:}

\only<2>{\begin{itemize}
\item[1)] Planned Parenthood
\item[2)] Parks
\item[3)] Gun Range
\item[4)] Fire Department
\item[5)] Police 
\item[6)] Roads
\end{itemize}
\vspace{0.125in}}

\only<4>{\begin{itemize}
\item[1)] \$50 Thousand
\item[2)] \$20 Million 
\end{itemize}
\vspace{1.05in}}

\only<3>{\begin{itemize}
\item[1)] Will request
\item[2)] Requested
\item[3)] Secured
\end{itemize}
\vspace{0.825in}

}

%\only<4>{ \invisible<1-8>{\begin{itemize}
%\item[1)] Will request
%\item[2)] Request
%\item[3)] Secured
%\end{itemize}
%\vspace{0.825in}
%}}

\only<5>{\begin{itemize}
\item[1)] Alone 
\item[2)] w/ Senate Democrat
\item[3)] w/ Senate Republican 
\end{itemize}
\vspace{.825in}
}

\only<6>{\begin{itemize}
\item[1)] Democrat
\item[2)] Republican
\end{itemize}
\vspace{1.05in}
}

\only<7>{\begin{itemize}
\item[] Advertising press release
\end{itemize}
\vspace{1.125in}
}

\pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Rewarding Actions and Type of Expenditure, Not Money}

\only<1>{Example  Treatment: \\
\textbf{Headline}: Representative [blackbox] \alert{secured} \alert{\$50 Thousand} \alert{to purchase safety equipment for local firefighters}  \\
\textbf{Body}: Representative [blackbox] (\alert{Democrat}) and \alert{Senator [blackbox], a Democrat}, \alert{secured} \alert{\$50 Thousand} \alert{to purchase safety equipment for local firefighters}.  \\
Rep. [blackbox] said ``This money \alert{will help} \alert{our brave firefighters stay safe as they protect our businesses and homes}" \\}

\only<2>{Example Treatment:\\
\textbf{Headline}: Representative [blackbox] \alert{will request} \alert{\$20 million} \alert{for medical equipment at the local Planned Parenthood.}  \\
\textbf{Body}: Representative [blackbox] (\alert{Democrat}), \alert{will request} \alert{\$20 million} \alert{for medical equipment at the local Planned Parenthood}.  \\
Rep. [blackbox] said ``This money \alert{would help} \alert{provide state of the art care for women in our community.}" \\}

\only<3->{
\invisible<1-2>{\alert{214} other conditions} \\
\invisible<1-3>{Dependent variable: Approve of representative}\\

\vspace{0.175in}
\large 
\invisible<1-4>{\alert{Goal} $\leadsto$ measure effect of credit claiming content on approval ratings }
\invisible<1-5>{Mechanics$\leadsto$  Mechanical Turk sample (\alert{Findings are replicated in representative samples, using real representatives/senators}  )}
}

\pause \pause \pause \pause \pause %\pause \pause 
\end{frame}

\begin{frame}
\frametitle{Rewarding Actions and Type of Expenditure, Not Money}

\begin{itemize} 
\item[-] Participant  $i$ ($i=1, \hdots, N$), has treatment assignment $\textbf{T}_{i}$   \\
\invisible<1>{\item[-] If $\text{T}_{i} = 0$ for control condition} \\
\invisible<1-2>{\item[-] $\textbf{T}_{i} = (\text{T}_{i, \text{type}},  \text{T}_{i, \text{stage} },\text{T}_{i, \text{money}},  \text{T}_{i, \text{collab.}}, \text{T}_{i, \text{part.}} )$ }

\invisible<1-3>{\item[-] $Y_{i}(\textbf{T}_{i} )$ : participant $i$'s Approval decision under treatment $\textbf{T}_{i} $}  
\invisible<1-4>{\item[-] \alert{Quantities of Interest} } 
\only<1-10>{\invisible<1-5>{\item[-] Effect of particular component of message: }
\begin{itemize}
\invisible<1-6>{\item[-] T$_{\text{stage}} = $ Secured}
\invisible<1-7>{\item[-] T$_{\text{stage}}  = $ Requested }
\invisible<1-8>{\item[-] T$_{\text{stage}} = $ Will Request } 
\invisible<1-9>{\item[-] T$_{j} = k $} 
\end{itemize}
}

\invisible<1-10>{\item[-]  Marginal Average Treatment Effect  (MATE$_{\text{T}_{j} = k } $) }  
\end{itemize}
\only<1-13>{
\begin{eqnarray}
\invisible<1-11>{\text{MATE}_{\text{T}_{j} = k} & = & \int \text{E}[Y(\text{T}_{j} = k , \textbf{T}_{-j} )  - Y(0) ] \text{d}\text{F}_{\textbf{T}_{-j} | \text{T}_{j} = k } \nonumber \\}
\invisible<1-12>{\text{MATE}_{\text{T}_{j} = k}	& = & \text{E}[Y(\text{T}_{j} = k ) - Y(0) ] \nonumber }
\end{eqnarray}
\vspace{1.5in}

}
\only<14->{		
\begin{eqnarray}
		\text{MATE}_{\text{T}_{j} = k}	& = & \text{E}[Y(\text{T}_{j} = k )|\text{T}_{j} = k ]  - \text{E}[Y(0)|\text{T} = 0 ] \nonumber \\
\invisible<1-14>{\widehat{\text{MATE}_{\text{T}_{j} = k} } & = & 		\frac{\sum_{i=1}^{N} Y_{i} I(\text{T}_{ij} = k)  }{\sum_{i=1}^{N} I(\text{T}_{ij} = k) } - \frac{\sum_{i=1}^{N} Y_{i} I(\text{T}_{i}=0)  }{\sum_{i=1}^{N} I(\text{T}_{i}= 0) } \nonumber								}
\end{eqnarray}										
\vspace{1.5in}
}

\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Rewarding Actions and Type of Expenditure, Not Money}
%(1) Marginal Average Treatment Effect (MATE$_{T_{j} = k } $): $\text{E}[Y(T_{j} = k ) - Y(0) ]$ \\
%\vspace{0.025in} 
%\pause 
\begin{itemize}
\item[-] Response may be conditional on respondent characteristics $\textbf{x}$ \pause \\
\invisible<1>{\item[-] For example $\textbf{x}  = $ (Conservative, Republican)} \pause \\
\invisible<1-2>{\item[-] Marginal Conditional Average Treatment Effect (MCATE$_{\text{T}_{j} = k,\textbf{x}}$)} \pause 
\end{itemize}
\begin{eqnarray}
\invisible<1-3>{\text{MCATE}_{\text{T}_{j} = k,\textbf{x}} & = & \text{E}[Y(\text{T}_{j} = k) - Y(0) | \textbf{x}] }    \nonumber\\
\invisible<1-4>{\text{MCATE}_{\text{T}_{j} = k, \textbf{x}} & = & \text{E}[Y(\text{T}_{j} = k)|\textbf{x} ] - \text{E}[Y(0) | \textbf{x} ] \nonumber }  \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Rewarding Actions and Type of Expenditure, Not Money}
\begin{eqnarray}
\text{MCATE}_{\text{T}_{j} = k, \textbf{x}} & = & \text{E}[Y(\text{T}_{j} = k)|\textbf{x} ] - \text{E}[Y(0) | \textbf{x} ] \nonumber \\
\only<1-8>{\invisible<1>{\widehat{\text{MCATE}_{\text{T}_{j} = k,\textbf{x}}}& = &\frac{\sum_{i=1}^{N} Y_{i} I(\text{T}_{j} = k ,  \textbf{x}_{i} = \textbf{x} )  }{\sum_{i=1}^{N} I(\text{T}_{j} = k , \textbf{x}_{i} = \textbf{x} ) }    - \frac{\sum_{i=1}^{N} Y_{i} I(\text{T}_{i}=0 , \textbf{x}_{i} = \textbf{x})  }{\sum_{i=1}^{N} I(\text{T}_{i}= 0 , \textbf{x}_{i} = \textbf{x}) }  \nonumber } \pause }
\only<9->{
\widehat{\text{MCATE}_{\text{T}_{j} = k,\textbf{x}}} & = & \widehat{g}_{m} (\text{T}_{j} = k, \textbf{x} ) - \widehat{g}_{m}(0, \textbf{x} ) \nonumber 
}
\end{eqnarray}

\begin{itemize}
\invisible<1-2>{\item[-] \alert{Curse of Dimensionality}: highly variable estimates, (sometimes) empty strata} 
\invisible<1-3>{\item[-] Separate systematic differences from noise $\leadsto$ \alert{data} and \alert{assumptions} } \invisible<1-4>{ Heterogeneous treatment effect methods} % ($g_{m} (\text{T}_{j} = k, \textbf{x} ) $)}
\begin{itemize}
\invisible<1-5>{\item[-] LASSO, Find It (Imai and Ratkovic, 2013)$\leadsto$ sparsity} 
\invisible<1-6>{\item[-] Ridge, KRLS (Hainmueller and Hazlett, 2013)$\leadsto$ flexible surface, dense} 
\invisible<1-7>{\item[-] Model $m$ to estimate some function $g_{m}(\text{T}_{j} = k, \boldsymbol{x})$}
\end{itemize}
\invisible<1-8>{\item[-] Perform well: $g_{m}(\text{T}_{j} = k, \boldsymbol{x})$ accurately estimates response surface ($\text{E}[Y(\text{T}_{j} = k)|\textbf{x} ]$)}
\invisible<1-9>{\item[-] Perform well: accurate out of sample prediction and classification (van der Laan et al 2007, Raftery et al 2005) }
\end{itemize}

\invisible<1-10>{Create ensemble: weighting methods by (unique) out of sample predictive performance}

\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Weighted Ensemble to Measure Credit Claiming Rate}

\begin{itemize}
\item[-] Suppose we have $M$ $(m = 1, \hdots, M)$ models.  
\end{itemize}

\begin{eqnarray}
\only<1-13>{\invisible<1>{\widehat{\text{MCATE}_{\text{T}_{j} = k,\textbf{x}}}  & = & \sum_{m=1}^{M} \alert<3>{\widehat{\pi}_{m}} (\alert<4>{\widehat{g}_{m} (\text{T}_{j} = k, \textbf{x} )  }-\alert<4>{\widehat{ g}_{m} (0, \textbf{x} )  })} \nonumber }
\only<14->{\alert{\widehat{\text{MCATE}_{\text{T}_{j} = k,\textbf{x}_{\text{new}}}}  }& = & \sum_{m=1}^{M} \alert{\widehat{\pi}_{m}} (\alert{\widehat{g}_{m} (\text{T}_{j} = k, \textbf{x}_{\text{new}} ) } -\alert{\widehat{ g}_{m} (0, \textbf{x}_{\text{new}} )  } )\nonumber }
\end{eqnarray}

\begin{itemize}
\invisible<1-4>{\item[-] Estimate weights $(\widehat{\pi}_{m})$} 
\only<1-12>{
\begin{itemize}
\invisible<1-5>{\item[-] 10-fold cross validation: generate $M$ out of sample predictions for each observation}
\invisible<1-6>{\item[] $\widehat{\textbf{Y}}_{i}  = (\widehat{Y}_{i1}, \widehat{Y}_{i2}, \hdots, \widehat{Y}_{iM} )$} 
\only<1-11>{\invisible<1-7>{\item[-] Estimate weights with constrained regression:}
\begin{eqnarray}
\invisible<1-8>{Y_{i} & = & \sum_{m=1}^{M} \pi_{m} \hat{Y}_{im} + \epsilon_{i} \nonumber }
\end{eqnarray}
\invisible<1-9>{\item[] where we impose constraints: $\pi_{m} \geq 0 $ and $\sum_{m=1}^{M} \pi_{m} = 1$. } 
\invisible<1-10>{\item[-] Result $\widehat{\pi}_{m}$ for each method } }
\only<12>{\item[-] (Alternatively) Estimate weights from mixture model (EBMA) (Raftery et al 2005;  Montgomery, Hollenback, Ward 2012)$\leadsto$ EM, Gibbs, Variational Approximation} 
\end{itemize}
}
\invisible<1-12>{\item[-] Estimate  $\widehat{g}_{m}(\text{T}_{j} = k, \textbf{x} ) \leadsto $ Apply all $M$ models to entire data set}

\invisible<1-13>{\item[-] Generate effects  of interest (perhaps weighting to other population)  $\textbf{x}_{\text{new}}$ } 
\end{itemize}
%\invisible<1-14>{Applied to this experiment: Positive weight on three methods:} \\
%\invisible<1-15>{(1) LASSO (0.62), (2) KRLS (0.24), (3) Find It (0.14)} 
%\begin{eqnarray}
%\invisible<1-11>{\text{Pr}(Y_{i} = \text{Credit} | \textbf{w}_{i} ) & = & \sum_{m=1}^{M} \widehat{\pi}_{m} \widehat{g}_{m}(\textbf{w}_{i} ) \nonumber } 
%\end{eqnarray}
%\invisible<1-14>{(Classify if above threshold)} \\
%\invisible<1-15>{{\large \alert{90\% accuracy}} }\\

\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause 
\end{frame}

\begin{frame}
\frametitle{Monte Carlo Evidence}
\begin{center}
\only<1>{\scalebox{0.4}{\includegraphics{Plot1.pdf}}}
\only<2>{\scalebox{0.4}{\includegraphics{Plot2.pdf}}}
\only<3->{\scalebox{0.3}{\includegraphics{Plot2.pdf}}}
\end{center}
\only<3->{\large Ensembles outperform constituent methods $\leadsto$ ensembles place weight on  better performing method}

\end{frame}

\begin{frame}
\frametitle{Returning to \alert{Example} Experiment}

\alert{Recall}: experiment to assess effects of credit claiming on approval $\leadsto$ 1,074 participants (MTurk) \pause  \\
\invisible<1>{Apply ensemble method (7 constituent methods, 10 fold cross validation), including treatments and Partisanship and Ideology.  } \pause \\
\invisible<1-2>{Positive  weight on three methods:} \pause 
\begin{itemize}
\invisible<1-3>{\item[1)] LASSO (0.62)} \pause 
\invisible<1-4>{\item[2)] KRLS (0.24)} \pause 
\invisible<1-5>{\item[3)] Find it (0.14) } 
\end{itemize}

\end{frame}

\begin{frame}
\begin{tikzpicture}
\node (dumm) at (-8, 8) [] {} ; 
\only<1-2, 4, 6>{\node (plot1) at (-5, 8) [] {\scalebox{0.25}{\includegraphics{HetExpIdeoFig2.pdf}}}; }
\only<8>{\node (plot_no) at (-3, 8) [] {\scalebox{0.3}{\includegraphics{SmallTypeMoneyIdeology.pdf}}}; }
\only<9->{\node (plot_no) at (-3, 8) [] {\scalebox{0.2}{\includegraphics{SmallTypeMoneyIdeology.pdf}}}; }
\node (d_plan) at (-8, 4.5) [] {} ; 
\node (d_plan3) at (-1.25, 4.5) [] {} ; 
\node (d_plan2) at (-8, 5.75) [] {} ; 
\node (d_plan4) at (-1.25, 5.75) [] {} ;

\only<2>{\draw[-, line width = 2pt, red] (d_plan) to [out = 0, in = 180] (d_plan3) ; 
\draw[-, line width = 2pt, red] (d_plan2) to [out = 0, in = 180] (d_plan4) ; }

\only<3>{\node (plot2) at (-5, 8) [] {\scalebox{0.4}{\includegraphics{HetPlanned.pdf}}}; }

\node (d_gun) at (-8, 6.85) [] {} ; 
\node (d_gun3) at (-1.25, 6.85) [] {} ; 
\node (d_gun2) at (-8, 8.05) [] {} ; 
\node (d_gun4) at (-1.25, 8.05) [] {} ;

\only<4>{\draw[-, line width = 2pt, red] (d_gun) to [out = 0, in = 180] (d_gun3) ; 
\draw[-, line width = 2pt, red] (d_gun2) to [out = 0, in = 180] (d_gun4) ; }

\node (d_gun) at (-8, 9.25) [] {} ; 
\node (d_gun3) at (-1.25, 9.25) [] {} ; 
\node (d_gun2) at (-8, 10.4) [] {} ; 
\node (d_gun4) at (-1.25, 10.4) [] {} ;

\only<5>{\node (plot3) at (-5, 8) [] {\scalebox{0.4}{\includegraphics{HetGun.pdf}}}; }

\only<6>{\draw[-, line width = 2pt, red] (d_gun) to [out = 0, in = 180] (d_gun3) ; 
\draw[-, line width = 2pt, red] (d_gun2) to [out = 0, in = 180] (d_gun4) ; }

\only<7>{\node (plot3) at (-5, 8) [] {\scalebox{0.4}{\includegraphics{HetPolice.pdf}}}; }

\end{tikzpicture}

\only<9>{$\leadsto$ Constituents evaluate expenditures using \alert{qualitative} information, rather than numerical facts}

\pause \pause \pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Ensembles to Estimate Heterogeneous Effects}

Ensembles: prediction, classification, \alert{estimation of heterogeneous effects} \pause \\
\invisible<1>{{\tt R} package$\leadsto$ implement methods, create synthetic observations, visualize results } \pause \\
\invisible<1-2>{\alert{Ensembles} as companion:} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Better individual methods$\leadsto$ better ensembles } \pause 
\invisible<1-4>{\item[-] Evaluate new methods $\leadsto$ more weight from ensemble } \pause 
\begin{itemize}
\invisible<1-5>{\item[1)] Distinct} \pause 
\invisible<1-6>{\item[2)] Accurate} \pause 
\end{itemize}
\end{itemize}

\invisible<1-7>{\alert{Ensembles} $\leadsto$ leverage many contributions to build better estimates.}

\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/tc18.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{November 20th, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Ideological Scaling}
\begin{itemize}
\item[1)] Task
\begin{itemize}
\item[-] Measure political actors' position in policy space
\item[-] Low dimensional representation of beliefs
\end{itemize}
\item[2)] Objective function
\begin{itemize}
\item[-] Linear Discriminant Analysis (ish)$\leadsto$ Wordscores (today)
\item[-] Item Response Theory $\leadsto$ Wordfish 
\item[-] Item Response Theory + Roll Call Votes $\leadsto$ Issue-specific ideal points (12/2)
\end{itemize}
\item[3)] Optimization
\begin{itemize}
\item[-] Wordscores$\leadsto$ straightforward, based on training texts 
\item[-] Wordfish$\leadsto$ EM, MCMC methods
\end{itemize}
\item[4)] Validation
\begin{itemize}
\item[-] What is the goal of embedding?
\item[-] What is the \alert{gold standard}?
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{The Spatial Model}

\begin{itemize}
\item[-] Suppose we have actor $i$ ($i= 1, 2,3, \hdots, N$) \pause \\
\invisible<1>{\item[-] Actor has \alert{ideal point} $\boldsymbol{\theta}_{i} \in \Re^{M}$ } \pause 
\invisible<1-2>{\item[-] We describe actor $i$'s utility from proposal $\boldsymbol{p} \in \Re^{M}$ with utility function} \pause 
\begin{eqnarray}
\invisible<1-3>{u_{i}(\boldsymbol{\theta}_{i}, \boldsymbol{p}) & = & -d(\boldsymbol{\theta}_{i}, \boldsymbol{p}) \nonumber } \pause \\
\invisible<1-4>{& = & -\sum_{l=1}^{L} (\underbrace{\theta_{il}}_{\text{ideal policy}} - p_{l})^2 \nonumber } \pause 
\end{eqnarray}
\end{itemize}

\invisible<1-5>{Estimation goal: $\widehat{\boldsymbol{\theta}}_{i}$\\} \pause 
\invisible<1-6>{\alert{Scaling}$\leadsto$ placing actors in low-dimensional space (like principal components!)}

\end{frame}

\begin{frame}
\frametitle{Estimating Ideal Points: Roll Call Data and the US Congress}

US Congress and Roll Call  \pause 
\begin{itemize}
\invisible<1>{\item[-] Poole and Rosenthal {\tt voteview}} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Roll Call Data$\leadsto$ 1789-Present} \pause 
\invisible<1-3>{\item[-] {\tt NOMINATE} methods$\leadsto$ place legislators on one dimension, estimate of \alert{ideology}} \pause
\end{itemize}
\invisible<1-4>{\item[-] Wildly successful:} \pause
\begin{itemize}
\invisible<1-5>{\item[-] Estimates are accurate: face validity Congressional scholars agree upon} \pause
\invisible<1-6>{\item[-] Insightful$\leadsto$ unidimensional Congress} \pause
\invisible<1-7>{\item[-] Extensible: insight of IRT allows model to be embedded in many forms} \pause
\invisible<1-8>{\item[-] Widely used: hard to write a paper on American political institutions with ideal points} 
\end{itemize}
\end{itemize}

\large
\invisible<1-9>{Why not just use roll call votes?}

\end{frame}

\begin{frame}
\frametitle{Estimating Ideal Points in General}

Two Limitations with the NOMINATE project: \pause 
\begin{itemize}
\invisible<1>{\item[1)] US Congress is distinct}\pause\invisible<1-2>{$\leadsto$ roll call votes fail to measure ideology in other settings} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Weak party pressure$\leadsto$ individual discretion on votes} \pause 
\invisible<1-4>{\item[-] Parliamentary systems$\leadsto$ no discretion, no variation.  } \pause 
\invisible<1-5>{\item[-] Spirling and Quinn (2011)$\leadsto$ mixture model like models for blocs in UK Parliament} \pause
\end{itemize}
\invisible<1-6>{\item[2)] Not everyone votes!} \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Voters$\leadsto$ survey responses (but problems with that)} \pause 
\invisible<1-8>{\item[-] Challengers$\leadsto$ NPAT surveys (but they don't fill those out anymore)} \pause 
\invisible<1-9>{\item[-] Bonica (2013, 2014)$\leadsto$ estimate ideology from donations (but not everyone donates)} 
\end{itemize}

\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Estimating Ideal Points in General}

But Everyone talks! \pause

\begin{itemize}
\invisible<1>{\item[-] If we could \alert{scale} based on conversation, we can measure ideology anywhere} \pause 
\invisible<1-2>{\item[-] Much of the literature$\leadsto$ relies upon intuition from US Congress} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Hard \alert{not} to find ideology} \pause 
\invisible<1-4>{\item[-] Behavior that is primarily ideological} \pause 
\end{itemize}
\invisible<1-5>{\item[-] Reality: scaling is much more difficult than roll call voting examples}\pause 
\begin{itemize}
\invisible<1-6>{\item[-] Hard to find ideology } \pause 
\invisible<1-7>{\item[-] Much of political speech reveals little about position on ideological spectrum$\leadsto$ advertising, regional} \pause 
\end{itemize}
\end{itemize}

\huge

\invisible<1-8>{Healthy skepticism!}

\end{frame}

\begin{frame}

Our plan \pause 
\begin{itemize}
\invisible<1>{\item[1)] Wordscores$\leadsto$ ``supervised" scaling } \pause 
\invisible<1-2>{\item[2)] Wordfish$\leadsto$ single dimension} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle<1>{Wordscores$\leadsto$ Big in Europe}
\frametitle<2>{Wordscores, Like the Hoff$\leadsto$ Big in Europe}
\pause 
\only<2>{\scalebox{0.5}{\includegraphics{Hasselhoff.jpg}}}

\end{frame}

\begin{frame}
\frametitle{Wordscores: Objective Function}

For each legislator $i$, suppose we observe $D_{i}$ documents.  \pause \\
\invisible<1>{Define:} \pause 
\begin{eqnarray}
\invisible<1-2>{\boldsymbol{x}_{i} & = & \sum_{l = 1}^{D_{i} } \boldsymbol{x}_{il} \nonumber } \pause \\
\invisible<1-3>{& = &  \sum_{l = 1}^{D_{i} } (x_{il1}, x_{il2}, \hdots, x_{ilJ}) \nonumber } \pause 
\end{eqnarray}

\invisible<1-4>{$\boldsymbol{x}_{i}\leadsto$ aggregation across documents.  \\}

\end{frame}

\begin{frame}
\frametitle{Wordscores: Objective Functions}

Choose two legislators as \alert{exemplars} \pause 
\begin{itemize}
\invisible<1>{\item[-] Legislator $L \in \{1, 2, \hdots, N\}$ is \alert{liberal}.  $Y_{L} = - 1$} \pause 
\invisible<1-2>{\item[-] For example, might select \alert{Elizabeth Warren} } \pause 
\invisible<1-3>{\item[-] Legislator $C \in \{1, 2, \hdots, N\}$ is \alert{Conservative}.  $Y_{C} = 1$ } \pause 
\invisible<1-4>{\item[-] For example, might select \alert{Ted Cruz}} \pause 
\end{itemize}

\invisible<1-5>{For each word $j$ we can define:} \pause 
\begin{eqnarray}
\invisible<1-6>{P_{jL} & = & \text{Probability of word from Liberal} \nonumber \\} \pause 
\invisible<1-7>{P_{jC} & = & \text{Probability of word from Conservative} \nonumber } \pause 
\end{eqnarray}

\invisible<1-8>{Define the \alert{score} for word $j$} \pause 
\begin{eqnarray}
\invisible<1-9>{S_{j} & = & Y_{C} P_{jC} + Y_{L} P_{jL} \nonumber \\} \pause 
\invisible<1-10>{& = & P_{jC} - P_{jL} \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Wordscores: Objective Functions}

Scale other legislators: \pause 
\begin{eqnarray}
\invisible<1>{N_{i} & = & \sum_{j=1}^{J}  \boldsymbol{x}_{i}  \nonumber } 
\end{eqnarray}
\pause

\invisible<1-2>{$\hat{\theta}_{i}$ is } \pause 
\begin{eqnarray}
\invisible<1-3>{\hat{\theta}_{i} & = & \sum_{j=1}^{J} \left(\frac{x_{ij}}{N_{i}} \right)S_{j} \nonumber } \pause \\
\invisible<1-4>{ & = & \frac{\boldsymbol{x}_{i}^{'}}{N_{i} }\boldsymbol{S} \nonumber }
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Wordscores: Optimization}

\begin{eqnarray}
N_{L} & = & \sum_{m=1}^{J} x_{mL} \nonumber \\
N_{C} & = & \sum_{m=1}^{J} x_{mC} \nonumber 
\end{eqnarray}
\pause
\invisible<1>{Estimate $P_{jL}$, $P_{jC}$, and $S_{j}$} \pause 
\begin{eqnarray}
\invisible<1-2>{P_{jL} & = & \frac{ \frac{x_{jL}}{N_{L}}}{\frac{x_{jL}}{N_{L}} + \frac{x_{jC}}{N_{C}}  } \nonumber \\} \pause
\invisible<1-3>{P_{jC} & = &  1 - P_{jL} = \frac{ \frac{x_{jC}}{N_{C}}}{\frac{x_{jL}}{N_{L}} + \frac{x_{jC}}{N_{C}}  } \nonumber \\} \pause
\invisible<1-4>{S_{j} & = & P_{jC} - P_{jL} \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Applied to the Senate Press Releases}

$L = $ Ted Kennedy\\
$C = $ Tom Coburn \\
Apply to other senators.

\end{frame}

\begin{frame}
\frametitle<1>{Applying to Senate Press Releases$\leadsto$ Gold Standard Scaling from NOMINATE}
\frametitle<2>{Applying to Senate Press Releases$\leadsto$ WordScores}
\only<1>{\scalebox{0.5}{\includegraphics{Votes1.pdf}}} 
\only<2>{\scalebox{0.45}{\includegraphics{WordScores.pdf}} }

\end{frame}

\begin{frame}
\frametitle{Supervised Scaling}

Wordscores is one example of \alert{supervised} embedding: \pause 
\begin{itemize}
\invisible<1>{\item[1)] Linear Discriminant Analysis (LDA)$\leadsto$ the Federalist Papers} \pause 
\invisible<1-2>{\item[2)] Multinomial Inverse Regression} \pause 
\invisible<1-3>{\item[3)] \alert{Any method that separates words}} \pause 
\end{itemize}

\invisible<1-4>{The findings will depend \alert{heavily} on supervision} \pause
\begin{itemize}
\invisible<1-5>{\item[-] Sensitive to who is chosen} \pause 
\invisible<1-6>{\item[-] False prediction problem$\leadsto$ speech accomplishes many goals, only some of which are ideological} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{What Can Go Wrong with Wordscores?}

Lowe (2008): Discusses potentially problematic wordscores properties \pause 
\begin{itemize}
\invisible<1>{\item[1)] Each word is weighted equally (fixable with different scoring procedure) } \pause
\invisible<1-2>{\item[2)] Unique words are conflated with centrist (fixable with MCQ fightin' words style algorithm)} \pause 
\invisible<1-3>{\item[3)] General problem: \alert{hard to interpret}$\leadsto$ lack of a model}\pause 
\end{itemize}

\invisible<1-4>{\alert{To be fair}: fast, nonparametric, and novel [trailblazing] method for scoring documents  (starts conversation)}
\end{frame}

\begin{frame}
\frametitle{Unsupervised Embedding}

Basic idea: \pause 
\begin{itemize}
\invisible<1>{\item[-] Actors have underlying \alert{latent} position} \pause 
\invisible<1-2>{\item[-] Actors articulate that latent position in their speech} \pause 
\invisible<1-3>{\item[-] This is associated with word usage, so high discriminating words correspond to ideological speech } \pause
\invisible<1-4>{\item[-] Some words \alert{discriminate} better than others$\leadsto$ encode that in our model} \pause 
\end{itemize}

\invisible<1-5>{Simplest model: Principal Components}

\end{frame}

\begin{frame}
\frametitle{Application of Principal Components in {\tt R}}

Consider press releases from 2005 US Senators \pause \\
\invisible<1>{Define $\boldsymbol{x}_{i} = (x_{i1}, x_{i2}, \hdots, x_{iJ})$ as the rate senator $i$ uses $J$ words.  }\pause 
\begin{eqnarray}
\invisible<1-2>{x_{ij} & = & \frac{\text{No. Times $i$ uses word $j$}}{\text{No. words $i$ uses}} \nonumber } \pause 
\end{eqnarray}

\invisible<1-3>{{\tt  dtm}: $100 \times 2796$ matrix containing word rates for senators\\} \pause 
\invisible<1-4>{{\tt prcomp(dtm) } applies principal components}

\end{frame}

\begin{frame}
\frametitle{Application of Principal Components in {\tt R}}

\only<1>{\scalebox{0.5}{\includegraphics{FirstPrinComp.pdf}}}
\only<2>{\scalebox{0.5}{\includegraphics{CreditClaimPrinComp.pdf}}}

\end{frame}

\begin{frame}
\frametitle{Probabilistic Unsupervised Embeddings}

Principal components is powerful\pause\invisible<1>{$\leadsto$ statistical model for unsupervised scaling\\} \pause
\invisible<1-2>{\alert{Item Response Theory} (IRT)} \pause

\begin{itemize}
\invisible<1-3>{\item[-] Origins: educational testing} \pause
\invisible<1-4>{\item[-] Jackman (2002), Clinton, Jackman, and Rivers (2004) apply to roll call voting} \pause
\invisible<1-5>{\item[-] Power of IRT:} \pause 
\begin{itemize}
\invisible<1-6>{\item[a)] Estimate ideal points with few observations} \pause
\invisible<1-7>{\item[b)] \alert{Makes clear how to extend models}} \pause
\invisible<1-8>{\item[c)] Tuesday$\leadsto$ IRT and topic models to scale with votes + text} \pause
\end{itemize}
\invisible<1-9>{\item[-] Clinton, Jackman, and Rivers (2004)$\leadsto$ intuition about IRT} \pause
\invisible<1-10>{\item[-] Rivers (2002)$\leadsto$ Identification conditions} \pause
\invisible<1-11>{\item[-] Bonica (2014a, 2014b)$\leadsto$ uses IRT (like the one we're about to use) to scale donors} \pause
\end{itemize}

\invisible<1-12>{Monroe and Maeda (2005) and \alert{Slopkin and Proksch} (2008) develop similar algorithms} 
\end{frame}

\begin{frame}
\frametitle{WordFish Objective Function}

Suppose we have legislator $i$. \pause   \\

\begin{eqnarray}
\invisible<1>{x_{ij} & \sim & \text{Poisson}(\lambda_{ij} )  \nonumber \\} \pause
\invisible<1-2>{\lambda_{ij} & = & \exp(\alpha_{i} + \psi_{j} + \beta_j \times \theta_{i} ) \nonumber } \pause 
\end{eqnarray}
\invisible<1-3>{Where, } \pause 
\begin{eqnarray}
\invisible<1-4>{\lambda_{ij} & = & \text{Rate individual $i$ uses word $j$ } \nonumber \\} \pause 
\invisible<1-5>{\alpha_{i} & = & \text{Individual $i$ loquaciousness}  \nonumber \\} \pause 
\invisible<1-6>{\psi_{j} & = & \text{Word $j$'s frequency} \nonumber \\} \pause 
\invisible<1-7>{\beta_{j} &= & \text{Word $j$'s discrimination} \nonumber \\} \pause 
\invisible<1-8>{\theta_{i} & = & \text{Legislator $i$'s latent positions} \nonumber } \pause 
\end{eqnarray}

\invisible<1-9>{``Regression" of $x_{ij}$ on ideal points $\theta_{i}$, where we have to learn $\theta_{i}$}

\end{frame}

\begin{frame}
\frametitle{WordFish Objective Function/Optimization}

Implies the following posterior distribution:\pause 
\begin{small}
\begin{eqnarray}
\invisible<1>{p(\boldsymbol{\theta}, \boldsymbol{\alpha}, \boldsymbol{\psi}, \boldsymbol{\beta}) & \propto & p(\boldsymbol{\alpha}) p(\boldsymbol{\beta}) p(\boldsymbol{\psi}) p(\boldsymbol{\theta}) \times \nonumber \\}
\invisible<1>{&& \prod_{i=1}^{N} \prod_{j=1}^{J} \frac{\exp\left[ - \left(\alpha_{i} + \psi_{j} + \beta_j \times \theta_{i}\right)   \right] (\alpha_{i} + \psi_{j} + \beta_j \times \theta_{i})^{x_{ij}}}{x_{ij}!} \nonumber }
\end{eqnarray}
\end{small}
\pause
\invisible<1-2>{Estimate parameters:} \pause
\begin{itemize}
\invisible<1-3>{\item[-] EM-algorithm} \pause 
\invisible<1-4>{\item[-] MCMC algorithm} \pause
\invisible<1-5>{\item[-] Variational Approximation}  \pause 
\end{itemize}

\invisible<1-6>{{\tt Wordfish} package in {\tt R}}

\end{frame}

\begin{frame}
\frametitle<1>{Applications: German Party Manifestos}
\frametitle<2>{Applications: German Party Manifestos}

\only<1>{\scalebox{0.5}{\includegraphics{WordFish1.pdf}}}
\only<2>{\scalebox{0.5}{\includegraphics{WordFish3.pdf}}}

\end{frame}

\begin{frame}
\frametitle{The Problem with Text-Based Scaling}

What does validation mean?
\begin{itemize}
\item[1)] Replicate NOMINATE, DIME, or other gold standards?
\item[2)] Agreement with experts
\item[3)] Prediction of other behavior
\end{itemize}

Must answer this to make progress on pure text scaling

\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/tc19.tex
normal update

--- 2017-12-10 resources/text_as_data/tc17.tex
@@
 
-\date{November 18th, 2014}%[Big Data Workshop] 
+\date{December 2nd, 2014}%[Big Data Workshop] 
 %\date{\today}
@@
 \begin{frame}
-\frametitle{Final Project}
+\frametitle{Poster Session}
 
-Poster Session: 12/4 \pause \\
-\begin{itemize}
-\invisible<1>{\item[-] Make posters in \LaTeX\ or related software for asthetics} \pause 
-\invisible<1-2>{\item[-] Landscape orientation is preferable} \pause 
-\invisible<1-3>{\item[-] \alert{Less is More}} \pause 
-\end{itemize}
-\invisible<1-4>{Papers Due: 12/12, 5pm {\huge \alert{This is a hard deadline}!}} \pause 
-\begin{itemize}
-\invisible<1-5>{\item[-] An academic paper$\leadsto$ appropriate for your field} \pause 
-\begin{itemize}
-\invisible<1-6>{\item[-] Succinct (not cute) title} \pause 
-\invisible<1-7>{\item[-] Abstract that explains your contribution} \pause 
-\invisible<1-8>{\item[-] Introduction that explains why your paper exists} \pause 
-\invisible<1-9>{\item[-] Presentation of Results} \pause 
-\invisible<1-10>{\item[-] Avoid: Long/breezy lit reviews that merely list previous scholarship} 
-\end{itemize}
+Thursday.  Set up begins at 9am, take down (promptly!) at 11am\\
 
-\end{itemize}
+Please email me a copy of your poster\\
+
+Please attend!!!
 
@@
 \begin{frame}
-\frametitle{Supervised Learning: Ensemble Learning}
+\frametitle{Causal Inference and Text}
+
+\begin{small}
 \begin{itemize}
-\item[1)] Task \pause 
+\item[1)] Task
 \begin{itemize}
-\invisible<1>{\item[-] Subsidize hand coding$\leadsto$ learn a rule between labels and features} \pause 
+\item[i)] Assess the effect of a text
+\begin{itemize}
+\item[-] Advertisement
+\item[-] Argument
 \end{itemize}
-\invisible<1-2>{\item[2)] Objective function } \pause 
-\begin{eqnarray}
-\invisible<1-3>{\text{Pr}(Y_{i} = C_{k} | \boldsymbol{x}_{i} ) & = & f(\boldsymbol{x}_{i}, \boldsymbol{\beta}, \boldsymbol{\lambda}) \nonumber } \pause 
-\end{eqnarray}
+\item[ii)] Assess a text based response 
 \begin{itemize}
-\invisible<1-4>{\item[-] ``Coefficients" $\boldsymbol{\beta}$} \pause 
-\invisible<1-5>{\item[-] Tuning parameters $\boldsymbol{\lambda}$} \pause 
-\invisible<1-6>{\item[-] Functional form $f$} \pause 
-\invisible<1-7>{\item[-] \alert{Necessarily requires consequential assumptions}} \pause 
-\invisible<1-8>{\item[-] Ensembles: aggregate classifiers to increase performance} \pause 
+\item[-] Open ended responses (Roberts et al, 2014)
+\item[-] Politicians + rhetoric 
 \end{itemize}
-\invisible<1-9>{\item[3)] Optimization} \pause 
+\item[iii)] Condition on text for selection on observable
 \begin{itemize}
-\invisible<1-10>{\item[-] Optimization of individual classifiers$\leadsto$ methods already discussed} \pause 
-\invisible<1-11>{\item[-] Determination of weights on models$\leadsto$ equal (bagging), out of sample performance via cross validation (super learning)} \pause 
-\end{itemize}
-\invisible<1-12>{\item[4)] Validation} \pause 
-\begin{itemize}
-\invisible<1-13>{\item[-] Out of sample predictive performance} 
+\item[-] Popularity of Clerics, given prior rhetoric (Nielsen, 2014)
 \end{itemize}
 \end{itemize}
+\item[2)] Objective Function
+\begin{itemize}
+\item[-] Depends on Setting
+\end{itemize}
+\item[3)] Optimization: 
+\begin{itemize}
+\item[-] Depends on Setting
+\end{itemize}
+\item[4)] Validation
+\begin{itemize}
+\item[-] Assumptions$\leadsto$ proofs for identification
+\item[-] Simulations$\leadsto$ strain identification assumptions, observe behavior
+\item[-] Sensitivity analysis $\leadsto$ examine sensitivity of analysis to assumptions
+\end{itemize}
+\end{itemize}
+\alert{Many Open Questions!}
+\end{small}
+\end{frame}
+
+\begin{frame}
+\frametitle{A Causal Inference Refresher}
+
+\pause
+
+\begin{itemize}
+\invisible<1>{\item[-] Suppose we have $N$ units, $i = 1, \hdots, N$.\\} \pause 
+\invisible<1-2>{\item[-] Each unit receives treatment $\boldsymbol{T}_{i}$ (potentially vector valued)} \pause 
+\invisible<1-3>{\item[-] Suppose we have (potentially vector valued) response $\boldsymbol{Y}_{i}(\boldsymbol{T}_{i})$} \pause 
+\begin{itemize}
+\invisible<1-4>{\item[-] Unit $i$'s response to treatment $\boldsymbol{T}_{i}$ } \pause 
+\invisible<1-5>{\item[-] Function: maps from treatments to responses} \pause 
+\end{itemize}
+\invisible<1-6>{\item[-] Fundamental problem of causal inference observe only one $\boldsymbol{Y}_{i}(\boldsymbol{T}_{i})$ } \pause 
+\invisible<1-7>{\item[-] Quantity of interest:} \pause 
+\begin{itemize}
+\invisible<1-8>{\item[-] Simplest (yet very powerful) case$\leadsto$ $T_{i} \in \{0, 1\}$, $Y_{i}(T_{i}) \in \{0, 1\}$} \pause 
+\begin{eqnarray}
+\invisible<1-9>{\text{ATE} & = & E[Y(1) - Y(0)]  \nonumber } \pause 
+\end{eqnarray}
+\invisible<1-10>{\item[-] Estimate with: } \pause 
+\begin{eqnarray}
+\only<1-12>{\invisible<1-11>{\widehat{\text{ATE}} & = & E[Y(1)| T= 1] - E[Y(0)| T = 0 ] \nonumber } }
+\only<13->{\widehat{\text{ATE}} & = & \frac{\sum_{i=1}^{N} I(T_{i} = 1) Y_{i}}{ \sum_{i=1}^{N} I(T_{i} = 1) } - \frac{\sum_{i=1}^{N} I(T_{i} = 0) Y_{i}}{ \sum_{i=1}^{N} I(T_{i} = 0) }} \nonumber 
+\end{eqnarray}
+\pause 
+\end{itemize}
+\end{itemize}
+
+\pause 
+\invisible<1-13>{Question: how do we \alert{accurately} estimate quantities like ATE?}
 
@@
 \begin{frame}
-\frametitle{Ensemble Learning: Intuition}
+\frametitle{Our Plan for the Day}
 
-\alert{Heuristic} (upon which we'll improve):\pause\invisible<1>{ if classifiers are \alert{accurate} and \alert{diverse}$\rightarrow$ ensemble methods improve} \pause \\
-\invisible<1-2>{\alert{Intuition}: } \pause 
 \begin{itemize}
-\invisible<1-3>{\item[-] Classify documents into two categories (Category 1, Category 2). }  \pause 
-\invisible<1-4>{\item[-] True labels: evenly distributed across two categories}  \pause 
-\invisible<1-5>{\item[-] Three classifiers with $75\%$ accuracy, but independent  }\pause 
-\invisible<1-6>{\item[-] Implement majority voting rule  }\pause 
+\item[-] Experimental research design
+\begin{itemize}
+\alert{\item[1)] Many potential treatments$\leadsto$ text based treatments}
+\alert{\item[2)] Text based responses}
 \end{itemize}
-\begin{eqnarray}
-\invisible<1-7>{\text{Pr(Correct Guess}| \text{Votes} )} \pause \invisible<1-8>{ & = & \text{Pr(3 correct)} + \text{Pr(2 correct)} } \pause \nonumber \\
- \invisible<1-9>{& = & 0.75^3 + 3 \times (0.75^2 \times 0.25)} \pause  \nonumber \\
-  \invisible<1-10>{& = &  0.844 \nonumber }
-  \end{eqnarray}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Ensemble Learning: Intuition}
-
-\only<1>{\scalebox{0.45}{\includegraphics{Ensemble1.pdf}}}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Ensemble Learning: Intuition}
-
-\alert{Diverse} and \alert{Accurate} matter.
-
-\only<1>{\scalebox{0.45}{\includegraphics{Ensemble2.pdf}}} 
-\only<2>{\scalebox{0.45}{\includegraphics{Ensemble3.pdf}}}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Wisdom of the Crowds:}
-
-Goal: estimate a document's category$\leadsto$ $Y \in \{0, 1\}$ \pause \\
-\invisible<1>{Classifiers: (suppose) a sequence of identically distributed (\alert{not independent}) random variables. } \pause  \\
-\invisible<1-2>{Suppose $Y = 1$} \pause \\
-\invisible<1-3>{Guess from classifer $m$ is $B_{m}$ with Pr$(B_{i} = 1) = p>0.5$.  \\} \pause 
-\begin{eqnarray}
-\invisible<1-4>{\bar{B} & = & \sum_{m=1}^{M} \frac{B_{m}}{M} \nonumber } \pause 
-\end{eqnarray}
-
-\invisible<1-5>{\alert{Wisdom of crows} (Condorcet Jury Theorem)} \pause 
-\begin{eqnarray}
-\invisible<1-6>{\lim_{M\rightarrow \infty} P(\bar{B}> 0.5) & = & 1 \nonumber } 
-\end{eqnarray}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Wisdom of the Crowds}
-
-Suppose $B_{m}$ have variance $\sigma^2$ and pairwise correlation $\rho$. \pause   \\
-\invisible<1>{Then, } \pause
-
-\begin{eqnarray}
-\invisible<1-2>{\text{var}(\bar{B}) }\pause\invisible<1-3>{& = & \text{var}\left(\sum_{i=1}^{M} \frac{B_{i}}{M}  \right)} \pause  \nonumber \\
- \invisible<1-4>{& = & \frac{1}{M^{2}} \sum_{i=1}^{M} \text{var}\left(B_{i}\right) + \frac{2}{M^2} \sum_{i<j} \text{cov}(B_{i}, B_{j}) \nonumber } \pause\\
- \invisible<1-5>{& = & \frac{M \sigma^2}{M^2}  + \frac{2}{M^2} \rho \sigma^2 {{M}\choose{2}} \nonumber } \pause\\
-\invisible<1-6>{& = & \underbrace{\rho \sigma^2}_{\text{Resolve with independence}} + \underbrace{\frac{1 - \rho}{M} \sigma^2}_{\text{Resolve with $\uparrow$classifiers}} \nonumber } 
-\end{eqnarray}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{\alert{Bagging}: bootstrap aggregation}
-
-\begin{small}
-Creating Weak Classifiers with resampling: \pause 
+\item[-] Observational research design
 \begin{itemize}
-\invisible<1>{\item[-] Suppose we have labels $\boldsymbol{Y}$ and document term matrix $\boldsymbol{X}$} \pause
-\invisible<1-2>{\item[-] For each bootstrap step $m$, $(m = 1,2, \hdots, M)$ draw $N$ observations with replacement, $\tilde{\boldsymbol{Y}}_{m}$, $\tilde{\boldsymbol{X}}_{m}$.  } \pause 
-\invisible<1-3>{\item[-] Train classifier on bootstrapped data, } \pause 
-\begin{eqnarray}
-\invisible<1-4>{\tilde{\boldsymbol{Y}}_{m} & = & f^{m}(\tilde{\boldsymbol{X}}_{m}, \widehat{\boldsymbol{\beta}}, \boldsymbol{\lambda} ) \nonumber } \pause 
-\end{eqnarray}
-\invisible<1-5>{\item[-] Aggregating across classifiers, } \pause 
-\begin{eqnarray}
-\invisible<1-6>{f_{\text{bag}}(\boldsymbol{x}_{i}) & = & \frac{1}{M} \sum_{m=1}^{M} f^{m}(\tilde{\boldsymbol{X}}_{m}, \widehat{\boldsymbol{\beta}}, \boldsymbol{\lambda}) \nonumber } \pause 
-\end{eqnarray}
-\invisible<1-7>{\item[-] Only leads to a difference in estimate if classifiers are non-linear. } \pause 
-\invisible<1-8>{\item[-] Strong Correlation between classifiers}
-\end{itemize}
-\end{small}
-\end{frame}
-
-\begin{frame}
-\frametitle{Classification and Regression Trees (CART): Intuition}
-
-Consider regression $E[Y|\boldsymbol{x}_{i}]$. \pause  \\
-\invisible<1>{With no assumptions, \alert{stratify}$\leadsto$ different mean for unique values of $\boldsymbol{x}_{i}$\\} \pause
-\begin{itemize}
-\invisible<1-2>{\item[-] Within each strata $p$, compute average $Y$} \pause 
-\begin{eqnarray}
-\invisible<1-3>{\bar{Y}|\boldsymbol{x}_{p} & = & \sum_{i=1}^{N} \frac{I(\boldsymbol{x}_{i} = \boldsymbol{x}_{p})Y_{i}}{\sum_{t=1}^{N} I(\boldsymbol{x}_{t} = \boldsymbol{x}_{p}) } \nonumber } \pause 
-\end{eqnarray}
+\item[3)] Condition on prior texts
 \end{itemize}
 
-\invisible<1-4>{Implies that for test data we would fit:} \pause
-
-\begin{eqnarray}
-\invisible<1-5>{\hat{f}(\boldsymbol{x}_{i}) & = & \sum_{p=1}^{P} \bar{Y}|\boldsymbol{x}_{p}  I(\boldsymbol{x}_{i} = \boldsymbol{x}_{p}) \nonumber }\pause\\
-\invisible<1-6>{& = & \sum_{p=1}^{P} c_{p}  I(\boldsymbol{x}_{i} = \boldsymbol{x}_{p}) \nonumber }\pause 
-\end{eqnarray}
-
-\invisible<1-7>{Curse of dimensionality(!!!)\\} \pause 
-\invisible<1-8>{Approximate with \alert{regions}$\leadsto$ search for splits of data to approximate stratification}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Classification and Regression Trees (CART): Objective function}
-
-Labels $\boldsymbol{Y}_{i}$ and documents $\boldsymbol{x}_{i}$
-
-\begin{eqnarray}
-E[Y| \boldsymbol{x}_{i}] & = & \widehat{f}(\boldsymbol{x}_{i}) \nonumber \\
-& = & \sum_{p=1}^{P} c_{p} I (\boldsymbol{x}_{i} \in R_{p}) \nonumber 
-\end{eqnarray}
-
-where:
-\begin{itemize}
-\item[-] $R_{p}$ describes a \alert{region} $\leadsto$ node
-\item[-] $c_{p}$ describes values of $Y_{i}$ for document in $R_{p}$
 \end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Classification and Regression Trees (CART): Optimization function}
-
-Suppose we want to minimize sum of squared residuals with each \alert{node}\\ \pause
-
-\invisible<1>{Then $c_{p} = $ Average $Y$ for documents assigned to $R_{p}$ \\} \pause 
-\begin{eqnarray}
-\invisible<1-2>{\widehat{c}_{p} & =&  \sum_{i=1}^{N} \frac{Y_{i} I(\boldsymbol{x}_{i} \in R_{p} )  }{\sum_{j=1}^{N} I(\boldsymbol{x}_{j} \in R_{p} )  } \nonumber } \pause
-\end{eqnarray}
-
-\invisible<1-3>{Determining an optimal partition$\leadsto$ NP-Hard.  \\} \pause 
-\invisible<1-4>{Suppose we are in some node (perhaps at the start).  \\} \pause 
-\invisible<1-5>{Greedy algorithm:} \pause 
-\begin{footnotesize}
-\begin{eqnarray}
-\invisible<1-6>{(j^{*}, s^{*})  & = & \text{arg min}_{j, s} \left[ \underbrace{\text{min}_{c_{1}} \sum_{i=1}^{N}I(x_{ij}< s)(Y_{i} - c_{1})^2}_{\text{``cost" group 1}}  + \underbrace{\text{min}_{c_{2}} \sum_{i=1}^{N}I(x_{ij}> s)(Y_{i} - c_{2})^2}_{\text{``cost" group 2}}   \right] \nonumber }
-\end{eqnarray}
-\end{footnotesize}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Classification and Regression Trees (CART): Algorithm}
-
-\begin{itemize}
-\item[-] Start in Node
-\item[-] Partition according to Greedy algorithm
-\item[-] Continue until some stopping rule: number of observations per node
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{CART Picture (Spirling 2008)}
-
-\scalebox{0.7}{\includegraphics{CART_Example.png}}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Forests and Trees}
-
-Recall: accurate (unbiased) and uncorrelated classifiers \pause 
-\begin{itemize}
-\invisible<1>{\item[-] Grow trees deeply$\leadsto$ unbiased classifers, though high variance} \pause
-\invisible<1-2>{\item[-] \alert{Average}$\leadsto$ reduces variance, but will be correlated} \pause 
-\invisible<1-3>{\item[-] Random forest$\leadsto$ introduce additional sampling to induce independence$\leadsto$ Only split on subset of variables} 
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Random Forest Algorithm (ESL, 588)}
-
-\pause 
-\begin{itemize}
-\invisible<1>{\item[1)] For $m$ bootstrap samples $(m = 1,\hdots, M)$, draw $N$ observations with replacement, $\tilde{\boldsymbol{Y}_{m}}, \tilde{\boldsymbol{X}_{m}}$} \pause 
-\invisible<1-2>{\item[2)] Until a minimum node size is reached:} \pause 
-\begin{itemize}
-\invisible<1-3>{\item[i)] \alert{Select $z$ of the $J$ variables}$\leadsto$ introduces independences across the trees} \pause 
-\invisible<1-4>{\item[ii)] Among those $z$, select the best split node} \pause 
-\invisible<1-5>{\item[iii)] Split into daughter nodes} \pause 
-\end{itemize}
-\invisible<1-6>{\item[3)] The result is an ensemble (forest) of trees $\boldsymbol{T} = (T_{1}, T_{2}, \hdots, T_{M})$, } \pause 
-\begin{eqnarray}
-\invisible<1-7>{\hat{f}(\boldsymbol{x}_{i}) & = & \frac{1}{M} \sum_{m=1}^{M} T_{m} (\boldsymbol{x}_{i}) \nonumber } \pause 
-\end{eqnarray}
-\end{itemize}
-
-\invisible<1-8>{{\tt RandomForest}$\leadsto$ Not a silver bullet!} \pause 
-\begin{itemize}
-\invisible<1-9>{\item[-] With many poor predictors$\leadsto$ the $p$ selected may be meaningless} 
-\end{itemize}
-
-\end{frame}
-
-% \begin{frame}
-% \frametitle{Common Ensemble Methods}
-
-% \alert{Boosting}: sequential training of weak classifiers
-% \begin{itemize}
-% \item[-] Method for combining several \alert{weak} classifiers
-% \item[-] Basic idea: 
-% \begin{itemize}
-% \item[-] Model 1: classify initially based on all data (equal weight)
-% \item[-] Model 2: classify all data, more weight to incorrectly classified data
-% \item[-] Model 3: classify all data, more weight to incorrectly classified data
-% \item[] $\hdots $
-% \item[-] Model M: classify all data, more weight to incorrectly classified data
-% \end{itemize}
-% \item[-] Aggregate using weighted committee 
-% \end{itemize}
-
-% \end{frame}
-
-\begin{frame}
-\frametitle{Super Learning}
-
-\begin{itemize}
-\item[1) ] Set of hand labeled documents.  For each $i$, $(i=1, \hdots, N_{\text{train}})$
-\begin{itemize}
-\invisible<1>{\item[] $Y_{i, \text{train} } \in \{C_{1} C_{2}, \hdots C_{K} \}$}
-\end{itemize}
-\invisible<1-2>{\item[2)] Estimate relationship between labels and words } 
-\begin{itemize}
-\invisible<1-3>{\item[-] Each document $i$  is a \alert{count vector} of $K$ words} 
-\invisible<1-4>{\item[] $ \textbf{x}_{i, \text{train}}  =  (X_{i1}, X_{i2}, \hdots, X_{iK}  )$ } \nonumber 
-\end{itemize}
-\end{itemize}
-
-\only<1->{
-\begin{eqnarray}
-\invisible<1-5>{\text{Pr}(Y_{i} = C_{k} | \textbf{x}_{i} )\invisible<1-6>{_{\text{train}}}\invisible<1-7>{& = & \widehat{g} (\textbf{x}_{i} )_{\text{train}} } \nonumber }
-\end{eqnarray}
-} 
-%\only<7->{
-%\begin{eqnarray}
-%\text{Pr}(Y_{i}  = \text{Credit} | \textbf{w}_{i} )_{\text{train}} \invisible<1-7>{& = & \widehat{g} (\textbf{w}_{i} )_{\text{train}} } %\nonumber 
-%\end{eqnarray}
-%}
-
-\begin{itemize}
-\invisible<1-7>{\item[-] Identify systematic relationship between words, labels}  \invisible<1-8>{$\leadsto$ Data and \alert{assumptions}}
-\begin{itemize}
-\invisible<1-9>{\item[-] LASSO (Tibshirani 1996): \alert{sparsity} }
-\invisible<1-10>{\item[-] KRLS (Hainmueller and Hazlett 2013): \alert{dense}, flexible surface}
-\invisible<1-11>{\item[-] Ridge, Elastic-Net, SVM, Random Forests, BART, ...}
-\end{itemize}
-\invisible<1-12>{\item[-] Which model?  Difficult to know before hand}
-\invisible<1-13>{\item[-] Assess out of sample performance with \alert{cross validation}}
-\end{itemize}
-\invisible<1-14>{\alert{Weighted ensemble}: weights determined by (unique) out of sample predictive performance}
-
-\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause 
-\end{frame}
-
-\begin{frame}
-
-Committee Methods:\\
-
-Fit many methods, average with equal weights
-
-\begin{itemize}
-\item[-] Voting (classification)
-\item[-] Averaging (predictions) 
-\end{itemize}
-
-Problem: many poor methods may overwhelm high quality fit (remember earlier figures)\\
-Solution: learn weights via cross validation
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Weighted Ensemble to Classify Documents}
-
-\begin{itemize}
-\item[-] Suppose we have $M$ $(m = 1, \hdots, M)$ models.  
-\end{itemize}
-\begin{eqnarray}
-\invisible<1>{\alert<14->{\text{Pr}(Y_{i}   =  \text{C}_{1} | \textbf{x}\only<1-13>{_{i}}\only<14->{_{i,\text{test}}} )_{\text{train}} } & = & \alert<14->{  \sum_{m=1}^{M} \alert<3>{\widehat{\pi}_{m} } \alert<4>{\widehat{g}_{m}(\textbf{x}\only<1-13>{_{i}}\only<14->{_{i, \text{test}}} )}} \nonumber }
-\end{eqnarray}
-
-\begin{itemize}
-\invisible<1-4>{\item[-] Estimate weights $(\widehat{\pi}_{m})$} 
-\only<1-11>{
-\begin{itemize}
-\invisible<1-5>{\item[-] K-fold cross validation: generate $M$ out of sample predictions for each document in training set}
-\invisible<1-6>{\item[] $\widehat{\textbf{Y}}_{i}  = (\widehat{Y}_{i1}, \widehat{Y}_{i2}, \hdots, \widehat{Y}_{iM} )$} 
-\invisible<1-7>{\item[-] Estimate weights with constrained regression:}
-\begin{eqnarray}
-\invisible<1-8>{Y_{i} & = & \sum_{m=1}^{M} \pi_{m} \hat{Y}_{im} + \epsilon_{i} \nonumber }
-\end{eqnarray}
-\invisible<1-9>{\item[] where we impose constraints: $\pi_{m} \geq 0 $ and $\sum_{m=1}^{M} \pi_{m} = 1$. } 
-\invisible<1-10>{\item[-] Result $\widehat{\pi}_{m}$ for each method } 
-\end{itemize}
-}
-\invisible<1-11>{\item[-] Estimate  $\widehat{g}_{m}(\textbf{x}_{i} ) \leadsto $ Apply all $M$ models to entire training set} 
-\end{itemize}
-\invisible<1-12>{3) For each document $i$ in test set, $\textbf{x}_{i, \text{test}}$ } \\
-%\begin{eqnarray}
-%\invisible<1-11>{\text{Pr}(Y_{i} = \text{Credit} | \textbf{w}_{i} ) & = & \sum_{m=1}^{M} \widehat{\pi}_{m} \widehat{g}_{m}(\textbf{w}_{i} ) \nonumber } 
-%\end{eqnarray}
-\invisible<1-14>{(Classify if above threshold)} \\
-
-\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause 
-\end{frame}
-
-\begin{frame}
-
-\scalebox{0.6}{\includegraphics{SuperLearner.png}}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Why Super Learn?}
-
-van der Laan et al (2007) prove:
-\begin{itemize}
-\item[-] \alert{Asymptotically}: super learners will perform as well the \alert{best} candidates for data 
-\item[-] \alert{Oracle}: performs like the best possible method among candidate methods
-\begin{itemize}
-\item[-] Asymptotically outperforms constituent methods
-\item[-] Performs as well as optimal combinations of those methods
-\end{itemize}
-\end{itemize}
-
-Practical questions:
-\begin{itemize}
-\item[-] Final regression: 
-\begin{itemize}
-\item[-] Logistic
-\item[-] Linear 
-\item[-] \alert{Could super learn again!}
-\end{itemize}
-\item[-] How Many Folds?
-\begin{itemize}
-\item[-] van der Laan et al's proofs rely on growing folds with $N$ (but slowly)
-\item[-] Use 10-fold cross validation for simulations
-\end{itemize}
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Impression of Influence}
-
-Estimate: $Y_{i} \in \{\text{Credit}, \text{Not Credit} \}$ \pause \\
-\begin{itemize}
-\invisible<1>{\item[-] Triple hand code 800 press releases} \pause 
-\invisible<1-2>{\item[-] Resolve disagreement with voting$\leadsto$ few disagreements} \pause
-\end{itemize}
-
-\invisible<1-3>{Use five classifiers to form Ensemble (cross validating within each to tune parameters)}\pause 
-\begin{itemize}
-\invisible<1-4>{\item[-] LASSO} \pause \invisible<1-9>{0} 
-\invisible<1-5>{\item[-] Elastic-Net}\pause \invisible<1-9>{ 23\%} 
-\invisible<1-6>{\item[-] Random Forest} \pause \invisible<1-9>{61\%} 
-\invisible<1-7>{\item[-] A Support Vector Machine}\pause \invisible<1-9>{16\%} 
-\invisible<1-8>{\item[-] Kernel Regularized Least Squares (KRLS, Hainmueller and Hazlett 2014)}\pause \invisible<1-9>{ 0} 
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Strategic Credit Claiming to Build a Personal Vote}
-
-\begin{tikzpicture}
-\node (dummy1) at (-8, 8) [] {} ; 
-\node at (-6, 8) [] {\scalebox{0.4}{\includegraphics{DensTikz.pdf}}};
-
-\invisible<1>{\node (trial) at (-8.75,5.7) [] {} ; 
-\only<1-9>{\node(Burton) at (-10, 10) [] {\scalebox{0.5}{\includegraphics{Burton.jpg}}}; 
-\draw[->, line width = 1.5pt] (Burton) to [out = 270, in = 90] (trial) ; }
-
-\only<3>{\node (McGroff) at (-3, 11) [] {\alert{John McGroff}: ``voted for every spending bill "} ; }
-\only<3>{\node (McGroff2) at (-3, 10.6) [] {that went through the office"} ;}
-\only<4>{\node (McGroff3) at (-3, 11) [] {\alert{John McGroff}:  ``Not the actions of a fiscally "};}
-\only<4>{\node (McGroff4) at (-3, 10.6) [] {conservative congressman who } ; } 
-\only<4>{\node (McGroff5) at (-3, 10.2) [] {cares about personal responsibility"}; }
-}
-%\invisible<1-4>{\node (Price) at (-10, 8) [] {\scalebox{0.2}{\includegraphics{Price.jpg}}} ; 
-%\node (trial1) at (-8.7,5.7) [] {} ; 
-%\draw[->, line width = 1.5pt] (Price) to [out = 0, in = 90] (trial1) ; }
-
-\only<1-9>{
-\invisible<1-4>{\node (Flake) at (-8.2, 11) [] {\scalebox{0.1}{\includegraphics{Flake.jpg}}} ; 
-\node (trial2) at (-8.6,5.7) [] {} ; 
-\draw[->, line width = 1.5pt] (Flake) to [out = 270, in = 90] (trial2) ; }
-
-\invisible<1-5>{\node (Degette) at (-10, 6) [] {\scalebox{0.1}{\includegraphics{Jan.jpg}}} ; 
-\node (trial3) at (-8.65, 5.7) [] {} ; 
-\draw[->, line width = 1.5pt] (Degette) to [out = 30, in = 90] (trial2) ; }
-
-\invisible<1-6>{\node (Lobiondo) at (-6, 10) [] {\scalebox{0.08}{\includegraphics{Lobiondo.jpg}}} ; 
-\node (trial4) at (-5.1, 5.7) [] {} ; 
-\draw[->, line width = 1.5pt] (Lobiondo) to [out = 270, in = 90] (trial4) ; }
-
-\invisible<1-7>{\node (Lobiondo) at (-4, 9.5) [] {\scalebox{0.125}{\includegraphics{Edwards.jpg}}} ; 
-\node (trial5) at (-4.95, 5.7) [] {} ; 
-\draw[->, line width = 1.5pt] (Lobiondo) to [out = 270, in = 90] (trial5) ; }}
-
-\invisible<1-8>{\node (Rogers) at (-1.8, 11) [] {\scalebox{0.15}{\includegraphics{Rogers.jpg}}}; 
-\node (trial6) at (-2.4, 5.7) [] {} ; 
-\draw[->, line width = 1.5pt] (Rogers) to [out = 270, in = 90] (trial6) ; }
-
-\only<10>{\node (Pork1) at (-7, 11)  [] {``We just can't afford luxuries like ideology" } ; } 
-\only<11>{\node (Pork2) at (-7, 11)  [] {Lexington Herald-Leader: \alert{Prince of Pork}} ; }
-
-\end{tikzpicture}
-
-\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause
-
-%\only<1>{\scalebox{0.4}{\includegraphics{DensTikz.pdf}}}
-%\only<1>{\scalebox{0.4}{\includegraphics{NewDensity1.pdf}}}\only<2>{\scalebox{0.4}{\includegraphics{NewDensity2.pdf}}}\only<3>{\scalebox{0.4}{\includegraphics{NewDensity3.pdf}}}\only<4>{\scalebox{0.4}{\includegraphics{NewDensity4.pdf}}}\only<5>{\scalebox{0.4}{\includegraphics{NewDensity5.pdf}}}\only<6>{\scalebox{0.4}{\includegraphics{NewDensity9.pdf}}}\only<7>{\scalebox{0.4}{\includegraphics{NewDensity10.pdf}}}\only<8>{\scalebox{0.4}{\includegraphics{NewDensity11.pdf}}}\only<9>{\scalebox{0.4}{\includegraphics{NewDensity12.pdf}}}\only<10>{\scalebox{0.4}{\includegraphics{NewDensity13.pdf}}}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Other Reasons to Ensemble (Dietterich 2000) }
-
-Statistical \pause 
-\begin{itemize}
-\invisible<1>{\item[-] With little data, many algorithms offer similar performance } \pause 
-\invisible<1-2>{\item[-] Ensemble ensures we avoid \alert{wrong} model in test set } \pause 
-\end{itemize}
-\invisible<1-3>{Computational } \pause 
-\begin{itemize}
-\invisible<1-4>{\item[-] Methods stuck in local modes} \pause 
-\invisible<1-5>{\item[-] Result: no one run provides best model} \pause 
-\invisible<1-6>{\item[-] Averages of runs may perform better } \pause 
-\end{itemize}
-\invisible<1-7>{Complex ``true" functional forms } \pause 
-\begin{itemize} 
-\invisible<1-8>{\item[-] One method may be unable to approximate true DGP } \pause 
-\invisible<1-9>{\item[-] Mixtures of methods may approximate better } \pause 
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Ensembles Beyond Text Data}
-
-Machine Learning $\leftrightarrow$ Causal Inference
 
@@
 \begin{frame}
-\frametitle{Ensembles to Estimate Heterogeneous Effects}
+\frametitle{Estimating Heterogeneous Treatment Effects and the Effects of Heterogeneous Treatments}
 
-Ensembles: prediction, classification, \alert{estimation of heterogeneous effects} \pause \\
-\invisible<1>{{\tt R} package$\leadsto$ implement methods, create synthetic observations, visualize results } \pause \\
-\invisible<1-2>{\alert{Ensembles} as companion:} \pause 
+Issues with experimental design \pause 
 \begin{itemize}
-\invisible<1-3>{\item[-] Better individual methods$\leadsto$ better ensembles } \pause 
-\invisible<1-4>{\item[-] Evaluate new methods $\leadsto$ more weight from ensemble } \pause 
+\invisible<1>{\item[-] Treatments are conditional on what else is included: averaging other quantities $\neq$ to excluding other quantities} \pause 
+\invisible<1-2>{\item[-] Potential for \alert{fishing} is massive$\leadsto$ \alert{pre analysis plan}} \pause 
+\invisible<1-3>{\item[-] Assumption about the way information delivered:} \pause 
 \begin{itemize}
-\invisible<1-5>{\item[1)] Distinct} \pause 
-\invisible<1-6>{\item[2)] Accurate} \pause 
+\invisible<1-4>{\item[1)] We know salient dimensions} \pause 
+\invisible<1-5>{\item[2)] We're constructing effects that correspond with effects in reality} 
 \end{itemize}
@@
 
-\invisible<1-7>{\alert{Ensembles} $\leadsto$ leverage many contributions to build better estimates.}
+\end{frame}
+
+\begin{frame}
+\frametitle{The Causal Effect of Texts?}
+
+\pause 
+\invisible<1>{More general framework.  \\} \pause 
+\invisible<1-2>{Suppose we have text $j$, $j = 1, 2, \hdots, J$,  $\boldsymbol{T}_{j}$.   \\} \pause 
+\invisible<1-3>{Potential outcome is: $Y_{i} (\boldsymbol{T}_{j} )$\\} \pause 
+\invisible<1-4>{Question: how do we encode the information in $\boldsymbol{T}_{j}$ to find effects?} 
+\end{frame}
+
+\begin{frame}
+\frametitle{Text as the Response}
+
+\pause 
+\invisible<1>{Suppose we have some dichotomous treatment $T_{i} \in \{0, 1\}$. \\} \pause 
+\invisible<1-2>{Outcome: some text based response $\boldsymbol{Y}_{i}(T_{i}) $:} \pause 
+\begin{itemize}
+\invisible<1-3>{\item[-] Treatment:} \invisible<1-4>{marginal legislators}\invisible<1-5>{, issue frame}\invisible<1-6>{, negative emotion words} 
+\invisible<1-3>{\item[-] Potential outcome:} \invisible<1-4>{press releases}\invisible<1-5>{, open ended survey response}\invisible<1-6>{, subsequent Facebook posts} 
+\end{itemize}
+
+\pause \pause \pause
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Text as the Response$\leadsto$ Assumed Categories}
+
+Set of predetermined categories: \pause \invisible<1>{ $\{C_{1}, C_{2}, \hdots, C_{K} \}$\\} \pause 
+\begin{itemize}
+\invisible<1-2>{\item[-] Classify the texts$\leadsto$ hand coding or supervised learning} \pause 
+\begin{itemize}
+\invisible<1-3>{\item[-] Each document now an indicator vector $\boldsymbol{L}_{i}$} \pause 
+\end{itemize}
+\invisible<1-4>{\item[-] Straightforward estimator } \pause 
+\begin{eqnarray}
+\invisible<1-5>{\text{ATE}_{k}  & = & \frac{ \sum_{i=1}^{N} I (L_{i k} = 1, T_{i} = 1)}{ \sum_{i=1}^{N} I (T_{i} = 1) } - \frac{ \sum_{i=1}^{N} I (L_{i k} = 1, T_{i} = 0)}{ \sum_{i=1}^{N} I (T_{i} = 0) }\nonumber } \pause
+\end{eqnarray}
+\invisible<1-6>{\item[-] Additional (or usual?) concern: measurement error } 
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Text as the Response$\leadsto$ Unsupervised Categories}
+
+Structural Topic Models \pause \invisible<1>{$\leadsto$ suppressing priors} \pause
+
+\begin{eqnarray}
+\invisible<1-2>{\boldsymbol{\pi}_{i} & \sim & \text{Logistic Normal}(\boldsymbol{\beta}_{0} + \boldsymbol{\beta}_{1}\boldsymbol{T}_{i}, \boldsymbol{\Sigma}) \nonumber \\} \pause 
+\invisible<1-3>{\boldsymbol{\tau}_{im} & \sim & \text{Multinomial}(1, \boldsymbol{\pi}_{i}) \nonumber \\} \pause 
+\invisible<1-4>{x_{im} | \tau_{imk} = 1 & \sim & \text{Multinomial}(\boldsymbol{\theta}_{k}) \nonumber \\} \pause 
+\invisible<1-5>{\theta_{kj} & \propto & \exp\left( \gamma_{j} + \gamma_{jk1} T_{i}     \right) \nonumber } \pause 
+\end{eqnarray}
+
+\begin{itemize}
+ \invisible<1-6>{\item[-] Quantity 1: Topic prevalence } \pause 
+ \begin{itemize}
+  \invisible<1-7>{\item[-] $\boldsymbol{\beta}_{1}   =   (\beta_{11}, \beta_{12}, \hdots, \beta_{1K}) $} \pause 
+  \invisible<1-8>{\item[-] $\beta_{1k}  = $ change in attention to topic $k$ for treated units in logistic-normal space} \pause 
+\end{itemize}
+ \invisible<1-9>{\item[-] Quantity 2: Topic Content } \pause 
+\begin{itemize}
+ \invisible<1-10>{\item[-] $\gamma_{jk1}  = $ change in prevalence of word $j$ for topic $k$ for treated units} \pause 
+\end{itemize}
+\end{itemize}
+
+ \invisible<1-11>{Parameters (mapped back to appropriate space) are used for effect estimates}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Topic Prevalence}
+\begin{center}
+
+\only<1>{Gadarian and Albertson: 
+\begin{itemize}
+\item[1)] Treatment: worry about immigration
+\item[2)] Control (treatment 2): think about immigration
+\item[3)] Response: open ended survey prompt about immigration
+\end{itemize}
+}
+\only<2>{\scalebox{0.55}{\includegraphics{MainEffects1.png}}}
+\only<3>{\scalebox{0.75}{\includegraphics{ModerateEffects1.png}}}
+\end{center}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Topic Content}
+
+\only<1>{
+Rand, Greene and Nowak: one-shot public goods game
+\begin{itemize}
+\item[1)] Treatment: encourage to think intuitively
+\item[2)] Control (treatment 2): encourage to think strategically
+\item[3)] Response: open ended response on strategy
+\item[4)] Different in topic content by gender
+\end{itemize}
+}
+\begin{center}
+\only<2>{\scalebox{0.6}{\includegraphics{GenderDifferences.png}}}
+\end{center}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Estimating the Effect of Treatment with Text Response}
+
+What do you when treatment affects the categories (not just attention to categories)? \pause
+
+\begin{itemize}
+\invisible<1>{\item[1)] What are the quantities of interest?} \pause 
+\begin{itemize}
+\invisible<1-2>{\item[-] They are a function of the treated quantities}\pause\invisible<1-3>{$\leadsto$ categories depend on treatment}\pause
+\end{itemize}
+\invisible<1-4>{\item[2)] What are the conditions for accurate estimation? (identification)} \pause 
+\begin{itemize}
+\invisible<1-5>{\item[-] Take an expectation to compute bias, but categories change with each treatment arrangement} 
+\end{itemize}
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Text as Data: Going Forward}
+
+\pause 
+\begin{itemize}
+\invisible<1>{\item[-] What we've done} \pause 
+\begin{itemize}
+\invisible<1-2>{\item[-] Text preprocessing$\leadsto$ variable recipe} \pause 
+\invisible<1-3>{\item[-] Text tasks} \pause 
+\begin{itemize}
+\invisible<1-4>{\item[-] Separating words$\leadsto$ Fightin' words} \pause 
+\invisible<1-5>{\item[-] Embedding$\leadsto$ principal components } \pause 
+\invisible<1-6>{\item[-] Unsupervised methods$\leadsto$ clustering, topic models} \pause 
+\invisible<1-7>{\item[-] Supervised methods $\leadsto$ LASSO, Ridge} \pause 
+\invisible<1-8>{\item[-] Ideology } \pause 
+\end{itemize}
+\end{itemize}
+\invisible<1-9>{\item[-] A lot left to do:} \pause 
+\begin{itemize}
+\invisible<1-10>{\item[-] Text preprocessing} \pause 
+\begin{itemize}
+\invisible<1-11>{\item[-] Natural language processing techniques} \pause 
+\invisible<1-12>{\item[-] Bringing along other information$\leadsto$ synonyms, previous sentences, etc} \pause 
+\end{itemize}
+\invisible<1-13>{\item[-] Machine learning$\leadsto$ scratched the surface} \pause 
+\begin{itemize}
+\invisible<1-14>{\item[-] Classification methods } \pause 
+\invisible<1-15>{\item[-] Unsupervised methods} \pause 
+\invisible<1-16>{\item[-] Deep learning} \pause 
+\end{itemize}
+\end{itemize}
+\end{itemize}
+
+\begin{large}
+\invisible<1-17>{Course theme: \alert{think} what is the social scientific purpose of the task?} 
+\end{large}
 

### 2017-12-10 resources/text_as_data/tc3.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\newcommand{\argmin}{\arg\!\min}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
 \numberwithin{equation}{section}

%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{September 30th, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

%%Introduction: who is in the class
%%what are they working on

\begin{frame}
\frametitle{Our Class Approach}

\begin{itemize}
\item[1)] Choose task
\item[2)] Decide on objective function
\begin{eqnarray}
f(\boldsymbol{\theta}, \boldsymbol{X}) \nonumber
\end{eqnarray}
\item[3)] Optimize object function over parameters $\boldsymbol{\theta}$
\end{itemize}

\pause

\invisible<1>{Part of model$\leadsto$ creating $\boldsymbol{X}$}

\end{frame}

\begin{frame}
\frametitle{Goal for Today: Document-Term Matrices}

\begin{eqnarray}
\boldsymbol{X} & = & \begin{pmatrix}
1 & 0 & 0 & \hdots & 3 \\
0 & 2 & 1 & \hdots & 0 \\
\vdots & \vdots & \vdots & \ddots & \vdots \\
0 & 0 & 0 & \hdots & 5 \\
\end{pmatrix} \nonumber 
\end{eqnarray}

$\boldsymbol{X} = \alert<2>{N} \times \alert<3>{K}$ matrix

\begin{itemize}
\invisible<1>{\item[-] $N = $ Number of documents} 
\invisible<1-2>{\item[-] $K = $ Number of features} 
\end{itemize}

\pause \pause

\end{frame}

\begin{frame}
\frametitle{Learning From Text}

A plan for using texts
\begin{itemize}
\item[1)] Acquiring text data
\item[2)] Regular expression search in text
\item[3)] Creating document-term matrices (term-document matrices)
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Finding Text Data } 
Many places to find text (which we we'll review) \pause

\invisible<1>{Goal: plan text (.txt) file. (UTF-8, ASCII) \\} \pause 
\invisible<1-2>{(May also want to create an {\tt XML} or {\tt JSON} file) } 
\end{frame}

\begin{frame}
\frametitle<1>{Plain Text}
\frametitle<2>{XML}
\only<1>{
{\tt 
                    September 19, 2010 Sunday 10:46 AM  EST\\ 
                    REP. FOXX VISITS LOCAL SCHOOLS, TALKS WITH STUDENTS ON CONSTITUTION DAY \\
                   	LENGTH: 320  words\\ 
                   	CLEMMONS, N.C., Sept. 17 -- Rep. Virginia Foxx, R-N.C. (5th CD), issued the following press release:\\
                   	Congresswoman Virginia Foxx is celebrating Constitution Day today by visiting several schools in her district to talk with students about the Constitution and the individuals who helped create our charter document. She will visit Davie County High School, Forbush High School in Yadkin County and Piney Creek School in Alleghany County. 
}
}

\only<2>{
{\tt 
$<$DOC$>$\\
$<$DOCNO$>$101-levin-mi-1-19901027$<\//$DOCNO$>$\\
$<$TEXT$>$\\
Mr. LEVIN. Mr. President, today the House passed and sent to the President the Great Lakes Critical Programs Act. ... Mr. President, I commend and thank Ms. Bean for her exceptional efforts on the Great Lakes Critical Programs Act\\
$<\//$TEXT$>$\\ 
$<\//$DOC$>$
}
}

\end{frame}

\begin{frame}
\frametitle{JSON}

{\tt 
\{"id":"tag:search.twitter.com,2005:287886850381713411",\\"objectType":"activity"...displayName":"Linda Bowersox",\\"postedTime":"2010-03-10T05:16:14.000Z"...\\"body":"@JeffFlake thank you for standing firm and voting NO on the \#FiscalCliff (via \#PJNET)","object"...
}

\end{frame}

\begin{frame}
\frametitle{Prepackaged Data Sources}

{\tt http://dfr.jstor.org}

\scalebox{0.5}{\includegraphics{dfr.png}}

\end{frame}

\begin{frame}
\frametitle{Prepackaged Data Sources}

Lexis Nexis (and other data base sources) \pause

\begin{itemize}
\invisible<1>{\item[1)] Batch search and download} \pause 
\invisible<1-2>{\item[2)] \alert{Do not try to scrape Lexis Nexis(!!!!)}} \pause 
\end{itemize}

\invisible<1-3>{Application Programming Interface (APIs)} \pause

\begin{itemize}
\invisible<1-4>{\item[-] Facilitate interaction with applications (like Twitter)} \pause 
\invisible<1-5>{\item[-] Download data (often in JSON format)$\leadsto$ Twitter, Data.gov, ...} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Books, Archives, and Other Non-Digital Material}

\only<1>{\scalebox{0.35}{\includegraphics{ScannedBook.png}}}
\only<2->{
	\begin{itemize}
\item[1)] Create images of texts
\invisible<1-2>{\item[2)] \alert{O}ptical \alert{C}haracter \alert{R}ecognition} 
\begin{itemize}
\invisible<1-3>{\item[-] Built in Adobe Pro} 
\invisible<1-4>{\item[-] Abbyy FineReader (Batch processing)} 
\invisible<1-5>{\item[-] Tesseract (Google, command line tool)}
\end{itemize}
\invisible<1-6>{\item[3)] Also use, e-book formats...}
	\end{itemize}

}

\pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Acquiring Data from Web: Automated Web Collection}

\only<1>{\scalebox{0.5}{\includegraphics{tonko_press.png}}}
\only<2>{\scalebox{0.3}{\includegraphics{TonkoSource.png}}}
\only<3>{\begin{center}\scalebox{0.4}{\includegraphics{TonkoPyCode.png}}  \end{center}}
\only<4-5>{\scalebox{0.35}{\includegraphics{TonkoPress.png}}}
%07Nov2009Tonko6.txt

\invisible<1-4>{This week's assignment: ``scrape" a presidential debate:
\begin{itemize}
\item[-] {\tt http://www.crummy.com/software/BeautifulSoup/}
\item[-] Parse paragraphs, label speakers
\end{itemize}
}
\end{frame}

\begin{frame}
\frametitle{Acquiring Data from Web: Distributed Human Computing}
Amazon.com's \alert{Mechanical Turk}

\begin{itemize}
\item[-] Marketplace for \alert{H}uman \alert{I}tensive \alert{T}asks
\item[-] Requester (you): create HITs, offer \$ (about \$0.05 per task)
\item[-] Workers (bored + broke people): complete task
\item[-] Requester: evaluate and pay
\end{itemize}

Odesk, elance, ...

\end{frame}

\begin{frame}

\huge 
You have text, now what?

\end{frame}

\begin{frame}
\frametitle{Regular Expressions (from Jurafsky Slides) }

\begin{center}
\scalebox{0.35}{\includegraphics{RegExXKCD.png}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Systematic Searches}

A language for searching texts:  
\begin{itemize}
\item[-] Count mentions of a person
\item[-] Calculate amount of money discussed
\item[-] Prepare texts for analysis: Identify where to ``split" a document
\item[-] ...
\end{itemize}

Provide a quick introduction here, with some examples

\end{frame}

\begin{frame}
\frametitle{Regular Expressions, Some Basics (from Jurafsky Slides) }

%%Do the slides where there are the basics of how to computer regular expressions
%%False Negative/ False positive rates.  
%%Include cheating detection as a closely related tool.  
%%Show how to apply this with a few examples before launching in earnest to the bag of words

%%Then, show how to do this in both python and R 
%%python has the advantage of being easier to write files
%%the R example can show how to count incidence of something happening

%%wcopyfind for uptake and joint press releases

\begin{itemize}
\item[-] Disjunctions
\end{itemize}
\begin{center}
\begin{tabular} {lll} 
\textbf{RE} & \textbf{Match} & \textbf{Example Patterns Matched}\\
{\tt [mM]oney } & Money or money  & ``\underline{Money}" \\
{\tt [abc] } & `a', `b', \emph{or} `c'  & ``Investing in Ir\underline{a}n" \\
               &                              & ``is d\underline{a}ngerous \underline{b}usiness"\\
{\tt [1234567890]} & any digit &     ``sitting on \$\underline{7}.\underline{5} billion dollars"      \\
   &   & ``\underline{2}\underline{0}\underline{0}\underline{5} and \underline{2}\underline{0}\underline{0}\underline{6}, more than " \\
   &  &   ``\$\underline{1}\underline{5}\underline{0} million  dollars"    \\
{\tt [$\backslash$.] } & A period &`` `Run!', he screamed\underline{.}" 
\end{tabular}
\end{center}

\end{frame}

\begin{frame} 
\frametitle{Regular Expressions, Some Basics (from Jurafsky Slides) } 
\begin{itemize}
\item[-] Ranges 
\end{itemize}
\begin{center}
\begin{tabular} {lll} 
\textbf{RE} & \textbf{Match} & \textbf{Example Patterns Matched}\\
{\tt [A-Z]}  & an upper case letter   & ``\underline{R}ep. \underline{A}nthony \underline{W}einer\\
  &    &   (\underline{D}-\underline{B}rooklyn \& \underline{Q}ueens)" \\
{\tt [a-z]}  & a lower case letter &   ``ACORN'\underline{s}" \\
{\tt [0-9]}  & a single digit  & ``(\underline{9}th CD) " 
\end{tabular}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Regular Expressions, Some Basics (from Jurafsky Slides) } 
\begin{itemize}
\item[-] Negations 
\end{itemize}
\begin{center}
\begin{tabular}{lll}
\textbf{RE} & \textbf{Match} & \textbf{Example Patterns Matched}\\
{\tt [\^{}A-Z] } & not an upper case letter &  ``ACORN\alert{\underline{'}\underline{s}}" \\
{\tt[\^{}Ss] } & neither `S' nor `s' & ``\alert{\underline{ACORN'}}s" \\
{\tt[\^{}\textbackslash.] } & not a period & `` `\underline{Run!', he screamed}." \\
\end{tabular}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Regular Expressions, Some Basics (from Jurafsky Slides) } 
\begin{itemize}
\item[-] Optional Characters: {\tt ?}, {\tt *}, {\tt +} 
\end{itemize}
\begin{center}
\begin{tabular}{lll}
\textbf{RE} & \textbf{Match} & \textbf{Example Patterns Matched}\\
{\tt colou?r } &  Words with {\tt u}  0 or 1 times& ``\underline{color}"  or \\
                   &                                & ``\underline{colour} " \\
{\tt oo*h!}     & Words with {\tt o}  0 or more times & ``\underline{oh!}" or \\
                      &                                                   &   ``\underline{ooh!}" or \\
                       &                                                   &   ``\underline{oooh!}" \\ 
{\tt o+h!} &   Words with {\tt o} 1 or more times & ``\underline{oh!}" or \\
  &                                                   &   ``\underline{ooh!}" or \\
    &                                                   &   ``\underline{oooooh!}" or \\                       
\end{tabular}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Regular Expressions, Some Basics (from Jurafsky Slides) } 
\begin{itemize}
\item[-] Wild Cards \alert{{\tt .} } 
\end{itemize}
\begin{center}
\begin{tabular}{lll}
\textbf{RE} & \textbf{Match} & \textbf{Example Patterns Matched}\\
{\tt beg\alert{.}n} & Any word with ``beg" then ``n" & ``beg\textcolor{blue}{i}n" or \\
                          &                                            &  ``beg\textcolor{blue}{a}n" or \\
                          &                                            &  ``beg\textcolor{blue}{u}n" or \\
                          &                                            &  ``beg\textcolor{blue}{g}n" (Poor grammar!)

 \end{tabular}
 \end{center}

 \end{frame}

\begin{frame}
\frametitle{Regular Expressions, Some Basics (from Jurafsky Slides) }

\begin{itemize}
\item[-] Start of the line anchor \alert{\^{}}, end of the line anchor \alert{\$}
\end{itemize}

\begin{center}
\begin{tabular}{lll}
\textbf{RE} & \textbf{Match} & \textbf{Example Patterns Matched}\\
{\tt \alert{\^{}}[A-Z] } & Upper case start of line & ``\underline{P}alo Alto" \\
                            &                                                        & ``the town of \textcolor{gray}{P}alo Alto" \\
{\tt \alert{\^{}}[\^{}A-Z] } & Not upper case start of line &      ``\underline{t}he town of Palo Alto" \\
                            &                                                        & ``\textcolor{gray}{P}alo Alto" \\
{\tt \alert{\^{}}.} & Start of line  & ``\underline{P}alo Alto" \\
                            &                                                        & ``\underline{t}he town of Palo Alto" \\
{\tt .\alert{\$} }      & Identify character that ends a line &    ``Wait\alert{\underline{!}}" \\
                              &                                                & ``This is the end\alert{\underline{.}}" \\

 \end{tabular}
 \end{center}

\end{frame}

\begin{frame}
\frametitle{Regular Expressions, Some Basics (from Jurafsky Slides) }

\begin{itemize}
\item[-] ``Or"$|$ statements, Useful short hand 
\end{itemize}
\begin{center}
\begin{tabular}{lll}
\textbf{RE} & \textbf{Match} & \textbf{Example Patterns Matched}\\
yours$|$mine & Matches``yours" or ``mine" & ``it's either \underline{yours} or \underline{mine}"\\
$\backslash$ d  & Any digit  & ``\underline{1}-Mississippi" \\
$\backslash$ D  & Any non-digit & ``1\underline{-Mississippi}" \\
$\backslash$ s & Any whitespace character & ``1,\underline{ }2"\\
$\backslash$ S & Any non-whitespace character & ``\underline{1,} \underline{2}" \\
$\backslash$ w & Any alpha-numeric  &  ``\underline{1}-\underline{Mississippi} " \\
$\backslash$ W & Any non-alpha numeric & ``1\underline{-}Mississippi"  \\
\end{tabular}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Regular Expressions, Some Basics (from Jurafsky Slides) } 
Quick Example to Illuminate Differences:

A ``simple" example: identify all instances of \alert{{\tt the}}. \pause

\begin{itemize}
\invisible<1>{\item[-] \alert{{\tt the } }} \pause 
\invisible<1-2>{\item[] Misses capitalized examples} \pause 
\invisible<1-3>{\item[-] \alert{{\tt [tT]he}}} \pause 
\invisible<1-4>{\item[] Returns words that are too long ({\tt theocrat}, {\tt theme} )} \pause 
\invisible<1-5>{\item[-] \alert{[\^{}a-zA-Z][tT]he[\^{}a-zA-Z] }} \pause 
\invisible<1-6>{\item[] Misses the first ``the" in a sentence } \pause 
\invisible<1-7>{\item[-] \alert{(\^{} $|$ [\^{} a-zA-Z])[tT]he[\^{} a-zA-Z] } } 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{An Example: Searching for Tea Party Language}

\only<1-4>{Grimmer, Westwood, and Messing (2014): Criticism and credit \\}
\only<5>{Goodman, Grimmer, Parker, Zlotnik (2014): Criticism}

\begin{center}
\only<1-2>{\invisible<1, 3->{
\scalebox{0.475}{\includegraphics{BigGovernment.pdf}}
}}

\only<3>{
\scalebox{0.475}{\includegraphics{BudgetDeficit.pdf}}
}

\only<4>{
\scalebox{0.475}{\includegraphics{AntiDemRepPlot.pdf}}
}

\only<5>{

\scalebox{0.475}{\includegraphics{TeaPartShiftPress.pdf}}

}

\end{center}

\end{frame}

\begin{frame}
\frametitle{Regular Expressions on Steroids: Cheating Detection Software}

\begin{itemize}
\item[-] WCopyFind:
\begin{footnotesize}
{\tt http://plagiarism.bloomfieldmedia.com/z-wordpress/software/wcopyfind/} \pause \end{footnotesize}
\invisible<1>{\item[-] What constitutes \alert{plagiarism}?} \pause 
\invisible<1-2>{\item[-] \alert{Edit distance}: } \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Heuristically: how many letters to change from $a$ to $b$ } \pause 
\end{itemize}
\invisible<1-4>{\item[-] Sets many parameters: } \pause 
\begin{itemize}
\invisible<1-5>{\item[-] Number of differences between pair of ``strings"} \pause 
\invisible<1-6>{\item[-] Length of character strings to consider} \pause 
\invisible<1-7>{\item[-] Number of matching strings to constitute match} \pause 
\end{itemize}
\invisible<1-8>{\item[-] Useful:} \pause 
\begin{itemize}
\invisible<1-9>{\item[-] Media uptake} \pause 
\invisible<1-10>{\item[-] Joint Press Releases} 
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Document Term Matrices}

Regular expressions and search are useful \pause \\
\invisible<1>{We want to use statistics/algorithms to characterize text}\pause  \\
\invisible<1-2>{\alert{We'll put it in a document-term matrix} }

\end{frame}

\begin{frame}
\frametitle{Document Term Matrices}
Preprocessing$\leadsto$\alert{Simplify} text, make it useful \pause \\
\invisible<1>{\alert{Lower dimensionality} } \pause

\begin{itemize}
\invisible<1-2>{\item[-] \alert{For our purposes} } \pause 
\end{itemize}
\invisible<1-3>{Remember: characterize the \alert{Hay stack} } \pause 
\begin{itemize}
\invisible<1-4>{\item[-] If you want to analyze a straw of hay, these methods \alert{are unlikely to work}} \pause 
\invisible<1-5>{\item[-] But even if you want to closely read texts, characterizing hay stack can be useful } 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Preprocessing for Quantitative Text Analysis}

{\huge \alert{One} (of many) }recipe for preprocessing: retain \alert{useful} information \pause 
\begin{itemize}
\invisible<1>{\item[1)] Remove capitalization, punctuation} \pause 
\invisible<1-2>{\item[2)] \alert{Discard Word Order} (Bag of Words Assumption) } \pause 
\invisible<1-3>{\item[3)] \alert{Discard stop words} } \pause 
\invisible<1-4>{\item[4)] \alert{Create Equivalence Class}: Stem, Lemmatize, or synonym} \pause 
\invisible<1-5>{\item[5)] \alert{Discard less useful features}$\leadsto$ depends on application} \pause 
\invisible<1-6>{\item[6)] Other reduction, specialization} \pause 
\end{itemize}

\invisible<1-7>{\alert{Output}: Count vector, each element counts occurrence of stems } \pause \\

\invisible<1-8>{\alert{Provide tools to preprocess via this recipe} }

\end{frame}

\begin{frame}
\frametitle{Preprocessing Texts}

We're going to use the {\tt Natural Language Toolkit} {\tt (nltk)} to work with texts \\
\begin{itemize}
\item[-] Built in functionality
\item[-] Ensures we can customize our feature spaces
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Text Loaded into Python}

Gettysburg Address

\vspace{0.25in}
\begin{footnotesize}

{\tt
from BeautifulSoup import BeautifulSoup\\
from urllib import urlopen\\
import re, os\\

url  = urlopen(`http://avalon.law.yale.edu/19th\_century/gettyb.asp').read()\\

soup = BeautifulSoup(url)\\

text = soup.p.contents$[$0$]$\\

}

\end{footnotesize}

\end{frame}

\begin{frame}
\frametitle{Preprocessing Texts}

Removing capitalization: 
\begin{itemize}
\item[-] {\tt Python} : \alert{{\tt string.lower()}}
\item[-] {\tt R} : \alert{{\tt tolower(`string')}}
\end{itemize}
Removing punctuation
\begin{itemize}
\item[-] {\tt Python}: \alert{{\tt re.sub(`$\backslash$W', ` ', string)}}
\item[-] {\tt R} : \alert{{\tt gsub(`$\backslash\backslash$W', ` ', string)}}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Preprocessing Texts}

{\tt 
text\_1 = text.lower()

text\_2 = re.sub(`$\backslash$W', ` ', text\_1)
}

\end{frame}

\begin{frame}
\frametitle{The Bag of Words Assumption}
\alert{Assumption: Discard Word Order}

\only<1>{{\tt Now we are engaged in a great civil war, testing whether that nation, or any nation} }
\only<2>{{\tt now we are engaged in a great civil war testing whether that nation or any nation}}
\only<3>{\alert{Unigrams}
\small
\begin{tabular}{ll} 
Unigram & Count \\
 a   &    1 \\
 any &    1 \\
 are   &  1\\
 civil  & 1\\
 engaged & 1 \\
 great  & 1 \\
 in   &   1 \\
 nation &  2  \\
 now  &   1   \\
 or   &   1  \\
 testing & 1  \\
 that &    1  \\
 war &     1  \\
 we &      1  \\
 whether & 1  
 \end{tabular}
 }
\only<4>{\alert{Bigrams}
\small
\begin{tabular}{ll}
Bigram & Count \\
now we & 1 \\
we are & 1 \\
are engaged & 1  \\
engaged in & 1  \\
in a & 1  \\
a great & 1  \\
great civil & 1  \\
civil war & 1  \\
war testing & 1  \\
testing whether & 1  \\
whether that & 1  \\
that nation & 1  \\
nation or & 1  \\
or any & 1   \\
any nation & 1
\end{tabular}}
\only<5>{\alert{Trigrams}
\small
\begin{tabular}{ll}
Trigram & Count \\
now we are & 1\\
we are engaged & 1\\
are engaged in & 1\\
engaged in a & 1\\
in a great & 1 \\
a great civil & 1\\
great civil war & 1\\
civil war testing & 1 \\
war testing whether & 1 \\
whether that nation & 1 \\
that nation or & 1 \\
nation or any & 1 \\
or any nation & 1
\end{tabular} 
}

\pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{How Could This Possibly Work?}

Speech is: 
\begin{itemize}
\item[-] Ironic
\item[] {\tt The Raiders make very good personnel decisions }
\item[-] Subtle Negation (Source: Janyce Wiebe) : 
\item[] {\tt They have not succeeded, and will never succeed, in breaking the will of this valiant people}
\item[-] Order Dependent (Source: Arthur Spirling): 
\item[]{\tt Peace, no more war}
\item[]{\tt War, no more peace}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{How Could This Possibly Work?}

Three answers 
\begin{itemize}
\item[1)] \alert{It might not}: Validation is critical (task specific)
\item[2)] \alert{Central Tendency in Text}: Words often imply what a text is about 
{\tt war, civil, union} or tone {\tt consecrate, dead, died, lives}.  
\item[] Likely to be used repeatedly: create a theme for an article
\item[3)] \alert{Human supervision}: Inject human judgement (coders): helps methods identify subtle relationships between words and outcomes of interest
\item[] \alert{Dictionaries}
\item[] \alert{Training Sets}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Discarding Word Order in {\tt Python}}

{\tt 
from nltk import word\_tokenize \\
from nltk import bigrams \\
from nltk import trigrams \\
from nltk import ngrams \\

\vspace{0.25in}
text\_3 = word\_tokenize(text\_2) \\
text\_3\_bi = bigrams(text\_3) \\
text\_3\_tri = trigrams(text\_3)\\
text\_3\_n = ngrams(text\_3, 4)\\

}

\end{frame}

\begin{frame}
\frametitle{Stop Words}

\begin{itemize}
\item[-] \alert{Stop Words}: English Language place holding words  \pause 
\invisible<1>{\item[] {\tt the, it, if, a, able, at, be, because...}} \pause 
\invisible<1-2>{\item[-] Add ``noise" to documents (without conveying much information)} \pause 
\invisible<1-3>{\item[-] Discard stop words: focus on \alert{substantive} words} \pause 
\end{itemize}
\invisible<1-4>{\alert{Note of Caution}: Monroe, Colaresi, and Quinn (2008)\\} \pause 
\invisible<1-5>{{\tt she, he, her, his}\\} \pause 
\invisible<1-6>{\alert{Many English language stop lists include gender pronouns}} \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Exercise caution when discarding stop words } \pause 
\invisible<1-8>{\item[-] You may need to customize your stop word list$\leadsto$ abbreviations, titles, etc} \pause 
\end{itemize}

\invisible<1-9>{{\tt To the Python code!}}

\end{frame}

\begin{frame}
\frametitle{Creating an Equivalence Class of Words}

Reduce dimensionality further \pause \invisible<1>{$\leadsto$ create equivalence class between words} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Words used to refer to same basic concept\\} \pause 
\invisible<1-3>{\item[] {\tt family, families, familial}$\rightarrow$ {\tt famili}} \pause 
\invisible<1-4>{\item[-] Stemming/Lemmatizing algorithms: Many-to-one mapping from words to stem/lemma}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Comparing Stemming and Lemmatizing}

Stemming algorithm: \pause 
\begin{itemize}
\invisible<1>{\item[-] Simplistic algorithms} \pause 
\invisible<1-2>{\item[-] Chop off end of word} \pause 
\invisible<1-3>{\item[-] \alert{Porter} stemmer, \alert{Lancaster} stemmer, \alert{Snowball} stemmer} \pause 
\end{itemize}

\invisible<1-4>{Lemmatizing algorithm:} \pause

\begin{itemize}
\invisible<1-5>{\item[-] Condition on part of speech (noun, verb, etc)} \pause 
\invisible<1-6>{\item[-] Verify result is a word} \pause 
\end{itemize}

\invisible<1-7>{Key comparison: \alert{equivalence classes}} \pause

\invisible<1-8>{{\tt Python Code!}}

\end{frame}

\begin{frame}
\frametitle{All together now...}

\only<1-3>{{\tt Four score and seven years ago our fathers brought forth on this continent a new nation, conceived in liberty, and dedicated to the proposition that all men are created equal. } \\}\pause
\invisible<1>{Step 1: Remove capitalization and punctuation}:\pause \\
\only<3-5>{\invisible<1-2>{{\tt four score and seven years ago our fathers brought forth on this continent a new nation conceived in liberty and dedicated to the proposition that all men are created equal }}\pause \\}
\invisible<1-3>{Step 2: Discard word order}: \pause \\
\only<5-7>{\invisible<1-4>{ {\tt four, score, and, seven, years, ago, our, fathers, brought, forth, on, this, continent, a, new, nation, conceived, in, liberty, and, dedicated, to, the, proposition, that, all, men, are, created, equal } } \pause \\}
\invisible<1-5>{Step 3: Remove stop words} : \pause \\
\only<7-9>{\invisible<1-6>{ {\tt  four, score, seven, years, ago, fathers, brought, forth, continent, new, nation, conceived, liberty, dedicated, proposition, men, created, equal }  } \pause \\}
\invisible<1-7>{Step 4: Applying Stemming Algorithm} \pause \\
\only<9-10>{ {\tt four, score, seven, year, ago, father, brought, forth, contin, new, nation, conceiv, liberti, dedic, proposit, men, creat, equal} \pause \\ }
\invisible<1-9>{Step 5: Create Count Vector ({\tt Python Code!}) } \\
\only<10-11>{\begin{tabular}{ll} 
Stem & Count \\
ago & 1\\
brought & 1\\
seven & 1\\
creat & 1\\
conceiv & 1\\
men & 1\\
father & 1 \\
$\vdots$ & $\vdots$ 
\end{tabular}}

\end{frame}

\begin{frame}
\frametitle{This Can Actually Work!}

  \includegraphics[width=5in]{future2b.pdf}
\end{frame}

\begin{frame}
  \frametitle{Evaluators' Rate Machine Choices Better Than Their
    Own (Grimmer and King) }

 Generate pairs of \alert{similar} documents: Humans vs Machines

  \begin{itemize}
  \item Scale: (1) unrelated, (2) loosely related, or (3)
    closely related
  \item Table reports: mean(scale)
  \end{itemize}

\vspace{.4in}

%\rowcolors[]{1}{blue!20}{blue!10}
  \begin{tabular}{llll}
    \multicolumn{1}{l}{Pairs from}& \multicolumn{1}{c}{Overall Mean} & \multicolumn{1}{c}{Evaluator 1} & \multicolumn{1}{c}{Evaluator 2}   \\
    \hline
 \invisible<1>{  Random Selection &1.38&1.16&1.60}\pause\\
\invisible<1-2>{ Hand-Coded Clusters &1.58&1.48&1.68}\pause\\
\invisible<1-3>{ Hand-Coding &2.06&1.88&2.24}\pause\\
\invisible<1-4>{\alert{Machine}  &\alert{2}.\alert{24}&\alert{2}.\alert{08}&\alert{2}.\alert{40}}\pause\\
    \end{tabular}

\pause 
\invisible<1-5>{\alert{p.s. The hand-coders did the evaluation!}}
\end{frame}

\begin{frame}
\frametitle{Preprocessing Text}

\begin{normalsize}

\alert{One} (of many) potential recipes$\leadsto$ task specific recipes\\

\vspace{0.5in}

Assess value$\leadsto$  \alert{Particular task}\\

\vspace{0.5in}

Thursday: Dictionary methods

\end{normalsize}

\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/tc4.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\newcommand{\argmin}{\arg\!\min}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
 \numberwithin{equation}{section}

%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{October 2nd, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Classification via Dictionary Methods}

\begin{itemize}
\item[1)] Task 
\begin{itemize} 
\invisible<1>{\item[a)] Categorize documents into predetermined categories}
\invisible<1-2>{\item[b)] Measure documents association with predetermined categories} 
\end{itemize}
\invisible<1-3>{\item[2)] Objective function:} 
\begin{eqnarray}
\invisible<1-4>{f(\boldsymbol{\theta}, \boldsymbol{X}_{i}) & = & \frac{\sum_{j=1}^{N} \alert<7>{\theta}_{j} \alert<8>{X}_{ij} }{\sum_{j = 1}^{N} \alert<8>{X}_{ij} } \nonumber } 
\end{eqnarray}

\invisible<1-5>{where: } 
\begin{itemize}
\invisible<1-6>{\item[-] $\boldsymbol{\theta} = (\theta_{1}, \theta_{2}, \hdots, \theta_{N})$ are word weights}
\invisible<1-7>{\item[-] $\boldsymbol{X}_{i} = (X_{i1}, X_{i2}, \hdots, X_{iN})$ count the occurrence of each corresponding word in document $i$}
\end{itemize}

\invisible<1-8>{\item[3)] Optimization$\leadsto$ predetermined word list, no task specific optimization}

\invisible<1-9>{\item[4)] Validation (Model checking)$\leadsto$ weight (model) checking, replication of hand coding, face validity}

\end{itemize}

\pause \pause \pause \pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Word Weights: Separating Classes}

General Classification Goal: Place documents into categories\pause \\

\invisible<1>{How To Do Classification?} \pause

\begin{itemize}
\invisible<1-2>{\item[-] Dictionaries:} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Rely on Humans$\leadsto$ humans to identify words that associate with classes} \pause 
\invisible<1-4>{\item[-] Measure how well words separate (positive/negative, emotional, ...)} \pause 
\end{itemize}
\invisible<1-5>{\item[-] Supervised Classification Methods (Later in the Quarter): } \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Rely on statistical models} \pause 
\invisible<1-7>{\item[-] Given set of coded documents, statistical relationship between classes/words} \pause 
\invisible<1-8>{\item[-] Statistical measures of separation} \pause 
\end{itemize}
\end{itemize}

\large 
\invisible<1-9>{Key point: this is the same task}

\end{frame}

\begin{frame}
\frametitle{Types of Classification Problems}

\alert{Topic}: What is this text about? \pause 
\invisible<1>{\begin{itemize}
\item[-] Policy area of legislation  \\
$\Rightarrow$ $\{$Agriculture, Crime, Environment, ...$\}$
\item[-] Campaign agendas \\ 
$\Rightarrow$ $\{$Abortion, Campaign, Finance, Taxing, ...       $\}$
\end{itemize}} \pause

\invisible<1-2>{\alert{Sentiment}: What is said in this text? [\alert{Public Opinion}] } \pause 
\invisible<1-3>{\begin{itemize}
\item[-] Positions on legislation\\
 $\Rightarrow$ $\{$ Support, Ambiguous, Oppose $\}$
\item[-] Positions on Court Cases \\
$\Rightarrow$ $\{$ Agree with Court, Disagree with Court $\}$
\item[-] Liberal/Conservative Blog Posts \\
$\Rightarrow$ $\{$ Liberal, Middle, Conservative, No Ideology Expressed $\}$
\end{itemize} } \pause

\invisible<1-4>{\alert{Style}/\alert{Tone}: How is it said?} \pause 
\invisible<1-5>{\begin{itemize}
\item[-] Taunting in floor statements\\
 $\Rightarrow$ $\{$ Partisan Taunt, Intra party taunt, Agency taunt, ... $\}$
\item[-] Negative campaigning \\
$\Rightarrow$ $\{$ Negative ad, Positive ad$\}$
\end{itemize} }

\end{frame}

\begin{frame}
\frametitle{Pre-existing word weights$\leadsto$ Dictionaries}

\invisible<1>{{\tt DICTION}}\\

\invisible<1>{\only<2>{\scalebox{0.55}{\includegraphics{DICTION2.png}}}} 
\only<3>{\scalebox{0.55}{\includegraphics{DICTION3.png}}} 
\only<4>{\scalebox{0.55}{\includegraphics{DICTION4.png}}} 
\only<5>{\scalebox{0.85}{\includegraphics{DICTION5.png}}} 
\only<6>{\scalebox{0.85}{\includegraphics{DictionCost.png}}}

\pause \pause \pause \pause \pause

\end{frame}

\begin{frame}

\scalebox{0.75}{\includegraphics{Year.jpg}}

\end{frame}

\begin{frame}
\frametitle{Dictionary Methods}

Many Dictionary Methods (like DICTION) \pause

\begin{itemize}
\invisible<1>{\item[1)] Proprietary}\pause\invisible<1-2>{$\leadsto$ wrapped in GUI} \pause 
\invisible<1-3>{\item[2)] Basic tasks:} \pause
\begin{itemize}
\invisible<1-4>{\item[a)] Count words} \pause 
\invisible<1-5>{\item[b)] Weighted counts of words} \pause 
\invisible<1-6>{\item[c)] Some graphics}\pause 
\end{itemize}
\invisible<1-7>{\item[3)] Pricey$\leadsto$ \alert{inexplicably}} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{DICTION}

\begin{columns}[]

\column{0.5\textwidth}
\scalebox{0.15}{\includegraphics{PolTone.jpg}}

\column{0.5\textwidth}
\pause 
\begin{itemize}
\item[-] \invisible<1>{$\{$ Certain, Uncertain $\}$}\pause\invisible<1-2>{\\, $\{$ Optimistic, Pessimistic $\}$} \pause
\item[-] \invisible<1-3>{$\approx$ 10,000 words} \pause 
\end{itemize}

\invisible<1-4>{Applies DICTION to a wide array of political texts\\} \pause 
\invisible<1-5>{Examine specific periods of American political history}

\end{columns}

\end{frame}

\begin{frame}
\frametitle{Other Dictionaries }

\begin{itemize}
\item[1)] General Inquirer Database (\url{http://www.wjh.harvard.edu/~inquirer/} ) \pause 
\begin{itemize}
\invisible<1>{\item[-] Stone, P.J., Dumphy, D.C., and Ogilvie, D.M. (1966) \emph{The General Inquirer: A Computer Approach to Content Analysis}} \pause 
\invisible<1-2>{\item[-] $\{$ Positive, Negative $\}$ } \pause 
\invisible<1-3>{\item[-] 3627 negative and positive word strings } \pause 
\invisible<1-4>{\item[-] Workhorse for classification across many domains/papers} \pause 
\end{itemize}
\invisible<1-5>{\item[2)] Linguistic Inquiry Word Count (LIWC)} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Creation process:} \pause 
\begin{itemize}
\invisible<1-7>{\item[1)] Generate word list for categories$\leadsto$ `` We drew on common emotion rating scales...Roget's Thesaurus...standard English dictionaries. [then] brain-storming sessions among 3-6 judges were held" to generate other words } \pause 
\invisible<1-8>{\item[2)] Judge round$\leadsto$ (a) Does the word belong? (b) What other categories might it belong to?} \pause 
\end{itemize}
\invisible<1-9>{\item[-] $\{$ Positive emotion, Negative emotion $\}$} \pause 
\invisible<1-10>{\item[-] 2300 words grouped into 70 classes} \pause 
\end{itemize}
\invisible<1-11>{\item[-] Harvard-IV-4 } \pause 
\invisible<1-12>{\item[-] Affective Norms for English Words (we'll discuss this more later)} \pause 
\invisible<1-13>{\item[-] ...} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Generating New Words}

Three ways to create dictionaries (non-exhaustive): \pause 
\begin{itemize}
\invisible<1>{\item[-] Statistical methods$\leadsto$ next Tuesday} \pause 
\invisible<1-2>{\item[-] Manual generation } \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Careful thought (prayer? epiphanies? divine intervention?) about useful words} \pause 
\end{itemize}
\invisible<1-4>{\item[-] Populations of people who are surprisingly willing to perform ill-defined tasks} \pause 
\begin{itemize}
\invisible<1-5>{\item[a)] Undergraduates$:\text{Pizza}\rightarrow \text{Research Output}$} \pause 
\invisible<1-6>{\item[b)] Mechanical turkers} \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Example: $\{$ Happy, Unhappy $\}$ } \pause 
\invisible<1-8>{\item[-] Ask turkers: how happy is } \pause 
\invisible<1-9>{\item[] {\tt elevator}, {\tt car}, {\tt pretty}, {\tt young} } \pause 
\invisible<1-10>{\item[] Output as dictionary} 
\end{itemize}
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Applying Methods to Documents}

Applying the model: \pause 
\begin{itemize}
\invisible<1>{\item[-] Vector of word counts:  $\boldsymbol{X}_i = (X_{i1}, X_{i2}, \hdots, X_{iK}$, $(i = 1, \hdots, N)$} \pause
\invisible<1-2>{\item[-] Weights attached to words  $\boldsymbol{\theta} = (\theta_{1}, \theta_{2}, \hdots, \theta_{K})$  } \pause 
\begin{itemize}
\invisible<1-3>{\item[-] $\theta_{k} \in \{0,1\}$} \pause
\invisible<1-4>{\item[-] $\theta_{k} \in \{-1, 0, 1 \}$} \pause
\invisible<1-5>{\item[-] $\theta_{k} \in \{-2, -1, 0, 1, 2\}$} \pause
\invisible<1-6>{\item[-] $\theta_{k} \in \Re$} \pause
\end{itemize}
\end{itemize}

\invisible<1-7>{For each document $i$ calculate score for document } \pause
\begin{eqnarray}
\invisible<1-8>{Y_i  & = &  \frac{\sum_{k=1}^{K} \theta_k X_{ik}}{\sum_{k=1}^{K} X_{k}} \nonumber \\} \pause
\invisible<1-9>{Y_i  & = &  \frac{\boldsymbol{\theta}^{'} \boldsymbol{X}_i}{\boldsymbol{X}_{i}^{'} \boldsymbol{1} } \nonumber } \pause
\end{eqnarray}

\invisible<1-10>{$Y_{i} \approx $ continuous $\leadsto$ Classification} \pause
\begin{itemize}
\invisible<1-11>{\item[] $Y_i> 0 \Rightarrow$ Positive Category} \pause
\invisible<1-12>{\item[] $Y_i< 0 \Rightarrow$ Negative Category} \pause
\invisible<1-13>{\item[] $Y_i \approx 0$ Ambiguous} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Applying a Dictionary to Press Releases}

\pause 
\begin{itemize}
\invisible<1>{\item[-] Collection of 169,779 press releases (US House members 2005-2010)} \pause 
\invisible<1-2>{\item[-] Dictionary from Neal Caren's website $\leadsto$ Theresa Wilson, Janyce Wiebe, and Paul Hoffman's dictionary } \pause 
\invisible<1-3>{\item[-] Create positive/negative score for press releases.  } 
\end{itemize}

\invisible<1-4>{{\tt Python} code and press releases}

\pause 
\end{frame}

\begin{frame}
\frametitle{Examining Positive and Negative Statements in Press Releases}

\pause

\only<1-10>{
\invisible<1>{Least positive members of Congress:} 
\begin{itemize}
\invisible<1-2>{\item[1)] Dan Burton, 2008} 
\invisible<1-3>{\item[2)] Nancy Pelosi, 2007} 
\invisible<1-4>{\item[3)] Mike Pence 2007} 
\invisible<1-5>{\item[4)] John Boehner, 2009}  
\invisible<1-6>{\item[5)] Jeff Flake, (basically all years)} 
\invisible<1-7>{\item[6)] Eric Cantor, 2009} 
\invisible<1-8>{\item[7)] Tom Price, 2010} 
\end{itemize}

\invisible<1-9>{Legislators who are more extreme$\leadsto$ less positive in press releases}

}

\only<11>{\scalebox{0.5}{\includegraphics{pressOverTime.pdf}}}

\only<12-13>{
\begin{itemize}
\item[-] Credit Claiming press release: 9.1 percentage points ``more positive" than a non-credit claiming press release
\invisible<1-12>{\item[-] Anti-spending press release: 10.6 percentage points ``less positive" than a non-anti spending press release}
\end{itemize}
}

\only<14>{\scalebox{0.5}{\includegraphics{CreditPositive.pdf}}}
\only<15->{\scalebox{0.5}{\includegraphics{AntiCreditPositive.pdf}}}

\pause \pause \pause \pause \pause\pause \pause \pause \pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Methodological Issues/Problems with Dictionaries}

\alert{Dictionary methods are context invariant} \pause \\
\begin{itemize}
\invisible<1>{\item[-] No optimization step $\leadsto$ same word weights regardless of texts} \pause 
\invisible<1-2>{\item[-] Optimization$\leadsto$ incorporate information specific to context} \pause 
\invisible<1-3>{\item[-] Without optimization$\leadsto$ unclear about dictionaries performance} \pause 
\end{itemize}

\invisible<1-4>{\alert{Just because dictionaries provide measures labeled ``positive" or ``negative" it doesn't mean they are accurate measures in your text} (!!!!) \\} \pause

\vspace{0.5in}

\invisible<1-5>{{\huge \alert{Validation}}}

\end{frame}

\begin{frame}
\frametitle{Validation}

Classification Validity: \pause 
\begin{itemize}
\invisible<1>{\item[-] \alert{Training}: build dictionary on subset of documents \alert{with known labels}} \pause 
\invisible<1-2>{\item[-] \alert{Test}: apply dictionary method to other documents \alert{with known labels}} \pause 
\invisible<1-3>{\item[-] Requires hand coded documents} \pause 
\invisible<1-4>{\item[-] Hand coded documents useful for other reasons} \pause 
\begin{itemize}
\invisible<1-5>{\item[-] Is the classification scheme well defined for your texts?} \pause 
\invisible<1-6>{\item[-] Can humans accomplish the coding task?} \pause 
\invisible<1-7>{\item[-] Is the dictionary your using appropriate?} \pause 
\end{itemize}
\end{itemize}

\large 
\invisible<1-8>{\alert{Replicate} classification exercise}  \pause 
\normalsize 
\begin{itemize}
\invisible<1-9>{\item[-] How well does our method perform on \alert{held out} documents?} \pause 
\invisible<1-10>{\item[-] Why held out?} \pause \invisible<1-11>{\alert{Over fitting} } \pause 
\invisible<1-12>{\item[-] Using off-the-shelf dictionary: all labeled documents to test} \pause 
\invisible<1-13>{\item[-] Supervised learning classification: \alert{(Cross)validation} } 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Hand Coding: A Brief Digression}

\alert{Humans should be able to classify documents into the categories you want the machine to classify them in} \pause 
\begin{itemize}
\invisible<1>{\item[-] This is \alert{hard}} \pause 
\invisible<1-2>{\item[-] Why? } \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Ambiguity in language} \pause 
\invisible<1-4>{\item[-] Limited working memory} \pause 
\invisible<1-5>{\item[-] Ambiguity in classification rules} \pause 
\end{itemize}
\invisible<1-6>{\item[-] A procedure for training coders: } \pause 
\invisible<1-7>{\begin{itemize}
\item[1)] Coding rules
\item[2)] Apply to new texts
\item[3)] Assess coder agreement (we'll discuss more in a few weeks)
\item[4)] Using information and discussion, revise coding rules
\end{itemize}} 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Assessing Classification}

Measures of classification performance

\begin{tabular}{l|l|l}
 \hline
  & \multicolumn{2}{c}{Actual Label}  \\
  \hline
  Guess &   Liberal & Conservative \\
  \hline 
  Liberal &  \alert{True Liberal} & False Liberal \\
  \hline
  Conservative & False Conservative & \alert{True Conservative} \\
  \hline
  \hline
\end{tabular}

\pause 
\begin{eqnarray}
\invisible<1>{\text{Accuracy} & = & \frac{ \alert{\text{TrueLib} }+ \alert{\text{TrueCons}}  } { \alert{\text{TrueLib} } + \alert{\text{TrueCons}} + \text{FalseLib} + \text{FalseCons} } \nonumber } \pause  \\
\invisible<1-2>{\text{Precision}_{\text{Liberal}} &= &   \frac{ \alert{\text{True Liberal}}    }  { \alert{\text{True Liberal }} + \text{False Liberal}      } } \pause  \nonumber \\
\invisible<1-3>{\text{Recall}_{\text{Liberal} } & = & \frac{ \alert{\text{True Liberal}}   } { \alert{\text{True Liberal}} + \text{False Conservative}   } } \pause  \nonumber \\
\invisible<1-4>{F_{\text{Liberal}} & = & \frac{ 2\text{Precision}_{\text{Liberal}} \text{Recall}_{\text{Liberal} } } { \text{Precision}_{\text{Liberal}} +  \text{Recall}_{\text{Liberal} }} }   \nonumber \pause 
\end{eqnarray}

\invisible<1-5>{\alert{Under reported for dictionary classification} } 
\end{frame}

\begin{frame}
\frametitle{What about continuous measures?}

\pause

\invisible<1>{\alert{Necessarily more complicated}\\} \pause

\begin{itemize}
\invisible<1-2>{\item[-] Go back to hand coding exercise} \pause 
\invisible<1-3>{\item[-] Imagine asking undergraduates to rate document on a continuous scale (0-100)} \pause 
\invisible<1-4>{\item[-] \alert{Difficult} to create classifications with agreement} \pause 
\invisible<1-5>{\item[-] \alert{Precisely} the point$\leadsto$ merely creating a gold standard is hard, let alone computer classification} \pause 
\end{itemize}

\invisible<1-6>{\alert{Lower level classification}}\pause\invisible<1-7>{$\leadsto$ label phrases and then aggregate} \pause \\

\invisible<1-8>{Modifiable areal unit problem in texts}\pause$\leadsto$\invisible<1-9>{aggregating destroys information, conclusion may depend on level of aggregation}

\end{frame}

\begin{frame}
\frametitle{Validation, Dictionaries from other Fields}
\pause 
\invisible<1>{Accounting Research: measure \alert{tone} of \alert{10-K} reports} \pause 
\begin{itemize}
%\item[-] Comprehensive public summary of company performance
\invisible<1-2>{\item[-] \alert{tone} matters (\$)} \pause 
\end{itemize}

\invisible<1-3>{Previous state of art: Harvard-IV-4 Dictionary applied to texts} \\
\invisible<1-4>{Loughran and McDonald (2011): \alert{Financial Documents are Different}, \textcolor{blue}{polysemes} } \pause 
\begin{itemize}
\invisible<1-5>{\item[-] Negative words in Harvard, Not Negative in Accounting: \\} \pause 
\invisible<1-6>{{\tt tax, cost, capital, board, liability, foreign,  cancer, crude (oil), tire } } \pause 
\invisible<1-7>{\item[-] \alert{73\%} of Harvard negative words in this set(!!!!!)} \pause 
\invisible<1-8>{\item[-] Not Negative Harvard, Negative in Accounting: \\} \pause 
\invisible<1-9>{{\tt felony, litigation, restated, misstatement, and unanticipated} } \pause 
\end{itemize}

\large 
\invisible<1-10>{\alert{Context Matters}}

\end{frame}

\begin{frame}
\frametitle{Measuring Happiness}

\begin{columns}[]
\column{0.5\textwidth}
\scalebox{0.35}{\includegraphics{Bentham.jpg}}

\column{0.5\textwidth}

\pause 
\begin{itemize}
\invisible<1>{\item[-] Quantifying Happiness: How happy is society?} \pause 
\invisible<1-2>{\item[-] How Happy is a Song?} \pause 
\invisible<1-3>{\item[-] Blog posts?} \pause
\invisible<1-4>{\item[-] Facebook posts? (Gross National Happiness)} \pause 
\end{itemize}

\invisible<1-5>{Use \alert{Dictionary Methods} }

\end{columns}

\end{frame}

\begin{frame}
\frametitle{Measuring Happiness}

Dodds and Danforth (2009): Use a dictionary method to measure happiness \pause 
\begin{itemize}
\invisible<1>{\item[-]  \alert{Affective Norms for English Words} (ANEW)} \pause 
\invisible<1-2>{\item[-] Bradley and Lang 1999:  1034 words, Affective reaction to words} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] On a scale of 1-9 how happy does this word make you?} \pause 
\invisible<1-4>{\item[] \alert{Happy} : triumphant (8.82)/paradise (8.72)/ love (8.72) } \pause 
\invisible<1-5>{\item[] \alert{Neutral}: street (5.22)/ paper (5.20)/ engine (5.20) } \pause 
\invisible<1-6>{\item[] \alert{Unhappy} : cancer (1.5)/funeral (1.39)/ rape (1.25) /suicide (1.25) } \pause 
\end{itemize}
\invisible<1-7>{\item[-] \alert{Happiness} for text $i$ (with word $j$ having happiness $\theta_j$ and document frequence $X_{ij}$} \pause 
\begin{eqnarray}
\invisible<1-8>{\text{Happiness}_{i}  & = & \frac{ \sum_{k=1}^{K} \theta_{k} X_{ik} } { \sum_{k=1}^{K} X_{ik}} }  \nonumber 
\end{eqnarray}
\end{itemize}

\end{frame}

\begin{frame}

\scalebox{0.5}{\includegraphics{BillyJean.png}}
\pause

\invisible<1>{\alert{Homework Hints}:}
\invisible<1>{One approach: write a {\tt for} loop searching for words in dictionary (caution: is dictionary stemmed?) }\\ \pause 
\invisible<1-2>{Happiest Song on Thriller?}  \\ \pause 
\invisible<1-3>{\alert{P.Y.T. (Pretty Young Thing) }   (This is the right answer!)}

\end{frame}

\begin{frame}
\frametitle{Happiness in Society}

\only<1>{\scalebox{1}{\includegraphics{SongHappiness.png}}}
\only<2>{\scalebox{1}{\includegraphics{SongType.png}}}
\only<3>{\scalebox{0.7}{\includegraphics{Blog.png}}}

\end{frame}

\begin{frame}
\frametitle{Dictionary Methods}

Today: Classification via Dictionaries\\
Next week: Seperating Words and the Geometry of Text\\
Good luck on the homework!

\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/tc5.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\newcommand{\argmin}{\arg\!\min}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
 \numberwithin{equation}{section}

%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{October 7th, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Estimating Word Discrimination}

\begin{itemize}
\item[1)] Task
\begin{itemize}
\item[a)] \alert{Classification}$\leadsto$ learn word weights for dictionaries
\item[b)] \alert{Fictitious prediction problem}$\leadsto$ Identify features that discriminate between groups to learn features that are indicative of some group
\end{itemize}
\item[2)] Objective function
\begin{eqnarray}
f(\boldsymbol{\theta}, \boldsymbol{X}) &= & f(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y}) \nonumber 
\end{eqnarray}
where: 
\begin{itemize}
\item[] $\boldsymbol{Y}$ = Document Labels 
\item[] $\boldsymbol{X}$  = Document Features
\item[] $\boldsymbol{\theta}$ = Parameters that measure words discrimination between categories
\end{itemize}
\item[3)] Optimization$\leadsto$ method specific
\item[4)] Validation $\leadsto$ depends on task
\begin{itemize}
\item[i)] Classification$\leadsto$ Accuracy, Precision, Recall
\item[ii)] Fictitious prediction$\leadsto$ Face, convergent, discriminatory, and \alert{confound}
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Stylometry$\leadsto$ Who Wrote Disputed Federalist Papers?}

Federalist papers $\leadsto$ Mosteller and Wallace (1963)
\begin{itemize}
\item[-] Persuade citizens of New York State to adopt constitution
\item[-] Canonical texts in study of American politics
\item[-] 77 essays 
\begin{itemize}
\item[-] Published from 1787-1788 in Newspapers
\item[-] And under the name \alert{Publius}, anonymously
\end{itemize}
\end{itemize}
\alert{Who Wrote the Federalist papers}?
\begin{itemize}
\item[-] Jay wrote essays 2, 3, 4,5, and 64
\item[-] Hamilton: wrote 43 papers
\item[-] Madison: wrote 12 papers
\end{itemize}
\alert{Disputed:} Hamilton or Madison?
\begin{itemize}
\item[-] Essays: 49-58, 62, and 63
\item[-] Joint Essays: 18-20
\end{itemize}
\alert{Task}: identify authors of the disputed papers.  \\
\alert{Task}: Classify papers as Hamilton or Madison using dictionary methods

\end{frame}

\begin{frame}
\frametitle{Setting up the Analysis}

\alert{Training}$\leadsto$ papers Hamilton, Madison are known to have authored\\
\alert{Test}$\leadsto$ unlabeled papers\\
\alert{Preprocessing}:
\begin{itemize}
\item[-] Hamilton/Madison both discuss similar issues
\item[-] Differ in extent they use \alert{stop words}
\item[-] Focus analysis on the stop words
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Setting up the Analysis}

\begin{itemize}
\item[-] $\boldsymbol{Y} = (Y_{1}, Y_{2}, \hdots, Y_{N}) = (\text{Hamilton}, \text{Hamilton}, \text{Madison}, ..., \text{Hamilton})  $ \\ $N \times 1$ matrix with author labels
\item[-] Define the number of words in federalist paper $i$ as num$_{i}$
$\boldsymbol{X} = \begin{pmatrix}
\frac{1}{\text{num}_{1}}  & \frac{2}{\text{num}_{1}} & \frac{0}{\text{num}_{1}} & \hdots & \frac{3}{\text{num}_{1}}\\
\frac{0}{\text{num}_{2}} & \frac{1}{\text{num}_{2}} & \frac{0}{\text{num}_{2}} & \hdots & \frac{0}{\text{num}_{2}} \\
\vdots & \vdots & \vdots& \ddots & \vdots \\
\frac{0}{\text{num}_{N}} & \frac{0}{\text{num}_{N}} & \frac{1}{\text{num}_{N}} & \hdots & \frac{0}{\text{num}_{N}} \\
\end{pmatrix}$

 $N \times J$ counting stop word usage rate
\item[-] $\boldsymbol{\theta} = (\theta_{1}, \theta_{2}, \hdots, \theta_{J})$ \\ Word weights.\\
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Objective Function}

\alert{Heuristically}: find $\boldsymbol{\theta}^{*} = (\theta_{1}^{*}, \theta_{2}^{*}, \hdots, \theta_{J}^{*}) $ used to create score 
\begin{eqnarray}
p_{i}  = \sum_{j=1}^{J} \theta_{j}^{*} X_{ij} \nonumber 
\end{eqnarray}

 that maximally discriminates between categories

\scalebox{0.4}{\includegraphics{LDALine.pdf}}

\end{frame}

\begin{frame}
\frametitle{Objective Function}

Define:
\begin{eqnarray}
\boldsymbol{\mu}_{\text{Madison}} & = & \frac{1}{N_{\text{Madison}}} \sum_{i=1}^{N} I(Y_{i} = \text{Madison}) \boldsymbol{X}_{i} \nonumber \\
\boldsymbol{\mu}_{\text{Hamilton}} & = & \frac{1}{N_{\text{Hamilton}}} \sum_{i=1}^{N} I(Y_{i} = \text{Hamilton}) \boldsymbol{X}_{i} \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Objective Function}

\begin{small}

We can then define functions that describe the ``projected" mean and variance for each author

\begin{eqnarray}
g(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y},  \text{Madison}) & = & \frac{1}{N_{\text{Madison}}} \sum_{i= 1}^{N}  I(Y_{i} = \text{Madison} ) \boldsymbol{\theta}^{'}\boldsymbol{X}_{i}  = \boldsymbol{\theta}^{'} \boldsymbol{\mu}_{\text{Madison}} \nonumber  \\
g(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y},  \text{Hamilton}) & = & \frac{1}{N_{\text{Hamilton}}} \sum_{i= 1}^{N}  I(Y_{i} = \text{Hamilton} ) \boldsymbol{\theta}^{'}\boldsymbol{X}_{i}  = \boldsymbol{\theta}^{'} \boldsymbol{\mu}_{\text{Hamilton}} \nonumber  \\
s(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y},  \text{Madison}) & = & \sum_{i=1}^{N} I(Y_{i} = \text{Madison} ) (\boldsymbol{\theta}^{'} \boldsymbol{X}_{i} - \boldsymbol{\theta}^{'} \boldsymbol{\mu}_{\text{Madison}})^2 \nonumber \\
s(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y},  \text{Hamilton}) & = & \sum_{i=1}^{N} I(Y_{i} = \text{Hamilton} ) (\boldsymbol{\theta}^{'} \boldsymbol{X}_{i} - \boldsymbol{\theta}^{'} \boldsymbol{\mu}_{\text{Hamilton}})^2 \nonumber 
\end{eqnarray}

\end{small}

\end{frame}

\begin{frame}
\frametitle{Objective Function$\leadsto$ Optimization}

\begin{eqnarray}
f(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y} ) & = & \frac{\left(g(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y},  \text{Hamilton}) - g(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y},  \text{Madison}) \right)^2}{s(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y},  \text{Hamilton})  + s(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y},  \text{Madison}) } \nonumber\\
& =&  \frac{\left(\boldsymbol{\theta}^{'} ( \boldsymbol{\mu}_{\text{Hamilton}} - \boldsymbol{\mu}_{\text{Madison}})     \right)^2  }{\text{Scatter}_{\text{Hamilton}} + \text{Scatter}_{\text{Madison}}    } \nonumber 
\end{eqnarray}

\alert{Optimization}$\leadsto$ find $\boldsymbol{\theta}^{*}$ to maximize $f(\boldsymbol{\theta}, \boldsymbol{X}, \boldsymbol{Y} ) $, assuming independence across dimensions.\\

\alert{(Fisher's) Linear Discriminant Analysis}

\end{frame}

\begin{frame}
\frametitle{Optimization$\leadsto$ Word Weights}

For each word $j$, construct weight $\theta^{*}_{j}$, 
\begin{small}
\begin{eqnarray}
\mu_{j, \text{Hamilton}} & = & \frac{\sum_{i = 1}^{N} I(Y_{i} = \text{Hamilton}) X_{ij} }{\sum_{j=1}^{J} \sum_{i = 1}^{N} I(Y_{i} = \text{Hamilton}) X_{ij} } \nonumber \\
\mu_{j, \text{Madison}} & = & \frac{\sum_{i = 1}^{N} I(Y_{i} = \text{Madison}) X_{ij} }{\sum_{j=1}^{J} \sum_{i = 1}^{N} I(Y_{i} = \text{Madison}) X_{ij} } \nonumber \\
\sigma^{2}_{j, \text{Hamilton}} & = & \text{Var}(X_{i,j} |  \text{Hamilton}) \nonumber \\
\sigma^{2}_{j, \text{Madison} }& = & \text{Var}(X_{i,j} | \text{Madison}) \nonumber 
\end{eqnarray}
\end{small}

We can then generate weight $\theta^{*}_{j}$ as

\begin{eqnarray}
\theta^{*}_j &= & \frac{\mu_{j, \text{Hamilton}}  - \mu_{j, \text{Madison}}  } {\sigma_{j, \text{Hamilton}}^{2} + \sigma_{j, \text{Madison}}^{2}    }  \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Optimization$\leadsto$ Trimming the Dictionary}

\begin{itemize}
\item[-] Trimming weights: Focus on discriminating words (very simple \alert{regularization})
\item[-] Cut off: For all $|\theta^{*}_{j}|<0.025$ set $\theta^{*}_{j} = 0$.  
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Classification$\leadsto$ Determining Authorship}

For each disputed document $i$, compute discrimination statistic
\begin{eqnarray}
p_{i}  & = & \sum_{j =1}^{J} \theta^{*}_{j} X_{ij} \nonumber 
\end{eqnarray}

$p_i \leadsto$ classification (\alert{linear discriminator})
\begin{itemize}
\item[-] Above midpoint in training set $\rightarrow$ Hamilton text
\item[-] Below midpoint in training set $\rightarrow$ Madison text
\end{itemize}

\alert{Findings}: Madison is the author of the disputed federalist papers.

\end{frame}

\begin{frame}
\frametitle{Inferring Separating Words}

\only<1-9, 11->{Classification$\leadsto$ Custom Dictionaries 
\begin{itemize}
\invisible<1>{\item[-] Stylometry$\leadsto$ Classify Authors} 
\invisible<1-2>{\item[-] Dictionary based classification $\leadsto$ Gentzkow and Shapiro (2010) and measures of media slant} \pause 
\invisible<1-3>{\item[-] Dictionary based classification$\leadsto$ Customized to particular setting}
\end{itemize}
\invisible<1-4>{\alert{Fictitious Prediction Problem} $\leadsto$ Infer words that are indicative of some class/group} 
\begin{itemize}
\invisible<1-5>{\item[-] Difference in Republican, Democratic language $\leadsto$ \alert{Partisan} words} 
\invisible<1-6>{\item[-] Difference in Liberal, Conservative language $\leadsto$ Ideological Language} 
\invisible<1-7>{\item[-] Difference in Secret/Not Secret Language $\leadsto$ Secretive Language (Gill and Spirling 2014)}  
\invisible<1-8>{\item[-] Difference in Toy advertising } 
\invisible<1-10>{\item[-] Difference in Language across groups$\leadsto$ Labeling output from Clustering/Topic Models}
\end{itemize}
\invisible<1-11>{\alert{Vague} and \alert{Difficult} to derive before hand}

}
\begin{center}
\only<10>{\scalebox{0.4}{\includegraphics{BoyGirlsAd.jpg}}}
\end{center}
\pause \pause\pause \pause \pause  \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Congressional Language Across Sources}
\pause

\invisible<1>{Congressional Press Releases and Floor Speeches} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Collected 64,033 press releases} \pause 
\invisible<1-3>{\item[-] Problem: are they \alert{distinct} from floor statements (approx. 52,000 during same time)?} \pause 
\begin{itemize}
\invisible<1-4>{\item[-] Yes: press releases have different purposes, targets, and need not relate to official business } \pause 
\invisible<1-5>{\item[-] No: press releases are just reactive to floor activity, will follow floor statements} \pause 
\end{itemize}
\invisible<1-6>{\item[-] Deeper question: what does it mean for two text collections to be \alert{different?}} \pause 
\invisible<1-7>{\item[-] One Answer: \alert{texts used for different purposes}} \pause 
\invisible<1-8>{\item[-] Partial answer: identify words that distinguish press releases and floor speeches} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{A Method for Identifying Distinguishing Words}

\pause

\invisible<1>{Mutual Information} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Unconditional uncertainty (entropy): } \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Randomly sample a press release } \pause 
\invisible<1-4>{\item[-] Guess press release/floor statement} \pause 
\invisible<1-5>{\item[-] Uncertainty about guess } \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Maximum: No. press releases = No. floor statements} \pause 
\invisible<1-7>{\item[-] Minimum : All documents in one category} \pause 
\end{itemize}
\end{itemize}
\invisible<1-8>{\item[-] Conditional uncertainty ($X_{j}$) (conditional entropy)} \pause 
\begin{itemize}
\invisible<1-9>{\item[-] Condition on presence of word $X_{j}$}\pause
\invisible<1-10>{\item[-] Randomly sample a press release}\pause
\invisible<1-11>{\item[-] Guess press release/floor statement}\pause
\invisible<1-12>{\item[-] Word presence reduces uncertainty }\pause
\begin{itemize}
\invisible<1-13>{\item[-] Unrelated: Conditional uncertainty = uncertainty}\pause
\invisible<1-14>{\item[-] Perfect predictor: Conditional uncertainty = 0}\pause
\end{itemize}
\end{itemize}
\invisible<1-15>{\item[-] Mutual information($X_{j}$): uncertainty - conditional uncertainty ($X_{j}$)} \pause
\begin{itemize}
\invisible<1-16>{\item[-] Maximum: Uncertainty $\rightarrow$ $X_{j}$ is perfect predictor} \pause
\invisible<1-17>{\item[-] Minimum: 0 $\rightarrow$ $X_{j}$ fails to separate speeches and floor statements}
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{A Method for Identifying Distinguishing Words}

\pause 
\begin{itemize}
\invisible<1>{\item[-] $\text{Pr}(\text{Press}) \equiv $ Probability selected document press release} \pause 
\invisible<1-2>{\item[-] $\text{Pr}(\text{Speech}) \equiv $ Probability selected document speech} \pause 
\invisible<1-3>{\item[-] Define \alert{entropy} $H(\text{Doc})$ } \pause 
\begin{eqnarray}
\invisible<1-4>{H(\text{Doc})  & = &  \alert{-} \sum_{t \in \{\text{Pre}, \text{Spe} \} } \text{Pr}(t) \log_2 \text{Pr}(t) \nonumber } \pause 
% & = &  - (\text{Pr(Press)}\log_2 \text{Pr(Press)} + \text{Pr(Speech)} \log_2 \text{Pr(Speech)} ) \nonumber  
\end{eqnarray}
\invisible<1-5>{\item[-] $\log_2$? Encodes bits} \pause 
\invisible<1-6>{\item[-] Maximum: Pr(Press) = Pr(Speech) = 0.5} \pause 
\invisible<1-7>{\item[-] Minimum: Pr(Press) $\rightarrow$ 0 (or Pr(Press) $\rightarrow$ 1)} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{A Method for Identifying Distinguishing Words}

\pause
\begin{itemize}
\invisible<1>{\item[-] Consider presence/absence of word $X_j$} \pause 
\invisible<1-2>{\item[-] Define \alert{conditional entropy} $H(\text{Doc}|X_j)$ } \pause 
\end{itemize}
\begin{eqnarray}
\invisible<1-3>{H(\text{Doc}|X_j) & = &  - \sum_{s = 0}^{1} \sum_{t \in \{\text{Pre}, \text{Spe} \} } \text{Pr}(t, X_j = s) \log_2 \text{Pr}(t| X_j = s) \nonumber } \pause
\end{eqnarray}
\begin{itemize}
\invisible<1-4>{\item[-] Maximum: $X_j$ unrelated to Press Releases/Floor Speeches} \pause
\invisible<1-5>{\item[-] Minimum: $X_j$ is a perfect predictor of press release/floor speech} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{A Method for Identifying Distinguishing Words}

\pause

\begin{itemize}
\invisible<1>{\item[-] Define \alert{Mutual Information}($X_j$) as } \pause 
\begin{eqnarray}
\invisible<1-2>{\text{Mutual Information}(X_j) & = & H(\text{Doc}) - H(\text{Doc}|X_j) \nonumber } \pause 
\end{eqnarray}
\invisible<1-3>{\item[-] Maximum: entropy $\Rightarrow H(\text{Doc}|X_j) = 0$} \pause 
\invisible<1-4>{\item[-] Minimum:  0  $\Rightarrow H(\text{Doc}|X_j) = H(\text{Doc}) $.  } \pause 
\end{itemize}
\large
\invisible<1-5>{Bigger mutual information $\Rightarrow$ better discrimination } \pause \\
\vspace{0.25in} 
\invisible<1-6>{Objective function and optimization$\leadsto$ estimate probabilities that we then place in mutual information}

\end{frame}

\begin{frame}
\frametitle{A Method for Identifying Distinguishing Words}

Formula for mutual information \\ (based on ML estimates of probabilities) 
\begin{eqnarray}
n_p & = & \text{Number Press Releases} \nonumber \\
n_s & = & \text{Number of Speeches} \nonumber \\
D  & = & n_p + n_s \nonumber \\
n_j & = & \sum_{i=1}^{D} X_{i,j} \hspace{0.25in} \text{ (No. docs $X_j$ appears ) } \nonumber \\
n_{-j} & =& \text{ No. docs $X_j$ does not appear  } \nonumber \\
n_{j,p} & = & \text{No. press and $X_j$} \nonumber \\
n_{j,s} & = & \text{No. speech and $X_j$} \nonumber \\
n_{-j,p} & = & \text{No. press and not $X_j$} \nonumber \\
n_{-j,s} & = & \text{No. speech and not $X_j$} \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{A Method for Identifying Distinguishing Words}

Formula for Mutual Information

\begin{eqnarray}
\text{MI}(X_j)  & = & \frac{n_{j,p}}{D} \log_2 \frac{n_{j,p} D}{n_j n_p}
    +\frac{n_{j,s}}{D} \log_2 \frac{n_{j,s} D}{n_j n_{s}}
    \nonumber \\
   & &
    +\frac{n_{-j,p}}{D} \log_2 \frac{n_{-j,p} D}{n_{-j} n_p}
    +\frac{n_{-j, s}}{D} \log_2 \frac{n_{-j,s} D}{n_{-j} n_{s}}.
     \nonumber
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{What's Different About Press Releases}

\only<1>{\scalebox{0.225}{\includegraphics{MutInfPlot1.pdf}}}
\only<2>{\scalebox{0.225}{\includegraphics{MutInfPlot2.pdf}}}
\only<3>{\scalebox{0.225}{\includegraphics{MutInfPlot3.pdf}}} 
\begin{center}
\only<4-10>{\scalebox{0.125}{\includegraphics{MutInfPlot3.pdf}}}
\only<11>{\scalebox{0.45}{\includegraphics{AttentionPressSpeech}}}
\end{center}

\alert{What's Different?}

\only<4->{\begin{itemize}
\invisible<1-4>{\item[-] Press Releases: Credit Claiming} 
\invisible<1-5>{\item[-] Floor Speeches: Procedural Words} 
\invisible<1-6>{\item[-] Validate: Manual Classification}  
\invisible<1-7>{\item[-] Sample 500 Press Releases, 500 Floor Speeches} 
\invisible<1-8>{\item[-] Credit Claiming: 36\% Press Releases, 4\% Floor Speeches} 
\invisible<1-9>{\item[-] Procedural: 0\% Press Releases, 44\% Floor Speeches} 
\invisible<1-10>{\item[-] Validate: Topic Classification} 
\end{itemize}
}

\pause \pause \pause \pause \pause \pause \pause\pause \pause\pause 
\end{frame}

\begin{frame}
\frametitle{Fightin' Words$\leadsto$ An Introduction to Regularization}

Monroe, Colaresi, and Quinn (2009)$\leadsto$ what makes a word partisan? \pause \\

\invisible<1>{Argue for using \alert{Log Odds Ratio}, weighted by variance\\} \pause

\invisible<1-2>{Recall: For some event $E$ and $F$} \pause 
\begin{eqnarray}
\invisible<1-3>{P(E) & = & 1 - P(E^{c}) \nonumber \\} \pause 
\invisible<1-4>{\text{Odds}(E) & = & \frac{P(E)}{1- P(E)} \nonumber \\} \pause 
\invisible<1-5>{\text{Odds Ratio}(E, F) & = & \frac{\frac{P(E))}{(1 - P(E))}}{\frac{P(F)}{1-P(F)}}\nonumber \\} \pause 
\invisible<1-6>{\text{Log Odds Ratio}(E, F) & = & \log\left(\frac{P(E)}{1- P(E)}\right) - \log\left(\frac{P(F)}{1-P(F)} \right) \nonumber} \pause 
\end{eqnarray}

\invisible<1-7>{Strategy$\leadsto$ Construct objective function on $\alert{proportions}$ (and then calculate log-odds)} \pause

\end{frame}

\begin{frame}
\frametitle{Objective Function}

Suppose we're interested in how a word separates partisan speech.  \\
$\boldsymbol{Y} = (\text{Republican}, \text{Republican}, \text{Democrat}, \hdots, \text{Republican})$\\
$\boldsymbol{X} =$ Unnormalized matrix of word counts $N \times J$

Define
\begin{small}
\begin{eqnarray}
\boldsymbol{x}_{\text{Republican}} & = & (\sum_{i=1}^{N}I(Y_{i} = \text{Republican})X_{i1}, \sum_{i=1}^{N}I(Y_{i} = \text{Republican})X_{i2}, \nonumber \\
&&  \hdots, \sum_{i=1}^{N}I(Y_{i} = \text{Republican})X_{iJ} ) \nonumber 
\end{eqnarray}
\end{small}

with $N_{\text{Republican}} = $ Total number of Republican words

\end{frame}

\begin{frame}
\frametitle{Objective Function}

\pause 
\begin{eqnarray}
\invisible<1>{\boldsymbol{\pi}_{\text{Republican}} & \sim & \text{Dirichlet}(\boldsymbol{\alpha}) \nonumber \\} \pause 
\invisible<1-2>{\boldsymbol{x}_{\text{Republican}}| \boldsymbol{\pi}_{\text{Republican}}  & \sim & \text{Multinomial}(N_{\text{Republican}}, \boldsymbol{\pi}_{\text{Republican}}) \nonumber }\pause 
\end{eqnarray}

\invisible<1-3>{This implies an objective function on $\boldsymbol{\pi}$, } \pause 
\begin{eqnarray}
\invisible<1-4>{p(\boldsymbol{\pi}| \boldsymbol{\alpha}, \boldsymbol{X}, \boldsymbol{Y}) & \propto & p(\boldsymbol{\pi}| \boldsymbol{\alpha}) p(\boldsymbol{x}_{\text{Republican}}| \boldsymbol{\pi} \boldsymbol{\alpha}, \boldsymbol{Y})  \nonumber \\} \pause 
\invisible<1-5>{& \propto & \frac{\Gamma(\sum_{j=1}^{J} \alpha_{j} ) }{\prod_{j} \Gamma(\alpha_{j}) } \prod_{j=1}^{J} \pi_{j}^{\alpha_{j} - 1} \pi_{j}^{x_{\text{Republican}, j}} \nonumber } \pause 
\end{eqnarray}

\invisible<1-6>{$p(\boldsymbol{\pi}| \boldsymbol{\alpha}, \boldsymbol{X}, \boldsymbol{Y}) $ is a Dirichlet distribution:} \pause 
\begin{eqnarray}
\invisible<1-7>{\pi_{\text{Republican}, j}^{*} & = & \frac{x_{\text{Republican}, j} + \alpha_{j} }{N_\text{Republican} + \sum_{j=1}^{J}\alpha_{j}} \nonumber } \pause 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Calculating Log Odds Ratio}

Define $\log \text{Odds Ratio}_{j} $ as 
\begin{eqnarray}
\log \text{Odds Ratio}_{j} & = & \log \left(\frac{\pi_{\text{Republican}, j}}{1 - \pi_{\text{Republican}, j}} \right) - \log \left( \frac{\pi_{\text{Democratic}, j}}{1 - \pi_{\text{Democratic}, j}} \right) \nonumber 
\end{eqnarray}

\begin{eqnarray}
\text{Var}(\log \text{Odds Ratio}_j ) & \approx & \frac{1 } { x_{jD} + \alpha_j }  + \frac{1} {x_{jR} + \alpha_j }  \nonumber \\
\text{Std. Log Odds}_j & = & \frac { \log \text{Odds Ratio}_j  } { \sqrt{\text{Var}(\log \text{Odds Ratio}_j ) }} \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Applying the Model}

How do Republicans and Democrats differ in debate?\\

Condition on \alert{topic} and examine word usage\\

\begin{itemize}
\item[-] Press Releases (64,033)
\item[-] Topic Coded (Structural Topic Model)
\item[-] Given press release is about topic, what are the features that distinguish Republican and Democratic language?
\end{itemize}

\end{frame}
\begin{frame}

Mutual Information, Standardized Log Odds
\begin{center}
\only<1>{\scalebox{0.375}{\includegraphics{IraqWarPartisan.pdf}}}
\only<2>{\scalebox{0.375}{\includegraphics{GasPricesPartisan.pdf}}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Multinomial Inverse Regression}

\begin{itemize}
\item[-] In classification we're generally interested in:
\begin{eqnarray}
E[Y| \boldsymbol{X}] & = & g(X_{1}, X_{2}, \hdots, X_{J}) \nonumber 
\end{eqnarray}
\item[-] Problem: $J$ might be very, very big.  
\item[-] Potential solution$\leadsto$ invert regression
\begin{eqnarray}
E[\boldsymbol{X}|Y] & = & g(Y) \nonumber 
\end{eqnarray}
\item[-] Inversion is particularly useful for \alert{feature selection}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Multinomial Inverse Regression: Objective Function (Taddy 2014)}

As before, $\boldsymbol{x}_{\text{Republican}}$ to be the Republican count vector. \pause

\begin{eqnarray}
\invisible<1>{\boldsymbol{x}_{\text{Republican}} & \sim & \text{Multinomial}(N_{\text{Republican}}, \boldsymbol{\pi}_{\text{Republican}}) \nonumber \\} \pause 
\invisible<1-2>{\pi_{\text{Republican}, j} & = & \frac{\exp[\alpha_{j} + I(\text{Republican}) \phi_{j} ]}{\sum_{l=1}^{J} \exp[\alpha_{l} + I(\text{Republican}) \phi_{l} ]}\nonumber \\} \pause 
\invisible<1-3>{\phi_{j} & \sim & \text{Laplace}(\lambda_{j}) \nonumber \\} \pause 
\invisible<1-4>{\lambda_{j} & \sim & \text{Gamma}(s, r) \nonumber } \pause 
\end{eqnarray}

\invisible<1-5>{\alert{Laplace} priors $\leadsto$ \alert{regularize} or \alert{shrink} estimates toward zero \\} \pause 
\invisible<1-6>{\alert{Laplace} priors $\leadsto$ Equivalent to $L1$ or \alert{lasso} penalization\\} \pause 
\invisible<1-7>{\alert{Gamma-Lasso} prior \\} \pause

\invisible<1-8>{Optimization$\leadsto$ Coordinate descent (paper is great!) $\leadsto$ {\tt textir} package}

\end{frame}

\begin{frame}
\frametitle{Applying Multinomial Inverse Regression: Objective Function}

Taddy (2014) considers speeches made on Congressional floor in 2005\\
``Most" Republican words  \pause \\
\invisible<1>{{\tt un.official,term.care.insurance, weapons.grade.plutonium}\\
{\tt million.illegal.immigrant, \alert{grand ole opry}, ..., personal.injury.lawyer}                \\} \pause

\invisible<1-2>{``Most" Democratic Words\\} \pause 
\invisible<1-3>{{\tt wild.bird, dealth.penalty.system, record.budget.deficit}\\
{\tt security.private.account, able.buy.gun}  }

\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/tc6.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\newcommand{\argmin}{\arg\!\min}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
 \numberwithin{equation}{section}

%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{October 9th, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{The Vector Space Model of Text}

\begin{itemize}
\item[1)] Task:
\begin{itemize}
\item[-] Numerous tasks will suppose that we can measure document \alert{similarity} or \alert{dissimiliarity}
\end{itemize}
\item[2)] Objective Function
\begin{itemize}
\item[-] For a variety of tasks, will impose some \alert{measure} or \alert{definition} of similarity, dissimilarity, or distance.
\begin{eqnarray}
d(\boldsymbol{X}_{i}, \boldsymbol{X}_{j}) & = & \text{Dissimilarity}(\text{Distance})\leadsto\text{Bigger implies further apart} \nonumber \\
s(\boldsymbol{X}_{i}, \boldsymbol{X}_{j}) & = & \text{Similarity}\leadsto\text{Bigger implies closer together} \nonumber
\end{eqnarray}
\item[-] Objective functions$\leadsto$ determine which points we compare and aggregate similarity, dissimilarity, and distance
\end{itemize}
\item[3)] Optimization
\begin{itemize}
\item[-] Depends on the particular task, likely arranging/grouping objects to find similarity
\end{itemize}
\item[4)] Validation
\begin{itemize}
\item[-] Are the mathematical definitions of similarity actually \alert{similar} for our particular purpose? 
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Texts and Geometry}

Consider a document-term matrix

\begin{eqnarray}
\boldsymbol{X} & = & \begin{pmatrix}
1 & 2 & 0 & \hdots & 0 \\
0 & 0 & 3 & \hdots & 0 \\
\vdots & \vdots & \vdots & \ddots & \vdots \\
1 & 0 & 0 & \hdots & 3 \\
\end{pmatrix}\nonumber 
\end{eqnarray}

\pause \invisible<1>{Suppose documents live in a \alert{space}}\pause\invisible<1-2>{ $\leadsto$ rich set of results from linear algebra} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Provides a \alert{geometry}}\pause\invisible<1-4>{$\leadsto$ modify with word weighting} \pause 
\invisible<1-5>{\item[-] Natural notions of \alert{distance}} \pause 
\invisible<1-6>{\item[-] \alert{Kernel Trick}: richer comparisons of large feature spaces} \pause 
\invisible<1-7>{\item[-] Building block for clustering, supervised learning, and scaling} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Texts in Space}
\pause 
\begin{eqnarray}
\invisible<1>{\text{Doc1} & = & (1, 1, 3, \hdots, 5) \nonumber \\ } \pause 
\invisible<1-2>{\text{Doc2} & = & (2, 0, 0, \hdots, 1) \nonumber \\} \pause
\invisible<1-3>{\textbf{Doc1}, \textbf{Doc2} & \in & \Re^{J} \nonumber } \pause
\end{eqnarray}

\invisible<1-4>{\alert{Inner Product} between documents: } \pause 
\begin{eqnarray} 
\invisible<1-5>{\textbf{Doc1} \cdot \textbf{Doc2}  &  = &  (1, 1, 3, \hdots, 5)^{'} (2, 0, 0, \hdots, 1) \nonumber \\} \pause 
\invisible<1-6>{  & = &  1 \times 2 + 1 \times 0 + 3 \times 0 + \hdots + 5 \times 1  \nonumber \\} \pause 
\invisible<1-7>{   & = & 7 \nonumber} 
   \end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Vector Length}

\begin{columns}[]

\column{0.6\textwidth} 
\only<1>{\scalebox{0.5}{\includegraphics{Length1.pdf}}}
\only<2>{\scalebox{0.5}{\includegraphics{Length2.pdf}}}
\only<3>{\scalebox{0.5}{\includegraphics{Length3.pdf}}}
\only<4-5>{\scalebox{0.5}{\includegraphics{Length4.pdf}}}

\column{0.4\textwidth} 
\begin{itemize}
\invisible<1>{\item[-] \alert{Pythogorean Theorem}: Side with length $a$} 
\invisible<1-2>{\item[-] Side with length $b$ and right triangle}
\invisible<1-3>{\item[-] $c = \sqrt{ a^2 + b^2} $ }
\invisible<1-4>{\item[-] \alert{This is generally true} }
\end{itemize}

\end{columns}

\pause \pause \pause \pause 
\end{frame}

\begin{frame}
\frametitle{Vector (Euclidean) Length}

\begin{defn} Suppose $\boldsymbol{v} \in \Re^{J}$. Then, we will define its \alert{length} as 
\begin{eqnarray}
||\boldsymbol{v}|| & = & (\boldsymbol{v} \cdot \boldsymbol{v} )^{1/2} \nonumber \\
						   & = & (v_{1}^2 + v_{2}^{2} + v_{3}^{2} + \hdots + v_{J}^{2} )^{1/2} \nonumber 
\end{eqnarray}						   
\end{defn}

\end{frame}

\begin{frame}
\frametitle{Measures of Dissimilarity}

Initial guess$\leadsto$ \alert{Distance metrics} \\

Properties of a metric: (distance function) $d(\cdot, \cdot)$.  Consider arbitrary documents $\boldsymbol{X}_{i}$, $\boldsymbol{X}_{j}$, $\boldsymbol{X}_{k}$ \pause 
\begin{itemize}
\invisible<1>{\item[1)] $d(\boldsymbol{X}_{i}, \boldsymbol{X}_{j}) \geq 0$} \pause 
\invisible<1-2>{\item[2)] $d(\boldsymbol{X}_{i}, \boldsymbol{X}_{j} ) = 0 $ if and only if $\boldsymbol{X}_{i} = \boldsymbol{X}_{j}$} \pause 
\invisible<1-3>{\item[3)] $d(\boldsymbol{X}_{i}, \boldsymbol{X}_{j} ) = d(\boldsymbol{X}_{j}, \boldsymbol{X}_{i} )$} \pause 
\invisible<1-4>{\item[4)] $d(\boldsymbol{X}_{i}, \boldsymbol{X}_{k}) \leq d(\boldsymbol{X}_{i}, \boldsymbol{X}_{j})  + d(\boldsymbol{X}_{j}, \boldsymbol{X}_{k})$} \pause 
\end{itemize}

\vspace{0.5in}

\invisible<1-5>{Explore \alert{distance} functions to compare documents}$\leadsto$\pause\invisible<1-6>{Do we want additional assumptions/properties?}

\end{frame}

\begin{frame}
\frametitle{Measuring the Distance Between Documents}

\alert{Euclidean Distance}

\begin{center}
\only<1>{\scalebox{0.5}{\includegraphics{Doc1.pdf}}}
\only<2>{\scalebox{0.5}{\includegraphics{Doc2.pdf}}} 
\only<3>{\scalebox{0.5}{\includegraphics{Doc3.pdf}}} 
\end{center}

\end{frame}

\begin{frame}
\frametitle{Measuring the Distance Between Documents}

\begin{defn}
The Euclidean distance between documents $\boldsymbol{X}_{i}$ and $\boldsymbol{X}_{j}$ as

\begin{eqnarray}
||\boldsymbol{X}_{i} - \boldsymbol{X}_{j}||  & =  & \sqrt{\sum_{m=1}^{J} \left(x_{im} -  x_{jm} \right)^2} \nonumber 
\end{eqnarray}

\end{defn}

\pause 
\invisible<1>{Suppose $\boldsymbol{X}_{i} = (1, 4)$ and $\boldsymbol{X}_{j} = (2, 1)$.  The distance between the documents is:
\begin{eqnarray}
||(1, 4) - (2,1) || & = & \sqrt{ (1 -2 )^2 + (4 - 1)^2 } \nonumber\\
   & = & \sqrt{10}  \nonumber  
\end{eqnarray}
}

\end{frame}

\begin{frame}
\frametitle{Measuring the Distance Between Documents}

\alert{Many distance metrics} \pause  \invisible<1>{ Consider the \alert{Minkowski} family \\} \pause

\invisible<1-2>{\begin{defn}
The Minkowski Distance between documents $\boldsymbol{X}_{i}$ and $\boldsymbol{X}_{j}$ for value $p$ is

\begin{eqnarray}
d_{p} (\textbf{X}_{i}, \textbf{X}_{j} )  & = & \left(\sum_{m=1}^{J}  |x_{im} - x_{jm}|^{p}  \right) ^{1/p} \nonumber
\end{eqnarray}

\end{defn}

}

\end{frame}

\begin{frame}
\frametitle{Members of the Minkowski Family}

\pause 
\invisible<1>{Manhattan metric} \pause 
\begin{eqnarray}
\invisible<1-2>{d_{1} (\textbf{X}_{i} , \textbf{X}_{j} ) & = & \sum_{m=1}^{J} | x_{im} - x_{jm} | \nonumber \\} \pause 
\invisible<1-3>{d_{\text{1} } ( (1,4) , (2,1) )  & = & | 1| + |3| = 4\nonumber } \pause 
\end{eqnarray}

\invisible<1-4>{Minkowski (p) metric } \pause 
\begin{eqnarray}
\invisible<1-5>{d_{p} (\textbf{X}_{i}, \textbf{X}_{j} )  & = & \left(\sum_{m=1}^{J}  |x_{im} - x_{jm}|^{p}  \right) ^{1/p} \nonumber \\
d_{p} ((1,4), (2,1) )  & = & \left( |1 - 2|^{p} + |4 - 1|^{p} \right)^{1/p} \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{What Does $p$ Do?}

\pause

\invisible<1>{Increasing $p$ $\leadsto$ greater importance of coordinates with largest differences \\}\pause

\invisible<1-2>{If we let $p \rightarrow \infty$ Obtain maximum-metric (Chebyshev's Metric)} \pause 
\invisible<1-3>{\begin{eqnarray}
\lim_{p\rightarrow \infty} d_{p} (\textbf{X}_{i}, \textbf{X}_{j} ) & = & \max_{m=1}^{J} | x_{im} - x_{jm} | \nonumber
\end{eqnarray} } \pause

\invisible<1-4>{In words: distance between documents only the biggest difference}  \\ \pause 
\invisible<1-5>{\alert{All} other differences do not contribute to distance measure \\} \pause 
\invisible<1-6>{Decreasing $p \leadsto$ greater importance of coordinates with smallest differences \\} \pause 
\invisible<1-7>{\begin{eqnarray}
\lim_{p \rightarrow -\infty} d_{p}(\textbf{X}_{i}, \textbf{X}_{j} )  & = & \min_{m=1}^{J} | x_{im} - x_{jm} | \nonumber
\end{eqnarray}
}
\end{frame}

\begin{frame}
\frametitle{Comparing the Metrics}

Suppose $\boldsymbol{X}_{i} = (10,4, 3)$, $\boldsymbol{X}_{j} = (0, 4, 3)$, and $\boldsymbol{X}_{k} = (0, 0, 0)$ \pause \\
\invisible<1>{Then:} \pause 
\begin{eqnarray}
\invisible<1-2>{d_{1} (\boldsymbol{X}_{i}, \boldsymbol{X}_{j} ) & = & 10 \nonumber \\} \pause 
\invisible<1-3>{d_{1} (\boldsymbol{X}_{i}, \boldsymbol{X}_{k} ) & = & 10 + 4 + 3 = 17 \nonumber \\} \pause 
\invisible<1-4>{d_{2} (\boldsymbol{X}_{i}, \boldsymbol{X}_{j} ) & = & 10 \nonumber \\} \pause 
\invisible<1-5>{d_{2} (\boldsymbol{X}_{i}, \boldsymbol{X}_{k} ) & = & \sqrt{10^2 + 4^2 + 3^2} = \sqrt{125} = 11.18 \nonumber \\} \pause 
\invisible<1-6>{d_{4} (\boldsymbol{X}_{i}, \boldsymbol{X}_{j} ) & = & 10 \nonumber \\} \pause 
\invisible<1-7>{d_{4} (\boldsymbol{X}_{i}, \boldsymbol{X}_{k} ) & = & \sqrt{10^4 + 4^4 + 3^4} = (10337)^{1/4}= 10.08 \nonumber \\} \pause 
\invisible<1-8>{d_{\infty} (\boldsymbol{X}_{i}, \boldsymbol{X}_{j} ) & = & 10 \nonumber \\} \pause 
\invisible<1-9>{d_{\infty} (\boldsymbol{X}_{i}, \boldsymbol{X}_{k} ) & = & 10 \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Are all differences equal?}

Previous metrics treat all dimensions as \alert{equal} \pause \\
\invisible<1>{We may want to engage in some \alert{scaling}/reweighting \\} \pause

\invisible<1-2>{\alert{Mahalanobis Distance}\\} \pause

\invisible<1-3>{
\begin{defn}

Suppose that we have a covariance matrix $\boldsymbol{\Sigma}$}\pause\invisible<1-4>{. Then we can define the Mahalanobis Distance between documents $\boldsymbol{X}_{i}$ and $\boldsymbol{X}_{j}$ as} \pause , 
\begin{eqnarray}
\invisible<1-5>{d_{\text{Mah}}(\boldsymbol{X}_{i}, \boldsymbol{X}_{j}) & = & \sqrt{(\boldsymbol{X}_{i} - \boldsymbol{X}_{j})^{'}\boldsymbol{\Sigma}^{-1} (\boldsymbol{X}_{i} - \boldsymbol{X}_{j}) } \nonumber }
\end{eqnarray}
\end{defn}
\pause 
\invisible<1-6>{More generally: $\boldsymbol{\Sigma}$ could be symmetric and positive-definite} \pause

\invisible<1-7>{\alert{What does $\boldsymbol{\Sigma}$ do?}}

\end{frame}

\begin{frame}
\frametitle{Some Intuition: The Unit Circle}

\begin{columns}[]
\column{0.5\textwidth} 
\only<1>{\scalebox{0.35}{\includegraphics{Unit1.pdf}} } 
\only<2>{\scalebox{0.35}{\includegraphics{Unit2.pdf}} } 
\only<3>{\scalebox{0.35}{\includegraphics{Unit3.pdf}} }
\only<4-6>{\scalebox{0.35}{\includegraphics{Unit4.pdf}}}

\column{0.5\textwidth} 
\Huge
\only<1>{$\boldsymbol{\Sigma}  = \begin{pmatrix} 1 & 0 \\ 
										0 & 1\end{pmatrix} $} 
\only<2>{$\boldsymbol{\Sigma}  = \begin{pmatrix} 1 & 0 \\ 
										0 & 0.5\end{pmatrix} $}

\only<3>{$\boldsymbol{\Sigma}  = \begin{pmatrix} 0.5 & 0 \\ 
										0 & 1\end{pmatrix} $} 		
\only<4-6>{$\boldsymbol{\Sigma}  = \begin{pmatrix} 1 & 0.3 \\ 
										0.3 & 0.5\end{pmatrix} $}

\end{columns}

\end{frame}

\begin{frame}
\frametitle{Measuring Distance with Mahalanobis}

Special Case 1: Identity Matrix \pause 
\invisible<1>{\begin{eqnarray}
\boldsymbol{\Sigma} & = & \begin{pmatrix} 1 & 0 \\
0 & 1 \\
\end{pmatrix} \nonumber 
\end{eqnarray}
} \pause

\invisible<1-2>{Then distance is \alert{Euclidean}} \pause \\

\invisible<1-3>{Special Case 2: Diagonal Matrix
\begin{eqnarray}
\boldsymbol{\Sigma} & = & \begin{pmatrix} \sigma_{1}^{2} & 0 & \hdots &  0 \\
0 & \sigma_{2}^{2}& \hdots & 0  \\
\vdots & \vdots & \ddots & \vdots \\
0 & 0 & \hdots & \sigma^{2}_{J} \\
\end{pmatrix} \nonumber 
\end{eqnarray}
} \pause 
\invisible<1-4>{Then 
\begin{eqnarray}
d_{\text{Mah}}(\boldsymbol{X}_{i}, \boldsymbol{X}_{j} ) & = & \sqrt{\sum_{m=1}^{J} \frac{(x_{im} - x_{jm})^2}{\sigma_{m}^2}    } \nonumber 
\end{eqnarray}
}
\end{frame}

\begin{frame}
\frametitle{Measuring Similarity}

\pause

\invisible<1>{What properties should similarity measure have?} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Maximum: document with itself} \pause 
\invisible<1-3>{\item[-] Minimum: documents have no words in common (\alert{orthogonal} ) } \pause 
\invisible<1-4>{\item[-] Increasing when \alert{more} of same words used } \pause 
\invisible<1-5>{\item[-] \alert{?} $s(a, b)  = s(b,a)$.  }  \pause 
\end{itemize}

\invisible<1-6>{How should additional words be treated?}

\end{frame}

\begin{frame}
\frametitle{Measuring Similarity}

\begin{center}
\scalebox{0.35}{\includegraphics{Fig1.pdf}}
\end{center}

Measure 1: Inner product \pause  \\
\begin{eqnarray}
\invisible<1>{(2, 1)^{'} \cdot (1, 4) & = & 6 }   \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}

\begin{center}
\only<1-3>{\scalebox{0.35}{\includegraphics{Fig2.pdf}}} 
\only<4>{\scalebox{0.35}{\includegraphics{Fig3.pdf}}}
\end{center}

\invisible<1>{\alert{Problem}(?): length dependent } 
\begin{eqnarray}
\invisible<1-2>{(4,2)^{'} (1,4) & = & 12 } \nonumber \\ 
\invisible<1-3>{a \cdot b & = & ||a|| \times ||b|| \times \cos \theta \nonumber }
\end{eqnarray}

\pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Cosine Similarity}

\begin{center}
\only<7->{\scalebox{0.35}{\includegraphics{Fig4.pdf}}}
\end{center}

\only<7->{
$\cos \theta$: removes document length from similarity measure\\ \pause 
\invisible<1-7>{Projects texts to unit length representation$\leadsto$ onto sphere}
}

\only<1-6>{\begin{eqnarray}
\invisible<1>{\cos \theta & = & \left(\frac{a} {||a||}\right)  \cdot \left(\frac{b} {||b||}  \right) \nonumber \\} 
\invisible<1-2>{\frac{(4,2)}{||(4,2) ||} & = & (0.89, 0.45) \nonumber \\} 
\invisible<1-3>{\frac{(2,1)}{||(2,1) || } & = & (0.89, 0.45) \nonumber \\}
\invisible<1-4>{\frac{(1,4)} {||(1,4)||}  & = & (0.24, 0.97) \nonumber } \\
\invisible<1-5>{(0.89, 0.45)^{'} (0.24, 0.97) & = & 0.65 \nonumber } 
\end{eqnarray}
}

\pause \pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Von Mises-Fisher Distribution}

Consider document $\boldsymbol{X}_{i}$. \pause 
\begin{eqnarray}
\invisible<1>{\boldsymbol{X}_{i}^{*} & = & \frac{\boldsymbol{X}_{i}}{||\boldsymbol{X}_{i} ||} \nonumber } \pause 
\end{eqnarray}

\invisible<1-2>{Then we might suppose: } \pause 
\begin{eqnarray}
\invisible<1-3>{\boldsymbol{X}_{i}^{*} & \sim & \text{von Mises-Fisher}(\kappa, \boldsymbol{\mu}) \nonumber \\} \pause 
\invisible<1-4>{p(\boldsymbol{x}_{i} | \kappa, \boldsymbol{\mu}) & = & c(\kappa) \exp\left( \kappa \boldsymbol{x}_{i}^{*} \boldsymbol{\mu}   \right) \nonumber } \pause 
\end{eqnarray}

\invisible<1-5>{\alert{Normal distribution}, on a sphere} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Straightforward to Maximize} \pause 
\invisible<1-7>{\item[-] Conjugate to itself} \pause 
\invisible<1-8>{\item[-] Useful for clustering, hierarchies of topics} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Kernel Similarity}

\begin{defn}

Suppose we have documents $\boldsymbol{X}_{i}$ and $\boldsymbol{X}_{j}$.  Define the \alert{Gaussian} kernel as

\begin{eqnarray}
k(\boldsymbol{X}_{i}, \boldsymbol{X}_{j} ) & = & \exp\left( - \frac{||\boldsymbol{X}_{i} - \boldsymbol{X}_{j}||^2}{\sigma^2}   \right) \nonumber 
\end{eqnarray}

\end{defn}
\pause

\begin{itemize}
\invisible<1>{\item[] \alert{Kernel} of the \alert{Gaussian} distribution} \pause 
\invisible<1-2>{\item[] $\sigma^2$ = determines sensitivity of the kernel} \pause 
\invisible<1-3>{\item[] If $\boldsymbol{X}_{i} = \boldsymbol{X}_{j}$ then $k(\boldsymbol{X}_{i}, \boldsymbol{X}_{j}) = 1$} \pause
\invisible<1-4>{\item[] As $\boldsymbol{X}_{i} $ and $\boldsymbol{X}_{j}$ become more dissimilar, then $k(\boldsymbol{X}_{i}, \boldsymbol{X}_{j}) = 0$} \pause 
\invisible<1-5>{\item[] Result$\leadsto$ often justify setting some kernel weights to zero} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{The Kernel Trick}

Suppose all of our documents $\boldsymbol{X}_{i} \in \Re^{J}$\\ \pause 
\invisible<1>{There may be some mapping $\phi:\Re^{J} \rightarrow \Re^{M}$ where $M>J$ that improves our performance ``lift" to higher dimension\\} \pause 
\invisible<1-2>{We might want, then, } \pause 
\begin{eqnarray}
\invisible<1-3>{s(\phi(\boldsymbol{X}_{i}), \phi(\boldsymbol{X}_{j})) & = & < \phi(\boldsymbol{X}_{i}), \phi(\boldsymbol{X}_{j}) > \nonumber } \pause 
\end{eqnarray}

\begin{itemize}
\invisible<1-4>{\item[-] The only thing we care about, though is \alert{inner product} of transformed variables\\} \pause 
\invisible<1-5>{\item[-] $\leadsto$ So long as we can calculate inner product, we need not make explicit transformation\\} \pause 
\invisible<1-6>{\item[-] $\leadsto$ \alert{Kernels} provide methods for capture wide array of transformations.  \\} \pause 
\invisible<1-7>{\item[-] \alert{Kernel Trick}$\leadsto$ calculate inner products on \alert{untransformed} data (Gaussian Kernel), implicitly use wide array of $\phi$'s.  } 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Weighting Words}

Are all words created equal?  \pause 
\begin{itemize}
\invisible<1>{\item[-] Treat all words equally} \pause 
\invisible<1-2>{\item[-] \alert{Lots of noise} } \pause 
\invisible<1-3>{\item[-] Reweight words} \pause 
\begin{itemize}
\invisible<1-4>{\item[-] Accentuate words that are likely to be \alert{informative}} \pause 
\invisible<1-5>{\item[-] Make specific assumptions about characteristics of \alert{informative} words} \pause 
\end{itemize}
\end{itemize}

\invisible<1-6>{How to generate weights?} \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Assumptions about separating words} \pause 
\invisible<1-8>{\item[-] Use \alert{training} set to identify separating words (Monroe, Ideology measurement)} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Weighting Words: TF-IDF Weighting}

What properties do words need to separate concepts? \pause 
\begin{itemize}
\invisible<1>{\item[-] Used frequently} \pause 
\invisible<1-2>{\item[-] But not too frequently} \pause 
\end{itemize}
\invisible<1-3>{\alert{Ex.} If all statements about OBL contain {\tt Bin Laden} than this contributes nothing to similarity/dissimilarity measures\\} \pause

\invisible<1-4>{\alert{Inverse document frequency}:} \pause
\begin{eqnarray}
\invisible<1-5>{\text{n}_{j} & = & \text{No. documents in which word $j$ occurs} \nonumber \\} \pause
\invisible<1-6>{\text{idf}_{j} & = & \log \frac{N} {n_j} \nonumber  \\ } \pause
\invisible<1-7>{\textbf{idf} & = & (\text{idf}_{1} , \text{idf}_{2}, \hdots, \text{idf}_{J} ) \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Weighting Words: TF-IDF Weighting}

Why $\log$ ? \pause 
\begin{itemize}
\invisible<1>{\item[-] Maximum at $n_j$ = 1} \pause 
\invisible<1-2>{\item[-] Decreases at rate $\frac{1}{n_j} \Rightarrow$ diminishing ``penalty" for more common use} \pause 
\invisible<1-3>{\item[-] Other functional forms are fine, embed assumptions about penalization of common use} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Weighting Words: TF-IDF}

\pause 
\begin{eqnarray}
\invisible<1>{\textbf{X}_{i, \text{idf}}  \equiv \underbrace {\textbf{X}_{i}}_{\text{tf} } \times \textbf{idf} & = & (X_{i1} \times \text{idf}_1 , X_{i2} \times \text{idf}_2 , \hdots, X_{iJ} \times \text{idf}_J) \nonumber \\} \pause 
\invisible<1-2>{\textbf{X}_{j,\text{idf}}\equiv \textbf{X}_{j} \times \textbf{idf} & = & (X_{j1} \times \text{idf}_1 , X_{j2} \times \text{idf}_2 , \hdots, X_{jJ} \times \text{idf}_J ) \nonumber} \pause 
\end{eqnarray}

\invisible<1-3>{How Does This Matter For Measuring Similarity/Dissimilarity? \\} \pause

\invisible<1-4>{\alert{Inner Product} } \pause 
\begin{eqnarray}
\invisible<1-5>{\textbf{X}_{i, \text{idf}} \cdot \textbf{X}_{j, \text{idf}} & = &(\textbf{X}_{i} \times \textbf{idf} )^{'} ( \textbf{X}_{j} \times \textbf{idf})  \nonumber \\} \pause 
\invisible<1-6>{ & = & (\text{idf}_1^2 \times  X_{i1} \times X_{j1}) + (\text{idf}^{2}_2 \times X_{i2} \times X_{j2}) + \nonumber \\
 & &  \hdots + (\text{idf}_J^{2} \times X_{iJ} \times X_{jJ}) \nonumber } 
 \end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Weighting Words: Inner Product}

Define: \pause \\
\vspace{0.25in}

\invisible<1>{$\boldsymbol{\Sigma}  = \begin{pmatrix}
											\text{idf}_1^{2} & 0 & 0 &\hdots & 0 \\
											0 & \text{idf}_2^{2} & 0 &\hdots &0 \\
											\vdots & \vdots & \vdots & \ddots & \vdots \\
											0 & 0 & 0 & \hdots & \text{idf}_J^{2}
											\end{pmatrix} $} \pause

\vspace{0.25in}
\invisible<1-2>{If we use tf-idf for our documents, then  } \pause 
\begin{eqnarray}
\invisible<1-3>{d_{2}(\boldsymbol{X}_{i}, \boldsymbol{X}_{j} ) & = & \sqrt{\sum_{m=1}^{J}(x_{im, \text{idf}} - x_{jm, \text{idf}} )^{2} } \nonumber \\
 & = & \sqrt{(\boldsymbol{X}_{i}  - \boldsymbol{X}_{j})^{'}\boldsymbol{\Sigma} (\boldsymbol{X}_{i}  - \boldsymbol{X}_{j})  } \nonumber }
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Final Product}

Applying some measure of distance, similarity (if symmetric) yields:

$\textbf{D} = \begin{pmatrix} 
0 & d (1, 2)  & d(1, 3) & \hdots & d(1, N) \\
\alert{d(2,1)} & 0 &  d(2,3)  & \hdots & d(2, N) \\
\alert{d(3,1)} & \alert{d(3,2)} & 0 & \hdots & d(3, N ) \\
\vdots & \vdots & \vdots & \ddots & \vdots \\
\alert{d(N,1)} & \alert{d(N,2)} & \alert{d(N,3)}   & \alert{\hdots}  & 0  
\end{pmatrix} $

\vspace{0.5in}

\alert{Lower Triangle} contains unique information $N(N-1)/2$

\end{frame}

\begin{frame}
\frametitle{Spirling and Indian Treaties}

\alert{Spirling (2013)}: model Treaties between US and Native Americans \pause \\
\invisible<1>{Why?} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] American political development} \pause 
\invisible<1-3>{\item[-] IR Theories of Treaties and Treaty Violations} \pause 
\invisible<1-4>{\item[-] Comparative studies of indigenous/colonialist interaction} \pause 
\invisible<1-5>{\item[-] \alert{Political Science question}: how did Native Americans lose land so quickly?} \pause 
\end{itemize}

\invisible<1-6>{Paper does \alert{a lot}.  We're going to focus on } \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Today: Text representation and similarity calculation} \pause 
\invisible<1-8>{\item[-] Tuesday: Projecting to low dimensional space} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Spirling and Indian Treaties}

How do we preserve word order and semantic language? \\

After stemming, stopping, bag of wording: 
\begin{itemize}
\item[-] {\tt Peace Between Us} 
\item[-] {\tt No Peace Between Us} 
\end{itemize}

 are identical.  \\

 Spirling uses complicated representation of texts to preserve word order$\leadsto$ broad application\\
\only<1>{\tt \alert{Peac}e Between Us} 
\only<2>{\tt P\alert{eace} Between Us } 
\only<3>{\tt Pe\alert{ace }Between Us }
\only<4>{\tt Pea\alert{ce B}etween Us }
\only<5>{\tt Peac\alert{e Be}tween Us }
\only<6>{\tt Peace\alert{ Bet}ween Us }
\only<7>{\tt Peace \alert{Betw}een Us }
\only<8>{\tt Peace B\alert{etwe}en Us }
\only<9>{\tt Peace Be\alert{twee}n Us }
\only<10>{\tt Peace Bet\alert{ween} Us }
\only<11>{\tt Peace Betw\alert{een }Us }
\only<12>{\tt Peace Betwe\alert{en U}s }
\only<13>{\tt Peace Betwee\alert{n Us} }

\alert{Analyzes K-substrings}

\end{frame}

\begin{frame}
\frametitle{\alert{Kernel Trick} }

\pause

\begin{itemize}
\invisible<1>{\item[-] \alert{Kernel Methods}: Represent texts, measure similarity} \pause \invisible<1-2>{ \alert{simultaneously}} \pause
\invisible<1-3>{\item[-] Compare only \alert{substrings} in both documents (without explicitly quantifying entire documents)} \pause 
\invisible<1-4>{\item[-] Problem solved:} \pause 
\begin{itemize}
\invisible<1-5>{\item[-] \textcolor{blue}{Arthur} gives all his money to \alert{Justin}} \pause 
\invisible<1-6>{\item[-] \alert{Justin} gives all his money to \textcolor{blue}{Arthur}} \pause 
\invisible<1-7>{\item[-] Discard word order: same sentence } \pause \invisible<1-8>{Kernel : different sentences.  } 
\end{itemize}
\end{itemize}
\invisible<1-9>{Uses Kernel methods to measure \alert{similarity}}

\pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Similarity and Dissimilarity of Many Things}

Throughout the course we'll measure \alert{similarity} between documents\\
We'll also (implicitly) study \alert{similarity of probability distributions}\\
Develop a measure of distribution dissimilarity\\

\end{frame}

\begin{frame}
\frametitle{Similarity of Probability Distributions}

\begin{defn}
Suppose $P$ is a continuous random variable with density $p:\Re \rightarrow \Re$ and $Q$ is a continuous random variable with 
density $q:\Re \rightarrow q$.  \\

We can define the KL-Divergence between $P$ and $Q$ as
\begin{eqnarray}
KL(P||Q) & = & \int_{-\infty}^{\infty} p(x) \log \frac{p(x)}{q(x)} dx \nonumber 
\end{eqnarray}
\end{defn}

\end{frame}

\begin{frame}
\frametitle{Assessing Similarity of Other Things}

 KL-divergence measures \alert{dissimilarity}
between two distributions.
\end{frame}

\begin{frame}
%Functions vs \alert{Functionals} \pause \\
Consider a function. $f(x) = - x^2$. \pause \\
\invisible<1>{ Maps numbers to other numbers.} \pause
\begin{center}
\invisible<1-2>{\scalebox{0.5}{\includegraphics{Function1.pdf}}}
\end{center}
\end{frame}

\begin{frame}
Take some input (-2 here)
\begin{center}
\scalebox{0.5}{\includegraphics{Function2.pdf}}
\end{center}
\end{frame}

\begin{frame}
Then obtain the value of $f(-2)$
\begin{center}
\scalebox{0.5}{\includegraphics{Function3.pdf}}
\end{center}
\end{frame}

\begin{frame}
Then obtain the value of $f(-2) = -4$
\begin{center}
\scalebox{0.5}{\includegraphics{Function4.pdf}}
\end{center}
\end{frame}

\begin{frame}
KL$(q||p)$ is a \alert{functional}.  \pause \invisible<1>{ A
functional takes \alert{functions} as inputs,
returns a real number.} \pause \\
\invisible<1-2>{KL$(q||p)$ maps from sets of distributions $q \in \mathcal{Q}$ and $p \in \mathcal{P}$ to positive real numbers.}\pause \\
\invisible<1-3>{For example, we could set $q$ = \alert{Uniform(0,1)}
and $p$ = \textcolor{blue}{Normal(0, 1)} } \pause \\
\invisible<1-4>{KL($\alert{\text{Uniform(0,1)}}||\textcolor{blue}{\text{Normal(0,1)}}$)
= 1.09}
\begin{center}
\invisible<1-3>{\scalebox{0.4}{\includegraphics{Functional.pdf}}}
\end{center}
\end{frame}

\begin{frame}
If $q$ and $p$ are the \alert{same} distribution then KL$(q||p) =
0$.
\pause \\
\invisible<1>{Variational Approximation (topic models!): \alert{approximate} one
distribution $p$, with another, simpler distribution $q$.} \pause \\
\invisible<1-2>{Then make this approximation the \alert{best}
possible--minimize the KL-divergence.}
\end{frame}

\begin{frame}
A simple example.\\ \pause \invisible<1>{ Approximate a
\textcolor{blue}{Normal(0,1)} with symmetric \alert{Uniform} distribution, \alert{Uniform(-b, b)}.} \pause \\
\invisible<1-2>{Choose $b$ to min. KL(\alert{Uniform(-b, b)}$||$
\textcolor{blue}{Normal(0,1)})} \pause \invisible<1-3>{
\begin{center}
 \scalebox{0.45}{\includegraphics{Functional2.pdf}}
\end{center}
}
\end{frame}

\begin{frame}
Answer: \pause \\
\invisible<1>{$b = \sqrt{3}$} \pause
\begin{center}
\invisible<1-2>{ \scalebox{0.55}{\includegraphics{Functional3.pdf}}}
\end{center}

\end{frame}

\begin{frame}

\begin{itemize}
\item[1)] Documents in vector space $\leadsto$ geometry of texts
\item[2)] Many methods to measure similarity and dissimilarity
\end{itemize}

\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/tc7.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\newcommand{\argmin}{\arg\!\min}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
 \numberwithin{equation}{section}

%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{October 14th, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Finding Lower Dimensional Embeddings of Text}
\begin{itemize}
\item[1)] Task: \pause 
\begin{itemize}
\invisible<1>{\item[-] Embed our documents in a lower dimensional space} \pause 
\invisible<1-2>{\item[-] Visualize our documents} \pause 
\invisible<1-3>{\item[-] Inference about similarity} \pause 
\invisible<1-4>{\item[-] \alert{Social science inference about behavior}} \pause 
\end{itemize}
\invisible<1-5>{\item[2)] Objective Function, $f(\boldsymbol{X}, \boldsymbol{\theta})$ } \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Reconstruction error: measure the distance between the \alert{embedded} points and the original points}\pause\invisible<1-7>{$\leadsto$ $\boldsymbol{\theta}$ will contain basis vectors (\alert{principal components}) and \alert{weights} to those vectors } \pause 
\invisible<1-8>{\item[-] Distance preservation: measure how well pairwise distances are preserved with distances$\leadsto$ $\boldsymbol{\theta}$ a set of new lower-dimensional coordinates} \pause 
\end{itemize}
\invisible<1-9>{\item[3)] Optimization}\pause\invisible<1-10>{$\leadsto$ eigenvectors, eigenvalues} \pause 
\begin{itemize}
\invisible<1-11>{\item[-] Reconstruction error$\leadsto$ Search over components and weights } \pause 
\invisible<1-12>{\item[-] Distance preservation$\leadsto$ Search over locations} \pause 
\end{itemize}
\invisible<1-13>{\item[4)] Validation} \pause 
\begin{itemize}
\invisible<1-14>{\item[a)] Labeling exercise: What are the dimensions? } \pause 
\invisible<1-15>{\item[b)] Are the dimensions interesting semantically?} 
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{An Introduction to Eigenvectors, Values, and Diagonalization}

\begin{defn}
Suppose $\boldsymbol{A}$ is an $N \times N$ matrix and $\lambda$ is a scalar.  \\

If

\begin{eqnarray}
\boldsymbol{A}\boldsymbol{x} &= & \lambda \boldsymbol{x} \nonumber 
\end{eqnarray}

Then $\boldsymbol{x}$ is an \alert{eigenvector} and $\lambda$ is the associated \alert{eigenvalue}

\end{defn}

\pause

\begin{itemize}
\invisible<1>{\item[-] $\boldsymbol{A}$ stretches the eigenvector $\boldsymbol{x}$ } \pause 
\invisible<1-2>{\item[-] $\boldsymbol{A}$ stretches $\boldsymbol{x}$ by $\lambda$ } \pause 
\invisible<1-3>{\item[-] To find eigenvectors/values: ({\tt eigen} in {\tt R} ) } \pause 
\begin{itemize}
\invisible<1-4>{\item Find $\lambda$ that solves $\text{det}(\boldsymbol{A}- \lambda \boldsymbol{I}) = 0 $} \pause 
\invisible<1-5>{\item Find vectors in \alert{null space} of:} \pause 
\begin{eqnarray}
\invisible<1-6>{(\boldsymbol{A} - \lambda \boldsymbol{I} ) &= & 0 \nonumber } 
\end{eqnarray}
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Finding a Lower Dimensional Space (Manifold Learning)}
\begin{center}
\only<1>{\scalebox{0.5}{\includegraphics{PrCompExamp1.pdf}}}
\only<2>{\scalebox{0.5}{\includegraphics{PrCompExamp2.pdf}}}
\only<3>{\scalebox{0.5}{\includegraphics{PrCompExamp3.pdf}}}
\end{center}
\only<4-7>{
\begin{center}
\scalebox{0.15}{\includegraphics{PrCompExamp3.pdf}}
\end{center}
Original data:
\begin{eqnarray}
\invisible<1-4>{\boldsymbol{x}_{i} & = &  (x_{i1}, x_{i2}) \nonumber }
\end{eqnarray}

\invisible<1-5>{Which we approximate with } 
\begin{eqnarray}
\invisible<1-6>{\tilde{\boldsymbol{x}}_{i} & = & z_{i} \boldsymbol{w}_{1} \nonumber \\
& =& z_{i} (w_{11}, w_{12}) \nonumber } 
\end{eqnarray}
}

\only<8->{
\begin{center}
\scalebox{0.15}{\includegraphics{PrCompExamp3.pdf}}
\end{center}

Original data $\boldsymbol{x}_{i} \in \Re^{J}$ 
\begin{eqnarray}
\boldsymbol{x}_{i} & = & (x_{i1}, x_{i2}, \hdots, x_{iJ}) \nonumber 
\end{eqnarray}

Which we approximate with $L$($<J$) weights $z_{il}$ and vectors $\boldsymbol{w}_{l} \in \Re^{J}$
\begin{eqnarray}
\tilde{\boldsymbol{x}}_{i} & = & z_{i1} \boldsymbol{w}_{1} + z_{i2} \boldsymbol{w}_{2} + \hdots + z_{iL} \boldsymbol{w}_{L} \nonumber 
\end{eqnarray}

Define $\boldsymbol{\theta} = (\underbrace{\boldsymbol{Z}}_{N \times L}, \underbrace{\boldsymbol{W}_{L}}_{L \times J} )$

}
\pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Principal Component Analysis$\leadsto$ Objective function}

Consider 1-dimensional case ($L = 1$), centered data, and $||\boldsymbol{w}_{1}|| = 1$.  \pause  \\
\begin{eqnarray}
\invisible<1>{f(\boldsymbol{\theta},  \boldsymbol{X}) & = & \frac{1}{N} \sum_{i=1}^{N} ||\boldsymbol{x}_{i} - z_{i1}\boldsymbol{w}_{1} ||^2  } \pause  \nonumber \\
\invisible<1-2>{& = & \frac{1}{N} \sum_{i=1}^{N} (\boldsymbol{x}_{i}  - z_{i1} \boldsymbol{w}_{1} )^{'}(\boldsymbol{x}_{i}  - z_{i1} \boldsymbol{w}_{1} ) \nonumber } \pause \\
\invisible<1-3>{& = & \frac{1}{N}\sum_{i=1}^{N}\left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i} - 2 z_{i1}\boldsymbol{w}_{1}^{'}\boldsymbol{x}_{i} + z_{i1}^{2} \right ) \nonumber } \pause 
\end{eqnarray}

\invisible<1-4>{$\boldsymbol{w}_{1}^{'}\boldsymbol{w}_{1} = 1$}  
\end{frame}

\begin{frame}
\frametitle{Principal Component Analysis$\leadsto$ Optimization}

Optimization: \pause 
\begin{eqnarray}
\invisible<1>{\frac{\partial f(\boldsymbol{\theta}, \boldsymbol{X})}{\partial z_{i1}}  & = &  - \frac{2 \boldsymbol{w}_{1}^{'} \boldsymbol{x}_{i} + 2 z_{i1}}{N} \nonumber \\} \pause 
\invisible<1-2>{0 & = & - \frac{2 \boldsymbol{w}_{1}^{'} \boldsymbol{x}_{i} + 2 z_{i1}^{*}}{N} \nonumber \\} \pause 
\invisible<1-3>{z_{i1}^{*} & = & \boldsymbol{w}_{1}^{'} \boldsymbol{x}_{i} \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Principal Component Analysis$\leadsto$ Optimization}
Substituting in $z_{i1}^{*}$ \pause

\begin{eqnarray}
\invisible<1>{& = & \frac{1}{N} \sum_{i=1}^{N} (\boldsymbol{x}_{i}  - z_{i1}^{*} \boldsymbol{w}_{1} )^{'}(\boldsymbol{x}_{i}  - z_{i1}^{*} \boldsymbol{w}_{1} ) \nonumber } \pause \\
 \invisible<1-2>{& = & \frac{1}{N} \sum_{i=1}^{N} (\underbrace{\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i}}_{\text{Constant}}  - 2 z_{i1}^{*} \underbrace{\boldsymbol{w}_{1}^{'}\boldsymbol{x}_{i}}_{z_{i1}^{*}}  + \left(z_{i1}^{*}\right)^{2} \underbrace{\boldsymbol{w}_{1}^{'}\boldsymbol{w}_{1}}_{1} )   \nonumber } \pause \\
 \invisible<1-3>{& = &  - \frac{1}{N} \sum_{i=1}^{N}   \left(z_{i1}^{*}\right)^{2} + c \nonumber } \pause \\
 \invisible<1-4>{& = & - \frac{1}{N} \sum_{i=1}^{N} \boldsymbol{w}_{1}^{'}\boldsymbol{x}_{i}\boldsymbol{x}^{'}_{i}\boldsymbol{w}_{1} \nonumber } \pause \\
 \invisible<1-5>{& = & -  \boldsymbol{w}_{1}^{'}\boldsymbol{\Sigma} \boldsymbol{w}_{1} \nonumber} 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Principal Component Analysis$\leadsto$ Optimization}

\begin{eqnarray}
 & = & -  \sum_{i=1}^{N} \boldsymbol{w}_{1}^{'}\boldsymbol{\Sigma} \boldsymbol{w}_{1} \nonumber \pause 
\end{eqnarray}

\invisible<1>{where $\boldsymbol{\Sigma}$ is the :} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] Empirical covariance matrix$\leadsto \frac{1}{N} \boldsymbol{X}^{'}\boldsymbol{X}$} \pause 
\invisible<1-3>{\item[-] \alert{Variance} of the projected data.  Define } \pause 
\begin{eqnarray}
\invisible<1-4>{\boldsymbol{z}_{1} & = & (\boldsymbol{w}_{1} \boldsymbol{x}_{1}, \boldsymbol{w}_{1} \boldsymbol{x}_{2}, \hdots, \boldsymbol{w}_{1}\boldsymbol{x}_{N}) \nonumber \\} \pause 
\invisible<1-5>{\text{var}(\boldsymbol{z}_{1}) & = & E[\boldsymbol{z}_{1}^{2} ]  - E[\boldsymbol{z}_{1}]^{2} \nonumber \\} \pause 
\invisible<1-6>{& = & \frac{1}{N} \sum_{i=1}^{N} z_{i1}^{2} - 0 \nonumber \\} \pause 
\invisible<1-7>{& = & \frac{1}{N} \sum_{i=1}^{N} \boldsymbol{w}_{1}^{'}\boldsymbol{x}_{i}\boldsymbol{x}_{i}^{'}\boldsymbol{w}_{1} \nonumber } \pause 
\end{eqnarray}

\end{itemize}

\invisible<1-8>{Minimize reconstruction error }\pause \invisible<1-9>{$\leadsto$ maximize variance of projected data}

\end{frame}

\begin{frame}
\frametitle{Principal Component Analysis$\leadsto$ Optimization}

Maximize variance, subject to constraints \pause

\begin{eqnarray}
\invisible<1>{g(\boldsymbol{z}^{*}, \boldsymbol{w}_{1}, \boldsymbol{X}) & = & \boldsymbol{w}_{1}^{'} \boldsymbol{\Sigma}\boldsymbol{w}_{1} - \lambda_{1}(\boldsymbol{w}_{1}^{'} \boldsymbol{w}_{1} - 1 ) \nonumber \\} \pause 
 \invisible<1-2>{\frac{\partial g(\boldsymbol{z}^{*}, \boldsymbol{w}_{1}, \boldsymbol{X})}{\partial \boldsymbol{w}_{1}} &= & 2 \boldsymbol{\Sigma}\boldsymbol{w}_{1}  - 2 \lambda_{1} \boldsymbol{w}_{1} \nonumber \\}\pause 
 \invisible<1-3>{\boldsymbol{\Sigma}\boldsymbol{w}_{1}^{*} & = &  \lambda_{1} \boldsymbol{w}_{1}^{*} \nonumber } \pause 
\end{eqnarray}

\invisible<1-4>{$\alert{\boldsymbol{w}_{1}^{*}}$ = \alert{Eigenvector of $\boldsymbol{\Sigma}$}}\pause \invisible<1-5>{ (!!!!!!)} \pause \\
\invisible<1-6>{
We want $\boldsymbol{w}_{1}$ to maximize variance and } \pause 
\invisible<1-7>{
	\begin{eqnarray}
\boldsymbol{w}_{1}^{'} \boldsymbol{\Sigma} \boldsymbol{w}_{1} = \lambda_{1} \nonumber 
	\end{eqnarray}}\pause
\invisible<1-8>{
So $\boldsymbol{w}_{1}$ is eigenvector associated with the largest eigenvalue $\lambda_{1}$ 
}

\end{frame}

\begin{frame}
\frametitle{An Introduction to Eigenvectors, Values, and Diagonalization}

\begin{thm}
Suppose $\boldsymbol{A}$ is an \alert{invertible} $N \times N$ matrix.  Then $\boldsymbol{A}$ has $N$ distinct eigenvalues and $N$ linearly independent eigenvectors.  Further, we can write $\boldsymbol{A}$ as,

\begin{eqnarray}
\boldsymbol{A} &= & \boldsymbol{W}^{'}\begin{pmatrix}
\lambda_{1} & 0 & \hdots & 0 \\
0 & \lambda_{2} & \hdots & 0 \\
\vdots & \vdots & \ddots & \vdots \\
0 & 0&  \hdots & \lambda_{N}\\
\end{pmatrix}
\boldsymbol{W} \nonumber 
\end{eqnarray}

where $\boldsymbol{W} = \left(\boldsymbol{w}_{1}, \boldsymbol{w}_{2}, \hdots, \boldsymbol{w}_{N} \right)$ is an $N \times N$ matrix with the $N$ eigenvectors as column vectors.

\end{thm}

\end{frame}

\begin{frame}
\frametitle{An Introduction to Eigenvectors, Values, and Diagonalization}

\begin{defn}
Suppose $A$ is a covariance matrix.  Then, we can write $A$ as

\begin{eqnarray}
\boldsymbol{A} &= & \boldsymbol{W}^{'}\begin{pmatrix}
\lambda_{1} & 0 & \hdots & 0 \\
0 & \lambda_{2} & \hdots & 0 \\
\vdots & \vdots & \ddots & \vdots \\
0 & 0&  \hdots & \lambda_{N}\\
\end{pmatrix}
\boldsymbol{W} \nonumber 
\end{eqnarray}

Where $\lambda_{1}>\lambda_{2} > \hdots > \lambda_{N} \geq 0$. \\
We will call $\boldsymbol{w}_{1}$ the first eigenvector, $\boldsymbol{w}_{2}$ the second eigenvector, ..., $\boldsymbol{w}_{j}$ the $\text{j}^{th}$ eigenvector.

\end{defn}

\end{frame}

\begin{frame}
\frametitle{Back to Principal Components}

\begin{thm}
Suppose we want to approximate $N$ observations $\boldsymbol{x}_{i} \in \Re^{J}$ with $L < J$ orthogonal-unit length vectors $\boldsymbol{w}_{l} \in \Re^{J}$ with associated scores $z_{il}$ to minimize reconstruction error: \pause

\begin{eqnarray}
\invisible<1>{f(\boldsymbol{X}, \boldsymbol{\theta}) & = & \frac{1}{N} \sum_{i=1}^{N} || \boldsymbol{x}_{i}  - \sum_{l = 1}^{L} z_{il} \boldsymbol{w}_{l}||^{2} \nonumber  } \pause 
\end{eqnarray}

\invisible<1-2>{The optimal solution sets each $\boldsymbol{w}_{l}$ to be the $l^{\text{th}}$ eigenvector of the empirical covariance matrix.}\pause \invisible<1-3>{Further $z_{il}^{*} = \boldsymbol{w}_{l}^{'}\boldsymbol{x}_{i}$ so that the $L$ dimensional representation is:} \pause 
\begin{eqnarray}
\invisible<1-4>{\boldsymbol{x}^{L}_{i} & = & (\boldsymbol{w}_{1}^{'}\boldsymbol{x}_{i}, \boldsymbol{w}_{2}^{'}\boldsymbol{x}_{i}, \hdots, \boldsymbol{w}_{L}^{'}\boldsymbol{x}_{i} ) \nonumber } 
\end{eqnarray}

\end{thm}

\end{frame}

\begin{frame}
\frametitle{Application of Principal Components in {\tt R}}

Consider press releases from 2005 US Senators \pause \\
\invisible<1>{Define $\boldsymbol{x}_{i} = (x_{i1}, x_{i2}, \hdots, x_{iJ})$ as the rate senator $i$ uses $J$ words.  }\pause 
\begin{eqnarray}
\invisible<1-2>{x_{ij} & = & \frac{\text{No. Times $i$ uses word $j$}}{\text{No. words $i$ uses}} \nonumber } \pause 
\end{eqnarray}

\invisible<1-3>{{\tt  dtm}: $100 \times 2796$ matrix containing word rates for senators\\} \pause 
\invisible<1-4>{{\tt prcomp(dtm) } applies principal components}

\end{frame}

\begin{frame}
\frametitle{Application of Principal Components in {\tt R}}

\only<1>{\scalebox{0.5}{\includegraphics{FirstPrinComp.pdf}}}
\only<2>{\scalebox{0.5}{\includegraphics{CreditClaimPrinComp.pdf}}}

\end{frame}

\begin{frame}
\frametitle{How do we select the number of dimensions $L$?$\leadsto$ \alert{Model}}

We want to minimize reconstruction error \pause \invisible<1>{$\leadsto$ how well did we do? } \pause \\

\begin{eqnarray}
\invisible<1-2>{\text{error}(L) & = & \frac{1}{N} \sum_{i=1}^{N} ||\boldsymbol{x}_{i} - \sum_{l = 1}^{L} z_{il} \boldsymbol{w}_{l} ||^{2} } \pause \nonumber 
\end{eqnarray}

\invisible<1-3>{Simplifying:} \pause 
\begin{eqnarray}
\invisible<1-4>{\text{error}(L)  & = & \frac{1}{N} \sum_{i=1}^{N} (\boldsymbol{x}_{i} - \sum_{l = 1}^{L} z_{il}\boldsymbol{w}_l)^{'} (\boldsymbol{x}_{i} - \sum_{l = 1}^{L} z_{il}\boldsymbol{w}_l ) \nonumber \\} \pause 
\invisible<1-10>{& = & \frac{1}{N} \sum_{i=1}^{N} \left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i} - \sum_{l=1}^{L} z_{il}^{2} \right)\nonumber } 
\end{eqnarray}

\invisible<1-5>{Four types of terms:} \pause 
\begin{itemize}
\invisible<1-6>{\item[1)] $\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i} $} \pause 
\invisible<1-7>{\item[2)] $z_{ij}z_{ik} \boldsymbol{w}_{j}^{'}\boldsymbol{w}_{k} = z_{ij}z_{ik} 0  = 0 $} \pause 
\invisible<1-8>{\item[3)] $z_{ij}z_{ij} \boldsymbol{w}_{j}^{'}\boldsymbol{w}_{j} = z_{ij}^2$ } \pause 
\invisible<1-9>{\item[4)] $\boldsymbol{x}_{i}^{'}\sum_{l=1}^{L} z_{il} \boldsymbol{w}_{l} = \sum_{l=1}^{L} z_{il}^{2} $}\pause 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{How do we select the number of dimensions $L$?$\leadsto$ \alert{Model}}

\begin{small}
\begin{eqnarray}
\text{error}(L) & = & \frac{1}{N} \sum_{i=1}^{N} \left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i} - \sum_{l=1}^{L} z_{il}^{2} \right)\nonumber \pause \\
\invisible<1>{& = & \frac{1}{N} \sum_{i=1}^{N} \left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i} - \sum_{l=1}^{L} \boldsymbol{w}_{l} \boldsymbol{x}_{i} \boldsymbol{x}_{i}^{'}\boldsymbol{w}_{l} \right) \nonumber } \pause \\
\invisible<1-2>{& = & \frac{1}{N} \sum_{i=1}^{N} \left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i}\right)  - \frac{1}{N} \sum_{l=1}^{L} \sum_{l=1}^{N} \boldsymbol{w}_{i}^{'}\boldsymbol{x}_{i} \boldsymbol{x}_{i}^{'} \boldsymbol{w}_{i} \nonumber } \pause \\
\invisible<1-3>{& = & \frac{1}{N} \sum_{i=1}^{N} \left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i}\right)  - \sum_{l=1}^{L} \boldsymbol{w}_{l}^{'} \boldsymbol{\Sigma} \boldsymbol{w}_{l}  \nonumber } \pause \\
\invisible<1-4>{& = & \frac{1}{N} \sum_{i=1}^{N} \left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i}\right) - \sum_{l=1}^{L} \lambda_{l} \boldsymbol{w}_{l}^{'}\boldsymbol{w}_{l} \nonumber } \pause \\
\invisible<1-5>{& = & \frac{1}{N} \sum_{i=1}^{N} \left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i}\right) - \sum_{l=1}^{L} \lambda_{l} \nonumber } 
\end{eqnarray}

\end{small}

\end{frame}

\begin{frame}
\frametitle{How do we select the number of dimensions $L$?$\leadsto$ \alert{Model}}

If $L = J$ \pause 
\begin{eqnarray}
\invisible<1>{\text{error}(J) & = & \frac{1}{N} \sum_{i=1}^{N} \left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i}\right) - \sum_{l=1}^{J} \lambda_{l} = 0 \nonumber } \pause 
\end{eqnarray}

\invisible<1-2>{So for $L < J$, } \pause

\begin{eqnarray}
\invisible<1-3>{0  & = & \frac{1}{N} \sum_{i=1}^{N} \left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i}\right) - (\sum_{l=1}^{L} \lambda_{l} + \sum_{j=L+1}^{J} \lambda_{l} ) \nonumber \\} \pause 
\invisible<1-4>{\sum_{j=L+1}^{J} \lambda_{l}  & = & \frac{1}{N} \sum_{i=1}^{N} \left(\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i}\right) - \sum_{l=1}^{L} \lambda_{l} \nonumber \\} \pause 
\invisible<1-5>{\sum_{j=L+1}^{J} \lambda_{l}  & = & \text{error}(L) \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{How do we select the number of dimensions $L$?$\leadsto$ \alert{Model}}

\begin{eqnarray}
\sum_{j=L+1}^{J} \lambda_{l}  & = & \text{error}(L) \nonumber  \pause 
\end{eqnarray}

\begin{itemize}
\invisible<1>{\item[-] Error = Sum of ``remaining" eigenvalues} \pause 
\invisible<1-2>{\item[-] Total variance explained =  (sum of included eigenvalues)/(sum of all eigenvalues) } \pause 
\end{itemize}

\invisible<1-3>{Recommendation$\leadsto$ look for Elbow}

\end{frame}

\begin{frame}
\frametitle{How do we select the number of dimensions $L$?$\leadsto$ \alert{Model}}

\only<1>{\scalebox{0.425}{\includegraphics{ToyExamplePlot.pdf}}}
\only<2>{\scalebox{0.5}{\includegraphics{EigenPlot1.pdf}}}
\only<3>{\scalebox{0.5}{\includegraphics{EigenPlot2.pdf}}}
\only<4>{\scalebox{0.5}{\includegraphics{EigenPlot3.pdf}}}

\end{frame}

\begin{frame}
\frametitle{Non-model based evaluations: What's the point?}

What is the true underlying dimensionality of $\boldsymbol{X}$?\pause\invisible<1>{ \alert{J}}\pause\invisible<1-2>{(!!!!!)} \pause \\

\begin{itemize}
\invisible<1-3>{\item[-] Attempts to assess dimensionality require a \alert{model}$\leadsto$ some way to tradeoff accuracy of reconstruction with simplicity} \pause 
\invisible<1-4>{\item[-] \alert{Any} answer (no matter how creatively obtained) supposes \alert{you have the right function to measure tradeoff}} \pause 
\invisible<1-5>{\item[-] The ``right" number of dimensions depends on the \alert{task} you have in mind} \pause 
\end{itemize}

\invisible<1-6>{{\huge Mathematical model$\leadsto$ insufficient to make modeling decision}}

\end{frame}

\begin{frame}
\frametitle{Kernel Principal Component Analysis}
Recall from Thursday that we define a \alert{Kernel} ($N \times N$) matrix as:
\begin{eqnarray}
\boldsymbol{K} & = & \begin{pmatrix}
k(\boldsymbol{x}_{1}, \boldsymbol{x}_{1}) & k(\boldsymbol{x}_{1}, \boldsymbol{x}_{2}) & \hdots & k(\boldsymbol{x}_{1}, x_{N}) \\
k(\boldsymbol{x}_{2}, \boldsymbol{x}_{1}) & k(\boldsymbol{x}_{2}, \boldsymbol{x}_{2}) & \hdots & k(\boldsymbol{x}_{2}, \boldsymbol{x}_{N}) \\
\vdots & \vdots & \ddots & \vdots \\
k(\boldsymbol{x}_{N}, \boldsymbol{x}_{1}) & k(\boldsymbol{x}_{N}, \boldsymbol{x}_{2}) & \hdots & k(\boldsymbol{x}_{N}, \boldsymbol{x}_{N}) \\
\end{pmatrix}\nonumber 
\end{eqnarray}
\pause 
\invisible<1>{Where we suppose this matrix emerges from applying $\phi: \Re^{J} \rightarrow \Re^{M}$ to the data and then taking the inner product:} \pause 
\begin{eqnarray}
\invisible<1-2>{\boldsymbol{K} & = & \boldsymbol{\Phi}\boldsymbol{\Phi}^{'} \text{ (The inner product matrix)} \nonumber \\} \pause 
\invisible<1-3>{& = & \begin{pmatrix}
\phi(\boldsymbol{x}_{1})^{'}\phi(\boldsymbol{x}_{1}) & \phi(\boldsymbol{x}_{1})^{'}\phi(\boldsymbol{x}_{2}) & \hdots & \phi(\boldsymbol{x}_{1})^{'}\phi(\boldsymbol{x}_{N}) \nonumber \\
\phi(\boldsymbol{x}_{2})^{'}\phi(\boldsymbol{x}_{1}) & \phi(\boldsymbol{x}_{2})^{'}\phi(\boldsymbol{x}_{2}) & \hdots & \phi(\boldsymbol{x}_{2})^{'}\phi(\boldsymbol{x}_{N})\\
\vdots & \vdots & \ddots & \vdots \\
\phi(\boldsymbol{x}_{N})^{'}\phi(\boldsymbol{x}_{1}) & \phi(\boldsymbol{x}_{N})^{'}\phi(\boldsymbol{x}_{2}) & \hdots & \phi(\boldsymbol{x}_{N})^{'}\phi(\boldsymbol{x}_{N}) \\
\end{pmatrix} \nonumber } \pause 
\end{eqnarray}
\invisible<1-4>{\alert{Compute PCA of $\boldsymbol{\Phi}$ from $\boldsymbol{\Phi}\boldsymbol{\Phi}^{'}$ }} 
\end{frame}

\begin{frame}
\frametitle{Kernel PCA}

PCA of $\boldsymbol{X}$ \pause\invisible<1>{Eigenvectors of $\boldsymbol{X}^{'}\boldsymbol{X}$ ($\frac{1}{N}$ doesn't affect eigenvectors)} \pause  \\
\invisible<1-2>{Suppose $\boldsymbol{u}_{1}$ is an eigenvector for $\boldsymbol{X}\boldsymbol{X}^{'}$, with value $\lambda_{1}$.}\pause \invisible<1-3>{  Then } \pause 
\begin{eqnarray}
\invisible<1-4>{(\boldsymbol{X}\boldsymbol{X}^{'})\boldsymbol{u}_{1} & = & \lambda_{1} \boldsymbol{u}_{1} \nonumber \\} \pause
\invisible<1-5>{(\boldsymbol{X}^{'}\boldsymbol{X}) (\boldsymbol{X}^{'} \boldsymbol{u}_{1})  & = & \lambda_{1} (\boldsymbol{X}^{'}\boldsymbol{u}_{1}) \nonumber \\} \pause 
 \invisible<1-6>{& = & \lambda_{1} \boldsymbol{v}_{1} \nonumber } \pause 
\end{eqnarray}

\invisible<1-7>{But $\boldsymbol{v}_{1}$ needs unit length, and} \pause 
\begin{eqnarray}
\invisible<1-8>{||\boldsymbol{v}_{1}||^{2}  = \boldsymbol{v}^{'}_{1} \boldsymbol{v}_{1}  \nonumber \\ } \pause 
\invisible<1-9>{& = & \boldsymbol{u}_{1}^{'}\boldsymbol{X}\boldsymbol{X}^{'}\boldsymbol{u}_{1} \nonumber \\} \pause 
\invisible<1-10>{& = & \lambda_{1} \boldsymbol{u}_{1}^{'}\boldsymbol{u}_{1} = \lambda_{1}  \nonumber } \pause 
\end{eqnarray}

\invisible<1-11>{So first eigenvector of $\boldsymbol{X}^{'}\boldsymbol{X}$ is } \pause 
\begin{eqnarray}
\invisible<1-12>{\boldsymbol{w}_{1} & = & \frac{1}{\sqrt{\lambda_{1}} } \boldsymbol{X}^{'}\boldsymbol{u}_{1} \nonumber} 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Kernel PCA}

$\boldsymbol{K} = \boldsymbol{\Phi}\boldsymbol{\Phi}^{'}$ (assume $\boldsymbol{\Phi}$ is mean-centered, for now) \pause \\

\invisible<1>{We can obtain $\boldsymbol{u}_{1}$ and $\lambda_{1}$ from $\boldsymbol{K}$.}\pause \invisible<1-2>{ We know that } \pause 
\begin{eqnarray}
\invisible<1-3>{\boldsymbol{w}_{1} & = & \frac{1}{\sqrt{\lambda_{1}}} \underbrace{\boldsymbol{\Phi}^{'}}_{\text{Unknown}} \boldsymbol{u}_{1} \nonumber } \pause 
\end{eqnarray}

\invisible<1-4>{But suppose we want to project a point $\phi(\boldsymbol{x}_{i})$, then } \pause 
\begin{eqnarray} 
\invisible<1-5>{\phi(\boldsymbol{x}_{i})^{'}\boldsymbol{w}_{1}  &= & \frac{1}{\sqrt{\lambda_{1}}} \phi(\boldsymbol{x}_{i})^{'} \boldsymbol{\Phi}^{'} \boldsymbol{u}_{1} \nonumber \\} \pause 
\invisible<1-6>{\phi(\boldsymbol{x}_{i})^{'} \boldsymbol{\Phi}^{'} & = & \left[\phi(\boldsymbol{x}_{i} )^{'}\phi(\boldsymbol{x}_{1}), \phi(\boldsymbol{x}_{i} )^{'}\phi(\boldsymbol{x}_{2}), \hdots, \phi(\boldsymbol{x}_{i} )^{'}\phi(\boldsymbol{x}_{N}) \right] \nonumber \\} \pause 
 \invisible<1-7>{&  = & \left[k(\boldsymbol{x}_{i}, \boldsymbol{x}_{1}) , k(\boldsymbol{x}_{i}, \boldsymbol{x}_{2}) , \hdots, k(\boldsymbol{x}_{i}, \boldsymbol{x}_{N}) \right]}\pause \invisible<1-8>{= \boldsymbol{k}(\boldsymbol{x}_{i}, * ) \nonumber } \pause 
\end{eqnarray}

\invisible<1-9>{Then, we can obtain projection for observation $i$ using Kernel with } \pause 
\begin{eqnarray}
\invisible<1-10>{\phi(\boldsymbol{x}_{i})^{'} \boldsymbol{w}_{1} & = & \frac{1}{\sqrt{\lambda_{1}} } \boldsymbol{k}(\boldsymbol{x}_{i}, *) \boldsymbol{u}_{1} \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Kernel PCA}

Center $\boldsymbol{K}$?\\

Use centering matrix $\boldsymbol{H}$
\begin{eqnarray}
\boldsymbol{H}  & = & \boldsymbol{I}_{N}  - \frac{(\boldsymbol{1}_{N} \boldsymbol{1}_{N}^{'})}{N} \nonumber \\
\boldsymbol{K}_{\text{center}} & = & \boldsymbol{H} \boldsymbol{K} \boldsymbol{H} \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Spirling and Indian Treaties}

\alert{Spirling (2013)}: model Treaties between US and Native Americans \pause \\
\invisible<1>{Why?} \pause 
\begin{itemize}
\invisible<1-2>{\item[-] American political development} \pause 
\invisible<1-3>{\item[-] IR Theories of Treaties and Treaty Violations} \pause 
\invisible<1-4>{\item[-] Comparative studies of indigenous/colonialist interaction} \pause 
\invisible<1-5>{\item[-] \alert{Political Science question}: how did Native Americans lose land so quickly?} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Spirling and Indian Treaties}

How do we preserve word order and semantic language? \pause \\

\invisible<1>{After stemming, stopping, bag of wording: } \pause 
\begin{itemize}
\invisible<1-2>{\item[-] {\tt Peace Between Us} } \pause 
\invisible<1-3>{\item[-] {\tt No Peace Between Us} } \pause 
\end{itemize}

 \invisible<1-4>{are identical.  \\} \pause

 \invisible<1-5>{Spirling uses complicated representation of texts to preserve word order}\pause \invisible<1-6>{$\leadsto$ broad application\\} \pause 
\invisible<1-7>{\only<8>{\tt \alert{Peac}e Between Us} 
\only<9>{\tt P\alert{eace} Between Us } 
\only<10>{\tt Pe\alert{ace }Between Us }
\only<11>{\tt Pea\alert{ce B}etween Us }
\only<12>{\tt Peac\alert{e Be}tween Us }
\only<13>{\tt Peace\alert{ Bet}ween Us }
\only<14>{\tt Peace \alert{Betw}een Us }
\only<15>{\tt Peace B\alert{etwe}en Us }
\only<16>{\tt Peace Be\alert{twee}n Us }
\only<17>{\tt Peace Bet\alert{ween} Us }
\only<18>{\tt Peace Betw\alert{een }Us }
\only<19>{\tt Peace Betwe\alert{en U}s }
\only<20->{\tt Peace Betwee\alert{n Us} }
}

\end{frame}

\begin{frame}
\frametitle{Spirling and Indian Treaties}

Consider documents $\boldsymbol{x}_{i}$ and $\boldsymbol{x}_{j}$, where we have preserved order, punctuation, and all else. \pause \\
\invisible<1>{We say $\boldsymbol{x}_{i} \in \mathcal{X}$ } \pause \\
\invisible<1-2>{Spirling examines $5$-character strings, $s \in \mathcal{A}$} \pause \\
\invisible<1-3>{Define:} \pause \\
\invisible<1-4>{$\phi_{s}:\mathcal{X}\rightarrow\Re$ as a function that counts the number of times string $s$ occurs in document $\boldsymbol{x}$.\\} \pause

\invisible<1-5>{Define \alert{string kernel} to be, } \pause 
\begin{eqnarray}
\invisible<1-6>{k(\boldsymbol{x}_{i}, \boldsymbol{x}_{j} ) & = & \sum_{s \in \mathcal{A}} w_{s} \phi_{s}(\boldsymbol{x}_{i})\phi_{s}(\boldsymbol{x}_{j}) \nonumber  } \pause 
\end{eqnarray}

\invisible<1-7>{$\boldsymbol{\phi}(\boldsymbol{x}_{i}) \approx {{32}\choose{5}}$ element long count vector }

\end{frame}

\begin{frame}
\frametitle{Spirling and Indian Treaties}

\begin{center}
\only<1>{\scalebox{0.5}{\includegraphics{Scree.png}}}
\only<2>{\scalebox{0.5}{\includegraphics{HarshFig.png}}}
\end{center}

\end{frame}

\begin{frame}
\frametitle{Classic Multidimensional Scaling$\leadsto$ Objective Function}

Suppose we have an $N \times N$ matrix $\boldsymbol{D}\leadsto$ \pause \invisible<1>{matrix of squared Euclidean distances between documents $\boldsymbol{x}_{i}, \boldsymbol{x}_{j}  \in \Re^{J}$.} \pause   \\

\invisible<1-2>{Typical distance between $\boldsymbol{x}_{i}$ and $\boldsymbol{x}_{j}$ } \pause

\begin{eqnarray}
\invisible<1-3>{d_{ij}^{2} & = & \sum_{k=1}^{J} (x_{ik} - x_{jk})^{2} \nonumber } \pause 
\end{eqnarray}

\invisible<1-4>{For all $N$ documents we look for points $\boldsymbol{z}_{i} \in \Re^{L}$ (with $L < J$ ) to minimize } \pause 
\begin{eqnarray}
\invisible<1-5>{f(\boldsymbol{X}, \boldsymbol{\theta}) & = & f(\boldsymbol{X}, \boldsymbol{Z}) \nonumber \\} \pause 
 \invisible<1-6>{& =& \sum_{i\neq j} \left(d_{ij} - ||z_{i} - z_{j}|| \right)^{2} \nonumber  } \pause 
\end{eqnarray}

\invisible<1-7>{\alert{Recover best low-dimensional representation}$\leadsto$ Eigenvector decomposition of $\boldsymbol{D}$}

\end{frame}

\begin{frame}
\frametitle{Classic Multidimensional Scaling$\leadsto$ Optimization}

\begin{itemize}
\item[1)] Start with $\boldsymbol{D}$ \\
\item[2)] ``Center" $\boldsymbol{D}$ to obtain $\boldsymbol{X}\boldsymbol{X}^{'}$
\item[3)] Find largest eigenvectors of $\boldsymbol{X}\boldsymbol{X}^{'}$
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Classic Multidimensional Scaling$\leadsto$ Optimization}

Center the distance matrix, obtain inner product\pause 
\begin{eqnarray}
\invisible<1>{d_{ij}^{2} &= & \sum_{k=1}^{J} (x_{ik} - x_{jk})^{2} \nonumber \\}\pause
 \invisible<1-2>{&= & \sum_{k=1}^{J} (x_{ik}^2 - 2x_{ik} x_{jk} + x_{jk}^{2} ) \nonumber \\}\pause 
 \invisible<1-3>{& = & \underbrace{\boldsymbol{x}_{i}^{'}\boldsymbol{x}_{i}}_{\text{rows}} - 2 \boldsymbol{x}_{i} \boldsymbol{x}_{j} + \underbrace{\boldsymbol{x}_{j}^{'}\boldsymbol{x}_{j}}_{\text{columns}} \nonumber }\pause 
\end{eqnarray}

\begin{itemize}
\invisible<1-4>{\item[-] Subtract off row means}\pause 
\invisible<1-5>{\item[-] Subtract off column means}\pause 
\invisible<1-6>{\item[-] Divide by -2}\pause 
\end{itemize}

\begin{eqnarray}
\invisible<1-7>{\boldsymbol{X}\boldsymbol{X}^{'} & = & \frac{-\boldsymbol{H}\boldsymbol{D}\boldsymbol{H} \nonumber }{2}}
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Classic Multidimensional Scaling$\leadsto$ Optimization}

We can write $\boldsymbol{X}\boldsymbol{X}^{'}$ as

\begin{eqnarray}
\boldsymbol{X}\boldsymbol{X}^{'} & = & \boldsymbol{W}^{'}\begin{pmatrix}
\lambda_{1} & 0 & \hdots &  0 \\
0 & \lambda_{2} & \hdots & 0 \\
\vdots  & \vdots & \ddots & \vdots \\
0 & 0 & \hdots & \lambda_{N} \\
\end{pmatrix} \boldsymbol{W} \nonumber \\
& = & \underbrace{\boldsymbol{W}^{'} \begin{pmatrix}
\sqrt{\lambda_{1}} & 0 & \hdots &  0 \\
0 & \sqrt{\lambda_{2}} & \hdots & 0 \\
\vdots  & \vdots & \ddots & \vdots \\
0 & 0 & \hdots & \sqrt{\lambda_{N}} \\
\end{pmatrix}}_{\boldsymbol{X}} \underbrace{\begin{pmatrix}
\sqrt{\lambda_{1}} & 0 & \hdots &  0 \\
0 & \sqrt{\lambda_{2}} & \hdots & 0 \\
\vdots  & \vdots & \ddots & \vdots \\
0 & 0 & \hdots & \sqrt{\lambda_{N}} \\
\end{pmatrix} \boldsymbol{W}}_{\boldsymbol{X}^{'}} \nonumber 
\end{eqnarray}

Approximate $\boldsymbol{X}$ with first $L$ eigenvectors

\end{frame}

\begin{frame}
\frametitle{Classic Multidimensional Scaling$\leadsto$ Optimization}

Define $\boldsymbol{z}_{i}  \in \Re^{L}$ as, 
\begin{eqnarray}
\boldsymbol{z}_{i}^{*} & = & \left(\sqrt{\lambda_{1}}w_{1i},\sqrt{\lambda_{2}}w_{2i}, \hdots, \sqrt{\lambda_{L}} w_{Li} \right) \nonumber 
\end{eqnarray}

\pause

\begin{itemize}
\invisible<1>{\item[-] Same diagnostics as before: eigenvalues} \pause 
\invisible<1-2>{\item[-] Same issues in dimension reduction$\leadsto$ what are the dimensions for your task} \pause 
\invisible<1-3>{\item[-] Information up to \alert{rotation} and arbitrary \alert{center} (same result with any \alert{orthogonal} matrix $\boldsymbol{M}$)} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Comparing MDS and PCA}

\only<1>{\scalebox{0.5}{\includegraphics{PCAvsMDS.pdf}}}
\only<2>{\scalebox{0.5}{\includegraphics{PCAvsMDS2.pdf}}}
\only<3>{\scalebox{0.5}{\includegraphics{PCAvsMDS3.pdf}}}

\end{frame}

\begin{frame}
\frametitle{Sammon Multidimensional Scaling$\leadsto$ Manifold Learning}

Many other methods we won't cover: \pause

\begin{itemize}
\invisible<1>{\item[-] Sammon Multidimensional Scaling$\leadsto$ prioritizes small differences } 
\begin{eqnarray}
\invisible<1-2>{f(\boldsymbol{X}, \boldsymbol{Z}) & = & \sum_{i\neq j} \frac{ (d_{ij}  - ||z_{i} - z_{j}||)^{2}  }{d_{ij} }} \nonumber 
\end{eqnarray}
\invisible<1-3>{\item[-] \alert{Landmark MDS}$\leadsto$ for large scale embeddings} 
\invisible<1-4>{\item[-] \alert{ISOMap}$\leadsto$ Non-linear embedding, emphasizing local patterns} 
\end{itemize}

\begin{itemize}
\invisible<1-5>{\item[1)] Calculate distance matrix}
\invisible<1-6>{\item[2)] Create $K$ nearest neighbor graph: find $K$ nearest neighbors for each point, with edge weight = Euclidean distance}
\invisible<1-7>{\item[3)] Compute shortest weighted path between each node (distance matrix)}
\invisible<1-8>{\item[4)] Apply classic MDS }
\end{itemize}

\invisible<1-9>{Common theme$\leadsto$ Manifold Learning}

\pause \pause \pause \pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Low Dimensional Embedding}

\begin{itemize}
\item[1)] Find lower dimensional space to summarize documents$\leadsto$ Eigenvectors
\item[2)] Thursday: basic language models and the Dirichlet distribution
\end{itemize}

\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/tc9.tex
normal update

\documentclass{beamer}

%\usepackage[table]{xcolor}
\mode<presentation> {
  \usetheme{Boadilla}
%  \usetheme{Pittsburgh}
%\usefonttheme[2]{sans}
\renewcommand{\familydefault}{cmss}
%\usepackage{lmodern}
%\usepackage[T1]{fontenc}
%\usepackage{palatino}
%\usepackage{cmbright}
  \setbeamercovered{transparent}
\useinnertheme{rectangles}
}
%\usepackage{normalem}{ulem}
%\usepackage{colortbl, textcomp}
\setbeamercolor{normal text}{fg=black}
\setbeamercolor{structure}{fg= black}
\definecolor{trial}{cmyk}{1,0,0, 0}
\definecolor{trial2}{cmyk}{0.00,0,1, 0}
\definecolor{darkgreen}{rgb}{0,.4, 0.1}
\usepackage{array}
\newcommand{\argmin}{\arg\!\min}
\beamertemplatesolidbackgroundcolor{white}  \setbeamercolor{alerted
text}{fg=red}

\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}

%\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{colortbl}
%\usepackage[usenames, dvipsnames]{color}
%\setbeamertemplate{caption}[numbered]\newcounter{mylastframe}c
%\newcolumntype{Y}{\columncolor[cmyk]{0, 0, 1, 0}\raggedright}
%\newcolumntype{C}{\columncolor[cmyk]{1, 0, 0, 0}\raggedright}
%\newcolumntype{G}{\columncolor[rgb]{0, 1, 0}\raggedright}
%\newcolumntype{R}{\columncolor[rgb]{1, 0, 0}\raggedright}

%\begin{beamerboxesrounded}[upper=uppercol,lower=lowercol,shadow=true]{Block}
%$A = B$.
%\end{beamerboxesrounded}}
\renewcommand{\familydefault}{cmss}
%\usepackage[all]{xy}

\usepackage{tikz}
\usepackage{lipsum}

 \newenvironment{changemargin}[3]{%
 \begin{list}{}{%
 \setlength{\topsep}{0pt}%
 \setlength{\leftmargin}{#1}%
 \setlength{\rightmargin}{#2}%
 \setlength{\topmargin}{#3}%
 \setlength{\listparindent}{\parindent}%
 \setlength{\itemindent}{\parindent}%
 \setlength{\parsep}{\parskip}%
 }%
\item[]}{\end{list}}
\usetikzlibrary{arrows}
%\usepackage{palatino}
%\usepackage{eulervm}
\usecolortheme{lily}
\newtheorem{com}{Comment}
\newtheorem{lem} {Lemma}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{cor}{Corollary}
\newtheorem{obs}{Observation}
 \numberwithin{equation}{section}

%\usepackage[latin1]{inputenc}
\title[Text as Data] % (optional, nur bei langen Titeln nötig)
{Text as Data}

\author{Justin Grimmer}
\institute[Stanford University]{Associate Professor\\Department of Political Science \\  Stanford University}
\vspace{0.3in}

\date{October 21st, 2014}%[Big Data Workshop] 
%\date{\today}

\begin{document}
\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Fully Automated Clustering$\leadsto$ Discovering Categories and Classifying Documents}

\begin{footnotesize}
\begin{itemize}
\item[1)] Task
\begin{itemize}
\item[a)] Discovering categories and placing documents in those categories
\item[b)] Partitioning documents into similar groups
\end{itemize}
\item[2)] Objective function
\begin{itemize}
\item[a)] What makes a pair of documents similar (dissimilar)?
\item[b)] What makes a good clustering of texts?
\end{itemize}
\begin{eqnarray}
f(\boldsymbol{X}, \boldsymbol{\theta}) & = & f(\boldsymbol{X}, \boldsymbol{T}, \boldsymbol{\Theta}) \nonumber \end{eqnarray}
where:
\begin{itemize}
\item[-] $\boldsymbol{\Theta} = $ parameters that describe clusters $J \times K\leadsto$ unigram model 
\item[-] $\boldsymbol{T} = $ cluster assignments for each observation $N \times K$
\end{itemize}
\item[3)] Optimization
\begin{itemize}
\item[-] Algorithms search over $\boldsymbol{T}$ and $\boldsymbol{\Theta}$
\item[-] Expectation-Maximization Algorithm 
\end{itemize}
\item[4)] Validation
\begin{itemize}
\item[1)] Model based$\leadsto$ Exclusive/Cohesive
\item[2)] Human based$\leadsto$ Experiments to detect properties
\end{itemize}
\end{itemize}
\end{footnotesize}

\end{frame}

\begin{frame}
\frametitle{Unsupervised vs Supervised Methods}

\only<1-13, 16->{\alert{Unsupervised}\invisible<1>{$\leadsto$ estimate \alert{categories} and categorize documents} \\
\invisible<1-2>{\alert{Supervised}}\invisible<1-3>{$\leadsto$ know categories, supervise computer with classification} \\

\invisible<1-4>{ There is \alert{NO} sense in which there are fewer assumptions in unsupervised methods\\}
\begin{itemize}
\invisible<1-5>{\item[-] IF you know categories of interest}\invisible<1-6>{$\leadsto$ do supervised learning  }
\invisible<1-7>{\item[-] IF you want to}\invisible<1-11>{$\leadsto$ do unsupervised learning} 
\begin{itemize}
\invisible<1-8>{\item[-] Explore data set} 
\invisible<1-9>{\item[-] Discover new categories} 
\invisible<1-10>{\item[-] Quickly distill documents} 
\end{itemize}
\invisible<1-12>{\item[-] Debate: Unsupervised vs Supervised} 
\begin{itemize}
\invisible<1-15>{\item[-] NOT COMPETING METHODS$\leadsto$ fruitful combination} 
\invisible<1-16>{\item[-] Validate unsupervised methods$\leadsto$ supervised methods} 
\invisible<1-17>{\item[-] Explore heterogeneity in coding$\leadsto$ unsupervised methods in categories} 
\end{itemize}
\end{itemize}
}

\only<14>{\scalebox{0.75}{\includegraphics{LiterallyCant1.jpg}}}
\only<15>{\scalebox{0.7}{\includegraphics{LiterallyCanEven2.jpg}}}

\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{K-Means$\leadsto$ Objective Function}

$N$ documents $\boldsymbol{x}_{i} = (x_{i1}, x_{i2}, \hdots, x_{iJ})$ (normalized) \pause \\
\invisible<1>{Goal$\leadsto$ Partition documents into $K$ clusters. } \pause  \\
\invisible<1-2>{Two parameters to estimate} \pause 
\begin{itemize}
\invisible<1-3>{\item[1)] $K\times J$ matrix of cluster centers $\Theta$. } \pause \\
\invisible<1-4>{Cluster $k$ has center } \pause 
\begin{eqnarray}
\invisible<1-5>{\boldsymbol{\theta}_{k} & = & (\theta_{1k}, \theta_{2k}, \hdots, \theta_{Jk}) \nonumber }\pause
\end{eqnarray}
\invisible<1-6>{$\boldsymbol{\theta}_{k} = $ \alert{exemplar} for cluster $k$} \pause

\invisible<1-7>{\item[2)] $\boldsymbol{T}$ is an $N \times J$ matrix. Each row is an indicator vector.\\} \pause
\invisible<1-8>{If observation $i$ is from cluster $k$, then  } \pause 
\begin{eqnarray}
\invisible<1-9>{\boldsymbol{\tau}_{i} & = & (0, 0, \hdots, 0, \underbrace{1}_{k^{th}}, 0, \hdots, 0) \nonumber }\pause
\end{eqnarray}
\invisible<1-10>{\alert{Hard Assignment}}

\end{itemize}

\end{frame}

\begin{frame}
\frametitle{K-Means$\leadsto$ Objective Function}

Assume squared euclidean distance \pause

\begin{eqnarray}
\invisible<1>{f(\boldsymbol{X},\boldsymbol{T}, \boldsymbol{\Theta}) & = & \sum_{i=1}^{N} \sum_{k=1}^{K} \overbrace{\tau_{ik}}^{\text{cluster indicator}} \underbrace{\left(\sum_{j=1}^{J} (x_{ij} - \theta_{kj})^2 \right)}_{\text{Squared Euclidean Distance}} \nonumber }\pause
\end{eqnarray}

\begin{itemize}
\invisible<1-2>{\item[-] Calculate squared euclidean distance from center} \pause 
\invisible<1-3>{\item[-] \alert{Only} for the assigned cluster} \pause
\invisible<1-4>{\item[-] Two trivial solutions} \pause 
\begin{itemize}
\invisible<1-5>{\item[-] If $K = N$ then $f( \boldsymbol{X}, \boldsymbol{T}, \boldsymbol{\Theta})  = 0 $ (Minimum)} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Each observation in its own cluster} \pause 
\invisible<1-7>{\item[-] $\boldsymbol{\theta}_{i} = \boldsymbol{x}_{i}$} \pause 
\end{itemize}
\invisible<1-8>{\item[-] If $K = 1$, $f(\boldsymbol{X}, \boldsymbol{T}, \boldsymbol{\Theta}) = N \times \sigma^2$} \pause 
\begin{itemize}
\invisible<1-9>{\item[-] Each observation in same cluster} \pause 
\invisible<1-10>{\item[-] $\boldsymbol{\theta}_{1} = $ Average across documents} 
\end{itemize}
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{K-Means$\leadsto$ Optimization}

\alert{Coordinate descent}\pause \invisible<1>{$\leadsto$ iterate between labels and centers. } \pause  \\
\invisible<1-2>{Iterative algorithm: each iteration $t$} \pause 
\begin{itemize}
\invisible<1-3>{\item[-] Conditional on $\boldsymbol{\Theta}^{t-1}$ (from previous iteration), choose $\boldsymbol{T}^{t}$ } \pause 
\invisible<1-4>{\item[-] Conditional on $\boldsymbol{T}^{t}$, choose $\boldsymbol{\Theta}^{t}$} \pause 
\end{itemize}

\invisible<1-5>{Repeat until convergence$\leadsto$ as measured as change in $f$ dropping below threshold $\epsilon$} \pause 
\begin{eqnarray}
\invisible<1-6>{\text{Change} & = & f(\boldsymbol{X}, \boldsymbol{T}^{t}, \boldsymbol{\Theta}^{t} ) - f(\boldsymbol{X}, \boldsymbol{T}^{t-1}, \boldsymbol{\Theta}^{t-1} ) \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{K-Means$\leadsto$ Optimization}

\pause 
\begin{itemize}
\invisible<1>{\item[1)] initialize $K$ cluster centers $\boldsymbol{\theta}_{1}^{t}, \boldsymbol{\theta}_{2}^{t}, \hdots, \boldsymbol{\theta}_{K}^{t}$.  } \pause 
\end{itemize}

\begin{itemize}
\invisible<1-2>{\item[2)] Choose $\boldsymbol{T}^{t} $} \pause 
\end{itemize}

\begin{equation}
\invisible<1-3>{\tau_{im}^{t} =  \left \{ \begin{array} {ll}
1 \text{ if } m = \arg\min_{k} \sum_{j=1}^{J} (x_{ij} - \theta_{kj}^{t} )^2 \\
0  \text{ otherwise } ,
\end{array} \right. . \nonumber} \pause 
\end{equation}

\invisible<1-4>{In words: Assign each document $\boldsymbol{x}_{i}$ to the closest center $\boldsymbol{\theta}_{m}^{t}$}

\end{frame}

\begin{frame}
\frametitle{K-Means$\leadsto$ Optimization}

\pause 
\begin{itemize}
\invisible<1>{\item[3)] Choose $\Theta^{t} \leadsto$ Focus on the center for cluster $k$ } \pause 
\end{itemize}
\begin{eqnarray}
\invisible<1-2>{f(\boldsymbol{X}, \boldsymbol{T}^{t}, \boldsymbol{\Theta})_{k}  & = & \sum_{i=1}^{N} \tau_{ik}^{t} \left(\sum_{j=1}^{J} (x_{ij} - \theta_{jk})^{2}  \right) \nonumber \\} \pause 
\invisible<1-3>{\frac{\partial f(\boldsymbol{X}, \boldsymbol{T}^{t}, \boldsymbol{\Theta})_{k} }{\partial \theta_{kj} } & = & - 2 \sum_{i=1}^{N} \tau_{ij}^{t} \left(x_{ij} - \theta_{jk} \right) \nonumber \\} \pause 
\invisible<1-4>{0 & = &- 2 \sum_{i=1}^{N} \tau_{ij}^{t} \left(x_{ij} - \theta_{jk}^{*} \right) \nonumber\\}\pause 
\invisible<1-5>{& = & \sum_{i=1}^{N} \tau_{ij}^{t} x_{ij} - \theta_{jk}^{*} \sum_{i=1}^{N} \tau_{ij}^{t} \nonumber \\} \pause 
\invisible<1-6>{\frac{\sum_{i=1}^{N} \tau_{ik}^{t} x_{ij} }{ \sum_{i=1}^{N} \tau_{ik}^{t} } & = & \theta_{jk}^{*} \nonumber }
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{K-Means$\leadsto$ Optimization}

\begin{eqnarray}
\boldsymbol{\theta}^{t+1} & = & \frac{ \sum_{i=1}^{N} \tau_{ik} \boldsymbol{x}_{i} }{ \sum_{i=1}^{N} \tau_{ik}  } \pause \invisible<1>{ \propto \sum_{i=1}^{N} \tau_{ik} \boldsymbol{x}_{i} \nonumber }\pause 
\end{eqnarray}

\invisible<1-2>{In words: $\boldsymbol{\theta}^{t+1}$ is the average of the documents assigned to $k$.  \\}\pause

\invisible<1-3>{Optimization algorithm:} \pause 
\begin{itemize}
\invisible<1-4>{\item Initialize centers}\pause 
\invisible<1-5>{\item Do until converged:}\pause
\begin{itemize}
\invisible<1-6>{\item For each document, find closest center$\leadsto \boldsymbol{\tau}^{t}_{i}$}\pause
\invisible<1-7>{\item For each center, take average of assigned documents$\leadsto \boldsymbol{\theta}^{t}_{k}$ }\pause
\invisible<1-8>{\item Update change $f(\boldsymbol{X}, \boldsymbol{T}^{t}, \boldsymbol{\Theta}^{t} ) -  f(\boldsymbol{X}, \boldsymbol{T}^{t-1}, \boldsymbol{\Theta}^{t-1}) $}
\end{itemize}
\end{itemize}

\invisible<1-9>{Guaranteed convergence to \alert{local} minimum$\leadsto$ Each step decreases $f$ and there is an optimal partition$\leadsto$ close connection to EM-algorithms (see appendix to slides)}

\end{frame}

\begin{frame}
\frametitle{Visual Example}

\only<1>{\scalebox{0.5}{\includegraphics{BlankPoints.pdf}}}
\only<2>{\scalebox{0.5}{\includegraphics{KMeans1.pdf}}}
\only<3>{\scalebox{0.5}{\includegraphics{KMeans2.pdf}}}
\only<4>{\scalebox{0.5}{\includegraphics{KMeans3.pdf}}}
\only<5>{\scalebox{0.5}{\includegraphics{KMeans4.pdf}}}
\only<6>{\scalebox{0.5}{\includegraphics{KMeans5.pdf}}}
\only<7>{\scalebox{0.5}{\includegraphics{KMeans6.pdf}}}
\only<8>{\scalebox{0.5}{\includegraphics{KMeans7.pdf}}}
\only<9>{\scalebox{0.5}{\includegraphics{KMeans8.pdf}}}
\only<10>{\scalebox{0.5}{\includegraphics{KMeans9.pdf}}}
\only<11>{\scalebox{0.5}{\includegraphics{KMeans10.pdf}}}
\only<12>{\scalebox{0.5}{\includegraphics{KMeans11.pdf}}}
\only<13>{\scalebox{0.5}{\includegraphics{KMeansFinal.pdf}}}

\end{frame}

\begin{frame}
\frametitle{An Example: Jeff Flake}

{\tt To the R Code!}

\end{frame}

\begin{frame}
\frametitle{Interpreting Cluster Components}

Unsupervised methods\pause\invisible<1>{$\leadsto$ low startup costs, high post-model costs} \pause

\begin{itemize}
\invisible<1-2>{\item[-] Apply clustering methods, we have groups of documents} \pause
\invisible<1-3>{\item[-] How to interpret the groups?} \pause 
\invisible<1-4>{\item[-] Two (broad) methods:} \pause 
\begin{itemize}
\invisible<1-5>{\item[-] Manual identification (Quinn et al 2010)} \pause 
\begin{itemize}
\invisible<1-6>{\item[-] Sample set of documents from same cluster} \pause 
\invisible<1-7>{\item[-] Read documents} \pause 
\invisible<1-8>{\item[-] Assign cluster label} \pause 
\end{itemize}
\invisible<1-9>{\item[-] Automatic identification} \pause 
\begin{itemize}
\invisible<1-10>{\item[-] Know label classes} \pause 
\invisible<1-11>{\item[-] Use methods to identify separating words} \pause 
\invisible<1-12>{\item[-] Use these to help infer differences across clusters} \pause 
\end{itemize}
\end{itemize}
\invisible<1-13>{\item[-] \alert{Transparency}} \pause 
\begin{itemize}
\invisible<1-14>{\item[-] Debate what clusters are} \pause 
\invisible<1-15>{\item[-] Debate what they mean} \pause 
\invisible<1-16>{\item[-] Provide documents + organizations} \pause 
\end{itemize}
\end{itemize}

\invisible<1-17>{{\tt back to the R code!}}

\end{frame}

\begin{frame}
\frametitle{How Do We Choose $K$?}

\pause

\begin{itemize}
\invisible<1>{\item[-] Previous Analysis Assumed We Know Number of Clusters} \pause 
\invisible<1-2>{\item[-] How Do We Choose Cluster Number? } \pause 
\invisible<1-3>{\item[-] Cannot Compare $f$ across clusters  } \pause 
\begin{itemize}
\invisible<1-4>{\item[-] Sum squared errors decreases as $K$ increases } \pause 
\invisible<1-5>{\item[-] Trivial answer: each document in own cluster (useless) } \pause 
\invisible<1-6>{\item[-] Modeling problem: Fit often increases with features} \pause
\end{itemize}
\invisible<1-7>{\item[-] How do we choose number of clusters?} \pause 
\end{itemize}
\Huge
\invisible<1-8>{\alert{Think!}}\pause 
\normalsize
\begin{itemize}
\invisible<1-9>{\item[-] No one statistic captures how you want to use your data} \pause 
\invisible<1-10>{\item[-] But, can help guide your selection} \pause 
\invisible<1-11>{\item[-] Combination statistic +  manual search}\pause\invisible<1-12>{$\leadsto$discuss statistical methods/experimental methods on Thursday}
\invisible<1-12>{\item[-] \alert{Humans should be the final judge}  } \pause 
\begin{itemize}
\invisible<1-13>{\item[-] Compare insights across clusterings}
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Mixture of Unigram Models (Mixture of Multinomials)}

Mixture models$\leadsto$ wide range of applications \pause \\

\invisible<1>{Single distribution data generating process:} \pause 
\begin{eqnarray}
\invisible<1-2>{\boldsymbol{x}_{i} & \sim & \text{Distribution(parameters)} \nonumber } \pause 
\end{eqnarray}

\invisible<1-3>{Mixture of distribution data generating process:} \pause 
\begin{eqnarray}
\invisible<1-4>{\boldsymbol{\tau}_{i}| \boldsymbol{\pi} & \sim & \text{Multinomial}(1, \boldsymbol{\pi}) \nonumber \\} \pause
\invisible<1-5>{\boldsymbol{x}_{i} | \tau_{ik} = 1 & \sim & \text{Distribution(parameters$_{k}$)} \nonumber }\pause
\end{eqnarray}

\invisible<1-6>{In words:} \pause 
\begin{itemize}
\invisible<1-7>{\item[-] Draw a cluster label} \pause 
\invisible<1-8>{\item[-] Given distribution, draw realization} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Mixture of Unigram Models (Mixture of Multinomials)}

A mixture of unigram-language models

\begin{eqnarray}
\boldsymbol{\pi} & \sim & \text{Dirichlet}(\boldsymbol{1}) \nonumber \\
\boldsymbol{\theta} & \sim & \text{Dirichlet}(\boldsymbol{1}) \nonumber \\
\boldsymbol{\tau}_{i} | \boldsymbol{\pi} & \sim & \text{Multinomial}(1, \boldsymbol{\pi}) \nonumber \\
\boldsymbol{x}_{i}| \tau_{ik} = 1, \boldsymbol{\theta}_{k} & \sim & \text{Multinomial}(N_{i}, \boldsymbol{\theta}_{k} ) \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Mixture of Unigram Models (Mixture of Multinomials)}

This implies the following posterior distribution:

\begin{eqnarray}
p(\boldsymbol{T}, \boldsymbol{\Theta}, \boldsymbol{\pi} | \boldsymbol{X})\pause\invisible<1>{ & \propto & \overbrace{p(\boldsymbol{\pi}) p(\boldsymbol{\theta})}^{1} \underbrace{p(\boldsymbol{X}, \boldsymbol{T}| \boldsymbol{\pi}, \boldsymbol{\theta})}_{\text{Complete data likelihood}} \nonumber } \pause  \\
\invisible<1-2>{& \propto & \underbrace{\prod_{i=1}^{N} p(\boldsymbol{\tau}_{i} , \boldsymbol{x}_{i}| \boldsymbol{\theta}, \boldsymbol{\pi})}_{\text{Complete data likelihood}} \nonumber \\} \pause 
\invisible<1-3>{& \propto & \prod_{i=1}^{N} p(\boldsymbol{\tau}_{i} |\boldsymbol{\pi} ) p(\boldsymbol{x}_{i}| \boldsymbol{\theta}, \boldsymbol{\tau}_{i}) \nonumber \\} \pause 
\invisible<1-4>{& \propto & \prod_{i=1}^{N} \prod_{k=1}^{K} \left[ \pi_{k} \prod_{j=1}^{J} \theta_{jk}^{x_{ik}}  \right]^{\tau_{ik}} \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Mixture of Unigram Models (Mixture of Multinomials)}

Obtain MAP estimates$\leadsto$ EM Algorithm \pause 
\begin{itemize}
\invisible<1>{\item[1)] Initialize parameters $\boldsymbol{\Theta}^{t}$, $\boldsymbol{\pi}^{t}$} \pause 
\invisible<1-2>{\item[2)] \alert{Expectation step}: compute $p(\boldsymbol{\tau}_{i} | \boldsymbol{\Theta}^{t}, \boldsymbol{\pi}^{t}, \boldsymbol{X})\leadsto \boldsymbol{r}_{i}^{t}$  } \pause 
\invisible<1-3>{\item[3)] \alert{Maximization step}: maximize with respect to $\boldsymbol{\Theta}$ and $\boldsymbol{\pi}$:} \pause 
\begin{eqnarray}
\invisible<1-4>{\text{E}[\log \text{Complete data} | \boldsymbol{\theta}_{k}, \boldsymbol{\pi}] & = & \sum_{i=1}^{N}\sum_{k=1}^{K} \log p(\boldsymbol{x}_{i}, \tau_{ik}^{t} | \boldsymbol{\theta}_{k}, \pi_{k} ) p(\tau_{ik}^{t} | \boldsymbol{\Theta}, \pi_{k} )  \nonumber } \pause 
\end{eqnarray}
\invisible<1-5>{Obtain $\boldsymbol{\Theta}^{t+1}$, $\boldsymbol{\pi}^{t+1}$}\pause
\invisible<1-6>{\item[4)] Assess change} \pause 
\begin{eqnarray}
\invisible<1-7>{\text{Change} & =& \text{E}[\log \text{Complete data} | \boldsymbol{\Theta}^{t+1} , \boldsymbol{\pi}^{t+1} ] \nonumber \\
&&  - \text{E}[\log \text{Complete data} | \boldsymbol{\Theta}^{t}, \boldsymbol{\pi}^{t} ]\nonumber } \pause 
\end{eqnarray}
\end{itemize}

\invisible<1-8>{Our update steps will be strikingly similar to the K-Means algorithm} \pause

\end{frame}

\begin{frame}
\frametitle{Mixture of Unigram Models (Mixture of Multinomials)}
\begin{itemize}
\item[1)] Initialize parameters $\boldsymbol{\Theta}^{t}$ and $\boldsymbol{\pi}^{t}$  \pause \\
\invisible<1>{\item[2)] \alert{E-Step} } \pause 
\end{itemize}

\begin{eqnarray}
\invisible<1-2>{p(\tau_{ik} | \boldsymbol{\Theta}^{t}, \boldsymbol{\pi}^{t}, \boldsymbol{X}) }\pause \invisible<1-3>{ & =  & \overbrace{\frac{p(\tau_{ik} |\boldsymbol{\pi}^{t}) p(\boldsymbol{x}_{i} | \boldsymbol{\theta}_{k}^{t} )}{ \sum_{m=1}^{K} \left(p(\tau_{im} |\boldsymbol{\pi}^{t}) p(\boldsymbol{x}_{i} | \boldsymbol{\theta}_{m}^{t} ) \right) }}^{\text{general form}} \nonumber}\pause   \\
\invisible<1-4>{& = & \frac{ \pi_{k}^{t} \prod_{j=1}^{J} (\theta_{jk}^{t})^{x_{ij}}}{ \sum_{m=1}^{K} \left( \pi_{m}^{t} \prod_{j=1}^{J} (\theta_{jm}^{t})^{x_{ij}}\right) } \nonumber } \pause 
\end{eqnarray}

\invisible<1-5>{Define:} \pause \invisible<1-7>{Avoid underflow}
\begin{eqnarray}
\only<1-7>{\invisible<1-6>{r_{ik}^{t} &\equiv &  \frac{ \pi_{k}^{t} \prod_{j=1}^{J} (\theta_{jk}^{t})^{x_{ij}}}{ \sum_{m=1}^{K} \left( \pi_{m}^{t} \prod_{j=1}^{J} (\theta_{jm}^{t})^{x_{ij}}\right) } \nonumber } }
\only<8>{r_{ik}^{t} & = & \left[ 1 + \sum_{k^{'} \neq k} \frac{\pi_{k^{'}}\prod_{j=1}^{J} (\theta_{jk^{'}}^{t})^{x_{ij}}    }{\pi_{k} \prod_{j=1}^{J} (\theta_{jk}^{t})^{x_{ij}}}   \right]^{-1} \nonumber }
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Mixture of Unigram Models (Mixture of Multinomials)}

\begin{itemize}
\item[3)] \alert{M-Step}: \pause 
\end{itemize}

\begin{eqnarray}
\invisible<1>{\text{E}[\log \text{Complete data} | \boldsymbol{\theta}, \boldsymbol{\pi}] & = & \sum_{i=1}^{N} \sum_{k=1}^{K} E[\tau_{ik}] \log \left(\pi_{k}\prod_{j=1}^{J} \theta_{jk}^{x_{ik}} \right) \nonumber \\}\pause
\invisible<1-2>{& = & \sum_{i=1}^{N}\sum_{k=1}^{K} r_{ik}^{t} \log \pi_{k}  + \sum_{i=1}^{N}\sum_{k=1}^{K} \sum_{j=1}^{J} r_{ik}^{t} x_{ij}\log\theta_{jk} \nonumber  } \pause 
\end{eqnarray}

\invisible<1-3>{Introducing constraints, differentiating, setting equal to zero and algebra yields:} \pause 
\begin{eqnarray}
\invisible<1-4>{\pi^{t+1}_{k} & = & \frac{\sum_{i=1}^{N} r_{ik}^{t}}{N} \nonumber \\} \pause
\invisible<1-5>{\theta_{jk}^{t+1} & = & \frac{\sum_{i=1}^{N} r_{ik}^{t} x_{ij}}{ \sum_{m=1}^{J} \sum_{i=1}^{N} r_{ik}^{t} x_{im}   }}\pause \invisible<1-6>{ \propto \sum_{i=1}^{N} r_{ik}^{t} \boldsymbol{x}_{i} \nonumber } 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Example: Jeff Flake Again!}

{\tt To the R Code!}

\end{frame}

\begin{frame}
\frametitle{Fully Automated Clustering}

\pause 
\begin{itemize}
\invisible<1>{\item[-] Notion of similarity and ``good" partition$\leadsto$ clustering} 
\invisible<1-2>{\item[-] Many clustering methods:} 
\begin{itemize}
\invisible<1-3>{\item Spectral clustering}
\invisible<1-4>{\item Affinity Propagation}
\invisible<1-5>{\item Non-parametric statistical models}
\invisible<1-6>{\item Hierarchical clustering }
\invisible<1-7>{\item Biclustering}
\invisible<1-8>{\item ...}
\end{itemize}
\invisible<1-9>{\item[-] How do we know we have something useful?}
\begin{itemize}
\invisible<1-10>{\item Validation: read the documents}
\invisible<1-11>{\item Validation: experiments to assess cluster quality$\leadsto$ Thursday}
\invisible<1-12>{\item Validation: model based fit statistics}
\end{itemize}
\invisible<1-13>{\item[-] How do we know we have the ``right" model?}
\end{itemize}

\begin{huge}
\invisible<1-14>{\alert{YOU DON'T!}}\invisible<1-15>{$\leadsto$ And never will}\invisible<1-16>{$\leadsto$ but still useful(!!!!)}
\end{huge}

\pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause \pause

\end{frame}

\begin{frame}
\frametitle{Appendix: Why EM Works}

Goal: 
\begin{eqnarray}
\text{argmax}_{\boldsymbol{\theta}} p(\boldsymbol{X}| \boldsymbol{\theta} ) & = & \sum_{\boldsymbol{T}} p(\boldsymbol{X}, \boldsymbol{T}|\boldsymbol{\theta}) \nonumber 
\end{eqnarray}

Define: 
\begin{eqnarray}
\mathcal{L}(q, \boldsymbol{\theta}) & = & \sum_{\boldsymbol{T}} q(\boldsymbol{T}) \log \left[ \frac{ p(\boldsymbol{X}, \boldsymbol{T}| \boldsymbol{\theta}) }{q(\boldsymbol{T} )}   \right] \nonumber \\
K(q||p) & = & - \sum_{\boldsymbol{T}} q(\boldsymbol{T}) \log \left[ \frac{p(\boldsymbol{T}| \boldsymbol{X}, \boldsymbol{\theta}) }{q(\boldsymbol{T})}    \right] \nonumber 
\end{eqnarray}

Then: 
\begin{eqnarray}
\log p(\boldsymbol{X}| \boldsymbol{\theta}) & = & \mathcal{L}(q, \boldsymbol{\theta})  + K(q||p) \nonumber 
\end{eqnarray}

\end{frame}

\begin{frame}
\frametitle{Appendix: Why EM Works}

\begin{footnotesize}
\begin{eqnarray}
\log p(\boldsymbol{X}| \boldsymbol{\theta}) & = & \mathcal{L}(q, \boldsymbol{\theta})  + K(q||p) \nonumber \\
& = & \sum_{\boldsymbol{T}} q(\boldsymbol{T}) \log \left[ \frac{ p(\boldsymbol{X}, \boldsymbol{T}| \boldsymbol{\theta}) }{q(\boldsymbol{T} )}   \right] - \sum_{\boldsymbol{T}} q(\boldsymbol{T}) \log \left[ \frac{p(\boldsymbol{T}| \boldsymbol{X}, \boldsymbol{\theta}) }{q(\boldsymbol{T})}    \right] \nonumber \\
& =& \sum_{\boldsymbol{T} } q(\boldsymbol{T}) \log(p(\boldsymbol{X}|\boldsymbol{\theta}) ) + \sum_{\boldsymbol{T} } q(\boldsymbol{T}) \log (p(\boldsymbol{T}|\boldsymbol{X}, \boldsymbol{\theta}) )  \nonumber \\
&&  - \sum_{\boldsymbol{T}} q(\boldsymbol{T}) \log q(\boldsymbol{T}) - \sum_{\boldsymbol{T}} q(\boldsymbol{T}) \log p(\boldsymbol{T}|\boldsymbol{X}, \boldsymbol{\theta}) + \sum_{\boldsymbol{T}} q(\boldsymbol{T}) \log q(\boldsymbol{T}) \nonumber 
\end{eqnarray}
\end{footnotesize}

Collect terms that cancel and recognize $\sum_{\boldsymbol{T}} q(\boldsymbol{T}) = 1$ and we see equivalence

\end{frame}

\begin{frame}
\frametitle{Appendix: Why EM Works}

$K(q||p)\geq0$ with $K(q||p) = 0$ only if $q = p$.  So, $\mathcal{L}(q, \boldsymbol{\theta})$ is a lower-bound on the log-likelihood.  \\
E-step
\begin{eqnarray}
\log p(\boldsymbol{X}|\boldsymbol{\theta}) - K(q||p) & = & \mathcal{L}(q, \boldsymbol{\theta}) \nonumber 
\end{eqnarray}

$\mathcal{L}(q, \boldsymbol{\theta})\leadsto$ biggest when $K(q||p) = 0$, so set 
\begin{eqnarray}
q(\boldsymbol{T}) & = & p(\boldsymbol{T}| \boldsymbol{X}, \boldsymbol{\theta}) \nonumber 
\end{eqnarray}

M-step:\\
Given the new value of $q$, maximize parameters (expectation of the log complete data likelihood)\\
Change in log-likelihood will be greater$\leadsto$ because new maximum induces non-zero KL-divergence.  Changes in log-likelihood are greater than changes in lower bound.

\end{frame}

\end{document}

### 2017-12-10 resources/text_as_data/Class15Code.R

@@ -1,0 +1,31 @@
+##LASSO example (ridge is straightforward in this setting too)
+
+
+load('/Users/justingrimmer/dropbox/teaching/text/tad14/class15/LASSO.RData')
+
+library(glmnet)
+##x is the dtm 
+x<- LASSO.list[[1]]
+
+##y are dichotomous indicators of credit claiming or not
+y<- LASSO.list[[2]]
+
+
+
+y.train<- y[1:697]
+x.train<- x[1:697,]
+
+y.valid<- y[-c(1:697)]
+x.valid<- x[-c(1:697),]
+
+
+
+##cv.glmnet uses a ``cross validation" method to determine a key parameter in LASSO, I strongly recommend using it
+##alpha = 1 is the LASSO
+##alpha = 0 is Ridge
+train.model <- cv.glmnet(x = x.train, y = y.train, alpha = 1, nfolds=5, family="binomial", type.measure="mse")
+
+predict.new<- predict(train.model, newx = x.valid, s = train.model$lambda.min)
+
+predict.probs<- 1/(1 + exp(-predict.new))
+final.pred<- ifelse(predict.probs>0.46, 1, 0) ## we determined this threshold via validation

### 2017-12-10 resources/text_as_data/Code_tc4.py

@@ -1,0 +1,72 @@
+##########################
+###
+###
+###  4th lecture code, Text as Data
+###
+###
+###
+##########################
+
+
+import re, os
+from urllib import urlopen
+from BeautifulSoup import BeautifulSoup
+
+out = open('/users/justingrimmer/Dropbox/HouseData/NewListPress.csv', 'r')
+
+press = out.readlines()
+
+
+pos_words = urlopen('http://www.unc.edu/~ncaren/haphazard/positive.txt').read().split('\n')
+neg_words = urlopen('http://www.unc.edu/~ncaren/haphazard/negative.txt').read().split('\n')
+
+from nltk import PorterStemmer
+from nltk import word_tokenize
+st = PorterStemmer()
+
+
+
+pos_stem = map(st.stem, pos_words)
+neg_stem = map(st.stem, neg_words)
+
+
+
+stop_words = urlopen('http://jmlr.org/papers/volume5/lewis04a/a11-smart-stop-list/english.stop').read().split('\n')
+
+stop_stemmed = map(st.stem, stop_words)
+
+pos_stem = [x for x in pos_stem if x not in stop_stemmed]
+neg_stem = [x for x in neg_stem if x not in stop_stemmed]
+
+
+##now going through a big collection of press releases
+
+output = open('/users/justingrimmer/dropbox/teaching/text/tad14/class4/ScorePress.csv', 'w')
+
+output.write('Document,Num_Words,Pos_Words,Neg_Words')
+output.write('\n')
+
+for z in range(1, len(press)):
+	temp = press[z].strip('\n').split(',')[-1]
+	start = open(temp, 'r').read()
+	start2 = start.lower()
+	start3 = re.sub('\W', ' ', start2)
+	start4 = word_tokenize(start3)
+	start5 = map(pt.stem, start4)
+	num_words = len([x for x in start5 if x not in stop_stemmed])
+	pos_words = len([x for x in start5 if x in pos_stem])
+	neg_words = len([x for x in start5 if x in neg_stem])
+	part = str(z) + str(num_words) + ',' + str(pos_words) +',' + str(neg_words) 
+	output.write(part)
+	output.write('\n')
+	if z %100 == 0:
+		print z
+
+
+output.close()
+
+##this creates the figures, we can then use the output.  
+
+
+
+

### 2017-12-10 resources/text_as_data/Examp_tc11.R

@@ -1,0 +1,48 @@
+###loading the mallet objects
+##topics are indexed 
+
+
+
+mallet.topics<- function(file, num_topics){
+	start<- read.delim(file, header=F, sep =' ', row.names=NULL)
+	start<- start[-1,]
+	store.props<- matrix(NA, nrow=nrow(start), ncol=num_topics)
+	seq1<- seq(3, 2*num_topics + 2, by = 2)
+	seq2<- seq(4, 2*num_topics + 2, by = 2)
+	for(z in 1:nrow(start)){
+		for(k in 1:num_topics){
+			store.props[z,as.numeric(as.character(start[z,seq1[k]])) +1]<- as.numeric(as.character(start[z, seq2[k]]))
+			}
+		}
+	
+	rownames(store.props)<- as.character(start[,2])
+	return(store.props)
+	}	
+		
+
+flake_tops<- mallet.topics('/users/justingrimmer/dropbox/teaching/text/tad14/class11/FlakeExample_Topics', 3)
+
+##now extracting the keys
+
+mallet.keys<- function(file, num_topics){
+	start<- read.delim(file, header=F, sep=' ', row.names=NULL)
+	keys<- matrix(NA, nrow=num_topics, ncol=10)
+	props<- c()
+	for(z in 1:num_topics){
+		ff<- strsplit(as.character(start[z,1]), split='\t')
+		props[z]<- as.character(ff[[1]][2])
+		keys[z,1]<- as.character(ff[[1]][3])
+		for(g in 2:10){
+		keys[z,g]<- as.character(start[z,g])
+	}
+	}
+	keys_prop<- cbind(props, keys)
+	return(keys_prop)
+	}
+
+flake_keys<- mallet.keys('/users/justingrimmer/dropbox/teaching/text/tad14/class11/FlakeExample_keys', 3)
+
+
+flake_tops_20<- mallet.topics('/users/justingrimmer/dropbox/teaching/text/tad14/class11/FlakeExample_Topics_20', 20)
+flake_keys_20<- mallet.keys('/users/justingrimmer/dropbox/teaching/text/tad14/class11/FlakeExample_keys_20', 20)
+

### 2017-12-10 resources/text_as_data/HW1_key.py

@@ -1,0 +1,9 @@
+import os
+
+os.chdir("/Users/franceszlotnick/Dropbox/TextAsData/ProblemSets/PS1/")
+
+with open("hw1.txt", "w") as f:
+	f.write("hello world" + "\n")
+
+	for i in range(1, 101):
+		f.write(str(i) + "\n")

### 2017-12-10 resources/text_as_data/examp_c9.R

@@ -1,0 +1,147 @@
+######putting together some example R code
+
+load('~/dropbox/teaching/text/tad14/class9/FlakeMatrix.RData')
+
+##that loads flake_matrix
+
+extra_stop<- c('rep', 'jeff', 'flake', '2022252635', 'matthew', 'jagirdar', 'email', 'byline','specht', 'sarabjit', 'dateline') 
+
+flake_matrix<- flake_matrix[-c(603, 604),-which(colnames(flake_matrix)%in% extra_stop)]
+
+
+?kmeans
+
+flake_norm<- flake_matrix
+for(z in 1:nrow(flake_norm)){
+	flake_norm[z,]<- flake_norm[z,]/sum(flake_norm[z,])
+	}
+	
+
+n.clust<- 3
+set.seed(8675309) ##complicated objective function
+k_cluster<- kmeans(flake_norm, centers = n.clust)
+table(k_cluster$cluster)
+
+##labeling the topics
+##just use the ``biggest" in each category
+key_words<- matrix(NA, nrow=n.clust, ncol=10)
+for(z in 1:n.clust){
+	key_words[z,]<- colnames(flake_matrix)[order(k_cluster$center[z,], decreasing=T)[1:10]]
+	}
+
+##we can then try to compare the ``relative" strong words
+
+key_words2<- matrix(NA, nrow=n.clust, ncol=10)
+for(z in 1:n.clust){
+	diff<- k_cluster$center[z,] - apply(k_cluster$center[-z, ], 2, mean)
+	key_words2[z,]<- colnames(flake_matrix)[order(diff, decreasing=T)[1:10]]
+	}
+
+
+setwd('/Users/justingrimmer/dropbox/HousePress/JEFF_FLAKE_20100')
+file.show(rownames(flake_matrix)[which(k_cluster$cluster==2)[11]])
+file.show(rownames(flake_matrix)[which(k_cluster$cluster==2)[20]])
+cluster2<- which(k_cluster$cluster==2)
+for(z in 1:len(cluster2)){
+	file.show(rownames(flake_matrix)[which(k_cluster$cluster==2)[z]])
+	readline('wait')
+	}
+	
+
+
+#################
+#################
+##Code for the Mixture of Multinomials
+
+mix_mult<- function(X, k, tol, seed){
+	library(MCMCpack)
+	
+	
+	##initializing parameters
[…]

### 2017-12-10 resources/text_as_data/examp_tc3.py

@@ -1,0 +1,167 @@
+##putting together an example for the preprocessing steps
+
+from BeautifulSoup import BeautifulSoup
+from urllib import urlopen
+import re, os
+
+url  = urlopen('http://avalon.law.yale.edu/19th_century/gettyb.asp').read()
+
+
+soup = BeautifulSoup(url)
+
+
+text = soup.p.contents[0]
+
+
+text_1 = text.lower()
+
+
+text_2 = re.sub('\W', ' ', text_1)
+
+
+
+from nltk import word_tokenize
+from nltk import bigrams
+from nltk import trigrams
+
+text_3 = word_tokenize(text_2)
+
+text_3_bi = bigrams(text_3)
+text_3_tri = trigrams(text_3)
+text_3_n = ngrams(text_3, 4)
+
+
+
+stop_words = urlopen('http://jmlr.org/papers/volume5/lewis04a/a11-smart-stop-list/english.stop').read().split('\n')
+
+##we can then identify the stop words and then eliminate them from the list
+
+##this is code that executes a very simple for loop to check the list
+text_4 = [x for x in text_3 if x not in stop_words]
+
+##you can check what was removed with:
+
+text_rem = [x for x in text_3 if x not in text_4]
+
+##we're going to use a similar format to apply various stemming/lemmatizing/synonyms algorithms
+
+
+from nltk.stem.lancaster import LancasterStemmer
+
+st = LancasterStemmer()
+
+
+
+from nltk.stem import PorterStemmer
+
+pt = PorterStemmer()
+
+
+from nltk.stem.snowball import EnglishStemmer
+
+sb = EnglishStemmer()
+
+
+from nltk.stem.wordnet import WordNetLemmatizer
+
+wn = WordNetLemmatizer()
+
+
+##let's examine the word ``better"
+st.stem('better')
+pt.stem('better')
+sb.stem('better')
+
+wn.lemmatize('better', 'a')
+
+##
+##applying the porter stemmer to the gettysburg address
+
+
+text_5 = map(pt.stem, text_4)
+
+##now creating a dictionary that will count the occurrence of the words
+
+getty = {}
+used = []
+for word in text_5:
+	if word in getty:
+		getty[word] += 1 
+	if word not in getty and word not in used:
+		getty[word] = 1
+		used.append(word)
+
[…]

### 2017-12-10 resources/text_as_data/probit.R

@@ -1,0 +1,60 @@
+##this implements code for lecture 2, particularly the probit model
+##generating synthetic data 
+
+
+
+true.beta<- c(-0.75, 1)
+xs<- cbind(1, rnorm(1000))
+y.star<- xs%*%true.beta
+y.obs<- c()
+for(z in 1:1000){
+  y.obs[z]<- rbinom(1, prob = pnorm(y.star[z]), size = 1)
+  
+}
+
+####writing the probit function
+
+
+
+
+log.prob<- function(pars, X, Y){
+  beta<- pars[1:ncol(X)]
+  probs<- pnorm(X%*%beta)
+  part1<- Y*log(probs)
+  part2<- (1-Y)*log( 1- probs) 
+  total<- sum(part1,  part2)
+  return(total)
+}
+
+max.output<- optim(c(0, 0), log.prob, control = list(trace = 100, fnscale = -1 ), method = 'BFGS', hessian=T, X = xs, Y = y.obs)
+par.est<- max.output$par
+sqrt(diag(solve(-max.output$hessian)))
+
+glm.output<- glm(y.obs~xs[,-1], family=binomial(link = 'probit'))
+sqrt(diag(vcov(glm.output)))
+
+##probability of observing an event, given xs = c(1, 0.5)
+
+new.xs<- seq(-2, 2, len = 1000)
+probs<- c()
+for(z in 1:1000){
+  probs[z]<- pnorm(c(1, new.xs[z] )%*%par.est)
+}
+
+plot(probs~new.xs, xlab = 'Ideology', ylab = 'Probability', type='l', lwd = 4)
+
+
+
+
+  
+  
+  
+  
+  
+
+
+
+
+
+
+

### 2019-03-24 paper_notes.tex
Normal update

@@
 \usepackage[utf8]{inputenc}
-\usepackage{indentfirst}	% make indent in first paragraph
+
+\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,pdflscape,subfigure,array,hyperref}
+
+% \usepackage{indentfirst}	% make indent in first paragraph
+\setlength\parindent{0pt}
+\setlength{\parskip}{1em}
+\renewcommand{\baselinestretch}{1.5}
+
 \usepackage{bm}
@@
 \usepackage{mathrsfs}
-\usepackage{amssymb}
 \usepackage{hyperref}
@@
 \usepackage{natbib}			% to insert citations
-\usepackage{xcolor}			% extend the colors can be used
+\usepackage[table,xcdraw]{xcolor}			% extend the colors can be used
 \usepackage{calrsfs}		% caligraphy font family
@@
 \usepackage{bibentry}		% package used to insert full citation in body text
+
 \makeatletter 
@@
 \usepackage[english]{babel}
-\renewcommand{\baselinestretch}{1.5}
 
@@
 
+\newcommand{\red}[1]{{\color{red} #1}}
+\newcommand{\blue}[1]{{\color{blue} #1}}
+\newcommand{\mytitle}[1]{{\large{\textbf{#1}}}}
+\newcommand{\mysubtitle}[1]{{\normalsize{\textbf{#1}}}}
+
 \usepackage{amsmath}
 \DeclareMathOperator*{\argmin}{arg\,min}
+
+% \usepackage{graphicx}
+% \usepackage[table,xcdraw]{xcolor}
 
@@
 
-\part{Economics}
-\label{part:economics}
-
-\chapter{Econometrics}
-\label{cha:econometrics}
-
-\section{Low and Meghir, 2017, JEP} % (fold)
-\label{sec:low_and_meghir_jep_2017}
-
-\textbf{\bibentry{Low:2017jb}}\\
-
-\textbf{Defining a structural model:}
-
-A \textbf{fully specified model} make explicit assumptions about the economic actors' objectives and their economic enviroment and information set, as well as specifying which choices are being made within the model.
-They allow a complete solution to the individual's optimization problem as a function of current information set.
-Fully specified models are particularly useful in understanding mechanism of a policy, especially when we want to estimate some long-term effects of the policy.
-
-A \textbf{partially specified model} relies on a sufficient statistic that summarizes choices not being modeled specifically.
-For example, assuming that the choices is only intratemporal instead of intertemporal.
-
-\textbf{Treatment effect models} focus on identifying a specific causal effect of a policy while saying least about the theoretical environment.
-The pro is the cleaness of causality.
-The con is the limitation in exploiting the results outside.
-The identification of treatment model depends on assumptions that the experienment has not been compromised and there is no spillovers from the treatment units.
-
-A combination of fully speficied model and randomized experiments can enhance anaysis for both.
-Experimental evidence can be used either to validate a structural model, or to aid in the estimation process (in identification).
-
-\textbf{Solving structural models}
-
-This has been described in Adda and Cooper(2003) well. 
-The general process is: 
-1) write down the bellmand function;
-2) discrete the state space and decision space;
-3) use value function iteration to solve the bellman function.
-
-% section low_and_meghir_jep_2017 (end)
+\part{Econometrics}
+\label{part:econometrics}
+
+\chapter{Common Tools} % (fold)
+\label{cha:common_tools}
+
+\noindent
+\textbf{Seemingly Unrelated Regressions:}
+\footnote{see Pinkse notes.}
+\begin{itemize}
+	\item $y_i=X_i^T\theta_0+u_i$, where $X_i$ is $k$ by 1.
+	\item $\hat \theta=(\sum_{i=1}^n{X_i\hat\Psi^{-1} X_i^T})^{-1}
+	\sum_{i=1}^n{X_i\hat\Psi^{-1} y_i}$
+	\item This estimator is more efficient than OLS.
+And it only requires the estimation of unconditional variance of error term, while WLS requires the whole distribution of error term conditional on $X_i$.
+So will also be more efficient than WLS in practice.
+	\item Intuitively, it uses the correlation information of error terms across equations.
+	\item Notice, more applicable when $k$ is not very large (relative to $n$). Otherwise the estimation of $\hat \Psi$ will be too demanding.
+\end{itemize}
+
+\chapter{Identification} % (fold)
+\label{cha:identification}
+
+% chapter identification (end)
+
+\section{Identification in Multi-Equilibria} % (fold)
+\label{sec:identification_in_multi_equilibria}
+
+\begin{itemize}
+	\item Find some feature that is common to all equilibria. For example, \cite{Berry:1992gl}
+
+	\item Set identification. For example, \cite{Shum:2018hw}
+\end{itemize}
+
+% section identification_in_multi_equilibria (end)
 
@@
 
+\section{Low and Meghir, 2017, JEP} % (fold)
+\label{sec:low_and_meghir_jep_2017}
+
+\textbf{\bibentry{Low:2017jb}}\\
+
+\textbf{Defining a structural model:}
+
+A \textbf{fully specified model} make explicit assumptions about the economic actors' objectives and their economic enviroment and information set, as well as specifying which choices are being made within the model.
+They allow a complete solution to the individual's optimization problem as a function of current information set.
+Fully specified models are particularly useful in understanding mechanism of a policy, especially when we want to estimate some long-term effects of the policy.
+
+A \textbf{partially specified model} relies on a sufficient statistic that summarizes choices not being modeled specifically.
+For example, assuming that the choices is only intratemporal instead of intertemporal.
+
+\textbf{Treatment effect models} focus on identifying a specific causal effect of a policy while saying least about the theoretical environment.
+The pro is the cleaness of causality.
+The con is the limitation in exploiting the results outside.
+The identification of treatment model depends on assumptions that the experienment has not been compromised and there is no spillovers from the treatment units.
+
+A combination of fully speficied model and randomized experiments can enhance anaysis for both.
+Experimental evidence can be used either to validate a structural model, or to aid in the estimation process (in identification).
+
+\textbf{Solving structural models}
+
+This has been described in Adda and Cooper(2003) well. 
+The general process is: 
+1) write down the bellmand function;
+2) discrete the state space and decision space;
+3) use value function iteration to solve the bellman function.
+
+% section low_and_meghir_jep_2017 (end)
+
+\chapter{Moment Inequality} % (fold)
+\label{cha:moment_inequality}
+
+\section{PPHI, 15 EMCA} % (fold)
+\label{sec:pphi_15_emca}
+
+% section pphi_15_emca (end)
+
+% chapter moment_inequality (end)
+
 % subsection point_identification (end)
@@
 % section lewbel_2016_jel (end)
+
+\chapter{Others} % (fold)
+\label{cha:others}
+
+% chapter others (end)
 
@@
 
+\section{Gillen-Montero-Moon-Shum, 18 MP} % (fold)
+\label{sec:gillen_montero_moon_shum_18mp}
+
+\noindent
+\textbf{\bibentry{Gillen:2018bg}}
+
+This paper uses LASSO to pick instruments for BLP style model. They apply it in Mexico voting model.
+
+\vspace{1em}
+\noindent
+\textbf{Applications:}
+\begin{itemize}
+	\item Maybe in education choice
+\end{itemize}
+
+% section gillen_montero_moon_shum_18mp (end)
+
 \section{Seminar Notes} % (fold)
@@
 
+\myline
+
+\textcolor{red}{Is there any cases where only structural estimation can work, while reduced estimation, no matter how frequently A/B test, can not work?}
+
+\myline
+
+Lixiong Li in IO brownbag introduces a way for identification where there is moment restrictions.
+The idea is to replace the specific distribution assumptions of the error term by some moment restrictions.
+By this, we can not have point identification in many cases, but can get set identification even with very weak conditions.
+
+\textcolor{blue}{I think it a good paper.}
+
 % section seminar_notes (end)
@@
 
-\chapter{IO} % (fold)
-\label{cha:io}
-
-\section{Data and Techniques} % (fold)
-\label{sec:data_and_techniques}
-
-\subsection{Data Source} % (fold)
-\label{sub:data_source}
+\part{IO} % (fold)
+\label{part:io}
+
+\chapter{Data and Techniques} % (fold)
+\label{cha:data_and_techniques}
+
+\section{Data Source} % (fold)
+\label{sec:data_source}
 
@@
 
+\noindent
+\textbf{Nielson Consumer Panel Dataset}
+\begin{itemize}
+	\item Penn State has institutional access
+\end{itemize}
+
+\noindent
+\textbf{ISMS Durable Goods Dataset 1}
+\begin{itemize}
+	\item \bibentry{Ni:2012in}
+\end{itemize}
+
+\noindent
+\textbf{Bureau of Transportation Statistics}
+\begin{itemize}
+	\item \url{https://www.transtats.bts.gov}
+\end{itemize}
+
+\noindent
+\textbf{Airbnb data}
+\begin{itemize}
+	\item Penn State Department of Real Estate \textcolor{red}{(?) how to get it}
+\end{itemize}
+
 % subsection data_source (end)
 
-\subsection{Techniques} % (fold)
+\section{Timber Data by Forest Service} % (fold)
+\label{sec:timber_data}
+
+\noindent
+\textbf{Timber Industry:}
+\begin{itemize}
+	\item Dropping off timber, then process timber to log, then process log to lumber by mill
+	\begin{itemize}
+		\item Loggers do not possess mill machines, so they will sell the dropping timber to mills.
+At the same time since there are many different kinds of logs (e.g.
+in diameters), one specific mill may lack the machine for some logs and will resell them in the market.
+So the resale market after timber auction is frequent.
+This create a pro-collusion environment.
+	\end{itemize}
+
+	\item Timber tracts are very different from one to another.
+For older timber tracts, the values of bidders are more heterogeneous.
+For young or second-grow timber tracts, the value is easier to estimate and we can think it more like common value auction.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Databook:}
+\begin{itemize}
+	\item BDA: number of bidders bid excess reserve price. In sealed auction, must bid larger than reserve price. In ascending auction, must actively bid at least once in auction.
+
+	BDT: number of bidders actually show up in an auction.
+	\begin{itemize}
+		\item e.g. BDA 0, BDT 1: 1 show up, bid lower than reserve price. Notice that BDA=1 does not mean the auction is not successful.
+
+		\begin{itemize}
+			\item See 884F060103002, where BDA=0, BDT=1, the bidding value is the same as advalue, but the status (stt) is 1.
+		\end{itemize}
+		\item e.g. BDA 3, BDT 6: the price might increase too fast, the remaining 3 don't have a chance to bid.
+	\end{itemize}
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Research Questions:}
+\begin{itemize}
+	\item \cite{Athey:2011cs} shows that small bidders (loggers) pay higher in sealed auction. Why they do not move to the ascending auction in this case? Why the arbitrage does not work here?
+	\begin{itemize}
+		\item Maybe it's easier to collude in ascending auction than in sealed auction.
+Then independent bidders will prefer to stay at sealed bid auction even the realized price is higher.
+Because if they move to ascending auction, then they are likely not to win.
+	\end{itemize}
+
+	\item What if the reserve price is strategically picked by the auctioneer?
+
+	\item Timber auction is multidimensional.
+Each tract have different species, and each firm will have different values over this species.
+Can we use the Nima's optimal multidimensional mechanism design to verify the data?
+
+	\item \textcolor{blue}{Timber firms may have special interest in some species, so they may want to participate in specific auctions. And thus the private value assumption does not hold.}
+	\begin{itemize}
+		\item Bob: Firms have strong incentive to collude in this case.
+Firm A prefer species a, firm B prefers species b.
+Such preference may derive from their specialization in processing, and is commonly known among bidders.
+Then in an auction where there are 80\% specie a and 20\% specie b, it is very likely that firm A will win and sell species b to firm B after auction.
+
+		\item Then they are very likely to be engaged in an collusion.
+How can we distinguish it from the pure collusion based rotation mechanism, where firm A will attend in some auctions more frequently while B will attend others?
+	\end{itemize}
+\end{itemize}
+
+\section{FCC data} % (fold)
+\label{sec:fcc_data}
+
+\noindent
+\textbf{Related Literature:}
+\begin{itemize}
+	\item \cite{McMillan:1994bc}
+
+	\item \cite{Cramton2000} clarifies many terms in a narrative way.
+
+	\item \cite{Weber:1997ce} introduces \textit{strategic demand reduction} in simultaneous ascending bidding auctions.
+	\begin{itemize}
+		\item e.g.
+Two firms, three objects.
+Each firm either any one object 100, and any combination 200.
+Then if one firm take the strategy that keep bidding on two objects until some of which exceeds 100.
+Then the other firm will find it optimal to bid at the other object.
+The auction will end at a very low bid for all three objects.
+	\end{itemize}
+
+	\item \cite{Krishna:1996fo} discusses payoff complementarity in ascending bidding auction. Their model is based on second price sealed auction.
+
+\end{itemize}
+
+% subsection fcc_data (end)
+
+% subsection timber_data (end)
+
+\section{Techniques} % (fold)
 \label{sub:techniques}
@@
 \noindent
+\textbf{Google Street View Data:}
+\begin{itemize}
+	\item \cite{Gebru:2017wk} uses Google Street View data to collect automobile information, and use machine learning to predict socioeconomic conditions of different cities.
+\end{itemize}
+
+\myline
+
+\noindent
 \textbf{Paralelle Computation:}
@@
 
-% section data_and_techniques (end)
-
-\section{Rey and Stiglitz, 1995, RAND} % (fold)
-\label{sec:rey_and_stiglitz_1995_rand}
+\chapter{Cartels and Collusion} % (fold)
+\label{sec:cartels_and_collusion}
+
+A very good narrative of cartel and bidding rings is from \textit{Economics of Collusion} by Marshall and Marx.
+I will briefly summarize.
+
+\begin{itemize}
+	\item A cartel in most cases will need explicit agreement instead of just tacit collusion.
+	\item They will hire a consulting firm to negotiate the meeting and to keep track of all records.
+	\item They will fix a market share instead of just prices, and use `true-up' to redistribute as agreed at the end of the period.
+	\item They will also change the incentive of the sales team to avoid over selling.
+\end{itemize}
+
+A bidding ring is a group of bidders where they will not compete within the group. 
+There are two benefits.
+First, competition is directly lowered and price would be lower for bidders.
+Second, by reduce bidding within the group they will not leak information to other less informed bidders, and reduce competition indirectly.
+
+\myline
+
+\noindent
+\textbf{Measure of Concentrations:}
+\begin{itemize}
+	\item Herfindal Index: 
+\end{itemize}
+
+\section{Green and Porter, 84 EMCA} % (fold)
+\label{sec:green_and_porter_84_emca}
+
+\textbf{\bibentry{Green_Porter:1984EMCA}}
+
+\cite{Green_Porter:1984EMCA} points out that \textbf{price war can be a part of collusion equilibrium}, challenging the view that price war being a signal of competition.
+The key point is that there is \textbf{uncertainty in demand}, which is after the decision of firm's quantity decision.
+So firms are unable to distinguish between a low demand shock and someone's possible deviating.
+
+They show that the equilibrium strategy is a \textbf{\textcolor{blue}{trigger strategy with forgiveness}}.
+For realized price $p$ higher than some threshold $\bar p$,
+firms choose the cooperative quantity;
+otherwise they will choose the Cournot quantity for T periods, where the punish time is given (maybe by explicit negotiation process).
+
+The dynamic incentive is very interesting here.
+In equilibrium, no firms will have incentive to deviate. 
+So the only possibility for a low price is a bad demand shock.
+Despite everyone knowing this, they will still choose the Cournot quantity for $T$ periods as a punishment.
+This is to give correct dynamic incentive.
+Suppose a strategy profile features no punishment even in low price.
+Then firms would have incentive to output more since they would not be punished anyway.
+
+\begin{mdframed}[style=comment]
+\noindent
+\textbf{Learning Process:}
+
+One thing I feel uncomfortable is the information structure of the firm. 
+In this paper, firms are assumed to know the realization of price, the distribution of shocks $\theta$, and the function form of price $p()$.
+
+If they do not know the distribution, not do they know the functional form.
+Then it would be impossible for them to distinguish the volatility in $\theta$ and in quantity.
+Thus it would be impossible to detect probable deviation.
+\footnote{In the paper, we can detect deviation at some probability. But even this cannot be satisfied because the distribution is unknown and relative parameters are unidentified.}
+\end{mdframed}
+
+\textbf{Identification:} in appendix they show that in principle the collusion behavior can be identified.
+But in practice it is generally quite difficult.
+
+% subsection green_and_porter_84_emca (end)
+
+\section{Rotemberg-Saloner, 86 AER} % (fold)
+\label{sec:rotemberg_saloner_86_aer}
+
+\textbf{\bibentry{RotembergSaloner:86aer}}
+\vspace{1em}
+
+\cite{RotembergSaloner:86aer} also tries to explain price war, but they show that \textbf{price wars are more likely to happen during the demand boom instead of doom.}
+In their model, firms make decisions \textit{after} realization of shocks.
+So firms can distinguish between the price drop by deviation and price drop by low demand.
+Then their result is quite intuitive.
+It is more profitable to deviate when demand is high.
+So the collusive price at high demand should be lower, the lower is collusive price, the less attractive to deviate.
+
+\vspace{1em}
+\noindent
+\textit{Comments:}
+\begin{itemize}
+	\item With more specific assumption on knowledge of firm, they can say more about the competition structure.
+	In \cite{Green_Porter:1984EMCA}, the only reasonable competition mode is Cournot.
+	But both Bertrand and Cournot are appropriate in this paper.
+	\item The establishment of price competition equilibrium is skillful.
+	They first assume a exogenous punishment to generate optimal decision, then use such decision to generate an actual punishment.
+	This constitutes a fixed point argument.
+	\footnote{Same trick as in \cite{Peters_Siow:2002dx} small market case.}
+
+	\item This model is `\textit{really about countercyclical pricing---firms have perfect information and adjust prices smoothly in response to demand conditions.}'(by \cite{Ellison:94RAND} p.38).
+	There is no \textit{regime shift} like in \cite{Green_Porter:1984EMCA} since the past has no uncertainty.
+	\begin{itemize}
+		\item It is not important whether the future has uncertainty.
+Say, the demand is seasonal and is certain.
+It won't change the result, the pricing will still be countercyclical.
+Intuitively, what the firms compare is the current deviation profit and expected future gain, thus future uncertainty is not important (as long as firms are risk neutral).
+	\end{itemize}
+\end{itemize}
+
+\section{Porter, 83 Bell} % (fold)
+\label{sec:porter_83_bell}
+
+\textbf{\bibentry{Porter:83bell}}
+
+\cite{Porter:83bell} is specifically to test \cite{Green_Porter:1984EMCA} using JEC data.
+\footnote{Joint Executive Committee, which is widely used since it records the cartel in 1880-1886 for the train industry in US.}
+
+\vspace{2mm}
+\noindent
+\textbf{Estimation Strategy:}
+\vspace{-0.5em}
+\begin{itemize}
+	\item \textbf{Goal} is to test whether regime switch happens in supply side, and to identify when such switches happen.
+	This paper does not test whether firms actually play the equilibrium as described by \cite{Green_Porter:1984EMCA}, but only describes the reversion pattern.
+	\item \textbf{Data} is aggregate time series price and quantity.
+	\begin{itemize}
+		\item KZ: notice there is some internal inconsistency in this setting.
+Porter assumes 1) no secret deviation, without giving justification; 2) homogeneous good, which is largely due to data limitation; and 3) firms do price competition.
+But then we should see prices near marginal cost, which should not fluctuate a lot.
+	\end{itemize}
+
+	\item \textbf{Firm Strategy:} The firms in JEC actually use price instead of quantity as strategic variable, and they use differentiated products (through different service).
+This is different from \cite{Green_Porter:1984EMCA} model.
+	\begin{itemize}
+		\item But in econometrics model part, this paper seems to still assume the quantity competition. This may due to the data limitation --- they only have aggregated price and quantity.
+		\item Firm's decision problem is summarized by 
+		\[p_t(1+\theta_{it}/\alpha_t)=MC_i(q_{it})\]
+		Porter notes that this form can encompass Bertrand competition, Cournot competition and perfect collusion, with $\theta_{it}$ being 0, $(0,1)$, 1 respectively.
+		\textcolor{red}{This seems reasonable, what I don't understand is how it can be compatible with Green-Porter's model?
+In their model it is obvious that Cournot is the only possible way of competition.}
+
+		\begin{mdframed}[style=comment]
+			This form can be derived from firm profit maximization. Suppose \[\pi_i(q_i,q_{-i}) =p(q_1,\dots,q_n)q_i-C(q_i) \]
+			by taking derivative w.r.t. $q_i$ we will get:
+			\[p(1+\frac{1}{\varepsilon_{q_i,p}})=MC(q_i)\]
+			Also notice that this can actually encompass both Cournot and Bertrand.
+In Cournot, we have $p(q_1,\dots,q_n)=p(\sum_{i=1}^nq_i)$; and in Bertrand we have $p(q_1,\dots,q_n) = p(\sum q'|q' \in \max\{q_1,\dots,q_n\},0=q_i\notin q')$
+
+		\end{mdframed}
+		\item In firm optimization problem, there is no uncertainty.
+But in turning it to reduced form, the paper has to add error term $U_{2t}$ to match the data.
+In adding this term, we implicitly assume 1) firms do not know this shock when making decision; 2) this shock is aggregate for all firms (?).
+	\end{itemize}
+	\item \textbf{Estimation:}
+	\begin{itemize}
+		\item Demand Curve:
+		\item Supply Curve:
+		\item Simultaneous Equation System:
+		\item Conditional pdf:
+		\item Unconditional pdf:
+		\item Convergence algorithm:
+	\end{itemize}
+\end{itemize}
+
+% subsection porter_83_bell (end)
+
+% subsection rotemberg_saloner_86_aer (end)
+
+\section{Genesove-Mullin, 01 AER} % (fold)
+\label{sec:genesove_mullin_01_aer}
+
+\textbf{\bibentry{Genesove:2001jz}}
+
+\cite{Genesove:2001jz} narratively describes how the sugar cartel in 1930-1936 actually works.
+They find cartel's action deviates from what collusion theory predicted.
+The main idea they try to convey is: \textbf{collusion is more a contraction problem than a market structure problem}.
+
+Questions they want to answer:
+\begin{itemize}
+	\item How firms coordinate their pricing?
+	\begin{itemize}
+		\item Mainly through rules, and by ordinary meetings to adjust to rules. Such meetings are necessary due to the uncertain nature of competition environment.
+	\end{itemize}
+	\item How prevalent is cheating? What's the punishment?
+	\begin{itemize}
+		\item Cheating is not discussed in neither \cite{Green_Porter:1984EMCA} nor \cite{RotembergSaloner:86aer}.
+There the price war is just an equilibrium result, and no one has incentive to `secretly cheat'.
+		\item But in reality cheat actually happens.
+Because contract is always incomplete and firms have many tricks to escape.
+But retaliation does not always happen.
+They will first make some effort to partially identify a cheat and a bad draw, e.g.
+by asking the suspect to show some hard evidence.
+When the cartel is convinced that someone has cheated, they are mostly likely to take tit-for-tat strategy instead of trigger.
+	\end{itemize}
+\end{itemize}
+
+Below are notes taken during the reading.
+
+\begin{itemize}
+	\item Cartel mainly collude through rules.
+	\begin{itemize}
+		\item Open prices and publicly announced items
+		\item Prior notification
+		\begin{itemize}
+			\item Complementary to open announcement. Ensure that firms can potentially retaliate before consumers react.
+		\end{itemize}
+		\item Restrictions on contractual practices between the refiners and downstream firms
+		\begin{itemize}
+			\item Mainly to eliminate discriminatory pricing
+			\item Very detailed and standardized.
+Because `every contractual term can mask a price cut'.
+The standardized model is implicitly assumed in Green-Porter, though homogeneous good and the extremely simplified contract and strategy form.
+			\item Such rigidity is also costly to cartel
+		\end{itemize}
+		\item Alternative explanation for such limitation on contracts:
+		\begin{itemize}
+			\item Limiting non-price competition
+			\item Authors did not agree. They argue that the \textit{contractual harmonization} conveys more than non-price competition limitation.
+		\end{itemize}
+	\end{itemize}
+	\item Collusion contract is always incomplete
+	\begin{itemize}
+		\item The regular and frequent meetings are to fix the holes
+	\end{itemize}
+
+	\item Why firms do not directly retaliate when they find cheating?
+	\begin{itemize}
+		\item Different from \cite{Green_Porter:1984EMCA}, firms in Sugar Cartel can argue within the institute meeting.
+Such meeting gives them a chance to figure out whether it is a shock or a intentional cheat.
+In other words, firms do have a choice to reduce the confounding uncertainty, which reduces their incentive to retaliate.
+	\end{itemize}
+	\item Firms do not retaliate to every cheating. They do not use massive retaliation unless the cheating is very high. The retaliation they take generally is `matching', kind of tit-for-tat.
+	\begin{itemize}
+		\item One reason to desist from full-scale retaliation (as in \cite{Green_Porter:1984EMCA}) is the vertical contractual arrangement in the industry.
+Firms sell sugar through brokers.
+Brokers will have much higher incentive to deviate since their number is much larger than that of firms.
+Such structure made deviation more prevalent.
+It is also more costly, since one more layer of brokers make it more difficult for firms to switch between two pricing regimes.
+	\end{itemize}
+	\item Firms rarely react to market share.
+	\begin{itemize}
+		\item Market share is too noisy a signal.
+	\end{itemize}
+	\item Firms choose to meet frequently to adapt quickly to external change, and to fix any holes in rule as soon as possible. They seem not care much about the \textit{renegotiation problem}.
+\end{itemize}
+
+% subsection genesove_mullin_01_aer (end)
+
+\section{Graham-Marshall, 87 JPE} % (fold)
+\label{sec:graham_marshall_87_jpe}
+
+\textbf{\bibentry{Graham_Marshall:87jpe}}
+
+This paper models the collusion within bidders in Second Price Sealed auction and English auction in IPV framework.
+They find collusion strategy equilibrium can be stable in such settings.
+Coalition of any size is stable, and the expected payoff to each member increases with the coalition size.
+
+\begin{itemize}
+	\item In second price auction. The optimal reserve price is a increasing function of coalition size.
+	\item In English auction.
+The optimal reserve price is identical to that of second price auction, and independent of observed highest bid.
+This result is striking since it seems at first that auctioneer at English auction can do better with this additional information.
+\end{itemize}
+
+Some stylized facts are not incorporated in this model:
+\begin{itemize}
+	\item Fact: brokers will not be invited to the coalition.
+If a broker has a customer, his willingness to pay is much stronger than any dealer.
+Thus he does not want to join the ring since other ring members will push price high in the knock-out round.
+If a broker does not have a customer, the he is not really coming to bid but to share the `ring hat'.
+The ring does not want him in this case.
+
+	$\rightarrow$ This fact cannot be encompassed in this model. Because the model assumes IPV, while brokers represent a very special distribution (0 or very high) of value, against the assumption.
+\end{itemize}
+
+\section{MMRS, 94 GEB} % (fold)
+\label{sec:marshall_meurer_richard_stromquist_94_geb}
+
+\textbf{\bibentry{Marshall:1994bc}}
+
+This paper raises a algorithm to numerically solve equilibrium in heterogeneous auctions.
+And they use this algorithm to investigate simulate some facts for auction coalition in first price auction.
+
+\vspace{1em}
+\noindent
+\textbf{Facts from Simulation:}
+\begin{itemize}
+	\item Revenue equivalence of first price auction (or Dutch) and second price auction (or English) does not hold in existence of collusion. The expected revenue is higher in first price auction.
+
+	\item In second price auction, the individual has no incentive to deviate from the coalition even when coalition size is very large.
+Actually the surplus of coalition gain to individual gain increases with coalition size $k_1$.
+
+	\item In first price auction, the individual has no incentive to deviate when coalition size is small, but does have incentive to deviate when coalition size is large.
+The relative advantage of individual bidder increases with coalition size $k_1$.
+
+	\item In ascending auction, for any given value, the weaker bidder will be more aggressively than stronger bidder. 
+	\begin{itemize}
+		\item This induces inefficiency. Stronger bidder with higher value may lose the auction.
+		{\color{blue}
+		\item Payoff equivalence not holding in this environment?
+		\begin{itemize}
+			\item maybe sealed auction and ascending auction does not reduce to the same direct mechanism in this environment
+		\end{itemize}
+		}
+	\end{itemize}
+
+	\item The same features are also found in \cite*{Athey:2011cs}.
+Although in Athey el al., the heterogeneity is not from collusion but from different cost distribution between large (mill) and small (logger) bidders.
+But the mathematical representation is the same, larger bidders value distribution FOSD that of the small bidders.
+	\begin{itemize}
+		\item They find the timber auction has following stylized facts: sealed first price auction attract more small bidders, shit the allocation toward these bidders, and can generate higher revenue to auctioneer.
+	\end{itemize}
+\end{itemize}
+
+% subsection marshall_meurer_richard_stromquist_94_geb (end)
+
+% subsection graham_marshall_87_jpe (end)
+
+% section cartels_and_collusion (end)
+
+\chapter{Price Dispersion} % (fold)
+\label{cha:price_dispersion}
+
+\section{Butters, 77 RES} % (fold)
+\label{sec:butters_77_res}
+
+\textbf{\bibentry{butters:77res}}
+
+This paper tries to generate price dispersion in a homogeneous environment.
+Homogeneity is in the sense that commodity characteristics, consumer preference, seller cost are all the same.
+The only heterogeneity comes from seller's strategy on pricing and advertisement.
+
+Unlike previous literature only focusing on consumer side, Butters models both consumer search behavior and the firm strategy.
+In other words, previous models are `partial-partial equilibrium', while this paper is `partial equilibrium'.
+
+\vspace{1em}
+\noindent
+\textbf{No Consumer Search:}
+\begin{itemize}
+	\item Seller: decide the amount of ads, for each ad can post a different price. Each ads costs $b$.
+	\item Buyer: the only way to purchase is through ads, and pick the lowest price (unless all prices higher than reserved price $m$).
+Each ads reach each consumer with equal probability, that's to say, the probability distribution of number of ads of any given consumer is Poison distribution.
+Most importantly, the probability that a consumer receives no price quotes lower than $p$, given the ads distribution $A(p)$, is $exp(-A(p))$.
+	\item The model is solved purely at market level.
+Denote $A(p)$ to be the number of ads with prices equal or lower than $p$ divided by consumer number $M$.
+$S(p)$ to be the sales actually happen with price lower than $p$ divided by consumer number $M$.
+$\pi(p)$ be the probability of selling a good by pricing at $p$.
+	\begin{itemize}
+		\item We thus have $s(p)=a(p)\pi(p)$, where $s(p),a(p)$ are derivatives of $S,A$ respectively.
+		\item The profit function is:
+		\[\text{profit}=\int{[(p-p_0)\pi(p)-b]a(p)}dp\]
+	\end{itemize}
+	\item By no deviation condition, the marginal profit at any equilibrium price level should be zero. Thus, $(p-p_0)\pi(p)=b$, and $\pi(p)=b/(p-p_0)$
+	\item By similar arguments as in allpay auction, the equilibrium price can only be a range $[p_0+b,m]$
+	\item IMPORTANT: $\pi(p)=exp(-A(p))$
+	\begin{itemize}
+		\item $\pi(p)$ is the probability that an ad with price $p$ being accepted.
+This is the probability that this ad goes to a consumer with ZERO price quotes lower than $p$.
+By our previous analysis, $A(p)$ is the number of ads per consumer, i.e.
+the single time probability that a consumer receives an ad with price lower than $p$.
+Then by the results of Poison distribution, the probability that a consumer receiving no price quotes lower than $p$ is $exp(-A(p))$.
+		\item This is important since it connects the individual behavior and market index.
+Firms only cares about $\pi$ when making ads decision; while $A(p)$ can induce $\pi(p)$.
+These two have to be consistent in equilibrium.
+	\end{itemize}
+	\item The equilibrium is easy to solve with above characterization.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{With Consumer Search:}
+\begin{itemize}
+	\item The setting is quite tricky. The equilibrium is greatly simplified due to the following two assumptions of \textit{word-of-mouth search}:
+	\begin{itemize}
+		\item ASSP-1: The probability that a search yield an offer from any particular seller is proportional to his share in total shares;
+		\item ASSP-2: The probability that this offer is at a price within a particular interval $(p_1,p_2)$ is proportional to the seller's sale at this particular interval.
+	\end{itemize}
+	Above two assumptions makes the profit from searching consumers exactly proportional to that of non-searching consumers.
+So we only need to maximize the profit from non-searching consumers, which has the same structure as no-search case.
+	\begin{itemize}
+		\item KZ: I find these two assumptions uncomfortable. This is not about the search behavior, but all about the optimal advertisement.
+	\end{itemize}
+
+	\item Claim: consumers will search iff they receive no ads, and in this case they will accept the first price they find.
+	\begin{itemize}
+		\item The second half is direct implication of the assumptions, especially assumption 2.
+		\item For first half, denote the highest posted price $p_{max}$, and the threshold price of searching $p_c$.
+Obviously $p_{max}\leq p_c$.
+Further we claim that $p_{max}=p_c$, otherwise the firm can increasing highest posted price by $\varepsilon$ while keep advertisement same as in $p_{max}$.
+	\end{itemize}
+
+	\item The equilibrium is very similar to no-search case. The only difference is $\pi(p_{min})=1/\phi>1$. At lowest posted price, one ad will induce more than one purchase.
+	\begin{itemize}
+		\item This is because now we have $1-\phi$ portion of people receive no ads, at any price interval.
+Thus conditional on the consumer receiving at least one ad, $p_{min}$ will for sure lead them to buy.
+But such ads will induce even more purchase because those receiving no ad will also buy from this seller at this price $p_{min}$ proportionally.
+		\item This makes sense because since consumer can search, firms can transfer the load of advertisement partly to the consumer side.
+	\end{itemize}
+
+	\item The portion $\phi$ can be pinned down in equilibrium by the fact that eventually every consumer will buy.
+\end{itemize}
+
+\section{Sorensen, 00 JPE} % (fold)
+\label{sec:sorensen_00_jpe}
+
+\textbf{\bibentry{Sorensen:00jpe}}
+
+\vspace{1em}
+\noindent
+\textbf{Facts and Identification Strategy:}
+\begin{itemize}
+	\item This paper is a reduced form paper testing price distribution in drugs.
+
+	\item The identification strategy is to \textbf{use \textit{frequency} as the key explanation variable}. 
+	\begin{itemize}
+		\item This is the \textit{comparative static} approach.
+Because by \cite{butters:77res} the price dispersion will shrink if the cost of search is lower.
+Here the searching frequency is a proxy as search cost.
+	\end{itemize}
+
+	\item Measure of price dispersion is \textbf{price range}.
+This is an absolute measure, because search cost generally do not vary with price scale.
+There are other measures possible, for example standard deviation, or relative range.
+
+	\item The environment is carefully picked for clean identification:
+	\begin{itemize}
+		\item The market is some small isolated markets, with sufficiently many pharmacies within each market.
+		\item The frequency of purchase is determined by instruction of doctor, which is uncontrollable by drug consumers.
+		\item The drug price is posted, thus is in principal public so that econometricians can collect them. But consumers have to pay the search cost to gain such information.
+		\item All pharmacies face similar cost.
+	\end{itemize}
+
+	\item They also exclude the possibility of heterogeneous pharmacy service.
+	\begin{itemize}
+		\item First, they show that pharmacies have very different rankings for different drug price. This fact is inconsistent with the explanation of pharmacy level heterogeneity.
+		\item Second, they run a residual regression to show that pharmacy heterogeneity at most account for 30\% of price dispersion.
+	\end{itemize}
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{What Cannot be Answered:}
+\begin{itemize}
+	\item The data generating process. How exactly search cost affects the price dispersion.
+	\item Quantifying search cost.
+	\item This has to be done with a structural model like \cite{Hortacsu:2004bg}.
+\end{itemize}
+
+% subsection sorensen_00_jpe (end)
+
+\section{Hortacsu-Syverson, 04 QJE} % (fold)
+\label{sec:hortacsu_syverson_04_qje}
+
+\textbf{\bibentry{Hortacsu:2004bg}}
+
+\vspace{1em}
+\noindent
+\textbf{Facts and Explanations:}
+\begin{itemize}
+	\item Mutual fund prices are hugely dispersed, despite their financial homogeneity. The 75th to 25th price ratio of Index Funds is 3.1;
+	\item Nonportaforlio Differentiation. Funds attributes like manager tenure, the age of the fund, rate of taxable distributions will not directly affect return, but do affect investors' choice.
+	\begin{itemize}
+		\item Only focus on vertical differentiation and assume homogeneous preference over these attributes. Because horizontal differentiation is unidentifiable from search cost differences.
+	\end{itemize}
+	\item Search Cost.
+	\item Switch Cost.
+If switch cost is important, then we should observe in data that inflow/outflow of S\&P Fund in a non-load funds family should be less volatile than those in a load funds family.
+Because when index fund performs poor, those in a load fund family will switch to another fund in the same fund family, inducing larger imbalance within the fund family.
+This is not significant in data.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Model:}
+\begin{itemize}
+	\item Funds are different in both prices and other vertical attributes. But investors have homogeneous utility form. 
+	\footnote{We cannot identify taste heterogeneity using BLP. The taste differentiation is unidentifiable with search cost differentiation.}
+	We assume a specific utility form, where price enters linearly:
+	\[u_j=W_j \beta-p_j+\varepsilon_j\]
+	\item Investors have cost $c_i$ for each search, which is distributed in population as $G(c)$. An investor searches sequentially until the expected utility gain is smaller than search cost:
+	\[c_i \leq \int_{u^*}^{\bar u} (u-u^*)dH(u)\]
+	where $H(u)$ is investors' belief about the distribution about funds' indirect utility, which is unknown to econometricians and have to be assumed.
+We assume that funds provide $N$ levels of utility, $u_1 < ...
+<u_N$.
+If we further assume equal sampling probabilities, we have:
+	\[H(u)=\frac{1}{N}\sum_{j=1}^N I[u_j \leq u]\]
+	Investors are assumed to know the value of each $u_j$, they are only uncertain about which fund provides which utility level.
+	\begin{itemize}
+		\item KZ: this assumption very strong, which greatly reduces the dimension of information investors need to learn about.
+	\end{itemize}
+	\item The optimal search rule yields critical points in search cost:
+	\[c_j=\sum_{k=j}^N{\rho_k (u_k-u_j)}\]
+	where $\rho_k$ is the probability that fund $k$ is sampled on each search, which is known to all investors.
+The RHS is the expected payoff of another search conditional on already found $j$.
+Thus $c_j$ is the highest possible search cost that could allow such search.
+	\begin{itemize}
+		\item KZ: $\rho_k$ is just the density of $H(u)$.
+If equal sampling, then $\rho_k=1/N$ for all $k$.
+If not equal sampling, it should be conditional on how much time an investor has already searched, unless we assume the funds pool is infinite.
+	\end{itemize}
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Identification:}
+\begin{itemize}
+	\item \textbf{Goal:} identify the search cost and coefficients of other attributes with only price and market share data.
+	\item Funds market share can be written in cost thresholds.
+Thinking of $u_1$ with lowest indirect utility.
+Only those with really high search cost will end up buying fund-1, and they have to be unlucky to draw this fund at the first time.
+	\[q_1=\rho_1(1-G(c_1))=\rho_1\Big[1-G\Big(\sum_{k=1}^N{\rho_k(u_k-u_1)}\Big)\Big]\]
+	For fund-2, there are two sources. One investor may have cost higher than $c_1$ and draw fund-2 in the first time; or he has cost $c_2<c<c_1$ and draw fund-2 first time or directly after fund-1.
+	\footnote{$Pr=\rho_2+\rho_1\rho_2+\rho_1\rho_1\rho_2+...=\rho_2/(1-\rho_1)$}
+	\[q_2 = \rho_2(1-G(c_2))+\frac{\rho_2}{1-\rho_1}(G(c_2)-G(c_1)) \tag{7}\]
+	Similarly, we can write $N$ equations for all funds market share. 
+	\begin{itemize}
+		\item Thus we can back out $G(c_j)$ with known $\rho_j$ and $q_j$ for all $j$.
+		Moreover, we can normalize $G(c_N)=0$ because we have $c_N=0$ by threshold equation, and search cost have to be nonnegative.
+		\item We can take derivative with $p_j$, because $c_j$ is influenced by $u_j$ which contains $p_j$. Thus we can write $N-1$ derivatives:
+		\[\frac{\partial q_j}{\partial p_j}
+		=f(\rho_1,...,\rho_N,g(c_1),...,g(c_j)) \tag{10}\]
+		where $g(c_j)$ is the p.d.f. of cost distribution at $c_j$.
+	\end{itemize}
+
+	\item For supply side, we first write the FOC of fund $j$.
+	\[q_j(p,W)+(p_j-mc_j)\frac{\partial q_j(p,W)}{\partial p_j}=0 \tag{9}\]
+	In above equation, only $q_j$ and $p_j$ is observable to econometricians.
+	If we further assume Bertrand-Nash competition, we have:
+	\[\frac{\partial q_j(p)}{\partial p_j}
+	=-\frac{q_j(p)}{p_j-mc_j}\]
+	If we know $mc_j$, then we can calculate $\partial q_j/\partial p_j$, and plugging into (10) get us $g(c_j)$ for all $c_1, ... ,c_{N-1}$
+
+	\textcolor{red}{The paper says $mc_j$ can be estimated, don't know how}
+
+	\item Knowing $G_j$ and $g_j$ for all $c_1,...c_{N-1}$, we can back out all $c_j$ through:
+	\[G(c_{j-1})-G(c_j)\approx 0.5[g(c_{j-1})+g(c_j)](c_{j-1}-c_j)\]
+	Recall that $c_N=0$, we have known all $c_j$.
+	Since we know all $c_j$ and $G(c_j)$, we have backed out the distribution of search cost (in these thresholds).
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Estimation:}
+\begin{itemize}
+	\item \textbf{Basic Model:} homogeneous funds except for price, equal sampling $\rho_j=1/N$
+	\begin{itemize}
+		\item By homogeneity, we have $u_j = u-p_j$. Thus $c_j$ is only function of $p_j$'s.
+	\end{itemize}
+
+	\item \textbf{Homogeneous Fund + Unequal Sampling Probability:}
+	\begin{itemize}
+		\item By homogeneity, we have $u_j = u-p_j$. Thus $c_j$ is only function of $p_j$'s. Since we know $p_j$ for all $j$, we then know $c_j$ as well.
+		\item By unequal sampling, assume specifically:
+		\[\rho_j=\frac{Z_j^\alpha}{\sum_{k=1}^N{Z_k^\alpha}}\]
+		where $Z_j$ is the attributes that will affect the likelihood of being found, e.g. advertisement expenditure. We use age of a fund as proxy.
+		\item Estimate the model by fitting $(N-1)$ (7) and $(N-1)$ (9).
+We know $c_j$, $Z_j$, and $G(c_j)$ can be written as function of $Z_j$ and unknown parameter $\alpha$.
+So we have $2N-2$ equations to estimate $\alpha$ and $mc_j$ for all $j$.
+	\end{itemize}
+
+	\item \textbf{Heterogeneous Fund + Equal Sampling Probability:}
+	\begin{itemize}
+		\item Since funds are heterogeneous, $c_j$ cannot be directly derived from $u_j$. But we can still non-parametrically identify $c_j$ as described in previous section.
+		\item For identification, we must assume equal sampling probability. We also assume $mc_j$ is constant and equals 10 basis point for all $j$.
+		\item Estimation result shows that overall search cost decreases sizable amount in 1996 to 2000, but in upper quantile increases. This may be due to the entering of many novice family investors.
+	\end{itemize}
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Questions Remaining:}
+\begin{itemize}
+	\item The assumptions of drawing funds with replacement is not satisfying, especially when the industry is very concentrated in several star funds.
+
+	\item If we want to investigate both horizontal differentiation and vertical differentiation.
+Then we have to know not only the individual level data on what choice they made, but also the \textit{choice set} they have.
+	\begin{itemize}
+		\item There are two possible interpretation for a fund to be chosen.
+1) the consumer observes all the funds and prefers this fund most; 2) the consumer only observes a limited number of funds and have to pick one.
+This causes the identification problem between preference and search cost.
+	\end{itemize}
+
+	\item Bundling problem.
+The consumers do not just buy one fund, but buying a bundle of funds.
+They react to the whole bundle price instead of single fund price.
+This is one specific kind of product differentiation.
+	\begin{itemize}
+		\item The importance of such product differentiation is, it can hardly say that such differentiation is only vertical.
+Different investors have different financial goals, and thus have different preference on bundles.
+	\end{itemize}
+\end{itemize}
+
+\section{Allen-Clark-Houde, 14 AER} % (fold)
+\label{sec:allen_clark_houde}
+
+\textbf{\bibentry{Allen:2014kr}}
+
+\vspace{1em}
+\noindent
+\textbf{Empirical Takeaway:}
+\begin{itemize}
+	\item The competition of firms mostly benefit consumers with low search cost.
+	\begin{itemize}
+		\item The merger led to an increase in \textit{average} interest rate of appx 6 bps.
+		\item This merger effect is between 7 to 9 bps for consumers with lower and middle range percentile search cost; and has no effect for consumers with top 30\% serch cost.
+		\item The merger led to a 16\% decrease in interquartile price range.
+	\end{itemize}
+\end{itemize}
+
+\textcolor{blue}{Identification and estimation part to be added.}
+
+% subsection allen_clark_houde (end)
+
+% subsection hortacsu_syverson_04_qje (end)
+
+\myline
+
+\textbf{\bibentry{Baye:2013un}}
+
+\begin{itemize}
+	\item Price comparing sites becoming less popular,
+	more consumers choose to directly go to like Amazon and eBay.
+	These websites also have `marketplace'.
+	\item Many searching behavior are not observed. Non-texture data (e.g. in the menu, directories).
+	\item Search time across platforms can hardly be compared.
+	Because maybe it's enough to search only once in Amazon, 
+	but many times in eBay.
+\end{itemize}
+
+\myline
+
+\noindent
+\textbf{Random Ideas}
+\begin{itemize}
+	\item Collusion when there is consumer searching cost.
+	Intuitively, collusion should be easier to sustein with 
+	\textcolor{blue}{[no idea]}
+
+	\item Awaya-Krishna (2016) 
+\end{itemize}
+
+% subsection butters_77_res (end)
+
+\chapter{Auction} % (fold)
+\label{cha:auction}
+
+\section{McMillan, 94 JEP} % (fold)
+\label{sec:mcmillan_94_jep}
+
+\textbf{\bibentry{McMillan:1994bc}}
+
+\vspace{1em}
+\noindent
+\begin{itemize}
+	\item Lessons from New Zealand and Australia:
+	\begin{itemize}
+		\item Second price auction may have political defect and revenue loss.
+People are dissatisfied to see firms pay less than their revealed true value.
+And reserve price will enhance revenue when bidder number is small.
+		\item Australia's auction shows that penalty for default is necessary to restrain incentive of over bid.
+		\begin{itemize}
+			\item FCC: the highest bidder need to pay the difference between his bid and actual sale price if he chooses to exit.
+		\end{itemize}
+	\end{itemize}
+
+	\item Open Bidding v.s. Sealed Bidding
+	\begin{itemize}
+		\item Open auction can mitigate winner's curse because bidders can learn from others' biddings, and thus be less cautious.
+		\item Sealed bid auction increases revenue when bidders are risk averse. Because bidders will bid higher to ensure winning in sealed auction.
+		\item Sealed bid auction deters collusion.
+		\item FCC: run multiple rounds of sealed auction, announce bids after each round, but do not announce bidder identity.
+	\end{itemize}
+
+	\item Simultaneous v.s. Sequential Auction
+	\begin{itemize}
+		\item Sequential bidding have two disadvantages:
+		\begin{itemize}
+			\item It is less flexible, impeding the possible aggregation. The firm cannot go back and adjust his portfolio.
+			\item Encourage predatory bidding in early stage.
+		\end{itemize}
+		\item Simultaneous auction has difficulty in implementing effective stopping rule.
+		\item FCC: for 20\% core licenses, use simultaneous stopping, and use license-by-license stopping for the rest.
+	\end{itemize}
+
+	\item Combinational v.s. Non-Combinational Bidding
+	\begin{itemize}
+		\item Combinational bidding allows bidders to bid for bundles of licenses together. It is efficient in the sense that different licenses are complementary and have economics of scale.
+		\item Combinational bidding has another advantage of expanding the preference space.
+		\item Combinational bidding will refrain competition.
+Because there is free rider effect within independent bidders.
+Even there total value of separately awarded licenses exceed that of the nationwide bidder, they would not like to bid high because they only get a share of winning rent.
+		\item FCC: combinational bidding not allowed in simultaneous bidding; allowed in sequential bidding with a possible premium.
+	\end{itemize}
+
+	\item Aid Designated Bidders
+	\begin{itemize}
+		\item Give those bidders a price preference.
+	\end{itemize}
+
+	\item Royalties v.s. Single Payment
+	\begin{itemize}
+		\item Royalty partially shifts the risk to government, thus increasing bidders' willingness to pay.
+		\item Makes auction more like common value. \textcolor{blue}{The paper says this will stimulate competition, don't understand.}
+		\item Causes post-auction incentive problem.
+		\item Difficulty to isolate revenue induced by such license in practice.
+	\end{itemize}
+\end{itemize}
+
+% subsection mcmillan_96_jep (end)
+
+\section{Kawai, 18 WP} % (fold)
+\label{sec:kawai_18_wp}
+
+\noindent
+\textbf{Kei Kawai (2018 WP): Missing Bids and Scoring Auctions}\\
+
+There are two main contributions for this paper:
+\begin{itemize}
+	\item It introduces a way of measuring collusion level in auction.
+	\item It empirically shows that scoring auction is more competitive (less collusive) than pure price-based auction.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Detecting Collusion:}
+\begin{itemize}
+	\item Define the distance of bid-i to the winning bid of remaining bidders to be:
+	$$\Delta_i = bid_i - \min_{j\neq i}bid_j$$
+	If we pile (sum up) $\Delta_i$ for all bidders, and plot the density, we should find them to be relatively smooth.
+	But in data, the authors find that the density around $\Delta = 0$ is a low spike. This suggests collusion.
+	\item Intuition is, if there is no collusion, then the bidders can increase their bids by a little bit.
+Since the density of $\Delta$ near 0 is very low, the probability of losing the auction by increasing bid is low.
+So the optimal strategy should be to increase the bidding price.
+	\item The author further introduces a scale measure of collusion possibility. \red{Do not understand this part.}
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Score Auction:}
+\begin{itemize}
+	\item The auctioneer of score auction does not take price as the only deterministic attribute for allocation.
+He will also consider the \textit{quality} of the bid.
+But since the quality is a multi-dimension property, there is uncertainty about the allocation result.
+This uncertainty is essentially uncertainty about auctioneer's preference.
+	\item Such uncertainty makes it more difficulty to monitor deviation within a bidding ring, thus makes the cartel more difficult to sustain. The intuition is from \cite{Green_Porter:1984EMCA}.
+\end{itemize}
+
+% section kawai_18_wp (end)
+
+% section auction (end)
+
+% section price_dispersion (end)
+
+\chapter{Spatial Competition} % (fold)
+\label{cha:spatial_competition}
+
+% section spatial_competition (end)
+
+\section{DGT, 78 EMCA} % (fold)
+\label{sec:dgt_78_emca}
+
+% subsection dgt_78_emca (end)
+
+\textbf{\bibentry{DGT78}}
+
+\textcolor{blue}{This paper serves as an example of clear writing.}
+
+Hotelling's `converging to middle' result is not a generic property of the model.
+For example, 
+\begin{itemize}
+	\item When transportation cost is linear, there exists no pure strategy Cournot Eqm when two firms are very close;
+	\item When transportation cost is quadratic, there exists pure strategy Cournot for any location pair, but both firms would like to move away from each other.
+\end{itemize}
+
+Intuition is, for $p_1^*$ to be equilibrium price against $p_2^*$, it has to be better than any other price.
+Specifically, it has to be better than a price $\hat p_1$ which will grab all consumers from firm 2.
+When two firms are located close, $\hat p_1$ will be attractive.
+However, this cannot be an equilibrium since firm 2 will do the same reasoning.
+This is like a double auction with a cap, here the cap is decided by the distance between two firms.
+
+\section{Chaterjee, 18 JMP} % (fold)
+\label{sec:chaterjee_18_jmp}
+
+\textbf{\bibentry{Chatterjee:2017tn}}
+
+This job market paper estimates the market power within spatial competition framework.
+
+\vspace{1em}
+\noindent
+\textbf{Settings:}
+\begin{itemize}
+	\item Market is divided into several regions.
+Within each region, there are many farmers and intermediaries.
+Farmers first sell good to intermediaries, then intermediaries sell them in the retail market.
+	\item Farmers in one region can only sell to intermediaries in the same market. Intermediaries has no such restriction.
+	\item All transactions are subject to iceberg cost. So each intermediaries enjoys some monopoly power, which is increasing with scarcity of intermediaries in one region.
+	\item Farmers do Nash bargaining with intermediaries. The whole market is playing a Nash-in-Nash game. Define the optimal alternative by:
+	\[\underline p(m)=\max_{k\in \mathcal{M}-\{m\}}
+	\{\frac{p^f(k)}{\tau_{mk}}\}\]
+	where $\tau_{mk}$ is the distance cost from $m$ to $k$.
+	And the Nash bargaining outcome is the solution to:
+	\[\max_\lambda (\lambda-\underline p(m)q_m)^\delta
+	(p_m^rq_m-\lambda)^{1-\delta}\]
+
+	\item Void the region restriction will increase the welfare of farmers. Intuitively, if information gathering is of no cost, then enlarging farmers' information set will do them no harm.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{KZ Questions:}
+\begin{itemize}
+	\item What if farmers have to search for the cost? Will the welfare result hold?
+
+	\item {\color{blue} This paper introduces a `ripple effect' of competition spread through the neighbors. How we can modify this to our liquor data?}
+\end{itemize}
+% section chaterjee_18_jmp (end)
+
+\chapter{Vertical Relationship} % (fold)
+\label{cha:vertical_relationship}
+
+\section{Horn and Wolinsky, 88 RAND} % (fold)
+\label{sec:horn_and_wolinsky_88_rand}
+
+\textbf{\bibentry{Horn:1988ce}}
+
+\vspace{1em}
+\noindent
+\textbf{Highlights of the Paper:}
+\begin{itemize}
+	\item When price is determined by negotiation, the incentives to merger will be very different with the case where price is unilaterally set.
+	\item Symmetric case.
+Two suppliers, two retailers, independent or simultaneous bargaining.
+When down-stream firms are strategically complementary.
+Then a monopoly upstream firm is \textit{less} profitable than two independent suppliers.
+	\begin{itemize}
+		\item \textcolor{blue}{[Intuition]} Because when a monopoly supplier has to take into account the profit of both downstream firms, which weakens its bargaining power when the downstream firms are strategically complementary.
+	\end{itemize}
+	\item Asymmetric case.
+One supplier, two retailer, sequential bargaining.
+Whether the upstream firm will earn more profit through merging depends on the reference point (disagreement point).
+When the disagreement point is high, then the supplier can earn higher profit though sequential bargaining; otherwise profit is higher though simultaneous bargaining.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Model:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Pros:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+% subsection horn_and_wolinsky_88_rand (end)
+
+% section vertical_relationship (end)
+
+\chapter{Demand Estimation} % (fold)
+\label{cha:demand_estimation}
+
+\noindent
+\textbf{Reference:} \cite{shum:2016bk} CH 1 is very good for motivation and techniques.\\
+
+\noindent
+\textbf{Motivation for demand estimation}
+\begin{itemize}
+	\item Firstly, it is important per se, we want to understand consumer behaviour. And we want to \textit{predict the results of price change}, and \textit{introduction of new products}. 
+	Such counter factual predictions can only be built upon a structural model.
+	\item Secondly, estimation of demand function helps us better understand market structure.
+Markup itself is rarely observed (with some exceptions, like the electronic industry), but we can generally observe demand elasticity.
+	Recall that $\frac{p-MC}{p}=1/\varepsilon$ (see \ref{sec:rey_and_stiglitz_1995_rand}). Estimation of $\varepsilon$ will help us know the markup of firm, thus infer market structure.
+\end{itemize}
+
+\noindent
+\textbf{Challenges in demand function estimation:}
+\begin{itemize}
+	\item Too many parameters.
+Think of a market with 100 commodities and we want to estimate the cross elasticities.
+The number of parameters will be 10,000.
+Obviously it is impossible to have enough data to estimate so many parameters.
+	\begin{itemize}
+		\item Solved by nested logit model.
+	\end{itemize}
+	\item Unobserved quality. This will causes the endogeneity of price. And because the unobservable quality affects the selling in a highly nonlinear way, so IV is not very applicable in this case.
+	\begin{itemize}
+		\item Solved by BLP style estimation.
+	\end{itemize}
+\end{itemize}
+
+\section{Brief Literature Review} % (fold)
+\label{sec:brief_literature_review}
+
+There are two branches of demand function estimation.
+The early literature features differentiated goods (continuous choices). Classical examples include \cite{Hausman:1994km} introducing a nested approach to reduce the dimension of parameters.
+
+Recent literature focus much more on discrete choice model. The seminal papers are \cite{Berry:1994jh} and \cite*{berry.et.al.1995.emca}.
+The address of these two papers is to overcome the \textbf{endogenous price problem due to unobserved quality}. 
+Suppose we use a characteristic approach, where consumer utility and thus their purchase decision is decided by characteristics of products. 
+Some of the characteristics are obervable to consumer (and firms) but not to econometricians, for example the advertisement. 
+For higher unobserved quality, the equilibrium price will be higher, leading to a downward bias of price elasticity.
+
+\cite{Berry:1994jh} comes with a method to overcome this endogeneity problem with only \textit{market level data}.
+\begin{itemize}
+	\setlength{\itemsep}{0pt}
+	\item The basic idea is a IV based two step estimation.
+	\item First step: denote $\delta_j$ to be the `mean utility' for brand $j$.
+Notice this includes unobserved quality.
+Under some (weak) conditions, $\delta_j$ can be \textit{inversed} by market shares $(s_1,...,s_J)$, and thus we can get $\hat \delta_j$ by observed market shares.
+	\textcolor{blue}{This inversion step is the key for this paper, and many following papers treating endogenous quality problem.}
+	\item Second step: By definition, $\delta_j=X_j\beta -\alpha p +\xi_j$.
+Thus we can get $\hat \xi_j$ if we get $\hat \delta_j$.
+Suppose $E[\xi Z]=0$, then we can use $Z$ as IV to estimate consistently.
+\end{itemize}
+
+\cite{berry.et.al.1995.emca} (BLP henceforce) is more comprehensive with the same idea.
+They introduce random-coefficients logit model, which allows each individual to have different taste coefficients.
+Thus we can't directly use the inverse technique.
+The way is to use a Simulation Method of Moments (inner loop and outer loop).
+First guees a $\delta$, match mkt share, then run a IV regression, then guess different $\delta$ and get an outer loop.
+They prove a contraction mapping.
+
+\myline
+
+\textbf{\bibentry{Quan_Williams:2017wp}}
+
+This paper addresses the local heterogeneity of consumer demand,
+and concludes that usual BLP method will overestimate the welfare increase of e-commerce because local stores have satisfied most local demands.\\
+
+\noindent
+\textbf{Challenges:}
+\begin{itemize}
+	\item Huge varieties of goods in fine-grid locations make scarce data in each category. Two possible solutions for this: 1) aggregating over locations; 2) just ignore the zero sales. 
+	Aggregating is unsatisfactory since the heterogeneity of local preference is our study focus.
+	Ignoring will cause selection bias and cause overestimation of local heterogeneity.
+	\item Mean utility level cannot be recovered solely by observable variables.
+	They raise specific Converging in Distribution theorem to tackle this.
+\end{itemize}
+
+% subsection brief_literature_review (end)
+
+\myline
+
+\textbf{\bibentry{erdem_kean:96_MngSci}}
+
+\cite{erdem_kean:96_MngSci} provides an example on how to estimate demand when quality is uncertain and consumer learns by Bayesian rule.
+
+\vspace{2mm}
+\noindent
+\textbf{Motivation:}
+\begin{itemize}
+	\item Avoide ad hoc assumptions on how consumers utilizing experience information
+	\item Estimate structural models to do policy analysis
+\end{itemize}
+
+\noindent
+\textbf{Features:}
+\begin{itemize}
+	\item Estimate Dynamic Programming.
+	Consumers make decision based on their perceptions,
+	but econometricians only observe the consumption. 
+	So have to integrate over the distribution of perception errors $v_{ij}(t)$, which is is a Markov process.
+	The integration part will be very complicated.
+	\begin{itemize}
+		\item Provides a way to estimate Dynamic Programming model with simulation. Also see \cite{keane_wolpin:94REStat}.
+	\end{itemize}
+	\item Experience Shocks.
+	This indicates that even after purchasing once, 
+	consumer is not certain about the quality of the good (or the preference of himself).
+	This is mainly motivated by empirical fact: 
+	consumption behavior generally do not converge.
+\end{itemize}
+
+\noindent
+\textbf{Empirical Findings:}
+\begin{itemize}
+	\item Bayesian learning very well fit the date.
+
+\end{itemize}
+
+% section demand_function_estimation (end)
+
+\section{BLP, 95 EMCA} % (fold)
+\label{sec:blp_95_emca}
+
+The note on BLP draws deeply from \cite{Nevo:2000gn}, the original paper \cite{berry.et.al.1995.emca} is very worth reading.
+
+\textbf{Consumer Utility:}
+
+The consumer indirect utility is specified as:
+\[u _ { i j t } = \alpha _ { i } \left( y _ { i } - p _ { j t } \right) + x _ { j t } \beta _ { i } + \xi _ { j t } + \varepsilon _ { i j t } \]
+where $i$ for consumer, $j$ for products and $t$ for time periods (markets); $ x_{jt}$ are the observable characteritics, $\xi_{jt}$ is the unobservable product charateristics.
+Note that the quasilinear structure is not important, BLP beings from Cobb-Douglas form direct utility and end up with a log linear indirect utility form.
+
+We also need to specify an outside good:
+\[u _ { i 0 t } = \alpha _ { i } y _ { i } + \xi _ { 0 t } + \pi _ { 0 } D _ { i } + \sigma _ { 0 } v _ { i 0 } + \varepsilon _ { i 0 t }\]
+
+Consumer preference $\alpha_i$ and $\beta_i$ is heterogeneous across individuals. They are specified by:
+\[\left( \begin{array} { l } { \alpha _ { i } } \\ { \beta _ { i } } \end{array} \right) = \left( \begin{array} { l } { \alpha } \\ { \beta } \end{array} \right) + \Pi D _ { i } + \Sigma v _ { i }\]
+where $\alpha$ and $\beta$ are the common part; $D_i$ is hte demographics of individual $i$, for which the distribution is known (for example from census data); $v_i$ is the unobserved heterogeneous part, we assume it being multi-variate normal.
+$\Pi$ is a mapping from demographics to preference, and $\Sigma$ stands for the covariance matrix of heterogeneous part.
+
+The utility can be divided into two parts, the mean utility common for every consumer and the heterogeneous utility part:
+\[u _ { i j t } = \alpha _ { i } y _ { i } + \delta _ { j t } \left( x _ { j t ^ { \prime } } , p _ { j t } , \xi _ { j t } ; \theta _ { 1 } \right) + \mu _ { i j t } \left( x _ { j t } , p _ { j t } , v _ { i } , D _ { i } ; \theta _ { 2 } \right) + \varepsilon _ { i j t }\]
+where the $\delta_{jt}$ is the mean utility for product $j$ in market $t$, and $\mu_{ijt}$ is the heterogeneous part. 
+The parameters in $\delta_{jt}$ are called \textit{linear} parameters, and parameters in $\mu_{ijt}$ are called \textit{nonlinear} parameters.
+\[\delta _ { j t } = x _ { j t } \beta - \alpha p _ { j t } + \xi _ { j t } , \quad u _ { i j t } = \left[ - p _ { j t } , x _ { j t } \right] \left( \Pi D _ { i } + \Sigma v _ { i } \right)\]
+
+\textbf{Market Share:}
+
+The market share can be computed by:
+\begin{align}
+	s _ { j t } \left( x _ { . t } , p _ { \cdot t } , \delta _ { t } ; \theta _ { 2 } \right) &= \int _ { A _ { j t } } d P ^ { * } ( D , v , \varepsilon ) \notag \\
+	&= \int _ { A _ { j t } } d P _ { \varepsilon } ^ { * } ( \varepsilon ) d P _ { v } ^ { * } ( \nu ) d \widehat { P } _ { D } ^ { * } ( D )
+\end{align}
+where $A_{jt}$ is the set of all product characteristics that lead to choosing product $j$. Notice that the distribution of $\varepsilon, \nu$ and $D$ are known to econometrician.
+
+\textbf{Estimation:}
+
+Notice that unobservable $\xi_{jt}$ enters the market share non-linearly. But if we have $\delta_{jt}$, then $\xi_{jt}$ can be represented linearly by:
+\[\xi_{jt}\equiv \delta _ { j t } \left( S _ { . t } ; \theta _ { 2 } \right) - \left( x _ { j t } \beta + \alpha p _ { j t } \right)\]
+BLP shows that $\delta_{jt}$ can be calculated from observed market shares using contraction mapping:
+\[\delta _ { \cdot t } ^ { h + 1 } = \delta _ { \cdot t } ^ { h } + \ln S _ { \cdot t } - \ln S \left( p _ { \cdot t } , x _ { \cdot t } , \delta _ { \cdot t } ^ { h } , P _ { n s } ; \theta _ { 2 } \right)\]
+
+% chapter blp_95_emca (end)
+
+\chapter{Entry and Exit} % (fold)
+\label{cha:entry_and_exit}
+
+\section{Berry, 92 EMCA} % (fold)
+\label{sec:berry_92_emca}
+
+\textbf{\bibentry{Berry:1992gl}}
+
+\vspace{1em}
+\noindent
+\textbf{Highlights of the Paper:}
+\begin{itemize}
+	\item This paper studies the entry in airline industry.
+There are two issues to be focused: first is the simultaneity of of profits and market structure in oligopolistic market; second is the presence of a large number of heterogeneous potential entrants, which induces computational difficulty in estimation.
+
+	\item This paper features \textbf{heterogeneity of firms}, and there is a large number of potential entrants.
+	This paper shows that the SMM approach can solve this complicated equilibrium problem in a relatively easy way.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Model:}
+\begin{itemize}
+	\item The model is assumed to be \textbf{static}. At the beginning of each period, each firm takes the current network structure as given and decides whether to operate in a given city pair. 
+	The expost profit of a firm in a given market is determined by market level characteristics, its own airport presence, and of the number of competitors it faces in this market.
+	Notice the profit is independent of the firm's profit in other markets.
+
+	\item The profit function for firm $k$ in market $i$ is:
+	\[\pi_{ik}(s) = v_i(N(s))+\phi_{ik} \tag{1}\]
+	where $s$ is a given strategy file of all firms; $N(s)$ is the number of entering firms; and $\phi_{ik}$ is the index of profitability of firm $k$ in market $i$.
+	\begin{itemize}
+		\item \textcolor{blue}{[Firm Heterogeneity]}
+		We assume firm characteristics will only affect the fixed cost part, so the expost competition is symmetry.
+Thus $v_i(\cdot)$ only depends on the number of entering firms (up to scale), and the firm specific $\phi_{ik}$ only enters linearly.
+		This assumption is relaxed in \cite{Ciliberto:2009hy}, which assumes a very general form of firm heterogeneity.
+
+		\item \textcolor{blue}{[Unique $N^*$]} This separability of market level profit and firm level profit is essential.
+		Given equation (1), all equilibriums feature a unique $N^*$. And this can be used as identification tool.
+
+		\item We further specify $v_i(N)$ and $\phi_{ik}$ parametrically:
+		\[v_i(N)=X_i\beta+h(\delta,N)+\rho u_{io} \tag{2}\]
+		$\beta,\delta,\rho$ are parameters to be estimated. $X_i$ are characteristics of market $i$, $u_{io}$ are market characteristics observed by all firms but not econometricians.
+		\footnote{This is a complete information game.}
+		This can be derived from a Cournot model with constant and identical marginal costs together with a constant-elasticity demand function.
+
+		\item Firm specific portion of profit is:
+		\[\phi_{ik}=Z_{ik}\alpha+\sigma u_{ik}\]
+		$Z_{ik}$ are firm level characteristics and $u_{ik}$ unobservable to econometricians.
+
+		\item KZ: We have to assume some independence on unobservable characteristics for identification. 
+		But this is actually not very reasonable since in the firm side these characteristics are nothing special and thus may possess any kind of correlation.
+	\end{itemize}
+	Combine all these and we get:
+	\[\pi_{ik}(N)=X_i\beta-\delta \ln(N)+Z_{ik}\alpha
+	+\rho u_{io}+\sigma u_{ik} \tag{4}\]
+	We denote the observed terms as $r_{ik}(N)$ and the unobserved terms as $\varepsilon_{ik}$.
+	Notice that we can not identify $\rho, \sigma$ separately since they are just scale parameters, and this discrete choice model is identified up to scale.
+	This paper normalize $\sigma$ to $\sqrt{1-\rho^2}$.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Identification:}
+\begin{itemize}
+	\item The identification is through the equilibrium number $N^*$ of entering firms.
+	For a given unobserved $\varepsilon$, the equilibrium entering firm number is smaller or equal than $N$ iff:
+	\[(\varepsilon:\# \{\varepsilon_k:
+	\varepsilon_k \geq -r_k(N+1)\}=j)
+	,\ j=0,\dots,N\]
+	That is, no more than (but may be less than) $N$ firms can make a profit if $N+1$ firms enter.
+
+	\item Then suppose exact $J$ firms can make profits in a $N+1$ equilibrium, the probability of this event is:
+	\[H_{J(N+1)}=\sum_{s\in S(J)}
+	\int_{A_1(s,N+1)} \dots \int_{A_k(s,N+1)}
+	p(\varepsilon)d \varepsilon\]
+	where $s$ is a specific entering profile, and $S(J)$ is the set of entering profiles with $J$ entering firms.
+	For $K$ potential entering firms, there are $C_{N+1}^J$ many possible entering profiles.
+	The area $A_k(s,N+1)$ is:
+	\begin{align*}
+	A_k(s,N+1)&=(-r_k(N+1),\infty),\ \text{if}\ s_k=1\\
+	&= (-\infty,-r_k(N+1)),\ \text{else}
+	\end{align*}
+	That is, $A_k(s,N)$ is the region of $\varepsilon_k$ that firm $k$ can earn profit in a $(N+1)$-firm equilibrium if the profile $s$ shows it enters.
+	The probability $Pr(N^*\leq N)$ is:
+	\[Pr(N^* \leq N)= \sum_{J=0}^N H_{J(N+1)}\]
+	And thus the probability of an $N$-firm equilibrium is:
+	\[Pr(N^* = N)=Pr(N^* \leq N)-Pr(N^* \leq (N-1))\]
+	We can then apply MLE to maximize this probability.
+
+	\item Notice that although in principle we can estimate this in MLE as long as we have enough variation in $X_i$, the computation of $Pr(N^*=N)$ is very difficult.
+	This paper tackles this difficulty with two approaches: 1) they put additional restrictions over the parameters; 2) they use simulation methods to simplify.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Computation Issues:}
+\begin{itemize}
+	\item Although in principle we can identify the parameter using MLE using above expression, but the computation burden is huge.
+As we have pointed out, the number of possible combinations of potential entrants and actual entrants are $C_n^k$, which grows very fast.
+	To solve this problem, this paper takes two approaches.
+	\begin{itemize}
+		\item Put more restrictions over the parameters
+		\item Use SMM
+	\end{itemize}
+	We focus on the second approach.
+
+	\item \textcolor{blue}{[SMM]}
+	First we generate a series of $\hat u_i$, then given $\theta$, we can calculate an estimate $\hat N$ for each market, with the property:
+	\[E_{\hat u}[\hat N(W_i,\theta,\hat u)] = E[N^*|W_i,\theta]\]
+	So we can write the moment condition as:
+	\[v_{io}(N_i^*,W_i,\theta)\equiv N^*_i-E_{\hat u}[\hat N(W_i,\theta,\hat u)]\]
+	Estimating this moment condition will give us consistent $\theta$.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Empirical Results:}
+\begin{itemize}
+	\item Firm observable heterogeneities, such as airport presence, play an important role in determining airline profitability.
+
+	\item Profits decline rapidly in the number of entering firms, consistent with \cite{Bresnahan:1990gw}.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Pros:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item The unobserved term $u_{ik}$ and $u_{io}$ are assumed to be i.i.d. across both firms and markets.
+	Especially, $u_{ik}$ are more likely to be correlated across markets for a given firm.
+
+	\item The heterogeneity is assumed to be a very specific term, which only affects the ``fixed cost'' of firms.
+Conditional on firm entering, the subsequent subgame is symmetric.
+This restriction is quite strong.
+\end{itemize}
+
+% subsection berry_92_emca (end)
+
+\section{Seim, 06 RAND} % (fold)
+\label{sec:seim_06_rand}
+
+\textbf{\bibentry{Seim:2006em}}
+
+\vspace{1em}
+\noindent
+\textbf{Highlights of the Paper:}
+\begin{itemize}
+	\item By introducing private information and using Bayesian Nash Equilibria, the strategy of each firm is a mapping from its own type $c_i$ to a strategy $s_i$, which does not directly depend on other firms' strategies.
+	This ensures the uniqueness of equilibrium in the specific setting of this paper, but uniqueness is not guaranteed in general.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Model:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Empirical Results:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Pros:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item Charlie Murry points out that the result is somewhat directly being assumed.
+The potential number of entrants $\mathcal F$ is being assumed, but if we assume this and we know the actual entrant number $\mathcal E$, isn't the probability of entrant directly derived?
+\end{itemize}
+
+\section{Davis, 06 JoE} % (fold)
+\label{sec:davis_06_joe}
+
+\textbf{\bibentry{Davis:2006kn}}
+
+\vspace{1em}
+\noindent
+\textbf{Highlights:}
+\begin{itemize}
+	\item This paper is a natural generalization of \cite{Berry:1992gl}.
+Berry guarantees the uniqueness of entering firms using assumption of ``separable profit function'' and ``symmetric second stage competition''.
+	This paper relaxes the assumptions by supermodularity conditions.
+
+	\item Under his assumptions, this paper guarantees: 1) existence of PSNE; 2) the uniqueness of market index (number of entering firms in Berry's model) within PSNE.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Model:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Empirical Results:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Pros:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+% subsection subsection_name (end)
+
+% subsection seim_02_rand (end)
+
+\section{Jia, 08 EMCA} % (fold)
+\label{sec:jia_08_emca}
+
+\textbf{\bibentry{Jia:2008fz}}
+
+\vspace{1em}
+\noindent
+\textbf{Highlights of the Paper:}
+\begin{itemize}
+	\item Jia's paper does not investigate the crowdness of stores in one market.
+It focuses on the distribution of stores across the country.
+In Jia's market segmentation, each brand will put at most one store in each market.
+So the whole story is about how to allocate stores in different markets, instead of how many stores in one market.
+\end{itemize}
+
+% subsection jia_08_emca (end)
+
+\section{Tamer, 03 RES} % (fold)
+\label{sec:tamer_03_res}
+
+\textbf{\bibentry{Tamer:2003hi}}
+
+\mytitle{Highlights:}
+\begin{itemize}
+	\item This paper shows that ``games with multiple equilibria can be estimated without imposing coherency conditions if the model is used only to inform upper and lower bounds on the probabilities of outcomes rather than assigning exact probabilities to each potential outcome.'' \citep{Davis:2006kn}
+
+	\item This paper differentiates \textbf{incoherent model} with \textbf{incomplete model}.
+	\textit{Incoherency} comes from the not well defined optimization problem of the agent; while \textit{incomplete} econometric models means that the mapping from $(x,u)$ to $y$ is not a function but a correspondence.
+
+	\item The paper also shows, the parameter of an incomplete model can be \textbf{point identified}, as long as we have at least one exogenous variable with unbounded range.
+This is called identification at infinity.
+\end{itemize}
+
+\mytitle{Identification:}
+\begin{itemize}
+	\item For a model like in \cite{Bresnahan:1990gw}:
+		\[\begin{array} { l } { y _ { 1 }= x _ { 1 } \beta _ { 1 } + y _ { 2 } \Delta _ { 1 } + u _ { 1 } } \\ { y _ { 2 } = x _ { 2 } \beta _ { 2 } + y _ { 1 } \Delta _ { 2 } + u _ { 2 } } \end{array}\]
+
+	\item If there is one exogenous variable (exclusively) on $x_1$ or $x_2$ that can take value at infinity, then the parameter is point identified.
+The idea is simple, say $x_{1k}$ takes $-\infty$ and $\beta_{1k}$ is positive, then firm 1 will not enter the market for sure regardless of $(u_1,u_2)$.
+Thus all other parameters can be point identified using this subsample.
+
+	\item {[$\beta$ Identification]} Take $x_{1k}$ to $-\infty$:
+	\begin{align}
+	\operatorname { Pr } [ ( 0,0 ) | x _ { 1 } , x _ { 2 } ^ { * } ] = \operatorname { Pr } \left[ u _ { 1 } \leq - x _ { 1 } \beta _ { 1 } , u _ { 2 } \leq - x _ { 2 } ^ { * } \beta _ { 2 } \right] & \neq \operatorname { Pr } \left[ u _ { 1 } \leq - x _ { 1 } b _ { 1 } , u _ { 2 } \leq - x _ { 2 } ^ { * } b _ { 2 } \right] \\
+	& 
+	\end{align}
+	the inequality is from:
+	\[\begin{aligned} \operatorname { Pr } \left[ u _ { 1 } \leq - x _ { 1 } \beta _ { 1 } , u _ { 2 } \leq - x _ { 2 } ^ { * } \beta _ { 2 } \right] & \simeq \operatorname { Pr } \left[ u _ { 2 } \leq - x _ { 2 } ^ { * } \beta _ { 2 } \right] \neq \operatorname { Pr } \left[ u _ { 2 } \leq - x _ { 2 } ^ { * } b _ { 2 } \right] \\ & \simeq \operatorname { Pr } \left[ u _ { 1 } \leq - x _ { 1 } b _ { 1 } , u _ { 2 } \leq - x _ { 2 } ^ { * } b _ { 2 } \right] \end{aligned}\]
+	Thus $\beta_2$ is identified. Given $\beta_2$, we can identify $\beta_1$ since $x_1$ is full rank.
+
+	\item {[$\Delta$ Identification]} The identification of $\Delta$ is similar to that of $\theta$. The difference is that we now use $(y_1,y_2) = (1,1)$ instead of $(0,0)$.
+	\begin{align}
+		\Pr[(1,1) | x_1, x_2^*] = \Pr(u_1 > -x_1\beta_1 - \Delta_1, 
+		u_2 > - x_2\beta_2 - \Delta_2) \neq \Pr(u_2 > -x_2\beta_2 -d_2)
+	\end{align}
+
+	\item Only observations of $(0,0)$ and $(1,1)$ are necessary for identification. The main point to use $(0,1)$ and $(1,0)$ is to increase efficiency with finite data.
+\end{itemize}
+
+\mytitle{Semi-Parametric Estimation:}
+\begin{itemize}
+	\item Define the population frequency of $(0,1)$ to be $H(\cdot)$:
+	\[H ( x ) = \operatorname { Pr } [ ( 0,1 ) | x ]\]
+	and the quasi-likelihood can be defined as:
+	\[\begin{aligned} L \left( b ; \hat { H } _ { t n } \right) = & \sum _ { i = 1 } ^ { n } \left[ y _ { i 1 } y _ { i 2 } \log \left( P _ { 1 } \left( x _ { i } , b \right) \right) \right.
+\\ & + \left( 1 - y _ { i 1 } \right) \left( 1 - y _ { i 2 } \right) \log \left( P _ { 2 } \left( x _ { i } , b \right) \right) + \left( 1 - y _ { i 1 } \right) y _ { i 2 } \log \left( \hat { H } _ { t n } \left( x _ { i } , b \right) \right) \\ & + y _ { i 1 } \left( 1 - y _ { i 2 } \right) \log \left( 1 - P _ { 1 } \left( x _ { i } , b \right) - P _ { 2 } \left( x _ { i } , b \right) - \hat { H } _ { t n } \left( x _ { i } , b \right) \right) ] \end{aligned}\]
+	where $P_1, P_2$ can analytically be derived and $H$ is non-parametrically estimated.
+	\item The SML $\beta$ is consistent and normally distributed (in BR case).
+\end{itemize}
+% subsection tamer_03_res (end)
+
+\section{Ciliberto and Tamer, 09 RES} % (fold)
+\label{sec:ciliberto_and_tamer_09_res}
+
+\textbf{\bibentry{Ciliberto:2009hy}}
+
+\vspace{1em}
+\noindent
+\textbf{Highlights of the Paper:}
+\begin{itemize}
+	\item This paper has two contributions to entry game estimation literature.
+First, it allows very general form of firm heterogeneity; second, by adopting partial identification it makes no assumption on equilibrium selection.
+
+	\item {[Firm Heterogeneity]} Recall that in \cite{Berry:1992gl}, the only heterogeneity is a heterogeneous ``fixed cost'', which enters linearly.
+If we allow more general form of heterogeneity, then even the number of entrants is not unique.
+
+	\item {[Multiple Equilibria]} The estimation procedure allows mixed strategy.
+But this will make the equilibrium solving process more difficult.
+The model \textbf{does not specify or estimate any equilibrium selection rule} ($\Pr(y|\varepsilon,X)$ in the paper).
+In principle this can be estimated, either non-parametrically (as in \cite{Tamer:2003hi}) or as a function of $\varepsilon$ and $X$ (as in Berry and Tamer (2006)).
+This makes the identified set not sharp, but the computation much easier.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Model:}
+\begin{itemize}
+	\item The profit function for firm $i$ in market $m$ is:
+	\[\pi_{im}=S'_m\alpha_i + Z'_{im}\beta_i+W'_{im}\gamma_i+
+	\textcolor{blue}{\sum_{j\neq i }\delta^i_j y_{jm}+\sum_{j\neq i}Z'_{jm}\phi^i_j y_{im}}
+	+\varepsilon_{im}\]
+	where $S_m$ is market characteristics; $W_{im}$ is the firm characteristics that will only affect its own profit in market $m$, such as cost variables; $Z_{im}$ is the firm characteristics that may affect both own and others profit.
+	$\sum_{j\neq i }\delta^i_j y_{jm}$ captures the effect of other firm's entering, and $\sum_{j\neq i}Z'_{jm}\phi^i_j y_{im}$ further captures the effect of entering firms' characteristics.
+	\begin{itemize}
+		\item Notice that the impact of other firms can be directly dependent on firm identity.
+		For a specific firm $i$, having $j$ or having $k$ in the market may impact $i$'s profit differently, even if $j$ and $k$ has same characteristics on this market.
+	\end{itemize}
+
+	\item {[Main Idea]} Conditional on observables, although we cannot calculate \textit{the probability} of a entering profile $y$ if multiple equilibria exist, but we can get the \textit{bound} of probabilities.
+	\begin{align}
+		& \underline \Pr(y) = \Pr(\vec \varepsilon | \text{ y is the unique equilibrium}) \notag \\
+	& \overline \Pr(y) = \Pr(\vec \varepsilon | \text{ y is among the equilibria})
+	\end{align}
+
+	\item {[Identification]} The identified set $\Theta_I$ contains all $\theta$'s s.t. the \textit{all moment inequalities} hold. 
+	Point identified at infinite exogenous variable, see \cite{Tamer:2003hi}.
+	In practical estimation, variation in excluded exogenous variables (like the airport presence or cost variables in this paper) help shrink the set $\Theta_I$.
+\end{itemize}
+
+\mysubtitle{Estimation:}
+\begin{itemize}
+	\item The estimation is based on the moment inequalities:
+	\begin{align}
+		\mathbf { H } _ { 1 } ( \boldsymbol { \theta } , \mathbf { X } ) \equiv \left[ \begin{array} { c } { H _ { 1 } ^ { 1 } ( \boldsymbol { \theta } , X ) } \\ { \vdots } \\ { H _ { 1 } ^ { 2 K } ( \boldsymbol { \theta } , X ) } \end{array} \right] \leq \left[ \begin{array} { c } { \operatorname { Pr } \left( \mathbf { y } _ { 1 } | X \right) } \\ { \vdots } \\ { \operatorname { Pr } \left( \mathbf { y } _ { 2 ^ { K } } | X \right) } \end{array} \right] \leq \left[ \begin{array} { c } { H _ { 2 } ^ { 1 } ( \boldsymbol { \theta } , X ) } \\ { \vdots } \\ { H _ { 2 } ^ { 2 ^ { K } } ( \boldsymbol { \theta } , X ) } \end{array} \right] \equiv \mathbf { H } _ { 2 } ( \boldsymbol { \theta } , \mathbf { X } )
+	\end{align}
+	The objection function is:
+	\[Q ( \boldsymbol { \theta } ) = \int \left[ \left\| \left( P ( \mathbf { X } ) - H _ { 1 } ( \mathbf { X } , \boldsymbol { \theta } ) \right) - \right\| + \left\| \left( P ( \mathbf { X } ) - H _ { 2 } ( \mathbf { X } , \boldsymbol { \theta } ) \right) _ { + } \right\| \right] d F _ { x }\]
+	Notice that $\mathbf H_1$ and $\mathbf H_2$ cannot be analytically derived in a complicated game, and have to be estimated by simulation.
+
+	\item {[$\Theta_I$ or $\theta_I$]} When doing infernece, the interest is either the identified set $\Theta_I$ or the true parameter $\theta_I \in \Theta_I$.
+Note that there is one true $\theta_I$ even if  $\Theta_I$ is only set identified (e.g.
+when the unbounded exclusion variable $x$ is not available).
+\end{itemize}
+
+\mysubtitle{Empirics:}
+\begin{itemize}
+	\item \red{To be added: the use of hub airports}
+	\item \red{To be added: the marginal effect table}
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item The identified set is not sharp. \red{What is a sharp identified set?}
+
+	\item \red{Does the effect of other firms $\delta$ have to be negative?}
+\end{itemize}
+
+% subsection ciliberto_and_tamer_09_res (end)
+
+\section{Grieco, 14 RAND} % (fold)
+\label{sec:grieco_14_rand}
+
+\textbf{\bibentry{Grieco:2014hz}}
+
+\mytitle{Highlights:}
+\begin{itemize}
+	\item This paper integrate complete information entry game and incomplete information entry game in one model.
+The paper also tests the two polar case of complete information and incomplete information.
+
+	\item The intuition for the identification relies on instrument variable that affects private information but not public information.
+In the private information game, player 1's decision will not depend on private information $x_2$, because player 1 can only take into account public informations and make a guess on player 2's decision.
+	Contrary to this, private information $x_2$ will affect player 1's decision in a complete information game if the covariates support is rich enough.
+	Thus if we can find some instruments affecting private information $(x_1,x_2)$, we can identify complete and incomplete information. 
+\end{itemize}
+
+\mytitle{Model:}
+\begin{itemize}
+	\item The model is a two firm entry problem with binary decisions:
+	\[\pi _ { i } \left( y _ { i } , y _ { - i } ; x , \theta \right) = \left\{ \begin{array} { l l } { x _ { i } \theta _ { i \mu } + y _ { - i } x _ { i } \theta _ { i \delta } + \epsilon _ { i } + v _ { i } } & { \text { if } y _ { i } = 1 } \\ { 0 } & { \text { if } y _ { i } = 0 } \end{array} \right.\]
+	where the $\varepsilon_i$ represents public shock, and $\mu_i$ is private shock.
+	The public shocks $(\varepsilon_1, \varepsilon_2)$ follows bivariate normal, with common variance component $\sigma^2_\varepsilon$ and correlation coefficient $\rho$.
+	Private shocks are independent and have variance $\sigma^2_\mu \equiv 1- \sigma^2_\varepsilon$.
+	$\sigma^2_\varepsilon$ controls relative importance of public shocks.
+
+	\item The equilibrium of this model is:
+	\[\chi _ { i } ^ { b } \left( \chi _ { j } , \epsilon , x ; \theta \right) = - \left( x _ { i } \theta _ { i \mu } + \varrho _ { j } \left( \chi _ { j } , \epsilon ; \theta \right) x _ { i } \theta _ { i \delta } + \epsilon _ { i } \right)\]
+	where the left is the threshold of player $i$ to enter, and $\varrho_j$ is the expected probability of $j$ to enter, conditional on $j$'s threshold.
+	Any joint set $\chi = \left( \chi _ { 1 } , \chi _ { 2 } \right)$ satisfies the above equation will be an equilibrium.
+
+	\item {[Multiplicity]} Note that even with incomplete shock only, there may exist multiple equilibria.
+Though each player will play a threshold strategy, the values of thresholds are coordinated.
+Note the difference with \cite{Seim:2006em}.
+
+	\item Grieco finds that the area of multiplicity shrinks as the information environment becomes more and more incomplete. See their Fig 1.
+\end{itemize}
+
+\mytitle{Identification:}
+\begin{itemize}
+
+	\item {[Only Private Shock Case]} The probability of observing outcome $y$ given a selected equilibrium $e$ is:
+	\[\tilde { \Psi } ( y | x , \theta , e ) = \prod _ { i = 1 } ^ { 2 } \varrho _ { i } ^ { e } ( x , \theta ) ^ { 1 \left[ y _ { i } = 1 \right] } \left( 1 - \varrho _ { i } ^ { e } ( x , \theta ) \right) ^ { 1 \left[ y _ { i } = 0 \right] }\]
+	Unconditional on equilibrium, it can be represented as:
+	\[\Psi ( y | x , \theta , \lambda ) = \sum _ { e \in \delta ( x , \theta ) } \lambda ^ { e } ( x , \theta ) \tilde { \Psi } ( y | x , \theta , e )\]
+	where $\lambda^e$ is the equilibrium selection rule and can be jointly estimated. See \cite{Tamer:2003hi} semi-parametric estimation routine.
+	The sharp identified set is:
+	\[\Theta _ { I } = \left\{ \begin{aligned} \theta \in \Theta : \forall y , x , \exists \tilde { \lambda } \in [ 0,1 ] ^ { \overline { E } } \text { s.t.
+} & P ( y | x ) = \Psi ( y | x , \theta , \tilde { \lambda } ) \\ & \sum _ { e \in \mathcal { E } ( x ; \theta ) } \tilde { \lambda } ^ { e } = 1 \end{aligned} \right\}\]
+	\red{How we are going to estimate this? are the set convex or something?}
+\end{itemize}
+
+\mytitle{Inference}
+\begin{itemize}
+	\item This paper uses a sieve based weighted Bootstrap to do inference. But Karl says there is something wrong with this approach. Not sure about this.
+\end{itemize}
+
+% section grieco_14_rand (end)
+
+\section{Holmes, 11 EMCA} % (fold)
+\label{sec:holmes_2011_emca}
+
+\mytitle{Estimation}
+
+\mysubtitle{Disagregate Inequalities v.s. Aggregate Inequalities}
+
+Why not using disaggregate inequalities which will generate more moment inequalities? Because there is measurement error. Suppose the model is:
+\[y_a \geq \theta\]
+but the LHS is is observed with error:
+\[\tilde y_a = y_a + \eta_a\]
+If we pick $\theta$ to minimize the disaggregated inequalities, then we are looking for $\theta$ that satisfies:
+\[\left\{\theta | \theta \leq \min_{a}\{y_a+\eta_a\}\right\}\]
+and some very extreme $\eta_a$ will drive the results.
+% section holmes_2011_emca (end)
+
+% subsection ellickson_houghton_timmins_13_rand (end)
+
+\section{Lee and Pakes, 09 EL}
+\label{sec:lee_pakes_09_el}
+
+There is multiplicity problem in counterfactual analysis of entry game. This paper discusses two possible ways of dealing multiple equilibria.
+
+\mytitle{Enumerating Equilibria}
+
+The first approach just enumerate all possible limiting equilibria, and then compare them. 
+The equilibria are limiting in the sense that all firms know the expected value of the cost shock.
+The good news is, there are only a handful of possible equilibria in their case.
+
+\mytitle{Equilibria Selection by Learning}
+
+Based on previous enumeration results, we can apply learning process to see which equilibrium is more possible. There are two possible learning processes:
+\begin{itemize}
+	\item {[Best Response Dynamics]} Firm believes its competitors will play the same strategy as they did in the prior period, and thus each firm will play its best response to last periods' play.
+
+	\item {[Fictitious Play]} Each firm believes that the next play of its competitors will be a random draw from the set of tuples of plays observed since the regime change, and chooses it's optimal strategy accordingly.
+(KZ: the optimal should be mix?)
+\end{itemize}
+
+To get the distribution of equilibria, they compute 1000 runs for each learning process.
+Each run is stopped when they converged to a single allocation profile, where convergence is defined as having remained in the same state for 50 iterations.
+
+\section{Wollman, 18 AER} % (fold)
+\label{sec:wollman_18_aer}
+
+\mytitle{Identification}
+
+The identification of the second stage is a standard BLP, I will focus on the identification of the first step about the fixed costs.
+
+The inequalities based on rationality condition is:
+\[\begin{array}{l}{\Delta \pi\left(J_{f, t}, J_{f, t} \backslash j, J_{-f, t}, z_{t}, w_{t}\right)} \\ {\quad+x_{j}^{\prime}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right) \mathscr{E}\left[\theta_{f, x_{j}, t} | \mathscr{J}_{f, t}\right] \geq 0}\end{array} \tag{6}\]
+\[\begin{array}{l}{\Delta \pi\left(J_{f, t}, J_{f, t} \cup j, J_{-f, t}, z_{t}, w_{t}\right)} \\ {-x_{j}^{\prime}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right) \mathscr{E}\left[\theta_{f x_{j}, t} | \mathscr{I}_{f, t}\right] \geq 0}\end{array} \tag{7}\]
+
+Note that $\mathcal E [\theta_{f,x_j,t}|\mathcal F_{f,t}]$ is unknown to econometricians, thus we need to parameterize it and convert the inequalities to some observable moments. By parameterization:
+\[\theta_{f}=\left[\theta_{0}+\theta_{0}^{B i g 3}+\theta_{0}^{J p n}, \theta_{g}+\theta_{g}^{B i g 3}, \theta_{c a b o v e r}+\theta_{c a b o v e r}^{J p n}, \theta_{c o m p a c t}, \theta_{l o n g}\right]\]
+and the suck cost parameter $\theta_{f,x_j,t} \equiv \theta_f + \nu_{2,t}$.
+Notice that the structural error $\nu_{2,t}$ is a vector, with each element indexing a characteristic error.
+To rationalize data, we need to introduce structural error $\nu_{2,t}$ and expectation error $\nu_{1,t}$.
+\begin{itemize}
+	\item $\nu_2$ is known to the firms when making entry decision, but unknown to econometricians
+	\item $\nu_1$ is unknown to firms when making entry decision
+\end{itemize}
+
+The actual moment inequalities for estimation are:
+\[\begin{array}{l}{\frac{1}{X T F} \sum_{x_{j}} \sum_{t} \sum_{f} h_{f, x, t}^{i}\left\{j \in J_{f, t}\right\}} \\ { \times\left[\Delta \hat{\pi}\left(J_{f, t}, J_{f, t} \backslash j, J_{-f, t}, z_{t}, w_{t}\right)+x_{j}^{\prime} \theta_{f}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right)\right] \geq 0}\end{array} \tag{8}\]
+\[\begin{array}{l}{\frac{1}{X T F} \sum_{x_{j}} \sum_{t} \sum_{f} h_{f, x_{j}, t}^{i}\left\{j \notin J_{f, t}\right\}} \\ { \times\left[\Delta \hat{\pi}\left(J_{f, t}, J_{f, t} \cup j, J_{-f, t}, z_{t}, w_{t}\right)-x_{j}^{\prime} \theta_{f}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right)\right] \geq 0}\end{array} \tag{9}\]
+In appendix, the empirical moment is shown to converge in probability to:
+\begin{align*}
+	\stackrel{p}{\rightarrow} & E_{x_{j}, t, f}\left[h_{f, x_{j}, t}^{i}\left\{j \in J_{f, t}\right\} \Delta \pi\left(J_{f, t}, J_{f, t} \backslash j, J_{-f, t}, x_{t}, w_{t}\right)\right] \\
+	& +E_{x_{j}, t, f}\left[h_{f, x_{j}, t}^{i}\left\{j \in J_{f, t}\right\}\left[x_{j}^{\prime}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right) \mathscr{E}\left[\theta_{f, x_{j}, t} | \mathscr{F}_{f, t}\right]\right]\right] \\
+	& +E_{x_{j}, t, f}\left[h_{f, x_{j}, t}^{i}\left\{j \in J_{f, t}\right\}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right) \nu_{1, f, t, J_{f, t}, J_{f, t} \backslash j, J_{f, t-1}}\right] \\
+	& -C E_{x_{j}}\left[x_{j}^{\prime} h_{f, x_{j}}^{i} E_{t}\left[h_{x_{j}, t}^{i} \nu_{2, t}\right]\right] \geq 0
+\end{align*}
+The first two lines larger than 0 by rationality assumption, the third line is 0 in expectation since $\nu_1$ is mean independent of agents' information set.
+The forth line is tricky, and we need to pick $h^i$ to make it zero in expectation.
+
+Things to be noted here:
+\begin{enumerate}
+	\item $\mathcal E$ represents agent's subjective expectation, and $E$ is the expectation by actual DGP.
+	\item The unobservable $\mathcal E[\theta_{f,x_j,t}]$ has been substituted by parameter $\theta_f$. We have to take care of $\nu_2$ because it may induce selection problem.
+	\item $h_{f, x_{j}, t}^{i}\left\{j \notin J_{f, t}\right\}$ is used as instruments and to control the endogenous problem induced by $\nu_2$.
+\end{enumerate}
+
+% section wollman_18_aer (end)
+
+% section entry_and_exit (end)
+
+\chapter{Dynamic Decisions} % (fold)
+\label{cha:dynamic_decisions}
+
+\section{Rust, 87 EMCA} % (fold)
+\label{sec:rust_87_emca}
+
+\textbf{\bibentry{Rust:1987hn}}
+
+\vspace{1em}
+\noindent
+\textbf{Highlight of the Paper:}
+\begin{itemize}
+	\item This is the seminal paper to estimate a dynamic model.
+	A very clever trick is separating $EV_\theta$ with a Bellman function, which greatly reduces the dimension since $\varepsilon$ is not an argument of $EV$.
+
+	\item But the computation burden is still heavy, because for every $\theta$ we need to solve a contraction mapping. \cite{Hotz:1993ea} eases the computation using SMM.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Structural Estimation without Closed-form Solutions:}
+\begin{itemize}
+	\item The decision maker has the following value function:
+	\[V_\theta(x_t,\varepsilon_t)=
+	\sup_\Pi E\Big\{
+	\sum_{j=t}^{\infty} \beta^{j-t}[u(x_j,f_j,\theta_1)
+	+\varepsilon_j(f_j)] | x_t,\varepsilon_t,\theta_2,\theta_3
+	\Big\}\]
+	where $f_t(x_t,\varepsilon_t,\theta)$ is the optimal control function. The transition rule is:
+	\[dp\{x_{t+1},\varepsilon_{t+1},\dots,
+	x_{t+N},\varepsilon_{t+N}\}
+	=\prod_{i+t}^{N-1}p(x_{i+1},\varepsilon_{i+1}
+	| x_i,\varepsilon_i,f_i(x_i,\varepsilon_i),\theta_2,\theta_3)\]
+	This infinite horizon problem can be rewritten as a Bellman function with stationary decision rule:
+	\[V_\theta(x_t,\varepsilon_t)=
+	\max_{i \in C(x_i)}
+	[u(x_i,i,\theta_1)+\varepsilon_t(i)+\beta
+	E V_\theta(x_t,\varepsilon_t,i)]\]
+
+	where
+	\[EV_\theta(x_t,\varepsilon_t,i)=
+	\int_y \int_\eta V_\theta(y,\eta)
+	p(dy,d \eta|x_t,\varepsilon_t,i,\theta_2,\theta_3)\]
+	One property (difficulty) of this model is that distribution of $\varepsilon_{t+1}$ is conditional on $i$ and $\varepsilon_t$.
+So $EV_\theta$ is a nonlinear function of $\varepsilon_t$, which would induce huge dimensionality problem in value function iteration.
+	\begin{itemize}
+		\item This model is actually a simple version of Cooper's general durable consumption problem.
+The key is that $\{x_t\}$ follows different transition rule after different action $i$.
+This problem is actually simpler because the only decision variable is $i$.
+	\end{itemize}
+
+	\item \textcolor{blue}{[Conditional Independence Assumption]}
+	To make this problem computationally tractable, we assume:
+	\[p(x_{t_1},\varepsilon_{t+1}|x_t,\varepsilon_t,i,\theta_2,\theta_3)=
+	q(\varepsilon_{t+1}|x_{t+1},\theta_2)p(x_{t+1}|x_t,i,\theta_3)
+	\]
+	This assumption says, the transition of $(x_t,\varepsilon_t)$ is separable.
+Probability of $\varepsilon_{t+1}$ only directly depends on $x_{t+1}$, and the transition of $x_{t+1}$ is independent of current $\varepsilon_t$.
+	That's to say, $\varepsilon_t$ is like a temporary disturbance on $x_t$.
+
+	\item \textcolor{blue}{[Below Important]}
+	The power of above assumption is that we now can solve $EV_\theta$ in a contraction mapping $T_\theta$
+	(the proof is not trivial):
+	\[EV_\theta(x,i)=\int_y G(u(y,\theta_1)+\beta EV_\theta(y)|y,\theta_2)\cdot p(dy|x,i,\theta_3)\]
+	where $V_\theta(x)$ actually is $\max\{V_\theta(x,0),V_\theta(x,1)\}$, and
+	\[G(u(x,\theta_1)+\beta EV_\theta(x)|x,\theta_2)
+	= \int_\varepsilon \max_{j \in C(x)}
+	[u(x,j,\theta_1)+\beta EV_\theta(x,j)]
+	q(d \varepsilon|x,\theta_2)\]
+	And the conditional probability of choosing choice $i$ is given by:
+	\[P(i|x,\theta)=G_i(u(x,\theta_1)+\beta EV_\theta(x)|x,\theta_2)\]
+	Now we can define the likelihood function: (directly from conditional independence assumption)
+	\[\mathcal{L}^f(x_1,i_1,\dots,x_T,i_T|x_0,i_0,\theta)=
+	\prod_{t=1}^{T}P(i_t|x_t,\theta)p(x_t|x_{t-1},i_{t-1},\theta_3)\]
+	\begin{itemize}
+		\item The transition rule parameter $\theta_3$ can be separately estimated. 
+	\end{itemize}
+
+	\item \textcolor{blue}{[Nested Fixed Point Algorithm]}
+	An inner fixed point algorithm solves $EV_\theta$ for each value of $\theta$; 
+	an outer algorithm captures $\theta$ that maximizes the likelihood.
+	\begin{itemize}
+		\item To estimate $EV_\theta$, we need to further assume that $\varepsilon$'s are i.i.d. distributed across choices and time according to T1EV.
+		With this assumption, we have:
+		\begin{align*}
+		EV_\theta(x,i)& \equiv E_{y,\varepsilon|x,i}
+		\Big\{\max_{j=0,1}[u(y,\varepsilon;\theta)+\beta EV(y,j;\theta)]
+		\Big\} \\
+		&=E_{y|x,i}\log \Big\{
+		\sum_{j=0,1} \exp[u(y,\varepsilon;\theta)+\beta EV(y,j;\theta)]
+		\Big\}\\
+		&= \int_y log \Big\{
+		\sum_{j=0,1}\exp[u(y,j;\theta)+\beta EV(y,j;\theta)]
+		\Big\}p(dy|x,i)
+	\end{align*}
+	The second equality uses the closed form of maximization over expectation of T1EV.
+	\footnote{See \cite*{Chiong:2016ga} for details.}
+
+	\item Once $EV_\theta(x,i)$ has been calculated using value function iteration, the choice probability $p(i_t|x_t)$ can be computed as:
+	\[\frac{\exp(E_\varepsilon u(x_t,\varepsilon, i_t;\theta)+
+	\beta EV(x,i;\theta))}
+	{\sum_{i=0,1}\exp(E_\varepsilon u(x_t,\varepsilon, i_t;\theta)+
+	\beta EV(x,i;\theta))}\]
+
+	\item Once we get $EV_\theta(x,i)$, then we can get $P(i_t|x_T,\theta)$.
+And since the transition rule $p(x_t|x_{t-1},i_{t-1},\theta_3)$ can be separately estimated.
+We now have collected all components of the likelihood function.
+Loop over $\theta$ to maximize the likelihood function.
+	\end{itemize}
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Empirical Results:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Pros:}
+\begin{itemize}
+	\item The \textit{Conditional Independence} assumption of $\varepsilon$ is very important.
+With this assumption, the $\varepsilon_T$ becomes a perturbation of $x_t$ and independent of everything else.
+	So although $\varepsilon$ is still a state variable of $V$, it is no longer a state variable of $EV$. 
+	Then we can first solve $EV(x)$ by Bellman iteration.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item The inner fixed point loop is computationally burdensome.
+And the complexity will significantly grow if we add more state variables.
+\cite{Hotz:1993ea} uses an inversion function to avoid the Bellman iteration.
+\end{itemize}
+
+% subsection rust_87_emca (end)
+
+% section dynamic_decisions (end)
+
+\section{Hotz and Miller, 93 RES} % (fold)
+\label{sec:hotz_and_miller_93_res}
+
+\textbf{\bibentry{Hotz:1993ea}}
+
+\vspace{1em}
+\noindent
+\textbf{Highlights of the Paper:}
+\begin{itemize}
+	\item The main idea of this paper is to \textbf{ease the computation burden} of calculating the value function in \cite{Rust:1987hn}.
+	HM shows that value function can be represented in terms of choice probabilities, transition probabilities and expected per period payoffs. This hinges on the \textbf{
+	\textcolor{blue}{invertibility}} similar in BLP.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Model:}
+\begin{itemize}
+	\item The model uses a similar framework as \cite{Rust:1987hn}. The agent is solving a single agent dynamic programming problem, the choice set is from $1,\dots,J$.
+	Denote the history to be $H_t$, which is a collection of period outcomes $b_t\in \R$, where $b_t$ is affected by choice $d_t$. The history is generated according to the transition probabilities:
+	\[F_j(H_{t+1}|H_t)\]
+	\begin{itemize}
+		\item $H_t$ is the state variable here, corresponding to $x_t$ in Rust paper. The transition rule is exogenous conditional on decision.
+	\end{itemize}
+	In each period $t$, there is a current utility $u_{tj}$ associated with each choice $j$. Let $u^*_t(H_t)=E(u_{tj}|H_t)$.
+	\[u_{tj}=u^*_j(H_t)+\varepsilon_{tj}\]
+	\begin{itemize}
+		\item Notice that by construction $\varepsilon_t$ conditional on history $H_t$ is independent of other $\varepsilon_{t'}$.
+The \textit{conditional independence} assumption in \cite{Rust:1987hn} is implicitly assumed.
+	The state variable $x_t$ in Rust paper is included in $H_t$. Also, $\varepsilon_{tj}$ is known to the agent.
+	The distribution of $\varepsilon_t$ is $G(\varepsilon_t|H_t)$.
+	\end{itemize}
+	The agent chooses a sequence $\{d_t\}_t\in T$ to maximize summed discounted utility.
+
+	Denote $p_k(H_t)$ to be the probability of choosing action $k$ at history, and $p(H_t)$ be a $(J-1)$ vector of conditional choice probability function.
+
+	\item 
+	Due to the conditional independence condition, we can write the probability of choosing choice 1:
+	\begin{align*}
+	p_1(H_t)&=E(d_{t_1}=1|H_t) \\
+	&=\int_{\varepsilon_1=-\infty}^\infty \int_{\varepsilon_2=-\infty}^{\varepsilon_1+u^*_{11}-u^*_{12}+v_{t1}-v_{t2}}\dots \int_{\varepsilon_J=-\infty}^{\varepsilon_1+u^*_{11}-u^*_{1J}+v_{t1}-v_{tJ}} dG(\varepsilon_1,\dots,\varepsilon_J|H_t) \\
+	&= \int_{-\infty}^{\infty}G_1(\varepsilon_1,[\varepsilon_1+u^*_{11}-u^*_{12}+v_{t1}-v_{t2}],\dots,\varepsilon_1+u^*_{11}-u^*_{1J}+v_{t1}-v_{tJ}|H_t)d \varepsilon_1 \\
+	& \equiv Q_1(\tilde v,H_t)
+	\end{align*}
+	Similarly we can write $p_j(H_t)$ for each $j$.
+	Then if we denote $\tilde v = (v_{t1}-v_{tJ},\dots,v_{t,J-1}-v_{t,J}) \equiv \tilde v(H_t)$. 
+	We can write:
+	\[p(H_t)=Q(\tilde v(H_t),H_t)\]
+	\begin{itemize}
+		\item Notice that any $v_{t,j}-v(t,j')$ can be represented by two elements of $\tilde v$. $\tilde v$ just says that the scale of $v$ is unidentified.
+	\end{itemize}
+	The key idea of estimation is to express $\tilde v(H_t)$ as a function of $p(H_t)$. This requires $Q(\tilde v,H_t)$ being \textbf{invertible} in $\tilde v$ for every $H_t$.
+
+	\item KZ Guess: If $\tilde v$ can be expressed as function of $p(H_t)$, then we can use empirical $\hat p(H_t)$ to get empirical $\hat v$.
+If we further assume a functional form of $\varepsilon$ distribution to be F1EV, then we can get an estimated choice probability $\bar p$.
+Then we can use GMM to match $\hat p$ and $\bar p$.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Empirical Results:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Pros:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+% subsection hotz_and_miller (end)
+
+\section{Bajari-Benkard-Levin, 07 EMCA} % (fold)
+\label{sec:bajari_benkard_levin_07_emca}
+
+\textbf{\bibentry{Bajari:2007ky}}
+
+\vspace{1em}
+\noindent
+\textbf{Question of the Paper:}
+\begin{itemize}
+	\item This paper raises a two-stage algorithm for estimating dynamic games under the assumption of Markov Perfect Equilibria.
+	In first step, policy function and state variable transition rule are estimated.
+	In second step, remaining structural parameters are estimated.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{First Stage Estimation:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Second Stage Estimation:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Pros:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+% subsection bajari_benkard_levin_07_emca (end)
+
+\chapter{Asymmetric Information} % (fold)
+\label{cha:asymmetric_information}
+
+\section{Chiappori-Salanie, 00 JPE} % (fold)
+\label{sec:chiappori_salanie_00_jpe}
+
+\textbf{\bibentry{Chiappori:2000bu}}
+
+This is a first paper empirically testing \textit{asymmetric information}. The \textbf{\textcolor{blue}{pair probits methodology}} is important.\\
+
+\noindent
+\textbf{Identification:}
+\begin{itemize}
+	\item Suppose a pair probits system:
+	\[y_i = 1(X_i \beta +\varepsilon_i>0)\]
+	\[z_i = 1(X_i\gamma+ \eta_i>0)\]
+	where $y_i$ is the probability of choosing high coverage, and $z_i$ is the probability of accident.
+	If there is no asymmetric information, then we should have $\varepsilon_i$ and $\eta_i$ independent.
+	\textbf{
+	If there is positive correlation, indicates negative selection; if negative correlation, indicates advantageous selection.
+	}
+
+	\item We first estimate these two probits separately. Then it provides a way of testing independence.
+	\[W = \frac{\Big(\sum_{i=1}^n{\omega_i\hat \varepsilon_i \hat \eta_i}\Big)^2}
+	{\sum_{i=1}^n{\omega_i^2 \hat \varepsilon_i^2 \hat \eta_i^2}}\]
+	$W$ should follow a $\chi^2(1)$ distribution.
+	\footnote{This is why we use a probit system.} 
+	Where $\hat \varepsilon_i$ and $\hat \eta_i$ are generalized residuals.
+	\[\hat \varepsilon_i=
+	E(\varepsilon_i|y_i)=
+	\frac{\phi(X_i\beta)}{\Phi(X_i\beta)}y_i
+	-(1-y_i)\frac{\phi(X_i\beta)}{\Phi(-X_i\beta)}\]
+
+	\item We can modify the test to get estimation of correlation between $\varepsilon_i$ and $\eta_i$.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Empirical Results:}
+\begin{itemize}
+	\item Data: Car Insurance in France.
+	\item Conditioning on the subset of young drivers, no significant evidence for adverse selection.
+	\begin{itemize}
+		\item This paper strikes back Puelz and Snow (1994) in specific, which is criticized to suffer omitted observable variable problem.
+	\end{itemize}
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Pros:}
+\begin{itemize}
+	\item Data requirement is low. Only need the individual choice of coverage, and individual accident probability.
+	\begin{itemize}
+		\item Do not need premium information. Do not need exogenous price variation, which is needed in \cite*{Einav:2010hb}.
+	\end{itemize}
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item Cannot disentangle moral hazard, which may induce correlation as well.
+	\begin{itemize}
+		\item KZ: an ideal data will have $z_i$ data before and after the exogenous insurance coverage change. Then we can directly test moral hazard.
+	\end{itemize}
+	\item Only uses the coverage information, many other information about insurance (like premium, coinsurance rate) are not used.
+\end{itemize}
+
+% subsection chiappori_salanie_00_jpe (end)
+
+\section{Cardon-Hendel, 01 RAND} % (fold)
+\label{sec:cardon_hendel_01_rand}
+
+\textbf{\bibentry{Cardon:2001jf}}
+
+This paper sets up a two stage model to investigate the asymmetric information in health insurance market. The adverse selection mainly happens in the first stage.
+The do not find significant evidence for adverse selection.
+
+\vspace{1em}
+\noindent
+\textbf{Question of the Paper:}
+\begin{itemize}
+	\item Use a two-stage model to investigate the asymmetric information in health insurance market.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Model:}
+\begin{itemize}
+	\item Agent do a two stage model to decide consumption of health insurance in first stage, and health care consumption in second stage.
+
+	\item In second stage, given realized health state $s_i$ and  insurance policy $j$, each agent $i$ decides how much health care to consume:
+	\begin{gather*}
+	U_{ij}^*(s_i)=U^*(y_i,s_i,Z_j)=\max_{x_i}U(m_i,h_i)\\
+	s.t.\  m_i+C_j(x_i)=y_i-p_j
+	\end{gather*}
+	where $m_i$ is the consumption good and $h_i$ is the health consumption. $h_i=x_i+s_i$, i.e. health care and health state are perfect substitution.
+	$y_i$ is income, $p_j$ is premium of policy $j$, $C_j(x_i)$ is out of pocket money for consumption $x_i$ with policy $j$.
+
+	\item In first stage, the
+
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Empirical Results:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Pros:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+% subsection cardon_hendel_01_rand (end)
+
+\section{Einav-Finkelstein-Cullen, 10 QJE} % (fold)
+\label{sec:einav_finkelstein_cullen_10_qje}
+
+\textbf{\bibentry{Einav:2010hb}}
+
+\vspace{1em}
+\noindent
+\textbf{Main Contribution:}
+\begin{itemize}
+	\item Estimate the welfare loss caused by adverse selection with reduced form estimation. The key point for this approach is \textbf{exogenous price change}.
+	\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.4]{EFC_10qje_1.png}
+	\end{figure}
+
+	\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.4]{EFC_10qje_2.png}
+	\end{figure}
+
+	The adverse selection effect is totally represented by the downward sloping MC/AC curve. If it is advantageous selection, the MC/AC curve will be upward. 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Empirical Results:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Pros:}
+\begin{itemize}
+	\item This approach has very low demanding on data. Researchers only need \textit{exogenous price change} to get the MC and demand curve. Such change is easy to obtain in insurance industry.
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Cons:}
+\begin{itemize}
+	\item 
+\end{itemize}
+
+% subsection einav_finkelstein_cullen_10 (end)
+
+% section asymmetric_information (end)
+
+\chapter{Production Function Estimation} % (fold)
+\label{cha:production_function_estimation}
+
+There are several difficulties in estimating production functions which will cause endogeneity problem. To name some:
+\begin{itemize}
+	\item Simultaneity.
+For a production function like $y_{it}=\beta_0+\beta_1 k_{it}+\beta_2 l_{it} + \omega_{it}+\varepsilon_{it}$, we suppose that $\omega_{it}$ is obseved by firm but not by econometricians, and $\varepsilon_{it}$ is observed neither by firm nor econometricians.
+This could induce endogeneity when directly using OLS.
+	Suppose $\omega_{it}$ has \textit{positive serial correlation}, when $\omega_{it}$ is high, firm will choose higher input because it is very possible that $\omega$ in next period will be high as well.
+This induces a positive bias for $\beta_k$.
+	\item Exit selection bias. When constructing a balanced panel, then we only observe those firms with high $\omega_{it}$.
+	\textcolor{blue}{Why we have to construct a balanced panel?}
+\end{itemize}
+
+There are several approaches in solving this problem.
+
+\begin{itemize}
+	\item Classical Approach.
+	\begin{itemize}
+		\item Use input price as IV.
+The problem is input price is generally the same across firms.
+When we do observe different input prices, which generally indicates market power in input markets.
+Thus those facing higher $\omega_i$ will tend to produce more, inducing their input price to increase, which has a negative bias on $\beta_k$.
+		\begin{itemize}
+			\item (My comment) When using input price as IV, we actually assume they are independent of individual firm productivities.
+			This may not be the case.
+			If productivity has some correlation across the firms,
+			then it is possible that when productivity is high,
+			the input price in the market will also be high.
+		\end{itemize}
+		\item Use fixed effect. We need to assume that a firm faces same $\omega_{it}$ across time, which is not very practical.
+	\end{itemize}
+	\item Control Function for  $\omega_{it}$.
+This approach first raised by \cite{Olley:1996ef} and developed by \cite{Levinsohn:2003ej} and \cite*{Ackerberg:2015ha}.
+We name them OP, LP, ACF here after.
+The key idea is to use a function of what we know (for example, $k_t$ and $i_{t-1}$ in OP) to proxy $\omega$, the existence of such function is guaranteed by the solutioin property of the firm optimization problem.
+And the specific form of this function is estimated non-parametrically.
+	\begin{itemize}
+		\item OP uses a two step estimation process.
+First step, use $k_t$ and $i_{t}$ non-parametrically estimate $\omega_t$, plug this into original production function then use OLS.
+Notice the unobserved $\omega_t$ has been controlled by $k_t$ and $i_{t}$, then OLS will give consistent estimator for $l_t$ but not $k_t$.
+In second step, we first write $\omega_{it} = E[\omega_{it}|\omega_{it-1}]+\xi_{it}$, notice that $\xi_{it}$ is independent of any information set at t-1.
+Thus we get the moment condition $E[\xi_{it}k_{it}]=0$, then we can use method of simulating moments to estimate $\beta_k$.
+		\begin{itemize}
+			\item The key assumption in first step is, current period investment $i_t$ can be represented by a function of $f(k_t,\omega_t)$. 
+			If $f$ is invertible in $\omega_t$ (for example, $f$ being monotone in $\omega$), then we can write $\omega$ as a function of $(i_t, k_t)$.
+		\end{itemize}
+
+		\item LP is very similar to OP, just that use intermediate input $m_{it}$ instead of investment $i_{it}$ in proxy $\omega_{it}$.
+Because OP approach requires the policy function of $i_{it}$ be monotonicity in $\omega_{it}$, which is obviously unsatisfied when $i_{it}=0$.
+But data shows that in many observations $i=0$.
+Using intermediate input can solve this.
+
+		\item ACF criticizing is that $\beta_l$ cannot be identified in the first step.
+In LP we assume that $m_{it}=f_t(k_{it},\omega_{it})$.
+But we can reasonably argue by the same reason that $l_{it}=h_t(k_{it},\omega_{it})$.
+Then since $f(\cdot)$ is invertible, then we can write $l_t$ as some deterministic function of $k_{it}$ and $m_{it}$.
+This implies we cannot identify $\beta_l$ in the first step.
+The solution of ACF is to identify both $\beta_k$ and $\beta_l$ simultaneously at step 2, which is feasible since we now have two moment conditions.
+	\end{itemize}
+	\item \cite*{Gandhi:2017un} Approach (GNR).
+GNR criticizes control function approach is nonparametrically not identified in the presence of flexible inputs.
+They raise a new approach using FOC conditions.
+\end{itemize}
+
+% section production_function_estimation (end)
+
+\chapter{Multisided Platforms} % (fold)
+\label{cha:multisided_platforms}
+
+\textbf{\bibentry{Evans_Schmalensee:2012wp} }
+\begin{itemize}
+	\item Price structure matters. Reduce charge by one side and increase charge by another side will affect the transaction.
+	\item Transaction cost is necessarily high for multisided platform.
+	\item Two kind of externalities. Usage externality and membership externality.
+	\item Pricing is compelicated. Per-transaction fee, or membership-fee. \textcolor{blue}{This looks similar to conventional IO model.}
+	\begin{itemize}
+		\item In per-transaction fee case. Price is directly proportional to the elasticity, while in conventional models price is inversely related to elasticity.
+		\[\frac{p_1+p_2-c_1-c_2}{c_1+c_2}=\frac{1}{e_1+e_2}\]
+		\[\frac{p_1}{e_1}=\frac{p_2}{e_2}\]
+		Notice the second equation is unconventional.
+		\item In membership-fee case.
+		\item Both models can lead to a highly skewed price structure.
+	\end{itemize}
+	\item Competition Structure.
+	\begin{itemize}
+		\item Product differentiation
+		\item Multi-home.
+		\item Asymetric Competition.
+A n-sided platform may face competition from 1) one-sided firms; 2) a multisided platform competing in some but not all sides; 3) a multisided platform that has additional sides
+	\end{itemize}
+\end{itemize}
+
+\myline
+
+\textbf{Random Ideas}
+\begin{itemize}
+	\item Multisided platform as a commitment device changes the game structure.
+Like in the Truck-GasStation case raised in the book, the fleet-card company provides commitment power to the card companny, no renegotiation problem.
+\end{itemize}
+
+% section multisided_platforms (end)
+
+\chapter{Product Reviews} % (fold)
+\label{cha:product_reviews}
+
+\textbf{\bibentry{Berger:2010es}}
+
+\vspace{1em}
+\noindent
+\textbf{Question and Explanations:}
+\begin{itemize}
+	\item Why negative reviews may have positive effect on selling?
+
+	\item Negative review may increase awareness of the product.
+	\begin{itemize}
+		\item Theory prediction: negative reviews should have more negative effect for high awareness products than for low awareness products.
+	\end{itemize}
+
+	\item Cannot explain: why some established bad movies like \textit{Fu Chun Shan Ju Tu} still sell a lot.
+	\begin{itemize}
+		\item May because the different taste between reviewers and mass watchers.
+		\item As a social topic, just to be fashion.
+	\end{itemize}
+\end{itemize}
+
+% section product_reviews (end)
+
+\section{Gentzkov-Shapiro-Taddy, 17 WP} % (fold)
+\label{sec:gentzkov_shapiro_taddy_17_wp}
+
+\textbf{\bibentry{Gentzkow:2017hb}}
+
+\begin{itemize}
+	\item Methods for analyzing high-dimensional choices decisions
+	\begin{itemize}
+		\item also see \bibentry{Gentzkow_el.al:17WP}
+	\end{itemize}
+	\item Index for measuring polarization
+\end{itemize}
+
+This is a methodology paper introducing how to analyze high-dimensional choices decisions. They show that traditional logit model has severe finite sample bias.
+They also raise a index for measuring polarization.
+
+\textcolor{red}{[TO BE ADDED]}
+
+% section gentzkov_shapiro_taddy_17_wp (end)
+
+\chapter{Others} % (fold)
+\label{cha:others}
+
+\textbf{\bibentry{Einav:2010cd}}
+
+This survey paper provides a map for current empirical IO research, its range, and its relationship to theory.
+In addition, the ending part has a critique on the `reduced' view on IO (e.g. Angrist), worth reading.
+
+\subsection{Rey and Stiglitz, 1995, RAND} % (fold)
+\label{subsec:rey_and_stiglitz_1995_rand}
 
@@
 
-\subsection{Benchmark Case} % (fold)
+\subsubsection{Benchmark Case} % (fold)
 \label{sub:benchmark}
@@
 
-% subsection benchmark (end)
-
-% section patrick_and_stiglitz_1995_rand (end)
-
-\section{Production Function Estimation} % (fold)
-\label{sec:production_function_estimation}
-
-There are several difficulties in estimating production functions which will cause endogeneity problem. To name some:
-\begin{itemize}
-	\item Simultaneity.
-For a production function like $y_{it}=\beta_0+\beta_1 k_{it}+\beta_2 l_{it} + \omega_{it}+\varepsilon_{it}$, we suppose that $\omega_{it}$ is obseved by firm but not by econometricians, and $\varepsilon_{it}$ is observed neither by firm nor econometricians.
-This could induce endogeneity when directly using OLS.
-	Suppose $\omega_{it}$ has \textit{positive serial correlation}, when $\omega_{it}$ is high, firm will choose higher input because it is very possible that $\omega$ in next period will be high as well.
-This induces a positive bias for $\beta_k$.
-	\item Exit selection bias. When constructing a balanced panel, then we only observe those firms with high $\omega_{it}$.
-	\textcolor{blue}{Why we have to construct a balanced panel?}
-\end{itemize}
-
-There are several approaches in solving this problem.
-
-\begin{itemize}
-	\item Classical Approach.
-	\begin{itemize}
-		\item Use input price as IV.
-The problem is input price is generally the same across firms.
-When we do observe different input prices, which generally indicates market power in input markets.
-Thus those facing higher $\omega_i$ will tend to produce more, inducing their input price to increase, which has a negative bias on $\beta_k$.
-		\begin{itemize}
-			\item (My comment) When using input price as IV, we actually assume they are independent of productivities.
-			This may not be the case.
-			If productivity has some correlation across the firms,
-			then it is possible that when productivity is high,
-			the input price in the market will also be high.
-		\end{itemize}
-		\item Use fixed effect. We need to assume that a firm faces same $\omega_{it}$ across time, which is not very practical.
-	\end{itemize}
-	\item Control Function for  $\omega_{it}$.
-This approach first raised by \cite{Olley:1996ef} and developed by \cite{Levinsohn:2003ej} and \cite{Ackerberg:2015ha}.
-We name them OP, LP, ACF here after.
-The key idea is to use a function of what we know (for example, $k_t$ and $i_{t-1}$ in OP) to proxy $\omega$, the existence of such function is guaranteed by the solutioin property of the firm optimization problem.
-And the specific form of this function is estimated non-parametrically.
-	\begin{itemize}
-		\item OP uses a two step estimation process.
-First step, use $k_t$ and $i_{t}$ non-parametrically estimate $\omega_t$, plug this into original production function then use OLS.
-Notice the unobserved $\omega_t$ has been controlled by $k_t$ and $i_{t}$, then OLS will give consistent estimator for $l_t$ but not $k_t$.
-In second step, we first write $\omega_{it} = E[\omega_{it}|\omega_{it-1}]+\xi_{it}$, notice that $\xi_{it}$ is independent of any information set at t-1.
-Thus we get the moment condition $E[\xi_{it}k_{it}]=0$, then we can use method of simulating moments to estimate $\beta_k$.
-		\begin{itemize}
-			\item The key assumption in first step is, current period investment $i_t$ can be represented by a function of $f(k_t,\omega_t)$. 
-			If $f$ is invertible in $\omega_t$ (for example, $f$ being monotone in $\omega$), then we can write $\omega$ as a function of $(i_t, k_t)$.
-		\end{itemize}
-
-		\item LP is very similar to OP, just that use intermediate input $m_{it}$ instead of investment $i_{it}$ in proxy $\omega_{it}$.
-Because OP approach requires the policy function of $i_{it}$ be monotonicity in $\omega_{it}$, which is unsatisfied when $i_{it}=0$.
-But data shows that in many observations $i=0$.
-Using intermediate input can solve this.
-
-		\item ACF criticizing is that $\beta_l$ cannot be identified in the first step.
-In LP we assume that $m_{it}=f_t(k_{it},\omega_{it})$.
-But we can reasonably argue by the same reason that $l_{it}=h_t(k_{it},\omega_{it})$.
-Then since $f(\cdot)$ is invertible, then we can write $l_t$ as some deterministic function of $k_{it}$ and $m_{it}$.
-This implies we cannot identify $\beta_l$ in the first step.
-The solution of ACF is to identify both $\beta_k$ and $\beta_l$ simultaneously at step 2, which is feasible since we now have two moment conditions.
-	\end{itemize}
-	\item \cite{Gandhi:2017un} Approach (GNR).
-GNR criticizes control function approach is nonparametrically not identified in the presence of flexible inputs.
-They raise a new approach using FOC conditions.
-\end{itemize}
-
-% section production_function_estimation (end)
-
-\section{Demand Function Estimation} % (fold)
-\label{sec:demand_function_estimation}
-
-\noindent
-\textbf{Reference:} \cite{shum:2016bk} CH 1 is very good for motivation and techniques.\\
-
-\noindent
-\textbf{Motivation for demand estimation}
-\begin{itemize}
-	\item Firstly, it is important per se, we want to understand consumer behaviour. And we want to \textit{predict the results of price change}, and \textit{introduction of new products}. 
-	Such counter factual predictions can only be built upon a structural model.
-	\item Secondly, estimation of demand function helps us better understand market structure.
-Markup itself is rarely observed (with some exceptions, like the electronic industry), but we can generally observe demand elasticity.
-	Recall that $\frac{p-MC}{p}=1/\varepsilon$ (see \ref{sec:rey_and_stiglitz_1995_rand}). Estimation of $\varepsilon$ will help us know the markup of firm, thus infer market structure.
-\end{itemize}
-
-\noindent
-\textbf{Challenges in demand function estimation:}
-\begin{itemize}
-	\item Too many parameters.
-Think of a market with 100 commodities and we want to estimate the cross elasticities.
-The number of parameters will be 10,000.
-Obviously it is impossible to have enough data to estimate so many parameters.
-	\begin{itemize}
-		\item Solved by nested logit model.
-	\end{itemize}
-	\item Unobserved quality. This will causes the endogeneity of price. And because the unobservable quality affects the selling in a highly nonlinear way, so IV is not very applicable in this case.
-	\begin{itemize}
-		\item Solved by BLP style estimation.
-	\end{itemize}
-\end{itemize}
-
-\subsection{Brief Literature Review} % (fold)
-\label{sub:brief_literature_review}
-
-There are two branches of demand function estimation.
-The early literature features differentiated goods (continuous choices). Classical examples include \cite{Hausman:1994km} introducing a nested approach to reduce the dimension of parameters.
-
-Recent literature focus much more on discrete choice model. The seminal papers are \cite{Berry:1994jh} and \cite{berry.et.al.1995.emca}.
-The address of these two papers is to overcome the \textbf{endogenous price problem due to unobserved quality}. 
-Suppose we use a characteristic approach, where consumer utility and thus their purchase decision is decided by characteristics of products. 
-Some of the characteristics are obervable to consumer (and firms) but not to econometricians, for example the advertisement. 
-For higher unobserved quality, the equilibrium price will be higher, leading to a downward bias of price elasticity.
-
-\cite{Berry:1994jh} comes with a method to overcome this endogeneity problem with only \textit{market level data}.
-\begin{itemize}
-	\setlength{\itemsep}{0pt}
-	\item The basic idea is a IV based two step estimation.
-	\item First step: denote $\delta_j$ to be the `mean utility' for brand $j$.
-Notice this includes unobserved quality.
-Under some conditions, $\delta_j$ can be \textit{inversed} by market shares $(s_1,...,s_J)$, and thus we can get $\hat \delta_j$ by observed market shares.
-	\textcolor{blue}{This inversion step is the key for this paper, and many following papers treating endogenous quality problem.}
-	\item Second step: By definition, $\delta_j=X_j\beta -\alpha p +\xi_j$.
-Thus we can get $\hat \xi_j$ if we get $\hat \delta_j$.
-Suppose $E[\xi Z]=0$, then we can use $Z$ as IV to estimate consistently.
-\end{itemize}
-
-\cite{berry.et.al.1995.emca} (BLP henceforce) is more comprehensive with the same idea.
-They introduce random-coefficients logit model, which allows each individual to have different taste coefficients.
-Thus we can't directly use the inverse technique.
-The way is to use a Simulation Method of Moments (inner loop and outer loop).
-First guees a $\delta$, match mkt share, then run a IV regression, then guess different $\delta$ and get an outer loop.
-They prove a contraction mapping.
-
-\myline
-
-\textbf{\bibentry{Quan_Williams:2017wp}}
-
-This paper addresses the local heterogeneity of consumer demand,
-and concludes that usual BLP method will overestimate the welfare increase of e-commerce because local stores have satisfied most local demands.\\
-
-\noindent
-\textbf{Challenges:}
-\begin{itemize}
-	\item Huge varieties of goods in fine-grid locations make scarce data in each category. Two possible solutions for this: 1) aggregating over locations; 2) just ignore the zero sales. 
-	Aggregating is unsatisfactory since the heterogeneity of local preference is our study focus.
-	Ignoring will cause selection bias and cause overestimation of local heterogeneity.
-	\item Mean utility level cannot be recovered solely by observable variables.
-	They raise specific Converging in Distribution theorem to tackle this.
-\end{itemize}
-
-% subsection brief_literature_review (end)
-
-% section demand_function_estimation (end)
-
-\section{Price Dispersion} % (fold)
-\label{sec:price_dispersion}
-
-\textbf{\bibentry{Baye:2013un}}
-
-\begin{itemize}
-	\item Price comparing sites becoming less popular,
-	more consumers choose to direcly go to like Amazon and eBay.
-	These websites also have `marketplace'.
-	\item Many searching behaviour are not observed. Non-texture data (e.g. in the menu, directories).
-	\item Search time across platforms can hardly be compared.
-	Because maybe it's enough to search only once in Amazon, 
-	but many times in eBay.
-\end{itemize}
-
-\myline
-
-\noindent
-\textbf{Random Ideas}
-\begin{itemize}
-	\item Collusion when there is consumer searching cost.
-	Intuitively, collusion should be easier to sustein with 
-	\textcolor{blue}{[no idea]}
-
-	\item Awaya-Krishna (2016) 
-\end{itemize}
-
-% section price_dispersion (end)
-
-\section{Multisided Platforms} % (fold)
-\label{sec:multisided_platforms}
-
-\textbf{\bibentry{Evans_Schmalensee:2012wp} }
-\begin{itemize}
-	\item Price structure matters. Reduce charge by one side and increase charge by another side will affect the transaction.
-	\item Transaction cost is necessarily high for multisided platform.
-	\item Two kind of externalities. Usage externality and membership externality.
-	\item Pricing is compelicated. Per-transaction fee, or membership-fee. \textcolor{blue}{This looks similar to conventional IO model.}
-	\begin{itemize}
-		\item In per-transaction fee case. Price is directly proportional to the elasticity, while in conventional models price is inversely related to elasticity.
-		\[\frac{p_1+p_2-c_1-c_2}{c_1+c_2}=\frac{1}{e_1+e_2}\]
-		\[\frac{p_1}{e_1}=\frac{p_2}{e_2}\]
-		Notice the second equation is unconventional.
-		\item In membership-fee case.
-		\item Both models can lead to a highly skewed price structure.
-	\end{itemize}
-	\item Competition Structure.
-	\begin{itemize}
-		\item Product differentiation
-		\item Multi-home.
-		\item Asymetric Competition.
-A n-sided platform may face competition from 1) one-sided firms; 2) a multisided platform competing in some but not all sides; 3) a multisided platform that has additional sides
-	\end{itemize}
-\end{itemize}
-
-\myline
-
-\textbf{Random Ideas}
-\begin{itemize}
-	\item Multisided platform as a commitment device changes the game structure.
-Like in the Truck-GasStation case raised in the book, the fleet-card company provides commitment power to the card companny, no renegotiation problem.
-\end{itemize}
-
-% section multisided_platforms (end)
-
-\section{Erdem-Keane, 96 MktSci} % (fold)
-\label{sec:erdem_keane_96_mktsci}
-
-\textbf{\bibentry{erdem_kean:96_MngSci}}
-
-\cite{erdem_kean:96_MngSci} provides an example on how to estimate demand when quality is uncertain and consumer learns by Bayesian rule.
-
-\vspace{2mm}
-\noindent
-\textbf{Motivation:}
-\begin{itemize}
-	\item Avoide ad hoc assumptions on how consumers utilizing experience information
-	\item Estimate structural models to do policy analysis
-\end{itemize}
-
-\noindent
-\textbf{Features:}
-\begin{itemize}
-	\item Estimate Dynamic Programming.
-	Consumers make decision based on their perceptions,
-	but econometricians only observe the consumption. 
-	So have to integrate over the distribution of perception errors $v_{ij}(t)$, which is is a Markov process.
-	The integration part will be very complicated.
-	\begin{itemize}
-		\item Provides a way to estimate Dynamic Programming model with simulation. Also see \cite{keane_wolpin:94REStat}.
-	\end{itemize}
-	\item Experience Shocks.
-	This indicates that even after purchasing once, 
-	consumer is not certain about the quality of the good (or the preference of himself).
-	This is mainly motivated by empirical fact: 
-	consumption behavior generally do not converge.
-\end{itemize}
-
-\noindent
-\textbf{Empirical Findings:}
-\begin{itemize}
-	\item Bayesian learning very well fit the date.
-
-\end{itemize}
-
-% section erdem_keane_96_mngsci (end)
-
-\section{Gentzkov-Shapiro-Taddy, 17 WP} % (fold)
-\label{sec:gentzkov_shapiro_taddy_17_wp}
-
-\textbf{\bibentry{Gentzkow:2017hb}}
-
-\begin{itemize}
-	\item Methods for analyzing high-dimensional choices decisions
-	\begin{itemize}
-		\item also see \bibentry{Gentzkow_el.al:17WP}
-	\end{itemize}
-	\item Index for measuring polarization
-\end{itemize}
-
-This is a methodology paper introducing how to analyze high-dimensional choices decisions. They show that traditional logit model has severe finite sample bias.
-They also raise a index for measuring polarization.
-
-\textcolor{red}{[TO BE ADDED]}
-
-% section gentzkov_shapiro_taddy_17_wp (end)
+% section others (end)
+
+\part{Trade and Spatial Economics} % (fold)
+\label{prt:trade_ _and_ _spatial_ _economics_}
+
+\chapter{Trade Basic Model} % (fold)
+\label{cha:trade_basic_model}
+
+\section{CES Functions} % (fold)
+\label{sec:ces_functions}
+
+\subsection{CES Utility (discrete)} % (fold)
+\label{sub:ces_utility_discrete}
+
+Reference: Rutherford (2002), Lecture Notes on Constant Elasticity Functions
+
+The CES utility function is defined as:
+\[U ( x , y ) = \left( \alpha x ^ { \rho } + ( 1 - \alpha ) y ^ { \rho } \right) ^ { 1 / \rho }\]
+We can calculate the demand:
+\[\begin{array} { c } { x \left( p _ { x } , p _ { y } , M \right) = \left( \frac { \alpha } { p _ { x } } \right) ^ { \sigma } \frac { M } { \alpha ^ { \sigma } p _ { x } ^ { 1 - \sigma } + ( 1 - \alpha ) ^ { \sigma } p _ { y } ^ { 1 - \sigma } } } \\ { y \left( p _ { x } , p _ { y } , M \right) = \left( \frac { 1 - \alpha } { p _ { y } } \right) ^ { \sigma } \frac { M } { \alpha ^ { \sigma } p _ { x } ^ { 1 - \sigma } + ( 1 - \alpha ) ^ { \sigma } p _ { y } ^ { 1 - \sigma } } } \end{array}\]
+and also the indirect utility:
+\[V \left( p _ { x } , p _ { y } , M \right) = M \left( \alpha ^ { \sigma } p _ { x } ^ { 1 - \sigma } + ( 1 - \alpha ) ^ { \sigma } p _ { y } ^ { 1 - \sigma } \right) ^ { \frac { 1 } { \sigma - 1 } }\]
+$V$ is homogeneous of degree 1 in M. This permits us to form an exact \textbf{price index} corresponding to the cost of a unit of utility:
+\begin{align*}
+	1 \equiv V(p_x,p_y,e(p_x,p_y,V=1)) = e(p_x,p_y,V=1)\left( \alpha ^ { \sigma } p _ { x } ^ { 1 - \sigma } + ( 1 - \alpha ) ^ { \sigma } p _ { y } ^ { 1 - \sigma } \right) ^ { \frac { 1 } { \sigma - 1 } } \\
+	\Rightarrow e(p_x,p_y) \equiv e(p_x,p_y,V=1) = 
+	\left( \alpha ^ { \sigma } p _ { x } ^ { 1 - \sigma } + ( 1 - \alpha ) ^ { \sigma } p _ { y } ^ { 1 - \sigma } \right) ^ { \frac { 1 } {1- \sigma } }
+\end{align*}
+The indirect utility can be reframed as:
+\[V(p_x,p_y,M) = \frac{M}{e(p_x,p_y)}\]
+Importantly, wlog, we can think of each consumer demand only one good, and $e(p_x,p_y)$ is the price index for that good.
+
+\mysubtitle{Elasticity:}
+
+CES get its name because the cross elasticity is a constant independent of consumption bundle. To see this we first use a more general form:
+\[U(\vec x) = \left[ \sum_{i=1}^n x_i^\rho \right]^{\frac{1}{\rho}}\]
+By brutal force calculation we get:
+\[\frac{\partial x_i/ x_i}{\partial p_j / p_j} = \frac{1}{1-\rho}\]
+% subsection ces_utility (end)
+
+\subsection{CES Utility (continuous)} % (fold)
+\label{sub:ces_utility_}
+
+CES can be generated to continuous version:
+\[\begin{aligned} \max U ( \mathbf { c } ) & = \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { 1 / \rho } \\ \text { s.t.
+} & \int _ { 0 } ^ { 1 } p ( i ) c ( i ) d i = I \end{aligned}\]
+Write the Lagranian and we have FOC:
+\begin{align*}
+	b(\iota)\rho c(\iota)^{\rho-1} \frac{1}{\rho} \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { (1-\rho) / \rho }
+	= \lambda p(\iota) \\
+	b(\iota)c(\iota)^{\rho-1} \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { (1 - \rho )/ \rho } 
+	= \lambda p(\iota),\ \forall \iota \in [0,1] \tag{2}
+\end{align*}
+Multiply both sides by $c(\iota)$ and take integration:
+\begin{align*}
+	\left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { ( 1 - \rho ) / \rho }
+	\left( \int _ { 0 } ^ { 1 } b ( \iota ) c ( \iota ) ^ { \rho } d \iota \right) 
+	= \lambda \int _ { 0 } ^ { 1 } p ( \iota ) c ( \iota ) d \iota = \lambda I\\
+	\left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { 1 / \rho } = \lambda I
+\end{align*}
+Define the LHS as $C$, the composite consumption, $P\equiv\lambda^{-1}$ and we will get:
+\[CP = I\]
+we call $P$ the \textbf{price index}, which has a natural interpretation to be the price of a unit util. 
+It should be noted that here $C$ is already the \textit{optimal} consumption bundle.
+
+We still need to solve $P$. Return to (2) and solve $c(\iota)$:
+\[
+c(\iota) = 
+\left[b(\iota)^{-1} \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { ( \rho -1) / \rho } \lambda p(\iota)
+\right]^{\frac{1}{\rho-1}}
+\]
+\begin{align*}
+	b(\iota)c(\iota)^{\rho} &= 
+b(\iota)\left[b(\iota)^{-1} \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { ( \rho -1) / \rho } \lambda p(\iota)
+\right]^{\frac{\rho}{\rho-1}}\\
+&= b(\iota)^{\frac{-1}{\rho-1}}\left(\lambda p(\iota)\right)^{\frac{\rho}{\rho-1}} \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i
+\end{align*}
+Taking integral in both sides:
+\begin{align*}
+	1 = 
+	\lambda^{\frac{\rho}{\rho-1}}
+	\int_0^1 b(\iota)^{\frac{-1}{\rho-1}} p(\iota)^{\frac{\rho}{\rho-1}} d \iota\\
+	P \equiv \lambda^{-1} = \left[\int_0^1 b(\iota)^{\frac{-1}{\rho-1}} p(\iota)^{\frac{\rho}{\rho-1}} d \iota\right]^{\frac{\rho-1}{\rho}}
+\end{align*}
+
+\mytitle{Properties}
+
+\mysubtitle{Cross Elasticity:}
+
+By equation (2), take the log form and take partial derivative, we get:
+\[
+\sigma  \equiv \frac{\partial c(x)/ c(x)}{\partial p(y)/p(y)} = \frac{1}{\rho-1}\]
+
+\mysubtitle{Own Elasticity:}
+
+Still from (2), we substitute $\lambda$ by $P^{-1}$. Then (2) can be written as:
+\begin{align*}
+	b(\iota)c(\iota)^{\rho-1}C^{1-\rho} = P^{-1}p(\iota)\\
+\end{align*}
+The trick is that a single product $c$ is so small that it will affect neither $C$ nor $P$. And thus the own elasticity is still $\frac{1}{\rho-1}$.
+
+\mysubtitle{Limiting Cases:}
+
+When $\rho \rightarrow 0$, Cobb-Douglas. When $\rho \rightarrow 1$, perfect substitution. When $\rho \rightarrow \infty$, Leontief.
+\blue{This is from Kim Ruhl's notes, I did not check.}
+
+\mysubtitle{Two Stage Budgeting:}
+
+Suppose there is some outside good $c_0$ in the economy:
+\[\begin{array} { c } { \max U \left( c _ { 0 } , \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { 1 / \rho } \right) } \\ { \text { s.t.
+} p _ { 0 } c _ { 0 } + \int _ { 0 } ^ { 1 } p ( i ) c ( i ) d i = I } \end{array}\]
+One thing important is that the differentiated goods can be aggregated into one commodity $C$. Then the above problem can be summarized as a two stage problem.
+\[\begin{array} { c } { \max U \left( c _ { 0 } , C \right) } \\ { \text { s.t. } p _ { 0 } c _ { 0 } + P C = I } \end{array}\]
+We first solve $C$ and $PC$. Then everything comes similar.
+% subsection ces_utility_ (end)
+
+% section ces_functions (end)
+
+\section{Ricardian Model} % (fold)
+\label{sec:ricardian_model}
+
+This representation is based on DFS 1977.
+
+\mytitle{Settings:}
+\begin{itemize}
+	\item Two countries: Home and Foreign
+	\item One factor of production
+	\begin{itemize}
+		\item This is important in Ricardian model, because the order of $z$ below relies on unique factor of production. Otherwise we won't have a meaningful order.
+		\item Denote $L, L^*$ as the labor endowments in two countries; and $w, w^*$ be the wages respectively. All terms are real.
+	\end{itemize}
+	\item A continuum of goods indexed by $z \in [0,1]$
+	\begin{itemize}
+		\item A continuum of $z$ is easier to deal with than discrete $z$.
+	\end{itemize}
+	\item Technology: $a(z)$ and $a^*(z)$ are the labor requirements for produing unit good.
+	\begin{itemize}
+		\item Order goods s.t. $A(z)\equiv \frac{a^*(z)}{a(z)}$ is decreasing. So Home has comparative advantage in low $z$.
+	\end{itemize}
+\end{itemize}
+
+\mytitle{Equilibrium:}
+\begin{itemize}
+	\item Suppose there is no trade cost. Let $p(z)$ denote the (home) price of good $z$ under free trade.
+	\item Since the competition is perfect, and there is no trade cost, the product will be produced in the country with lower labor cost:
+	\[\begin{aligned} p(z)-w a(z) & \leq 0, \text {w .
+equality if } z \text { is produced at Home }(1) \\ p(z)-w^{*} a^{*}(z) & \leq 0, \text { w.
+equality if } z \text { is produced Abroad }(2) \end{aligned}\]
+	\item A direct proposition is: there exists $\tilde z$ s.t. Home produces all goods $z<\tilde z$ and vice versa for Foreign.
+	Another result is: $A(\tilde z) = \frac{w}{w^*}\equiv \omega$. Note that $\omega$ is endogenous and can be calculated in equilibrium.
+	\item To calculate $\omega$, we further assume consumers have \textbf{identical Cobb Douglas} preference around the world.
+Then we denote $b(z)$ the share of expenditure on good $z$: (which actually should be understand as density of share):
+	\[
+	b(z)=\frac{p(z) c(z)}{w L}=\frac{p(z) c^{*}(z)}{w^{*} L^{*}}
+ 	\]
+ 	by def, shares should satisfy:
+ 	\[\int_{0}^{1} b(z) d z=1\]
+ 	Let $\theta(\widetilde{z}) \equiv \int_{0}^{\widetilde{z}} b(z) d z$ denote the fraction of income spent on goods produced at Home. Trade balance requires Home Exports = Home Imports:
+ 	\[\theta(\widetilde{z}) w^{*} L^{*}=[1-\theta(\widetilde{z})] w L\]
+ 	then we have relative wage to be:
+ 	\[\omega=\frac{\theta(\widetilde{z})}{1-\theta(\widetilde{z})}\left(\frac{L^{*}}{L}\right) \equiv B(\widetilde{z})\]
+ 	Notice this is an GE results. An technical advancement will increase $\tilde z$, which must be compensated by an increase in $\omega$ in equilibrium.
+\end{itemize}
+
+\mytitle{Comparative Statics:}
+\begin{itemize}
+	\item Below figure plots the equilibrium.$A(z)$ is downward by construction, $B(z)$ is upward by above equation.
+
+	\includegraphics[width=0.5\linewidth]{images/ricardian.png}
+	\item Suppose $L^*/L$ increases, how it will change equilibrium price and welfare?
+	\begin{itemize}
+		\item For notation ease, set $w=1$ wlog since it only serves as numerair.
+		\item First notice that $\omega$ increases and $\tilde z$ decreases in equilibrium.
+		\item For goods produced at Home, no change in $p(z)$ since it only depends on Home technology.
+		\item For goods whose production remains at Abroad:
+		\[\omega \nearrow \Rightarrow w^{*} \searrow \Rightarrow p(z)=w^{*} a^{*}(z) \searrow\]
+		\item For goods moved to be produced Abroad, then by profit optimization:
+		\[w^{*} a^{*}(z) \leq a(z) \Rightarrow p(z) \searrow\]
+		\item Thus Home gains.
+	\end{itemize}
+	\item KZ: The Abroad welfare decreases because of population increase.
+Why does this happen?
+Because Abroad now produces goods that they have less comparative advantages.
+They produce these goods because they have low wage, due to the competition effect of large population.
+
+\end{itemize}
+
+% section ricardian_model (end)
+
+\section{Eaton and Kortum, 02 EMCA} % (fold)
+\label{sec:eaton_and_kortum_02_emca}
+
+\mytitle{Setting:}
+\begin{itemize}
+	\item Efficiency: country $i$'s efficiency in product $j$ is $z_i(j)$
+	\item Input price in country $i$ is $c_i$, which can be further decomposed into labor cost and intermediate inputs cost
+	\item Geographic barriers between country $i$ and country $n$ is $d_{ni}$. \red{Is $d_{ni}$ symmetric?}
+	\item Production cost is:
+	\[p _ { n i } ( j ) = \left( \frac { c _ { i } } { z _ { i } ( j ) } \right) d _ { n i }\]
+	which is also the purchase cost by perfect competition assumption. However, the buyer will buy from the cheapest seller, and we assume the search is costless:
+	\[p _ { n } ( j ) = \min \left\{ p _ { n i } ( j ) ; i = 1 , \ldots , N \right\}\]
+	\item Utility: buyers have the love of variety, and we assume a CES utility form:
+	\[U = \left[ \int _ { 0 } ^ { 1 } Q ( j ) ^ { ( \sigma - 1 ) / \sigma } d j \right] ^ { \sigma / ( \sigma - 1 ) }\]
+	where the elasticity of substitution is $\sigma>0$.
+\end{itemize}
+
+\mysubtitle{Technology:}
+\begin{itemize}
+	\item The technology $z_i(j)$ is the realization of r.v. $Z_i$, drawn independently for each product $j$. $Z_i$ follows a Type II extreme value distribution:
+	\[F _ { i } ( z ) = e ^ { - T _ { i } z ^ { - \theta } }\]
+	$T_i$ governs the location of distribution, and $\theta$ common for all countries governs the variation \textit{within} the distribution. A bigger $\theta$ represents less variability.
+	\blue{This distribution is the key to the closed form solution.}
+\end{itemize}
+
+\mysubtitle{Prices:}
+\begin{itemize}
+	\item The induced price distribution is:
+	\begin{align*}
+		G _ { n i } ( p )
+		& = \Pr \left( P _ { n i } ( j ) \leq p \right) \\
+		& =  \Pr(\frac{c_i}{z_i(j)}d_{ni} \leq p) \\
+		& = 1-F_i(\frac{c_i d_{ni}}{p}) \\
+		& = 1 - e^{-T_i(c_i d_{ni})^{-\theta}p^{\theta}}
+	\end{align*}
+	The purchasing price distribution is thus: \red{how to derive?}
+	\begin{align*}
+		G _ { n } ( p ) & = 1 - \prod _ { i = 1 } ^ { N } \left[ 1 - G _ { n i } ( p ) \right] \\
+		& = 1 - e ^ { - \Phi _ { n } p ^ { \theta } }
+	\end{align*}
+	where $\Phi_n$ is:
+	\[\Phi _ { n } = \sum _ { i = 1 } ^ { N } T _ { i } \left( c _ { i } d _ { n i } \right) ^ { - \theta }\]
+
+	\item The probability that country $i$ provides a good at the lowest price in country $n$ is:
+	\begin{align*}
+	\pi _ { n i } &= \operatorname { Pr } \left[ P _ { n i } ( j ) \leq \min \left\{ P _ { n s } ( j ) ; s \neq i \right\} \right] \\
+	& = \int _ { 0 } ^ { \infty } \prod _ { s \neq i } ^ { \infty }  \left[ 1 - G _ { n s } ( p ) \right] d G _ { n i } ( p ) \\
+	&= \frac { T _ { i } \left( c _ { i } d _ { n i } \right) ^ { - \theta } } { \Phi _ { n } }
+	\end{align*}
+	\red{the last step?}
+
+	\item The price of a good that country $n$ \textit{actually buys} from country $i$ also has the distribution $G_n(p)$.
+This means that the price distribution \textit{conditional} on export country is the same as overall price distribution faced by importer country $n$.
+This result can be derived by showing that:
+	\[G _ { n } ( p ) = \frac { 1 } { \pi _ { n i } } \int _ { 0 } ^ { p } \prod _ { s \neq i } \left[ 1 - G _ { n s } ( q ) \right] d G _ { n i } ( q )\]
+
+	\item The price index for CES function is then \red{(why?)}
+	\[p _ { n } = \gamma \Phi _ { n } ^ { - 1 / \theta } \tag{9}\]
+	where 
+	\[\gamma = \left[ \Gamma \left( \frac { \theta + 1 - \sigma } { \theta } \right) \right] ^ { 1 / ( 1 - \sigma ) }\]
+	$\Gamma$ is the gamma function.
+
+\end{itemize}
+
+\mysubtitle{Trade Flows and Gravity}
+\begin{itemize}
+	\item Since the price distribution conditional on source is the same as overall price distribution, a corollary is that the average expenditure per good is identical across sources.
+Thus, the fraction of goods that country $n$ buys from country $i$, $\pi_{ni}$ is the fraction of expenditures:
+	\[\frac { X _ { n i } } { X _ { n } } = \pi_{ni} = \frac { T _ { i } \left( c _ { i } d _ { n i } \right) ^ { - \theta } } { \Phi _ { n } } = \frac { T _ { i } \left( c _ { i } d _ { n i } \right) ^ { - \theta } } { \sum _ { k = 1 } ^ { N } T _ { k } \left( c _ { k } d _ { n k } \right) ^ { - \theta } } \tag{10}\]
+	The exporter's total sales $Q_i$ are:
+	\[Q _ { i } = \sum _ { m = 1 } ^ { N } X _ { m i } = T _ { i } c _ { i } ^ { - \theta } \sum _ { m = 1 } ^ { N } \frac { d _ { m i } ^ { - \theta } X _ { m } } { \Phi _ { m } }\]
+	Then we can cancel out $T_i c_i^{-\theta}$:
+	\[T_i c_i^{-\theta} = 
+	\frac{X_{ni}\Phi_n d_{ni}^\theta}{X_n} = 
+	\frac{X_{ni}}{X_n} \left(\frac{p_n}{\gamma d_{ni}}\right)^{-\theta}\]
+	the second equation is from derived CES price index equation. Substitute $T_i c_i^{-\theta}$ into $Q_i$ and we get:
+	\[X _ { n i } = \frac { \left( \frac { d _ { n i } } { p _ { n } } \right) ^ { - \theta } X _ { n } } { \sum _ { m = 1 } ^ { N } \left( \frac { d _ { m i } } { p _ { m } } \right) ^ { - \theta } X _ { m } } Q _ { i } \tag{11}\]
+	\blue{Why we are interested in this equation?} Because it resembles the standard gravity equation.
+
+\end{itemize}
+
+\mytitle{Trade, Geography and Price: The Connection:}
+\begin{itemize}
+	\item Notice that if we divide (10) by $X_{ii}/X_i$, we get:
+	\[\frac { X _ { n i } / X _ { n } } { X _ { i i } / X _ { i } } = \frac { \Phi _ { i } } { \Phi _ { n } } d _ { n i } ^ { - \theta } = \left( \frac { p _ { i } d _ { n i } } { p _ { n } } \right) ^ { - \theta }\]
+	the LHS is called \textit{normalized import share}. \red{why we want to normalize it?}
+\end{itemize}
+
+\mytitle{Input Costs:}
+
+\mysubtitle{Production:}
+\begin{itemize}
+	\item The cost of an input bundle in country $i$ is:
+	\[c _ { i } = w _ { i } ^ { \beta } p _ { i } ^ { 1 - \beta }\]
+\end{itemize}
+
+% section eaton_and_kortum_02_emca (end)
+
+% chapter trade_basic_model (end)
+
+% part trade_ _and_ _spatial_ _economics_ (end)
 
 % chapter io (end)
+
+\part{Micro Theory} % (fold)
+\label{prt:micro_ _theory_}
+
+% part micro_ _theory_ (end)
 
@@
 
-There are many solution concepts:
+A very good reference for different solution concept is \cite{vanDamme:1987}.
 \begin{itemize}
@@
 % subsection solution_concept (end)
+
+\section{Decision Theory} % (fold)
+\label{sec:decision_theory}
+
+\subsection{Morris, 95 Econ\&Phil} % (fold)
+\label{sub:morris_95_econ_phil}
+
+% subsection morris_95_econ&phil (end)
+
+\textbf{\bibentry{Morris:1995ic}}
+
+This assumption reviews the common prior assumption in economics, its common justifications, and its impact on game theory.
+
+\textcolor{blue}{VEEY WORTH READING!! NOTES TO BE ADDED.}
+
+% section decision_theory (end)
+
+\section{Mechanism Design} % (fold)
+\label{sec:mechanism_design}
+
+\noindent
+Important tools and topics in mechanism design:
+\begin{itemize}
+	\item Revelation Principle
+	\item Single dimension mechanism design
+	\begin{itemize}
+		\item Bayesian mechanism design
+		\item Dominant strategy mechanism design
+		\item Revenue equivalence
+		\item Payoff equivalence
+	\end{itemize}
+	\item Multidimensional mechanism design
+	\item Interdependent types mechanism design
+\end{itemize}
+
+\subsection{Revelation Principle} % (fold)
+\label{sub:revelation_principle}
+
+There are many things assumed in the proof of revelation principle. Take p.10 in Borger's book as example.
+
+\begin{itemize}
+	% \item Assume that in initial game, one can pretend to be someone else. That is, $\sigma(\theta')$ is in the action space of $\theta$.
+	\item No verification.
+	\item Utility is transferable.
+\end{itemize}
+
+For an example where all three assumptions are violated, see \cite*{BenPorath:2014bc}.
+
+\begin{mdframed}[style=comment]
+\noindent
+\textbf{Information side of Revelation Principle:}
+
+In setting we prove revelation principle, we assume every thing is common knowledge except for the specific type.
+These include the type space, the action space of each type, the utility form of each type, and so on. 
+We also assume that in the direct mechanism, the action space is the \textit{whole} type space for \textit{every} agents.
+\textcolor{red}{[Don't understand this. Since in the proof we only require that one can report truthfully.]}
+
+\end{mdframed}
+
+% subsection revelation_principle (end)
+
+% section mechanism_design (end)
 
@@
 
-% section hard_information (end)
-
-\section{Green-Porter, 84 EMCA} % (fold)
-\label{sec:green_porter_84_emca}
-
-\textbf{\bibentry{Green_Porter:1984EMCA}}\\
-
-\noindent
-\textbf{Motivation:}
-\begin{itemize}
-	\setlength{\itemsep}{0pt}
-	\item In perfect monitoring models, the price is constant over time. But empirically, we observe price war frequently.
-	\item Using imperfect monitoring, the price war is an intrinsic property of the model.
-	\item The idea is: based on imperfect monitoring. The firms cannot perfectly distinguish others' deviation with a price shock.
-	\item So there will be an  price threshold. Above this threshold, they take the collusion action. Below this, they will exert retaliation for some period, then back to collusion.
-\end{itemize}
-
-\noindent
-\textbf{Model:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-% section green_porter_84_emca (end)
+% section hard_information (end
+
+\section{Bayesian Persuasion} % (fold)
+\label{sec:bayesian_persuasion}
+
+The question that \textit{Information Design} wants to answer is corresponding to that of Mechanism Design.
+In mechanism design, the designer can commit to the \textit{rule} of a game; in information design, the designer (sender) commits to a information structure.
+
+\subsection{Kamenica and Gentzkow, 11 AER} % (fold)
+\label{sub:kamenica_and_gentzkow_11}
+
+% subsection kamenica_and_gentzkow_11 (end)
+
+\textbf{\bibentry{Kamenica:2011ih}}
+
+\begin{exmp}
+Suppose there is one prosecutor (Sender) and one judge (Receiver).
+Both parties hold the prior that the suspect is guilty with $\rho=0.3$.
+The prosecutor decides whether to investigate the suspect. 
+After that the judge will see investigation report, which cannot be manipulated by the prosecutor, and then make the decision of acquit or convict.
+The prosecutor knows the world state (innocent or guilty), but he only wants to increase the probability of convict.
+The judge wants to matching state.
+What is the best thing the prosecutor can do?
+
+If the prosecutor does nothing, then the judge will action according to his prior, and \textit{acquit} the suspect with probability 1 since $\rho<0.5$.
+
+But the prosecutor can do much better than this.
+Suppose the prosecutor commits to following investigation:
+\[\pi(i|innocent)=4/7, \ \pi(g|innocent)=3/7\]
+\[\pi(i|guilty)=0, \ \pi(g|guilty)=1\]
+
+Thus when the judge see signal \textit{i}, he does Bayesian inference and gets:
+\(Pr(guilty|i)=0\)
+and 
+\(Pr(guilty|g)=\frac{1*0.3}
+{1*0.3+3/7*0.7}=0.5\).
+If the equilibrium is in favor of the prosecutor, the judge will choose \textit{convict} with probability 1 when seeing signal \textit{g}.
+\footnote{This specific tie breaking rule is not important since we can always add $\varepsilon$ to 0.5.}
+Then the total probability of \textit{convict} becomes 0.6.
+\end{exmp}
+
+\noindent
+\textit{Comment to Example:}
+\begin{itemize}
+	\item The sender actually commits to the \textit{precision} of investigation. The point is that he cannot change the result \textit{ex post}.
+
+	\item The judge will behave the same whether he believes the guilty probability is 0 or 0.49.
+So the information revelation scheme will make the belief of guilty under signal $i$ to be as low as possible, and make the belief under $g$ slightly over 0.5.
+\end{itemize}
+
+\subsection{Gentzkow and Kamenica, 17 RES} % (fold)
+\label{sub:gentzkow_and_kamenica_17_res}
+
+\textbf{\bibentry{Gentzkow:2017ff}}
+
+\vspace{1em}
+\noindent
+\textbf{Highlight of the Paper:}
+\begin{itemize}
+	\item This paper shows that the competition does not increase the amount of information being revealed in general.
+A key condition for competition to be beneficial is \textbf{Blackwell-connectedness}.
+
+	\item There are other papers answering this question.
+For example, the cheap talk games and the hard evidence game.
+But this paper is different because those papers take senders' information as given, and focus on the strategic communications subject to incentive compatibility.
+	This paper abstracts from the incentive problem by giving senders commitment and takes the senders' information structure as endogenous.
+
+\end{itemize}
+
+% subsection gentzkow_and_kamenica_16_res (end)
+
+% section bayesian_persuasion (end)
 
@@
 
+\subsection{Miscellanea} % (fold)
+\label{sub:miscellanea}
+
+\textbf{\bibentry{Hadfield:2012kc}}
+
+This paper asks an interesting question: what is the difference between law and social norm?
+And they argue that the key feature of law of `central judgment', while the punishment can be decentralized.
+
+Such a model wants to answer: what's the incentive for individuals to conduct punishment despite that such punishment is costly?
+Their model is weird.
+
+\textit{KZ: Intuitively this is like private monitoring.}
+
+% subsection miscellanea (end)
+
 % section repeated_game (end)
+
+\section{Financial Economics} % (fold)
+\label{sec:financial_economics}
+
+\noindent
+\textbf{Bid-Ask Spread:}
+
+\cite{oHara} Chapter-3 provides two explanations on existence of bid-ask spread, even with market makers being risk neutral and competitive.
+Both model based on asymmetrically informed investors.
+
+\vspace{1em}
+\cite{copeland1983information} uses a one-stage game with asymmetric informed investors.
+The informed investors have full information, 
+while the uninformed investors have no information except for common prior.
+The market maker will lose money when transact with informed with informed investors, and earn money when transacting with uninformed ones.
+The bid ask spread is to make market makers balance off.
+
+Several things are unspecified in their model.
+First, the motivation of uninformed participants are unspecified. Why they will enter the market knowing that they will lose money in expectation?
+Secondly, the information conveyed by trade action is not specified.
+A sell order may represent a bad news of informed investor and vice versa.
+
+\vspace{1em}
+\cite{glosten_milgrom:1985bid} addresses the second concern by studying a sequential trade structure.
+Market makers will learn in Bayesian to update his belief about the world state. 
+And the buy/sell order conveys different information about the world state since the existence informed investors.
+So when the investor wants to sell a stock, market maker will have a more gloomy prediction about world state, and thus decrease the price; vice versa.
+
+Glosten-Milgrom model explains the bid-ask spread in abscence of any exogenous transaction or inventory cost.
+In addition, they show that the price is a Martingale (for market maker).
+Their model also suggests that market may collapse if there are too many informed investors, since the spread in positively correlated with portion of informed investors.
+
+KZ: But in their model, investors will not use the information of previous transactions, which is unsatisfactory.
+We can think in social learning approach.
+If that is the case, then transaction conveys no additional information if investors are in a herd.
+
+% section financial_economics (end)
 
@@
 \begin{itemize}
-	\item \href{run:resources/learning/Talk_note_Learning in network.pdf}{Note of Takl by Board}
+	\item \href{run:resources/learning/Talk_note_Learning in network.pdf}{Note of Talk}
 	\item Two concerns in network learning
 	\begin{itemize}
-		\item I get awaked at a constant rate, and may want to try
+		\item I get awake at a constant rate, and may want to try
 		\item I see my neighbor trying, and want to try
@@
 \noindent
+\textbf{Yuval Salant (18 WP): Statistical Inference in Games}
+
+\begin{itemize}
+	\item Idea: the agents in the game only use a sample of all agents, and based on the decision of the sample, the agent forms an inference. Then makes his own decision based on this inference.
+
+	\item The trade-off the agent is making is: enlarging sampling size is costly, but a larger sampling size will induce more precise distribution, which is beneficial since agents are risk averse.
+
+	\item They proposes a \textit{Generalized Sampling Equilibrium} based on above idea. And they show that this equilibria is always smaller than Nash.
+
+	\item The difficulty in defining this equilibrium is that everyone draws a different sample, and how to define equilibrium in this case?
+The trick here is they use a continuum of agents, so that even though everyone draws differently, but as a population they draw a same ``distribution''.
+The difference among agents are just changing labels.
+
+	\item Applications:
+	\begin{itemize}
+		\item In defining equilibria with search behavior.
+
+		\item Wei stated that this concept can be used widely in macro. For example, the shock in TFP will induce an endogenous fluctuation in sampling size; so the total variation is enlarged.
+	\end{itemize}
+\end{itemize}
+
+\myline
+
+\noindent
 \textbf{Cooperation Game:}
@@
 
+\myline
+
+\noindent
+\textbf{\bibentry{Fainmesser:2018ju}}
+
+This paper discusses how how
+
 % section seminar_notes (end)
@@
 
-\chapter{Decision Theory} % (fold)
-\label{cha:decision_theory}
-
-\section{Dekel and Lipman, 2010, Annu Rev Econ} % (fold)
-\label{sec:dekel_and_lipman_2010_annu_rev_econ}
-
-\textbf{\bibentry{Dekel:2010bm}}\\
-
-\noindent
-\textbf{What we can learn from decision theory}
-
-1) to know whether our intuition is correct;
-2) to flesh out initial intuition to get additional or better prediction (e.g. some additional observable prediction);
-3) to help us understand of why and how mechanism works
-
-\noindent
-\textbf{Story of the model}
-
-Why the story of the model is important even if it is not realistic? Why we can't just choose the model by the 'prediction-rejection' procedure?
-
-1) The story makes us believe the predictions more;
-2) Having a nice intuition helps us to utilize the model and to expand the model;
-3) And a model can never be realistic, the important thing is whether it captures something important.
+% \chapter{Decision Theory} % (fold)
+% \label{cha:decision_theory}
+
+% \section{Dekel and Lipman, 2010, Annu Rev Econ} % (fold)
+% \label{sec:dekel_and_lipman_2010_annu_rev_econ}
+
+% \textbf{\bibentry{Dekel:2010bm}}\\
+
+% \noindent
+% \textbf{What we can learn from decision theory}
+
+% 1) to know whether our intuition is correct;
+% 2) to flesh out initial intuition to get additional or better prediction (e.g. some additional observable prediction);
+% 3) to help us understand of why and how mechanism works
+
+% \noindent
+% \textbf{Story of the model}
+
+% Why the story of the model is important even if it is not realistic? Why we can't just choose the model by the 'prediction-rejection' procedure?
+
+% 1) The story makes us believe the predictions more;
+% 2) Having a nice intuition helps us to utilize the model and to expand the model;
+% 3) And a model can never be realistic, the important thing is whether it captures something important.
 
@@
 
-\chapter{Search Theory} % (fold)
-\label{cha:search_theory}
-
-\section{Shi, 09 EMCA} % (fold)
-\label{sec:shi_09_emca}
-
-% subsection shi_09_emca (end)
-
-% section search_theory (end)
-
-\chapter{Macro} % (fold)
+\part{Macro} % (fold)
 \label{cha:chapter_name}
+
+\chapter{Bubbles} % (fold)
+\label{ch:bubbles}
+
+\section{Milgrom and Stokey, 82 JET} % (fold)
+\label{sec:milgrom_and_stokey_82_jet}
+
+\textbf{\bibentry{Milgrom:1982fv}}
+
+\begin{thm}[No Trade Thm]
+Suppose that all 1) traders are risk averse; 2) initial allocation $e=(e_1,...,e_n)$ is Pareto optimal relative to $\theta$-trades; 3) agents' prior beliefs are concordant; 4) each trader observes private information conveyed by the partition $\hat P_i$.
+If it is common knowledge at some world state $\omega$ that $t$ is a feasible $\theta$-trade and each trader weakly prefers $t$ to the zero trade, then every agent is indifferent between the two.
+If all agents are strictly risk averse, then $t$ is zero trade.
+\end{thm}
+
+\noindent
+\textit{Comment:}
+\begin{itemize}
+	\item This being called \textit{no trade theorem} because private information will not lead to trade, which is on the contrary to what static models predicts.
+
+	\item Intuitively, if some other wants to trade with me, then he must possess some private information that in favor of this trade.
+But if we have same concordant prior belief, such information must \textit{in against with} my trading with him.
+So I will not accept any trade being offered to me.
+By the same argument, others will not accept any offer being offered to them.
+
+	\item World state space is: $\Omega=\Theta \times X$. $\Theta$ is set of payoff-related events, which will affect endowment and utility (type), $X$ will not affect endowment and taste directly.
+	A trade is a function from $\Omega$ to $R^{ln}$, it is $\theta$-trade if it only depends on $\theta$.
+
+	\item Beliefs are \textit{concordant} if:
+	\[p_1(x|\theta)=...=p_n(x|\theta),\ \forall x,\theta\]
+\end{itemize}
+
+% subsection milgrom_and_stokey_82_jet (end)
+
+\section{Geanakoplos and Polemarchakis, 82 JET} % (fold)
+\label{sec:geanakoplos_and_polemarchakis}
+
+\textbf{\bibentry{Geanakoplos:1982fl}}
+
+\vspace{1em}
+\noindent
+\textbf{Main result:}
+\begin{itemize}
+	\item \textbf{Theorem: }With common priors, and if the information partitions of two agents are finite, then they can converge to a common equilibrium posterior by communicating \textit{only posterior}.
+And the communication steps are finite.
+
+	\item This result is more general than Aumann's, because it does not require the event A to be posterior common knowledge. Actually it does not put any restriction on event A.
+
+	\item Such converging posterior may NOT be the same as the one they will reach if they direct communicate.
+
+	\item Such convergence may NOT happen in \textit{each} step. It is possible that the posterior of both agents do not change until the last step. E.g. the blue/red eye island.
+\end{itemize}
+
+\begin{exmp}
+
+\end{exmp}
+
+% subsection geanakoplos_and_polemarchakis (end)
+
+\section{Morris, 94 EMCA} % (fold)
+\label{sec:morris_94_emca}
+
+\textbf{\bibentry{Morris:1994id}}
+
+This paper is an extension of \cite{Milgrom:1982fv}, which relaxes the concordant belief in MS-1982 paper and find the no-trade theorems under different \textit{trading rules} and \textit{belief structures}.
+
+The generalization is listed in \href{run:resources/Berk_bubbles_pres_feb20.pdf}{Berk's notes}:
+
+\begin{table}[h]
+\centering
+\begin{tabular}{cccc}
+\hline
+C \textbackslash\  T & \cellcolor[HTML]{C0C0C0}Ex-Ante & \cellcolor[HTML]{C0C0C0}Interim & \cellcolor[HTML]{C0C0C0}Ex-Post \\ \hline
+\cellcolor[HTML]{C0C0C0}Uncons. & condordant & consistent conc. & revelation cons. con. \\
+\cellcolor[HTML]{C0C0C0}IC & noisy conc. & {\color[HTML]{3166FF} noisy cons. conc.} & - \\
+\cellcolor[HTML]{C0C0C0}Public & public conc. & public cons. conc. & {\color[HTML]{FE0000} public rev. cons. conc.}
+\end{tabular}
+\end{table}
+
+The read of this table is: ``An initially efficient allocation is T C efficient \textit{iff} beliefs are (C,T).''
+
+\begin{itemize}
+	\item Noisy concordant and public concordant are weaker than concordant. If beliefs are concordant, then they are noisy concordant.
+\end{itemize}
+
+% subsection morris_94_emca (end)
+
+% section bubbles (end)
 
@@
 
-\section{Costly State Verification} % (fold)
-\label{sec:costly_state_verification}
+\chapter{Costly State Verification} % (fold)
+\label{cha:costly_state_verification}
 
@@
 
-\section{Euro Crisis} % (fold)
-\label{sec:euro_crisis}
+\chapter{Euro Crisis} % (fold)
+\label{cha:euro_crisis}
 
@@
 \begin{itemize}
-	\item Without labour mobility, a state has to make wage fall to restore the full employment, this will be much easier with its own to devalue.
-But if labour mobility is high, then workers can just move to other states.
-	\item Fiscal integration will also help. First because federal transfer is like a insurance, also because the borrowing cost for federal gevernment is much lower.
+	\item Without labor mobility, a state has to make wage fall to restore the full employment, this will be much easier with its own to devalue.
+But if labor mobility is high, then workers can just move to other states.
+	\item Fiscal integration will also help. First because federal transfer is like a insurance, also because the borrowing cost for federal government is much lower.
 \end{itemize}
@@
 
-\section{Seminar Notes} % (fold)
-\label{sec:seminar_notes}
+\chapter{Macro Seminar Notes} % (fold)
+\label{cha:macro_seminar_notes}
 
@@
 		\item \url{http://economics.sas.upenn.edu/~jesusfv/Cryptocurrencies.pdf}
-		\item Not positive on private currencies. First, competitive private money will not provide price stability, either with a profit-maximizing entrpreneurs or through automaton.
-		\item Even with price stability, value of private moneis may go zero in infinite equilibriums.
+		\item Not positive on private currencies. First, competitive private money will not provide price stability, either with a profit-maximizing entrepreneurs or through automaton.
+		\item Even with price stability, value of private money may go zero in infinite equilibriums.
 		\item Purely private money system does not provide social optimal quantity of money.
@@
 
+\myline
+
+\textbf{\bibentry{Sorkin:18qje}}
+
+\begin{itemize}
+	\item Use Google Page Ranking algorithm to rank good firms. `good firms hire from other good firms and have few workers leave'. Reduce computation burden greatly.
+	\item Previous literature use hedonic approach to rank firms. Two drawbacks:
+	\begin{itemize}
+		\item Need to completely model and measure all relevant elements
+		\item Do not consider the utility dispersion case. [not understand]
+	\end{itemize}
+\end{itemize}
+
+\textcolor{blue}{Worth reading.}
+
 % section seminar_notes (end)
@@
 
-\chapter{Methodology} % (fold)
-\label{cha:methodology}
+\part{Methodology} % (fold)
+\label{part:methodology}
+
+\chapter{Micro Foundations of Macroeconomics} % (fold)
+\label{cha:micro_foundations_of_macroeconomics}
+
+% section micro_foundations_of_macroeconomics (end)
 
@@
 There is no useful parallel to be drawn between the way in which complexity appears in simplest cases of many modies and chemistry and culture ones.}'
-The aggregated economy is so complecated that may not be reduced to individual decision problems.
+The aggregated economy is so complicated that may not be reduced to individual decision problems.
 \footnote{Zhao Dingxing has an article discussing this problem.
@@
 
-\vspace{3mm}
-\hrule
-\vspace{3mm}
+\vspace{2em}
+\noindent
+\textbf{Policy Making without Macroeconomic Theory:}
+\footnote{\href{https://docs.google.com/viewer?a=v&pid=sites&srcid=ZGVmYXVsdGRvbWFpbnxrb2NoZXJsYWtvdGEwMDl8Z3g6NDhhODQ0MTI1MWMyNDRjNQ}{Click for link to slides}}
+
+Kocherlakota (2018) points out that policy makers does not need to know economic theory, albeit the players are in the framework of theory.
+The key points of the theory are:
+\begin{itemize}
+	\item Private sectors are forward looking, but government is myopic
+	\item Gov suffers private taste shock, which will only affect the gov utility
+	\item Within an equilibrium, government can pick the optimal policy through simple regression over past actions and stages
+\end{itemize}
+
+\chapter{Decision Theory as a Foundation} % (fold)
+\label{cha:decision_theory_as_a_foundation}
+
+% section decision_theory_as_a_foundation (end)
 
@@
 
+\cite{Spiess:2017tp} has a fantastic discussion of this from the perspective of econometrics and mechanism design.
+
+\myline
+
+\noindent
+\textbf{Lucas Critique:}
+
+\cite{Hoover:94JEMethod} views Lucas critique as pointing the causal inference and identification problem in econometrics.
+
 % chapter methodology (end)
@@
 
+\section{Miscellanea} % (fold)
+\label{sec:miscellanea}
+
+\subsection{Elasticity} % (fold)
+\label{sub:elasticity}
+
+\begin{exmp}
+Suppose $Q=\sum{q_i}$, $p=Q^{1/\alpha}$ and define $s_i=\frac{q_i}{Q}$. In equilibrium, we have $s_i=s_i^*$.
+Then in equilibrium, we have $\frac{\partial p}{\partial q_i}=s_i^*/\alpha$ instead of $1/\alpha$.
+
+Why? In first look, $Q$ is linear in $q_i$, then the derivative $\partial p/\partial Q$ should be the same as $\partial p/\partial q_i$.
+The point is that $Q$ is just a aggregated notation.
+In equilibrium, small change in $q_i$ will induce small change in all $q_{j \neq i}$, thus the aggregate change in $Q$ will be proportion of change in $q_i$.
+\end{exmp}
+
+% subsection elasticity (end)
+
+% section miscellanea (end)
+
 % section supermodularity (end)
@@
 \label{cha:probability}
+
+\begin{thm}[Linear Combination of Dependent Normal RV]
+Suppose \(\left(\begin{matrix}X\\Y \end{matrix}\right) \sim \mathcal{N}\left[ \left(\begin{matrix}\mu_X\\\mu_Y\end{matrix}\right), \Sigma_{X,Y} \right]\),
+then
+\(AX+BY+C \sim \mathcal{N}\left[ 
+\left(\begin{matrix}A& B \end{matrix}\right)
+\left(\begin{matrix}\mu_X\\\mu_Y\end{matrix}\right) + C, 
+\left(\begin{matrix}A & B \end{matrix}\right)\Sigma_{X,Y} \left(\begin{matrix}A^T \\ B^T \end{matrix}\right)\right]\).
+\end{thm}
+
+\begin{thm}[Kolmogorov's zero–one law]
+Let $(\Omega,F,P)$ be a probability space, and $F_n$ be a series of independent $\sigma$-algebras contained in $F$.
+Let
+\[G_n = \sigma \left( \cup^\infty_{k=n} F_k\right)\]
+Then we define tail event $F$ to be any event such that:
+\[F \in \cap^\infty_{n=1}G_n\]
+Kolmogorov zero-one law claims that $Pr(F)=0$ or $Pr(F)=1$. 
+\end{thm}
+
+Intuitively, if the occurrence of a event $F$ can be determined when any finite initial segment is removed, then it either happens or not with probability 1.
+
+\section{Distributions} % (fold)
+\label{sec:distributions}
+
+\begin{itemize}
+	\item Pareto Distribution
+	\item T1EV (Type 1 Extreme Value)
+\end{itemize}
+
+% section distributions (end)
 
@@
 \begin{itemize}
-	\item Always motivate very clearly, both from economics facts and from literature.
+	\item Always \textit{motivate} very clearly, both from economics facts and from literature.
 	\begin{itemize}
 		\item In macro, a graph generally helps
+	\end{itemize}
+	\item Make clear propositions so that others won't misunderstand.
+	\begin{itemize}
+		\item Bad: analyze the competitive pattern of inter-brand and intra-brand
+
+		Good: Analyze how the per store profit is affected by own-brand store density and competitors' store density
 	\end{itemize}
@@
 	\item Understand the result both mathematically and intuitively
-	\item When writing, write horizontally!
+	\item Visualization:
+	\begin{itemize}
+		\item If only the scale of number is important, use a \textit{plot} instead of table full of numbers
+	\end{itemize}
+	\item When writing on the board, write horizontally!
+\end{itemize}
+
+\vspace{1em}
+\noindent
+\textbf{Writings:}
+\begin{itemize}
+	\item Good writing samples: \cite{Berry:1992gl}, \cite{doi:10.3982/ECTA7699}
+	\begin{itemize}
+		\item \cite{doi:10.3982/ECTA7699}: a good example of illustrating clear empirical results
+	\end{itemize}
 \end{itemize}
@@
 \bibliographystyle{chicago}
-\bibliography{paper_notes}
+\bibliography{reference}
 

### 2019-03-27 paper_notes.tex
Add Wollman 2018 AER

@@
 
+``Note that $h^i_{x_j}$ selects observations based on product characteristics.
+For example, if the i th moment considers conventional vehicles only, then $h^i_{x_j}=1$  when the cabover , compact , and long dummy variables in $x_j$ equal 0, and $h^i_{x_j}=0$ otherwise.
+Further, $h^i_{x_j,t}$  depends on the demand shifters specific to the subset of product types and action under consideration.
+For example, the construction industry accounts for the largest proportion of medium GWR vehicles.
+Hence, if the i th moment considers the entry of medium GWR vehicle buyers, then $h^i_{x_j,t}=1$ for $t$ in which the proportion of prospective buyers from the construction industry is particularly high.
+Finally, $\tilde h^i_{f,x_j,t}=1$ selects observations such that either $j \in J _ { f , t - 1 }$ or 
+$j \notin J_{f, t-1}$ . For example, if the $i$th moment considers entry, then $\tilde h^i_{f,x_j,t}=1$ when $j \notin J_{f,t-1}$. 
+Note that $C$ is a constant equal to 1 if $\tilde h^i_{f,x_j,t}$ selects $j \notin J_{f,t-1}$ and equal to $- \lambda$ otherwise, as described below.''
+
 Things to be noted here:
@@
 \end{enumerate}
+
+\mytitle{Instrument Variables}
+
+As in many PPHI application papers, the IVs here are just a set of indicator functions to pick selected observations.
+
+The idea is to use demand side shifters to pick periods when certain types of products will surely be introduced, and to pick periods when certain types will surely be retired.
+For these instruments to be valid, it requires that there is no selection of $\nu_2$ in the subset of observations picked by instruments $h_i$.
+Why such $h_i$ will not induce the selection of $\nu_2$?
+This is like a \cite{Tamer:2003hi} argument. 
+If there are some periods that the demand for product $j$ is super high, then someone will introduce the product regardless of $\nu_2$.
+
+The key is that the structural error term $\nu_2$ is characteristic-year specific rather than firm-product-year specific, so while the inequalities vary at the firm-product-year level, the structural error term does not.
+At each time period, $\nu_{2,t}$ is a vector with 6 elements. The same $\nu_2$ applies to all firm-products as long as their characteristics are the same.
 

### 2019-12-03 paper_notes.tex
Add paper_note2

@@
 The problem in these cases are that selection (determing who is treated or observed) and outcomes may be correlated.
-2. Another is to identify the true coefficient in a linear regression when regressors are measureed with error.
+2. Another is to identify the true coefficient in a linear regression when regressors are measured with error.
 
@@
 \end{mdframed}
+
+\part{Education} % (fold)
+\label{prt:education_}
+
+\chapter{Charter School} % (fold)
+\label{sec:charter_school}
+
+\section{Singleton, 2019 AER} % (fold)
+\label{sec:singleton_2019_aer}
+
+\textbf{\bibentry{Singleton:2019uy}}
+
+This paper investigates the following questions:
+\begin{enumerate}
+	\item How the non-differentiated stipend will affect the entry decision of charter schools, and then further affect the admission diversity of students?
+	\item Once a charter school is established, it cannot screen students. But it can pre-screen students by choosing where to locate. Different locations have very different student compositions.
+\end{enumerate}
+
+% section singleton_2019_aer (end)
+
+% section charter_school (end)
+
+% part education_ (end)
 

### 2019-12-03 paper_notes_2.tex
Add paper_note2

\include{preamber}

\title{Technical Notes for Math, Theory, and Econometrics}
\author{Kaida Zhang}
\date{\today}

\begin{document}

\maketitle

\part{Statistics}

\chapter{Basics} % (fold)
\label{cha:basics}

\section{Distributions} % (fold)
\label{sec:distributions}

% section distributions (end)

\begin{que}
    The 1st-order statistic among 10 i.i.d. obs and the 10th-oder statistic among 100 i.i.d. obs, which one has larger mean? 
\end{que}

\begin{answer}
    The 1st-order among 10 has larger mean. Proof to be added.
\end{answer}

\begin{thm}[Law of Iterated Expectation]
    We have:
    \[E[A] = E_B[E[A \mid B]]\]
    and can be generalized to:
    \[E[A \mid B] = E_{C \mid B}[E[A \mid B,C] \mid C]\]
\end{thm}

% section basics (end)

\part{Causal Inference}

\chapter{Matching} % (fold)
\label{cha:matching}

\section{General Matching} % (fold)
\label{sec:general_matching}

\textbf{Glossary}

ATT: Average Treatment on Treat group

ATC: Average Treatment on control group

ATE: Average Treatment Effect (on population)

The general idea for matching is that after controlling for some observable variables $X$, the expected $Y_{0i}$ and $Y_{1i}$ shall be the same on both the treatment and control group. Notice that for treatment group, $E[Y_{0i}]$ is counterfactual, and vice versa for control group.

\begin{assp}[Conditional Mean Independence (CMI)]
    \[E\left[Y_{0i}|\red{D_i=1},X_i\right] = E\left[Y_{0i}|\red{D_i=0},X_i\right]\]
    \[E\left[Y_{1i}|\red{D_i=1},X_i\right] = E\left[Y_{1i}|\red{D_i=0},X_i\right]\]
\end{assp}
Obviously, the CMI is weaker than CIA (Conditional Independence).
CMI only requires the equivalence of \textit{expectation of potential outcome}, while CIA requires the equivalence of actual potential outcome.

We can form ATT:
\begin{align*}
    ATT &\equiv E[Y_{1i}-Y_{0i} | D_i = 1] \\
    &= E_{X_i|D_i=1} \left\{ E\left[Y_{1i}|D_i=1,X_i\right] - E\left[Y_{0i}|\red{D_i=1},X_i\right]  \right\}\\
    &= E_{\red{X_i|D_i=1}} \left\{ E\left[Y_{1i}|D_i=1,X_i\right] - E\left[Y_{0i}|\red{D_i=0},X_i\right]  \right\} \\
    &= E\left[Y_i|D_i=1\right] - E_{\red{X_i|D_i=1}} \{E\left[Y_{0i}|\red{D_i=0},X_i\right] \}
\end{align*}
The last expression are taken expectation over distribution $F(X_i|D_i=1)$, which is identified in the data.
Line 2 to line 3 relies on the \textit{assumption Conditional Mean Independence (CMI)}.
Notice that each part is identified,
thus ATT is identified as long as CMI is satisfied.

And similarly ATC:
\begin{align*}
    ATC &\equiv E[Y_{1i}-Y_{0i} | D_i = 0] \\
    &= E_{X_i|D_i=0} \left\{ E\left[Y_{1i}|D_i=0,X_i\right] - E\left[Y_{0i}|D_i=0,X_i\right]  \right\}\\
    &= E_{X_i|D_i=0} \left\{ E\left[Y_{1i}|D_i=1,X_i\right] - E\left[Y_{0i}|D_i=0,X_i\right]  \right\}\\
    &=  E_{X_i|D_i=0} \left\{ E\left[Y_{1i}|D_i=1,X_i\right] \right\} - E[Y_i|D_i=0]
\end{align*}

Since ATT and ATC are identified, it's natural that ATE are also identified:
\begin{align*}
    ATE = \Pr(D_i=1) \cdot ATT + \Pr(D_i=0) \cdot ATC
\end{align*}
Note that the treatment probability is unconditional and thus can be easily estimated from data.

But to \textbf{implement} the above estimand, we would need to estimate components like $E_{\red{X_i|D_i=1}} \{E\left[Y_{0i}|\red{D_i=0},X_i\right] \}$, which has to be estimated non-parametrically.

As a first step, suppose $X_i$ is discrete. 
Then:
\begin{align*}
    E_{\red{X_i|D_i=1}} \{E\left[Y_{0i}|\red{D_i=0},X_i\right] \}
    = \sum_x E\left[Y_{0i}|\red{D_i=0},X_i = x\right] p(x|D_i=1)
\end{align*}
where we can estimate $p(x|D_i=1)$ as:
\begin{align*}
    \hat p(x|D_i=1) = \frac{\sum_{i=1}^{N} {1(X_i=x,D_i=1)}}{\sum_{i=1}^{N} {1(D_i=1)}}
\end{align*}
and the estimator for ATT is given by:
\begin{align*}
    \widehat {ATT} = \sum_{x} \left [
    \frac{\sum_{i=1}^{N} {1(X_i=x,D_i=0)Y_i}} {\sum_{i=1}^{N} {1(X_i=x, D_i=0)}} \cdot \hat p(x|D_i=1)
    \right ]
\end{align*}

With continuous $X$, the exact match cannot be executed and we would need to use some Kernel smooth. \red{To be added.}

\section{Propensity Score}
\label{sec:propensity_score}

The core idea of propensity score is to use appropriate weights to in the control units to reproduce the covariates distribution in the treatment group. 
And we can use a single dimension score to summarize the selection bias.
If we have enough data and all covariates are discrete, then we can simply calculate the propensity score by grouping data into stratum and simply counting the conditional probability of being treated in each stratum.
If we have continuous covariates, then we need some model (typically a logit or probit) to estimate the propensity score.

The propensity score would be sufficient to estimate both ATT and ATC. 
By simple Bayes rule we can calculate $Pr(X_i = x | D_i=1)$:
\begin{align*}
    Pr(X_i = x | D_i=1) = \frac{\Pr(D_i=1|X_i=x)\Pr(X_i=x)}{\Pr(D_i=1)}
\end{align*}
then we can form $\widehat{ATT}$ as in previous section.

\begin{thm}[Propensity Score Theorem]
    If CIA is satisfied, i.e. $\{Y_{0i},Y_{1i}\} \bot D_i \mid X_i $, then $\{Y_{0i},Y_{1i}\} \bot D_i \mid P(X_i) $. Here $P(X_i) \equiv \Pr(D_i=1|X_i)$
\end{thm}

\begin{proof}
    To be added. MHE p.81.
\end{proof}

Though we can use Bayes rule and the stratum to estimate ATE, this way is actually tedious. A easier way below, notice that:
\footnote{Recall: $p(X_i)\equiv \Pr(D_i=1|X_i)$}
\begin{align*}
    E[\frac{Y_i D_i}{p(X_i)}] &= E_{X_i}\{E[\frac{Y_i D_i}{p(X_i)} | X_i]\} \\
    &= E_{X_i} \{E[\frac{Y_i\cdot 1}{p(X_i)}p(X_i) + \frac{Y_i\cdot 0}{p(X_i)}(1-p(X_i))]\} \\
    &= E_{X_i}\{E[Y_i | D_i=1,X_i]\} \\
    &= E_{X_i}\{E[Y_i | X_i]\} \\
    &= E[Y_{1i}]
\end{align*}
Similarly, we have $E[\frac{Y_i(1-D_i)}{1-p(X_i)}] = E[Y_{0i}]$. 
Given propensity score $p(X_i)$, we can form an empirical estimator.
\begin{align*}
    E[Y_{1i}-Y_{0i}] &= E[\frac{Y_i D_i}{p(X_i)}] - E[\frac{Y_i(1-D_i)}{1-p(X_i)}]\\
    &= E[
    \frac{(D_i- p(X_i))Y_i}{p(X_i)(1-p(X_i))}
    ]
\end{align*}
Simply replacing $E[\cdot]$ by $\frac{1}{N} \sum_{i=1}^N$ gives us the empirical counterpart for this estimator.
This estimator also reveals the close relationship between regression estimator and matching estimator (below following MHE p.82).

\chapter{Instrument Variables} % (fold)
\label{cha:instrument_variables}

\textbf{2SLS}

The most basic instrument variable framework is:
\[
    y_i = \alpha + \beta X_i + \rho s_i + \varepsilon_i
\]
we are interested in $\rho$ while $s_i$ is correlated with $\varepsilon_i$.
But if we have some \textit{exclusion variable} $z_i$ which is uncorrelated with $\varepsilon_i$ but is correlated with $s_i$, then we can form a first stage estimation:
\[
    s_i = \delta X_i + \gamma z_i + \eta_i
\]
Plug into the initial problem:
\[
    y_i = \alpha + (\beta + \rho \delta)X_i + \rho \gamma z_i + (\rho \eta_i + \varepsilon_i)
\]
this equation can be consistently estimated since all covariates are exogenous.
Also note that the first stage also can be estimated. So we now can identify $\rho$:
\[
    \rho = \frac{\rho \gamma}{\gamma}
\]
where the denominator is estimated from first stage and numerator from second stage.

Some important cases where $z_i$ is a valid or invalid IV: (from Cyrus's lecture notes)
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\linewidth]{images/iv-direct-graph.png}
    \includegraphics[width=0.5\linewidth]{images/iv-direct-figure2.png}
\end{figure}
The last case is especially interesting.
Notice that in the last case we should \textit{not} control over $\varepsilon$ because that is a collider. Also the one with $W$ as collider.
So it actually does not matter how $z$ and $s$ are correlated, $z$ does \textit{not} have to have causal effect on $s$.

\textbf{Wald Statistic}

If the IV $z_i$ is a binary variable, then 2SLS is Wald statistic.
For Wald statistic:
\[
    \rho = \frac{E[y_i | z_i =1] - E[y_i | z_i=0]}
    {E[s_i | z_i =1] - E[s_i|z_i=0]}
\]
The intuition is straightforward,
since the only channel for $z_i$ to influence $y_i$ is through $s_i$.

\textbf{GMM Framework}

We can also do IV in GMM framework.
The benefit of using GMM is to have variance correct.
\[
    E [Z(Y - \beta X)] = 0
\]

\chapter{Diff in Diff} % (fold)
\label{cha:diff_in_diff}

The Diff-in-Diff estimators family include:
\begin{itemize}
    \item Plain diff-in-diff
    \item Synthetic control. See \citet{AbadieDiamondHainmueller2010}, \citet{Xu2017}
\end{itemize}

\chapter{Network Effect}
\label{cha:network_effect}

Network in Migration:
\begin{itemize}
    \item \citet{BayerRossTopa2008} leverages two effects: 1) the network effect is very local (say block); 2) the matching of unobservables happen at a larger neighborhood level. Then the migration difference of blocks within the same group can be attributed to network effects.
    \item \citet{StuartTaylor2019,StuartTaylor2019a}. They propose a new index to measure network effects, using individual level migration data.
\end{itemize}

\section{Bayer, Ross, Topa, 2008 JPE} % (fold)
\label{sec:bayer_ross_topa_2008_jpe}

\textbf{\fullcite{BayerRossTopa2008}}

This paper is the first one that uses the geographic in local areas to identify the network effects.
The identification assumption of their paper is:
\begin{enumerate}
    \item The network effect is very local (say block level);
    \item The matching of unobservables happen at a larger neighborhood level (say Census block group level)
\end{enumerate}

Their baseline regression is:
\[
    W_{i j}^{b}=\rho_{g}+\alpha_{0} R_{i j}^{b}+\varepsilon_{i j}
\]
where $i,j$ are two different individuals, $W_{ij}^b$ is a dummy which equals 1 if $i,j$ works in the same block; 
$R_{ij}^b$ equals 1 if they reside in the same block; 
$\rho_g$ is the fixed effect at block level.
The parameter of interest is $\alpha_0$

% section bayer_ross_topa_2008_jpe (end)

\section{Stuart, Taylor, 2019 (wp)} % (fold)
\label{sec:stuart_taylor_2019_wp}

\textbf{\fullcite{StuartTaylor2019}}

The basic idea of this paper is to use a diff-in-diff style estimator.
Pick two similar born towns $j$ and $j'$, which should have similar ex-ante migration probability to another town $k$.
Then the observed migration difference $D_{jk}$ and $D_{jk'}$ is explained by the network effect. 
They propose a simple index to capture the network effect, and they allow the network effect to differ across the destination towns.

The baseline regression is: (modified from \cite{BayerRossTopa2008})
\[
    D_{i, j(i), k} D_{i^{\prime}, j\left(i^{\prime}\right), k}=\alpha_{g, k}+\sum_{j \in g} \beta_{j, k} 1\left[j(i)=j\left(i^{\prime}\right)=j\right]+\epsilon_{i, i^{\prime}, k}
\]
where $j$ is the birth town of $i$, $k$ is the destination, $D_{i,j,k}$ is a dummy which equals 1 if $i$ moves from $j$ to $k$; $g$ is a group of towns where it is assumed that the ex-ante moving probability within the same group is the same.
the parameter of interest is $\beta_{j,k}$.
They show the following things:
\begin{enumerate}
    \item $\beta_{j,k} = C_{j,k}$, where $C_{j, k} \equiv \sum_{i \neq i^{\prime} \in j} \operatorname{Cov}\left[D_{i, j, k}, D_{i^{\prime}, j, k}\right] /\left(N_{j}\left(N_{j}-1\right)\right)$ being the average covariance of the location decisions for two migrants from the same town;
    \item $\alpha_{g,k} = P^2_{g,k}$, where $P_{j, k} \equiv \mathbb{E}\left[D_{i, j, k}\right]$ is the \textit{ex-ante} probability of an individual migrating from $j$ to $k$.
\end{enumerate}
Their main argument: $\beta_{j,k}$ does not well capture the network effect, because it varies with ex-ante moving probability $P_{j,k}$:
\[
    \beta_{j,k} = C_{j,k} = P_{g,k}(\mu_{j,k} - P_{g,k})
\]
where $\mu_{j, k} \equiv \mathbb{E}\left[D_{i, j, k} | D_{i^{\prime}, j, k}=1\right]$.

To overcome this problem, they propose a intuitive network index $\Delta_{j,k}$, which captures the expected increase in the number of people from birth town $j$ that move to destination $k$:
\[
    \Delta_{j, k} \equiv \mathbb{E}\left[N_{-i, j, k} | D_{i, j, k}=1\right]-\mathbb{E}\left[N_{-i, j, k} | D_{i, j, k}=0\right]
\]
they show that $\Delta_{j,k}$ can be derived from observable moving patterns:
\[
    \Delta_{j, k}=\frac{\left(\mu_{j, k}-P_{g, k}\right)\left(N_{j}-1\right)}{1-P_{g, k}}=\frac{C_{j, k}\left(N_{j}-1\right)}{P_{g, k}-P_{g, k}^{2}}
\]

% section stuart_taylor_2019_ (end)

% chapter diff_in_diff (end)

\part{IO} % (fold)
\label{prt:io}

\chapter{Demand Estimation} % (fold)
\label{cha:demand_estimation}

\section{Villas-Boas, 2007 RES} % (fold)
\label{sec:villas_boas_2007_res}

\textbf{\fullcite{Villas-Boas2007}}

The main goal of this paper is to recover the margins of both retailers and whosalers with only retailing data.

The demand side is typical BLP with random coefficients $\alpha_i, \beta_i$:
\[
    U_{i j t}=d_{j}+d_{t}+x_{j t} \beta_{i}-\alpha_{i} p_{j t}+\xi_{j t}+\epsilon_{i j t} \tag{1}
\]

The paper focuses on the vertical structural of the supply side.

\paragraph{Scenario 1: simple linear pricing model}

The retailer profit function is:
\[
    \pi_{r t}=\sum_{j \in S_{r t}}\left[p_{j t}-p_{j t}^{w}-c_{j t}^{r}\right] s_{j t}(p)
\]
and we can write FOC for product $j$ of retailer $r$:
\[
    s_{j t}+\sum_{m \in S_{r t}}\left[p_{m t}-p_{m t}^{w}-c_{m t}^{r}\right] \frac{\partial s_{m t}}{\partial p_{j t}}=0 \quad \forall j \epsilon S_{r t}, \quad \text { for } r=1, \ldots, N_{r}
    \tag{5}
\]
which is equivalent to the following equation holds for all commodities in the market $\mathcal J$:
\[
    s_{it} + \sum_{j \ in \mathcal J} [p_{jt} - p^w_{jt} - c^r_{jt}] \mathds 1\{i,j \in \mathcal J_r\} \frac{\partial s_{jt}}{ \partial p_{it}} = 0,\ \  \forall i \in \mathcal J
\]

Then stack all products in the market together in the market (this step is tricky):
\[
    p_{t}-p_{t}^{w}-c_{t}^{r}=-\left(T_{r} * \Delta_{r t}\right)^{-1} s_{t}(p)
\]
where $T_r$ is the ownership matrix, $T_r(i,j)$ equals to 1 if $i,j$ belong to the same owner, other wise 0. 
$\Delta_{rt}$ is the retailer's response matrix, $\Delta_{rt}(i,j)= \frac{\partial s_{jt}}{\partial p_{it}}$.
Both $p^w_t$ and $c^r_t$ are unobservable, other parts are observable. 
$\Delta_{rt}$ is estimated from the demand side.

Similarly, for wholesaler we have:
\[
    \pi_{w t}=\sum_{j \in S_{w t}}\left[p_{j t}^{w}-c_{j t}^{w}\right] s_{j t}\left(p\left(p^{w}\right)\right)
\]
the corresponding FOC is:
\[
    s_{j t}+\sum_{m \in S_{w t}}\left[p_{m t}^{w}-c_{m t}^{w}\right] \frac{\partial s_{m t}}{\partial p_{j t}^{w}}=0 \quad \forall j \epsilon S_{w t}, \quad \text { for } w=1, \ldots, N_{w}
\]

The $\frac{\partial s_{m t}}{\partial p_{j t}^{w}}$ for wholesalers are very complicated, because the wholesale price change in one product will induce all retailers to re-optimize their products.
Let $\Delta_{wt}(i,j)$ be $\frac{\partial s_{m t}}{\partial p_{j t}^{w}}$.
First notice that $\Delta_{wt} = \Delta_{pt}'\Delta_{rt}$, where $\Delta_{pt}$ is the derivative matrix of retail price to wholesale price. 
So the key for wholesaler FOC is to find $\Delta_{pt}$.
To obtain this, do total differentiation for all retail prices $dp_k,k=1,\ldots,N$ with respect to a wholesale price $p^w_f$ in the optimization equation (5) of retailers:
\[
    \sum_{k=1}^{N} \underbrace{\left[\frac{\partial s_{j}}{\partial p_{k}}+\sum_{i=1}^{N}\left(T_{r}(i, j) \frac{\partial^{2} s_{i}}{\partial p_{j} \partial p_{k}}\left(p_{i}-p_{i}^{w}-c_{i}^{r}\right)\right)+T_{r}(k, j) \frac{\partial s_{k}}{\partial p_{j}}\right]}_{g(j, k)} d p_{k} - 
    \underbrace{T_{r}(f, j) \frac{\partial S_{f}}{\partial p_{j}}}_{h(j, f)} d p_{f}^{w}=0
\]
Stack all products together, we have:
\[
    \frac{d p}{d p_{f}^{w}}=G^{-1} H_{f}
\]
where $G,H$ are matrixes for $g,h$ respectively.
Thus the FOC of wholesalers can be written as:
\[
    p_{t}^{w}-c_{t}^{w}=-\left(T_{w} * \Delta_{w t}\right)^{-1} s_{t}(p)
\]

% section villas_boas_2007_res (end)

\chapter{Dynamic Estimation}
\label{cha:dynamic_estimation}

\citet{Rust1987} proposes Fixed Nested Point approach.
The bad thing is computation complexity.

\section{Hendel, Nevo, 2006 EMCA} % (fold)
\label{sec:hendel_nevo_2006_emca}

\textbf{\fullcite{HendelNevo2006}}

This paper estimates a model with consumer storage. 
They solved two problems: 
1) the inventory (a state variable) is unobservable to researchers;
2) the state space is too large.

A key feature of their model is that they can separate a static problem from the dynamic problem, and use that static problem to estimate the purchasing utility parameters, which includes the brand heterogeneity.
The dynamic problem is then independent of brand, but solely quantity related.

\paragraph{Model}

The flow utility is assumed to be:
\[
    u\left(c_{h t}, \nu_{h t} ; 
    \boldsymbol{\theta}_{h}\right)+\boldsymbol{\alpha}_{h} m_{h t}
\]
where $c_{ht}$ is the quantity consumed (not purchased) by consumer $h$ in time $t$; 
$m_{ht}$ is the consumption of the outside good.
Note that $c_{ht}$ is assumed to be the total consumption of all brands: 
$c_{ht} \equiv \sum_{j} c_{jht}$. 
This implies: 
1) the consumption has no brand preference;
2) the consumption will not be affected by which brand is at storage.

Then we can write the dynamic problem:
\begin{align*}
    V\left(s_{1}\right)
    &{=\max _{\left\{c_{h}\left(s_{t}\right), d_{h j}\left(s_{t}\right)\right\}} \sum_{t=1}^{\infty} \delta^{t-1} E[u\left(c_{h t}, \nu_{h t} ; \boldsymbol{\theta}_{h}\right)-C_{h}\left(i_{h, t+1} ; \boldsymbol{\theta}_{h}\right)}\\
    & +\sum_{j} d_{h j x t}\left(\alpha_{h} p_{j x t}+\xi_{h j x}+\beta_{h} a_{j x t}+\varepsilon_{h j x t}\right) | s_{1}]
\end{align*}
\[
    \begin{array}{ll}{\text { s.t. } \quad 0 \leq i_{h t}, \quad 0 \leq c_{h t},} & {0 \leq x_{h t}, \quad \sum_{j, x} d_{h j x t}=1} \\ {} & {i_{h, t+1}=i_{h t}+x_{h t}-c_{h t}}\end{array}
\]
where $i_{ht}$ is the inventory of consumer $h$ at time $t$; 
$d_{hjxt}$ equals 1 if brand $j$ and size $x$ is purchased;
$C_h$ is the storage cost;
$a_{jht}$ is the advertising variable.

Notice, the purchasing per se (in addition to the following consumption) has utility here, which I do not understand.
Also, the product differentiation takes place at \textit{purchase}, not \textit{consumption}.
As mentioned by the authors, this assumption ``helps reduce the state space. Instead of the whole vector of brand inventories, only the total quantity in stock matters, regardless of brand.''

\paragraph{Estimation}

The estimation process of this dynamic problem is not trivial.
First, the state variable inventory $i_t$ is not observable.
Second, the state space include brand, variety, price and advertisements, which is very large and intractable.

To solve the unobservable inventory problem, they use the fact that the optimal consumption can be calculated. 
For this moment assume that the inventory $i_t$ is observable, then the researcher can derive the optimal consumption $c_t$ since all state variable now observable.
Then the researcher can derive the purchasing probability $d_{t+1}$ which is observed in the data, and, therefore, derive $i_{t+1}$.
The probability of the observed sequence of purchases is:
\[
    \begin{array}{l}{\operatorname{Pr}\left(d_{1} \cdots d_{T} | p_{1} \cdots p_{T}\right)} \\ {\quad=\int \prod_{t=1}^{T} \operatorname{Pr}\left(d_{t} | p_{t}, i_{t}\left(d_{t-1}, \ldots, d_{1},\right.\right.} \\ 
    \quad \quad \quad \quad \quad \quad {\left.\left.\nu_{t-1}, \ldots, \nu_{1}, i_{1}\right), \nu_{t}\right) d F\left(\nu_{1}, \ldots, \nu_{T}\right) d F\left(i_{1}\right)}\end{array}
\]
where $F(i_1)$ is observed in the data.

\paragraph{Dimension Reduction}

The dimension is too high for practical estimation.
So the paper uses \textit{inclusive value} to reduce the dimension. 
The steps are as following:
\begin{enumerate}
    \item Estimate the static parameters, which are purchasing utility parameters;
    \item Simplify the state of DP using inclusive value;
    \item Use nested fixed point to estimated the simplified DP problem.
\end{enumerate}

Recall that the consumption utility does not depend on the brand but only on the quantity; then it is natural that the optimal consumption depend only on the quantity of storage, independent of the brand. (details see their lemma 1)
This is an important assumption for them to separate the consumption and the purchasing. 
Then it's convenient to define:
\[
    M\left(s_{t}, j, x\right)
    \equiv \operatorname{Max}_{c}\left\{u\left(c+\nu_{t}\right)-C\left(i_{t+1}\right)+\delta E\left(V\left(s_{t+1}\right) | d_{j x}, c, s_{t}\right)\right\}
\]
The above paragraph is saying that, conditional on quantity $x$, $M(s_t,j,x)=M(s_t,j',x)$.
Then it's direct to show that:
\[
  \begin{aligned} \operatorname{Pr}\left(d_{j t}=1 | x_{t}, i_{t}, p_{t}, \nu_{t}\right) &=\frac{\exp \left(\alpha p_{j x t}+\xi_{k x}+\beta a_{k x t}\right)}{\sum_{k} \exp \left(\alpha p_{k x t}+\xi_{k x}+\beta a_{k x t}\right)} \\ &=\operatorname{Pr}\left(d_{j t}=1 | x_{t}, p_{t}\right) \end{aligned}  
\]
Using conditional probability rule, we can rewrite the joint choice probability of $j$ and $x$ to be:
\begin{align*}
\operatorname{Pr}\left(d_{j t}=1, x_{t} | p_{t}, i_{t}, \nu_{t}\right)&=
\operatorname{Pr}\left(d_{j t}=1 | p_{t}, x_{t}, i_{t}, \nu_{t}\right) 
\operatorname{Pr}\left(x_{t} | p_{t}, i_{t}, \nu_{t}\right) \\
&= \operatorname{Pr}\left(d_{j t}=1 | x_{t}, p_{t}\right) 
\operatorname{Pr}\left(d_{j t}=1 | p_{t}, x_{t}, i_{t}, \nu_{t}\right) 
\end{align*}
In the first step, we estimate the first part separately, which give us purchasing utility parameters.

Then in the second step, we show that the DP problem can be simplified using the inclusive value.
The inclusive value $\omega_{xt}$ is defined as:
\[
    \omega_{x t}=\log \left\{\sum_{k} \exp \left(\alpha p_{k x t}+\xi_{k x}+\beta a_{k x t}\right)\right\}
\]
Notice that the $\omega_{xt}$ is known up to parameters which can be estimated in the first step.
This simplifies the DP problem because $\omega_{xt}$ is a scalar, so we do not have to track the price distribution for different brands.
So if we can rewrite the DP using $\omega_{xt}$, we solve the problem of 
It can be shown that the DP problem is equivalent to the below DP using the inclusive value: (see their appendix for proof)
\[
    \begin{array}{l}{V\left(i_{t}, \omega_{t}, \varepsilon_{t}, \nu_{t}\right)} \\ {\quad=\operatorname{Max}_{\{c, x\}}\left\{u\left(c+\nu_{t}\right)-C\left(i_{t+1}\right)+\omega_{x t}+\varepsilon_{x t}\right.} \\ 
    \quad \quad \quad {\left.\quad+\delta E\left[V\left(i_{t+1}, \omega_{t+1}, \varepsilon_{t+1}, \nu_{t+1}\right) | i_{t}, \omega_{t}, \varepsilon_{t}, \nu_{t}, c, x\right]\right\}}\end{array}
\]
The key of the proof is to use the fact that all error terms are i.i.d. and T1EV distributed, so there is a closed form of expected maximum utility over alternative brands, which is $\omega_{xt}$.

With this, we can calculate the probability of a particular purchasing sequence using previous chain method.

% section hendel_nevo_2006_emca (end)

% chapter demand_estimation (end)

\chapter{Observational Learning} % (fold)
\label{cha:observational_learning}

Empirical Observational Learning:
\begin{itemize}
    \item Literature Review: \textcite{Sorensen2017}
    \item IO: \textcite{Moretti2011}, \textcite{HendricksSorensenWiseman2012}, \textcite{Newberry2016}, \textcite{LiWu2019}, \textcite{HollenbeckMoorthyProserpio2019}
    \item Development: \textcite{BobonisFinan2009}, \textcite*{AngelucciDeGiorgiRangelEtAl2010}, \textcite*{BursztynEdererFermanEtAl2014}
\end{itemize}

The \textit{observational learning} is often frequently associated with \textit{peer effects}.
Observational learning can be seen as a mechanism underlying peer effect \citep{BursztynEdererFermanEtAl2014}.

% chapter observational_learning (end)

\part{Education}

\chapter{Demand for Education}

A huge literature in school choice:
\begin{itemize}
    \item Theory paper: \textcite{BarseghyanClarkCoate2019}
    \item Empirical paper: \citet{HastingsKaneStaiger2009}, \citet*{DemingHastingsKaneEtAl2014}, \citet*{BurgessGreavesVignolesEtAl2015}, \textcite{Walters2018}
    \item Combine with location choice:   
    \begin{itemize}
        \item Methodology paper combining residential sorting with school choice: \textcite{Rothstein2006}, \textcite{BayerTimmins2007}, \textcite{BayerFerreiraMcMillan2007}, \textcite{BayerMcMillan2010}, \Textcite{BayerMcMillanMurphyEtAl2016}
        \item Empirical: \textcite{CordesSchwartzStiefel2019} uses NYC residential data to study the effect of mobility; \citet{EppleJhaSieg2018} seems to also estimate a demand model with student sorting
    \end{itemize}
\end{itemize}

Some other papers focus more on the school competition:
\begin{itemize}
    \item Reduced form: \textcite{Lavy2010} uses DiD and border discontinuity to show that the school competition in Tel-Aviv has positive results.
\end{itemize}

There are certain reasons why the competition among schools will not work.
\begin{enumerate}
    \item Schools (principals and teachers) may lack the incentive to correspond to the competition
    \item Schools may lack the flexibility to change. E.g. they cannot fire under-qualified teachers at their own discretion.
    \item Families may lack incentive to correspond to the ``value added'' of schools, but simply prefer schools with better peers \parencite{AbdulkadirogluPathakSchellenberg2017,MacLeodUrquiola2015,MacLeodUrquiola2019}.
    \item Families may not be able to identify effective schools \parencite{AllendeGallegoNeilson2018}
\end{enumerate}

Heterogeneous student response to inputs:
\begin{itemize}
    \item \textcite{Bau2019} shows that rich students are more responsive to quality.
    \item \textcite{JacksonJohnsonPersico2016} shows that school inputs are more valuable to poor students (p.192)
\end{itemize}

Endogenous school differentiation:
\begin{itemize}
    \item \textcite{MacLeodUrquiola2012}, \textcite{GilrainePetronijevicSingleton2019}
\end{itemize}

\subsection*{Review: Demand for schools}

\paragraph{\citet{HastingsKaneStaiger2009}}
They use a simple exploded logit model to show that the demand for high academic quality is heterogeneous across families.
The more affluent families put higher weights on academic performance, but poorer families and minorities put higher weights in the race composition of the school.

Cons:
\vspace{-1em}
\begin{enumerate}
    \item In their utility function (4), they directly include school average test score $S_j$, which is obviously endogenous of student composition. They do not deal with this using IV.
    \item They do not have an unobserved attractiveness term $\xi_j$ as BLP in the utility.
\end{enumerate}

\paragraph{\citet{EppleJhaSieg2018}}

The main contribution of this paper is that they incorporate the peer effects into demand estimation. 
They also deal with the limited capacity problem by introducing a \textit{shadow price} for over-subscribed schools.
Note that this is actually tricky, because when they estimate the demand, they assume no capacity constraint, and the constraint only holds in computing the counterfactual equilibrium.

The main contribution of their paper is an algorithm of calculating the counterfactual equilibrium with peer effects.
The demand estimation part is quite standard.
They use MLE for the demand estimation.

Cons:
\begin{enumerate}
    \item The demand estimation does not consider the capacity constraint
    \item The location sorting is not considered in the model
\end{enumerate}

\section{Review: School Competition} % (fold)
\label{sec:review_spillover_effects}

\subsection*{Charter School Spillover Effects}

\paragraph{\citet*{BookerGilpatricGronbergEtAl2008}}

This paper uses a longitudinal data in Texas to show that charter schools in Texas have positive spillovers in nearby TPS.
They use panel data to control student/campus fixed effect to exclude the sorting effect.
They focus on the response at district level instead of campus level.
One charter school nearby increase the Math and Reading test score by 0.021 sd; as a comparison, those who move to another campus have a negative effect of 0.104 sd on Math. 
They also find the effect is more salient for black and Hispanic students.

% section review_spillover_effects (end)

\section{Bayer, Timmins, 2007 EJ} % (fold)
\label{sec:bayer_timmins_2007_ej}

\textbf{\fullcite{BayerTimmins2007}}

This paper proposes a way to estimate the local spillover effects (summarized by the share of people living in location $j$, $\sigma_j$).
The basic idea is to use the BLP framework, but have $\sigma_j$ in the utility function.
They show that there is no need to exactly solve the model, and the complication mainly comes from multi-equilibria phenomena which they solve by proposing a semi-likelihood estimator as in BBL.
They do not encompass the followings in the paper: the endogenous price, the school choice problem. But both should be not difficult to deal with.

The utility is:
\begin{align}
    U_{i, j}=\mathbf{X}_{j}^{\prime} \boldsymbol{\beta}_{i}+\alpha_{i} \sigma_{j}+\xi_{j}+\varepsilon_{i, j}
\end{align}
Note:
\begin{itemize}
    \item $\sigma_j$ is share of individuals who choose location $j$. This is definitely endogenous since it's determined in the equilibrium, and needs to be instrumented.
    \item There is no price included in above utility. If included, needs additional instrument for price.
    \item Other parts are standard BLP
\end{itemize}

\textbf{Equilibrium:}

Given $\sigma,\xi$ (both being vector), the individual choice probability is:
\[
    P_{i, j}=g_{i, j}\left(\mathbf{Z}_{i}, \mathbf{X}, \boldsymbol{\sigma}, \xi\right) \forall i, j
\]
where we have the closed from for $g(\cdot)$ if $\varepsilon_{i,j}$ follows i.i.d. T1EV.

Aggregate over individuals and we get the shares:
\[
    \sigma_{j}=\int g_{i, j}\left(\mathbf{Z}_{i}, \mathbf{X}, \boldsymbol{\sigma}, \xi\right) \mathrm{d} h(\boldsymbol{Z}) \forall j
\]
where $h(Z)$ is the density of $Z$ in the population, which is known. 
KZ: notice that we can use Nevo strategy if we can observe individual level demographics.

Then the above two equations define the equilibrium. 
The uniqueness is not guaranteed in general, unless the local spillover effects $\alpha_i$ are constrained to be negative.
See \textcite{BayerMcMillan2010} for more details on uniqueness conditions.

\textbf{Estimation:}

Sketch:
\begin{itemize}
    \item The estimation is basically BLP, but we need to find instruments for market shares $\sigma_j$. The two steps approach below is very similar to that in \citet{Hackmann2019}.
    \item The equilibrium may have multiple equilibria, needs to be dealt with. The authors pick an equilibrium selection rule $P(\sigma | \Omega)$ and non-parametrically estimate this probability along with the likelihood. But other more robust approach may be used as well, like the moment inequality in \citet{CilibertoTamer2009}.
    \item Step 1: Estimate $\delta_j$ as fixed effects, as well as $\beta_1, \alpha_1$
    \item Step 2: Estimate the mean utility parameters within $\delta_j$
\end{itemize}

First rewrite the utility function to be the addition of mean utility $\delta_j$ and idiosyncratic utility part:
\[
    U_{i, j}=\delta_{j}+\mathbf{X}_{j}^{\prime} \mathbf{Z}_{i} \boldsymbol{\beta}_{1}+\sigma_{j} \mathbf{Z}_{i} \boldsymbol{\alpha}_{1}+\varepsilon_{i, j}
\]
where
\[
    \delta_{j}=\mathbf{X}_{j}^{\prime} \boldsymbol{\beta}_{0}+\alpha_{0} \sigma_{j}+\xi_{j}
\]

Since the possibility of multiple equilibria, the likelihood is not well defined. 
The authors then define $P(\sigma | \Omega)$ as the equilibrium selection rule, where $\Omega$ contains exogenous data $\{X,Z\}$ and parameters $\left\{\delta, \alpha_{1}, \beta_{1}, \Sigma\right\}$.
Importantly, $\Omega$ does not contain unobservable individual level shocks $\varepsilon_{ij}$.
\[
    L=P(\boldsymbol{\sigma} | \mathbf{\Omega}) \prod_{i} \prod_{j} P_{i}(j | \boldsymbol{\sigma}, \mathbf{\Omega})^{I_{i j}}
\]
Here, $P(\sigma | \Omega)$ does not need to be estimated! (see later); and for given $(\sigma, \Omega)$, the $P_i(j)$ can be calculated.
\blue{Importantly,} different from standard entry model in IO like \citet{CilibertoTamer2009}, here our equilibrium selection rule does not depend on unobservable terms $\varepsilon_{ij}$.
This relies on the assumption that for all observable $\{X,Z\}$, there are continuum number of consumers with different $\varepsilon_{ij}$.
This is similar to the incompelete information assumption made in \citet{Seim2006}.
Therefore, the likelihood of the two components are orthogonal to each other, and we can estimate the second part only, assuming that each individual behaves optimally in the \textit{observed} equilibrium.

\textbf{Instruments:}

\blue{The instruments are the most important contribution of this paper.}

In the first step MLE, where the mean utility $\delta_j$ is estimated as a fixed effect, we do not need IV.
But we use GMM to estimate the parameters within mean utility, then we need IV.
We need IV because $\sigma_j$ is correlated with $\xi_j$. So we need IV which is correlated with $\sigma_j$ but uncorrelated with $\xi_j$.

The IV chosen here are similar to BLP IV, they choose the fixed attributes of other (nearby) locations.
They further uses a function to summarize the impact of such fixed attributes to a single instrument of share.
``This corresponds to using the predicted share of individuals that chooses a location based only on the observed, exogenous choice and individual characteristics used in the model, ignoring the role of local spillovers. ''

For the identification to really work, one needs some choice set variations. 
For example, there are several markets and in each market the consumers will have different choice sets.
Their table 3 shows that IV approach performs poorly without choice set variation.

% section bayer_timmins_2007_ej (end)

\section{Bayer, McMillan, 2010 wp} % (fold)
\label{sec:bayer_mcmillan_2010_wp}

\textbf{\fullcite{BayerMcMillan2010}}

The main purpose of this paper is to investigate whether the schools will respond to the competition. 
\[
    T^{m}=X_{c}^{m} \gamma_{c}+X_{n}^{m} \gamma_{n}+\gamma_{E} E^{m}+\varepsilon^{m}
\]
where $T^m$ is the average test score for school $m$, $X_c$ for household characteristics, $X_n$ for neighborhood controls, $E^m$ is the slope for demand-quantity curve.
The parameter of interest is $\gamma_E$.
Assume that the only unobservable is the school and teacher effort.
Think of the two polarized cases:
1) the school only cares about its teaching quality;
2) the school is rent seeking.
If the school only cares about teaching quality, then the schools' production function shall not be related with the competition, but only related with the observables and we can control that. 
\red{This claim is tricky.}
But if the school is rent seeking, then the schools face the following trade-offs: raising quality (by raising effort) can make the school more attractive which is valuable, but the induced higher effort is also costly.
Whether increasing quality is worthwhile depends on the responsiveness of demand to quality, the $E^m$.

Since $E^m$ is not observed directly in the data, it needs to be estimated.
They use \texttt{housing price} as the proxy for demand and use \texttt{school average test scores} as proxy for quality, conditional on school and student characteristics.
\blue{KZ: notice this quality is ``net quality'', trying to capture the effort induced quality.}
In order to overcome the endogeneity, they construct a discrete choice model, simultaneously choosing schools and locations, using BLP and methods in \textcite{BayerFerreiraMcMillan2007}.
\blue{Learn this technique.}
Then they conduct the counterfactual by increasing the test score of school $m$ by 1 s.d., then re-estimate the model and see how much the housing price will increase.
The resulting change captures the responsiveness of demand to quality.

% section bayer_mcmillan_2010_wp (end)

\chapter{School Finance} % (fold)
\label{cha:school_finance}

\textcite{JacksonJohnsonPersico2016} uses the School Finance Reforms (SFR) as exogenous variations of funding levels across school districts.
They use this variation to conduct DiD to show that higher expenditure will improve the student performance.

\clearpage
\singlespacing
\printbibliography
% \setlength\bibsep{0pt}
% \renewcommand\refname{Reference}
% \bibliographystyle{chicago}
% \bibliography{/Users/mac/Dropbox/Academic_Writings/reference-mac.bib}
% \bibliography{C:/Users/Kaida/Dropbox/Academic_Writings/reference-win.bib}

\end{document}

### 2019-12-03 preamber.tex
Add paper_note2

--- 2019-03-24 paper_notes.tex
@@
 \documentclass{book}
-\usepackage[utf8]{inputenc}
+% \usepackage[utf8]{inputenc}
 
-\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,graphicx,caption,color,setspace,sectsty,comment,footmisc,caption,pdflscape,subfigure,array,hyperref}
+\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,graphicx,caption,color,setspace,sectsty,footmisc,caption,array,hyperref,dsfont}
 
@@
 \setlength{\parskip}{1em}
-\renewcommand{\baselinestretch}{1.5}
+% \renewcommand{\baselinestretch}{1.5}
 
@@
 \usepackage{mathrsfs}
-\usepackage{hyperref}
 
-\usepackage{natbib}			% to insert citations
+% \usepackage{natbib}			% to insert citations
+\usepackage[natbib,authordate,noibid,backend=biber]{biblatex-chicago}
+\addbibresource{/Users/mac/Dropbox/Academic_Writings/reference-macwin.bib}
+% \addbibresource{C:/Users/Kaida/Dropbox/Academic_Writings/reference-win.bib}
+
 \usepackage[table,xcdraw]{xcolor}			% extend the colors can be used
-\usepackage{calrsfs}		% caligraphy font family
 
-\usepackage{bibentry}		% package used to insert full citation in body text
+% \usepackage{bibentry}		% package used to insert full citation in body text
+% replaced by \fullcite in biblatex
 
-\makeatletter 
-\renewcommand\BR@b@bibitem[2][]{\BR@bibitem[#1]{#2}\BR@c@bibitem{#2}}
-\makeatother
-\nobibliography*
+% \makeatletter 
+% \renewcommand\BR@b@bibitem[2][]{\BR@bibitem[#1]{#2}\BR@c@bibitem{#2}}
+% \makeatother
+% \nobibliography*
 
@@
 \graphicspath{ {images/} }
-
-\usepackage[framemethod=default]{mdframed}
-\usepackage{showexpl}
-\mdfdefinestyle{comment}{
-linecolor=gray,leftmargin=60,
-rightmargin=40,
-backgroundcolor=gray!10,
-innertopmargin=4pt,
-topline=false,leftline=false,bottomline=false,rightline=false}
 
@@
 \newtheorem{obs}{Observation}
+\newtheorem{que}{Question}[section]
+\newtheorem{assp}{Assumption}[section]
 
@@
 
-\citestyle{chicago}
-\geometry{letterpaper, margin=1in}
+\newenvironment{answer}
+{\noindent\textit{Answer:}}{\hfill$\square$}
+
+% \citestyle{chicago}
+\geometry{letterpaper, margin=0.75in}
 % \setlength\parindent{0pt} % to cancel indent
@@
 
+\usepackage[normalem]{ulem} %to strike the words
+\usepackage{microtype}
+
 % \usepackage{graphicx}
 % \usepackage[table,xcdraw]{xcolor}
-
-\title{Paper Notes}
-\author{Kaida Zhang}
-\date{}
-
-\begin{document}
-
-% \maketitle
-
-\tableofcontents{}
-\label{toc}
-\setcounter{tocdepth}{1}			% show only parts, chapters, and sections in content
-
-\part{Econometrics}
-\label{part:econometrics}
-
-\chapter{Common Tools} % (fold)
-\label{cha:common_tools}
-
-\noindent
-\textbf{Seemingly Unrelated Regressions:}
-\footnote{see Pinkse notes.}
-\begin{itemize}
-	\item $y_i=X_i^T\theta_0+u_i$, where $X_i$ is $k$ by 1.
-	\item $\hat \theta=(\sum_{i=1}^n{X_i\hat\Psi^{-1} X_i^T})^{-1}
-	\sum_{i=1}^n{X_i\hat\Psi^{-1} y_i}$
-	\item This estimator is more efficient than OLS.
-And it only requires the estimation of unconditional variance of error term, while WLS requires the whole distribution of error term conditional on $X_i$.
-So will also be more efficient than WLS in practice.
-	\item Intuitively, it uses the correlation information of error terms across equations.
-	\item Notice, more applicable when $k$ is not very large (relative to $n$). Otherwise the estimation of $\hat \Psi$ will be too demanding.
-\end{itemize}
-
-\chapter{Identification} % (fold)
-\label{cha:identification}
-
-% chapter identification (end)
-
-\section{Identification in Multi-Equilibria} % (fold)
-\label{sec:identification_in_multi_equilibria}
-
-\begin{itemize}
-	\item Find some feature that is common to all equilibria. For example, \cite{Berry:1992gl}
-
-	\item Set identification. For example, \cite{Shum:2018hw}
-\end{itemize}
-
-% section identification_in_multi_equilibria (end)
-
-\section{Lewbel, 2016, JEL} % (fold)
-\label{sec:lewbel_2016_jel}
-
-\textbf{\bibentry{Lewbel:2016wn}}\\
-
-\url{https://www2.bc.edu/arthur-lewbel/ident-zoo-SL-Part1.pdf}
-
-\url{https://www2.bc.edu/arthur-lewbel/ident-zoo-SL-Part2.pdf}
-
-are links for a ppt on this paper by Lewbel.\\
-
-There are two kinds of identification problems. 
-1.
-One is to identify the treatment effect, a typical example is the selection bias.
-The problem in these cases are that selection (determing who is treated or observed) and outcomes may be correlated.
-2. Another is to identify the true coefficient in a linear regression when regressors are measureed with error.
-
-\subsection{Point Identification} % (fold)
-\label{sub:point_identification}
-
-We start by assuming some information $\phi$ is knowable.
-A simple definition of point identification is that a parameter $\theta$ is point identified if, given the model, is uniquely determined from $\phi$.
-Notice that this definition of point identification is recursive in some sense.
-To identify $\theta$, we first need to assume some $\phi$ is knowable, which means $\phi$ itself is identified.
-This identification of $\phi$ can only be justified by further assumptions of DGP (Data Generating Process).
-
-For example, for a model $Y = X\theta +e$, we assume that $E(E^2)\ne0$ and $E(eX)=0$, and suppose $\phi$ includes the second order of $(Y,X)$.
-Then we can conclude that $\phi$ is point identified, given by $E(XY)/E(X^2)$.
-Notice that the identification comes from the \textit{assumptions} of model.
-
-One common DGP is IID.
-Under this DGP, we can consistently indentify the distribution of observation W.
-Another DGP is where each data point consists of a value of X chosen from its support, then we randomly draw Y conditional on X, which is independent from other draws conditional on this X.
-Under this DGP, we can consistently identify $F(Y|X)$.
-We can also use more complicated DGPs, for example, we generally assume only the second order moments are knowable in time series.
-One reason is this being sufficient for identification, another reason is higher order moments become unstable over time.
-Assumptions over GDP are always needed, even in experienment data, and which specific assumptions to take depend on the model.
-
-\section{Low and Meghir, 2017, JEP} % (fold)
-\label{sec:low_and_meghir_jep_2017}
-
-\textbf{\bibentry{Low:2017jb}}\\
-
-\textbf{Defining a structural model:}
-
-A \textbf{fully specified model} make explicit assumptions about the economic actors' objectives and their economic enviroment and information set, as well as specifying which choices are being made within the model.
-They allow a complete solution to the individual's optimization problem as a function of current information set.
-Fully specified models are particularly useful in understanding mechanism of a policy, especially when we want to estimate some long-term effects of the policy.
-
-A \textbf{partially specified model} relies on a sufficient statistic that summarizes choices not being modeled specifically.
-For example, assuming that the choices is only intratemporal instead of intertemporal.
-
-\textbf{Treatment effect models} focus on identifying a specific causal effect of a policy while saying least about the theoretical environment.
-The pro is the cleaness of causality.
-The con is the limitation in exploiting the results outside.
-The identification of treatment model depends on assumptions that the experienment has not been compromised and there is no spillovers from the treatment units.
-
-A combination of fully speficied model and randomized experiments can enhance anaysis for both.
-Experimental evidence can be used either to validate a structural model, or to aid in the estimation process (in identification).
-
-\textbf{Solving structural models}
-
-This has been described in Adda and Cooper(2003) well. 
-The general process is: 
-1) write down the bellmand function;
-2) discrete the state space and decision space;
-3) use value function iteration to solve the bellman function.
-
-% section low_and_meghir_jep_2017 (end)
-
-\chapter{Moment Inequality} % (fold)
-\label{cha:moment_inequality}
-
-\section{PPHI, 15 EMCA} % (fold)
-\label{sec:pphi_15_emca}
-
-% section pphi_15_emca (end)
-
-% chapter moment_inequality (end)
-
-% subsection point_identification (end)
-
-% section lewbel_2016_jel (end)
-
-\chapter{Others} % (fold)
-\label{cha:others}
-
-% chapter others (end)
-
-\section{Gentzkow-Kelley-Taddy, 17 WP} % (fold)
-\label{sec:gentzkow_kelley_taddy_17_wp}
-
-\noindent
-\textbf{\bibentry{Gentzkow_el.al:17WP}}
-
-An survey paper on how text analysis can be used in economic research. 
-The main difficulty is the high-dimensionality of text.
-
-\noindent
-Steps to reduce dimension:
-\begin{enumerate}
-	\item Represent raw text $\mathcal{D}$ as a numerical array $C$
-	\begin{enumerate}
-		\item Divide $\mathcal D$ into individual documents $\mathcal D_i$, the level is determined by the level of $V$. For example, daily attributes or monthly attributes.
-		\item Feature Selection.
-Drop out punctuations, numbers, HTML tags, proper names and so on.
-Both very common and very rare words will be excluded.
-And words with the same stems will be reduced to one.
-		\item Limit dependence between words using N-gram. The idea is to only consider consider phrase of length n.
-	\end{enumerate}
-	\item Map $C$ to predicted values $\hat V$ of unknown outcomes $V$
-	\item Use $\hat V$ in subsequent descriptive or causla analysis
-\end{enumerate}
-
-\textcolor{blue}{Reading not finished.
-\cite{grimmer_stewart_2013} also talks this problem. worth reading}
-% section gentzkow_kelley_taddy_17_wp (end)
-
-\section{Gillen-Montero-Moon-Shum, 18 MP} % (fold)
-\label{sec:gillen_montero_moon_shum_18mp}
-
-\noindent
-\textbf{\bibentry{Gillen:2018bg}}
-
-This paper uses LASSO to pick instruments for BLP style model. They apply it in Mexico voting model.
-
-\vspace{1em}
-\noindent
-\textbf{Applications:}
-\begin{itemize}
-	\item Maybe in education choice
-\end{itemize}
-
-% section gillen_montero_moon_shum_18mp (end)
-
-\section{Seminar Notes} % (fold)
-\label{sec:seminar_notes}
-
-\noindent
-\textbf{AI and Economics}
-(\url{http://taddylab.com/slides/EconAI.pdf})
-
-This slides procides some clear intro on why and how AI (also deep learning) can be applied in economics.
-Many references provided in slides as well.
-
-\textcolor{blue}{Not understand much. Needs further reading.}
-
-\myline
-
-\textcolor{red}{Is there any cases where only structural estimation can work, while reduced estimation, no matter how frequently A/B test, can not work?}
-
-\myline
-
-Lixiong Li in IO brownbag introduces a way for identification where there is moment restrictions.
-The idea is to replace the specific distribution assumptions of the error term by some moment restrictions.
-By this, we can not have point identification in many cases, but can get set identification even with very weak conditions.
-
-\textcolor{blue}{I think it a good paper.}
-
-% section seminar_notes (end)
-
-% chapter econometrics (end)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% IO %%%%%%%%%%%%%%%%%%%%%%
-
-\part{IO} % (fold)
-\label{part:io}
-
-\chapter{Data and Techniques} % (fold)
-\label{cha:data_and_techniques}
-
-\section{Data Source} % (fold)
-\label{sec:data_source}
-
-\noindent
-\textbf{Uber and Taxi}
-\begin{itemize}
-	\item New York Taxi and Limousine Commission Trip Data
-	\begin{itemize}
-		\item \url{http://www.nyc.gov/html/tlc/html/about/trip_record_data.shtml}
-		\item Literature: Bian Bo (JMP)
-	\end{itemize}
-\end{itemize}
-
-\noindent
-\textbf{Nielson Consumer Panel Dataset}
-\begin{itemize}
-	\item Penn State has institutional access
-\end{itemize}
-
-\noindent
-\textbf{ISMS Durable Goods Dataset 1}
-\begin{itemize}
-	\item \bibentry{Ni:2012in}
-\end{itemize}
-
-\noindent
-\textbf{Bureau of Transportation Statistics}
-\begin{itemize}
-	\item \url{https://www.transtats.bts.gov}
-\end{itemize}
-
-\noindent
-\textbf{Airbnb data}
-\begin{itemize}
-	\item Penn State Department of Real Estate \textcolor{red}{(?) how to get it}
-\end{itemize}
-
-% subsection data_source (end)
-
-\section{Timber Data by Forest Service} % (fold)
-\label{sec:timber_data}
-
-\noindent
-\textbf{Timber Industry:}
-\begin{itemize}
-	\item Dropping off timber, then process timber to log, then process log to lumber by mill
-	\begin{itemize}
-		\item Loggers do not possess mill machines, so they will sell the dropping timber to mills.
-At the same time since there are many different kinds of logs (e.g.
-in diameters), one specific mill may lack the machine for some logs and will resell them in the market.
-So the resale market after timber auction is frequent.
-This create a pro-collusion environment.
-	\end{itemize}
-
-	\item Timber tracts are very different from one to another.
-For older timber tracts, the values of bidders are more heterogeneous.
-For young or second-grow timber tracts, the value is easier to estimate and we can think it more like common value auction.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Databook:}
-\begin{itemize}
-	\item BDA: number of bidders bid excess reserve price. In sealed auction, must bid larger than reserve price. In ascending auction, must actively bid at least once in auction.
-
-	BDT: number of bidders actually show up in an auction.
-	\begin{itemize}
-		\item e.g. BDA 0, BDT 1: 1 show up, bid lower than reserve price. Notice that BDA=1 does not mean the auction is not successful.
-
-		\begin{itemize}
-			\item See 884F060103002, where BDA=0, BDT=1, the bidding value is the same as advalue, but the status (stt) is 1.
-		\end{itemize}
-		\item e.g. BDA 3, BDT 6: the price might increase too fast, the remaining 3 don't have a chance to bid.
-	\end{itemize}
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Research Questions:}
-\begin{itemize}
-	\item \cite{Athey:2011cs} shows that small bidders (loggers) pay higher in sealed auction. Why they do not move to the ascending auction in this case? Why the arbitrage does not work here?
-	\begin{itemize}
-		\item Maybe it's easier to collude in ascending auction than in sealed auction.
-Then independent bidders will prefer to stay at sealed bid auction even the realized price is higher.
-Because if they move to ascending auction, then they are likely not to win.
-	\end{itemize}
-
-	\item What if the reserve price is strategically picked by the auctioneer?
-
-	\item Timber auction is multidimensional.
-Each tract have different species, and each firm will have different values over this species.
-Can we use the Nima's optimal multidimensional mechanism design to verify the data?
-
-	\item \textcolor{blue}{Timber firms may have special interest in some species, so they may want to participate in specific auctions. And thus the private value assumption does not hold.}
-	\begin{itemize}
-		\item Bob: Firms have strong incentive to collude in this case.
-Firm A prefer species a, firm B prefers species b.
-Such preference may derive from their specialization in processing, and is commonly known among bidders.
-Then in an auction where there are 80\% specie a and 20\% specie b, it is very likely that firm A will win and sell species b to firm B after auction.
-
-		\item Then they are very likely to be engaged in an collusion.
-How can we distinguish it from the pure collusion based rotation mechanism, where firm A will attend in some auctions more frequently while B will attend others?
-	\end{itemize}
-\end{itemize}
-
-\section{FCC data} % (fold)
-\label{sec:fcc_data}
-
-\noindent
-\textbf{Related Literature:}
-\begin{itemize}
-	\item \cite{McMillan:1994bc}
-
-	\item \cite{Cramton2000} clarifies many terms in a narrative way.
-
-	\item \cite{Weber:1997ce} introduces \textit{strategic demand reduction} in simultaneous ascending bidding auctions.
-	\begin{itemize}
-		\item e.g.
-Two firms, three objects.
-Each firm either any one object 100, and any combination 200.
-Then if one firm take the strategy that keep bidding on two objects until some of which exceeds 100.
-Then the other firm will find it optimal to bid at the other object.
-The auction will end at a very low bid for all three objects.
-	\end{itemize}
-
-	\item \cite{Krishna:1996fo} discusses payoff complementarity in ascending bidding auction. Their model is based on second price sealed auction.
-
-\end{itemize}
-
-% subsection fcc_data (end)
-
-% subsection timber_data (end)
-
-\section{Techniques} % (fold)
-\label{sub:techniques}
-
-% subsection techniques (end)
-
-\noindent
-\textbf{High Resolution Satelite Data:}
-\begin{itemize}
-	\item Pixel is as accurate as 0.5m, much finer than the Night Light data;
-	\item Use machine learning to identify the roads, cars, buildings etc;
-	\item Jonathan Hersh has a paper over this.
-\textbf{\href{https://www.dropbox.com/s/zeph7rrch2rwfwp/PovSpace_JMP_Oct31.pdf?dl=0}{Poverty from Space: Using High Resolution Satellite Imagery for Estimating Economic Well-being and Geographic Targeting}}
-\end{itemize}
-
-\myline
-
-\noindent
-\textbf{Google Street View Data:}
-\begin{itemize}
-	\item \cite{Gebru:2017wk} uses Google Street View data to collect automobile information, and use machine learning to predict socioeconomic conditions of different cities.
-\end{itemize}
-
-\myline
-
-\noindent
-\textbf{Paralelle Computation:}
-\begin{itemize}
-	\item A detailed cook manual on Paralelle computation of RBC model:
-
-	\url{https://www.kellogg.northwestern.edu/researchcomputing/docs/ParallelComputing/ParallelizationForRBCModel.pdf}
-
-	\item Another source: \url{https://bfi.uchicago.edu/sites/default/files/file_uploads/Lecture_Parallel_Programming_Chicago%20%282%29.pdf}
-\end{itemize}
-
-\myline
-
-\noindent
-\textbf{Text as Data:}
-\begin{itemize}
-	\item \href{run:resources/text_as_data}{Course Materials by Justin Grimmer}
-	\item \bibentry{grimmer_stewart_2013}
-	\item \bibentry{Gentzkow_el.al:17WP}
-\end{itemize}
-
-\chapter{Cartels and Collusion} % (fold)
-\label{sec:cartels_and_collusion}
-
-A very good narrative of cartel and bidding rings is from \textit{Economics of Collusion} by Marshall and Marx.
-I will briefly summarize.
-
-\begin{itemize}
-	\item A cartel in most cases will need explicit agreement instead of just tacit collusion.
-	\item They will hire a consulting firm to negotiate the meeting and to keep track of all records.
-	\item They will fix a market share instead of just prices, and use `true-up' to redistribute as agreed at the end of the period.
-	\item They will also change the incentive of the sales team to avoid over selling.
-\end{itemize}
-
-A bidding ring is a group of bidders where they will not compete within the group. 
-There are two benefits.
-First, competition is directly lowered and price would be lower for bidders.
-Second, by reduce bidding within the group they will not leak information to other less informed bidders, and reduce competition indirectly.
-
-\myline
-
-\noindent
-\textbf{Measure of Concentrations:}
-\begin{itemize}
-	\item Herfindal Index: 
-\end{itemize}
-
-\section{Green and Porter, 84 EMCA} % (fold)
-\label{sec:green_and_porter_84_emca}
-
-\textbf{\bibentry{Green_Porter:1984EMCA}}
-
-\cite{Green_Porter:1984EMCA} points out that \textbf{price war can be a part of collusion equilibrium}, challenging the view that price war being a signal of competition.
-The key point is that there is \textbf{uncertainty in demand}, which is after the decision of firm's quantity decision.
-So firms are unable to distinguish between a low demand shock and someone's possible deviating.
-
-They show that the equilibrium strategy is a \textbf{\textcolor{blue}{trigger strategy with forgiveness}}.
-For realized price $p$ higher than some threshold $\bar p$,
-firms choose the cooperative quantity;
-otherwise they will choose the Cournot quantity for T periods, where the punish time is given (maybe by explicit negotiation process).
-
-The dynamic incentive is very interesting here.
-In equilibrium, no firms will have incentive to deviate. 
-So the only possibility for a low price is a bad demand shock.
-Despite everyone knowing this, they will still choose the Cournot quantity for $T$ periods as a punishment.
-This is to give correct dynamic incentive.
-Suppose a strategy profile features no punishment even in low price.
-Then firms would have incentive to output more since they would not be punished anyway.
-
-\begin{mdframed}[style=comment]
-\noindent
-\textbf{Learning Process:}
-
-One thing I feel uncomfortable is the information structure of the firm. 
-In this paper, firms are assumed to know the realization of price, the distribution of shocks $\theta$, and the function form of price $p()$.
-
-If they do not know the distribution, not do they know the functional form.
-Then it would be impossible for them to distinguish the volatility in $\theta$ and in quantity.
-Thus it would be impossible to detect probable deviation.
-\footnote{In the paper, we can detect deviation at some probability. But even this cannot be satisfied because the distribution is unknown and relative parameters are unidentified.}
-\end{mdframed}
-
-\textbf{Identification:} in appendix they show that in principle the collusion behavior can be identified.
-But in practice it is generally quite difficult.
-
-% subsection green_and_porter_84_emca (end)
-
-\section{Rotemberg-Saloner, 86 AER} % (fold)
-\label{sec:rotemberg_saloner_86_aer}
-
-\textbf{\bibentry{RotembergSaloner:86aer}}
-\vspace{1em}
-
-\cite{RotembergSaloner:86aer} also tries to explain price war, but they show that \textbf{price wars are more likely to happen during the demand boom instead of doom.}
-In their model, firms make decisions \textit{after} realization of shocks.
-So firms can distinguish between the price drop by deviation and price drop by low demand.
-Then their result is quite intuitive.
-It is more profitable to deviate when demand is high.
-So the collusive price at high demand should be lower, the lower is collusive price, the less attractive to deviate.
-
-\vspace{1em}
-\noindent
-\textit{Comments:}
-\begin{itemize}
-	\item With more specific assumption on knowledge of firm, they can say more about the competition structure.
-	In \cite{Green_Porter:1984EMCA}, the only reasonable competition mode is Cournot.
-	But both Bertrand and Cournot are appropriate in this paper.
-	\item The establishment of price competition equilibrium is skillful.
-	They first assume a exogenous punishment to generate optimal decision, then use such decision to generate an actual punishment.
-	This constitutes a fixed point argument.
-	\footnote{Same trick as in \cite{Peters_Siow:2002dx} small market case.}
-
-	\item This model is `\textit{really about countercyclical pricing---firms have perfect information and adjust prices smoothly in response to demand conditions.}'(by \cite{Ellison:94RAND} p.38).
-	There is no \textit{regime shift} like in \cite{Green_Porter:1984EMCA} since the past has no uncertainty.
-	\begin{itemize}
-		\item It is not important whether the future has uncertainty.
-Say, the demand is seasonal and is certain.
-It won't change the result, the pricing will still be countercyclical.
-Intuitively, what the firms compare is the current deviation profit and expected future gain, thus future uncertainty is not important (as long as firms are risk neutral).
-	\end{itemize}
-\end{itemize}
-
-\section{Porter, 83 Bell} % (fold)
-\label{sec:porter_83_bell}
-
-\textbf{\bibentry{Porter:83bell}}
-
-\cite{Porter:83bell} is specifically to test \cite{Green_Porter:1984EMCA} using JEC data.
-\footnote{Joint Executive Committee, which is widely used since it records the cartel in 1880-1886 for the train industry in US.}
-
-\vspace{2mm}
-\noindent
-\textbf{Estimation Strategy:}
-\vspace{-0.5em}
-\begin{itemize}
-	\item \textbf{Goal} is to test whether regime switch happens in supply side, and to identify when such switches happen.
-	This paper does not test whether firms actually play the equilibrium as described by \cite{Green_Porter:1984EMCA}, but only describes the reversion pattern.
-	\item \textbf{Data} is aggregate time series price and quantity.
-	\begin{itemize}
-		\item KZ: notice there is some internal inconsistency in this setting.
-Porter assumes 1) no secret deviation, without giving justification; 2) homogeneous good, which is largely due to data limitation; and 3) firms do price competition.
-But then we should see prices near marginal cost, which should not fluctuate a lot.
-	\end{itemize}
-
-	\item \textbf{Firm Strategy:} The firms in JEC actually use price instead of quantity as strategic variable, and they use differentiated products (through different service).
-This is different from \cite{Green_Porter:1984EMCA} model.
-	\begin{itemize}
-		\item But in econometrics model part, this paper seems to still assume the quantity competition. This may due to the data limitation --- they only have aggregated price and quantity.
-		\item Firm's decision problem is summarized by 
-		\[p_t(1+\theta_{it}/\alpha_t)=MC_i(q_{it})\]
-		Porter notes that this form can encompass Bertrand competition, Cournot competition and perfect collusion, with $\theta_{it}$ being 0, $(0,1)$, 1 respectively.
-		\textcolor{red}{This seems reasonable, what I don't understand is how it can be compatible with Green-Porter's model?
-In their model it is obvious that Cournot is the only possible way of competition.}
-
-		\begin{mdframed}[style=comment]
-			This form can be derived from firm profit maximization. Suppose \[\pi_i(q_i,q_{-i}) =p(q_1,\dots,q_n)q_i-C(q_i) \]
-			by taking derivative w.r.t. $q_i$ we will get:
-			\[p(1+\frac{1}{\varepsilon_{q_i,p}})=MC(q_i)\]
-			Also notice that this can actually encompass both Cournot and Bertrand.
-In Cournot, we have $p(q_1,\dots,q_n)=p(\sum_{i=1}^nq_i)$; and in Bertrand we have $p(q_1,\dots,q_n) = p(\sum q'|q' \in \max\{q_1,\dots,q_n\},0=q_i\notin q')$
-
-		\end{mdframed}
-		\item In firm optimization problem, there is no uncertainty.
-But in turning it to reduced form, the paper has to add error term $U_{2t}$ to match the data.
-In adding this term, we implicitly assume 1) firms do not know this shock when making decision; 2) this shock is aggregate for all firms (?).
-	\end{itemize}
-	\item \textbf{Estimation:}
-	\begin{itemize}
-		\item Demand Curve:
-		\item Supply Curve:
-		\item Simultaneous Equation System:
-		\item Conditional pdf:
-		\item Unconditional pdf:
-		\item Convergence algorithm:
-	\end{itemize}
-\end{itemize}
-
-% subsection porter_83_bell (end)
-
-% subsection rotemberg_saloner_86_aer (end)
-
-\section{Genesove-Mullin, 01 AER} % (fold)
-\label{sec:genesove_mullin_01_aer}
-
-\textbf{\bibentry{Genesove:2001jz}}
-
-\cite{Genesove:2001jz} narratively describes how the sugar cartel in 1930-1936 actually works.
-They find cartel's action deviates from what collusion theory predicted.
-The main idea they try to convey is: \textbf{collusion is more a contraction problem than a market structure problem}.
-
-Questions they want to answer:
-\begin{itemize}
-	\item How firms coordinate their pricing?
-	\begin{itemize}
-		\item Mainly through rules, and by ordinary meetings to adjust to rules. Such meetings are necessary due to the uncertain nature of competition environment.
-	\end{itemize}
-	\item How prevalent is cheating? What's the punishment?
-	\begin{itemize}
-		\item Cheating is not discussed in neither \cite{Green_Porter:1984EMCA} nor \cite{RotembergSaloner:86aer}.
-There the price war is just an equilibrium result, and no one has incentive to `secretly cheat'.
-		\item But in reality cheat actually happens.
-Because contract is always incomplete and firms have many tricks to escape.
-But retaliation does not always happen.
-They will first make some effort to partially identify a cheat and a bad draw, e.g.
-by asking the suspect to show some hard evidence.
-When the cartel is convinced that someone has cheated, they are mostly likely to take tit-for-tat strategy instead of trigger.
-	\end{itemize}
-\end{itemize}
-
-Below are notes taken during the reading.
-
-\begin{itemize}
-	\item Cartel mainly collude through rules.
-	\begin{itemize}
-		\item Open prices and publicly announced items
-		\item Prior notification
-		\begin{itemize}
-			\item Complementary to open announcement. Ensure that firms can potentially retaliate before consumers react.
-		\end{itemize}
-		\item Restrictions on contractual practices between the refiners and downstream firms
-		\begin{itemize}
-			\item Mainly to eliminate discriminatory pricing
-			\item Very detailed and standardized.
-Because `every contractual term can mask a price cut'.
-The standardized model is implicitly assumed in Green-Porter, though homogeneous good and the extremely simplified contract and strategy form.
-			\item Such rigidity is also costly to cartel
-		\end{itemize}
-		\item Alternative explanation for such limitation on contracts:
-		\begin{itemize}
-			\item Limiting non-price competition
-			\item Authors did not agree. They argue that the \textit{contractual harmonization} conveys more than non-price competition limitation.
-		\end{itemize}
-	\end{itemize}
-	\item Collusion contract is always incomplete
-	\begin{itemize}
-		\item The regular and frequent meetings are to fix the holes
-	\end{itemize}
-
-	\item Why firms do not directly retaliate when they find cheating?
-	\begin{itemize}
-		\item Different from \cite{Green_Porter:1984EMCA}, firms in Sugar Cartel can argue within the institute meeting.
-Such meeting gives them a chance to figure out whether it is a shock or a intentional cheat.
-In other words, firms do have a choice to reduce the confounding uncertainty, which reduces their incentive to retaliate.
-	\end{itemize}
-	\item Firms do not retaliate to every cheating. They do not use massive retaliation unless the cheating is very high. The retaliation they take generally is `matching', kind of tit-for-tat.
-	\begin{itemize}
-		\item One reason to desist from full-scale retaliation (as in \cite{Green_Porter:1984EMCA}) is the vertical contractual arrangement in the industry.
-Firms sell sugar through brokers.
-Brokers will have much higher incentive to deviate since their number is much larger than that of firms.
-Such structure made deviation more prevalent.
-It is also more costly, since one more layer of brokers make it more difficult for firms to switch between two pricing regimes.
-	\end{itemize}
-	\item Firms rarely react to market share.
-	\begin{itemize}
-		\item Market share is too noisy a signal.
-	\end{itemize}
-	\item Firms choose to meet frequently to adapt quickly to external change, and to fix any holes in rule as soon as possible. They seem not care much about the \textit{renegotiation problem}.
-\end{itemize}
-
-% subsection genesove_mullin_01_aer (end)
-
-\section{Graham-Marshall, 87 JPE} % (fold)
-\label{sec:graham_marshall_87_jpe}
-
-\textbf{\bibentry{Graham_Marshall:87jpe}}
-
-This paper models the collusion within bidders in Second Price Sealed auction and English auction in IPV framework.
-They find collusion strategy equilibrium can be stable in such settings.
-Coalition of any size is stable, and the expected payoff to each member increases with the coalition size.
-
-\begin{itemize}
-	\item In second price auction. The optimal reserve price is a increasing function of coalition size.
-	\item In English auction.
-The optimal reserve price is identical to that of second price auction, and independent of observed highest bid.
-This result is striking since it seems at first that auctioneer at English auction can do better with this additional information.
-\end{itemize}
-
-Some stylized facts are not incorporated in this model:
-\begin{itemize}
-	\item Fact: brokers will not be invited to the coalition.
-If a broker has a customer, his willingness to pay is much stronger than any dealer.
-Thus he does not want to join the ring since other ring members will push price high in the knock-out round.
-If a broker does not have a customer, the he is not really coming to bid but to share the `ring hat'.
-The ring does not want him in this case.
-
-	$\rightarrow$ This fact cannot be encompassed in this model. Because the model assumes IPV, while brokers represent a very special distribution (0 or very high) of value, against the assumption.
-\end{itemize}
-
-\section{MMRS, 94 GEB} % (fold)
-\label{sec:marshall_meurer_richard_stromquist_94_geb}
-
-\textbf{\bibentry{Marshall:1994bc}}
-
-This paper raises a algorithm to numerically solve equilibrium in heterogeneous auctions.
-And they use this algorithm to investigate simulate some facts for auction coalition in first price auction.
-
-\vspace{1em}
-\noindent
-\textbf{Facts from Simulation:}
-\begin{itemize}
-	\item Revenue equivalence of first price auction (or Dutch) and second price auction (or English) does not hold in existence of collusion. The expected revenue is higher in first price auction.
-
-	\item In second price auction, the individual has no incentive to deviate from the coalition even when coalition size is very large.
-Actually the surplus of coalition gain to individual gain increases with coalition size $k_1$.
-
-	\item In first price auction, the individual has no incentive to deviate when coalition size is small, but does have incentive to deviate when coalition size is large.
-The relative advantage of individual bidder increases with coalition size $k_1$.
-
-	\item In ascending auction, for any given value, the weaker bidder will be more aggressively than stronger bidder. 
-	\begin{itemize}
-		\item This induces inefficiency. Stronger bidder with higher value may lose the auction.
-		{\color{blue}
-		\item Payoff equivalence not holding in this environment?
-		\begin{itemize}
-			\item maybe sealed auction and ascending auction does not reduce to the same direct mechanism in this environment
-		\end{itemize}
-		}
-	\end{itemize}
-
-	\item The same features are also found in \cite*{Athey:2011cs}.
-Although in Athey el al., the heterogeneity is not from collusion but from different cost distribution between large (mill) and small (logger) bidders.
-But the mathematical representation is the same, larger bidders value distribution FOSD that of the small bidders.
-	\begin{itemize}
-		\item They find the timber auction has following stylized facts: sealed first price auction attract more small bidders, shit the allocation toward these bidders, and can generate higher revenue to auctioneer.
-	\end{itemize}
-\end{itemize}
-
-% subsection marshall_meurer_richard_stromquist_94_geb (end)
-
-% subsection graham_marshall_87_jpe (end)
-
-% section cartels_and_collusion (end)
-
-\chapter{Price Dispersion} % (fold)
-\label{cha:price_dispersion}
-
-\section{Butters, 77 RES} % (fold)
-\label{sec:butters_77_res}
-
-\textbf{\bibentry{butters:77res}}
-
-This paper tries to generate price dispersion in a homogeneous environment.
-Homogeneity is in the sense that commodity characteristics, consumer preference, seller cost are all the same.
-The only heterogeneity comes from seller's strategy on pricing and advertisement.
-
-Unlike previous literature only focusing on consumer side, Butters models both consumer search behavior and the firm strategy.
-In other words, previous models are `partial-partial equilibrium', while this paper is `partial equilibrium'.
-
-\vspace{1em}
-\noindent
-\textbf{No Consumer Search:}
-\begin{itemize}
-	\item Seller: decide the amount of ads, for each ad can post a different price. Each ads costs $b$.
-	\item Buyer: the only way to purchase is through ads, and pick the lowest price (unless all prices higher than reserved price $m$).
-Each ads reach each consumer with equal probability, that's to say, the probability distribution of number of ads of any given consumer is Poison distribution.
-Most importantly, the probability that a consumer receives no price quotes lower than $p$, given the ads distribution $A(p)$, is $exp(-A(p))$.
-	\item The model is solved purely at market level.
-Denote $A(p)$ to be the number of ads with prices equal or lower than $p$ divided by consumer number $M$.
-$S(p)$ to be the sales actually happen with price lower than $p$ divided by consumer number $M$.
-$\pi(p)$ be the probability of selling a good by pricing at $p$.
-	\begin{itemize}
-		\item We thus have $s(p)=a(p)\pi(p)$, where $s(p),a(p)$ are derivatives of $S,A$ respectively.
-		\item The profit function is:
-		\[\text{profit}=\int{[(p-p_0)\pi(p)-b]a(p)}dp\]
-	\end{itemize}
-	\item By no deviation condition, the marginal profit at any equilibrium price level should be zero. Thus, $(p-p_0)\pi(p)=b$, and $\pi(p)=b/(p-p_0)$
-	\item By similar arguments as in allpay auction, the equilibrium price can only be a range $[p_0+b,m]$
-	\item IMPORTANT: $\pi(p)=exp(-A(p))$
-	\begin{itemize}
-		\item $\pi(p)$ is the probability that an ad with price $p$ being accepted.
-This is the probability that this ad goes to a consumer with ZERO price quotes lower than $p$.
-By our previous analysis, $A(p)$ is the number of ads per consumer, i.e.
-the single time probability that a consumer receives an ad with price lower than $p$.
-Then by the results of Poison distribution, the probability that a consumer receiving no price quotes lower than $p$ is $exp(-A(p))$.
-		\item This is important since it connects the individual behavior and market index.
-Firms only cares about $\pi$ when making ads decision; while $A(p)$ can induce $\pi(p)$.
-These two have to be consistent in equilibrium.
-	\end{itemize}
-	\item The equilibrium is easy to solve with above characterization.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{With Consumer Search:}
-\begin{itemize}
-	\item The setting is quite tricky. The equilibrium is greatly simplified due to the following two assumptions of \textit{word-of-mouth search}:
-	\begin{itemize}
-		\item ASSP-1: The probability that a search yield an offer from any particular seller is proportional to his share in total shares;
-		\item ASSP-2: The probability that this offer is at a price within a particular interval $(p_1,p_2)$ is proportional to the seller's sale at this particular interval.
-	\end{itemize}
-	Above two assumptions makes the profit from searching consumers exactly proportional to that of non-searching consumers.
-So we only need to maximize the profit from non-searching consumers, which has the same structure as no-search case.
-	\begin{itemize}
-		\item KZ: I find these two assumptions uncomfortable. This is not about the search behavior, but all about the optimal advertisement.
-	\end{itemize}
-
-	\item Claim: consumers will search iff they receive no ads, and in this case they will accept the first price they find.
-	\begin{itemize}
-		\item The second half is direct implication of the assumptions, especially assumption 2.
-		\item For first half, denote the highest posted price $p_{max}$, and the threshold price of searching $p_c$.
-Obviously $p_{max}\leq p_c$.
-Further we claim that $p_{max}=p_c$, otherwise the firm can increasing highest posted price by $\varepsilon$ while keep advertisement same as in $p_{max}$.
-	\end{itemize}
-
-	\item The equilibrium is very similar to no-search case. The only difference is $\pi(p_{min})=1/\phi>1$. At lowest posted price, one ad will induce more than one purchase.
-	\begin{itemize}
-		\item This is because now we have $1-\phi$ portion of people receive no ads, at any price interval.
-Thus conditional on the consumer receiving at least one ad, $p_{min}$ will for sure lead them to buy.
-But such ads will induce even more purchase because those receiving no ad will also buy from this seller at this price $p_{min}$ proportionally.
-		\item This makes sense because since consumer can search, firms can transfer the load of advertisement partly to the consumer side.
-	\end{itemize}
-
-	\item The portion $\phi$ can be pinned down in equilibrium by the fact that eventually every consumer will buy.
-\end{itemize}
-
-\section{Sorensen, 00 JPE} % (fold)
-\label{sec:sorensen_00_jpe}
-
-\textbf{\bibentry{Sorensen:00jpe}}
-
-\vspace{1em}
-\noindent
-\textbf{Facts and Identification Strategy:}
-\begin{itemize}
-	\item This paper is a reduced form paper testing price distribution in drugs.
-
-	\item The identification strategy is to \textbf{use \textit{frequency} as the key explanation variable}. 
-	\begin{itemize}
-		\item This is the \textit{comparative static} approach.
-Because by \cite{butters:77res} the price dispersion will shrink if the cost of search is lower.
-Here the searching frequency is a proxy as search cost.
-	\end{itemize}
-
-	\item Measure of price dispersion is \textbf{price range}.
-This is an absolute measure, because search cost generally do not vary with price scale.
-There are other measures possible, for example standard deviation, or relative range.
-
-	\item The environment is carefully picked for clean identification:
-	\begin{itemize}
-		\item The market is some small isolated markets, with sufficiently many pharmacies within each market.
-		\item The frequency of purchase is determined by instruction of doctor, which is uncontrollable by drug consumers.
-		\item The drug price is posted, thus is in principal public so that econometricians can collect them. But consumers have to pay the search cost to gain such information.
-		\item All pharmacies face similar cost.
-	\end{itemize}
-
-	\item They also exclude the possibility of heterogeneous pharmacy service.
-	\begin{itemize}
-		\item First, they show that pharmacies have very different rankings for different drug price. This fact is inconsistent with the explanation of pharmacy level heterogeneity.
-		\item Second, they run a residual regression to show that pharmacy heterogeneity at most account for 30\% of price dispersion.
-	\end{itemize}
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{What Cannot be Answered:}
-\begin{itemize}
-	\item The data generating process. How exactly search cost affects the price dispersion.
-	\item Quantifying search cost.
-	\item This has to be done with a structural model like \cite{Hortacsu:2004bg}.
-\end{itemize}
-
-% subsection sorensen_00_jpe (end)
-
-\section{Hortacsu-Syverson, 04 QJE} % (fold)
-\label{sec:hortacsu_syverson_04_qje}
-
-\textbf{\bibentry{Hortacsu:2004bg}}
-
-\vspace{1em}
-\noindent
-\textbf{Facts and Explanations:}
-\begin{itemize}
-	\item Mutual fund prices are hugely dispersed, despite their financial homogeneity. The 75th to 25th price ratio of Index Funds is 3.1;
-	\item Nonportaforlio Differentiation. Funds attributes like manager tenure, the age of the fund, rate of taxable distributions will not directly affect return, but do affect investors' choice.
-	\begin{itemize}
-		\item Only focus on vertical differentiation and assume homogeneous preference over these attributes. Because horizontal differentiation is unidentifiable from search cost differences.
-	\end{itemize}
-	\item Search Cost.
-	\item Switch Cost.
-If switch cost is important, then we should observe in data that inflow/outflow of S\&P Fund in a non-load funds family should be less volatile than those in a load funds family.
-Because when index fund performs poor, those in a load fund family will switch to another fund in the same fund family, inducing larger imbalance within the fund family.
-This is not significant in data.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Model:}
-\begin{itemize}
-	\item Funds are different in both prices and other vertical attributes. But investors have homogeneous utility form. 
-	\footnote{We cannot identify taste heterogeneity using BLP. The taste differentiation is unidentifiable with search cost differentiation.}
-	We assume a specific utility form, where price enters linearly:
-	\[u_j=W_j \beta-p_j+\varepsilon_j\]
-	\item Investors have cost $c_i$ for each search, which is distributed in population as $G(c)$. An investor searches sequentially until the expected utility gain is smaller than search cost:
-	\[c_i \leq \int_{u^*}^{\bar u} (u-u^*)dH(u)\]
-	where $H(u)$ is investors' belief about the distribution about funds' indirect utility, which is unknown to econometricians and have to be assumed.
-We assume that funds provide $N$ levels of utility, $u_1 < ...
-<u_N$.
-If we further assume equal sampling probabilities, we have:
-	\[H(u)=\frac{1}{N}\sum_{j=1}^N I[u_j \leq u]\]
-	Investors are assumed to know the value of each $u_j$, they are only uncertain about which fund provides which utility level.
-	\begin{itemize}
-		\item KZ: this assumption very strong, which greatly reduces the dimension of information investors need to learn about.
-	\end{itemize}
-	\item The optimal search rule yields critical points in search cost:
-	\[c_j=\sum_{k=j}^N{\rho_k (u_k-u_j)}\]
-	where $\rho_k$ is the probability that fund $k$ is sampled on each search, which is known to all investors.
-The RHS is the expected payoff of another search conditional on already found $j$.
-Thus $c_j$ is the highest possible search cost that could allow such search.
-	\begin{itemize}
-		\item KZ: $\rho_k$ is just the density of $H(u)$.
-If equal sampling, then $\rho_k=1/N$ for all $k$.
-If not equal sampling, it should be conditional on how much time an investor has already searched, unless we assume the funds pool is infinite.
-	\end{itemize}
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Identification:}
-\begin{itemize}
-	\item \textbf{Goal:} identify the search cost and coefficients of other attributes with only price and market share data.
-	\item Funds market share can be written in cost thresholds.
-Thinking of $u_1$ with lowest indirect utility.
-Only those with really high search cost will end up buying fund-1, and they have to be unlucky to draw this fund at the first time.
-	\[q_1=\rho_1(1-G(c_1))=\rho_1\Big[1-G\Big(\sum_{k=1}^N{\rho_k(u_k-u_1)}\Big)\Big]\]
-	For fund-2, there are two sources. One investor may have cost higher than $c_1$ and draw fund-2 in the first time; or he has cost $c_2<c<c_1$ and draw fund-2 first time or directly after fund-1.
-	\footnote{$Pr=\rho_2+\rho_1\rho_2+\rho_1\rho_1\rho_2+...=\rho_2/(1-\rho_1)$}
-	\[q_2 = \rho_2(1-G(c_2))+\frac{\rho_2}{1-\rho_1}(G(c_2)-G(c_1)) \tag{7}\]
-	Similarly, we can write $N$ equations for all funds market share. 
-	\begin{itemize}
-		\item Thus we can back out $G(c_j)$ with known $\rho_j$ and $q_j$ for all $j$.
-		Moreover, we can normalize $G(c_N)=0$ because we have $c_N=0$ by threshold equation, and search cost have to be nonnegative.
-		\item We can take derivative with $p_j$, because $c_j$ is influenced by $u_j$ which contains $p_j$. Thus we can write $N-1$ derivatives:
-		\[\frac{\partial q_j}{\partial p_j}
-		=f(\rho_1,...,\rho_N,g(c_1),...,g(c_j)) \tag{10}\]
-		where $g(c_j)$ is the p.d.f. of cost distribution at $c_j$.
-	\end{itemize}
-
-	\item For supply side, we first write the FOC of fund $j$.
-	\[q_j(p,W)+(p_j-mc_j)\frac{\partial q_j(p,W)}{\partial p_j}=0 \tag{9}\]
-	In above equation, only $q_j$ and $p_j$ is observable to econometricians.
-	If we further assume Bertrand-Nash competition, we have:
-	\[\frac{\partial q_j(p)}{\partial p_j}
-	=-\frac{q_j(p)}{p_j-mc_j}\]
-	If we know $mc_j$, then we can calculate $\partial q_j/\partial p_j$, and plugging into (10) get us $g(c_j)$ for all $c_1, ... ,c_{N-1}$
-
-	\textcolor{red}{The paper says $mc_j$ can be estimated, don't know how}
-
-	\item Knowing $G_j$ and $g_j$ for all $c_1,...c_{N-1}$, we can back out all $c_j$ through:
-	\[G(c_{j-1})-G(c_j)\approx 0.5[g(c_{j-1})+g(c_j)](c_{j-1}-c_j)\]
-	Recall that $c_N=0$, we have known all $c_j$.
-	Since we know all $c_j$ and $G(c_j)$, we have backed out the distribution of search cost (in these thresholds).
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Estimation:}
-\begin{itemize}
-	\item \textbf{Basic Model:} homogeneous funds except for price, equal sampling $\rho_j=1/N$
-	\begin{itemize}
-		\item By homogeneity, we have $u_j = u-p_j$. Thus $c_j$ is only function of $p_j$'s.
-	\end{itemize}
-
-	\item \textbf{Homogeneous Fund + Unequal Sampling Probability:}
-	\begin{itemize}
-		\item By homogeneity, we have $u_j = u-p_j$. Thus $c_j$ is only function of $p_j$'s. Since we know $p_j$ for all $j$, we then know $c_j$ as well.
-		\item By unequal sampling, assume specifically:
-		\[\rho_j=\frac{Z_j^\alpha}{\sum_{k=1}^N{Z_k^\alpha}}\]
-		where $Z_j$ is the attributes that will affect the likelihood of being found, e.g. advertisement expenditure. We use age of a fund as proxy.
-		\item Estimate the model by fitting $(N-1)$ (7) and $(N-1)$ (9).
-We know $c_j$, $Z_j$, and $G(c_j)$ can be written as function of $Z_j$ and unknown parameter $\alpha$.
-So we have $2N-2$ equations to estimate $\alpha$ and $mc_j$ for all $j$.
-	\end{itemize}
-
-	\item \textbf{Heterogeneous Fund + Equal Sampling Probability:}
-	\begin{itemize}
-		\item Since funds are heterogeneous, $c_j$ cannot be directly derived from $u_j$. But we can still non-parametrically identify $c_j$ as described in previous section.
-		\item For identification, we must assume equal sampling probability. We also assume $mc_j$ is constant and equals 10 basis point for all $j$.
-		\item Estimation result shows that overall search cost decreases sizable amount in 1996 to 2000, but in upper quantile increases. This may be due to the entering of many novice family investors.
-	\end{itemize}
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Questions Remaining:}
-\begin{itemize}
-	\item The assumptions of drawing funds with replacement is not satisfying, especially when the industry is very concentrated in several star funds.
-
-	\item If we want to investigate both horizontal differentiation and vertical differentiation.
-Then we have to know not only the individual level data on what choice they made, but also the \textit{choice set} they have.
-	\begin{itemize}
-		\item There are two possible interpretation for a fund to be chosen.
-1) the consumer observes all the funds and prefers this fund most; 2) the consumer only observes a limited number of funds and have to pick one.
-This causes the identification problem between preference and search cost.
-	\end{itemize}
-
-	\item Bundling problem.
-The consumers do not just buy one fund, but buying a bundle of funds.
-They react to the whole bundle price instead of single fund price.
-This is one specific kind of product differentiation.
-	\begin{itemize}
-		\item The importance of such product differentiation is, it can hardly say that such differentiation is only vertical.
-Different investors have different financial goals, and thus have different preference on bundles.
-	\end{itemize}
-\end{itemize}
-
-\section{Allen-Clark-Houde, 14 AER} % (fold)
-\label{sec:allen_clark_houde}
-
-\textbf{\bibentry{Allen:2014kr}}
-
-\vspace{1em}
-\noindent
-\textbf{Empirical Takeaway:}
-\begin{itemize}
-	\item The competition of firms mostly benefit consumers with low search cost.
-	\begin{itemize}
-		\item The merger led to an increase in \textit{average} interest rate of appx 6 bps.
-		\item This merger effect is between 7 to 9 bps for consumers with lower and middle range percentile search cost; and has no effect for consumers with top 30\% serch cost.
-		\item The merger led to a 16\% decrease in interquartile price range.
-	\end{itemize}
-\end{itemize}
-
-\textcolor{blue}{Identification and estimation part to be added.}
-
-% subsection allen_clark_houde (end)
-
-% subsection hortacsu_syverson_04_qje (end)
-
-\myline
-
-\textbf{\bibentry{Baye:2013un}}
-
-\begin{itemize}
-	\item Price comparing sites becoming less popular,
-	more consumers choose to directly go to like Amazon and eBay.
-	These websites also have `marketplace'.
-	\item Many searching behavior are not observed. Non-texture data (e.g. in the menu, directories).
-	\item Search time across platforms can hardly be compared.
-	Because maybe it's enough to search only once in Amazon, 
-	but many times in eBay.
-\end{itemize}
-
-\myline
-
-\noindent
-\textbf{Random Ideas}
-\begin{itemize}
-	\item Collusion when there is consumer searching cost.
-	Intuitively, collusion should be easier to sustein with 
-	\textcolor{blue}{[no idea]}
-
-	\item Awaya-Krishna (2016) 
-\end{itemize}
-
-% subsection butters_77_res (end)
-
-\chapter{Auction} % (fold)
-\label{cha:auction}
-
-\section{McMillan, 94 JEP} % (fold)
-\label{sec:mcmillan_94_jep}
-
-\textbf{\bibentry{McMillan:1994bc}}
-
-\vspace{1em}
-\noindent
-\begin{itemize}
-	\item Lessons from New Zealand and Australia:
-	\begin{itemize}
-		\item Second price auction may have political defect and revenue loss.
-People are dissatisfied to see firms pay less than their revealed true value.
-And reserve price will enhance revenue when bidder number is small.
-		\item Australia's auction shows that penalty for default is necessary to restrain incentive of over bid.
-		\begin{itemize}
-			\item FCC: the highest bidder need to pay the difference between his bid and actual sale price if he chooses to exit.
-		\end{itemize}
-	\end{itemize}
-
-	\item Open Bidding v.s. Sealed Bidding
-	\begin{itemize}
-		\item Open auction can mitigate winner's curse because bidders can learn from others' biddings, and thus be less cautious.
-		\item Sealed bid auction increases revenue when bidders are risk averse. Because bidders will bid higher to ensure winning in sealed auction.
-		\item Sealed bid auction deters collusion.
-		\item FCC: run multiple rounds of sealed auction, announce bids after each round, but do not announce bidder identity.
-	\end{itemize}
-
-	\item Simultaneous v.s. Sequential Auction
-	\begin{itemize}
-		\item Sequential bidding have two disadvantages:
-		\begin{itemize}
-			\item It is less flexible, impeding the possible aggregation. The firm cannot go back and adjust his portfolio.
-			\item Encourage predatory bidding in early stage.
-		\end{itemize}
-		\item Simultaneous auction has difficulty in implementing effective stopping rule.
-		\item FCC: for 20\% core licenses, use simultaneous stopping, and use license-by-license stopping for the rest.
-	\end{itemize}
-
-	\item Combinational v.s. Non-Combinational Bidding
-	\begin{itemize}
-		\item Combinational bidding allows bidders to bid for bundles of licenses together. It is efficient in the sense that different licenses are complementary and have economics of scale.
-		\item Combinational bidding has another advantage of expanding the preference space.
-		\item Combinational bidding will refrain competition.
-Because there is free rider effect within independent bidders.
-Even there total value of separately awarded licenses exceed that of the nationwide bidder, they would not like to bid high because they only get a share of winning rent.
-		\item FCC: combinational bidding not allowed in simultaneous bidding; allowed in sequential bidding with a possible premium.
-	\end{itemize}
-
-	\item Aid Designated Bidders
-	\begin{itemize}
-		\item Give those bidders a price preference.
-	\end{itemize}
-
-	\item Royalties v.s. Single Payment
-	\begin{itemize}
-		\item Royalty partially shifts the risk to government, thus increasing bidders' willingness to pay.
-		\item Makes auction more like common value. \textcolor{blue}{The paper says this will stimulate competition, don't understand.}
-		\item Causes post-auction incentive problem.
-		\item Difficulty to isolate revenue induced by such license in practice.
-	\end{itemize}
-\end{itemize}
-
-% subsection mcmillan_96_jep (end)
-
-\section{Kawai, 18 WP} % (fold)
-\label{sec:kawai_18_wp}
-
-\noindent
-\textbf{Kei Kawai (2018 WP): Missing Bids and Scoring Auctions}\\
-
-There are two main contributions for this paper:
-\begin{itemize}
-	\item It introduces a way of measuring collusion level in auction.
-	\item It empirically shows that scoring auction is more competitive (less collusive) than pure price-based auction.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Detecting Collusion:}
-\begin{itemize}
-	\item Define the distance of bid-i to the winning bid of remaining bidders to be:
-	$$\Delta_i = bid_i - \min_{j\neq i}bid_j$$
-	If we pile (sum up) $\Delta_i$ for all bidders, and plot the density, we should find them to be relatively smooth.
-	But in data, the authors find that the density around $\Delta = 0$ is a low spike. This suggests collusion.
-	\item Intuition is, if there is no collusion, then the bidders can increase their bids by a little bit.
-Since the density of $\Delta$ near 0 is very low, the probability of losing the auction by increasing bid is low.
-So the optimal strategy should be to increase the bidding price.
-	\item The author further introduces a scale measure of collusion possibility. \red{Do not understand this part.}
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Score Auction:}
-\begin{itemize}
-	\item The auctioneer of score auction does not take price as the only deterministic attribute for allocation.
-He will also consider the \textit{quality} of the bid.
-But since the quality is a multi-dimension property, there is uncertainty about the allocation result.
-This uncertainty is essentially uncertainty about auctioneer's preference.
-	\item Such uncertainty makes it more difficulty to monitor deviation within a bidding ring, thus makes the cartel more difficult to sustain. The intuition is from \cite{Green_Porter:1984EMCA}.
-\end{itemize}
-
-% section kawai_18_wp (end)
-
-% section auction (end)
-
-% section price_dispersion (end)
-
-\chapter{Spatial Competition} % (fold)
-\label{cha:spatial_competition}
-
-% section spatial_competition (end)
-
-\section{DGT, 78 EMCA} % (fold)
-\label{sec:dgt_78_emca}
-
-% subsection dgt_78_emca (end)
-
-\textbf{\bibentry{DGT78}}
-
-\textcolor{blue}{This paper serves as an example of clear writing.}
-
-Hotelling's `converging to middle' result is not a generic property of the model.
-For example, 
-\begin{itemize}
-	\item When transportation cost is linear, there exists no pure strategy Cournot Eqm when two firms are very close;
-	\item When transportation cost is quadratic, there exists pure strategy Cournot for any location pair, but both firms would like to move away from each other.
-\end{itemize}
-
-Intuition is, for $p_1^*$ to be equilibrium price against $p_2^*$, it has to be better than any other price.
-Specifically, it has to be better than a price $\hat p_1$ which will grab all consumers from firm 2.
-When two firms are located close, $\hat p_1$ will be attractive.
-However, this cannot be an equilibrium since firm 2 will do the same reasoning.
-This is like a double auction with a cap, here the cap is decided by the distance between two firms.
-
-\section{Chaterjee, 18 JMP} % (fold)
-\label{sec:chaterjee_18_jmp}
-
-\textbf{\bibentry{Chatterjee:2017tn}}
-
-This job market paper estimates the market power within spatial competition framework.
-
-\vspace{1em}
-\noindent
-\textbf{Settings:}
-\begin{itemize}
-	\item Market is divided into several regions.
-Within each region, there are many farmers and intermediaries.
-Farmers first sell good to intermediaries, then intermediaries sell them in the retail market.
-	\item Farmers in one region can only sell to intermediaries in the same market. Intermediaries has no such restriction.
-	\item All transactions are subject to iceberg cost. So each intermediaries enjoys some monopoly power, which is increasing with scarcity of intermediaries in one region.
-	\item Farmers do Nash bargaining with intermediaries. The whole market is playing a Nash-in-Nash game. Define the optimal alternative by:
-	\[\underline p(m)=\max_{k\in \mathcal{M}-\{m\}}
-	\{\frac{p^f(k)}{\tau_{mk}}\}\]
-	where $\tau_{mk}$ is the distance cost from $m$ to $k$.
-	And the Nash bargaining outcome is the solution to:
-	\[\max_\lambda (\lambda-\underline p(m)q_m)^\delta
-	(p_m^rq_m-\lambda)^{1-\delta}\]
-
-	\item Void the region restriction will increase the welfare of farmers. Intuitively, if information gathering is of no cost, then enlarging farmers' information set will do them no harm.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{KZ Questions:}
-\begin{itemize}
-	\item What if farmers have to search for the cost? Will the welfare result hold?
-
-	\item {\color{blue} This paper introduces a `ripple effect' of competition spread through the neighbors. How we can modify this to our liquor data?}
-\end{itemize}
-% section chaterjee_18_jmp (end)
-
-\chapter{Vertical Relationship} % (fold)
-\label{cha:vertical_relationship}
-
-\section{Horn and Wolinsky, 88 RAND} % (fold)
-\label{sec:horn_and_wolinsky_88_rand}
-
-\textbf{\bibentry{Horn:1988ce}}
-
-\vspace{1em}
-\noindent
-\textbf{Highlights of the Paper:}
-\begin{itemize}
-	\item When price is determined by negotiation, the incentives to merger will be very different with the case where price is unilaterally set.
-	\item Symmetric case.
-Two suppliers, two retailers, independent or simultaneous bargaining.
-When down-stream firms are strategically complementary.
-Then a monopoly upstream firm is \textit{less} profitable than two independent suppliers.
-	\begin{itemize}
-		\item \textcolor{blue}{[Intuition]} Because when a monopoly supplier has to take into account the profit of both downstream firms, which weakens its bargaining power when the downstream firms are strategically complementary.
-	\end{itemize}
-	\item Asymmetric case.
-One supplier, two retailer, sequential bargaining.
-Whether the upstream firm will earn more profit through merging depends on the reference point (disagreement point).
-When the disagreement point is high, then the supplier can earn higher profit though sequential bargaining; otherwise profit is higher though simultaneous bargaining.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Model:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Pros:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-% subsection horn_and_wolinsky_88_rand (end)
-
-% section vertical_relationship (end)
-
-\chapter{Demand Estimation} % (fold)
-\label{cha:demand_estimation}
-
-\noindent
-\textbf{Reference:} \cite{shum:2016bk} CH 1 is very good for motivation and techniques.\\
-
-\noindent
-\textbf{Motivation for demand estimation}
-\begin{itemize}
-	\item Firstly, it is important per se, we want to understand consumer behaviour. And we want to \textit{predict the results of price change}, and \textit{introduction of new products}. 
-	Such counter factual predictions can only be built upon a structural model.
-	\item Secondly, estimation of demand function helps us better understand market structure.
-Markup itself is rarely observed (with some exceptions, like the electronic industry), but we can generally observe demand elasticity.
-	Recall that $\frac{p-MC}{p}=1/\varepsilon$ (see \ref{sec:rey_and_stiglitz_1995_rand}). Estimation of $\varepsilon$ will help us know the markup of firm, thus infer market structure.
-\end{itemize}
-
-\noindent
-\textbf{Challenges in demand function estimation:}
-\begin{itemize}
-	\item Too many parameters.
-Think of a market with 100 commodities and we want to estimate the cross elasticities.
-The number of parameters will be 10,000.
-Obviously it is impossible to have enough data to estimate so many parameters.
-	\begin{itemize}
-		\item Solved by nested logit model.
-	\end{itemize}
-	\item Unobserved quality. This will causes the endogeneity of price. And because the unobservable quality affects the selling in a highly nonlinear way, so IV is not very applicable in this case.
-	\begin{itemize}
-		\item Solved by BLP style estimation.
-	\end{itemize}
-\end{itemize}
-
-\section{Brief Literature Review} % (fold)
-\label{sec:brief_literature_review}
-
-There are two branches of demand function estimation.
-The early literature features differentiated goods (continuous choices). Classical examples include \cite{Hausman:1994km} introducing a nested approach to reduce the dimension of parameters.
-
-Recent literature focus much more on discrete choice model. The seminal papers are \cite{Berry:1994jh} and \cite*{berry.et.al.1995.emca}.
-The address of these two papers is to overcome the \textbf{endogenous price problem due to unobserved quality}. 
-Suppose we use a characteristic approach, where consumer utility and thus their purchase decision is decided by characteristics of products. 
-Some of the characteristics are obervable to consumer (and firms) but not to econometricians, for example the advertisement. 
-For higher unobserved quality, the equilibrium price will be higher, leading to a downward bias of price elasticity.
-
-\cite{Berry:1994jh} comes with a method to overcome this endogeneity problem with only \textit{market level data}.
-\begin{itemize}
-	\setlength{\itemsep}{0pt}
-	\item The basic idea is a IV based two step estimation.
-	\item First step: denote $\delta_j$ to be the `mean utility' for brand $j$.
-Notice this includes unobserved quality.
-Under some (weak) conditions, $\delta_j$ can be \textit{inversed} by market shares $(s_1,...,s_J)$, and thus we can get $\hat \delta_j$ by observed market shares.
-	\textcolor{blue}{This inversion step is the key for this paper, and many following papers treating endogenous quality problem.}
-	\item Second step: By definition, $\delta_j=X_j\beta -\alpha p +\xi_j$.
-Thus we can get $\hat \xi_j$ if we get $\hat \delta_j$.
-Suppose $E[\xi Z]=0$, then we can use $Z$ as IV to estimate consistently.
-\end{itemize}
-
-\cite{berry.et.al.1995.emca} (BLP henceforce) is more comprehensive with the same idea.
-They introduce random-coefficients logit model, which allows each individual to have different taste coefficients.
-Thus we can't directly use the inverse technique.
-The way is to use a Simulation Method of Moments (inner loop and outer loop).
-First guees a $\delta$, match mkt share, then run a IV regression, then guess different $\delta$ and get an outer loop.
-They prove a contraction mapping.
-
-\myline
-
-\textbf{\bibentry{Quan_Williams:2017wp}}
-
-This paper addresses the local heterogeneity of consumer demand,
-and concludes that usual BLP method will overestimate the welfare increase of e-commerce because local stores have satisfied most local demands.\\
-
-\noindent
-\textbf{Challenges:}
-\begin{itemize}
-	\item Huge varieties of goods in fine-grid locations make scarce data in each category. Two possible solutions for this: 1) aggregating over locations; 2) just ignore the zero sales. 
-	Aggregating is unsatisfactory since the heterogeneity of local preference is our study focus.
-	Ignoring will cause selection bias and cause overestimation of local heterogeneity.
-	\item Mean utility level cannot be recovered solely by observable variables.
-	They raise specific Converging in Distribution theorem to tackle this.
-\end{itemize}
-
-% subsection brief_literature_review (end)
-
-\myline
-
-\textbf{\bibentry{erdem_kean:96_MngSci}}
-
-\cite{erdem_kean:96_MngSci} provides an example on how to estimate demand when quality is uncertain and consumer learns by Bayesian rule.
-
-\vspace{2mm}
-\noindent
-\textbf{Motivation:}
-\begin{itemize}
-	\item Avoide ad hoc assumptions on how consumers utilizing experience information
-	\item Estimate structural models to do policy analysis
-\end{itemize}
-
-\noindent
-\textbf{Features:}
-\begin{itemize}
-	\item Estimate Dynamic Programming.
-	Consumers make decision based on their perceptions,
-	but econometricians only observe the consumption. 
-	So have to integrate over the distribution of perception errors $v_{ij}(t)$, which is is a Markov process.
-	The integration part will be very complicated.
-	\begin{itemize}
-		\item Provides a way to estimate Dynamic Programming model with simulation. Also see \cite{keane_wolpin:94REStat}.
-	\end{itemize}
-	\item Experience Shocks.
-	This indicates that even after purchasing once, 
-	consumer is not certain about the quality of the good (or the preference of himself).
-	This is mainly motivated by empirical fact: 
-	consumption behavior generally do not converge.
-\end{itemize}
-
-\noindent
-\textbf{Empirical Findings:}
-\begin{itemize}
-	\item Bayesian learning very well fit the date.
-
-\end{itemize}
-
-% section demand_function_estimation (end)
-
-\section{BLP, 95 EMCA} % (fold)
-\label{sec:blp_95_emca}
-
-The note on BLP draws deeply from \cite{Nevo:2000gn}, the original paper \cite{berry.et.al.1995.emca} is very worth reading.
-
-\textbf{Consumer Utility:}
-
-The consumer indirect utility is specified as:
-\[u _ { i j t } = \alpha _ { i } \left( y _ { i } - p _ { j t } \right) + x _ { j t } \beta _ { i } + \xi _ { j t } + \varepsilon _ { i j t } \]
-where $i$ for consumer, $j$ for products and $t$ for time periods (markets); $ x_{jt}$ are the observable characteritics, $\xi_{jt}$ is the unobservable product charateristics.
-Note that the quasilinear structure is not important, BLP beings from Cobb-Douglas form direct utility and end up with a log linear indirect utility form.
-
-We also need to specify an outside good:
-\[u _ { i 0 t } = \alpha _ { i } y _ { i } + \xi _ { 0 t } + \pi _ { 0 } D _ { i } + \sigma _ { 0 } v _ { i 0 } + \varepsilon _ { i 0 t }\]
-
-Consumer preference $\alpha_i$ and $\beta_i$ is heterogeneous across individuals. They are specified by:
-\[\left( \begin{array} { l } { \alpha _ { i } } \\ { \beta _ { i } } \end{array} \right) = \left( \begin{array} { l } { \alpha } \\ { \beta } \end{array} \right) + \Pi D _ { i } + \Sigma v _ { i }\]
-where $\alpha$ and $\beta$ are the common part; $D_i$ is hte demographics of individual $i$, for which the distribution is known (for example from census data); $v_i$ is the unobserved heterogeneous part, we assume it being multi-variate normal.
-$\Pi$ is a mapping from demographics to preference, and $\Sigma$ stands for the covariance matrix of heterogeneous part.
-
-The utility can be divided into two parts, the mean utility common for every consumer and the heterogeneous utility part:
-\[u _ { i j t } = \alpha _ { i } y _ { i } + \delta _ { j t } \left( x _ { j t ^ { \prime } } , p _ { j t } , \xi _ { j t } ; \theta _ { 1 } \right) + \mu _ { i j t } \left( x _ { j t } , p _ { j t } , v _ { i } , D _ { i } ; \theta _ { 2 } \right) + \varepsilon _ { i j t }\]
-where the $\delta_{jt}$ is the mean utility for product $j$ in market $t$, and $\mu_{ijt}$ is the heterogeneous part. 
-The parameters in $\delta_{jt}$ are called \textit{linear} parameters, and parameters in $\mu_{ijt}$ are called \textit{nonlinear} parameters.
-\[\delta _ { j t } = x _ { j t } \beta - \alpha p _ { j t } + \xi _ { j t } , \quad u _ { i j t } = \left[ - p _ { j t } , x _ { j t } \right] \left( \Pi D _ { i } + \Sigma v _ { i } \right)\]
-
-\textbf{Market Share:}
-
-The market share can be computed by:
-\begin{align}
-	s _ { j t } \left( x _ { . t } , p _ { \cdot t } , \delta _ { t } ; \theta _ { 2 } \right) &= \int _ { A _ { j t } } d P ^ { * } ( D , v , \varepsilon ) \notag \\
-	&= \int _ { A _ { j t } } d P _ { \varepsilon } ^ { * } ( \varepsilon ) d P _ { v } ^ { * } ( \nu ) d \widehat { P } _ { D } ^ { * } ( D )
-\end{align}
-where $A_{jt}$ is the set of all product characteristics that lead to choosing product $j$. Notice that the distribution of $\varepsilon, \nu$ and $D$ are known to econometrician.
-
-\textbf{Estimation:}
-
-Notice that unobservable $\xi_{jt}$ enters the market share non-linearly. But if we have $\delta_{jt}$, then $\xi_{jt}$ can be represented linearly by:
-\[\xi_{jt}\equiv \delta _ { j t } \left( S _ { . t } ; \theta _ { 2 } \right) - \left( x _ { j t } \beta + \alpha p _ { j t } \right)\]
-BLP shows that $\delta_{jt}$ can be calculated from observed market shares using contraction mapping:
-\[\delta _ { \cdot t } ^ { h + 1 } = \delta _ { \cdot t } ^ { h } + \ln S _ { \cdot t } - \ln S \left( p _ { \cdot t } , x _ { \cdot t } , \delta _ { \cdot t } ^ { h } , P _ { n s } ; \theta _ { 2 } \right)\]
-
-% chapter blp_95_emca (end)
-
-\chapter{Entry and Exit} % (fold)
-\label{cha:entry_and_exit}
-
-\section{Berry, 92 EMCA} % (fold)
-\label{sec:berry_92_emca}
-
-\textbf{\bibentry{Berry:1992gl}}
-
-\vspace{1em}
-\noindent
-\textbf{Highlights of the Paper:}
-\begin{itemize}
-	\item This paper studies the entry in airline industry.
-There are two issues to be focused: first is the simultaneity of of profits and market structure in oligopolistic market; second is the presence of a large number of heterogeneous potential entrants, which induces computational difficulty in estimation.
-
-	\item This paper features \textbf{heterogeneity of firms}, and there is a large number of potential entrants.
-	This paper shows that the SMM approach can solve this complicated equilibrium problem in a relatively easy way.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Model:}
-\begin{itemize}
-	\item The model is assumed to be \textbf{static}. At the beginning of each period, each firm takes the current network structure as given and decides whether to operate in a given city pair. 
-	The expost profit of a firm in a given market is determined by market level characteristics, its own airport presence, and of the number of competitors it faces in this market.
-	Notice the profit is independent of the firm's profit in other markets.
-
-	\item The profit function for firm $k$ in market $i$ is:
-	\[\pi_{ik}(s) = v_i(N(s))+\phi_{ik} \tag{1}\]
-	where $s$ is a given strategy file of all firms; $N(s)$ is the number of entering firms; and $\phi_{ik}$ is the index of profitability of firm $k$ in market $i$.
-	\begin{itemize}
-		\item \textcolor{blue}{[Firm Heterogeneity]}
-		We assume firm characteristics will only affect the fixed cost part, so the expost competition is symmetry.
-Thus $v_i(\cdot)$ only depends on the number of entering firms (up to scale), and the firm specific $\phi_{ik}$ only enters linearly.
-		This assumption is relaxed in \cite{Ciliberto:2009hy}, which assumes a very general form of firm heterogeneity.
-
-		\item \textcolor{blue}{[Unique $N^*$]} This separability of market level profit and firm level profit is essential.
-		Given equation (1), all equilibriums feature a unique $N^*$. And this can be used as identification tool.
-
-		\item We further specify $v_i(N)$ and $\phi_{ik}$ parametrically:
-		\[v_i(N)=X_i\beta+h(\delta,N)+\rho u_{io} \tag{2}\]
-		$\beta,\delta,\rho$ are parameters to be estimated. $X_i$ are characteristics of market $i$, $u_{io}$ are market characteristics observed by all firms but not econometricians.
-		\footnote{This is a complete information game.}
-		This can be derived from a Cournot model with constant and identical marginal costs together with a constant-elasticity demand function.
-
-		\item Firm specific portion of profit is:
-		\[\phi_{ik}=Z_{ik}\alpha+\sigma u_{ik}\]
-		$Z_{ik}$ are firm level characteristics and $u_{ik}$ unobservable to econometricians.
-
-		\item KZ: We have to assume some independence on unobservable characteristics for identification. 
-		But this is actually not very reasonable since in the firm side these characteristics are nothing special and thus may possess any kind of correlation.
-	\end{itemize}
-	Combine all these and we get:
-	\[\pi_{ik}(N)=X_i\beta-\delta \ln(N)+Z_{ik}\alpha
-	+\rho u_{io}+\sigma u_{ik} \tag{4}\]
-	We denote the observed terms as $r_{ik}(N)$ and the unobserved terms as $\varepsilon_{ik}$.
-	Notice that we can not identify $\rho, \sigma$ separately since they are just scale parameters, and this discrete choice model is identified up to scale.
-	This paper normalize $\sigma$ to $\sqrt{1-\rho^2}$.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Identification:}
-\begin{itemize}
-	\item The identification is through the equilibrium number $N^*$ of entering firms.
-	For a given unobserved $\varepsilon$, the equilibrium entering firm number is smaller or equal than $N$ iff:
-	\[(\varepsilon:\# \{\varepsilon_k:
-	\varepsilon_k \geq -r_k(N+1)\}=j)
-	,\ j=0,\dots,N\]
-	That is, no more than (but may be less than) $N$ firms can make a profit if $N+1$ firms enter.
-
-	\item Then suppose exact $J$ firms can make profits in a $N+1$ equilibrium, the probability of this event is:
-	\[H_{J(N+1)}=\sum_{s\in S(J)}
-	\int_{A_1(s,N+1)} \dots \int_{A_k(s,N+1)}
-	p(\varepsilon)d \varepsilon\]
-	where $s$ is a specific entering profile, and $S(J)$ is the set of entering profiles with $J$ entering firms.
-	For $K$ potential entering firms, there are $C_{N+1}^J$ many possible entering profiles.
-	The area $A_k(s,N+1)$ is:
-	\begin{align*}
-	A_k(s,N+1)&=(-r_k(N+1),\infty),\ \text{if}\ s_k=1\\
-	&= (-\infty,-r_k(N+1)),\ \text{else}
-	\end{align*}
-	That is, $A_k(s,N)$ is the region of $\varepsilon_k$ that firm $k$ can earn profit in a $(N+1)$-firm equilibrium if the profile $s$ shows it enters.
-	The probability $Pr(N^*\leq N)$ is:
-	\[Pr(N^* \leq N)= \sum_{J=0}^N H_{J(N+1)}\]
-	And thus the probability of an $N$-firm equilibrium is:
-	\[Pr(N^* = N)=Pr(N^* \leq N)-Pr(N^* \leq (N-1))\]
-	We can then apply MLE to maximize this probability.
-
-	\item Notice that although in principle we can estimate this in MLE as long as we have enough variation in $X_i$, the computation of $Pr(N^*=N)$ is very difficult.
-	This paper tackles this difficulty with two approaches: 1) they put additional restrictions over the parameters; 2) they use simulation methods to simplify.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Computation Issues:}
-\begin{itemize}
-	\item Although in principle we can identify the parameter using MLE using above expression, but the computation burden is huge.
-As we have pointed out, the number of possible combinations of potential entrants and actual entrants are $C_n^k$, which grows very fast.
-	To solve this problem, this paper takes two approaches.
-	\begin{itemize}
-		\item Put more restrictions over the parameters
-		\item Use SMM
-	\end{itemize}
-	We focus on the second approach.
-
-	\item \textcolor{blue}{[SMM]}
-	First we generate a series of $\hat u_i$, then given $\theta$, we can calculate an estimate $\hat N$ for each market, with the property:
-	\[E_{\hat u}[\hat N(W_i,\theta,\hat u)] = E[N^*|W_i,\theta]\]
-	So we can write the moment condition as:
-	\[v_{io}(N_i^*,W_i,\theta)\equiv N^*_i-E_{\hat u}[\hat N(W_i,\theta,\hat u)]\]
-	Estimating this moment condition will give us consistent $\theta$.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Empirical Results:}
-\begin{itemize}
-	\item Firm observable heterogeneities, such as airport presence, play an important role in determining airline profitability.
-
-	\item Profits decline rapidly in the number of entering firms, consistent with \cite{Bresnahan:1990gw}.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Pros:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item The unobserved term $u_{ik}$ and $u_{io}$ are assumed to be i.i.d. across both firms and markets.
-	Especially, $u_{ik}$ are more likely to be correlated across markets for a given firm.
-
-	\item The heterogeneity is assumed to be a very specific term, which only affects the ``fixed cost'' of firms.
-Conditional on firm entering, the subsequent subgame is symmetric.
-This restriction is quite strong.
-\end{itemize}
-
-% subsection berry_92_emca (end)
-
-\section{Seim, 06 RAND} % (fold)
-\label{sec:seim_06_rand}
-
-\textbf{\bibentry{Seim:2006em}}
-
-\vspace{1em}
-\noindent
-\textbf{Highlights of the Paper:}
-\begin{itemize}
-	\item By introducing private information and using Bayesian Nash Equilibria, the strategy of each firm is a mapping from its own type $c_i$ to a strategy $s_i$, which does not directly depend on other firms' strategies.
-	This ensures the uniqueness of equilibrium in the specific setting of this paper, but uniqueness is not guaranteed in general.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Model:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Empirical Results:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Pros:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item Charlie Murry points out that the result is somewhat directly being assumed.
-The potential number of entrants $\mathcal F$ is being assumed, but if we assume this and we know the actual entrant number $\mathcal E$, isn't the probability of entrant directly derived?
-\end{itemize}
-
-\section{Davis, 06 JoE} % (fold)
-\label{sec:davis_06_joe}
-
-\textbf{\bibentry{Davis:2006kn}}
-
-\vspace{1em}
-\noindent
-\textbf{Highlights:}
-\begin{itemize}
-	\item This paper is a natural generalization of \cite{Berry:1992gl}.
-Berry guarantees the uniqueness of entering firms using assumption of ``separable profit function'' and ``symmetric second stage competition''.
-	This paper relaxes the assumptions by supermodularity conditions.
-
-	\item Under his assumptions, this paper guarantees: 1) existence of PSNE; 2) the uniqueness of market index (number of entering firms in Berry's model) within PSNE.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Model:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Empirical Results:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Pros:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-% subsection subsection_name (end)
-
-% subsection seim_02_rand (end)
-
-\section{Jia, 08 EMCA} % (fold)
-\label{sec:jia_08_emca}
-
-\textbf{\bibentry{Jia:2008fz}}
-
-\vspace{1em}
-\noindent
-\textbf{Highlights of the Paper:}
-\begin{itemize}
-	\item Jia's paper does not investigate the crowdness of stores in one market.
-It focuses on the distribution of stores across the country.
-In Jia's market segmentation, each brand will put at most one store in each market.
-So the whole story is about how to allocate stores in different markets, instead of how many stores in one market.
-\end{itemize}
-
-% subsection jia_08_emca (end)
-
-\section{Tamer, 03 RES} % (fold)
-\label{sec:tamer_03_res}
-
-\textbf{\bibentry{Tamer:2003hi}}
-
-\mytitle{Highlights:}
-\begin{itemize}
-	\item This paper shows that ``games with multiple equilibria can be estimated without imposing coherency conditions if the model is used only to inform upper and lower bounds on the probabilities of outcomes rather than assigning exact probabilities to each potential outcome.'' \citep{Davis:2006kn}
-
-	\item This paper differentiates \textbf{incoherent model} with \textbf{incomplete model}.
-	\textit{Incoherency} comes from the not well defined optimization problem of the agent; while \textit{incomplete} econometric models means that the mapping from $(x,u)$ to $y$ is not a function but a correspondence.
-
-	\item The paper also shows, the parameter of an incomplete model can be \textbf{point identified}, as long as we have at least one exogenous variable with unbounded range.
-This is called identification at infinity.
-\end{itemize}
-
-\mytitle{Identification:}
-\begin{itemize}
-	\item For a model like in \cite{Bresnahan:1990gw}:
-		\[\begin{array} { l } { y _ { 1 }= x _ { 1 } \beta _ { 1 } + y _ { 2 } \Delta _ { 1 } + u _ { 1 } } \\ { y _ { 2 } = x _ { 2 } \beta _ { 2 } + y _ { 1 } \Delta _ { 2 } + u _ { 2 } } \end{array}\]
-
-	\item If there is one exogenous variable (exclusively) on $x_1$ or $x_2$ that can take value at infinity, then the parameter is point identified.
-The idea is simple, say $x_{1k}$ takes $-\infty$ and $\beta_{1k}$ is positive, then firm 1 will not enter the market for sure regardless of $(u_1,u_2)$.
-Thus all other parameters can be point identified using this subsample.
-
-	\item {[$\beta$ Identification]} Take $x_{1k}$ to $-\infty$:
-	\begin{align}
-	\operatorname { Pr } [ ( 0,0 ) | x _ { 1 } , x _ { 2 } ^ { * } ] = \operatorname { Pr } \left[ u _ { 1 } \leq - x _ { 1 } \beta _ { 1 } , u _ { 2 } \leq - x _ { 2 } ^ { * } \beta _ { 2 } \right] & \neq \operatorname { Pr } \left[ u _ { 1 } \leq - x _ { 1 } b _ { 1 } , u _ { 2 } \leq - x _ { 2 } ^ { * } b _ { 2 } \right] \\
-	& 
-	\end{align}
-	the inequality is from:
-	\[\begin{aligned} \operatorname { Pr } \left[ u _ { 1 } \leq - x _ { 1 } \beta _ { 1 } , u _ { 2 } \leq - x _ { 2 } ^ { * } \beta _ { 2 } \right] & \simeq \operatorname { Pr } \left[ u _ { 2 } \leq - x _ { 2 } ^ { * } \beta _ { 2 } \right] \neq \operatorname { Pr } \left[ u _ { 2 } \leq - x _ { 2 } ^ { * } b _ { 2 } \right] \\ & \simeq \operatorname { Pr } \left[ u _ { 1 } \leq - x _ { 1 } b _ { 1 } , u _ { 2 } \leq - x _ { 2 } ^ { * } b _ { 2 } \right] \end{aligned}\]
-	Thus $\beta_2$ is identified. Given $\beta_2$, we can identify $\beta_1$ since $x_1$ is full rank.
-
-	\item {[$\Delta$ Identification]} The identification of $\Delta$ is similar to that of $\theta$. The difference is that we now use $(y_1,y_2) = (1,1)$ instead of $(0,0)$.
-	\begin{align}
-		\Pr[(1,1) | x_1, x_2^*] = \Pr(u_1 > -x_1\beta_1 - \Delta_1, 
-		u_2 > - x_2\beta_2 - \Delta_2) \neq \Pr(u_2 > -x_2\beta_2 -d_2)
-	\end{align}
-
-	\item Only observations of $(0,0)$ and $(1,1)$ are necessary for identification. The main point to use $(0,1)$ and $(1,0)$ is to increase efficiency with finite data.
-\end{itemize}
-
-\mytitle{Semi-Parametric Estimation:}
-\begin{itemize}
-	\item Define the population frequency of $(0,1)$ to be $H(\cdot)$:
-	\[H ( x ) = \operatorname { Pr } [ ( 0,1 ) | x ]\]
-	and the quasi-likelihood can be defined as:
-	\[\begin{aligned} L \left( b ; \hat { H } _ { t n } \right) = & \sum _ { i = 1 } ^ { n } \left[ y _ { i 1 } y _ { i 2 } \log \left( P _ { 1 } \left( x _ { i } , b \right) \right) \right.
-\\ & + \left( 1 - y _ { i 1 } \right) \left( 1 - y _ { i 2 } \right) \log \left( P _ { 2 } \left( x _ { i } , b \right) \right) + \left( 1 - y _ { i 1 } \right) y _ { i 2 } \log \left( \hat { H } _ { t n } \left( x _ { i } , b \right) \right) \\ & + y _ { i 1 } \left( 1 - y _ { i 2 } \right) \log \left( 1 - P _ { 1 } \left( x _ { i } , b \right) - P _ { 2 } \left( x _ { i } , b \right) - \hat { H } _ { t n } \left( x _ { i } , b \right) \right) ] \end{aligned}\]
-	where $P_1, P_2$ can analytically be derived and $H$ is non-parametrically estimated.
-	\item The SML $\beta$ is consistent and normally distributed (in BR case).
-\end{itemize}
-% subsection tamer_03_res (end)
-
-\section{Ciliberto and Tamer, 09 RES} % (fold)
-\label{sec:ciliberto_and_tamer_09_res}
-
-\textbf{\bibentry{Ciliberto:2009hy}}
-
-\vspace{1em}
-\noindent
-\textbf{Highlights of the Paper:}
-\begin{itemize}
-	\item This paper has two contributions to entry game estimation literature.
-First, it allows very general form of firm heterogeneity; second, by adopting partial identification it makes no assumption on equilibrium selection.
-
-	\item {[Firm Heterogeneity]} Recall that in \cite{Berry:1992gl}, the only heterogeneity is a heterogeneous ``fixed cost'', which enters linearly.
-If we allow more general form of heterogeneity, then even the number of entrants is not unique.
-
-	\item {[Multiple Equilibria]} The estimation procedure allows mixed strategy.
-But this will make the equilibrium solving process more difficult.
-The model \textbf{does not specify or estimate any equilibrium selection rule} ($\Pr(y|\varepsilon,X)$ in the paper).
-In principle this can be estimated, either non-parametrically (as in \cite{Tamer:2003hi}) or as a function of $\varepsilon$ and $X$ (as in Berry and Tamer (2006)).
-This makes the identified set not sharp, but the computation much easier.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Model:}
-\begin{itemize}
-	\item The profit function for firm $i$ in market $m$ is:
-	\[\pi_{im}=S'_m\alpha_i + Z'_{im}\beta_i+W'_{im}\gamma_i+
-	\textcolor{blue}{\sum_{j\neq i }\delta^i_j y_{jm}+\sum_{j\neq i}Z'_{jm}\phi^i_j y_{im}}
-	+\varepsilon_{im}\]
-	where $S_m$ is market characteristics; $W_{im}$ is the firm characteristics that will only affect its own profit in market $m$, such as cost variables; $Z_{im}$ is the firm characteristics that may affect both own and others profit.
-	$\sum_{j\neq i }\delta^i_j y_{jm}$ captures the effect of other firm's entering, and $\sum_{j\neq i}Z'_{jm}\phi^i_j y_{im}$ further captures the effect of entering firms' characteristics.
-	\begin{itemize}
-		\item Notice that the impact of other firms can be directly dependent on firm identity.
-		For a specific firm $i$, having $j$ or having $k$ in the market may impact $i$'s profit differently, even if $j$ and $k$ has same characteristics on this market.
-	\end{itemize}
-
-	\item {[Main Idea]} Conditional on observables, although we cannot calculate \textit{the probability} of a entering profile $y$ if multiple equilibria exist, but we can get the \textit{bound} of probabilities.
-	\begin{align}
-		& \underline \Pr(y) = \Pr(\vec \varepsilon | \text{ y is the unique equilibrium}) \notag \\
-	& \overline \Pr(y) = \Pr(\vec \varepsilon | \text{ y is among the equilibria})
-	\end{align}
-
-	\item {[Identification]} The identified set $\Theta_I$ contains all $\theta$'s s.t. the \textit{all moment inequalities} hold. 
-	Point identified at infinite exogenous variable, see \cite{Tamer:2003hi}.
-	In practical estimation, variation in excluded exogenous variables (like the airport presence or cost variables in this paper) help shrink the set $\Theta_I$.
-\end{itemize}
-
-\mysubtitle{Estimation:}
-\begin{itemize}
-	\item The estimation is based on the moment inequalities:
-	\begin{align}
-		\mathbf { H } _ { 1 } ( \boldsymbol { \theta } , \mathbf { X } ) \equiv \left[ \begin{array} { c } { H _ { 1 } ^ { 1 } ( \boldsymbol { \theta } , X ) } \\ { \vdots } \\ { H _ { 1 } ^ { 2 K } ( \boldsymbol { \theta } , X ) } \end{array} \right] \leq \left[ \begin{array} { c } { \operatorname { Pr } \left( \mathbf { y } _ { 1 } | X \right) } \\ { \vdots } \\ { \operatorname { Pr } \left( \mathbf { y } _ { 2 ^ { K } } | X \right) } \end{array} \right] \leq \left[ \begin{array} { c } { H _ { 2 } ^ { 1 } ( \boldsymbol { \theta } , X ) } \\ { \vdots } \\ { H _ { 2 } ^ { 2 ^ { K } } ( \boldsymbol { \theta } , X ) } \end{array} \right] \equiv \mathbf { H } _ { 2 } ( \boldsymbol { \theta } , \mathbf { X } )
-	\end{align}
-	The objection function is:
-	\[Q ( \boldsymbol { \theta } ) = \int \left[ \left\| \left( P ( \mathbf { X } ) - H _ { 1 } ( \mathbf { X } , \boldsymbol { \theta } ) \right) - \right\| + \left\| \left( P ( \mathbf { X } ) - H _ { 2 } ( \mathbf { X } , \boldsymbol { \theta } ) \right) _ { + } \right\| \right] d F _ { x }\]
-	Notice that $\mathbf H_1$ and $\mathbf H_2$ cannot be analytically derived in a complicated game, and have to be estimated by simulation.
-
-	\item {[$\Theta_I$ or $\theta_I$]} When doing infernece, the interest is either the identified set $\Theta_I$ or the true parameter $\theta_I \in \Theta_I$.
-Note that there is one true $\theta_I$ even if  $\Theta_I$ is only set identified (e.g.
-when the unbounded exclusion variable $x$ is not available).
-\end{itemize}
-
-\mysubtitle{Empirics:}
-\begin{itemize}
-	\item \red{To be added: the use of hub airports}
-	\item \red{To be added: the marginal effect table}
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item The identified set is not sharp. \red{What is a sharp identified set?}
-
-	\item \red{Does the effect of other firms $\delta$ have to be negative?}
-\end{itemize}
-
-% subsection ciliberto_and_tamer_09_res (end)
-
-\section{Grieco, 14 RAND} % (fold)
-\label{sec:grieco_14_rand}
-
-\textbf{\bibentry{Grieco:2014hz}}
-
-\mytitle{Highlights:}
-\begin{itemize}
-	\item This paper integrate complete information entry game and incomplete information entry game in one model.
-The paper also tests the two polar case of complete information and incomplete information.
-
-	\item The intuition for the identification relies on instrument variable that affects private information but not public information.
-In the private information game, player 1's decision will not depend on private information $x_2$, because player 1 can only take into account public informations and make a guess on player 2's decision.
-	Contrary to this, private information $x_2$ will affect player 1's decision in a complete information game if the covariates support is rich enough.
-	Thus if we can find some instruments affecting private information $(x_1,x_2)$, we can identify complete and incomplete information. 
-\end{itemize}
-
-\mytitle{Model:}
-\begin{itemize}
-	\item The model is a two firm entry problem with binary decisions:
-	\[\pi _ { i } \left( y _ { i } , y _ { - i } ; x , \theta \right) = \left\{ \begin{array} { l l } { x _ { i } \theta _ { i \mu } + y _ { - i } x _ { i } \theta _ { i \delta } + \epsilon _ { i } + v _ { i } } & { \text { if } y _ { i } = 1 } \\ { 0 } & { \text { if } y _ { i } = 0 } \end{array} \right.\]
-	where the $\varepsilon_i$ represents public shock, and $\mu_i$ is private shock.
-	The public shocks $(\varepsilon_1, \varepsilon_2)$ follows bivariate normal, with common variance component $\sigma^2_\varepsilon$ and correlation coefficient $\rho$.
-	Private shocks are independent and have variance $\sigma^2_\mu \equiv 1- \sigma^2_\varepsilon$.
-	$\sigma^2_\varepsilon$ controls relative importance of public shocks.
-
-	\item The equilibrium of this model is:
-	\[\chi _ { i } ^ { b } \left( \chi _ { j } , \epsilon , x ; \theta \right) = - \left( x _ { i } \theta _ { i \mu } + \varrho _ { j } \left( \chi _ { j } , \epsilon ; \theta \right) x _ { i } \theta _ { i \delta } + \epsilon _ { i } \right)\]
-	where the left is the threshold of player $i$ to enter, and $\varrho_j$ is the expected probability of $j$ to enter, conditional on $j$'s threshold.
-	Any joint set $\chi = \left( \chi _ { 1 } , \chi _ { 2 } \right)$ satisfies the above equation will be an equilibrium.
-
-	\item {[Multiplicity]} Note that even with incomplete shock only, there may exist multiple equilibria.
-Though each player will play a threshold strategy, the values of thresholds are coordinated.
-Note the difference with \cite{Seim:2006em}.
-
-	\item Grieco finds that the area of multiplicity shrinks as the information environment becomes more and more incomplete. See their Fig 1.
-\end{itemize}
-
-\mytitle{Identification:}
-\begin{itemize}
-
-	\item {[Only Private Shock Case]} The probability of observing outcome $y$ given a selected equilibrium $e$ is:
-	\[\tilde { \Psi } ( y | x , \theta , e ) = \prod _ { i = 1 } ^ { 2 } \varrho _ { i } ^ { e } ( x , \theta ) ^ { 1 \left[ y _ { i } = 1 \right] } \left( 1 - \varrho _ { i } ^ { e } ( x , \theta ) \right) ^ { 1 \left[ y _ { i } = 0 \right] }\]
-	Unconditional on equilibrium, it can be represented as:
-	\[\Psi ( y | x , \theta , \lambda ) = \sum _ { e \in \delta ( x , \theta ) } \lambda ^ { e } ( x , \theta ) \tilde { \Psi } ( y | x , \theta , e )\]
-	where $\lambda^e$ is the equilibrium selection rule and can be jointly estimated. See \cite{Tamer:2003hi} semi-parametric estimation routine.
-	The sharp identified set is:
-	\[\Theta _ { I } = \left\{ \begin{aligned} \theta \in \Theta : \forall y , x , \exists \tilde { \lambda } \in [ 0,1 ] ^ { \overline { E } } \text { s.t.
-} & P ( y | x ) = \Psi ( y | x , \theta , \tilde { \lambda } ) \\ & \sum _ { e \in \mathcal { E } ( x ; \theta ) } \tilde { \lambda } ^ { e } = 1 \end{aligned} \right\}\]
-	\red{How we are going to estimate this? are the set convex or something?}
-\end{itemize}
-
-\mytitle{Inference}
-\begin{itemize}
-	\item This paper uses a sieve based weighted Bootstrap to do inference. But Karl says there is something wrong with this approach. Not sure about this.
-\end{itemize}
-
-% section grieco_14_rand (end)
-
-\section{Holmes, 11 EMCA} % (fold)
-\label{sec:holmes_2011_emca}
-
-\mytitle{Estimation}
-
-\mysubtitle{Disagregate Inequalities v.s. Aggregate Inequalities}
-
-Why not using disaggregate inequalities which will generate more moment inequalities? Because there is measurement error. Suppose the model is:
-\[y_a \geq \theta\]
-but the LHS is is observed with error:
-\[\tilde y_a = y_a + \eta_a\]
-If we pick $\theta$ to minimize the disaggregated inequalities, then we are looking for $\theta$ that satisfies:
-\[\left\{\theta | \theta \leq \min_{a}\{y_a+\eta_a\}\right\}\]
-and some very extreme $\eta_a$ will drive the results.
-% section holmes_2011_emca (end)
-
-% subsection ellickson_houghton_timmins_13_rand (end)
-
-\section{Lee and Pakes, 09 EL}
-\label{sec:lee_pakes_09_el}
-
-There is multiplicity problem in counterfactual analysis of entry game. This paper discusses two possible ways of dealing multiple equilibria.
-
-\mytitle{Enumerating Equilibria}
-
-The first approach just enumerate all possible limiting equilibria, and then compare them. 
-The equilibria are limiting in the sense that all firms know the expected value of the cost shock.
-The good news is, there are only a handful of possible equilibria in their case.
-
-\mytitle{Equilibria Selection by Learning}
-
-Based on previous enumeration results, we can apply learning process to see which equilibrium is more possible. There are two possible learning processes:
-\begin{itemize}
-	\item {[Best Response Dynamics]} Firm believes its competitors will play the same strategy as they did in the prior period, and thus each firm will play its best response to last periods' play.
-
-	\item {[Fictitious Play]} Each firm believes that the next play of its competitors will be a random draw from the set of tuples of plays observed since the regime change, and chooses it's optimal strategy accordingly.
-(KZ: the optimal should be mix?)
-\end{itemize}
-
-To get the distribution of equilibria, they compute 1000 runs for each learning process.
-Each run is stopped when they converged to a single allocation profile, where convergence is defined as having remained in the same state for 50 iterations.
-
-\section{Wollman, 18 AER} % (fold)
-\label{sec:wollman_18_aer}
-
-\mytitle{Identification}
-
-The identification of the second stage is a standard BLP, I will focus on the identification of the first step about the fixed costs.
-
-The inequalities based on rationality condition is:
-\[\begin{array}{l}{\Delta \pi\left(J_{f, t}, J_{f, t} \backslash j, J_{-f, t}, z_{t}, w_{t}\right)} \\ {\quad+x_{j}^{\prime}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right) \mathscr{E}\left[\theta_{f, x_{j}, t} | \mathscr{J}_{f, t}\right] \geq 0}\end{array} \tag{6}\]
-\[\begin{array}{l}{\Delta \pi\left(J_{f, t}, J_{f, t} \cup j, J_{-f, t}, z_{t}, w_{t}\right)} \\ {-x_{j}^{\prime}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right) \mathscr{E}\left[\theta_{f x_{j}, t} | \mathscr{I}_{f, t}\right] \geq 0}\end{array} \tag{7}\]
-
-Note that $\mathcal E [\theta_{f,x_j,t}|\mathcal F_{f,t}]$ is unknown to econometricians, thus we need to parameterize it and convert the inequalities to some observable moments. By parameterization:
-\[\theta_{f}=\left[\theta_{0}+\theta_{0}^{B i g 3}+\theta_{0}^{J p n}, \theta_{g}+\theta_{g}^{B i g 3}, \theta_{c a b o v e r}+\theta_{c a b o v e r}^{J p n}, \theta_{c o m p a c t}, \theta_{l o n g}\right]\]
-and the suck cost parameter $\theta_{f,x_j,t} \equiv \theta_f + \nu_{2,t}$.
-Notice that the structural error $\nu_{2,t}$ is a vector, with each element indexing a characteristic error.
-To rationalize data, we need to introduce structural error $\nu_{2,t}$ and expectation error $\nu_{1,t}$.
-\begin{itemize}
-	\item $\nu_2$ is known to the firms when making entry decision, but unknown to econometricians
-	\item $\nu_1$ is unknown to firms when making entry decision
-\end{itemize}
-
-The actual moment inequalities for estimation are:
-\[\begin{array}{l}{\frac{1}{X T F} \sum_{x_{j}} \sum_{t} \sum_{f} h_{f, x, t}^{i}\left\{j \in J_{f, t}\right\}} \\ { \times\left[\Delta \hat{\pi}\left(J_{f, t}, J_{f, t} \backslash j, J_{-f, t}, z_{t}, w_{t}\right)+x_{j}^{\prime} \theta_{f}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right)\right] \geq 0}\end{array} \tag{8}\]
-\[\begin{array}{l}{\frac{1}{X T F} \sum_{x_{j}} \sum_{t} \sum_{f} h_{f, x_{j}, t}^{i}\left\{j \notin J_{f, t}\right\}} \\ { \times\left[\Delta \hat{\pi}\left(J_{f, t}, J_{f, t} \cup j, J_{-f, t}, z_{t}, w_{t}\right)-x_{j}^{\prime} \theta_{f}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right)\right] \geq 0}\end{array} \tag{9}\]
-In appendix, the empirical moment is shown to converge in probability to:
-\begin{align*}
-	\stackrel{p}{\rightarrow} & E_{x_{j}, t, f}\left[h_{f, x_{j}, t}^{i}\left\{j \in J_{f, t}\right\} \Delta \pi\left(J_{f, t}, J_{f, t} \backslash j, J_{-f, t}, x_{t}, w_{t}\right)\right] \\
-	& +E_{x_{j}, t, f}\left[h_{f, x_{j}, t}^{i}\left\{j \in J_{f, t}\right\}\left[x_{j}^{\prime}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right) \mathscr{E}\left[\theta_{f, x_{j}, t} | \mathscr{F}_{f, t}\right]\right]\right] \\
-	& +E_{x_{j}, t, f}\left[h_{f, x_{j}, t}^{i}\left\{j \in J_{f, t}\right\}\left(\left\{j \notin J_{f, t-1}\right\}-\lambda\left\{j \in J_{f, t-1}\right\}\right) \nu_{1, f, t, J_{f, t}, J_{f, t} \backslash j, J_{f, t-1}}\right] \\
-	& -C E_{x_{j}}\left[x_{j}^{\prime} h_{f, x_{j}}^{i} E_{t}\left[h_{x_{j}, t}^{i} \nu_{2, t}\right]\right] \geq 0
-\end{align*}
-The first two lines larger than 0 by rationality assumption, the third line is 0 in expectation since $\nu_1$ is mean independent of agents' information set.
-The forth line is tricky, and we need to pick $h^i$ to make it zero in expectation.
-
-Things to be noted here:
-\begin{enumerate}
-	\item $\mathcal E$ represents agent's subjective expectation, and $E$ is the expectation by actual DGP.
-	\item The unobservable $\mathcal E[\theta_{f,x_j,t}]$ has been substituted by parameter $\theta_f$. We have to take care of $\nu_2$ because it may induce selection problem.
-	\item $h_{f, x_{j}, t}^{i}\left\{j \notin J_{f, t}\right\}$ is used as instruments and to control the endogenous problem induced by $\nu_2$.
-\end{enumerate}
-
-% section wollman_18_aer (end)
-
-% section entry_and_exit (end)
-
-\chapter{Dynamic Decisions} % (fold)
-\label{cha:dynamic_decisions}
-
-\section{Rust, 87 EMCA} % (fold)
-\label{sec:rust_87_emca}
-
-\textbf{\bibentry{Rust:1987hn}}
-
-\vspace{1em}
-\noindent
-\textbf{Highlight of the Paper:}
-\begin{itemize}
-	\item This is the seminal paper to estimate a dynamic model.
-	A very clever trick is separating $EV_\theta$ with a Bellman function, which greatly reduces the dimension since $\varepsilon$ is not an argument of $EV$.
-
-	\item But the computation burden is still heavy, because for every $\theta$ we need to solve a contraction mapping. \cite{Hotz:1993ea} eases the computation using SMM.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Structural Estimation without Closed-form Solutions:}
-\begin{itemize}
-	\item The decision maker has the following value function:
-	\[V_\theta(x_t,\varepsilon_t)=
-	\sup_\Pi E\Big\{
-	\sum_{j=t}^{\infty} \beta^{j-t}[u(x_j,f_j,\theta_1)
-	+\varepsilon_j(f_j)] | x_t,\varepsilon_t,\theta_2,\theta_3
-	\Big\}\]
-	where $f_t(x_t,\varepsilon_t,\theta)$ is the optimal control function. The transition rule is:
-	\[dp\{x_{t+1},\varepsilon_{t+1},\dots,
-	x_{t+N},\varepsilon_{t+N}\}
-	=\prod_{i+t}^{N-1}p(x_{i+1},\varepsilon_{i+1}
-	| x_i,\varepsilon_i,f_i(x_i,\varepsilon_i),\theta_2,\theta_3)\]
-	This infinite horizon problem can be rewritten as a Bellman function with stationary decision rule:
-	\[V_\theta(x_t,\varepsilon_t)=
-	\max_{i \in C(x_i)}
-	[u(x_i,i,\theta_1)+\varepsilon_t(i)+\beta
-	E V_\theta(x_t,\varepsilon_t,i)]\]
-
-	where
-	\[EV_\theta(x_t,\varepsilon_t,i)=
-	\int_y \int_\eta V_\theta(y,\eta)
-	p(dy,d \eta|x_t,\varepsilon_t,i,\theta_2,\theta_3)\]
-	One property (difficulty) of this model is that distribution of $\varepsilon_{t+1}$ is conditional on $i$ and $\varepsilon_t$.
-So $EV_\theta$ is a nonlinear function of $\varepsilon_t$, which would induce huge dimensionality problem in value function iteration.
-	\begin{itemize}
-		\item This model is actually a simple version of Cooper's general durable consumption problem.
-The key is that $\{x_t\}$ follows different transition rule after different action $i$.
-This problem is actually simpler because the only decision variable is $i$.
-	\end{itemize}
-
-	\item \textcolor{blue}{[Conditional Independence Assumption]}
-	To make this problem computationally tractable, we assume:
-	\[p(x_{t_1},\varepsilon_{t+1}|x_t,\varepsilon_t,i,\theta_2,\theta_3)=
-	q(\varepsilon_{t+1}|x_{t+1},\theta_2)p(x_{t+1}|x_t,i,\theta_3)
-	\]
-	This assumption says, the transition of $(x_t,\varepsilon_t)$ is separable.
-Probability of $\varepsilon_{t+1}$ only directly depends on $x_{t+1}$, and the transition of $x_{t+1}$ is independent of current $\varepsilon_t$.
-	That's to say, $\varepsilon_t$ is like a temporary disturbance on $x_t$.
-
-	\item \textcolor{blue}{[Below Important]}
-	The power of above assumption is that we now can solve $EV_\theta$ in a contraction mapping $T_\theta$
-	(the proof is not trivial):
-	\[EV_\theta(x,i)=\int_y G(u(y,\theta_1)+\beta EV_\theta(y)|y,\theta_2)\cdot p(dy|x,i,\theta_3)\]
-	where $V_\theta(x)$ actually is $\max\{V_\theta(x,0),V_\theta(x,1)\}$, and
-	\[G(u(x,\theta_1)+\beta EV_\theta(x)|x,\theta_2)
-	= \int_\varepsilon \max_{j \in C(x)}
-	[u(x,j,\theta_1)+\beta EV_\theta(x,j)]
-	q(d \varepsilon|x,\theta_2)\]
-	And the conditional probability of choosing choice $i$ is given by:
-	\[P(i|x,\theta)=G_i(u(x,\theta_1)+\beta EV_\theta(x)|x,\theta_2)\]
-	Now we can define the likelihood function: (directly from conditional independence assumption)
-	\[\mathcal{L}^f(x_1,i_1,\dots,x_T,i_T|x_0,i_0,\theta)=
-	\prod_{t=1}^{T}P(i_t|x_t,\theta)p(x_t|x_{t-1},i_{t-1},\theta_3)\]
-	\begin{itemize}
-		\item The transition rule parameter $\theta_3$ can be separately estimated. 
-	\end{itemize}
-
-	\item \textcolor{blue}{[Nested Fixed Point Algorithm]}
-	An inner fixed point algorithm solves $EV_\theta$ for each value of $\theta$; 
-	an outer algorithm captures $\theta$ that maximizes the likelihood.
-	\begin{itemize}
-		\item To estimate $EV_\theta$, we need to further assume that $\varepsilon$'s are i.i.d. distributed across choices and time according to T1EV.
-		With this assumption, we have:
-		\begin{align*}
-		EV_\theta(x,i)& \equiv E_{y,\varepsilon|x,i}
-		\Big\{\max_{j=0,1}[u(y,\varepsilon;\theta)+\beta EV(y,j;\theta)]
-		\Big\} \\
-		&=E_{y|x,i}\log \Big\{
-		\sum_{j=0,1} \exp[u(y,\varepsilon;\theta)+\beta EV(y,j;\theta)]
-		\Big\}\\
-		&= \int_y log \Big\{
-		\sum_{j=0,1}\exp[u(y,j;\theta)+\beta EV(y,j;\theta)]
-		\Big\}p(dy|x,i)
-	\end{align*}
-	The second equality uses the closed form of maximization over expectation of T1EV.
-	\footnote{See \cite*{Chiong:2016ga} for details.}
-
-	\item Once $EV_\theta(x,i)$ has been calculated using value function iteration, the choice probability $p(i_t|x_t)$ can be computed as:
-	\[\frac{\exp(E_\varepsilon u(x_t,\varepsilon, i_t;\theta)+
-	\beta EV(x,i;\theta))}
-	{\sum_{i=0,1}\exp(E_\varepsilon u(x_t,\varepsilon, i_t;\theta)+
-	\beta EV(x,i;\theta))}\]
-
-	\item Once we get $EV_\theta(x,i)$, then we can get $P(i_t|x_T,\theta)$.
-And since the transition rule $p(x_t|x_{t-1},i_{t-1},\theta_3)$ can be separately estimated.
-We now have collected all components of the likelihood function.
-Loop over $\theta$ to maximize the likelihood function.
-	\end{itemize}
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Empirical Results:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Pros:}
-\begin{itemize}
-	\item The \textit{Conditional Independence} assumption of $\varepsilon$ is very important.
-With this assumption, the $\varepsilon_T$ becomes a perturbation of $x_t$ and independent of everything else.
-	So although $\varepsilon$ is still a state variable of $V$, it is no longer a state variable of $EV$. 
-	Then we can first solve $EV(x)$ by Bellman iteration.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item The inner fixed point loop is computationally burdensome.
-And the complexity will significantly grow if we add more state variables.
-\cite{Hotz:1993ea} uses an inversion function to avoid the Bellman iteration.
-\end{itemize}
-
-% subsection rust_87_emca (end)
-
-% section dynamic_decisions (end)
-
-\section{Hotz and Miller, 93 RES} % (fold)
-\label{sec:hotz_and_miller_93_res}
-
-\textbf{\bibentry{Hotz:1993ea}}
-
-\vspace{1em}
-\noindent
-\textbf{Highlights of the Paper:}
-\begin{itemize}
-	\item The main idea of this paper is to \textbf{ease the computation burden} of calculating the value function in \cite{Rust:1987hn}.
-	HM shows that value function can be represented in terms of choice probabilities, transition probabilities and expected per period payoffs. This hinges on the \textbf{
-	\textcolor{blue}{invertibility}} similar in BLP.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Model:}
-\begin{itemize}
-	\item The model uses a similar framework as \cite{Rust:1987hn}. The agent is solving a single agent dynamic programming problem, the choice set is from $1,\dots,J$.
-	Denote the history to be $H_t$, which is a collection of period outcomes $b_t\in \R$, where $b_t$ is affected by choice $d_t$. The history is generated according to the transition probabilities:
-	\[F_j(H_{t+1}|H_t)\]
-	\begin{itemize}
-		\item $H_t$ is the state variable here, corresponding to $x_t$ in Rust paper. The transition rule is exogenous conditional on decision.
-	\end{itemize}
-	In each period $t$, there is a current utility $u_{tj}$ associated with each choice $j$. Let $u^*_t(H_t)=E(u_{tj}|H_t)$.
-	\[u_{tj}=u^*_j(H_t)+\varepsilon_{tj}\]
-	\begin{itemize}
-		\item Notice that by construction $\varepsilon_t$ conditional on history $H_t$ is independent of other $\varepsilon_{t'}$.
-The \textit{conditional independence} assumption in \cite{Rust:1987hn} is implicitly assumed.
-	The state variable $x_t$ in Rust paper is included in $H_t$. Also, $\varepsilon_{tj}$ is known to the agent.
-	The distribution of $\varepsilon_t$ is $G(\varepsilon_t|H_t)$.
-	\end{itemize}
-	The agent chooses a sequence $\{d_t\}_t\in T$ to maximize summed discounted utility.
-
-	Denote $p_k(H_t)$ to be the probability of choosing action $k$ at history, and $p(H_t)$ be a $(J-1)$ vector of conditional choice probability function.
-
-	\item 
-	Due to the conditional independence condition, we can write the probability of choosing choice 1:
-	\begin{align*}
-	p_1(H_t)&=E(d_{t_1}=1|H_t) \\
-	&=\int_{\varepsilon_1=-\infty}^\infty \int_{\varepsilon_2=-\infty}^{\varepsilon_1+u^*_{11}-u^*_{12}+v_{t1}-v_{t2}}\dots \int_{\varepsilon_J=-\infty}^{\varepsilon_1+u^*_{11}-u^*_{1J}+v_{t1}-v_{tJ}} dG(\varepsilon_1,\dots,\varepsilon_J|H_t) \\
-	&= \int_{-\infty}^{\infty}G_1(\varepsilon_1,[\varepsilon_1+u^*_{11}-u^*_{12}+v_{t1}-v_{t2}],\dots,\varepsilon_1+u^*_{11}-u^*_{1J}+v_{t1}-v_{tJ}|H_t)d \varepsilon_1 \\
-	& \equiv Q_1(\tilde v,H_t)
-	\end{align*}
-	Similarly we can write $p_j(H_t)$ for each $j$.
-	Then if we denote $\tilde v = (v_{t1}-v_{tJ},\dots,v_{t,J-1}-v_{t,J}) \equiv \tilde v(H_t)$. 
-	We can write:
-	\[p(H_t)=Q(\tilde v(H_t),H_t)\]
-	\begin{itemize}
-		\item Notice that any $v_{t,j}-v(t,j')$ can be represented by two elements of $\tilde v$. $\tilde v$ just says that the scale of $v$ is unidentified.
-	\end{itemize}
-	The key idea of estimation is to express $\tilde v(H_t)$ as a function of $p(H_t)$. This requires $Q(\tilde v,H_t)$ being \textbf{invertible} in $\tilde v$ for every $H_t$.
-
-	\item KZ Guess: If $\tilde v$ can be expressed as function of $p(H_t)$, then we can use empirical $\hat p(H_t)$ to get empirical $\hat v$.
-If we further assume a functional form of $\varepsilon$ distribution to be F1EV, then we can get an estimated choice probability $\bar p$.
-Then we can use GMM to match $\hat p$ and $\bar p$.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Empirical Results:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Pros:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-% subsection hotz_and_miller (end)
-
-\section{Bajari-Benkard-Levin, 07 EMCA} % (fold)
-\label{sec:bajari_benkard_levin_07_emca}
-
-\textbf{\bibentry{Bajari:2007ky}}
-
-\vspace{1em}
-\noindent
-\textbf{Question of the Paper:}
-\begin{itemize}
-	\item This paper raises a two-stage algorithm for estimating dynamic games under the assumption of Markov Perfect Equilibria.
-	In first step, policy function and state variable transition rule are estimated.
-	In second step, remaining structural parameters are estimated.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{First Stage Estimation:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Second Stage Estimation:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Pros:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-% subsection bajari_benkard_levin_07_emca (end)
-
-\chapter{Asymmetric Information} % (fold)
-\label{cha:asymmetric_information}
-
-\section{Chiappori-Salanie, 00 JPE} % (fold)
-\label{sec:chiappori_salanie_00_jpe}
-
-\textbf{\bibentry{Chiappori:2000bu}}
-
-This is a first paper empirically testing \textit{asymmetric information}. The \textbf{\textcolor{blue}{pair probits methodology}} is important.\\
-
-\noindent
-\textbf{Identification:}
-\begin{itemize}
-	\item Suppose a pair probits system:
-	\[y_i = 1(X_i \beta +\varepsilon_i>0)\]
-	\[z_i = 1(X_i\gamma+ \eta_i>0)\]
-	where $y_i$ is the probability of choosing high coverage, and $z_i$ is the probability of accident.
-	If there is no asymmetric information, then we should have $\varepsilon_i$ and $\eta_i$ independent.
-	\textbf{
-	If there is positive correlation, indicates negative selection; if negative correlation, indicates advantageous selection.
-	}
-
-	\item We first estimate these two probits separately. Then it provides a way of testing independence.
-	\[W = \frac{\Big(\sum_{i=1}^n{\omega_i\hat \varepsilon_i \hat \eta_i}\Big)^2}
-	{\sum_{i=1}^n{\omega_i^2 \hat \varepsilon_i^2 \hat \eta_i^2}}\]
-	$W$ should follow a $\chi^2(1)$ distribution.
-	\footnote{This is why we use a probit system.} 
-	Where $\hat \varepsilon_i$ and $\hat \eta_i$ are generalized residuals.
-	\[\hat \varepsilon_i=
-	E(\varepsilon_i|y_i)=
-	\frac{\phi(X_i\beta)}{\Phi(X_i\beta)}y_i
-	-(1-y_i)\frac{\phi(X_i\beta)}{\Phi(-X_i\beta)}\]
-
-	\item We can modify the test to get estimation of correlation between $\varepsilon_i$ and $\eta_i$.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Empirical Results:}
-\begin{itemize}
-	\item Data: Car Insurance in France.
-	\item Conditioning on the subset of young drivers, no significant evidence for adverse selection.
-	\begin{itemize}
-		\item This paper strikes back Puelz and Snow (1994) in specific, which is criticized to suffer omitted observable variable problem.
-	\end{itemize}
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Pros:}
-\begin{itemize}
-	\item Data requirement is low. Only need the individual choice of coverage, and individual accident probability.
-	\begin{itemize}
-		\item Do not need premium information. Do not need exogenous price variation, which is needed in \cite*{Einav:2010hb}.
-	\end{itemize}
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item Cannot disentangle moral hazard, which may induce correlation as well.
-	\begin{itemize}
-		\item KZ: an ideal data will have $z_i$ data before and after the exogenous insurance coverage change. Then we can directly test moral hazard.
-	\end{itemize}
-	\item Only uses the coverage information, many other information about insurance (like premium, coinsurance rate) are not used.
-\end{itemize}
-
-% subsection chiappori_salanie_00_jpe (end)
-
-\section{Cardon-Hendel, 01 RAND} % (fold)
-\label{sec:cardon_hendel_01_rand}
-
-\textbf{\bibentry{Cardon:2001jf}}
-
-This paper sets up a two stage model to investigate the asymmetric information in health insurance market. The adverse selection mainly happens in the first stage.
-The do not find significant evidence for adverse selection.
-
-\vspace{1em}
-\noindent
-\textbf{Question of the Paper:}
-\begin{itemize}
-	\item Use a two-stage model to investigate the asymmetric information in health insurance market.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Model:}
-\begin{itemize}
-	\item Agent do a two stage model to decide consumption of health insurance in first stage, and health care consumption in second stage.
-
-	\item In second stage, given realized health state $s_i$ and  insurance policy $j$, each agent $i$ decides how much health care to consume:
-	\begin{gather*}
-	U_{ij}^*(s_i)=U^*(y_i,s_i,Z_j)=\max_{x_i}U(m_i,h_i)\\
-	s.t.\  m_i+C_j(x_i)=y_i-p_j
-	\end{gather*}
-	where $m_i$ is the consumption good and $h_i$ is the health consumption. $h_i=x_i+s_i$, i.e. health care and health state are perfect substitution.
-	$y_i$ is income, $p_j$ is premium of policy $j$, $C_j(x_i)$ is out of pocket money for consumption $x_i$ with policy $j$.
-
-	\item In first stage, the
-
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Empirical Results:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Pros:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-% subsection cardon_hendel_01_rand (end)
-
-\section{Einav-Finkelstein-Cullen, 10 QJE} % (fold)
-\label{sec:einav_finkelstein_cullen_10_qje}
-
-\textbf{\bibentry{Einav:2010hb}}
-
-\vspace{1em}
-\noindent
-\textbf{Main Contribution:}
-\begin{itemize}
-	\item Estimate the welfare loss caused by adverse selection with reduced form estimation. The key point for this approach is \textbf{exogenous price change}.
-	\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.4]{EFC_10qje_1.png}
-	\end{figure}
-
-	\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.4]{EFC_10qje_2.png}
-	\end{figure}
-
-	The adverse selection effect is totally represented by the downward sloping MC/AC curve. If it is advantageous selection, the MC/AC curve will be upward. 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Empirical Results:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Pros:}
-\begin{itemize}
-	\item This approach has very low demanding on data. Researchers only need \textit{exogenous price change} to get the MC and demand curve. Such change is easy to obtain in insurance industry.
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Cons:}
-\begin{itemize}
-	\item 
-\end{itemize}
-
-% subsection einav_finkelstein_cullen_10 (end)
-
-% section asymmetric_information (end)
-
-\chapter{Production Function Estimation} % (fold)
-\label{cha:production_function_estimation}
-
-There are several difficulties in estimating production functions which will cause endogeneity problem. To name some:
-\begin{itemize}
-	\item Simultaneity.
-For a production function like $y_{it}=\beta_0+\beta_1 k_{it}+\beta_2 l_{it} + \omega_{it}+\varepsilon_{it}$, we suppose that $\omega_{it}$ is obseved by firm but not by econometricians, and $\varepsilon_{it}$ is observed neither by firm nor econometricians.
-This could induce endogeneity when directly using OLS.
-	Suppose $\omega_{it}$ has \textit{positive serial correlation}, when $\omega_{it}$ is high, firm will choose higher input because it is very possible that $\omega$ in next period will be high as well.
-This induces a positive bias for $\beta_k$.
-	\item Exit selection bias. When constructing a balanced panel, then we only observe those firms with high $\omega_{it}$.
-	\textcolor{blue}{Why we have to construct a balanced panel?}
-\end{itemize}
-
-There are several approaches in solving this problem.
-
-\begin{itemize}
-	\item Classical Approach.
-	\begin{itemize}
-		\item Use input price as IV.
-The problem is input price is generally the same across firms.
-When we do observe different input prices, which generally indicates market power in input markets.
-Thus those facing higher $\omega_i$ will tend to produce more, inducing their input price to increase, which has a negative bias on $\beta_k$.
-		\begin{itemize}
-			\item (My comment) When using input price as IV, we actually assume they are independent of individual firm productivities.
-			This may not be the case.
-			If productivity has some correlation across the firms,
-			then it is possible that when productivity is high,
-			the input price in the market will also be high.
-		\end{itemize}
-		\item Use fixed effect. We need to assume that a firm faces same $\omega_{it}$ across time, which is not very practical.
-	\end{itemize}
-	\item Control Function for  $\omega_{it}$.
-This approach first raised by \cite{Olley:1996ef} and developed by \cite{Levinsohn:2003ej} and \cite*{Ackerberg:2015ha}.
-We name them OP, LP, ACF here after.
-The key idea is to use a function of what we know (for example, $k_t$ and $i_{t-1}$ in OP) to proxy $\omega$, the existence of such function is guaranteed by the solutioin property of the firm optimization problem.
-And the specific form of this function is estimated non-parametrically.
-	\begin{itemize}
-		\item OP uses a two step estimation process.
-First step, use $k_t$ and $i_{t}$ non-parametrically estimate $\omega_t$, plug this into original production function then use OLS.
-Notice the unobserved $\omega_t$ has been controlled by $k_t$ and $i_{t}$, then OLS will give consistent estimator for $l_t$ but not $k_t$.
-In second step, we first write $\omega_{it} = E[\omega_{it}|\omega_{it-1}]+\xi_{it}$, notice that $\xi_{it}$ is independent of any information set at t-1.
-Thus we get the moment condition $E[\xi_{it}k_{it}]=0$, then we can use method of simulating moments to estimate $\beta_k$.
-		\begin{itemize}
-			\item The key assumption in first step is, current period investment $i_t$ can be represented by a function of $f(k_t,\omega_t)$. 
-			If $f$ is invertible in $\omega_t$ (for example, $f$ being monotone in $\omega$), then we can write $\omega$ as a function of $(i_t, k_t)$.
-		\end{itemize}
-
-		\item LP is very similar to OP, just that use intermediate input $m_{it}$ instead of investment $i_{it}$ in proxy $\omega_{it}$.
-Because OP approach requires the policy function of $i_{it}$ be monotonicity in $\omega_{it}$, which is obviously unsatisfied when $i_{it}=0$.
-But data shows that in many observations $i=0$.
-Using intermediate input can solve this.
-
-		\item ACF criticizing is that $\beta_l$ cannot be identified in the first step.
-In LP we assume that $m_{it}=f_t(k_{it},\omega_{it})$.
-But we can reasonably argue by the same reason that $l_{it}=h_t(k_{it},\omega_{it})$.
-Then since $f(\cdot)$ is invertible, then we can write $l_t$ as some deterministic function of $k_{it}$ and $m_{it}$.
-This implies we cannot identify $\beta_l$ in the first step.
-The solution of ACF is to identify both $\beta_k$ and $\beta_l$ simultaneously at step 2, which is feasible since we now have two moment conditions.
-	\end{itemize}
-	\item \cite*{Gandhi:2017un} Approach (GNR).
-GNR criticizes control function approach is nonparametrically not identified in the presence of flexible inputs.
-They raise a new approach using FOC conditions.
-\end{itemize}
-
-% section production_function_estimation (end)
-
-\chapter{Multisided Platforms} % (fold)
-\label{cha:multisided_platforms}
-
-\textbf{\bibentry{Evans_Schmalensee:2012wp} }
-\begin{itemize}
-	\item Price structure matters. Reduce charge by one side and increase charge by another side will affect the transaction.
-	\item Transaction cost is necessarily high for multisided platform.
-	\item Two kind of externalities. Usage externality and membership externality.
-	\item Pricing is compelicated. Per-transaction fee, or membership-fee. \textcolor{blue}{This looks similar to conventional IO model.}
-	\begin{itemize}
-		\item In per-transaction fee case. Price is directly proportional to the elasticity, while in conventional models price is inversely related to elasticity.
-		\[\frac{p_1+p_2-c_1-c_2}{c_1+c_2}=\frac{1}{e_1+e_2}\]
-		\[\frac{p_1}{e_1}=\frac{p_2}{e_2}\]
-		Notice the second equation is unconventional.
-		\item In membership-fee case.
-		\item Both models can lead to a highly skewed price structure.
-	\end{itemize}
-	\item Competition Structure.
-	\begin{itemize}
-		\item Product differentiation
-		\item Multi-home.
-		\item Asymetric Competition.
-A n-sided platform may face competition from 1) one-sided firms; 2) a multisided platform competing in some but not all sides; 3) a multisided platform that has additional sides
-	\end{itemize}
-\end{itemize}
-
-\myline
-
-\textbf{Random Ideas}
-\begin{itemize}
-	\item Multisided platform as a commitment device changes the game structure.
-Like in the Truck-GasStation case raised in the book, the fleet-card company provides commitment power to the card companny, no renegotiation problem.
-\end{itemize}
-
-% section multisided_platforms (end)
-
-\chapter{Product Reviews} % (fold)
-\label{cha:product_reviews}
-
-\textbf{\bibentry{Berger:2010es}}
-
-\vspace{1em}
-\noindent
-\textbf{Question and Explanations:}
-\begin{itemize}
-	\item Why negative reviews may have positive effect on selling?
-
-	\item Negative review may increase awareness of the product.
-	\begin{itemize}
-		\item Theory prediction: negative reviews should have more negative effect for high awareness products than for low awareness products.
-	\end{itemize}
-
-	\item Cannot explain: why some established bad movies like \textit{Fu Chun Shan Ju Tu} still sell a lot.
-	\begin{itemize}
-		\item May because the different taste between reviewers and mass watchers.
-		\item As a social topic, just to be fashion.
-	\end{itemize}
-\end{itemize}
-
-% section product_reviews (end)
-
-\section{Gentzkov-Shapiro-Taddy, 17 WP} % (fold)
-\label{sec:gentzkov_shapiro_taddy_17_wp}
-
-\textbf{\bibentry{Gentzkow:2017hb}}
-
-\begin{itemize}
-	\item Methods for analyzing high-dimensional choices decisions
-	\begin{itemize}
-		\item also see \bibentry{Gentzkow_el.al:17WP}
-	\end{itemize}
-	\item Index for measuring polarization
-\end{itemize}
-
-This is a methodology paper introducing how to analyze high-dimensional choices decisions. They show that traditional logit model has severe finite sample bias.
-They also raise a index for measuring polarization.
-
-\textcolor{red}{[TO BE ADDED]}
-
-% section gentzkov_shapiro_taddy_17_wp (end)
-
-\chapter{Others} % (fold)
-\label{cha:others}
-
-\textbf{\bibentry{Einav:2010cd}}
-
-This survey paper provides a map for current empirical IO research, its range, and its relationship to theory.
-In addition, the ending part has a critique on the `reduced' view on IO (e.g. Angrist), worth reading.
-
-\subsection{Rey and Stiglitz, 1995, RAND} % (fold)
-\label{subsec:rey_and_stiglitz_1995_rand}
-
-\textbf{\bibentry{Rey:1995ft}}
-
-For detailed proof of this paper, see Evernote.\\
-
-\textbf{Main result:}
-vertical restrains can be used to reduce interband competition.
-Because exclusive territories alter the perceived demand curve, making each producer believe he faces a less elastic demand curve, inducing an increase in eqm price and producer's profits even in the abscence of franchise fee.
-This result is different from traditional Chicago school results, which insist that exclusive terittories will increase efficiency.
-This difference comes from market structure.
-Chicago schools investigate in full competition and full monopoly producer cases, while this paper looks at duopoly producer.
-In full competition and full monopoly case, the competition level has already been \textit{preassumed}, while exclusive territories can reduce the competition level among producers in other cases.\\
-
-The key for the result is the the following compound demand elastic:
-\[\tilde\varepsilon(p^e):=m_1(p,p)\varepsilon_1(q,q)+m_2(p,p)\varepsilon_2(q,q) \]
-where $q=q_1^r(p,p)$ (the response retail price),
-$m_1(p,p)=\partial \log q_1^r(p_1,p_2)/\partial \log p_1$ (the own elasticity of retail price to producer price),
-and  $m_2(p,p)=\partial \log q_1^r(p_1,p_2)/\partial \log p_2$ (the cross elasticity of retail price to producer price),
-and $\varepsilon_1(q_1,q_2)=-\partial \log D^1(q_1,q_2)/q_1$ (the own elasticity of demand to retail price, positive),
-and $\varepsilon_2(q_1,q_2)=-\partial \log D^1(q_1,q_2)/q_2$ (the cross elasticity of demand to retail price, negative).
-
-In the above equation, it is very reasonable to think $0<m_1<1$ and $0<m_2$.
-$m_1>0$ because the own elasticity of retail price to producer price is positive.
-$m_1<1$ means that retailer will absorb some increase in producers' price, which will be the case if demand elasticity becomes higher in high retail price.
-And $0<m_2$ derives from the two products to be substitutes.
-Under these two conditions, combined with $\varepsilon_1>0$ and $\varepsilon_2<0$, then $\tilde\varepsilon(p^e)<\varepsilon_1$.
-Thus, under exclusive territories, the producers' perceived demand curve is less elastic.
-So the equilibrium price (both retail and producer) is higher even when no franchise fee applies.
-
-\noindent
-\textbf{Setting:}
-
-\begin{itemize}
-	\item two manufacturers produce imperfect substitutes at same marginal cost \textit{c}
-	\item retailers are perfect competition / or exclusive territory
-	\item the final good demand depends on retail prices and is given by $D^i(q_1,q_2)$
-	\item costs and demand functions are common knowledge, retailers observe all contracts signed by each producer
-	\item producers only observer the quantity bought by retailers; they do not observe the quantities sold by retailers (i.e. fullline forcing is infeasible)
-	\item producers serve many markets at no addtional cost
-	\item consumers have no search cost
-\end{itemize}
-
-Under these settings and information conditions, we can see it as a two stave game.
-In the first stage, producers simultaneously set wholesale price $p_1$ and $p_2$.
-In the second stage, the retailer observe all wholesale price and decide the retail price simutaneously.
-
-\subsubsection{Benchmark Case} % (fold)
-\label{sub:benchmark}
-
-We use the following assumptions throughout the paper unless specified otherwise:
-
-\begin{enumerate}
-	\item Let $\pi(p_i,q_1,q_2) := (q_i-p_i)D^i(q_1,q_2)$ denote the retail profit for product i; assume it to be twice differentiable wrt each argument, and is sigle peaked wrt $q_i$.
-The reaction function $q_i^a(p_i,q_j)$ is thus continously differentiable and characterized by FOC.
-	\item Products are substitutes: $\partial D^i/\partial q_i \leq 0$ and $\partial D^i/\partial q_j \geq 0$
-	\item Demand functions are symmetric: $\forall p_1,p_2 \in \R_+, D^1(p_1,p_2) = D^2(p_2,p_1)$
-\end{enumerate}
-
-Think of the benckmark case that no vertical restriction so the retailers are perfect competitive, and the producer monopolizes.
-In this case, the game is just a one step optimal pricing problem.
-The producer chooses an optimal retail price.\\
-
-\begin{mdframed}[style=comment]
-
-\noindent
-\textbf{Useful trick:}
-
-Throughout this paper, we can write the symmetric eqm conditions in the following form:
-\[(p^c - c)/p^c=1/\varepsilon(p^c,p^c)\]
-where $p^c$ is the symmetric eqm price, and $\varepsilon$ is some kind of elasticity.
-
-In a symmetric eqm, the FOC of each producer gives 
-\((p^c - c)/p^c=1/\varepsilon_1(p^c,p^c)\)
-where $\varepsilon_1 = -\partial \log D^1(q_1,q_2)/\partial \log q_1$, i.e. the self elasticity of demand.
-
-In the simplest benchmark case, the two factories are integrated, leading us to:
-\((p^c - c)/p^c=1/E(q^m)\),
-$E(q):=\varepsilon_1(q,q)+\varepsilon_2(q,q)$, where $\varepsilon_2 = -\partial \log D^1(q_1,q_2)/\partial \log q_2$ (the cross demand elasticity).
-
-In the exclusive territory case, the symmetric eqm satisfies \((p^e - c)/p^e=1/\tilde\varepsilon(p^e)\), where 
-\[\tilde\varepsilon(p^e):=m_1(p,p)\varepsilon_1(q,q)+m_2(p,p)\varepsilon_2(q,q) \]
-where $q=q_1^r(p,p)$ (the response retail price),
-$m_1(p,p)=\partial \log q_1^r(p_1,p_2)/\partial \log p_1$ (the own elasticity of retail price to producer price),
-and  $m_2(p,p)=\partial \log q_1^r(p_1,p_2)/\partial \log p_2$ (the cross elasticity of retail price to producer price).
-
-\end{mdframed}
-
-% section others (end)
-
-\part{Trade and Spatial Economics} % (fold)
-\label{prt:trade_ _and_ _spatial_ _economics_}
-
-\chapter{Trade Basic Model} % (fold)
-\label{cha:trade_basic_model}
-
-\section{CES Functions} % (fold)
-\label{sec:ces_functions}
-
-\subsection{CES Utility (discrete)} % (fold)
-\label{sub:ces_utility_discrete}
-
-Reference: Rutherford (2002), Lecture Notes on Constant Elasticity Functions
-
-The CES utility function is defined as:
-\[U ( x , y ) = \left( \alpha x ^ { \rho } + ( 1 - \alpha ) y ^ { \rho } \right) ^ { 1 / \rho }\]
-We can calculate the demand:
-\[\begin{array} { c } { x \left( p _ { x } , p _ { y } , M \right) = \left( \frac { \alpha } { p _ { x } } \right) ^ { \sigma } \frac { M } { \alpha ^ { \sigma } p _ { x } ^ { 1 - \sigma } + ( 1 - \alpha ) ^ { \sigma } p _ { y } ^ { 1 - \sigma } } } \\ { y \left( p _ { x } , p _ { y } , M \right) = \left( \frac { 1 - \alpha } { p _ { y } } \right) ^ { \sigma } \frac { M } { \alpha ^ { \sigma } p _ { x } ^ { 1 - \sigma } + ( 1 - \alpha ) ^ { \sigma } p _ { y } ^ { 1 - \sigma } } } \end{array}\]
-and also the indirect utility:
-\[V \left( p _ { x } , p _ { y } , M \right) = M \left( \alpha ^ { \sigma } p _ { x } ^ { 1 - \sigma } + ( 1 - \alpha ) ^ { \sigma } p _ { y } ^ { 1 - \sigma } \right) ^ { \frac { 1 } { \sigma - 1 } }\]
-$V$ is homogeneous of degree 1 in M. This permits us to form an exact \textbf{price index} corresponding to the cost of a unit of utility:
-\begin{align*}
-	1 \equiv V(p_x,p_y,e(p_x,p_y,V=1)) = e(p_x,p_y,V=1)\left( \alpha ^ { \sigma } p _ { x } ^ { 1 - \sigma } + ( 1 - \alpha ) ^ { \sigma } p _ { y } ^ { 1 - \sigma } \right) ^ { \frac { 1 } { \sigma - 1 } } \\
-	\Rightarrow e(p_x,p_y) \equiv e(p_x,p_y,V=1) = 
-	\left( \alpha ^ { \sigma } p _ { x } ^ { 1 - \sigma } + ( 1 - \alpha ) ^ { \sigma } p _ { y } ^ { 1 - \sigma } \right) ^ { \frac { 1 } {1- \sigma } }
-\end{align*}
-The indirect utility can be reframed as:
-\[V(p_x,p_y,M) = \frac{M}{e(p_x,p_y)}\]
-Importantly, wlog, we can think of each consumer demand only one good, and $e(p_x,p_y)$ is the price index for that good.
-
-\mysubtitle{Elasticity:}
-
-CES get its name because the cross elasticity is a constant independent of consumption bundle. To see this we first use a more general form:
-\[U(\vec x) = \left[ \sum_{i=1}^n x_i^\rho \right]^{\frac{1}{\rho}}\]
-By brutal force calculation we get:
-\[\frac{\partial x_i/ x_i}{\partial p_j / p_j} = \frac{1}{1-\rho}\]
-% subsection ces_utility (end)
-
-\subsection{CES Utility (continuous)} % (fold)
-\label{sub:ces_utility_}
-
-CES can be generated to continuous version:
-\[\begin{aligned} \max U ( \mathbf { c } ) & = \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { 1 / \rho } \\ \text { s.t.
-} & \int _ { 0 } ^ { 1 } p ( i ) c ( i ) d i = I \end{aligned}\]
-Write the Lagranian and we have FOC:
-\begin{align*}
-	b(\iota)\rho c(\iota)^{\rho-1} \frac{1}{\rho} \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { (1-\rho) / \rho }
-	= \lambda p(\iota) \\
-	b(\iota)c(\iota)^{\rho-1} \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { (1 - \rho )/ \rho } 
-	= \lambda p(\iota),\ \forall \iota \in [0,1] \tag{2}
-\end{align*}
-Multiply both sides by $c(\iota)$ and take integration:
-\begin{align*}
-	\left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { ( 1 - \rho ) / \rho }
-	\left( \int _ { 0 } ^ { 1 } b ( \iota ) c ( \iota ) ^ { \rho } d \iota \right) 
-	= \lambda \int _ { 0 } ^ { 1 } p ( \iota ) c ( \iota ) d \iota = \lambda I\\
-	\left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { 1 / \rho } = \lambda I
-\end{align*}
-Define the LHS as $C$, the composite consumption, $P\equiv\lambda^{-1}$ and we will get:
-\[CP = I\]
-we call $P$ the \textbf{price index}, which has a natural interpretation to be the price of a unit util. 
-It should be noted that here $C$ is already the \textit{optimal} consumption bundle.
-
-We still need to solve $P$. Return to (2) and solve $c(\iota)$:
-\[
-c(\iota) = 
-\left[b(\iota)^{-1} \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { ( \rho -1) / \rho } \lambda p(\iota)
-\right]^{\frac{1}{\rho-1}}
-\]
-\begin{align*}
-	b(\iota)c(\iota)^{\rho} &= 
-b(\iota)\left[b(\iota)^{-1} \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { ( \rho -1) / \rho } \lambda p(\iota)
-\right]^{\frac{\rho}{\rho-1}}\\
-&= b(\iota)^{\frac{-1}{\rho-1}}\left(\lambda p(\iota)\right)^{\frac{\rho}{\rho-1}} \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i
-\end{align*}
-Taking integral in both sides:
-\begin{align*}
-	1 = 
-	\lambda^{\frac{\rho}{\rho-1}}
-	\int_0^1 b(\iota)^{\frac{-1}{\rho-1}} p(\iota)^{\frac{\rho}{\rho-1}} d \iota\\
-	P \equiv \lambda^{-1} = \left[\int_0^1 b(\iota)^{\frac{-1}{\rho-1}} p(\iota)^{\frac{\rho}{\rho-1}} d \iota\right]^{\frac{\rho-1}{\rho}}
-\end{align*}
-
-\mytitle{Properties}
-
-\mysubtitle{Cross Elasticity:}
-
-By equation (2), take the log form and take partial derivative, we get:
-\[
-\sigma  \equiv \frac{\partial c(x)/ c(x)}{\partial p(y)/p(y)} = \frac{1}{\rho-1}\]
-
-\mysubtitle{Own Elasticity:}
-
-Still from (2), we substitute $\lambda$ by $P^{-1}$. Then (2) can be written as:
-\begin{align*}
-	b(\iota)c(\iota)^{\rho-1}C^{1-\rho} = P^{-1}p(\iota)\\
-\end{align*}
-The trick is that a single product $c$ is so small that it will affect neither $C$ nor $P$. And thus the own elasticity is still $\frac{1}{\rho-1}$.
-
-\mysubtitle{Limiting Cases:}
-
-When $\rho \rightarrow 0$, Cobb-Douglas. When $\rho \rightarrow 1$, perfect substitution. When $\rho \rightarrow \infty$, Leontief.
-\blue{This is from Kim Ruhl's notes, I did not check.}
-
-\mysubtitle{Two Stage Budgeting:}
-
-Suppose there is some outside good $c_0$ in the economy:
-\[\begin{array} { c } { \max U \left( c _ { 0 } , \left( \int _ { 0 } ^ { 1 } b ( i ) c ( i ) ^ { \rho } d i \right) ^ { 1 / \rho } \right) } \\ { \text { s.t.
-} p _ { 0 } c _ { 0 } + \int _ { 0 } ^ { 1 } p ( i ) c ( i ) d i = I } \end{array}\]
-One thing important is that the differentiated goods can be aggregated into one commodity $C$. Then the above problem can be summarized as a two stage problem.
-\[\begin{array} { c } { \max U \left( c _ { 0 } , C \right) } \\ { \text { s.t. } p _ { 0 } c _ { 0 } + P C = I } \end{array}\]
-We first solve $C$ and $PC$. Then everything comes similar.
-% subsection ces_utility_ (end)
-
-% section ces_functions (end)
-
-\section{Ricardian Model} % (fold)
-\label{sec:ricardian_model}
-
-This representation is based on DFS 1977.
-
-\mytitle{Settings:}
-\begin{itemize}
-	\item Two countries: Home and Foreign
-	\item One factor of production
-	\begin{itemize}
-		\item This is important in Ricardian model, because the order of $z$ below relies on unique factor of production. Otherwise we won't have a meaningful order.
-		\item Denote $L, L^*$ as the labor endowments in two countries; and $w, w^*$ be the wages respectively. All terms are real.
-	\end{itemize}
-	\item A continuum of goods indexed by $z \in [0,1]$
-	\begin{itemize}
-		\item A continuum of $z$ is easier to deal with than discrete $z$.
-	\end{itemize}
-	\item Technology: $a(z)$ and $a^*(z)$ are the labor requirements for produing unit good.
-	\begin{itemize}
-		\item Order goods s.t. $A(z)\equiv \frac{a^*(z)}{a(z)}$ is decreasing. So Home has comparative advantage in low $z$.
-	\end{itemize}
-\end{itemize}
-
-\mytitle{Equilibrium:}
-\begin{itemize}
-	\item Suppose there is no trade cost. Let $p(z)$ denote the (home) price of good $z$ under free trade.
-	\item Since the competition is perfect, and there is no trade cost, the product will be produced in the country with lower labor cost:
-	\[\begin{aligned} p(z)-w a(z) & \leq 0, \text {w .
-equality if } z \text { is produced at Home }(1) \\ p(z)-w^{*} a^{*}(z) & \leq 0, \text { w.
-equality if } z \text { is produced Abroad }(2) \end{aligned}\]
-	\item A direct proposition is: there exists $\tilde z$ s.t. Home produces all goods $z<\tilde z$ and vice versa for Foreign.
-	Another result is: $A(\tilde z) = \frac{w}{w^*}\equiv \omega$. Note that $\omega$ is endogenous and can be calculated in equilibrium.
-	\item To calculate $\omega$, we further assume consumers have \textbf{identical Cobb Douglas} preference around the world.
-Then we denote $b(z)$ the share of expenditure on good $z$: (which actually should be understand as density of share):
-	\[
-	b(z)=\frac{p(z) c(z)}{w L}=\frac{p(z) c^{*}(z)}{w^{*} L^{*}}
- 	\]
- 	by def, shares should satisfy:
- 	\[\int_{0}^{1} b(z) d z=1\]
- 	Let $\theta(\widetilde{z}) \equiv \int_{0}^{\widetilde{z}} b(z) d z$ denote the fraction of income spent on goods produced at Home. Trade balance requires Home Exports = Home Imports:
- 	\[\theta(\widetilde{z}) w^{*} L^{*}=[1-\theta(\widetilde{z})] w L\]
- 	then we have relative wage to be:
- 	\[\omega=\frac{\theta(\widetilde{z})}{1-\theta(\widetilde{z})}\left(\frac{L^{*}}{L}\right) \equiv B(\widetilde{z})\]
- 	Notice this is an GE results. An technical advancement will increase $\tilde z$, which must be compensated by an increase in $\omega$ in equilibrium.
-\end{itemize}
-
-\mytitle{Comparative Statics:}
-\begin{itemize}
-	\item Below figure plots the equilibrium.$A(z)$ is downward by construction, $B(z)$ is upward by above equation.
-
-	\includegraphics[width=0.5\linewidth]{images/ricardian.png}
-	\item Suppose $L^*/L$ increases, how it will change equilibrium price and welfare?
-	\begin{itemize}
-		\item For notation ease, set $w=1$ wlog since it only serves as numerair.
-		\item First notice that $\omega$ increases and $\tilde z$ decreases in equilibrium.
-		\item For goods produced at Home, no change in $p(z)$ since it only depends on Home technology.
-		\item For goods whose production remains at Abroad:
-		\[\omega \nearrow \Rightarrow w^{*} \searrow \Rightarrow p(z)=w^{*} a^{*}(z) \searrow\]
-		\item For goods moved to be produced Abroad, then by profit optimization:
-		\[w^{*} a^{*}(z) \leq a(z) \Rightarrow p(z) \searrow\]
-		\item Thus Home gains.
-	\end{itemize}
-	\item KZ: The Abroad welfare decreases because of population increase.
-Why does this happen?
-Because Abroad now produces goods that they have less comparative advantages.
-They produce these goods because they have low wage, due to the competition effect of large population.
-
-\end{itemize}
-
-% section ricardian_model (end)
-
-\section{Eaton and Kortum, 02 EMCA} % (fold)
-\label{sec:eaton_and_kortum_02_emca}
-
-\mytitle{Setting:}
-\begin{itemize}
-	\item Efficiency: country $i$'s efficiency in product $j$ is $z_i(j)$
-	\item Input price in country $i$ is $c_i$, which can be further decomposed into labor cost and intermediate inputs cost
-	\item Geographic barriers between country $i$ and country $n$ is $d_{ni}$. \red{Is $d_{ni}$ symmetric?}
-	\item Production cost is:
-	\[p _ { n i } ( j ) = \left( \frac { c _ { i } } { z _ { i } ( j ) } \right) d _ { n i }\]
-	which is also the purchase cost by perfect competition assumption. However, the buyer will buy from the cheapest seller, and we assume the search is costless:
-	\[p _ { n } ( j ) = \min \left\{ p _ { n i } ( j ) ; i = 1 , \ldots , N \right\}\]
-	\item Utility: buyers have the love of variety, and we assume a CES utility form:
-	\[U = \left[ \int _ { 0 } ^ { 1 } Q ( j ) ^ { ( \sigma - 1 ) / \sigma } d j \right] ^ { \sigma / ( \sigma - 1 ) }\]
-	where the elasticity of substitution is $\sigma>0$.
-\end{itemize}
-
-\mysubtitle{Technology:}
-\begin{itemize}
-	\item The technology $z_i(j)$ is the realization of r.v. $Z_i$, drawn independently for each product $j$. $Z_i$ follows a Type II extreme value distribution:
-	\[F _ { i } ( z ) = e ^ { - T _ { i } z ^ { - \theta } }\]
-	$T_i$ governs the location of distribution, and $\theta$ common for all countries governs the variation \textit{within} the distribution. A bigger $\theta$ represents less variability.
-	\blue{This distribution is the key to the closed form solution.}
-\end{itemize}
-
-\mysubtitle{Prices:}
-\begin{itemize}
-	\item The induced price distribution is:
-	\begin{align*}
-		G _ { n i } ( p )
-		& = \Pr \left( P _ { n i } ( j ) \leq p \right) \\
-		& =  \Pr(\frac{c_i}{z_i(j)}d_{ni} \leq p) \\
-		& = 1-F_i(\frac{c_i d_{ni}}{p}) \\
-		& = 1 - e^{-T_i(c_i d_{ni})^{-\theta}p^{\theta}}
-	\end{align*}
-	The purchasing price distribution is thus: \red{how to derive?}
-	\begin{align*}
-		G _ { n } ( p ) & = 1 - \prod _ { i = 1 } ^ { N } \left[ 1 - G _ { n i } ( p ) \right] \\
-		& = 1 - e ^ { - \Phi _ { n } p ^ { \theta } }
-	\end{align*}
-	where $\Phi_n$ is:
-	\[\Phi _ { n } = \sum _ { i = 1 } ^ { N } T _ { i } \left( c _ { i } d _ { n i } \right) ^ { - \theta }\]
-
-	\item The probability that country $i$ provides a good at the lowest price in country $n$ is:
-	\begin{align*}
-	\pi _ { n i } &= \operatorname { Pr } \left[ P _ { n i } ( j ) \leq \min \left\{ P _ { n s } ( j ) ; s \neq i \right\} \right] \\
-	& = \int _ { 0 } ^ { \infty } \prod _ { s \neq i } ^ { \infty }  \left[ 1 - G _ { n s } ( p ) \right] d G _ { n i } ( p ) \\
-	&= \frac { T _ { i } \left( c _ { i } d _ { n i } \right) ^ { - \theta } } { \Phi _ { n } }
-	\end{align*}
-	\red{the last step?}
-
-	\item The price of a good that country $n$ \textit{actually buys} from country $i$ also has the distribution $G_n(p)$.
-This means that the price distribution \textit{conditional} on export country is the same as overall price distribution faced by importer country $n$.
-This result can be derived by showing that:
-	\[G _ { n } ( p ) = \frac { 1 } { \pi _ { n i } } \int _ { 0 } ^ { p } \prod _ { s \neq i } \left[ 1 - G _ { n s } ( q ) \right] d G _ { n i } ( q )\]
-
-	\item The price index for CES function is then \red{(why?)}
-	\[p _ { n } = \gamma \Phi _ { n } ^ { - 1 / \theta } \tag{9}\]
-	where 
-	\[\gamma = \left[ \Gamma \left( \frac { \theta + 1 - \sigma } { \theta } \right) \right] ^ { 1 / ( 1 - \sigma ) }\]
-	$\Gamma$ is the gamma function.
-
-\end{itemize}
-
-\mysubtitle{Trade Flows and Gravity}
-\begin{itemize}
-	\item Since the price distribution conditional on source is the same as overall price distribution, a corollary is that the average expenditure per good is identical across sources.
-Thus, the fraction of goods that country $n$ buys from country $i$, $\pi_{ni}$ is the fraction of expenditures:
-	\[\frac { X _ { n i } } { X _ { n } } = \pi_{ni} = \frac { T _ { i } \left( c _ { i } d _ { n i } \right) ^ { - \theta } } { \Phi _ { n } } = \frac { T _ { i } \left( c _ { i } d _ { n i } \right) ^ { - \theta } } { \sum _ { k = 1 } ^ { N } T _ { k } \left( c _ { k } d _ { n k } \right) ^ { - \theta } } \tag{10}\]
-	The exporter's total sales $Q_i$ are:
-	\[Q _ { i } = \sum _ { m = 1 } ^ { N } X _ { m i } = T _ { i } c _ { i } ^ { - \theta } \sum _ { m = 1 } ^ { N } \frac { d _ { m i } ^ { - \theta } X _ { m } } { \Phi _ { m } }\]
-	Then we can cancel out $T_i c_i^{-\theta}$:
-	\[T_i c_i^{-\theta} = 
-	\frac{X_{ni}\Phi_n d_{ni}^\theta}{X_n} = 
-	\frac{X_{ni}}{X_n} \left(\frac{p_n}{\gamma d_{ni}}\right)^{-\theta}\]
-	the second equation is from derived CES price index equation. Substitute $T_i c_i^{-\theta}$ into $Q_i$ and we get:
-	\[X _ { n i } = \frac { \left( \frac { d _ { n i } } { p _ { n } } \right) ^ { - \theta } X _ { n } } { \sum _ { m = 1 } ^ { N } \left( \frac { d _ { m i } } { p _ { m } } \right) ^ { - \theta } X _ { m } } Q _ { i } \tag{11}\]
-	\blue{Why we are interested in this equation?} Because it resembles the standard gravity equation.
-
-\end{itemize}
-
-\mytitle{Trade, Geography and Price: The Connection:}
-\begin{itemize}
-	\item Notice that if we divide (10) by $X_{ii}/X_i$, we get:
-	\[\frac { X _ { n i } / X _ { n } } { X _ { i i } / X _ { i } } = \frac { \Phi _ { i } } { \Phi _ { n } } d _ { n i } ^ { - \theta } = \left( \frac { p _ { i } d _ { n i } } { p _ { n } } \right) ^ { - \theta }\]
-	the LHS is called \textit{normalized import share}. \red{why we want to normalize it?}
-\end{itemize}
-
-\mytitle{Input Costs:}
-
-\mysubtitle{Production:}
-\begin{itemize}
-	\item The cost of an input bundle in country $i$ is:
-	\[c _ { i } = w _ { i } ^ { \beta } p _ { i } ^ { 1 - \beta }\]
-\end{itemize}
-
-% section eaton_and_kortum_02_emca (end)
-
-% chapter trade_basic_model (end)
-
-% part trade_ _and_ _spatial_ _economics_ (end)
-
-% chapter io (end)
-
-\part{Micro Theory} % (fold)
-\label{prt:micro_ _theory_}
-
-% part micro_ _theory_ (end)
-
-\chapter{Game Theory} % (fold)
-\label{cha:game_theory}
-
-\section{Important Tools} % (fold)
-\label{sec:important_tools}
-
-\begin{thm}[Revelation Principle, Myerson, 1981]
-Suppose that $\psi$ was a Bayes Nash equilibrium of the indirect mechanism $\Gamma$. 
-Then there exists a direct mechanism that is payoff-equivalent and where truthful revelation is an equilibrium.
-\end{thm}
-
-\begin{myproof}
-[to be added]
-\end{myproof}
-
-\begin{singlespacing}
-\noindent
-\textit{Comment:}
-\end{singlespacing}
-\begin{itemize}
-	\setlength{\itemsep}{0pt}
-	\item Revelation Principle is defined over some specific solution concept. Here it is Bayes Nash Eqm.
-	\item Revelation principle is not always satisfied. The stronger solution concept we use, the more likely it is not satisfied.
-\end{itemize}
-
-\subsection{Solution Concept} % (fold)
-\label{sec:solution_concept}
-
-A very good reference for different solution concept is \cite{vanDamme:1987}.
-\begin{itemize}
-	\item Nash eqm
-	\item Subgame Perfect eqm
-	\item Perfect eqm
-	\item $\varepsilon$-Perfect eqm
-	\item Proper eqm
-	\item Trembling-Hand eqm
-	\item Bayesian Nash eqm
-	\item (Weak) Perfect Bayesian eqm
-	\item Sequential eqm
-	\item Forward looking eqm
-	\item Self-Confirming eqm
-
-\end{itemize}
-
-\begin{defn}[Self-confirming Equilibrium, \cite{Fudenberg_Levine:93EMCAa}]
-Profile $\sigma$ is a \textit{self-confirming equilibrium} if for each player i, $s_i \in$ support($\sigma_i$) there exists belief $\mu_i$ such that:
-\begin{enumerate}
-	\item $s_i$ maximizes $u_i(\dot,\mu_i)$, and
-	\item $\mu_i[\{\pi_{-i}|\pi_j(h_j)=
-	\hat \pi_j(h_j|\sigma_j)\}]=1$, for all $j \neq i$ and $h_j \in \bar H(s_i,\sigma_-i)$, where $\bar H$ is the set of info sets that are reached with positive probability
-\end{enumerate}
-\end{defn}
-
-\begin{singlespacing}
-\noindent
-\textit{Comment:}
-\end{singlespacing}
-\begin{itemize}
-	\setlength{\itemsep}{0pt}
-	\item This definition mainly requires that the belief $\mu_i$ is consistent only at information sets that are reached with positive probability when player $i$ plays $s_i$.
-	\item This is most obvious when contrast with Nash Eqm, which is almost the same as this definition,
-	except for the consistency requirement is for all $h_j \in H_{-i}$. The consistency is required  for all information sets.
-	\item Self-confirming is a weaker solution concept than Nash Equilibrium. 
-	It uses the idea that players can only learn through what they observe.
-	For those outcomes that they cannot observe,
-	there is no particular reason for their beliefs to coincide.
-	Players can never learn something they lack information on.
-\end{itemize}
-
-\begin{exmp}
-
-\end{exmp}
-
-% subsection solution_concept (end)
-
-\section{Decision Theory} % (fold)
-\label{sec:decision_theory}
-
-\subsection{Morris, 95 Econ\&Phil} % (fold)
-\label{sub:morris_95_econ_phil}
-
-% subsection morris_95_econ&phil (end)
-
-\textbf{\bibentry{Morris:1995ic}}
-
-This assumption reviews the common prior assumption in economics, its common justifications, and its impact on game theory.
-
-\textcolor{blue}{VEEY WORTH READING!! NOTES TO BE ADDED.}
-
-% section decision_theory (end)
-
-\section{Mechanism Design} % (fold)
-\label{sec:mechanism_design}
-
-\noindent
-Important tools and topics in mechanism design:
-\begin{itemize}
-	\item Revelation Principle
-	\item Single dimension mechanism design
-	\begin{itemize}
-		\item Bayesian mechanism design
-		\item Dominant strategy mechanism design
-		\item Revenue equivalence
-		\item Payoff equivalence
-	\end{itemize}
-	\item Multidimensional mechanism design
-	\item Interdependent types mechanism design
-\end{itemize}
-
-\subsection{Revelation Principle} % (fold)
-\label{sub:revelation_principle}
-
-There are many things assumed in the proof of revelation principle. Take p.10 in Borger's book as example.
-
-\begin{itemize}
-	% \item Assume that in initial game, one can pretend to be someone else. That is, $\sigma(\theta')$ is in the action space of $\theta$.
-	\item No verification.
-	\item Utility is transferable.
-\end{itemize}
-
-For an example where all three assumptions are violated, see \cite*{BenPorath:2014bc}.
-
-\begin{mdframed}[style=comment]
-\noindent
-\textbf{Information side of Revelation Principle:}
-
-In setting we prove revelation principle, we assume every thing is common knowledge except for the specific type.
-These include the type space, the action space of each type, the utility form of each type, and so on. 
-We also assume that in the direct mechanism, the action space is the \textit{whole} type space for \textit{every} agents.
-\textcolor{red}{[Don't understand this. Since in the proof we only require that one can report truthfully.]}
-
-\end{mdframed}
-
-% subsection revelation_principle (end)
-
-% section mechanism_design (end)
-
-% section important_tools (end)
-
-\section{Learning Theory} % (fold)
-\label{sec:learning_theory}
-
-\subsection{Important tools in learning} % (fold)
-\label{sub:important_tools_in_learning}
-
-\begin{defn}[Monotone Likelihood Ratio Property]
-For all $l<S$,
-
-\[\frac{p_{q,l}}{p_{q+1,l}} \geq \frac{p_{q,l+1}}{p_{q+1,l+1}} \ for \ all \ q<R\]
-with strictly inequality for at least one q.
-
-\end{defn}
-
-This is first raised by \cite{Milgrom:1981dv}, which ensures that the conditional expectation of each individual increases in his signal realization.
-
-\begin{defn}[Martingale]
-A \textit{martingale} is a pair $(X_n,\F_N)$, where $\{\F_n\}$ is a filtration and $X_n$ an integrable (i.e. $E|X|<\infty$) stochastic process adapted to this filtration, such that 
-\[E[X_{n+1}|\mathcal{F}_n]=X_n,\ a.s. \ \forall n\]
-\end{defn}
-
-\noindent
-\textit{Comment:}
-\begin{itemize}
-	\setlength{\itemsep}{0pt}
-	\item Notice that Martingale process is much more restricted than Markov process, not only in the realization of expectation value. Markov process requires that 
-	\[Pr(X_{t+1}\in A)|X_t=x_0,X_{t-1}=x_{t-1},...,X_{t-k}=x_{t-k}
-	=Pr(X_{t+1}\in A)|X_t=x_0\]
-	for all $A \in \mathcal{X}$, all $x_0,x_1,...,x_k \in \mathbb{X}$, and all $0\leq k\leq t$. 
-	\begin{itemize}
-		\item This actually restricts all stochastic properties, including expectations, variations and others.
-		\item Also, Martingale process require conditional on $\F_t$, but Markov process only requires $x_t$.
-	\end{itemize}
-\end{itemize}
-
-\begin{thm}[Martingale Convergence Theorem]
-
-\end{thm}
-
-% subsection important_tools_in_learning (end)
-
-\subsection{Overview of literature} % (fold)
-\label{sub:overview_of_literature}
-
-% subsection overview_of_literature (end)
-
-\textcolor{red}{The equilibrium concept used in literature is Bayesian Nash Eqm.
-Thus we put no restriction on off-eqm path beliefs.
-Nageeb said something about this, but I don't understand why this is important.}
-
-\cite{Bikhchandani:1992fs} (BHW here after) is one of the original papers for learning in games.
-The main point is to explain the easily formulated but fragile information cascade when only actions are observed.
-The idea is, if only actions are observed, then after some threshold, private information will not affect action.
-And this private will NOT join the information pool, thus all following individual's private information will not contribute to the action.
-But since very little information is needed to form a cascade, this cascade can also be easily reversed when some shocks happen.
-
-\cite{Smith:2000tz} is a generalization of BHW paper. The generalization lies in these aspects:
-\begin{itemize}
-	\setlength{\itemsep}{0pt}
-	\item Heterogeneity in quality of information (possibly unbounded private information)
-	\item Heterogeneity of preference (noise by crazy types)
-	\item Information cascade is NOT a generic feature; but 'herding' is.
-	\item Necessary and sufficient condition for \textit{complete learning}.
-\end{itemize}
-This paper also provides a general approach on how to handle learning behaviour.
-% section learning_theory (end)
-
-\subsection{Bikhchandani-Hirshleifer-Welch, 92 JPE} % (fold)
-\label{subsec:bikhchandani_hirshleifer_welch_92_jpe}
-
-\textbf{\bibentry{Bikhchandani:1992fs}}
-
-BHW is the seminal paper of social learning, which explains imitating in social phenomena without any ad hoc assumptions. By ad hoc assumptions, I means following:
-\begin{itemize}
-	\setlength{\itemsep}{0pt}
-	\item sanctions on deviants
-	\item positive payoff externalities
-	\item conformity preference
-\end{itemize}
-This assumptions all have the unsatisfying property that puts the cart before the horse.
-
-\textcolor{red}{TO BE ADDED}
-
-% section bikhchandani_hirshleifer_welch_92_jpe (end)
-
-\subsection{Kremer-Mansour-Perry, 14 JPE} % (fold)
-\label{subsec:kremer_mansour_perry_14_jpe}
-
-\textbf{\bibentry{KMP:2014jpe}}
-
-Different from previous learning papers, KMP focuses on the optimal information disclosure of planner.
-They find that it is not always optimal for planner to disclose full information, because it will discourage agents' incentive to explore and exploration has positive externalities.
-
-Example: Online review website like TripAdvisor, Yelp; Google Map\\
-
-\noindent
-\textit{Illustrative example:}
-
-Say $R_1$ is uniformly distributed in $[-1,5]$, and $R_2$ is uniformly distributed in $[-5,-5]$.
-Then agent-1 for sure will choose $a_1$ since its ex-ante expeted payoff is higher.
-Planner cannot force agent-1 to choose $a_2$ because of IC condition.
-
-If realized $R_1$ is lower than 0, then for sure agent-2 will choose $a_2$.
-But planner can do better by recommending agnet-2 to play $a_2$ whenever $R_1 \leq 1$.
-Agent-2 will follow this suggestion because the $E[R_1]$ is 0 conditional on planner not disclosing.
-
-If unfortunately the realized $R_1$ is higher than 1, then there is no way to make agent-2 to choose $a_2$,
-but it is still possible to ask agent-3 to explore if $R_1$ is not too high.
-Because when player-3 is recommended to play $a_2$, she cannot distinguish between:
-1) planner knows both realization and $R_2>R_1$;
-or 2) planner wants her to explore.
-The second situation is in the same shoes as agent-2,
-but because of the possibility of the first situation,
-agent-3 will admit a higher upper threshold for exploring.\\
-$\hfill\square$
-
-\vspace{2mm}
-\noindent
-\textit{\textbf{Main Results:}}
-(The proof of this paper is not difficult, and worth learning)
-\begin{itemize}
-	\item The optimal policy is threshold policy. For each individual, there is an interval of realization $r_1$ such that he is the first agent to explore.
-	\item There is an upper bound of exploration time, which is independent of agents number $T$ and realization of $R_1,R_2$.
-	This indicates result will converge to first best when $T$ is large enough.
-\end{itemize}
-
-\vspace{2mm}
-\noindent
-\textit{\textbf{Comments:}}
-\begin{itemize}
-	\item Generalize action to $n$ will not affect the structure of optimal policy. While continuum of action will ask for new setting. See referee report for more.
-
-	\item We can also think the realization of $R_1$ and $R_2$ is \textbf{correlated}. 
-	The result of this paper will not hold in this case.
-	Think of the extreme case that correlation between $R_1$ and $R_2$ is $-1$.
-	Then for any $R_1>0$, the planner will never explore $a_2$. For any $R_1<0$, the planner will recommend $a_2$ for all agents except for first one, and they will accept this recommendation.
-	The correlation problem also exists when the relization of $R_i$ is not a value but a distribution, in the sense of correlation in mean value.
-In another direction, if the realization is positively correlated, then the exploration cost will be lower.
-And optimal policy should have lower upper threshold for each agent.
-	\vspace{1mm}
-
-	I think this extension important, because we have correlations in many real world applications.
-	Take TripAdvisor as an example. If we already have reviews on one Marriott hotel in Paris, then it's not very useful to explore another Marriott at Toulouse! 
-	Intuitively, planner should utilize such correlation, and put more weight on exploration of independent realizations.
-	The optimal policy could be interesting.
-
-	\item I also think of how this can be combined with optimal persuasion.
-	If planner and agents have discrepancy in interest, 
-	then persuasion is needed.
-\end{itemize}
-
-% section kremer_mansour_perry_14_jpe (end)
-
-\section{Hard Information} % (fold)
-\label{sec:hard_information}
-
-\noindent
-\textbf{Unraveling:}
-
-\textit{Unraveling} is first discussed by \cite{Grossman:1981ih} and \cite{Milgrom:1981dv}. 
-They show that if investor knows the type of firm's information, 
-such information is perfectly verifiable at no cost, and the disclosure of such information is at no cost.
-Then exist a sequential equilibrium, where the firm will disclose all information, good or bad.
-The intuition is, since investors know the type (distribution) of information firm has, the nondisclosure indicates a worst information.
-If the investor is so suspicious, firm will disclose those not so good information.
-
-\cite{Dye:1985a} finds that such unraveling may not always happen.
-There are many possible reasons, basically they are violations of above three assumptions.
-
-\cite{Quigley:2017us} discusses unraveling in existence of outside information. They show that such information beyond control of insiders will \textit{reverse} unraveling result.
-The highest quality insiders remain quiet, and only the mediocre insiders disclose information.
-Notice that sending message is costly in this model.
-The intuition for this result is,
-when type is high enough,
-outside information is enough to persuade the outsider.
-My guess is,
-this holds because the outsider decision is not fully divisible.
-
-\myline
-\noindent
-\textbf{Mechanism Design with Hard Information:}
-
-\cite{galzer_ruinstein:emca04} discusses the optimal decision rule when listener can check only one value.
-\textcolor{blue}{[Not yet read]}
-
-\cite{Green:1986gs} discusses the direct mechanism under partially verifiable information. 
-They show that the \textit{Nested Range Condition} is necessary and sufficient for all socially-implementable mechanisms to be truthfully-implementable mechanisms.
-The condition requires that if A can pretend to be B,
-B can pretend to be C, then A can pretend to be C.
-This condition is used in many other papers like \cite{Hart_et:17aer_evidence_games}, and monotonicity condition in \cite{Grossman:1981ih} is also included.
-But notice that their paper does not consider a explicit checking process, so the result cannot apply to \cite{BenPorath:2014bc}, where a perfect but costly checking technique exists.
-
-\subsection{Evidence Game} % (fold)
-\label{sub:evidence_game}
-
-\textcolor{blue}{[Below is based on the talk by Xiao]}
-The paper by \cite{Hart_et:17aer_evidence_games} provides a general framework for evidence games. It shows that under conditions:
-\begin{itemize}
-	\item A1. $\theta \in m(\theta) \subseteq \Theta$.
-	It basically restricts the message space to be the type space, and every can truthfully report his own type.
-	\item A2. If $\theta' \in m(\theta'')$ and $\theta \in m(\theta')$, then $\theta \in m(\theta'')$. It means the masquerade is transitive, which is quite restrictive condition.
-\end{itemize}
-With above two assumptions, and \textit{truth-leaning} refinement of equilibriums, they show that giving receiver commitment power will make him no strict better off.
-
-Many more basic models like \cite{Dye:1985a} and \cite{Milgrom:1981dv} can be encompassed by this framework. \textcolor{blue}{[Worth trying to put them in.]}
-
-% subsection evidence_game (end)
-
-\subsection{Beyer-Cohen-Lys-Walther, 10 JAcctE} % (fold)
-\label{sub:beyer_cohen_lys_Walther_10_jaccte}
-
-\textbf{\bibentry{Beyer:2010cj}}
-
-This paper surveys literature of \textbf{voluntary information disclosure}, which is highly correlated with \textit{hard information} literature we discuss in reading group.
-I mainly read the section 3 (voluntary disclosure) of this paper.
-
-We have unraveling result in \cite{Milgrom:1981dv} and \cite{Grossman:1981ih}. Unraveling means the agent will disclose all their private information. This result relies on the following conditions:
-\begin{enumerate}
-	\setlength{\itemsep}{0pt}
-	\item disclosures are costless;
-	\item investors know that firms DO have private info;
-	\item all investors interpret the firm's disclosure in the same way, and firms know how investors will interpret that disclosure;
-	\item agents want to maximize their firm's share prices (no moral hazard problem);
-	\item agents can credibly disclose their private info;
-	\item firms cannot commit ex-ante to a specific disclosure policy.
-\end{enumerate}
-
-Violation of any conditions will result in partial nondisclosure of private information.
-\begin{enumerate}
-	\setlength{\itemsep}{0pt}
-	\item \textit{Costly disclosure.} If disclosure is costly to a firm, then it will choose not to disclose even when signal is not that bad.
-	\item \textit{Probabilistic information endowment.} If firms get private information in probability, then they have incentive to not report some bad results.
-Because investors cannot distinguish them from those without private information.
-	\item \textit{Uncertain investor response.}
-	\item \textit{Uncertain disclosure incentives.} In this case, there will be moral hazard problem.
-	\item \textit{Non-verifiable disclosure.} There are many important models in this category.
-For example, Cheap Talk model and Costly State Verification models.
-In cheap talk, exists "babbling eqm" since signal can't be verified.
-In Costly State Verification, firms have some rent since it's not wise to investors to check at every case.
-	\item \textit{Ex-ante commitment}.
-\end{enumerate}
-
-% section beyer_cohen_lys_ (end)
-
-\subsection{Milgrom, 81 Bell} % (fold)
-\label{sub:milgrom_81_bell}
-
-\textbf{\bibentry{Milgrom:1981dv}}
-
-\cite{Milgrom:1981dv} introduces a way to measure how good a message is.
-The difficulty here is that we are comparing two conditional distributions, not two values, thus something similar to FOSD is needed.
-
-\begin{defn}
-A signal is \textit{more favorable than} another signal if the posterior belief $G(\cdot|x)$ FOSD $G(\cdot|y)$.
-\end{defn}
-
-\begin{prop}
-x is more faborable than y iff for every $\theta_1>\theta_2$,
-\begin{equation}
-\label{eq:milgrom81_2a}
-\frac{f(x|\theta_1)}{f(x|\theta_2)}>\frac{f(y|\theta_1)}{f(y|\theta_2)}
-\end{equation}
-\end{prop}
-
-Intuitively, x is more favorable iff x is more likely to appear when the state is high.
-
-\begin{defn}[Strict Monotone Likelihood Ratio Property]
-The family of densities $\{f(\cdot|\theta)\}$ have the monotone likelihood ratio property if for every $x>y$ ad $\theta_1>\theta_2$, \eqref{eq:milgrom81_2a} is satisfied.
-\end{defn}
-
-Densities with MLRP has the good property that any two signals are comparable.
-
-% subsection milgrom_81_bell (end)
-
-% section hard_information (end
-
-\section{Bayesian Persuasion} % (fold)
-\label{sec:bayesian_persuasion}
-
-The question that \textit{Information Design} wants to answer is corresponding to that of Mechanism Design.
-In mechanism design, the designer can commit to the \textit{rule} of a game; in information design, the designer (sender) commits to a information structure.
-
-\subsection{Kamenica and Gentzkow, 11 AER} % (fold)
-\label{sub:kamenica_and_gentzkow_11}
-
-% subsection kamenica_and_gentzkow_11 (end)
-
-\textbf{\bibentry{Kamenica:2011ih}}
-
-\begin{exmp}
-Suppose there is one prosecutor (Sender) and one judge (Receiver).
-Both parties hold the prior that the suspect is guilty with $\rho=0.3$.
-The prosecutor decides whether to investigate the suspect. 
-After that the judge will see investigation report, which cannot be manipulated by the prosecutor, and then make the decision of acquit or convict.
-The prosecutor knows the world state (innocent or guilty), but he only wants to increase the probability of convict.
-The judge wants to matching state.
-What is the best thing the prosecutor can do?
-
-If the prosecutor does nothing, then the judge will action according to his prior, and \textit{acquit} the suspect with probability 1 since $\rho<0.5$.
-
-But the prosecutor can do much better than this.
-Suppose the prosecutor commits to following investigation:
-\[\pi(i|innocent)=4/7, \ \pi(g|innocent)=3/7\]
-\[\pi(i|guilty)=0, \ \pi(g|guilty)=1\]
-
-Thus when the judge see signal \textit{i}, he does Bayesian inference and gets:
-\(Pr(guilty|i)=0\)
-and 
-\(Pr(guilty|g)=\frac{1*0.3}
-{1*0.3+3/7*0.7}=0.5\).
-If the equilibrium is in favor of the prosecutor, the judge will choose \textit{convict} with probability 1 when seeing signal \textit{g}.
-\footnote{This specific tie breaking rule is not important since we can always add $\varepsilon$ to 0.5.}
-Then the total probability of \textit{convict} becomes 0.6.
-\end{exmp}
-
-\noindent
-\textit{Comment to Example:}
-\begin{itemize}
-	\item The sender actually commits to the \textit{precision} of investigation. The point is that he cannot change the result \textit{ex post}.
-
-	\item The judge will behave the same whether he believes the guilty probability is 0 or 0.49.
-So the information revelation scheme will make the belief of guilty under signal $i$ to be as low as possible, and make the belief under $g$ slightly over 0.5.
-\end{itemize}
-
-\subsection{Gentzkow and Kamenica, 17 RES} % (fold)
-\label{sub:gentzkow_and_kamenica_17_res}
-
-\textbf{\bibentry{Gentzkow:2017ff}}
-
-\vspace{1em}
-\noindent
-\textbf{Highlight of the Paper:}
-\begin{itemize}
-	\item This paper shows that the competition does not increase the amount of information being revealed in general.
-A key condition for competition to be beneficial is \textbf{Blackwell-connectedness}.
-
-	\item There are other papers answering this question.
-For example, the cheap talk games and the hard evidence game.
-But this paper is different because those papers take senders' information as given, and focus on the strategic communications subject to incentive compatibility.
-	This paper abstracts from the incentive problem by giving senders commitment and takes the senders' information structure as endogenous.
-
-\end{itemize}
-
-% subsection gentzkow_and_kamenica_16_res (end)
-
-% section bayesian_persuasion (end)
-
-\section{Repeated Game} % (fold)
-\label{sec:repeated_game}
-
-This section highly depends on Nageeb's notes and Mailath-Samuelson book.
-
-\subsection{Imperfect Monitoring} % (fold)
-\label{sub:imperfect_monitoring}
-
-\begin{itemize}
-	\item \href{run:resources/repeated_game/imperfect_monitoring_najeeb.pdf}{Nageeb's notes}
-\end{itemize}
-
-Motivation for imperfect monitoring:
-\begin{itemize}
-	\item In practice, monitoring is often imperfect (\cite{Green_Porter:1984EMCA})
-	\item \textcolor{blue}{NOT UNDERSTAND.} Helps to understand punishments at off-path histories
-\end{itemize}
-
-With imperfect monitoring, `forgiveness' will often make the equilibrium better while keeping IC satisfied.
-
-The difficulty in describing imperfect monitoring game with automata is, we can only observe ex-post history, 
-how can we use automata graph to describe this ex-post history?
-The answer is we can think the equilibrium (and strategy) ex-ante. 
-Because everything is linear, so it actually does not really matter what ex post realization is.
-
-% subsection imperfect_monitoring (end)
-
-\subsection{Miscellanea} % (fold)
-\label{sub:miscellanea}
-
-\textbf{\bibentry{Hadfield:2012kc}}
-
-This paper asks an interesting question: what is the difference between law and social norm?
-And they argue that the key feature of law of `central judgment', while the punishment can be decentralized.
-
-Such a model wants to answer: what's the incentive for individuals to conduct punishment despite that such punishment is costly?
-Their model is weird.
-
-\textit{KZ: Intuitively this is like private monitoring.}
-
-% subsection miscellanea (end)
-
-% section repeated_game (end)
-
-\section{Financial Economics} % (fold)
-\label{sec:financial_economics}
-
-\noindent
-\textbf{Bid-Ask Spread:}
-
-\cite{oHara} Chapter-3 provides two explanations on existence of bid-ask spread, even with market makers being risk neutral and competitive.
-Both model based on asymmetrically informed investors.
-
-\vspace{1em}
-\cite{copeland1983information} uses a one-stage game with asymmetric informed investors.
-The informed investors have full information, 
-while the uninformed investors have no information except for common prior.
-The market maker will lose money when transact with informed with informed investors, and earn money when transacting with uninformed ones.
-The bid ask spread is to make market makers balance off.
-
-Several things are unspecified in their model.
-First, the motivation of uninformed participants are unspecified. Why they will enter the market knowing that they will lose money in expectation?
-Secondly, the information conveyed by trade action is not specified.
-A sell order may represent a bad news of informed investor and vice versa.
-
-\vspace{1em}
-\cite{glosten_milgrom:1985bid} addresses the second concern by studying a sequential trade structure.
-Market makers will learn in Bayesian to update his belief about the world state. 
-And the buy/sell order conveys different information about the world state since the existence informed investors.
-So when the investor wants to sell a stock, market maker will have a more gloomy prediction about world state, and thus decrease the price; vice versa.
-
-Glosten-Milgrom model explains the bid-ask spread in abscence of any exogenous transaction or inventory cost.
-In addition, they show that the price is a Martingale (for market maker).
-Their model also suggests that market may collapse if there are too many informed investors, since the spread in positively correlated with portion of informed investors.
-
-KZ: But in their model, investors will not use the information of previous transactions, which is unsatisfactory.
-We can think in social learning approach.
-If that is the case, then transaction conveys no additional information if investors are in a herd.
-
-% section financial_economics (end)
-
-\section{Seminar Notes} % (fold)
-\label{sec:seminar_notes}
-
-\noindent
-\textbf{George Mailath (WP 17): “The Wisdom of The Confused Crowd: Model-Based Inference”}\\
-
-\noindent
-\textbf{Main idea:}
-\begin{itemize}
-	\item If players are non-Bayesian, how do they update?
-	How they exchange information in the information mkt?
-	\item Agents do `model-based' inference.
-	Basically this is a two step structure.
-	\item Agents have a model which addresses on some dimension of the information,
-	and when they receive an information, 
-	they will only first focuses on the dimensions that their model addresses.
-	\item Then they exchange the posterior belief with other agents.
-	Since other agents have different model addressing different aspects,
-	their posterior belief reveals some information of other dimension signal.
-	\item Since the signals in different dimensions are correlated,
-	one agent may use other's posterior belief to infer partial information of signals in the dimensions that he is interested in.
-	\item Thus, although they have different models addressing different dimensions,
-	they can still exchange in the info market.
-\end{itemize}
-
-\myline
-
-\noindent
-\textbf{Simon Board, Moritz Meyer-ter-Vehn (WP 17): An Inspection Model of Learning in Networks}\\
-
-\noindent
-Main idea: 
-\begin{itemize}
-	\item \href{run:resources/learning/Talk_note_Learning in network.pdf}{Note of Talk}
-	\item Two concerns in network learning
-	\begin{itemize}
-		\item I get awake at a constant rate, and may want to try
-		\item I see my neighbor trying, and want to try
-	\end{itemize}
-	\item Learning in small network is very difficult to numerically computing.
-	\begin{itemize}
-		\item Self-reinforcement structure
-		\item Triangle correlation
-		\item $\Rightarrow$ can characterize, but cannot compute
-	\end{itemize}
-	\item In large random network, such concern disappears
-	\begin{itemize}
-		\item Because in large random network, the prob of each two points are connected is the same.
-		And with large enough network, the prob of a small local structure is second order small. 
-		\item Can write the graph as a tree in this case
-	\end{itemize}
-	\item (?) Learning rate increases exponentially with the number of neighbors.
-\end{itemize}
-
-\vspace{3mm}
-\hrule
-\vspace{3mm}
-
-\noindent
-\textbf{\bibentry{deb_kitamura_quah_stoye:2017wp}}
-
-\textcolor{blue}{Important paper, worth reading.}
-
-This paper raises a new representation theorem over preference and utility. 
-Traditionally we use preferences over consumption bundles $x$, 
-and Afriat theorem guarantees a well-behaving utility representation if GARP is satisfied for preference.
-This paper raises a representation theorem for preference over price bundles.
-
-More specifically, GARP says if we have $p^{t'}\cdot x^t<p^{t'}\cdot x^{t'}$,
-then we conclude $x^{t'}$ is revealed preferred to $x^t$, because $x^t$ is affordable when the consumer choose $x^{t'}$.
-To test this approach, econometricians have to observe the consumption bundles of \textit{all} goods, which is infeasible in many cases.
-
-This paper raises another way to view data.
-\begin{itemize}
-	\item If $p^{t'}\cdot x^t < p^t \cdot x^t$, then we say $p^{t'}$ is revealed preferred to $p^t$.
-	Because the consumer has money left for other goods when price is $p^{t'}$. 
-	In this way, we can construct the preference over prices.
-	\item This paper raises GAAP corresponding to GARP,
-	and augmented utility function (seems integrating expenditure directly in the utility) w.r.t. GAAP.
-	\item This representation can be empirically tested without observing all goods being purchased.
-	And solves the endogenous expenditure level problem,
-	which McFadden-Richter estimation approach assumes.
-	\item Ron points out that this representation model cannot account for budget change.
-\end{itemize}
-
-\myline
-
-\noindent
-\textbf{Yuval Salant (18 WP): Statistical Inference in Games}
-
-\begin{itemize}
-	\item Idea: the agents in the game only use a sample of all agents, and based on the decision of the sample, the agent forms an inference. Then makes his own decision based on this inference.
-
-	\item The trade-off the agent is making is: enlarging sampling size is costly, but a larger sampling size will induce more precise distribution, which is beneficial since agents are risk averse.
-
-	\item They proposes a \textit{Generalized Sampling Equilibrium} based on above idea. And they show that this equilibria is always smaller than Nash.
-
-	\item The difficulty in defining this equilibrium is that everyone draws a different sample, and how to define equilibrium in this case?
-The trick here is they use a continuum of agents, so that even though everyone draws differently, but as a population they draw a same ``distribution''.
-The difference among agents are just changing labels.
-
-	\item Applications:
-	\begin{itemize}
-		\item In defining equilibria with search behavior.
-
-		\item Wei stated that this concept can be used widely in macro. For example, the shock in TFP will induce an endogenous fluctuation in sampling size; so the total variation is enlarged.
-	\end{itemize}
-\end{itemize}
-
-\myline
-
-\noindent
-\textbf{Cooperation Game:}
-
-Nageeb mentions in class that one reason for cooperation game to be unpopular is the difficulty in treating informations.
-How to treat to coalition when someone has information while others don't?
-
-\myline
-
-\noindent
-\textbf{\bibentry{Fainmesser:2018ju}}
-
-This paper discusses how how
-
-% section seminar_notes (end)
-
-% chapter game_theory (end)
-
-% \chapter{Decision Theory} % (fold)
-% \label{cha:decision_theory}
-
-% \section{Dekel and Lipman, 2010, Annu Rev Econ} % (fold)
-% \label{sec:dekel_and_lipman_2010_annu_rev_econ}
-
-% \textbf{\bibentry{Dekel:2010bm}}\\
-
-% \noindent
-% \textbf{What we can learn from decision theory}
-
-% 1) to know whether our intuition is correct;
-% 2) to flesh out initial intuition to get additional or better prediction (e.g. some additional observable prediction);
-% 3) to help us understand of why and how mechanism works
-
-% \noindent
-% \textbf{Story of the model}
-
-% Why the story of the model is important even if it is not realistic? Why we can't just choose the model by the 'prediction-rejection' procedure?
-
-% 1) The story makes us believe the predictions more;
-% 2) Having a nice intuition helps us to utilize the model and to expand the model;
-% 3) And a model can never be realistic, the important thing is whether it captures something important.
-
-% section dekel_and_lipman_2010_annu_rev_econ (end)
-
-% chapter decision_theory (end)
-
-\chapter{Matching Theory} % (fold)
-\label{cha:matching_theory}
-
-\section{Gale and Shapley, 1962, Ame.Math.Mon.} % (fold)
-\label{sec:gale_and_shapley_1962}
-
-\textbf{\bibentry{Gale:1962kl}}
-
-This paper introduces Deferred Acceptance (DA) algorithms in matching, and shows that it is stable and optimal.
-
-\begin{defn}
-An assignment is called \textbf{unstable} if there are two applicants $\alpha$ and $\beta$ who are assigned to universities A and B, although $\beta$ prefers A to B and A prefers $\beta$ to $\alpha$.
-\end{defn}
-
-\begin{defn}
-A stable assignment is called \textbf{optimal} if \textit{every} applicant is at least as well off under it as under any other stable assignments.
-\end{defn}
-
-Comment: it looks at first that optimal assignments may not always exist. But as we will show constructively, it does.
-
-\begin{defn}
-\textbf{Deferred Acceptance algorithm} works as following.
-First let each boy propose to his favorite girl.
-Each girl who receives more than one proposal rejects all but her favorite boy.
-Yet, she doesn't accept him, but keeps him in a string to allow for the better may come later.
-Then in the second round, each rejected boy propose their second favorite girl, and each girl picks her favorite among the new proposers and the one in the string, and put him in her string.
-This process continues, until each girl has one boy in the string (this will happen after finite rounds), then each girl picks the boy in her string.
-\end{defn}
-
-We will show the assignment by above algorithm is stable and optimal.
-
-% section gale_and_shapley_1962 (end)
-
-% chapter matching_theory (end)
-
-\part{Macro} % (fold)
-\label{cha:chapter_name}
-
-\chapter{Bubbles} % (fold)
-\label{ch:bubbles}
-
-\section{Milgrom and Stokey, 82 JET} % (fold)
-\label{sec:milgrom_and_stokey_82_jet}
-
-\textbf{\bibentry{Milgrom:1982fv}}
-
-\begin{thm}[No Trade Thm]
-Suppose that all 1) traders are risk averse; 2) initial allocation $e=(e_1,...,e_n)$ is Pareto optimal relative to $\theta$-trades; 3) agents' prior beliefs are concordant; 4) each trader observes private information conveyed by the partition $\hat P_i$.
-If it is common knowledge at some world state $\omega$ that $t$ is a feasible $\theta$-trade and each trader weakly prefers $t$ to the zero trade, then every agent is indifferent between the two.
-If all agents are strictly risk averse, then $t$ is zero trade.
-\end{thm}
-
-\noindent
-\textit{Comment:}
-\begin{itemize}
-	\item This being called \textit{no trade theorem} because private information will not lead to trade, which is on the contrary to what static models predicts.
-
-	\item Intuitively, if some other wants to trade with me, then he must possess some private information that in favor of this trade.
-But if we have same concordant prior belief, such information must \textit{in against with} my trading with him.
-So I will not accept any trade being offered to me.
-By the same argument, others will not accept any offer being offered to them.
-
-	\item World state space is: $\Omega=\Theta \times X$. $\Theta$ is set of payoff-related events, which will affect endowment and utility (type), $X$ will not affect endowment and taste directly.
-	A trade is a function from $\Omega$ to $R^{ln}$, it is $\theta$-trade if it only depends on $\theta$.
-
-	\item Beliefs are \textit{concordant} if:
-	\[p_1(x|\theta)=...=p_n(x|\theta),\ \forall x,\theta\]
-\end{itemize}
-
-% subsection milgrom_and_stokey_82_jet (end)
-
-\section{Geanakoplos and Polemarchakis, 82 JET} % (fold)
-\label{sec:geanakoplos_and_polemarchakis}
-
-\textbf{\bibentry{Geanakoplos:1982fl}}
-
-\vspace{1em}
-\noindent
-\textbf{Main result:}
-\begin{itemize}
-	\item \textbf{Theorem: }With common priors, and if the information partitions of two agents are finite, then they can converge to a common equilibrium posterior by communicating \textit{only posterior}.
-And the communication steps are finite.
-
-	\item This result is more general than Aumann's, because it does not require the event A to be posterior common knowledge. Actually it does not put any restriction on event A.
-
-	\item Such converging posterior may NOT be the same as the one they will reach if they direct communicate.
-
-	\item Such convergence may NOT happen in \textit{each} step. It is possible that the posterior of both agents do not change until the last step. E.g. the blue/red eye island.
-\end{itemize}
-
-\begin{exmp}
-
-\end{exmp}
-
-% subsection geanakoplos_and_polemarchakis (end)
-
-\section{Morris, 94 EMCA} % (fold)
-\label{sec:morris_94_emca}
-
-\textbf{\bibentry{Morris:1994id}}
-
-This paper is an extension of \cite{Milgrom:1982fv}, which relaxes the concordant belief in MS-1982 paper and find the no-trade theorems under different \textit{trading rules} and \textit{belief structures}.
-
-The generalization is listed in \href{run:resources/Berk_bubbles_pres_feb20.pdf}{Berk's notes}:
-
-\begin{table}[h]
-\centering
-\begin{tabular}{cccc}
-\hline
-C \textbackslash\  T & \cellcolor[HTML]{C0C0C0}Ex-Ante & \cellcolor[HTML]{C0C0C0}Interim & \cellcolor[HTML]{C0C0C0}Ex-Post \\ \hline
-\cellcolor[HTML]{C0C0C0}Uncons. & condordant & consistent conc. & revelation cons. con. \\
-\cellcolor[HTML]{C0C0C0}IC & noisy conc. & {\color[HTML]{3166FF} noisy cons. conc.} & - \\
-\cellcolor[HTML]{C0C0C0}Public & public conc. & public cons. conc. & {\color[HTML]{FE0000} public rev. cons. conc.}
-\end{tabular}
-\end{table}
-
-The read of this table is: ``An initially efficient allocation is T C efficient \textit{iff} beliefs are (C,T).''
-
-\begin{itemize}
-	\item Noisy concordant and public concordant are weaker than concordant. If beliefs are concordant, then they are noisy concordant.
-\end{itemize}
-
-% subsection morris_94_emca (end)
-
-% section bubbles (end)
-
-\section{Kiyotaki, 2011} % (fold)
-\label{sec:kiyotaki_2011}
-
-\textbf{\bibentry{Kiyotaki:2011fc}}
-
-This paper mainly discusses the micro structures which may induce financial friction (inefficiency).
-These structures include private information of income, private technology for storage, limited commitment and their combinations.
-
-% section kiyotaki_2011 (end)
-
-\chapter{Costly State Verification} % (fold)
-\label{cha:costly_state_verification}
-
-Financial frictions is an important yet not well explained phenomena.
-Generally financial frictions means some possible financial frictions not happening, resulting in fluctuations in real economy.
-There are several micro foundations for financial frictions, we learned some in Ruilin's course:
-\begin{itemize}
-	\item costly state verification
-	\item collateral constraints
-	\item moral hazard
-	\item asymmetric information
-\end{itemize}
-
-The main framework for costly state verification is following.
-The borrower has some private information on productivity, and lender has to pay some cost to get this information.
-This will give the borrower some advantage, and make some possible transactions unable to happen.
-\cite{Townsend:1979ef} gives a micro model describing contract under costly state verification.
-\cite{BenBernanke:1989eg} and \cite{Carlstrom:1997fb} are two important works using this to explain business cycles (also called Financial Accelerator).
-
-\textcolor{red}{Add brief introduction for costly state verification literature.}
-
-\section{Townsend, 79 JET} % (fold)
-\label{sec:townsend_79_jet}
-
-\textcolor{red}{seminal paper in costly state verification, important, to be added.}
-
-% section townsend_79_jet (end)
-
-% section costly_state_verification (end)
-
-\section{Kiyotaki-Moore, 97 JPE} % (fold)
-\label{Kiyotaki_Moore_97_jpe}
-
-\textbf{\bibentry{Kiyotaki:1997hl}}
-
-Another explanation for financial friction is collateral constraint. Important literatures include \cite{Kiyotaki:1997hl},
-
-\cite{Kiyotaki:1997hl} has a simple idea.
-Suppose the borrower needs some collateral (say land) for borrowing.
-What is the effect of a temporary increase in land productivity?
-The direct effect is it will increase this period land price.
-More important is the indirect effect, the borrower now can buy more land since their collateral becomes more valuable.
-And thus in next period they can buy even more land.
-This long chain has a large effect on the initial price of the land.
-Thus financial sector can amplify the fluctuation of real economy.
-
-\includegraphics[width=\textwidth]{kiyotaki-moore-97.png}
-
-\noindent
-\textbf{Skills:}
-\begin{itemize}
-	\item How they deal with specific-targeted loan (i.e. the loan can only be used to purchase land)
-\end{itemize}
-
-% section collateral_constraints (end)
-
-\section{Gorton and Ordonez, 14 AER} % (fold)
-\label{sec:gorton_and_ordonez_14}
-
-\textbf{\bibentry{10.1257/aer.104.2.343}}\\
-
-\textbf{Motivation}: How a small shock can sometimes have a very huge, sudden effect, while at other times the effect of the same size shock is small or nonexistent.
-Leverage per se is not enough to explain this.
-This paper explains how credit booms arise, leading to financial fragility where a small shock can lead to huge consequences.
-Thus, "tail risk" is endogenous.
-The same reason causes boom and huge recession, and the degree of recession is positively correlated with the boom lasting time.
-
-\textbf{Mechanism}:
-
-\begin{enumerate}
-	\item Firm needs land as collateral to borrow money from households.
-Land is either good or bad.
-Neither firm nor household know the quality of land, and checking fee is $\gamma>0$.
-It can be shown that, when the probability of a land to be good is too high or too low, it will be optimal (for both firm and household) to not check the quality.
-	\item Then suppose there are idiosyncratic shocks to land.
-For each land in each period, there is $\lambda$ prob to be unchanged, and $1-\lambda$ to be changed.
-In case of changing, $\hat p$ prob becoming good and $1-\hat p$ becoming bad, independent of initial type.
-So we can take it as a $\hat p$ type, it will become either 0 or 1 after checking.
-If $\hat p$ lies in some range that no checking is appropriate, then uncertainty in the economy will accumulate.
-Notice such accumulation will lead to a boom.
-	\item Now think of an aggregate shock.
-All good type and $\hat p$ type have weaker beliefs after such shock, changing to $\eta$ and $\eta \hat p$ respectively.
-Notice that $\eta$ and $\eta \hat p$ may have very different effect.
-It may be optimal to not check with $\eta$ but optimal to check with $\eta \hat p$.
-Thus if an economy has accumulated a large portion of $\hat p$, i.e.
-a long boom, then many of them will choose to check, inducing a huge crisis.
-	\item Notice that it is not because of any \textit{intrisinc} change in economy.
-The $\hat p$ will change the real portion of good land in the economy only once.
-What really matters is that once the bad one becomes $\hat p$, then even it switches back to bad in following periods, it will still be taken as $\hat p$.
-That means, the $\hat p$ type will accumulate in the economy.
-\end{enumerate}
-
-\textcolor{red}{Why this paper is important}:
-\begin{itemize}
-	\item Provide a way to endogenize information in general equilibrium model.
-\end{itemize}
-
-% section gorton_and_ordonez (end)
-
-\section{Williamson, 87 QJE} % (fold)
-\label{sec:williamson_87_qje}
-
-\textbf{\bibentry{10.2307/1884684}}\\
-
-\cite{10.2307/1884684} mainly wants to explain two things:
-\begin{itemize}
-	\item Why is debt contract so popular?
-	\begin{itemize}
-		\item By MM Theorem, we know that in a frictionless world, debt contract is equivalent to equity contract. But we notice that most fund is raised through debt.
-		\item Explain by moral hazard. Borrower has private information on outcome. And lender has to pay for checking.
-	\end{itemize}
-	\item Why there is credit rationing?
-	\begin{itemize}
-		\item If the borrowing demand exceeds lending supply, why doesn't the interest rate increase to clear the market?
-		\item Because checking is costly, so incentive compatibleness requires interest rate not being too high.
-		They prove that the optimal interest rate is hump shape.
-	\end{itemize}
-\end{itemize}
-
-An IC contract $\{S,K(w),R(w)\}$ contains three parts.
-$S$ is the checking area.
-$K(w)$ is the transfer to lender when not checking.
-$R(w)$ is the transfer to lender when checking.
-Since the contract is IC, so the reported $\hat w$ is just actual realized $w$.
-
-There are three steps to prove the optimal contract is debt contract in this asymmetric information case.
-\begin{enumerate}
-	\item Prove $K(w)$ equals a constant x. [easy]
-	\item Prove the IR constraint of lender will be tight. [easy]
-	\item Prove $R(w)=w$, i.e. lender will take away everything in checking case. [difficult] 
-\end{enumerate}
-
-In the third step, the idea is easy.
-Because if lender takes away everything in checking case, then the checking area can be smaller, thus can save checking cost.
-The difficulty is: when we lower x (to make checking area A smaller), the non-checking area B becomes larger.
-The changes are in two different directions and problem becomes subtle.
-\textcolor{red}{In discussion we use the total differentiation approach to solve this.
-Important}.\\
-
-\noindent
-\textbf{Techniques:}
-
-\textbf{how to prove optimal contract format:}
-
-See above.\\
-
-\textbf{recursive structure in defining EQM:}
-
-One difficulty in determining the optimal contract is how to characterize outside options of lender.
-In equilibrium, When a lender decides whether to accept a contract from a specific borrower (entrepreneur), his outside option should be market interest rate $r$.
-Because entrepreneur can't identify lender, and all entrepreneur are homogeneous ex ante, so if the expected return from a specific contract should be larger than mkt interest rate $r$.
-Thus the IR of lender is:
-
-\[\int_A R(w)d(F(w))+\int_B xd(F(w))-\gamma Pr(A) \geq r\]
-
-$r$ has to be pinned down in the eqm. Because all agents have rational expectation, thus the market clearing $r$ will be the same as their expectation.
-
-The equilibrium is defined as:
-\begin{itemize}
-	\item 
-\end{itemize}
-
-% section williamson_87_qje (end)
-
-\section{Chari et.al, 14 AER} % (fold)
-\label{sec:chari_et_al_14_aer}
-
-\textbf{\bibentry{Chari_etal2014:aer}}
-
-\vspace{3mm}
-\noindent
-\textbf{Empirical Facts:}
-\begin{itemize}
- 	\item simultaneous fluctuation between secondary loan market and underlying land market
- 	\item persistence of collapse in secondary loan market trade volume
- \end{itemize}
-
- \noindent
- \textbf{Main Mechanism:}
- \begin{itemize}
- 	\item adverse selection AND reputation
- 	\item key assumptions:
- 	\begin{itemize}
- 		\item agent (bank) types persist over time
- 		\item players are non-annonymous (possible to build reputation)
- 	\end{itemize}
- 	\item adverse selection: can account for trade volume fluctuations correlated with underlying collateral value
- 	\item reputation:
- 	\begin{itemize}
- 		\item wihout reputation concern, adverse selection will be solved quickly. Because the first stage features a separating equilibrium
- 		\item with high enough reputation concern (patient enough), first stage cannot be fully separate, so adverse selection problem persists
- 	\end{itemize}
- \end{itemize}
-
-% section chari_et_al_14_aer (end)
-
-\chapter{Euro Crisis} % (fold)
-\label{cha:euro_crisis}
-
-This section is based on a course material of Wang Jue.
-Basically it discusses the theoretical concerns of Optimal Currency Area (OCA), why Europe adopts it, its success and its failure, and the recent Euro crisis.\\
-
-\textbf{\bibentry{Krugman:2012eu}}
-
-\cite{Krugman:2012eu} discusses the crisis of Euro area.
-Based on OCA theory by Mundell, there are two big things to look at: \textbf{labour mobility} and \textbf{fiscal integration}.
-Because areas are likely to suffer local idiosyncratic shocks.
-\begin{itemize}
-	\item Without labor mobility, a state has to make wage fall to restore the full employment, this will be much easier with its own to devalue.
-But if labor mobility is high, then workers can just move to other states.
-	\item Fiscal integration will also help. First because federal transfer is like a insurance, also because the borrowing cost for federal government is much lower.
-\end{itemize}
-The Euro crisis faces challenges in both parts.
-\begin{itemize}
-	\item The labor mobility is not high enough.
-	\item No fiscal integration. And the asymmetric shock is so severe, making fiscal burden so large that calls government solvency into question. (e.g. in Spain and Greek)
-	\item The bank issue. There is no `last resort', so the fear of sovereign default undermineds confidence in private banks which hold these bonds. This is called \textit{doom loops}.
-	\begin{itemize}
-		\item Compare between euro area countries and pegged-to-euro countries.
-Austria and Finland uses euro, but Finland just pegged to euro.
-This flexibility makes interest rate much lower during the crisis.
-	\end{itemize}
-\end{itemize}
-
-\vspace{2mm}
-\textbf{\bibentry{baldwin2015eurozone}}
-
-\chapter{Macro Seminar Notes} % (fold)
-\label{cha:macro_seminar_notes}
-
-\noindent
-\textbf{Cryptocurrency}
-
-\begin{itemize}
-	\item By Jesús Fernández-Villaverde and Daniel	Sanches 2017
-		.Use Lagos and Wright (2005) framework.
-	\begin{itemize}
-		\item \url{http://economics.sas.upenn.edu/~jesusfv/Cryptocurrencies.pdf}
-		\item Not positive on private currencies. First, competitive private money will not provide price stability, either with a profit-maximizing entrepreneurs or through automaton.
-		\item Even with price stability, value of private money may go zero in infinite equilibriums.
-		\item Purely private money system does not provide social optimal quantity of money.
-	\end{itemize}
-\end{itemize}
-
-\myline
-
-\textbf{\bibentry{Sorkin:18qje}}
-
-\begin{itemize}
-	\item Use Google Page Ranking algorithm to rank good firms. `good firms hire from other good firms and have few workers leave'. Reduce computation burden greatly.
-	\item Previous literature use hedonic approach to rank firms. Two drawbacks:
-	\begin{itemize}
-		\item Need to completely model and measure all relevant elements
-		\item Do not consider the utility dispersion case. [not understand]
-	\end{itemize}
-\end{itemize}
-
-\textcolor{blue}{Worth reading.}
-
-% section seminar_notes (end)
-
-% section euro_crisis (end)
-
-\part{Methodology} % (fold)
-\label{part:methodology}
-
-\chapter{Micro Foundations of Macroeconomics} % (fold)
-\label{cha:micro_foundations_of_macroeconomics}
-
-% section micro_foundations_of_macroeconomics (end)
-
-\noindent
-\textbf{Reductionism, and Micro Fundations of Economics:}
-
-Economists are fascinated in forming `micro fundations' for almost all models. But do we really need this, does this effort pay?
-
-As pointed in famous paper \cite{anderson1972:science}: `\textit{The ability to reduce everything to simple fundamental laws doesn't imply the ability to start from those laws and reconstruct the universe...
-At each level of complexity entirely new properties appear...
-There is no useful parallel to be drawn between the way in which complexity appears in simplest cases of many modies and chemistry and culture ones.}'
-The aggregated economy is so complicated that may not be reduced to individual decision problems.
-\footnote{Zhao Dingxing has an article discussing this problem.
-
-See \url{https://www.evernote.com/l/ATUOIdQb8hBM5r3QQv8cTK52Amq4-qlwb0E}}
-
-Another problem worth thinking is the relationship between Sonnethein-Debreu theorem and macro economics models.
-
-\vspace{2em}
-\noindent
-\textbf{Policy Making without Macroeconomic Theory:}
-\footnote{\href{https://docs.google.com/viewer?a=v&pid=sites&srcid=ZGVmYXVsdGRvbWFpbnxrb2NoZXJsYWtvdGEwMDl8Z3g6NDhhODQ0MTI1MWMyNDRjNQ}{Click for link to slides}}
-
-Kocherlakota (2018) points out that policy makers does not need to know economic theory, albeit the players are in the framework of theory.
-The key points of the theory are:
-\begin{itemize}
-	\item Private sectors are forward looking, but government is myopic
-	\item Gov suffers private taste shock, which will only affect the gov utility
-	\item Within an equilibrium, government can pick the optimal policy through simple regression over past actions and stages
-\end{itemize}
-
-\chapter{Decision Theory as a Foundation} % (fold)
-\label{cha:decision_theory_as_a_foundation}
-
-% section decision_theory_as_a_foundation (end)
-
-\vspace{3mm}
-\noindent
-\textbf{Meaning of Decision Theory:}
-
-(This part is heavily influenced by Henrique's class.)
-
-Why we need to do decision theory?
-Take an \textit{inverse engineering} perspective.
-Suppose we have a model, which uses utility function to describe people's decison choices. 
-That is, $u:X \rightarrow \R$.
-And we define $C(B)=\argmin_{x\in B} u(x)=
-\{x\in B | u(x)\geq u(y),\forall y\in B\}$.
-We can map such functions to a \textit{equivalent class}, and can further map it to a \textit{preference relation} (a subset of relations).
-
-The problem is such mapping is not surjective.
-Every utility function has a corresponding equivalence and a prefence relation,
-but there is some preference relation that cannot be represented by a utility function.
-Thus we need to put some restrictions over preference relation.
-
-The first relation is that the cardinality of indifference curves cannot be larger than $\R$.
-This is easy to understand.
-
-But this restriction is not enough.
-Think of lexicographic preference,
-every point in the two-dimension space is a indifference class.
-The cardinality of which is $R^2$, equivalent to cardinality of $\R$.
-But we know that such preference do not have a corresponding utility function.
-We can further restrict preference to \textit{order separable} relations,
-then by Debreu Thm, we can show the \textit{iff} between utility and preference relations.
-
-\begin{defn}[Order Separable]
-A preference relation defined over $X$ is order separable if $\exists Y \subseteq X$ countable s.t. $\forall x_1,x_3 \subseteq X$,
-we have $x_1 \succ x_2 \Rightarrow \exists y \in Y$
- s.t. $x_1 \succ y \succ x_2$.
-\end{defn}
-
-Important here is thaat by assuming the range of utility function is $\R$ (such a weak condition),
-we actually put some restrictions over preference.
-
-\vspace{3mm}
-\hrule
-\vspace{3mm}
-
-\vspace{2mm}
-\noindent
-\textbf{Calibration:}
-
-\noindent
-Why use calibration instead of estimation?
-\begin{itemize}
-	\item Because we live in a `tenth-best' world, and our model only catches a small part of the world.
-	Use calibration we can fit the moments that our model fail to catch,
-	in this sense to be more accurate.
-\end{itemize}
-
-May use calibration parameters as an intuitive check of whether the code we wrote is correct.
-
-\myline
-
-\noindent
-\textbf{Research Reproducibility}
-
-\cite{Maniadis:2017gq} claims two aspects of reproducibility problem.
-First, it can be seen as an `evidence game', 
-where researchers have some private information
-and evaluators have to design a incentive compatible mechanism for publishing and granting.
-Second, empirical methods from meta-research may help. 
-(I don't understand the second part.)
-
-\cite{Maniadis:2017hi} in the same issue provides more detailed guide on what will affect the credibility of scientific research.
-It raises a concept post-study probability,
-\[PSP=\frac{(1-\beta)\pi}{(1-\beta)\pi+ \alpha(1-\pi)}\]
-where $\alpha$ is significance level, $1-\beta$ is power,
-and $\pi$ is the probability that a research question is actually true. $\pi$ can be think of as \textit{prior} given by theory.
-This is the fraction of `truly true and reported true' divided by `all reported true'.
-Easy to see, when $\pi$ is low, 
-the PSP can be very low even with low $\alpha$.
-This indicates that with those fields where theory can provide little guide,
-we have to be very skeptical to the `rejection' outcomes.
-They are very likely to be `false positive'.
-
-\cite{Spiess:2017tp} has a fantastic discussion of this from the perspective of econometrics and mechanism design.
-
-\myline
-
-\noindent
-\textbf{Lucas Critique:}
-
-\cite{Hoover:94JEMethod} views Lucas critique as pointing the causal inference and identification problem in econometrics.
-
-% chapter methodology (end)
-
-% chapter macro (end)
-\part{Mathematics}
-
-\chapter{General (mathematical) Skills} % (fold)
-\label{cha:general_mathematical_skills}
-
-\section{Log-Linearization}
-
-\noindent
-\textbf{Motivation}
-
-Why we need log linearizations?
-Because for most nonlinear discrete dynamic programming problems,
-we fail to find a closed solution.
-Thus we have to use numerical method or to find a approximation.
-By using log-linearization,
-we transform the nonlinear problem to a linear problem (around the steady state),
-and we know how to solve the linear diffrence equations.
-
-Another advantege of log-linearization is,
-the new variables are in forms of $\frac{x-x^*}{x^*}$,
-which is interpretable.\\
-
-% subsection: how to do log-linearization
-\subsection{How to do Log-Linearization}
-
-Log linearization is a common method to approximate non-linear function using Taylor expansion.
-
-When we do linearization in macroeconomics, one key is to find \emph{\textbf{steady state}} of the model.
-Then we do linearization aroud the steady state.
-
-The basic idea is, for functions like:
-\[f(x)=\frac{g(x)}{h(x)}\]
-
-take log in both sides:
-\[ln(f(x))=ln(g(x))-ln(h(x))\]
-
-By Taylor expansion, for a smooth function f(x) we have:
-\[f(x)=f(x^*)+\frac{f'(x^*)}{1!}(x-x^*)+o(1)\]
-
-Thus 
-\[lnf(x) \approx lnf(x^*)+\frac{f'(x^*)}{f(x^*)}(x-x^*)\]
-
-The above follows from the fact that $\frac{dln(f(x))}{dx}=\frac{f'(x)}{f(x)}$. Thus,
-\[lnf(x)-lnf(x^*)=\frac{f'(x^*)}{f(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}\]
-
-And the equation becomes:
-\[lnf(x^*)+\frac{f'(x^*)}{f(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}=lng(x^*)-lnh(x^*)
-\frac{g'(x^*)}{g(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}-
-\frac{h'(x^*)}{h(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}\]
-
-\[\frac{f'(x^*)}{f(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}=
-\frac{g'(x^*)}{g(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}-
-\frac{h'(x^*)}{h(x^*)} \cdot x^* \cdot \frac{x-x^*}{x^*}\]
-
-Dedine $\hat x=\frac{x-x^*}{x^*}$, and we are done.
-\[\frac{f'(x^*)}{f(x^*)} x^* \cdot \hat x=
-\frac{g'(x^*)}{g(x^*)} x^* \cdot \hat x-
-\frac{h'(x^*)}{h(x^*)} x^* \cdot \hat x\]
-
-Notice, when we use $\hat x$ in place of $x-x^*$in the approximation,
-don't forget to times $x^*$ !!\\
-
-% How to do log-linearization when there is Expectation
-
-\subsection{log-linearization when there is expectation (An Example)}
-
-It may be annoying to do log-linearization when there is expectation,
-because in general,
-log and expectation cannot switch.
-But if we don't switch, we cannot do the log-linearization as previous.
-For example, see Adda\&Cooper(2003) CH5, page 115.
-
-Suppose we have the following Euler equation:
-
-\[u'(c)=\beta E_{A'|A}u'(c)[Af'(k')+(1-\delta)]\]
-
-where $c=Af(k)+(1-\delta)k-k'$.
-
-These two expressions, along with the evolution of A,
-defines a system of equations.
-
-In this system, actually we do not have to take log,
-but directly do Taylor expansion at $c^*$, $x^*$ and $k^*$.
-We get:
-
-\begin{multline}
-u'(c^*)+u''(c^*)c^*\hat c_t=
-\beta E_{A'|A}[u'(c^*)(\bar Af'(k^*)+(1-\delta))
-+(\bar Af'(k^*)+(1-\delta))u''(c^*)c^*\hat c_{t+1}\\
-+u'(c^*)f'(k^*)\bar A\hat A_{t+1}+
-u'(c^*)\bar Af''(k^*)k^* \hat k_{t+1}]
-\end{multline}
-
-The first term in LHS and the first term in RHS cancel each other.
-And we divide both sides by $u'(c^*)$, and we will get:
-
-\begin{equation}\label{eq1}
-\frac{u''(c^*)c^*}{u'(c^*)}\hat c_t
-=\beta E_{A|A'}[\frac{u''(c^*)c^*}{u'(c^*)}\hat c_{t+1} \frac{1}{\beta}
-+f'(k^*)\bar A \hat A{t+1}
-+f''(k^*)k^*\hat k_{t+1}]
-\end{equation}
-
-Notice, we derive this based on the fact $\frac{1}{\beta}=\bar A f'(k^*)+(1-\delta)$.
-Because by FOC
-\[u'(c)=\beta E_{A'|A}V'(k')\]
-
-To derive $V'(k')$, we first derive $V'(k)$,
-by Envelop THM we get:
-\[V'(k)=u'(c)[Af'(k)+(1-\delta)]\]
-
-Substitute this into FOC we get:
-\[u'(c)=\beta E_{A|A'}[u'(c')(A'f'(k')+(1-\delta))]\]
-
-In this approach we fix A at the mean $\bar A$,
-and thus the steady state satisfy:
-\[1=\beta [\bar Af'(k^*)+(1-\delta)]\]
-
-Here, the introduce of $\bar A$ is to describe the steady state in existence of shock.
-We can see $\bar A$ as the "long term" growth of the economy,
-and the we investigate what's the optimal steady $k^*$ under this long-term growth rate.
-
-\textcolor{red}
-{But I still don't know why we can cancel the expectation in the RHS.}
-
-The equation \ref{eq1} is the linear function we want.\\
-
-\noindent
-\emph{Some Comments on the above method:}
-
-Although it seems that the above method uses no log-linearization,
-actually it does!
-
-(to be added later)
-
-% section log-linearization (end)
-
-\section{Supermodularity} % (fold)
-\label{sec:supermodularity}
-
-\noindent
-Reference: 
-\begin{itemize}
-	\item \href{run:resources/sobel_supermodularity.pdf}{Sobel's Notes:} \url{http://econweb.ucsd.edu/~jsobel/205f10/notes12.pdf}
-	\item \href{run:resources/monotone_comparative_statics.pdf}{A more detailed note:} \url{https://pages.wustl.edu/files/pages/imce/nachbar/monotonecomparativestatics.pdf}
-	\item \bibentry{topkis1998:supermodularity}
-\end{itemize}
-
-\section{Miscellanea} % (fold)
-\label{sec:miscellanea}
-
-\subsection{Elasticity} % (fold)
-\label{sub:elasticity}
-
-\begin{exmp}
-Suppose $Q=\sum{q_i}$, $p=Q^{1/\alpha}$ and define $s_i=\frac{q_i}{Q}$. In equilibrium, we have $s_i=s_i^*$.
-Then in equilibrium, we have $\frac{\partial p}{\partial q_i}=s_i^*/\alpha$ instead of $1/\alpha$.
-
-Why? In first look, $Q$ is linear in $q_i$, then the derivative $\partial p/\partial Q$ should be the same as $\partial p/\partial q_i$.
-The point is that $Q$ is just a aggregated notation.
-In equilibrium, small change in $q_i$ will induce small change in all $q_{j \neq i}$, thus the aggregate change in $Q$ will be proportion of change in $q_i$.
-\end{exmp}
-
-% subsection elasticity (end)
-
-% section miscellanea (end)
-
-% section supermodularity (end)
-
-% chapter general_mathematical_skills (end)
-
-\chapter{Probability} % (fold)
-\label{cha:probability}
-
-\begin{thm}[Linear Combination of Dependent Normal RV]
-Suppose \(\left(\begin{matrix}X\\Y \end{matrix}\right) \sim \mathcal{N}\left[ \left(\begin{matrix}\mu_X\\\mu_Y\end{matrix}\right), \Sigma_{X,Y} \right]\),
-then
-\(AX+BY+C \sim \mathcal{N}\left[ 
-\left(\begin{matrix}A& B \end{matrix}\right)
-\left(\begin{matrix}\mu_X\\\mu_Y\end{matrix}\right) + C, 
-\left(\begin{matrix}A & B \end{matrix}\right)\Sigma_{X,Y} \left(\begin{matrix}A^T \\ B^T \end{matrix}\right)\right]\).
-\end{thm}
-
-\begin{thm}[Kolmogorov's zero–one law]
-Let $(\Omega,F,P)$ be a probability space, and $F_n$ be a series of independent $\sigma$-algebras contained in $F$.
-Let
-\[G_n = \sigma \left( \cup^\infty_{k=n} F_k\right)\]
-Then we define tail event $F$ to be any event such that:
-\[F \in \cap^\infty_{n=1}G_n\]
-Kolmogorov zero-one law claims that $Pr(F)=0$ or $Pr(F)=1$. 
-\end{thm}
-
-Intuitively, if the occurrence of a event $F$ can be determined when any finite initial segment is removed, then it either happens or not with probability 1.
-
-\section{Distributions} % (fold)
-\label{sec:distributions}
-
-\begin{itemize}
-	\item Pareto Distribution
-	\item T1EV (Type 1 Extreme Value)
-\end{itemize}
-
-% section distributions (end)
-
-\section{Bayesian Statistics} % (fold)
-\label{sec:bayesian_statistics}
-
-\subsection{Bayesian Updating} % (fold)
-\label{sub:bayesian_updating}
-
-\begin{thm}[Bayesian Update in Odds]
-For hypothesis $H$, data $d$ and prior odds $O(H)$. We have posterior odds 
-$O(H|d) = O(H)\cdot\frac{Pr(d|H)}{Pr(d|H^c)}$,
-where the second term is called \textit{Bayes Factor}.
-\end{thm}
-
-\begin{myproof}
-\begin{align*}
-	O(H|d)&=\frac{Pr(H|d)}{Pr(H^c|d)} \\
-	&=\frac{Pr(d|H)Pr(H)}{Pr(d|H^c)Pr(H^c)}\\
-	&=\frac{Pr(d|H)}{Pr(d|H^c)}\cdot O(H)
-\end{align*}
-\end{myproof}
-
-% subsection bayesian_updating (end)
-
-% section bayesian_statistics (end)
-
-% chapter probability (end)
-
-\chapter{Numerical Methods} % (fold)
-\label{cha:numerical_methods}
-
-\noindent
-\textbf{Computation laguage:}
-\begin{itemize}
-	\item \url{http://economics.sas.upenn.edu/~jesusfv/comparison_languages.pdf}
-	\begin{itemize}
-		\item discusses efficiency of different languages
-		\item hybrid language can significantly increase efficiency
-	\end{itemize}
-\end{itemize}
-
-\noindent
-\textbf{Matlab Speed Up:}
-\begin{itemize}
-	\item Microeconometrics and Matlab: an Introduction, Ch-10
-	\item vectorize and preallocate values
-		\begin{itemize}
-		 	\item Cooper's growth model uses clever vectorizing, avoid one loop
-		 \end{itemize} 
-	\item profiling code: profile on, main, profile off
-	\item parallel computing
-\end{itemize}
-
-\section{Numerical Maximization} % (fold)
-\label{sec:numerical_maximization}
-
-\noindent
-\textbf{Newton-Raphson Method:}
-
-Idea: use quadratic function to approaximating real function at current guess,
-then find the maximization point of this quadratic function as next guess.
-\[\beta_{t+1}=\beta_t + \lambda(-H^{-1}_t)g_t\]
-where $H_t$ is the Hessian of the function to be evaluated at $\beta_t$, 
-and $g_t$ is the Jacobian at $\beta_t$,
-$\lambda$ is the step size, generally may take 1.
-
-\vspace{3mm}
-\noindent
-\textbf{BHHH Method:}
-
-Idea: almost the same as Newton-Raphson, but use the outer product to approximate Hessian.
-\[\beta_{t+1}=\beta_t + \lambda(-B^{-1}_t)g_t\]
-where $B_t = \frac{1}{N}\sum_{n=1}^N{s_n(\beta_t)s_n(\beta_t)'}$
-and $s_n(\beta_t)= \partial P_n(\beta)/\partial \beta$ evaluated at $\beta_t$,
-and $g_t=\frac{1}{N}\sum_{n=1}^N{s_n(\beta_t)}$.
-
-Key is, when evaluated at maximum value, $s_n$ should be zero. Thus $B_t$ evaluated at maximum is the variance of $s_n$ in the sample, which is just the Hessian of the sample likelihood function.
-This is just \textit{information equality}.
-
-\begin{itemize}
-	\item [\textbf{pros:}] BHHH is generally faster than Newton-Raphson near the maximum.
-	Because $s_n$ have to be calculated anyway, 
-	but in NR procedure we have to calculate the second derivatives as well.
-	\textcolor{blue}{But seems this is not the case, in experiments BHHH always slower than Newton-Raphson.}
-	\item [\textbf{cons:}] BHHH is generally slower when $\beta_t$ is far from true value. 
-	Because at these points $B_t$ is not a good approximate of $H_t$.
-\end{itemize}
-
-% section numerical_maximization (end)
-
-\begin{itemize}
-	\item Root Solving
-	\item Integration
-	\begin{itemize}
-		\item Gaussian quadrature
-		\item Sparse grid
-		\item Monte Carlo integration
-		\begin{itemize}
-			\item antithetic accelerating
-			\item importantce sampling
-		\end{itemize}
-		\item Quasi Monte Carlo
-	\end{itemize}
-\end{itemize}
-
-% chapter numerical_methods (end)
-
-\bookmarksetup{startatroot}% this is it
-\addtocontents{toc}{\bigskip}% perhaps as well
-
-\chapter{Miscellany} % (fold)
-\label{cha:miscellany}
-
-\noindent
-\textbf{Presentation:}
-\begin{itemize}
-	\item Always \textit{motivate} very clearly, both from economics facts and from literature.
-	\begin{itemize}
-		\item In macro, a graph generally helps
-	\end{itemize}
-	\item Make clear propositions so that others won't misunderstand.
-	\begin{itemize}
-		\item Bad: analyze the competitive pattern of inter-brand and intra-brand
-
-		Good: Analyze how the per store profit is affected by own-brand store density and competitors' store density
-	\end{itemize}
-	\item If possible, always use a simple model at the beginning
-	\begin{itemize}
-		\item To pin down the concepts/definitions
-		\item To show the mechanism intuitively
-	\end{itemize}
-	\item Understand the result both mathematically and intuitively
-	\item Visualization:
-	\begin{itemize}
-		\item If only the scale of number is important, use a \textit{plot} instead of table full of numbers
-	\end{itemize}
-	\item When writing on the board, write horizontally!
-\end{itemize}
-
-\vspace{1em}
-\noindent
-\textbf{Writings:}
-\begin{itemize}
-	\item Good writing samples: \cite{Berry:1992gl}, \cite{doi:10.3982/ECTA7699}
-	\begin{itemize}
-		\item \cite{doi:10.3982/ECTA7699}: a good example of illustrating clear empirical results
-	\end{itemize}
-\end{itemize}
-
-% part miscellany_ (end)
-
-\renewcommand\refname{Reference}
-\bibliographystyle{chicago}
-\bibliography{reference}
-
-\end{document}

### 2020-07-30 paper_notes_2.tex
update

@@
 
-\chapter{Matching} % (fold)
-\label{cha:matching}
+\chapter{Treatment Effects} % (fold)
+\label{cha:treatment_effects}
 
-\section{General Matching} % (fold)
-\label{sec:general_matching}
+\paragraph{Ideal RCT}
+
+What can ideal RCT achieve?
+The limit of RCT identification is the marginal distribution of $Y_i(0)$ and $Y_i(1)$, and henceforth any function of the two.
+Therefore, $ATT \equiv E[Y_i(1)-Y_i(0)]$ is identified, while $\theta\equiv corr(Y_i(1),Y_i(0))$ is not identified, because the later requires $E[Y_i(1)Y_i(0)]$ which is unidentified.
+
+\section{Matching} % (fold)
+\label{sec:matching}
 
@@
 This estimator also reveals the close relationship between regression estimator and matching estimator (below following MHE p.82).
+
+\paragraph{Propensity Score and Fixed Effects}
+
+\citet{ArkhangelskyImbens2019} discusses how the propensity score can relax some assumptions of fixed effect.
+The traditional FE model usually assumes a linearly additive group term (fixed effect), and such linearity is too restrictive.
+
+The paper is motivated by the numerical equivalence:
+\[
+    Y_{i}=\alpha_{C_{i}}+W_{i} \tau+X_{i}^{\top} \beta+\varepsilon_{i}
+\] 
+is equivalent to
+\[
+    Y_{i}=\alpha+W_{i} \tau+X_{i}^{\top} \beta+\bar{W}_{C_{i}} \delta+\bar{X}_{C_{i}}^{\top} \gamma+\varepsilon_{i}
+\]
+\grey{KZ: I cannot derive the above two equation. And I failed to find relevant proofs in \citet{Mundlak1978}.}
+
+So fundamentally the underlying identification assumption is:
+\[
+    W_{i} \perp\left(Y_{i}(0), Y_{i}(1)\right) | X_{i}, \bar{W}_{C_{i}}, \bar{X}_{C_{i}}
+\]
+They also show that the \underline{ATE is consistent} even if the conditional mean function is \underline{misspecified}, as long as we we weight the unit by \underline{inverse of propensity score}.
+\[
+    \left(\hat{\alpha}_{c}, \hat{\tau}, \hat{\beta}\right)=\arg \min _{\alpha_{c}, \tau, \beta} \sum_{i=1}^{N}\left(Y_{i}-\alpha_{C_{i}}-W_{i} \tau-X_{i}^{\top} \beta\right)^{2} \frac{1}{p\left(X_{i}, C_{i}\right)^{W_{i}}\left(1-p\left(X_{i}, C_{i}\right)\right)^{1-W_{i}}}
+\]
+
+\grey{They also propose the estimator, but I do not understand those parts.}
 
@@
 
+Basics: \citet{BerryLevinsohnPakes1995}
+
+Micro moments: \citet{Petrin2002}, \citet{BerryLevinsohnPakes2004}
+
+Vertical relationships: \citet{Villas-Boas2007}, \citet{CrawfordYurukoglu2012}
+
+Durable consumptions: \citet{HendelNevo2006}
+
+\chapter{Vertical Relationships} % (fold)
+\label{cha:vertical_relationships}
+
+\paragraph{\citet{CrawfordYurukoglu2012}} This paper uses a Nash-in-Nash model to model the bargain process between upstream and downstream firms.
+Recall that in \citet{Villas-Boas2007}, the contract is either linear, or that upstream/downstream has all bargain power. This paper is a generalization in this aspect.
+
+% chapter vertical_relationships (end)
+
 \section{Villas-Boas, 2007 RES} % (fold)
@@
 
-The main goal of this paper is to recover the margins of both retailers and whosalers with only retailing data.
+The main goal of this paper is to recover the margins of both retailers and wholesalers with only retailing data.
+Unlike later papers like \citet{CrawfordYurukoglu2012} which endogenizes a bargain process, the relationship between the upstream and downstream firms are assumed to be one of the several stylized forms: simple linear contract, wholesaler with all rents, retailer with all rents.
+The paper tries to tell which one is more likely to be the truth among these stylized models.
 
@@
 \[
-    s_{it} + \sum_{j \ in \mathcal J} [p_{jt} - p^w_{jt} - c^r_{jt}] \mathds 1\{i,j \in \mathcal J_r\} \frac{\partial s_{jt}}{ \partial p_{it}} = 0,\ \  \forall i \in \mathcal J
+    s_{it} + \sum_{j \ in \  \mathcal J_t} [p_{jt} - p^w_{jt} - c^r_{jt}] \mathds 1\{i,j \in \mathcal J_r\} \frac{\partial s_{jt}}{ \partial p_{it}} = 0,\ \  \forall i \in \mathcal J_t, \forall t
 \]
 
-Then stack all products in the market together in the market (this step is tricky):
-\[
+Then stack all products in the market together in the market to write the matrix form:
+\begin{align*}
+    s_t(p) + (T_r * \Delta_r)(p_t-p_t^w-c_t^w) = 0 \\
+    \Rightarrow
     p_{t}-p_{t}^{w}-c_{t}^{r}=-\left(T_{r} * \Delta_{r t}\right)^{-1} s_{t}(p)
-\]
+    \tag{6}
+\end{align*}
 where $T_r$ is the ownership matrix, $T_r(i,j)$ equals to 1 if $i,j$ belong to the same owner, other wise 0. 
@@
     p_{t}^{w}-c_{t}^{w}=-\left(T_{w} * \Delta_{w t}\right)^{-1} s_{t}(p)
+    \tag{11}
 \]
+
+\paragraph{Estimation}
+
+This paper does not really estimate the supply side.
+Instead, it estimates only the demand side of retailers, then use this demand side to back out the margins of both retailers and wholesalers.
+The margins can be backed out by equation (6) and (11) RHS.
 
@@
 
-\citet{Rust1987} proposes Fixed Nested Point approach.
+\citet{Rust1987} proposes Nested Fixed Point approach.
 The bad thing is computation complexity.
@@
 \[
-    \begin{array}{l}{V\left(i_{t}, \omega_{t}, \varepsilon_{t}, \nu_{t}\right)} \\ {\quad=\operatorname{Max}_{\{c, x\}}\left\{u\left(c+\nu_{t}\right)-C\left(i_{t+1}\right)+\omega_{x t}+\varepsilon_{x t}\right.} \\
-    \quad \quad \quad {\left.\quad+\delta E\left[V\left(i_{t+1}, \omega_{t+1}, \varepsilon_{t+1}, \nu_{t+1}\right) | i_{t}, \omega_{t}, \varepsilon_{t}, \nu_{t}, c, x\right]\right\}}\end{array}
+    \begin{array}{l}{V\left(i_{t}, \omega_{t}, \varepsilon_{t}, \nu_{t}\right)} \\ {\quad=\operatorname{Max}_{\{c, x\}}\left\{u\left(c+\nu_{t}\right)-C\left(i_{t+1}\right)+\blue{\omega_{x t}}+\varepsilon_{x t}\right.} \\
+    \quad \quad \quad {\left.\quad+\delta E\left[V\left(i_{t+1}, \blue{\omega_{t+1}}, \varepsilon_{t+1}, \nu_{t+1}\right) | i_{t}, \omega_{t}, \varepsilon_{t}, \nu_{t}, c, x\right]\right\}}\end{array}
 \]
@@
 
+\chapter{School Effectiveness (Value Added)}
+
+Notice that most structural paper makes the school value added as homogeneous within a school, not heterogeneous across students, why? 
+Examples include \citet{Allende2019,Neilson2018}.
+This can be another contribution of my paper.
+
+\section{Black-White Gap} % (fold)
+\label{sec:black_white_gap}
+
+\paragraph{\citet[AEJ:AE]{ElderZhou2020}} This paper shows that the black-white gap in non-cognitive ability is underestimated. 
+Because non-cognitive ability is reported by the teachers, and the teacher will use similar peers as references. 
+Black students have poorer behaved peers than their white classmates.
+The authors use more objective measures like test scores to correct this subjective measure.
+The underlying assumption is that there are correlations between the objective and subjective measures between schools.
+This paper needs further read, I have not read the actual method yet.
+
+% section black_white_gap (end)
+
+% chapter end
+
 \chapter{Demand for Education}
@@
     \end{itemize}
+    \item Using discrete choice models: \citet{Allende2019}, \citet{Neilson2018}
 \end{itemize}
@@
     \item \textcite{MacLeodUrquiola2012}, \textcite{GilrainePetronijevicSingleton2019}
+    \item \citet{Neilson2018}
 \end{itemize}
@@
 \paragraph{\citet{HastingsKaneStaiger2009}}
-They use a simple exploded logit model to show that the demand for high academic quality is heterogeneous across families.
+They use a simple exploded logit model to show that the demand for high academic quality are heterogeneous across families.
 The more affluent families put higher weights on academic performance, but poorer families and minorities put higher weights in the race composition of the school.
@@
 
+\red{Add their IV strategy}
+
 Cons:
@@
 They also find the effect is more salient for black and Hispanic students.
+
+\section{Discrete School Choice} % (fold)
+\label{sec:discrete school choice}
+
+There are a growing literature showing this, borrowing tools from IO, including \citet{Neilson2018}, \citet{Allende2019}.
+
+\paragraph{\citet[JMP]{Allende2019}}
+
+This paper features \underline{endogenous school quality} + \underline{student sorting} + \underline{social interactions}.
+\grey{Worth carefully re-reading, and also the reference here.}
+
+The schools have three stages: 1) quality investment; 2) price setting; 3) school demand based on quality, price, and social interactions.
+
+The school quality $\theta_{jt}$ is assumed to be \underline{uniform} within a school, though it can depend on certain policies:
+\[
+    Y_{i j t}(\tau)=\mathbf{X}_{i t}^{\prime} \pi^{x}+\theta_{j t}(\tau)+\epsilon_{i j t}
+\]
+The school quality $\theta_{jt}$ can be further decomposed to inputs:
+\[
+    \theta_{j t}(\tau)=\mathbf{z}_{j t}(\tau)^{\prime} \pi^{z}+\underbrace{\mathbf{I}_{\mathrm{jt}}(\tau)^{\prime} \pi^{I}(\tau)+\epsilon_{j t}^{s}(\tau)}_{\mu_{j t}(\tau)}
+\]
+Notice, in this paper \blue{only $\mu_{jt}(\tau)$ is relevant}, there is no further decomposition of the terms.
+
+\mysubtitle{Demand side:}
+
+Individual utility is typical as in BLP and \citet{Neilson2018}.
+It also includes some unknown student level unobservables, I guess this is because they do not have huge computation burden in other parts.
+
+\grey{Why the price coefficient $\alpha_i$ and distance coefficient $\beta_i^d$ not have unobservable part? What is special about price and distance? (page 20)}
+
+The demand is based on \textit{nodes} and \textit{schools}. 
+This setting is similar to \citet{Neilson2018} and leverages the detailed node-level geographic data.
+The choice probability is defined as:
+\[
+    \mathcal{S}_{i j t}^{n k}\left(\boldsymbol{\mu}, \mathbf{p}, \mathbf{z}^{y}, \mathbf{z}^{e}\right)=\left(\frac{\exp \left(U_{i j t}\left(\boldsymbol{\mu}, \mathbf{p}, \mathbf{z}^{y}, \mathbf{z}^{e}\right)\right)}{\sum_{l \in \Omega_{i}} \exp \left(U_{i l t}\left(\boldsymbol{\mu}, \mathbf{p}, \mathbf{z}^{y}, \mathbf{z}^{e}\right)\right)}\right)
+\]
+where $i$ is student, $j$ is school, $t$ is time, $n$ is node, $k$ is the student type. 
+Student type $k$ is observable. $\mu$ is school quality, $p$ is tuition, $z^y, z^e$ are school observable characteristics.
+Note that the information is aggregated at the node-school level, so she uses GMM instead of MLE, thus the computation burden is smaller.
+
+Student body composition is assumed to be perfectly expected by the family.
+
+\mysubtitle{Supply side:}
+
+Similar as in \citet{Neilson2018}, the private schools are profit-maximizing, with following cost structure:
+\[
+    M C_{j}\left(\mu_{j t}\right)=\sum_{l} \gamma_{l} w_{j t}^{l}+\gamma_{\mu} \mu_{j t}+\omega_{j t}
+\]
+\[
+    F C_{j}\left(\mu_{j t}\right)=\sum_{l} \lambda_{l} w_{j t}^{l}+\psi_{j t} \mu_{j t}, \quad \text { where } \psi_{j t}=\bar{\psi}_{j}+\Delta \psi_{j t}
+\]
+\grey{One difficulty in my paper is that I cannot really observe the cost characteristics $w_{jt}^l$, but instead the monetary expenditure.
+Possible solutions: to find more direct cost characteristics data.}
+
+A worth learning feature in this paper is that Allende \blue{(analytically) decompose the effects} to direct effects, peer effects, and strategic social effects, which makes it clear about the channel of this model.
+
+\mysubtitle{Identification}
+
+There are three endogeneity to be solved: the quality of school, the price of school, and the student composition.
+
+The main identification leverages a natural experiment: the public school teacher strike in Lima. This makes more students turn to private schools.
+
+IV for \underline{student body composition}:
+\begin{itemize}
+    \item Lagged strike exposure index
+    \item Local market structure: share of private and number of schools
+    \item Local demographics: share of high SES
+\end{itemize}
+
+IV for \underline{price and quality}: (all distance weighted when applicable)
+\begin{itemize}
+    \item Public school teacher wage index
+    \item Public school teacher vacancies for post-reform contracts (distance weighted)
+    \item Stock of graduates with education degrees ($t-1$)
+    \item Tests scores for teachers ($t-1$)
+    \item The flow of new graduates with education degrees in the market
+\end{itemize}
+
+Notice that she presents all the first stages to show relevance.
+\grey{Seems this only requires school level data so can be done soon?}
+
+RD to identify \underline{price parameters}:
+\begin{itemize}
+    \item There is individual level variation in price generated discontinuity of private school voucher program.
+\end{itemize}
+
+% section endogenous_school_decisions (end)
 
@@
 
+\chapter{Road Construction Program}
+
+\noindent
+\textbf{Some Research Ideas}
+
+\begin{enumerate}
+    \item The price elasticity of the farmers before and after market access
+\end{enumerate}
+
+\paragraph{\citet{Aggarwal2018}}
+
+This paper is very similar to \citet{AdukiaAsherNovosad2019,AsherNovosad2019,Shamdasani2019} in terms of topics.
+It includes a lot of details of the rural road construction plan effects.
+
+To sum up:
+\begin{enumerate}[nosep]
+    \item Enrollments: enrollments for children less than 14 years old increase, while for elder than 14 years old decrease.
+    \item Employment: the decrease in enrollments in elder teenagers all goes to increase in work, for both boys and girls (table 7).
+    \item Employment sector: The increase in employment does not go to agriculture sector, for both boys and girls (table 8).
+For boys, the highest increase is in construction sector, and for girls is in animal rearing sector.
+    \item Employment Locations: For prime-age men (25-45) and girls, huge increase in urban works, smaller increase for boys, almost no increase for prime-age women (table 11).
+    \item Food diversity increases.
+    \item Fertilizer use increases.
+\end{enumerate}
+
+\paragraph{\citet{AdukiaAsherNovosad2019}}
+
+This paper studies the effect of massive road construction plan on rural enrollments in India.
+The prior is ambiguous in the direction of the effect.
+On the one hand, the road makes villagers easier to go outside for a higher wage, which lowers the incentive to stay at school;
+on the other hand, the road makes the diploma more worthy since the human capital can sell a better price outside of the village, which increases the incentive to stay at school.
+\textbf{Method:}
+This paper uses a RD method to get the causal effect.
+They leverage the fact that the road construction is discontinuous at some village population level, like 1000. But other covariates are continuous around that threshold.
+\textbf{Data:}
+The data they use is the same as \citet{AsherNovosad2019}, which is now public.
+\textbf{Conclusion:}
+They find that the middle school enrollments significantly increase after the road construction.
+
+\paragraph{\citet{Shamdasani2019}}
+
+This paper shows the massive road construction program has \textbf{heterogeneous} effect on villages, depending on their proximity to the town. 
+Villages far from the town are still not convenient to go to the town after road construction. 
+Thus, the first order effect for such villages is that they experience large gains in agriculture through crop diversification, with effects operating through rural-to-rural labor market integration.
+Such effects are huge, in the scale of 20\% to 50\%.
+\textbf{Method:} DiD.
+
+Closely related to \citet{AsherNovosad2019}.
+But this paper seems to use some independent data, worth reading.
+
+KZ: My derived idea from this is that the road construction has heterogeneous effects to the different villages, thus should have different effects on school enrolling decisions.
+For example, if there is no working opportunity in the village for high school graduates even after the road construction, then they shall not have incentive to enroll into high school.
+In contrast, if in near villages high school graduates can migrate into the town, then they will have higher incentive to enroll.
+The opposite may arise, though, if the young workers are important.
+
+\paragraph{\citet{Reis2020}}
+
+This paper uses a dynamic model similar to \citet{AttanasioMeghirSantiago2011} to study the joint problem of girls' enrolling and mothers' working decisions.
+
+I don't understand why this paper can be published in IER...
+
+\paragraph{\citet[IZA WP]{NajeebMoraleLopez-Acevedo2020}}
+
+This paper documents some important facts about female employment in south Asia.
+They find that 
+``(i) overall since 2001, women’s employment participation across South Asian countries has been low and broadly unchanged; (ii) the gender employment gap emerges more clearly in middle age brackets; (iii) rural female employment is higher than urban; (iv) agriculture is the economic sector accounting for the greatest share of female employment, although this is slowly changing in some countries, and; (v) women with mid-level education tend to have lower employment rates than those with both lower and higher education.''
+
 \clearpage
